### 2019-10-02 docs/EPJP-2019/Gross-EPJP-2019 - rev1.tex
Journal and conference papers - tex, bibtex and figures
Journal and conference papers

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for The European Physical Journal PLUS
%
% Copy it to a new file with a new name and use it as the basis
% for your article
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag / Societa` Italiana di Fisica  %%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{filecontents}{leer.eps}
!PS-Adobe-2.0 EPSF-2.0
%%CreationDate: Mon Jul 13 16:51:17 1992
%%DocumentFonts: (atend)
%%Pages: 0 1
%%BoundingBox: 72 31 601 342
%%EndComments

gsave
72 31 moveto
72 342 lineto
601 342 lineto
601 31 lineto
72 31 lineto
showpage
grestore
%%Trailer
%%DocumentFonts: Helvetica
\end{filecontents}
%
\documentclass[epj]{svjour}
% Remove option referee for final version
%
% Remove any % below to load the required packages
%\usepackage{latexsym}
\usepackage{mathtools} % Loads amsmath
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{authblk}
\usepackage{xfrac}
\usepackage{graphicx}
%\usepackage[colorlinks=true,linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref} % for hyperrefs
%\usepackage{cleveref}
%\usepackage[authoryear]{natbib}
\usepackage{gensymb}  % provides macro \degree which works in text and math
\usepackage{color}
%\usepackage{enumitem} 
\usepackage{bm}
\usepackage{multirow}
\usepackage{cite}
\usepackage{tikz}
\usetikzlibrary{arrows}

% for quotes
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

% for flow charts
% Define block styles
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\tikzstyle{discre} = [rectangle, draw, fill=white!20, 
text width=6em, text centered, minimum height=3em, node distance=3.5cm, line width=1pt]
\tikzstyle{decision} = [diamond, draw, fill=white!20, 
text width=3em, text badly centered, node distance=2cm, inner sep=1pt, line width=1pt]
\tikzstyle{block} = [rectangle, draw, fill=white!20, 
text width=6em, text centered, minimum height=3em, node distance=3.5cm, line width=1pt]
\tikzstyle{blockEq} = [rectangle, draw, fill=white!20, 
text width=8em, text centered, minimum height=3em, node distance=3.5cm, line width=0pt]
\tikzstyle{cloud} = [draw, ellipse,fill=white!20, node distance=4cm,
text centered, text width=3em, minimum height=2em, line width=1pt]
\tikzstyle{line} = [draw, -{latex'}, line width=1.0pt]

% For merging cells 
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}

% etc
%

\newcommand{\eq}[1]{Eq.~(\ref{#1})}
\newcommand{\eqnolabel}[1]{(\ref{#1})}
\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
\newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
\newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
\newcommand{\tbl}[1]{Table~\ref{#1}}
\newcommand{\tblnolabel}[1]{\ref{#1}}
\newcommand{\tbls}[1]{Tables~\ref{#1}}
\newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
\newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\fignolabel}[1]{\ref{#1}}
\newcommand{\figs}[1]{Figs.~\ref{#1}}
\newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
\newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
\newcommand{\sxn}[1]{Section~\ref{#1}}

\newcommand{\revised}[1]{{\color{red}{#1}}}
\newcommand{\tsup}[1]{\textsuperscript{#1}}
\newcommand{\tsub}[1]{\textsubscript{#1}}

\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}

\newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
\newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
\newcommand{\rr}{\ensuremath{\bm{r}}}
\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
\newcommand{\rE}{\ensuremath{(\rr,E)}}

\newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
\newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
\newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
%\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcL}{\tau}
\newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
\newcommand{\dx}{\ensuremath{\Delta x}}

%
% ---------------------------------------------------
\begin{document}
%
\title{High-accuracy neutron diffusion calculations based on integral transport theory}
%\subtitle{}
\author{
	Roy Gross\inst{1} \and 
	Daniele Tomatis\inst{2} \and 
	Erez Gilad\inst{1}\thanks{\email{gilade@bgu.ac.il} (corresponding author)}
}                     % Do not remove
%
%\offprints{}          % Insert a name or remove this line
%
\institute{
	The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel 
	\and
	CEA, DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),
	Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France}
%
\authorrunning{Gross, Tomatis \& Gilad} 
\titlerunning{Integral transport correction to diffusion calculations}
\date{Received: date / Revised version: date}
% The correct dates will be entered by Springer
%
\abstract{
In this paper, the Ronen method is developed, implemented and applied to resolve the neutron flux and the criticality eigenvalue in a simple homogeneous problem. The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and driven by the solutions of the integral transport equation. The local diffusion constants are modified in order to reproduce new estimates of the surface currents by a transport operator. The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme by means of drift terms. The corrected solutions are compared against reference results obtained  by a discrete ordinate code. Boundary conditions are discussed and proper approximations are introduced in order to conserve the particle balance. The results match extremely well the reference solutions, especially in the limit of fine meshes, but slow convergence of the scalar flux is reported.
%
\PACS{
	{28.00.00}{Nuclear engineering and nuclear power studies} \and
	{28.20.Gd}{Neutron transport: diffusion and moderation} \and
	{05.60.-k}{Transport processes} \and
	{28.41.-i}{Fission reactors}
     } % end of PACS codes
  \keywords{
  	neutron diffusion -- integral transport -- non-linear transport correction
  }
} %end of abstract
%
\maketitle
%
% ---------------------------------------------------
\section{Introduction}
\label{sec:intro}

Neutron transport calculations on a full core scale can be a highly intensive computational task. High-fidelity core design optimization or transient analyses can quickly become computationally impractical when using transport methods~\cite{Kim-2019}. For example, in order to achieve a 1\% accuracy in the local flux/power estimation, an order of 10\tsup{11} histories is needed in a full-core Monte Carlo calculation~\cite{Martin-2012}. Another problem is the huge number of variables and parameters to be stored and used during computation, e.g., tallies, geometry, cross sections, and depletion data. A conservative estimation of the memory needed for reasonably accurate full-core Monte Carlo neutronic calculation is in the range of terabytes (TBs)~\cite{Martin-2012}.

%The growing demand for high-accuracy and high-precision full-core computations challenges not only today’s high-end computing systems but will also challenge the near future (e.g., Exascale) computers~\cite{Martin-2012,Smith-2011,Kim-2019}.

To overcome this difficulty, faster (and less accurate) multigroup neutron diffusion solvers are frequently  used~\cite{Lawrence-1986,Smith-1986}. However, future Gen-IV reactor designs are characterized by strong heterogeneity in the core, e.g., axial and radial seed-blanket structures, as in the French ASTRID SFR CVF design~\cite{Bertrand-2016}, challenging the accuracy of diffusion calculations. Moreover, modern calculation schemes evolve towards so-called "best-estimate" codes, aiming at high accuracy~\cite{IAEA-BE-2008}.

A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient~\cite{Bell-1970,Pounders-2009}. The calculation of this parameter should be based on physical insights from the transport equation such that the resulting improved ("transport corrected") diffusion approximation can capture the transport phenomena of interest. Such transport corrections can be divided into two main classes. The first class is based on extending the $P_1$ model equations (and the associated boundary conditions) along with some closure scheme, such as the well-known $SP_3$ approximation~\cite{Brantley-2000}. The second class, to which this study belongs, is based on the re-calculation of the diffusion coefficients within the multigroup diffusion framework~\cite{Tomatis-2011}.

In this paper, the development, implementation, and qualification of the Ronen Method~\cite{Ronen-2004} in one-dimensional homogeneous plane geometry is reported. This method is implemented as a highly accurate multigroup neutron diffusion solver based on novel transport corrections. The main hypothesis underlying the Ronen method is based on iterative calculations of the multigroup diffusion coefficients driven by the solutions of the integral transport equation~\cite{Ronen-2004,Tomatis-2011}.

%This study addresses a critical issue in contemporary nuclear reactor calculations, which constitutes an inherent difficulty that will not be solved in the near future merely by increased computational capabilities. As modern and advanced nuclear systems become more complex and heterogeneous, the requirements for more precise and accurate calculations increase as well~\cite{Smith-2011,Martin-2012,Smith-2013,Tomatis-2011,Kim-2019}. This trend is not likely to fade away. In light of this trend, the development of highly accurate neutron diffusion calculations is of great importance for nuclear reactor's operation, safety, research, and design purposes.

The theoretical background is detailed in~\sxn{sec:theory}, the numerical implementation is described in~\sxn{sec:imp}, the results are presented in~\sxn{sec:res} and conclusions are brought in~\sxn{sec:conc}.

%
% ---------------------------------------------------
\section{Theoretical background}
\label{sec:theory}

%
% ---------------------------------------------------
\subsection{The Ronen method}
\label{sec:RM}

In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory. Denoting the integral transport and diffusion currents by $\jtr\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on changing the diffusion coefficient such that
\begin{equation}\label{eq:Fick}
\bm{J}_D\rE = -D\rE\bnabla\phi\rE = \jtr\rE \,\, . 
\end{equation}

Since these accurate estimates of the currents are based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation. 
\begin{equation}\label{eq:RM-it}
D^{(k+1)}\rE = - \jtr^{(k)}\rE \left[\bnabla\phi^{(k)}\rE\right]^{-1} \,\, ,
\end{equation}
where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.

The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus small neutron absorption rate with respect to scattering in general. Nevertheless, isotropic scattering remained as a basic postulate.
For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004} 
\begin{equation}\label{eq:RM-it-1D-slab}
D^{(k+1)}(x,E) = -\frac{\frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
{\partial \phi^{(k)}(x,E)/\partial x} \,\, .
\end{equation}

This idea was later used by Tomatis and Dall'Osso~\cite{Tomatis-2011}, who provided a numerical demonstration in a simple slab problem. Instead of updating the diffusion coefficient by the ratio of the current and the flux gradient, as in Fick's law, they adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver. 
%
%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
%
This technique, largely adopted in the literature of nodal methods~\cite{Smith-1983,Lawrence-1986}, can avoid indeterminate divisions in case of vanishing flux gradients. They tested this implementation in a homogeneous bare slab using two-group cross sections representative of a realistic PWR assembly. It was observed that the Ronen method (RM) could drive the flux distribution away from diffusion and closer to the reference solution of the integral Boltzmann transport equation, regardless of the initial formulation used for the diffusion coefficient. As expected, the largest errors were located near the boundary, where the transport effects are most pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.

%
% ---------------------------------------------------
\subsection{The one-dimensional Peierls equation}
\label{sec:Peierls}

There are several ways to drive the integral expression for the flux in slab geometry. Most of them start with assuming homogeneous and isotropic scattering and sources, yielding the \emph{Peierls equation} \cite{Davison-1957,Case-1967,Bell-1970,Pomraning-1973,Duderstadt-1979,Lewis-1984}. The derivation of expression for slab geometry (of thickness $a$) is straightforward, yielding
\begin{eqnarray}\label{eq:flux-slab-l-0-no-bndry-terms}
\phi(x,E)&=&\frac{1}{2}\int_0^a { dx'
	E_1\left[\sigma(E)\lvert x-x'\rvert\right] q(x',E) 
}\nonumber \\
&=& \frac{1}{2}\int_0^a { \!\!\! dx'
	E_1\left[\sigma(E)\lvert x-x'\rvert\right]
	\left[
	\int_0^\infty { \!\!\! dE'
		\sigma_s(E\leftarrow E')\phi(x',E') 
	} + S(x',E)
	\right] 
} \,\, ,
\end{eqnarray}
where $E_1(x)$ is a first order exponential integral~\cite{Abramowitz-1964}. Note that this expression does not include the contribution of uncollided neutrons originate from the flux at the boundaries.

Another starting point for the derivation of the integral expression for the flux in slab geometry is to directly integrate along a line the transport equation~\cite{Davison-1957,Pomraning-1973,Duderstadt-1979,Lewis-1984}
\begin{eqnarray}\label{eq:full-ITE-w-bndry-terms}
\psi(\rr,\OO) &=& \int_0^R { dR'
	q(\rr-R'\OO,\OO) e^{-\mcL(\rr,\rr-R'\OO)}
} 
%\nonumber \\
%&+& 
+\psi(\rr-R\OO,\OO) e^{-\mcL(\rr,\rr-R\OO)}
\,\, ,
\end{eqnarray}
where $\mcL(\rr,\rr-R'\OO)$ is the \emph{optical length}, defined as
\begin{equation}\label{eq:opl}
\mcL(\rr,\rr-R'\OO) \equiv 
\int_0^{R'} {\sigma(\rr-R''\OO)dR'} \,\, .
\end{equation}
Assuming isotropic scattering and homogeneous medium in one-dimension for~\eq{eq:full-ITE-w-bndry-terms} recovers~\eq{eq:flux-slab-l-0-no-bndry-terms}.

In what follows, a generalization of~\eq{eq:flux-slab-l-0-no-bndry-terms} is derived for heterogeneous medium with anisotropic scattering.  
%
% ---------------------------------------------------
\subsection{Integral expressions for the neutron flux \& current}
\label{sec:int-flux-J}

Consider an infinite one-dimensional slab of width $a$. The angular flux in the slab is given by~\cite{Lewis-1984}
\begin{subequations}\label{eq:int-ang-flx}
	\begin{eqnarray}
	\psi(x,E,\mu) &=& \psi(0,E,\mu) e^{-\mcL(0,x,E)/\mu}
	+ \int_0^x { dx' \,\,
		\frac{Q(x',E,\mu)}{\mu} 
		e^{-\mcL(x',x,E)/\mu} 
	} \,\, , \qquad \mu>0 \,\, ,   \label{eq:int-ang-flx-a}\\
	\psi(x,E,\mu) &=& \psi(a,E,\mu)e^{\mcL(x,a,E)/\mu} 
	-\int_x^a { dx' \,\,
		\frac{Q(x',E,\mu)}{\mu} 
		e^{\mcL(x,x',E)/\mu} 
	} \,\, , \qquad \mu<0 \,\, , \label{eq:int-ang-flx-b}
	\end{eqnarray}
\end{subequations}
where
\begin{equation}\label{eq:opl2}
\mcL(x',x,E) \equiv 
\int_{x'}^x {\sigma(x'',E) dx''} \,\, 
\end{equation}
and $Q(x,E,\mu)$ denotes all sources.

The angular dependence of the source and the uncollided boundary flux terms is expanded in a series of orthogonal Legendre polynomials
\begin{eqnarray}\label{eq:Q-series}
\psi(0,E,\mu) &=& \sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} \psi_l(0,E) \pl{\mu} 	
} \nonumber \\
\psi(a,E,\mu) &=& \sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} \psi_l(a,E) \pl{\mu} 	
} \,\, .
\end{eqnarray}
The source cross sections are written explicitly as~\cite{Tomatis-2011}
\begin{equation}\label{eq:src-mmnts}
\sigma_l(x,E\leftarrow E')dE' = 
\sigma_{s,l}(x,E\leftarrow E')dE'
+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, 
\end{equation}
and the source term is expanded 
\begin{eqnarray}\label{eq:src}
Q(x,E,\mu)&=& \sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} \int_0^\infty { dE'
		\sigma_{s,l}(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
	}
} 
+ \frac{\chi(E)}{2\keff} \int_0^\infty { dE'
	\nu\sigma_f(x,E') \psi_0(x,E')
}  \nonumber \\
&=&\sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} \int_0^\infty { dE'
		\sigma_l(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
	}
} \nonumber \\
&=&\sum\limits_{l=0}^\infty {
\frac{2l+1}{2} \int_0^\infty { dE'
	q_l(x,E\leftarrow E')\pl{\mu} 			
	}
} \nonumber \\
&=&\sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
} 
\,\, ,
\end{eqnarray}
where the source angular moments are defined as
\begin{equation}\label{eq:q_l}
q_l(x,E) \equiv \int_0^\infty dE' q_l(x,E\leftarrow E') \equiv 
\int_0^\infty dE' \sigma_l(x,E\leftarrow E')\psi_l(x,E') dE' \,\, .
\end{equation}

%with the corresponding coefficients
%\begin{eqnarray}\label{eq:Q-series-coeffs}
%q_l(x) &=& \int_{-1}^1 { d\mu
%	\psi(x,\mu)\pl{\mu} 
%} \nonumber \\
%\psi_l^0 &=& \int_{-1}^1 { d\mu
%	\psi(0,\mu)\pl{\mu} 
%} \nonumber \\
%\psi_l^a &=& \int_{-1}^1 { d\mu
%	\psi(a,\mu)\pl{\mu} 
%} \,\, .
%\end{eqnarray}

%The independent energy parameter is omitted here for brevity and clarity but restoring it is straightforward.
%
In order to calculate the scalar flux $\phi^+$ at $x$ resulting from neutrons coming from the left, i.e., $x'<x$ ($\mu>0$), substitute Eqs.~\eqref{eq:Q-series} in Eq.~\eqref{eq:int-ang-flx-a} and integrate over the angle 
\begin{eqnarray}\label{eq:phi+}
\phi^+(x,E)&\equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \nonumber \\
%&=& \int_0^1 {d\mu \psi(0,\mu) e^{-\mcL(0,x)/\mu} } 
%+ \int_0^1 {d\mu 
%	\int_0^x { dx'
%		\frac{Q(x',\mu)}{\mu} e^{-\mcL(x',x)/\mu} 
%	}
%}
%\nonumber \\
&=& \sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} 
		\left\{\psi_l(0,E) \int_0^1 { d\mu
		\pl{\mu} e^{-\mcL(0,x,E)/\mu}	
	}
	+	\int_0^x {\!\!\! dx'
		q_l(x',E)
		\int_0^1 { d\mu
			\frac{\pl{\mu}}{\mu} e^{-\mcL(x',x,E)/\mu}	
		}
	}
\right\}
} \,\, .
\end{eqnarray}

In order to solve the angular integrals we resort to the following result~\cite{Cengel-1984,Settle-1994}
\begin{equation}\label{eq:Sni}
\int_0^1 { 
	\mu^i \pl{\mu} e^{-y/\mu} d\mu
}
= \sum\limits_{m=0}^{[l/2]} {
	h_m E_{l+2+i-2m}(y)
} \,\, ,
\end{equation}
where $h_m$ is defined according to 
\begin{equation}\label{eq:h_i}
\pl{x}=\sum\limits_{m=0}^{[l/2]} {
	h_m x^{n-2m}
}
\end{equation}
and given explicitly by
\begin{equation}\label{eq:h_i-explicit}
h_m = \frac{(-1)^m (2l-2m)!}{2^l m! (l-m)! (l-2m)!}
\end{equation}
where
\begin{equation}\label{eq:l_2}
[l/2] = 
\begin{cases}
l/2, & l \text{ even}, \\
(l - 1)/2, & l \text{ odd}.
\end{cases}
\end{equation}
%
Hence, the contribution to the flux from $x'<x$ can be written as
\begin{equation}\label{eq:phi+2}
\phi^+(x)= \sum\limits_{l=0}^\infty {
	\frac{2l+1}{2} \sum\limits_{m=0}^{[l/2]} { h_m
		\left\{			
			 E_{l+2-2m}[\mcL(0,x,E)]			 
			 \psi_l(0,E) 
			+ 	\int_0^x { dx'
				E_{l+1-2m}[\mcL(x',x,E)]
				q_l(x',E)				
		} 
	\right\}
	}
} \,\, .
\end{equation}
The contribution to the flux from $x'>x$ ($\mu<0$) can be calculated in a similar manner, using the change of variables $\eta=-\mu$ for the angular integrals and the fact that $\pl{-\mu}=(-1)^l\pl{\mu}$, resulting in an expression for the scalar flux which accounts for anisotropic scattering and heterogeneous medium
\begin{eqnarray}\label{eq:int-scalar-flux}
\phi(x,E) &=& \phi^+(x,E)+\phi^-(x,E) \nonumber \\
&=& 
\sum\limits_{l=0}^\infty  \frac{2l+1}{2} 
\sum\limits_{m=0}^{[l/2]}  h_m
\bigg\{
E_{l+2-2m}[\mcL(0,x,E)]	\psi_l(0,E) 
+(-1)^l E_{l+2-2m}[\mcL(x,a,E)] \psi_l(a,E) 
\nonumber \\
&&+
		\int_0^x dx' E_{l+1-2m}[\mcL(x',x,E)] q_l(x',E)
		+(-1)^l \int_x^a dx' 
		E_{l+1-2m}[\mcL(x,x',E)] q_l(x',E)
\bigg\}	\,\, .		
\end{eqnarray}

%Defining $q_l(x,E)\equiv \int_0^\infty \!\!\!\! dE' \sigma_l(x,E\leftarrow E') \psi_l(x,E')$ 
%
The generalization of~\eq{eq:int-scalar-flux} to current is obtained in a similar procedure according to
\begin{eqnarray}\label{eq:tot-J}
J(x,E) &=& J^+(x,E) - J^-(x,E) = \int_0^1 {d\mu \mu \psi(x,E,\mu)} 
- \int_0^{-1} {d\mu \mu \psi(x,E,\mu)} \nonumber \\
&=&\sum\limits_{l=0}^\infty  \frac{2l+1}{2}
\sum\limits_{m=0}^{[l/2]}  h_m
\bigg\{
E_{l+3-2m}[\mcL(0,x,E)]	\psi_l(0,E) 
+(-1)^{l+1} E_{l+3-2m}[\mcL(x,a,E)]\psi_l(a,E)  \nonumber \\
&&+
\int_0^x dx' E_{l+2-2m}[\mcL(x',x,E)] q_l(x',E)
+(-1)^{l+1} \int_x^a dx' E_{l+2-2m}[\mcL(x,x',E)] q_l(x',E)
\bigg\}	\,\, . 
\end{eqnarray}
%
%For isotropic scattering ($l=0$), \eqsand{eq:int-scalar-flux}{eq:tot-J} reduce to the known expressions derived from the Peierls equation
%\begin{eqnarray}\label{eq:iso-flx-J}
%\ftr(x,E) &=& \frac{1}{2}\left\{\psi_0^0(E) E_2[\mcL(0,x,E)] 
%+ \psi_0^a E_2[\mcL(x,a,E)]\right\}
%+ \frac{1}{2}\int_0^a { dx' q_0(x',E)
%	 E_1\left[\lvert\mcL(x',x,E)\rvert\right]} \,\, , \nonumber \\
%\jtr(x,E) &=& \frac{1}{2}\left\{\psi_0^0(E) E_3[\mcL(0,x,E)] 
%- \psi_0^a E_3[\mcL(x,a,E)]\right\}
%+ \frac{1}{2}\int_0^a { dx' q_0(x',E)
%	 E_2\left[\lvert\mcL(x',x,E)\rvert\right]
%	sign(x-x') } \,\, .
%\end{eqnarray} 
%

%
% ---------------------------------------------------
\section{Numerical implementation}
\label{sec:imp}

The cross sections, as well as the diffusion coefficient, are usually available as volume-averaged data per cell in the mesh. Once the scalar flux is known from the finite differences solver using the original diffusion coefficients, the integral expressions derived in~\sxn{sec:int-flux-J} can be used to get new estimates of the currents $J$ at the cell interfaces.

Instead of computing new diffusion coefficients on the interfaces by Fick's law, $J_D(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\delta J(x_s,E) = \jtrr(x_s,E) - J_D(x_s,E)$ are obtained on cell interfaces $x_s$. Here, $J_D(x,E)$ is called the "diffusion current" and is obtained using Fick's law, with the original values of the homogeneous diffusion coefficients and with the derivative approximated by finite differences. In one-dimensional 
geometry and using the notation in \fig{fig:mesh1D}, the diffusion current and the corrective current are evaluated according to
\begin{eqnarray}\label{eq:JD-dJ}
J_D(x_{i+1/2},E) &\cong& -D(x_{i+1/2},E) 
\frac{\phi(x_{i+1},E) - \phi(x_i,E)}
{(\Delta x_{i+1} + \Delta x_i)/2} \nonumber \\
\delta J(x_{i+1/2},E) &=& -\delta D(x_{i+1/2},E) 
\frac{\phi(x_{i+1},E) + \phi(x_i,E)}
{(\Delta x_{i+1} + \Delta x_i)/2} \,\, ,
\end{eqnarray}
where integer and rational subscripts indicate node-averaged and interface quantities, respectively. The discretized form of the current $\delta J$ must involve the neighboring flux as well, but its representation is changed into a drift-advection term to get rid of possible undefined division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}. The so-called "transport current" $\jtrr(x_s,E)$ is evaluated using the integral expression derived in~\sxn{sec:int-flux-J} as described in~\sxn{sec:calc-int-curr}.

\begin{figure}[htbp!] 
	\centering
	\begin{tikzpicture}
	\tikzstyle{every node}=[font=\footnotesize]
	\draw[thick] (0,0) -- (3,0);
	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
	\draw[thick] (4,0) -- (7,0);
	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};

	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-1/2$};
	\node[anchor=south] at (1cm,1pt) {0};
	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+1/2$};

	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-1/2$};
	\node[anchor=south] at (5.5cm,1pt) {$i$};
	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+1/2$};

	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-3/2$};
	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-1/2$};
	\end{tikzpicture}
	\caption{Notation of the one-dimensional mesh.}
	\label{fig:mesh1D}
\end{figure}
%
Since the input diffusion coefficients are provided as node averaged, and they are always needed at interfaces, they are approximated by local volume averages:
\begin{equation}\label{eq:Ds}
D(x_{i+1/2},E) = \frac{\Delta x_i D(x_i,E) 
	+ \Delta x_{i+1} D(x_{i+1},E)}
{ \Delta x_i + \Delta x_{i+1}} \,\, .
\end{equation}

%
% ---------------------------------------------------
\subsection{The correction as a drift term}
\label{sec:corr-drift}

The new numerical corrections $\delta D$ are obtained on the interfaces using~\eq{eq:JD-dJ} to be used in the finite differences solver, together with the diffusive currents from~\eq{eq:JD-dJ}. Hence, the neutron balance resolved by the CMFD takes into account both types of currents $J_D$ and $\delta J$. %Non-linear iterations with new corrections given by $\delta J$ are needed because of their dependence on the unknown flux.
Hence, the one-dimensional multigroup neutron balance CMFD diffusion equations actually solved are
\begin{equation}\label{eq:diff1}
J_{D,g}^+(x) + \delta J_{D,g}^+(x) -  J_{D,g}^-(x) - \delta J_{D,g}^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x) \,\, ,
\end{equation}
where $J_{D,g}^\pm (x)\equiv J_{D,g}(x_{i\pm 1/2})$.

Using the definitions in~\eqsand{eq:JD-dJ}{eq:Ds} and~\fig{fig:mesh1D}, the discretized form of~\eq{eq:diff1} is
\begin{eqnarray}\label{eq:FD_diff_full}
- 2D_{i+1/2}^g\frac{\phi_{i+1,g}-\phi_{i,g}}{\dx_{i+1} + \dx_i}
- 2\delta D_{i+1/2}^g\frac{\phi_{i+1,g}+\phi_{i,g}}{(\dx_{i+1}+\dx_i)}
&+& 2D_{i-1/2}^g\frac{\phi_{i,g}-\phi_{i-1,g}}{\dx_{i} + \dx_{i-1}}  
+ 2\delta D_{i-1/2}^g\frac{\phi_{i,g}+\phi_{i-1,g}}{(\dx_i+\dx_{i-1})} 
\nonumber \\
&+& \sigma_{i}^g \phi_{i,g} 
= \sum\limits_{g'=1}^G \sigma_{s,i}^{g\leftarrow g'}\phi_{i,g'}
+ \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G
 \nu\sigma_{f,i}^{g'}\phi_{i,g'} 
\,\,.
\end{eqnarray}
Rearranging terms to get
\begin{eqnarray}\label{eq:FD_diff_org}
\left(
\frac{-D_{i-1/2}^g + \delta D_{i-1/2}^g }{\dx_{i-1}+\dx_{i}}
\right)
\phi_{i-1,g}
&+&\left[
\frac{D_{i+1/2}^g - \delta D_{i+1/2}^g}{\dx_{i+1}+\dx_i}
+\frac{D_{i-1/2}^g + \delta D_{i-1/2}^g}{\dx_{i}+\dx_{i-1}}
+\frac{\sigma_{i}^g}{2}
\right]
\phi_{i,g}
\nonumber \\
&+&\left(
\frac{-D_{i+1/2}^g -\delta D_{i+1/2}^g }{\dx_{i+1}+\dx_{i}}
\right)
\phi_{i+1,g} =
\frac{1}{2}q_{i,g}\,\, ,
\end{eqnarray}
where $q_{i,g}$ is the RHS of~\eq{eq:FD_diff_full}.

These equations can be formulated in operators notation according to
\begin{equation}\label{eq:op-not}
\mathcal{M}\Phi=\frac{1}{\keff}\mathcal{F}\Phi \,\, ,
\end{equation}
where $\mathcal{M}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by $q_{i,g}$. Note that $\mathcal{M}$ can be written as $\mathcal{M}=\mathcal{M}_0+\delta\mathcal{M}$ distinguishing the diffusion corrections from the constant diffusion coefficients derived from the transport problem. In the homogeneous case, $\mathcal{M}(x)=\mathcal{M}_0+\delta\mathcal{M}(x)$.
%
%Eq.~\eqref{eq:op-not} is solved using the power iteration algorithm, where the within-group equation is noted as $\mathcal{A}_g(x)\Phi_g(x)=\frac{1}{\keff}Q_g(x)$, where $\mathcal{A}_g(x)=\mathcal{A}_{g,0}+\delta\mathcal{A}_g(x)$.
%
% ---------------------------------------------------
\subsection{Calculation of the integral currents}
\label{sec:calc-int-curr}

The numerical evaluation of the neutron current $J(x,E)$ at cell interfaces requires spatial integration of~\eq{eq:tot-J}. The neutron current at any interface can be calculated by considering separately contributions from all cells who are to the left or to the right of the interface. The current at a cell interface is discretized as follows
\begin{eqnarray}\label{eq:tot-J-disc}
J_g(x_{i+1/2}) &=& \sum\limits_{l=0}^\infty  \frac{2l+1}{2}
\sum\limits_{m=0}^{[l/2]}  h_m
\bigg\{
E_{n_{l,m}+1}[\mcL_g(0,x_{i+1/2})] \psi_{l,g}(0) 
+(-1)^{l+1} E_{n_{l,m}+1}[\mcL_g(x_{i+1/2},a)]\psi_{l,g}(a)  \nonumber \\
&+&
\sum\limits_{j=0}^i q_{l,g,j}\int\limits_{x_{j-1/2}}^{x_{j+1/2}} dx'
E_{n_{l,m}}[\mcL_g(x',x_{i+1/2})]
%\nonumber \\
%&&
+(-1)^{l+1} 
\sum\limits_{j=i+1}^{I-1} q_{l,g,j}\int\limits_{x_{j-1/2}}^{x_{j+1/2}} dx'
E_{n_{l,m}}[\mcL_g(x_{i+1/2},x')]
\bigg\}	\,\, , 
\end{eqnarray}
where $n_{l,m}\equiv l+2-2m$. The source $q_{l,g,j}$ is the $l$\tsup{th} angular moment of the volume-average within-group source in the cell $j$. The optical lengths show the subscript $g$ because they are evaluated with the corresponding total cross section $\sigma_g$. Note that for void boundary conditions, the boundary terms vanish by definition. The spatial integrals in~\eq{eq:tot-J-disc} can be solved analytically knowing that $E'_{n+1}(u)=-E_n(u)$~\cite{Gradshteyn-2007}. Using the notation in Fig.~\ref{fig:Xi}, the optical length between the right surfaces of cell $j$ and cell $i$ is
\begin{equation}\label{eq:psi_w_left_right}
\Xi^g_{i,j} \equiv \begin{cases}
\Xi^g_{i\geqslant j} = \sum\limits_{k=j+1}^i \sigma_{g,k}\Delta x_k 
& x\geqslant x' \quad (i\geqslant j) \\
\Xi^g_{i<j} = \sum\limits_{k=i+1}^{j-1} \sigma_{g,k}\Delta x_k & x<x' \quad (i<j)\,\, .
\end{cases} 
\end{equation}

\begin{figure}[htbp!] 
	\centering
	For $x\geqslant x'$.	
	\begin{tikzpicture}
	\tikzstyle{every node}=[font=\footnotesize]
	\draw[thick] (0,0) -- (7.5,0);
	\draw[thick,->] (8.5,0) -- (16,0) node[anchor=west] {$x$};

	\node[anchor=south] at (1cm,1pt) {$x_{j-1}$};
	\node[anchor=north] at (1cm,-1pt) {$\sigma_{g,j-1}$};

	\draw ( 3 cm,2pt) -- ( 3 cm,-2pt) node[anchor=north] {$x_{j-1/2}$};
	\node[anchor=south] at (5cm,1pt) {$x_j$};
	\node[anchor=north] at (5cm,-1pt) {$\sigma_{g,j}$};
	\draw ( 7 cm,2pt) -- ( 7 cm,-2pt) node[anchor=north] {$x_{j+1/2}$};

	\node[anchor=south] at (8cm,-5pt) {$\ldots$};

	%\node[anchor=south] at (9cm,1pt) {$x_{j-1}$};

	\draw ( 10 cm,2pt) -- ( 10 cm,-2pt) node[anchor=north] {$x_{i-1/2}$};
	\node[anchor=south] at (12cm,1pt) {$x_{i}$};
	\node[anchor=north] at (12cm,-1pt) {$\sigma_{g,i}$};
	%\node[anchor=south] at (16.5cm,1pt) {$x_{j+1/2}$};
	\draw ( 14 cm,2pt) -- ( 14 cm,-2pt) node[anchor=north] {$x_{i+1/2}$};

	\node[anchor=south] at (4cm,2pt) {$x'$};

	% ------------------- Vertical dashed lines ------------------- %
	\draw [dashed] ( 7 cm, -0.5cm) -- ( 7 cm,-1.2cm);
	\draw [dashed] ( 14 cm, -0.5cm) -- ( 14 cm,-2.1cm);
	\draw [dashed] ( 4 cm, 0.1cm) -- ( 4 cm,-2.1cm);

	% ------------------- Horizontal arrows + text ------------------- %
	\draw[>=triangle 45, <->] (7cm,-1.2cm) -- (14cm,-1.2cm);
	\node[anchor=south] at (10.5cm,-1.2cm) {$\Xi_{i,j}^g$};

	\draw[>=triangle 45, <->] (4cm,-2.1cm) -- (14cm,-2.1cm);
	\node[anchor=south] at (9cm,-2.1cm) {$\Xi_{i,j}^g + \sigma_{g,j}\left(x_{j+1/2} - x'\right)$};

	\end{tikzpicture}
	\bigbreak
	\bigbreak
	For $x<x'$.
	\begin{tikzpicture}
	\tikzstyle{every node}=[font=\footnotesize]
	\draw[thick] (0,0) -- (7.5,0);
	\draw[thick,->] (8.5,0) -- (16,0) node[anchor=west] {$x$};

	\node[anchor=south] at (1cm,1pt) {$x_{i-1}$};
	\node[anchor=north] at (1cm,-1pt) {$\sigma_{g,i-1}$};

	\draw ( 3 cm,2pt) -- ( 3 cm,-2pt) node[anchor=north] {$x_{i-1/2}$};
	\node[anchor=south] at (5cm,1pt) {$x_i$};
	\node[anchor=north] at (5cm,-1pt) {$\sigma_{g,i}$};
	\draw ( 7 cm,2pt) -- ( 7 cm,-2pt) node[anchor=north] {$x_{i+1/2}$};

	\node[anchor=south] at (8cm,-5pt) {$\ldots$};

	%\node[anchor=south] at (9cm,1pt) {$x_{j-1}$};

	\draw ( 10 cm,2pt) -- ( 10 cm,-2pt) node[anchor=north] {$x_{j-1/2}$};
	\node[anchor=south] at (12cm,1pt) {$x_{j}$};
	\node[anchor=north] at (12cm,-1pt) {$\sigma_{g,j}$};
	%\node[anchor=south] at (16.5cm,1pt) {$x_{j+1/2}$};
	\draw ( 14 cm,2pt) -- ( 14 cm,-2pt) node[anchor=north] {$x_{j+1/2}$};

	\node[anchor=south] at (13cm,2pt) {$x'$};

	% ------------------- Vertical dashed lines ------------------- %
	\draw [dashed] ( 7 cm, -0.5cm) -- ( 7 cm,-2.1cm);
	\draw [dashed] ( 10 cm, -0.5cm) -- ( 10 cm,-1.2cm);
	\draw [dashed] ( 13 cm, 0.1cm) -- ( 13 cm,-2.1cm);

	% ------------------- Horizontal arrows + text ------------------- %
	\draw[>=triangle 45, <->] (7cm,-1.2cm) -- (10cm,-1.2cm);
	\node[anchor=south] at (8.5cm,-1.2cm) {$\Xi_{i,j}^g$};

	\draw[>=triangle 45, <->] (7cm,-2.1cm) -- (13cm,-2.1cm);
	\node[anchor=south] at (10cm,-2.1cm) {$\Xi_{i,j}^g + \sigma_{g,j}\left(x'-x_{j-1/2}\right)$};
	\end{tikzpicture}
	\bigbreak
	\caption{Notation for numerical evaluation of integral interface currents.}
	\label{fig:Xi}
\end{figure}

Substituting 
\begin{equation}\label{eq:usub}
u = \begin{cases}
\Xi^g_{i\geqslant j} + \sigma_{g,j}(x_{j+1/2}-x') & x'\leqslant x \quad (j\leqslant i) \\
\Xi^g_{i<j} + \sigma_{g,j}(x'-x_{j-1/2}) & x'>x \quad (j>i)\,\, ,
\end{cases}
\end{equation} 
and integrating the $E_{n_{l,m}}$ terms in~\eq{eq:tot-J-disc} yields
\begin{eqnarray}\label{eq:E-int}
\int_{x_{j-1/2}}^{x_{j+1/2}}  dx'
E_{n_{l,m}}[\mcL_g(x',x_{i+1/2})] &=& \frac{1}{\sigma_{g,j}}
	\left[
	E_{n_{l,m}+1}(\Xi^g_{i\geqslant j}) 
	- E_{n_{l,m}+1}(\Xi^g_{i\geqslant j	}+\sigma_{g,j}\Delta x_j)
	\right] \nonumber \\
	&=&
	\frac{1}{\sigma_{g,j}}
	\left\{
	E_{n_{l,m}+1}\left[
	\mcL_g(x_{j+1/2},x_{i+1/2}) \right] 
	- E_{n_{l,m}+1}\left[
	\mcL_g(x_{j-1/2},x_{i+1/2})
	\right] 
	\right\} \nonumber \\	
\int_{x_{j-1/2}}^{x_{j+1/2}} dx'
E_{n_{l,m}}[\mcL_g(x_{i+1/2},x')] &=& \frac{1}{\sigma_{g,j}}
\left[
E_{n_{l,m}+1}(\Xi^g_{i<j}) 
- E_{n_{l,m}+1}(\Xi^g_{i<j	}+\sigma_{g,j}\Delta x_j)
\right]\nonumber \\	
	&=&
\frac{1}{\sigma_{g,j}}
\left\{
E_{n_{l,m}+1}\left[
\mcL_g(x_{i+1/2},x_{j-1/2}) \right] 
- E_{n_{l,m}+1}\left[
\mcL_g(x_{i+1/2},x_{j+1/2})
\right]
\right\}
\,\, .
\end{eqnarray}
Hence, the interface currents can be written as
\begin{eqnarray}\label{eq:tot-J-disc2}
J_g(x_{i+1/2}) &=& \sum\limits_{l=0}^\infty  \frac{2l+1}{2}
\sum\limits_{m=0}^{[l/2]}  h_m
\bigg\{
E_{n_{l,m}+1}[\mcL_g(0,x_{i+1/2})] \psi_{l,g}(0) 
+(-1)^{l+1} E_{n_{l,m}+1}[\mcL_g(x_{i+1/2},a)]\psi_{l,g}(a)  \nonumber \\
&+&
\sum\limits_{j=0}^i \frac{q_{l,g,j}}{\sigma_{g,j}} 
\left\{
E_{n_{l,m}+1}\left[
\mcL_g(x_{j+1/2},x_{i+1/2}) \right] 
- E_{n_{l,m}+1}\left[
\mcL_g(x_{j-1/2},x_{i+1/2})
\right] 
\right\}
\nonumber \\
&+&(-1)^{l+1} 
\sum\limits_{j=i+1}^{I-1} \frac{q_{l,g,j}}{\sigma_{g,j}} 
\left\{
E_{n_{l,m}+1}\left[
\mcL_g(x_{i+1/2},x_{j-1/2}) \right] 
- E_{n_{l,m}+1}\left[
\mcL_g(x_{i+1/2},x_{j+1/2})
\right]
\right\}
\bigg\}	\,\, . 
\end{eqnarray}
Note that for the isotropic case ($l=0$) Eq.~\eqref{eq:tot-J-disc2} reduces  to
\begin{eqnarray}\label{eq:tot-J-disc2-l=0}
J_g(x_{i+1/2}) &=& \frac{1}{2}
\bigg\{
E_3[\mcL_g(0,x_{i+1/2})] \psi_{0,g}(0) 
- E_3[\mcL_g(x_{i+1/2},a)]\psi_{0,g}(a)  \nonumber \\
&&+
\sum\limits_{j=0}^i \frac{q_{0,g,j}}{\sigma_{g,j}} 
\left\{
E_3\left[
\mcL_g(x_{j+1/2},x_{i+1/2}) \right] 
- E_3\left[
\mcL_g(x_{j-1/2},x_{i+1/2})
\right] 
\right\}
\nonumber \\
&&-
\sum\limits_{j=i+1}^{I-1} \frac{q_{0,g,j}}{\sigma_{g,j}} 
\left\{
E_3\left[
\mcL_g(x_{i+1/2},x_{j-1/2}) \right] 
- E_3\left[
\mcL_g(x_{i+1/2},x_{j+1/2})
\right]
\right\}
\bigg\}	\nonumber \\
&=&\frac{1}{2}
\bigg\{
E_3[\mcL_g(0,x_{i+1/2})] \psi_{0,g}(0) 
- E_3[\mcL_g(x_{i+1/2},a)]\psi_{0,g}(a)  \nonumber \\
&&+
\sum\limits_{j=0}^{I-1} \frac{q_{0,g,j}}{\sigma_{g,j}} 
\left\{
E_3\left[
\mcL_g(x_{j+1/2},x_{i+1/2}) \right] 
- E_3\left[
\mcL_g(x_{j-1/2},x_{i+1/2})
\right] 
\right\}\text{sign}(i-j)
\bigg\}
\,\, . 
\end{eqnarray}
These transfer probabilities $E_{n_{l,m}}[\tau_g(x_i,x_j)]$ are pre-calculated once and are stored in a multi-dimensional array.

%
% ---------------------------------------------------
\subsection{Boundary conditions}
\label{sec:BC}
A generalized form for the boundary condition (at the left) follows as
\begin{equation}\label{eq:BC}
J_D(x=0) = \frac{\phi_{i=0}}{\Delta x_0/2 + \zeta} \,\, ,
\end{equation} 
where $\zeta$ is the extrapolation length in case of vacuum. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
%
The quantity $\delta J$ at the boundary takes the simpler form of $\delta J = -\delta D_{-1/2}\phi_0$, without dividing by the spatial width, since no particular extrapolation length is appropriate for the correction. The expression for the right boundary is straightforward, implying a non-negative current.

%
% ---------------------------------------------------
\subsection{The Ronen iterative scheme}
\label{sec:RM-scheme}

The Ronen algorithm is described as follows (see Fig.~\ref{fig:RM-algo}):
\begin{enumerate}
	\item\label{it:init} Initialize - the algorithm receives the geometry and the cross sections of the problem as input. At this stage, the corrections to the diffusion coefficients $\delta D^{(0)}(x,E)$ are set to zero and the initial pure-diffusion operator $\mathcal{A}_0(E)$ is constructed. Initial guesses for the flux $\phi^{(0)}(x,E)$ and multiplication factor $k^{(0)}_\texttt{eff}$ are set.
	\item\label{it:DF-solve} Diffusion Solver - a one-dimensional multigroup diffusion solver is executed until convergence using the diffusion corrections from the previous iteration $\delta D^{(k)}(x,E)$ through the diffusion operator $\mathcal{A}^{(k)}(x,E)=\mathcal{A}_0(E)+\delta A^{(k)}(x,E)$. The results are an updated estimation of the diffusion flux $\phi^{(k)}(x,E)$ and the multiplication factor $k^{(k)}_\texttt{eff}$.
	\item\label{it:Js} Calculate Currents - using the updated diffusion flux $\phi^{(k)}(x,E)$, both the diffusion current $J^{(k)}_D(x,E)$ (Eq.~\ref{eq:JD-dJ}) and the transport current $J^{(k)}_\texttt{tr}(x,E)$ (Eq.~\ref{eq:tot-J}) are calculated.
	\item\label{it:dD} Calculate corrections - the diffusion correction $\delta D^{(k+1)}(x,E)$ (Eq.~\ref{eq:JD-dJ}) is obtained using $\delta J^{(k)}(x,E)$ and Eq.~\eqref{eq:JD-dJ}.
	\item\label{it:dA} Update diffusion coefficients - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
	\item\label{it:conv} If flux and eigenvalue are not converged, go to step~\ref{it:DF-solve}.
\end{enumerate}

\begin{figure}[htbp!] 
	\centering
\begin{tikzpicture}[font=\scriptsize]
% Place nodes
	\node [cloud] 					 			(start) {START};
	\node [block, right of=start, xshift=0cm,yshift=0cm] (input) {Input\\parameters};
	\node [block, right of=input, xshift=0cm,yshift=0cm] (geoXS) {Geometry \& XS};
	\node [block, below of=geoXS, xshift=0cm,yshift=1.5cm] (Diff)  {Diffusion\\solver};
	\node [block, below of=Diff, xshift=0cm,yshift=1.5cm] (J)  {Calculate $J^{(k)}_{\texttt{tr}},J^{(k)}_D,\delta J^{(k)}$};
	\node [block, left  of=J,    xshift=0cm,yshift=0cm] (dD) {Obtain\\$\delta D^{(k+1)}$};
	\node [block, left  of=dD,   xshift=0cm,yshift=0cm](dA) {Calculate\\$\delta \mathcal{A}^{(k+1)}$};
	\node [block, above of=dA,   xshift=0cm,yshift=-1.5cm] (Anew) {Construct\\$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};

% Draw edges
	\path [line] (start) -- (input);
	\path [line] (input) -- (geoXS);
	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\mathcal{A}_0$}(Diff);
	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k)},k^{(k)}$}(J);
	\path [line] (J)  -- node[anchor= north]{}(dD);
	\path [line] (dD) -- node[anchor= north]{}(dA);
	\path [line] (dA)  -- node[anchor= north]{}(Anew);
	\path [line] (Anew)  -- node[near end,anchor= south west,xshift=-1.7cm]{$\mathcal{A}^{(k+1)}$}(Diff);

\end{tikzpicture}
	\caption{A flow chart of the Ronen algorithm.}
	\label{fig:RM-algo}
\end{figure}

%
% ---------------------------------------------------
\section{Results}
\label{sec:res}

The reference solution for the one-dimensional homogeneous slab is generated using a Python3 discrete ordinates ($S_n$) code with $N=16$~\cite{Lewis-1984}. The diffusion solutions and the Ronen iterations are produced using original codes developed in Pyhton3. All simulations utilize regular mesh in a slab of width $a=21.5$ cm. All thresholds are set to 1E-6 and no (over/under)-relaxation is done. The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$. Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group. The two-group dataset used in this study is taken from~\cite{Tomatis-2011} and is shown in Table~\ref{tab:xs}. 
%
\begin{table}[!htbp]	
	\centering
	\caption{Two-group dataset used in this study~\cite{Tomatis-2011}.}
	\label{tab:xs}
	\begin{tabular}{cccccc}
		%\midrule
		Group g &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
		\midrule
		1 & 5.3115$\times$10\tsup{-1} & 5.04664$\times$10\tsup{-1} & 2.03884$\times$10\tsup{-3} & 1 & 7.15848$\times$10\tsup{-3} \\
		%\midrule
		2 & 1.30058$\times$10\tsup{+0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{+0}	& 0 & 1.41284$\times$10\tsup{-1} \\
		%\midrule
	\end{tabular}
\end{table}

Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (w/ extrapolated length) and the Ronen method. The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and the Ronen method, respectively. The reference $k_\texttt{ref}$ value from S\tsub{16} is 0.744417 ($I = 400$).

\begin{table}[!htbp]
	\centering
	\caption{Reactivity differences as a function of mesh refinement using the Ronen method.}
	\label{tab:dx_drho}
	\begin{tabular}{lccccr}
		%\midrule
		$dx\quad (I)$ [cm]  &  $k_{\texttt{ref}}$ & $k_{\texttt{D}}$ & $\Delta\rho_\texttt{D}$ [pcm] & $k_{\texttt{RM}}$ & $\Delta\rho_\texttt{RM}$ [pcm]\\ 
		\midrule
		0.43 (50)     & 0.744307 & 0.741417 & -524 & 0.740552  & -681\\
		%\midrule
		0.215 (100)    & 0.744391 & 0.741355 & -550 & 0.743447 & -171\\
		%\midrule
		0.1075 (200)   & 0.744412 & 0.741339 & -557 & 0.744212 & -36\\
		%\midrule
		0.07167 (300) & 0.744416 & 0.741336 & -558 & 0.744356 & -11\\
		%\midrule
		0.05375 (400)  & 0.744417 & 0.741335 & -558 & 0.744407 & -2\\
		%\midrule
	\end{tabular}
\end{table}

%\begin{table}[htp!]
%	\centering
%	\caption{Reactivity differences in pcm by refining the mesh.}
%	\label{tab:kconv}
%	\begin{tabular}{crr}
%		\multirow{2}{*}{$I$} & \multicolumn{2}{c}{$\Delta \rho$ [pcm]} \\ \cline{2-3}
%		& $it=0$ & $it=100$ \\ \hline
%		~50 & 550.22 & 170.35 \\
%		100 & 556.85 & ~36.08 \\
%		200 & 558.50 & ~~1.72
%	\end{tabular}
%\end{table}

A comparison of the fast and thermal fluxes, as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion w/o RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} for half-slab. The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_n$ flux is also shown in Fig.~\ref{fig:fluxes}. The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.

The diffusion and transport currents calculated using the converged Ronen solution are plotted in Fig.~\ref{fig:current}. The full slab solution exhibits anti-symmetry, as expected, whereas the corrected diffusion current exhibit non-trivial behavior near the boundary. Fig.~\ref{fig:Dcoef} show the original standard diffusion coefficients ($D=(3\sigma_{tr})^{-1}$), the RM correction terms ($\delta D$), and the corrected (spatially-dependent) diffusion $D$. It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary. The convergence of the flux (max deviation) and the criticality eigenvalue are shown in Fig.~\ref{fig:conv}. While the eigenvalue converges within a few iterations, the flux exhibit slow convergence near the boundaries. The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%]. The spatial flux convergence of the Ronen iterations with respect to the reference $S_n$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.

% fluxes
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.45\linewidth]{flux0_half.pdf}
	\includegraphics[width=0.45\linewidth]{flux_deviation_half.pdf}	
	\caption{Comparison of the fluxes as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion w/o RM correction ($D_0$). Results shown here after 250 Ronen iterations.}
	\label{fig:fluxes}
\end{figure}

% current
\begin{figure}[htbp!]
	\centering
	%\includegraphics[width=0.45\linewidth]{current.pdf}
	\includegraphics[width=0.45\linewidth]{current_half.pdf}	
	\caption{The diffusion and transport currents calculated using the converged Ronen solution.}
	\label{fig:current}
\end{figure}

% D-coef
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.45\linewidth]{D_coeffs.pdf}
	%\includegraphics[width=0.45\linewidth]{D_coeffs_half.pdf}	
	\caption{The original standard diffusion coefficients ($D=(3\sigma_{tr})^{-1}$),
		the RM correction terms ($\delta D$), and the corrected (spatially-dependent)
		diffusion $D$. Results shown here after 250 Ronen iterations.}
	\label{fig:Dcoef}
\end{figure}

% convergence
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.45\linewidth]{convergence.pdf}
	\caption{Convergence of the flux (max deviation) and the criticality
		eigenvalue.}
	\label{fig:conv}
\end{figure}

% convergence
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_1.pdf}
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2.pdf}
	\caption{The spatial flux convergence between two successive Ronen iterations for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].}
	\label{fig:conv2}
\end{figure}

% convergence
\begin{figure}[htbp!]
	\centering
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_1_sn.pdf}
	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2_sn.pdf}
	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_n$ solution for the left half slab.}
	\label{fig:conv3}
\end{figure}

%
% ---------------------------------------------------
\section{Conclusions}
\label{sec:conc}

The Ronen Method was first proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux. This yielded an iterative scheme leading to new flux distributions solved by a diffusion solver but with a (spatially) modified diffusion coefficient driving the diffusion solution to that of the integral transport equation. The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning. The solution of the diffusion equation, on the other hand, offers many numerical advantages, e.g., speed and robustness. Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues resulting from small flux gradients. This is the option adopted in this study.

More accurate results are obtained for the two-group benchmark problem reported in \cite{Tomatis-2011}. In general, slow convergence is observed for the scalar flux, whose larger discrepancy with respect to the reference is always located on the vacuum boundary. Although the method is converging to the reference results provided by a discrete ordinate transport code, the improvement of the convergence rate and the use of coarser meshes are crucial for the advancement of the methodology in practical applications. These topics will be addressed as future developments, as well as heterogeneous systems and higher-order anisotropy.

%
% ---------------------------------------------------
\section*{Acknowledgments}
\label{sec:acknow}

The authors express their gratitude to Prof. Yigal Ronen who initiated the idea for this study. R.G. is partially supported by the Israel Ministry of Energy, contract no. 216-11-008.

%\appendix
%\section{Test 1}
%sdf asd asd adsf 
%\section{Test 2}
%sdf sdf sd

%
% BibTeX users please use
\bibliographystyle{unsrt}
\bibliography{refs-EPJP}

\end{document}

### 2019-10-02 docs/ICTT2019/RMethod_ictt26.tex
Journal and conference papers - tex, bibtex and figures
Journal and conference papers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  This is a sample LaTeX input file for your contribution to
%  the ICTT26 conference.
%
%  Adapted from the ICTT-22 template by T. Palmer (palmerts@ne.orst.edu)
%
%  Please use it as a template for your full paper
%    Accompanying/related file(s) include: class/format file ictt26.cls
%       2. Sample Postscript Figure:   figure.eps
%    Notes:
%      (1) You can use the "dvips" utility to convert .dvi
%          files to PostScript.  Then, use either Acrobat
%          Distiller or "ps2pdf" to convert to PDF format.
%      (2) Different versions of LaTeX have been observed to
%          shift the page down, causing improper margins.
%          If this occurs, adjust the "topmargin" value in the
%          ictt22.cls file to achieve the proper margins.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{ictt26}
%
%  various packages that you may wish to activate for usage
\usepackage{graphicx}
\usepackage{tabls}
\usepackage{afterpage}
\usepackage{lastpage}
%\usepackage{cites}
%\usepackage{epsf}
\usepackage{amsmath, amssymb}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usetikzlibrary{arrows,calc}
\usepackage{subcaption}
%
% Math commands
\newcommand{\mcl}[1]{\ensuremath{\Lambda_{#1}}}
\newcommand{\cl}[1]{\ensuremath{\lambda_{#1}}}
\newcommand{\partialx}[1]{\ensuremath{\frac{\partial {#1}}{\partial x}}}
\newcommand{\derivx}[1]{\ensuremath{\frac{d {#1}}{dx}}}
\newcommand{\aflux}[2]{\ensuremath{\psi\left({#1}, {#2} \right)}}
\newcommand{\cs}[2]{\ensuremath{\sigma_{#1}\left({#2}\right)}}
\newcommand{\src}[1]{\ensuremath{q\left({#1}\right)}}
\newcommand{\csmat}[2]{\ensuremath{\sigma_{#1}^{#2}}}
\newcommand{\scatratmat}[1]{\ensuremath{c_{#1}}}
\newcommand{\sfluxnofn}{\ensuremath{\phi}}
\newcommand{\sfluxmatnofn}[1]{\ensuremath{\sfluxnofn_{#1}}}
\newcommand{\sflux}[1]{\ensuremath{\sfluxnofn \left( {#1} \right)}}
\newcommand{\sfluxmat}[2]{\ensuremath{\sfluxmatnofn{#1}\left( {#2} \right)}}
\newcommand{\sfluxrmserr}[2]{\ensuremath{\sfluxnofn_{#1}^{#2}}}
\newcommand{\ensavg}[1]{\ensuremath{\left<{#1}\right>}}
%
% Shortcut commands
\newcommand{\eq}[1]{Eq.~(\ref{#1})}
\newcommand{\eqnolabel}[1]{(\ref{#1})}
\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
\newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
\newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
\newcommand{\tbl}[1]{Table~\ref{#1}}
\newcommand{\tblnolabel}[1]{\ref{#1}}
\newcommand{\tbls}[1]{Tables~\ref{#1}}
\newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
\newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\fignolabel}[1]{\ref{#1}}
\newcommand{\figs}[1]{Figs.~\ref{#1}}
\newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
\newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
\newcommand{\sxn}[1]{Section~\ref{#1}}
%
%
% Insert authors' names and short version of title in lines below
%
\newcommand{\authorHead}      % Author's names here
   {Daniele Tomatis et Al.}
\newcommand{\shortTitle}      % Short title here
   {The Ronen Method in simple 1-D problems}

\DeclareMathOperator{\sign}{sign}
\newcommand{\pluseq}{\mathrel{+}=}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   BEGIN DOCUMENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

% Fix the large top margin (psb)
\setlength{\topmargin}{-30pt}

%
%      Headers and Footers
\afterpage{%
\fancyhf{}%
\fancyhead[CE]{
{\scriptsize \authorHead}}
\fancyhead[CO]{
{\scriptsize \shortTitle}}
%\lfoot{\scriptsize{%
%26th International Conference on Transport Theory (ICTT-26) \\
%Sorbonne University, Paris, France, 2019}}%
%\rfoot{\thepage/\totalpages{}}%
\rfoot{\thepage/\pageref{LastPage}}%
\pagestyle{fancy}
}

\normalsize

\setlength{\baselineskip}{16.8pt}
\vspace{-3pt}

%
% TITLE
%

\begin{center}
\textbf{\large \\%
%NEUTRON DIFFUSION BY THE RONEN METHOD IN HETEROGENEOUS MEDIA
ON THE RONEN METHOD IN SIMPLE 1-D PROBLEMS
}

%
% FIRST AUTHORS
%
\setlength{\baselineskip}{12pt}
\textbf{Daniele Tomatis}\\
DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\
daniele.tomatis@cea.fr\\
\vspace{0.25in}
\textbf{Roy Gross and Erez Gilad}\\
The Unit of Nuclear Engineering\\
Ben-Gurion University of the Negev, Israel\\
roygros@post.bgu.ac.il, gilade@bgu.ac.il\\
\end{center}

\begin{abstract}
In this work we apply the Ronen method to resolve the neutron transport in simple homogeneous problems. Slab, cylindrical and spherical geometries are studied. This method demands successive resolutions of the diffusion equation, where the local diffusion constants are modified in order to reproduce new estimates of the currents by a transport operator. The diffusion solver employs here finite differences and the transport-corrected currents are forced in the numerical scheme by means of drift terms, like in the CMFD technique. The solution is compared against reference results provided by a discrete ordinate computer code. Boundary conditions are discussed introducing proper approximations to save the particle balance. Slow convergence is reported on the scalar flux, although the results match the reference solutions in the limit of fine meshes.
%
%In this work we apply the Ronen method in the slab geometry filled with heterogeneous media. Neutron diffusion is solved by a nodal method on a coarse mesh, while reference solutions of the neutron distribution are provided by a discrete ordinate transport solver. The CMFD technique is used for both the implementation of the nodal solver and for the corrections of the diffusion coefficient given by the Ronen method. The presence of discontinuity factors for equivalencing the diffusion solution is investigated jointly with the Ronen method. Results are presented for different levels of material heterogeneity at the slab interfaces.
\end{abstract}
%
% SET RAGGED RIGHT MARGIN
%
\raggedright

\section{INTRODUCTION}
\label{sec:intro}

In 2004 Ronen suggested to calculate more accurate currents by means of an integral transport operator still using a neutron flux computed in diffusion theory \cite{ronen2004accurate}. This allowed having new estimates of the diffusion coefficient still using Fick's law. Since these estimates need a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficient in the global calculation. The main reason motivating this method was to overcome the underlying limitation of Fick's law requiring low flux gradients, and so low neutron absorption and high scattering in general. Nevertheless, isotropic scattering remained as a basic postulate.

This idea was later used by Tomatis and Dall'Osso, who provided a numerical demonstration in a simple slab problem \cite{tomatis2011application}. Instead of updating the diffusion coefficient by the ratio of the current exchange and the flux gradient, as in Fick's law, they recurred to the coarse mesh finite differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
%
%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
%
This technique, largely adopted in the literature of nodal methods \cite{smith1983nodal,lawrence1986progress}, can avoid indeterminate divisions in case of vanishing current and flux gradient. They tested this implementation in a bare slab with two-group cross sections homogenized in a realistic PWR assembly. It was observed that the Ronen method (RM) could drive the flux from diffusion towards the reference of the integral Boltzmann transport equation, regardless of the initial formulation used for the diffusion coefficient. Remarkably, the unphysical zero-flux boundary condition was not preventing to correct the flux near the boundary, that is within a few mean free paths. However, higher errors were noticed at the boundary with vacuum, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
%
%In this work, we study the Ronen method with coarse meshes in order to approach the typical situation of core calculations, where homogenized cross sections are prepared in single fuel assemblies by lattice transport calculations. Nodal expansion methods are generally used with coarse meshes relying on polynomial-like or semi-analytical solutions \cite{lawrence1986progress}. They can also employ the discontinuity factors in their solving equations, thus yielding an equivalent form to the reference transport solution \cite{smith1986assembly}. Its implementation through the CMFD compensates the truncation errors caused by the approximate finite differences, and eases the global resolution to many local two-nodes problems. Of course, the simplified 1-D geometry let us disregard here all issues related to the transverse leakage approximation.
%
%Specifically, we compare hereafter the solutions obtained by the Ronen method and by the analytical nodal method, with the aim to present the first method as an on-line equivalence technique, farther capable to fulfill the neutron transport in its integral form on the coarse mesh. %We also use the discontinuity factors to enforce the physical equivalence between diffusion and transport, which is not preserved after the common flux-volume weighting homogenization of the cross sections. The implementation of both methods uses the CMFD, as shown in section \ref{sec:impl}. The basics of the analytical nodal method are reported in section \ref{sec:nd}, while the procedure to estimate the currents by the integral transport operator follows in section \ref{sec:ce}. New transport-corrected boundary conditions are derived in section \ref{sec:bc} to fix the bad performances observed in \cite{tomatis2011application}. The results on a few characteristic configurations are discussed in section \ref{sec:res}. Finally, the article ends with the conclusion in section \ref{sec:cncls}.

In this work we investigate further the convergence on the first flux moments, aiming to extend the study to the cylindrical and spherical geometries with homogeneous media. The details of the implementation of the Ronen method in the diffusion solver are presented in section \ref{sec:impl}, while the procedure to estimate the currents by the integral transport operator follows in section \ref{sec:ce}. Boundary conditions are derived in section \ref{sec:bc}. The results on a few characteristic configurations are discussed in section \ref{sec:res}. Finally, the article ends with the conclusion in section \ref{sec:cncls}.

\section{IMPLEMENTATION}
\label{sec:impl}

The cross sections, as well as the diffusion coefficient, are usually available as volume-averaged data per cell in the mesh. Once the scalar flux is known from the finite differences solver using the original diffusion coefficients, the integral expressions derived in section \ref{sec:ce} can be used to get new estimates of the current $J$ at the cell interfaces. %Alternatively, new current estimates can come from the two-nodes problem resolved by the nodal method in section \ref{sec:nd}.
Instead of computing new diffusion coefficients on the same interfaces straight by Fick's law, $J = -D \partial_x \phi$, we obtain new corrective currents $\delta J = J - \Upsilon$ that are supplied next to the neutron balance in diffusion. Here $\Upsilon$ is the current obtained with the original values of the diffusion coefficient and with the derivative approximated by finite differences. In 1-D %Cartesian
geometry and using the notation in Fig. \ref{fig:mesh1D}, it is:
\begin{equation}
  \Upsilon_{i+1/2} = -2 D_{i+1/2} \frac{\phi_{i+1} - \phi_{i}}{\Delta_{i+1} + \Delta_{i}}, \text{ for } i = 0, \ldots, I-1,
  % \Upsilon^{(i+1/2)} = -2 D^{(i+1/2)} \frac{\phi_{i+1} - \phi_{i}}{\Delta_{i+1} + \Delta_{i}}, \text{ for } i = 0, \ldots, I-1,
  % \Upsilon^{(i+1/2)} = -2 D^{(i+1/2)} \frac{\phi_{i+1} - \phi_{i}}{V_{i+1} + V_{i}}, \text{ for } i = 0, \ldots, I-1,
  \label{eq:cmfd}
\end{equation}
where $\Delta_i = (x_{i+1/2} - x_{i-1/2})$. Integer and rational subscripts indicate cell-averaged and interface quantities, respectively.
%
\begin{figure}[b]
\centering
\input{figures/mesh1d.tkz}
\caption{Notation of the 1-D mesh.}
\label{fig:mesh1D}
\end{figure}
Since the input diffusion coefficients are provided as volume-averaged, and that they are always needed at interfaces, we approximate them by local volume averages:
\begin{equation}
  % D^{(i+1/2)} = \frac{D_{i+1}c_{i+1}\Delta_{i+1} + D_{i}c_i\Delta_{i}}{c_{i+1}\Delta_{i+1} + c_i\Delta_{i}}, \text{ for } i = 0, \ldots, I-1.
  % D^{(i+1/2)} = \frac{D_{i+1} V_{i+1} + D_{i} V_i}{V_{i+1} + V_i}, \text{ for } i = 0, \ldots, I-1.
  D_{i+1/2} = \frac{D_{i+1} V_{i+1} + D_{i} V_i}{V_{i+1} + V_i}, \text{ for } i = 0, \ldots, I-1.
  \label{eq:dc0}
\end{equation}
The values of the diffusion coefficient at $-1/2$ and $I-1/2$ are simply the coefficients of the boundary cells. $V_i$ is the reduced volume in the $i$-th cell, that is determined along the only dimension of interest. It is then per unit of transverse surface in the slab, the unit azimuthal angle in the cylinder and per unit cone in the sphere. Specifically, $V_i = \Delta_i c_i$ with $c_i$ depending on the system of coordinates. The $c$ coefficients are unitary in the Cartesian frame. In the cylinder, $c_i = x_i$ for all $i$ with $x_i = (x_{i-1/2} + x_{i+1/2}) / 2$ (arithmetic mean), whereas $c_i = (4 x_i^2 - \hat{x}_i^2)$ in the sphere with $\hat{x}_i = \sqrt{x_{i-1/2} x_{i+1/2}}$ (geometric mean).
%
The discretized form of the current $\delta J$ must involve the flux in order to be taken into account in the finite differences equations. Its representation is changed into a drift-advection term determined by the neighboring cell fluxes, thus avoiding possible undefined division by zeros in case of flat flux \cite{smith1983nodal}:
\begin{equation}
  \delta J_{i+1/2} = -2 \delta D_{i+1/2} \frac{\phi_{i+1} + \phi_{i}}{\Delta_{i+1} + \Delta_{i}}, \text{ for } i = 0, \ldots, I-1.
  % \delta J^{(i+1/2)} = -2 \delta D^{(i+1/2)} \frac{\phi_{i+1} + \phi_{i}}{\Delta_{i+1} + \Delta_{i}}, \text{ for } i = 0, \ldots, I-1.
  % \delta J^{(i+1/2)} = -2 \delta D^{(i+1/2)} \frac{\phi_{i+1} + \phi_{i}}{V_{i+1} + V_{i}}, \text{ for } i = 0, \ldots, I-1.
  \label{eq:dj}
\end{equation}
This allows determining the new numerical corrections $\delta D$ to use in the finite differences solver, together with the diffusive currents from \eq{eq:cmfd}. If necessary, the spatial differences at the denominator of Eq. \ref{eq:dj} can be removed by reason of the arbitrary definition used for $\delta D$. Finally, the neutron balance resolved by the CMFD takes into account both types of currents $\Upsilon$ and $\delta J$. Non-linear iterations with new corrections given by $\delta J$ are needed because of their dependence on the unknown flux.

The divergence operator used in the multi-group balance equation can be described with the general form $d_x (x^b J_g)/ x^b$, with $b = 0$, $1$ and $2$ respectively for the slab, for the cylinder and for the sphere. We solve then for the volume-integrated flux,
\begin{equation*}
  \hat{\phi}_{g,i} = \int_{x_{i-1/2}}^{x_{i+1/2}}{ x^b \phi_g(x) dx } = \bar{\phi}_{g,i} V_i,
\end{equation*}
making the approximation that the average group flux $\bar{\phi}_{g,i} \approx \phi_{g,i}$ in the equations above.

%\section{NODAL DIFFUSION}
%\label{sec:nd}
%
%Daniele: this topic is postponed to future works.
%
\section{CURRENT ESTIMATION}
\label{sec:ce}

\subsection{Slab geometry}
\label{sec:slab}
The angular flux from the integral transport equation (with standard notation) is:
\begin{equation}
\varphi(x, \mu) = \varphi(x_b, \mu) e^{-\tau(x_b, x)/\mu} + \int_{x_0}^x {dx' \frac{q(x', \mu)}{\mu} e^{-\tau(x', x)/\mu}},
\label{eq:NTE}
\end{equation}
with the optical length $\tau(x_1, x_2) = \int_{x_1}^{x_2}{dx' \sigma_t(x')}$. Contrary to other formulations, we do not include $\mu$ in the definition of the optical length to ease the numerical integrations in the following. $x_b = x_{-1/2} = a$ if $\mu > 0$, $x_b = x_{I-1/2} = b$ otherwise. The inclusion of the energy variable in Eq. \ref{eq:NTE} is straightforward; we use hereafter the multi-group theory, writing the source $q_g$ as\footnote{Curly brackets remind the possible use of the $k$-eigenvalue with vanishing external sources.}:
\begin{equation*}
q_g = \sum_{g'=1}^G{\left[
  \sum_{l=0}^\infty{ \frac{2l+1}{2}\sigma_{s,l, g' \rightarrow g}(x)P_l(\mu)\varphi_{l,g'}(x)
  + \frac{\chi_g}{2\{k\}} \nu\sigma_{f,g'}(x)\phi_{g'}(x)}\right] + S_g
                 },
\end{equation*}
where the subscript $l$ refers to the moments of the expansions of the flux and of the scattering cross section on the Legendre polynomials $P_l$. Fission emission is isotropic, so that the scalar flux $\phi$ is equal to half of the first moment $\varphi_0$. Without the external source $S$, the multiplication factor $k$ is used as eigenvalue to avoid the trivial vanishing solution. Since $q$ is computed by the results of the diffusion equation in the Ronen method, $l$ can only assume the values 0 and 1. Hereafter we consider only isotropic sources.

Multiplication of Eq. \ref{eq:NTE} by the direction cosine of the neutron velocity $\mu$ and the integration over $[-1, 1]$ provides the expression for the current, see \cite{tomatis2011application}. The integration on $\mu$ yields integral exponential functions by a simple change of variable ($\mu = \pm 1/u$, according to the sign of $\mu$) \cite{AS1964handbook}:
\begin{equation*}
E_n(\tau) = \int_0^1{d\mu\, e^{-\tau / \mu} \mu^{n-2}} = \int_1^\infty{du\, e^{-\tau u}u^{-n}}.
\end{equation*}
These special functions are then used to compute the current at the cell interfaces for all $i$:
\begin{equation}
\begin{split}
% J_g(x_{i+1/2}) &=
J_{g,i+1/2} &= \int_0^1 {d\mu\, \mu \varphi_g(a, \mu) e^{-\tau_g(a, x_{i+1/2})/\mu}}
       - \int_0^{-1}{d\mu\, \mu \varphi_g(b, \mu) e^{-\tau_g(b, x_{i+1/2})/\mu}}\\
       & + \sum_{j=0}^{I-1} { \sign(x_{i+1/2} - x_{j+1/2}) \frac{q_{0,g,j}}{2} \int_{x_{j-1/2}}^{x_{j+1/2}}{dx' E_{2}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) } }.
\end{split}
\label{eq:J_tr}
\end{equation}
The $g$-th source $q_{g,j}$ is the volume-average in the cell $j$. The optical lengths show the subscript $g$ because they are evaluated with the corresponding total cross section $\sigma_{t,g}$. For the property $E'_{n+1}(\ell) = -E_n(\ell)$, the spatial integral of the $E_2$ function can be solved analytically by integrating on $\tau$:
\begin{equation*}
\begin{aligned}
\int_{x_{j-1/2}}^{x_{j+1/2}}{ dx' E_{n}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) } =
\frac{\sign(x_{i+1/2} - x_{j+1/2})}{\sigma_{t,g}} \cdot \\
\left[
  E_{n+1} \left(\lvert \tau_g(x_{j+1/2}, x_{i+1/2}) \rvert \right)
 -E_{n+1} \left(\lvert \tau_g(x_{j-1/2}, x_{i+1/2}) \rvert \right)
\right].
\end{aligned}
\end{equation*}

\subsection{Cylindrical geometry}
\label{sec:cylinder}

The expression of the current in curvilinear geometries is derived in this section from the 3-D Cartesian geometry, where the angular flux at the point $\mathbf{r}$ along the direction of flight $\mathbf{\Omega}$ is given by the general expression \cite{lewis1984computational}:
\begin{equation}
\varphi(\mathbf{r}, \mathbf{\Omega}) = \int_0^{S'}{ds'\, q(\mathbf{r} - s' \mathbf{\Omega}, \mathbf{\Omega}) \exp(-\tau(\mathbf{r}, \mathbf{r} - s' \mathbf{\Omega}))} + \varphi(\mathbf{r} - S' \mathbf{\Omega}, \mathbf{\Omega}) \exp(-\tau(\mathbf{r}, \mathbf{r} - S' \mathbf{\Omega})),
\label{eq:ITE_angflx}
\end{equation}
that is considering the contribution of the source $q$ within the distance $S'(\mathbf{r}, \mathbf{\Omega})$ from the boundary, and the possible entering amount of particles therein. We examine first the case of the cylinder. In planar geometry the angular flux and the source do not depend on the coordinate $z$. Hence, the position on the characteristic line identified by $\mathbf{\Omega}$ is projected on the $x$-$y$ plane (see Fig. \ref{fig:fullframe}): $\varphi(\mathbf{r} - s' \mathbf{\Omega},\mathbf{\Omega}) = \varphi(\mathbf{r} - s \mathbf{\Omega}_p,\mathbf{\Omega})$ and likewise for $q$, with the unit vector $\mathbf{\Omega}_p$ lying on the $x$-$y$ plane. $\theta$ is the polar angle measured between $\hat{e}_z$ and $\mathbf{\Omega}$. In absence of incoming particles, this allows to rewrite Eq. \ref{eq:ITE_angflx} as:
\begin{equation}
\varphi(\mathbf{r}, \mathbf{\Omega}) = \int_0^S{ds\, \frac{q(\mathbf{r} - s \mathbf{\Omega}_p, \mathbf{\Omega})}{\sin \theta} \exp(-\frac{\tau(\mathbf{r}, \mathbf{r} - s \mathbf{\Omega}_p)}{\sin \theta})}. % + \varphi(\mathbf{r} - S \mathbf{\Omega}_p, \mathbf{\Omega}) \exp(-\frac{\tau(\mathbf{r}, \mathbf{r} - S' \mathbf{\Omega})}{\sin \theta}).
\label{eq:ITE_xy}
\end{equation}

As well, integration of Eq. \ref{eq:ITE_xy} over the solid angle $d\mathbf{\Omega} = \sin \theta d\omega d \theta$ yields the scalar flux. The theory of collision probability methods originates from the use of isotropic sources, which are also considered as uniform in the cells of the spatial mesh. Two integration in space arise for each direction $\mathbf{\Omega}$, connecting the source in region $j$ to the flux (or its total reaction rate) in region $i$ by means of its collision probability. The incoming flux is considered as isotropic too, or linearly anisotropic in angle as in \cite{hebert2009applied} to relate the partial entering and outgoing currents to the only first flux moments. These partial currents on the boundary must satisfy a condition of albedo. Transfer probabilities across this outer surface are then derived to take into account of incoming particles in the equation for the $i$-th scalar flux. Escape probabilities accounts for neutrons produced in every region and leaving the outer surface uncollided.

The projections of partial currents on the outward normal $\hat{n}$ to a given surface are obtained from integration of Eq. \ref{eq:ITE_xy} with the weight $| \hat{n} \cdot \mathbf{\Omega} | = \sin \theta | \hat{n} \cdot \mathbf{\Omega}_p |$ on $\hat{n} \cdot \mathbf{\Omega} \lessgtr 0$. Higher moments are obtained by the weights associated to the corresponding spherical harmonics. Integrations along the polar angle are resolved with the introduction of the Bickley-Naylor functions \cite{amos1983uniform}:
\begin{equation}
\text{Ki}_n(\tau) = \int_0^{\pi/2}{ d\theta \sin^{n-1} \theta \exp\left(-\frac{\tau}{\sin \theta}\right) }.
\label{eq:Kin}
\end{equation}
The properties used for the computation of these functions are available elsewhere \cite{lewis1984computational,hebert2009applied,amos1983algorithm}.

\begin{subequations}
After introducing these arguments for a bare cylinder, the current leaving the cylindrical surface at $\mathbf{r}$ (with direction $\hat{n}$) given by neutrons flying along $\mathbf{\Omega}_p$ is:
\begin{equation}
J^+(\mathbf{r}) = \frac{1}{2\pi}\int_{W^+}{
  d\omega\, | \hat{n} \cdot \mathbf{\Omega}_p | \,
  \int_0^S ds\, \text{Ki}_2\left[ \tau\left(\mathbf{r}, \mathbf{r} - s \mathbf{\Omega}_p \right)\right]
  q(\mathbf{r} - s \mathbf{\Omega}_p)},
\label{eq:currp_cylinder1}
\end{equation}
with $W^+ = \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p > 0\right\}$. Using the surface element $dA' = s d\omega ds$ and $\mathbf{r}'_p = s \mathbf{\Omega}_p$, it is also:
\begin{equation}
J^+(\mathbf{r}) = \int_{W^+ \times [0, S]}{
  dA'\, \hat{n} \cdot (\mathbf{r} - \mathbf{r}'_p) \,
  \frac{\text{Ki}_2\left[ \tau\left(\mathbf{r}, \mathbf{r}'_p \right)\right]}{2 \pi \lvert \mathbf{r} - \mathbf{r}'_p \rvert^2}
  q(\mathbf{r}'_p)}.
\label{eq:currp_cylinder2}
\end{equation}
\label{eq:currp_cylinder}
\end{subequations}
$J^-$ is obtained with $w \in W^- =  \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p < 0\right\}$ instead.

Another integration on the total surface $S(r) = 2\pi r$ is necessary to obtain the current in the 1-D frame. For a given angle $\omega$, we have then volume integrals to solve numerically along many parallel lines called tracks, see Fig. \ref{fig:cyltracks}. Furthermore, the tracks are identical for any angle $\omega$ in the 1-D cylindrical geometry simplifying the integrals in Eqs. \ref{eq:currp_cylinder}, which can also be limited to half portion of the cylinder thanks to its symmetry. Finally, the outgoing and incoming currents at $r$ become:
\begin{equation}
J^\pm(r) = \pm \frac{1}{\pi r^2} \int_0^r { dh\, y \int_{-Y}^{\pm y}{
  d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right] q(h, y - \ell)}}
\label{eq:currp_cyl_atr}
\end{equation}
with $y(r,h) =\sqrt{r^2 - h^2}$, $Y = y(R,h)$ and the outer radius $R$. After multiplication by $S(r)$ and still with uniform sources, Eq. \ref{eq:currp_cyl_atr} can be written in terms of the escape probability $e_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided the semicylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
\begin{equation}
J^\pm(r)S(r) = \sum_j q_j V_j e^\pm_j(r) \mbox{ with }
e^\pm_j(r) = \pm \frac{2}{r V_j} \int_0^r { dh\, y \int_{L^\pm_j}{
  d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right]}},
\label{eq:esc_prob_cyl}
\end{equation}
$L^\pm_j(h) = [-Y,\pm y] \cap V_j$ and where $V_j$ is the ring area. The integral on the track $\ell$ is written differently for the convex and for the concave parts of the rings with respect to the direction of flight, see for instance track 1 and 2 in Fig. \ref{fig:cyltracks} where the same notation of Fig. \ref{fig:mesh1D} is used for the radial mesh. The current leaving the $i$-th ring at $r_{i+1/2}$ gets all source contributions weighted with the quantities $\varepsilon^+_{i+1/2,j} = V_j e^+_{i+1/2,j}$:
%
\newlength{\plussign}
\settowidth{\plussign}{$+$}
%
\begin{equation}
\label{eq:esc_prob_cyij}
  \begin{gathered}
  \varepsilon^+_{i+1/2,j} = \frac{2}{r_{i+1/2}} \cdot\\
  %\left\{
  \begin{cases}
  \displaystyle ~\int_0^{r_{i-1/2}} { dh\, y
    \int_0^{\ell_j}{ d\ell \bigg[ }}\\[3mm] \qquad
      \displaystyle \hspace{\the\plussign}
        \text{Ki}_2\left(2 \sigma_i \ell_i + \tau_{ii} + \tau_{ij} + \sigma_j \ell \right)
        \text{ if } i < j \\[3mm] \qquad
      \displaystyle +
        \text{Ki}_2\left(\sigma_i \ell_i + (1 - \delta_{ij})(\tau_{ij} + \sigma_j \ell_j) + \tau_{jj} + \sigma_j \ell \right)
        \text{ if } i \geq j \\[3mm] \qquad
      \displaystyle +
        \text{Ki}_2\left((1 - \delta_{ij})(\sigma_i \ell_i + \tau_{ij}) + \sigma_j \ell \right)
        \text{ if } i \geq j \\
%
%  \displaystyle + \int_0^{r_{i-1/2}} { dh\, y
%    \int_0^{\ell_j}{ d\ell \, \left[
%      \text{Ki}_2\left(\sigma_i \ell_i + \tau_{ij} + \sigma_j \ell_j + \tau_{jj} + \sigma_j \ell \right)
%      \right. }} \\ {{ \left.
%      + \text{Ki}_2\left(\sigma_i \ell_i + \tau_{ij} + \sigma_j \ell \right) \right]} }
%  \text{ if } i \geq j\\
%
  \displaystyle \: \bigg] +\int_{r_{i-1/2}}^{r_{i+1/2}} { dh\, y
    \int_0^{\ell_j}{ d\ell \, \text{Ki}_2\left((1-\delta_{ij})(\sigma_i \ell_i + \tau_{ij}) + \sigma_j \ell \right)} }
  \text{ if } i \leq j,\\
  \end{cases}
  %\right.
  \end{gathered}
\end{equation}
using the Kronecker function $\delta_{ij} = 1$ only if $i=j$ and null otherwise. $\tau_{ij}$ and $\tau_{ii}$ are respectively the optical lengths between the rings $i$ and $j$, and across the outer diameter of ring $i$. Reciprocity and conservation properties can be applied only after calculating the collision probabilities. The integrals involving the Ki function are solved thanks to the property $d_{\tau}\text{Ki}_n(\tau) = -\text{Ki}_{n-1}(\tau)$.

\textcolor{magenta}{
	The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:
	\begin{equation}
	\label{eq:esc_prob_cyij-}
	\varepsilon^-_{i+1/2,j} = \frac{2}{r_{i+1/2}} 
	\displaystyle ~\int_0^{r_{i+1/2}} { dh\, y
		\int_0^{\ell_j}{ d\ell 
			\text{Ki}_2\left(\tau_{ji} + \sigma_j \ell \right)
		}
	} \,\, ,
	\end{equation}
	for $i<j$, where $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergo a collision. 
}

Singularity of the integrand for the $h$-integration is noticed in the convex part while computing the collision probabilities \cite{hebert2009applied}; this notably happens at the outer radius of $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$. However, that integral can be regularized by a suitable change of variable. % $\varrho = \sqrt{r - h}$.
The calculation of the escape probabilities is not affected by this problem because of the factor $y$ that comes from the cosine of the angle described by the normal $\hat{n}$ and $\mathbf{\Omega}_p$, which cancels the endpoint singularity. The integral in $h$ can be resolved numerically with weights and points by the Gauss-Legendre quadrature in absence of endpoint singularities. Gauss-Jacobi quadrature is recommended in that case.

\begin{figure}[htbp]
  \centering
  \begin{minipage}[c]{.5\textwidth}
    \centering
    {%
    \input{figures/fullframe.tkz}
    \caption{Projection of vectors on the $x$-$y$ plane.}
    \label{fig:fullframe}
    }%
    \vspace{3mm}
    \vfill
    {%
    \input{figures/sphere.tkz}
    \caption{Use of symmetry in the sphere for integration in angle.}
    \label{fig:sphere_tracks}
    }%
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
    \input{figures/cyltracks.tkz}
    \caption{Integration along the tracks in the 1-D cylindrical geometry (suggested by Fig. 3.17 of reference \cite{hebert2009applied}).}
    \label{fig:cyltracks}
\end{minipage}%
\end{figure}

\subsection{Spherical geometry}
\label{sec:sphere}

The derivation of the scalar flux and current in the sphere follows the same rational adopted in section \ref{sec:cylinder} by angular integration of Eq. \ref{eq:ITE_angflx} and exploiting the symmetries available in the given coordinate frame. It is now convenient to start counting the polar coordinate $\theta$ from the normal $\hat{n}=\hat{e}_r$ and to have the azymuthal angle $\omega$ lying on a plane perpendicular to it, see Fig. \ref{fig:sphere_tracks}. It can be noticed then that by symmetry all tracks crossing a spherical surface in a point with the same polar angle are the same for any azymuthal angle. Therefore, when integrating over the unit solid angle ($d\mathbf{\Omega}=\sin \theta d\omega d\theta$), the integration on $\omega$ is promptly factored out, becoming simply $2\pi$. Positive and negative radial partial currents are obtained respectively by integrating on $\theta \in [0, \pi/2)$ and $\theta \in (\pi/2, \pi]$ with weight $\hat{n} \cdot \mathbf{\Omega} = \cos \theta$. The final integration on the sphere of radius $r$ %and division by the spherical surface $S(r)=4\pi r^2$
to get the total partial currents yields a situation similar to the case of the cylinder. The integration on the polar angle can be resolved again by the use of regularly spaced tracks at different values of $\theta$ covering the circular cut of the sphere that passes through the origin. Thanks to the central symmetry tracking integrals are the same for all directions, so that integration is carried on a semi-circle only, as in the case of the cylinder in Fig. \ref{fig:cyltracks}. Still by referring to Fig. \ref{fig:cyltracks}, we note that $\sin \theta = h/r$ and $\cos \theta = y/r$ with $y$ defined in Eq. \ref{eq:currp_cyl_atr}. Finally, Eq. \ref{eq:esc_prob_cyl} holds also for the sphere but using the new reduced escape probability:
\begin{equation}
\varepsilon_j(r) = \frac{2\pi}{r^2} \int_0^r { dh\, h y \int_{L_j}{
  d \ell \, \exp\left[-\tau( y, y - \ell )\right]}}.
\label{eq:esc_prob_sph}
\end{equation}
Endpoint singularities are avoided also in this case. The derivation of the equation for the current leaving the $i$-th spherical surface can be obtained straightforwardly from Eq. \ref{eq:esc_prob_cyij}.

\section{BOUNDARY CONDITIONS}
\label{sec:bc}

A generalized form for the boundary condition of the diffusion equation applying at the left side of the slab follows as $\Upsilon = - D_0 \phi_0 / (\Delta_0 / 2 + \zeta)$, where $\zeta$ is the extrapolation length in case of vacuum. Reflection can be reproduced by $\zeta \rightarrow \infty$, whereas the condition of zero-flux comes with $\zeta = 0$. The boundary $\delta J$ takes the simpler form $\delta J = - \delta D_{-1/2} \phi_0$ without dividing by the spatial width, since no particular extrapolation length is meant for the correction. Indeed, it will be possible to determine the actual extrapolation length only at convergence. The expression for the right boundary is straightforward, implying a non-negative current. Reflection is always reproduced at the center in curvilinear geometries.

About the currents from Eq. \ref{eq:J_tr}, the boundary conditions must be implemented through the first two terms at the right side due to the incoming flux. They are zero by definition only in case of vacuum. The flux expansion on the Legendre polynomials is necessary to reproduce other types of boundary condition. Again, we can only approximate the flux up to the first order, that is $\varphi \approx \phi/2 + 3/2 J \mu$. This approximation may not reproduce a vanishing current with reflection reproducing a symmetric distribution. At the left boundary for instance, the current can be expressed as $J(a) =  J^+ + J^- = 0$ with the entering current $J^+ = \int_0^1 { d\mu \mu \phi(a, \mu) } = - J^-$. $J^-$ takes into account all contributions coming from the right of $a$ up to $b$, see Eq. \ref{eq:J_tr}. In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \phi_0(a) / 2$, yielding $J^+(x) = \phi_0(a)/2\, E_3 \left(\tau(a, x)\right)$. This approximation does not guarantee to obtain the expected vanishing current at the boundary when computing the same current at the boundary with symmetric flux distributions. However, it is possible to determine the difference between the partial currents (remind that $J^-$ is negative). The higher (even) flux moments are responsible for this residual quantity, but they are not available unfortunately. A possible solution is considering that this quantity comes artificially from the only second moment, like\footnote{The operator $\pluseq$ assigns to $J$ the sum of itself and quantity to the right.}
\begin{equation}
\begin{split}
J^+(x) &\pluseq \frac{5}{4} \tilde{\phi}_2(a) \left[ 3 E_5(\tau(a, x)) - E_3(\tau(a, x)) \right],\\ &\text{ with } \tilde{\phi}_2(a) = - \frac{16}{5} \left( \frac{1}{4} \phi_0(a) + J^- \right).
\end{split}
\end{equation}
The flux expansion at the left boundary is then
\[ \phi(a, \mu) = \frac{1}{2} \phi_0 + \frac{3}{2} \mu \phi_1 + \frac{5}{4} \left( 3 \mu^2 - 1 \right) \tilde{\phi}_2, \]
with $\phi_1 = J = 0$ with reflection. The derivation of the correction at the other boundary of the slab can easily be derived. Although this correction improves the results, it cannot yield exactly the same results of the unfolded geometry, that is without reproducing the half symmetry by reflection. This occurs because the small current difference is assumed only on the second moment, neglecting the others which may become relevant on case-dependent basis.

\section{RESULTS}
\label{sec:res}

We resume here briefly the results of the two-group slab problem from \cite{tomatis2011application}. New results are also available for having new computer codes implemented with Python3. The reference solution is provided by a S$_{16}$ discrete ordinate computer code. Tab. \ref{tab:kconv} shows the differences on the reactivity by refining the mesh when the Ronen method is called with the diffusion solver. The reactivity is simply given as $\rho = 1 - 1/k$, where $k$ is the multiplication factor. The reference $k$ value from S$_{16}$ is 0.744417 ($I = 200$). Differences at $it=0$ correspond to the initial diffusion calculations without any current correction. Equidistant meshes are used in all calculations.
%
\begin{table}[htbp]
\centering
\caption{Reactivity differences in pcm by refining the mesh.\label{tab:kconv}}
\begin{tabular}{c|r|r}
\multirow{2}{*}{$I$} & \multicolumn{2}{|c}{$\Delta \rho$} \\ \cline{2-3}
     & $it=0$ & $it=100$ \\ \hline
 ~50 & 550.22 & 170.35 \\
 100 & 556.85 & ~36.08 \\
 200 & 558.50 & ~~1.72
\end{tabular}
\end{table}

The convergence on the flux is rather slow as shown in Fig. \ref{fig:kflx} and Fig. \ref{fig:eflx}. The corrections of the flux become smaller when iterating and a considerable number of iterations is necessary to approach the target results of the S$_{16}$ calculation.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=.8\linewidth]{figures/kflxconv.pdf}
  \caption{Behavior of the convergence on the flux (right) and on the reacitivity (left) for $I = 200$.}
  \label{fig:kflx}
\end{figure}
%
\begin{figure}[hbtp]
  \centering
  \includegraphics[width=.8\linewidth]{figures/eflxconv.pdf}
  \caption{Relative variation of the flux though the RM iterations ($I = 200$).}
  \label{fig:eflx}
\end{figure}

Results in the cylindrical and spherical coordinate systems will be presented in the final version of the article.

\section{CONCLUSION}
\label{sec:cncls}

The Ronen Method was firstly proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux. This originates an iterative scheme leading to new flux distributions solved by a diffusion solver yet with the aim to fulfill the integral transport equation. The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning. The solution of the diffusion equation offers many numerical advantages instead, solution speed and robustness above all.

Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues arising with flat flux. This is the option adopted in this work. The implementation of the boundary conditions is improved to reproduce the expected vanishing current in case of reflection.

We obtain more accurate results for the two-group benchmark problem reported in \cite{tomatis2011application}. The final version of the article will show the results of the application of the method in the curvilinear coordinate systems, still using isotropic sources. In general, slow convergence is observed for the scalar flux, whose larger discrepancy with respect to the reference is always located on the vacuum boundary. Although the method is converging to the reference results provided by a discrete ordinate transport code, the improvement of the convergence rate and the use of coarser meshes are crucial for the advancement of the methodology in practical applications. These topics will be addressed as future developements.

\section*{ACKNOWLEDGMENTS}

The authors express their gratitude to Prof. Yigal Ronen who initiated the method.

\setlength{\baselineskip}{12pt}
% warning: the style plain may not be the one of the conference
\bibliographystyle{unsrt}
\bibliography{RonenMethod}

\end{document}

### 2019-10-02 docs/ICTT2019/RMethod_ictt26_v2.tex
Journal and conference papers - tex, bibtex and figures
Journal and conference papers

--- 2019-10-02 docs/ICTT2019/RMethod_ictt26.tex
@@
 \textbf{Roy Gross and Erez Gilad}\\
-The Unit of Nuclear Engineering\\
+Unit of Nuclear Engineering\\
 Ben-Gurion University of the Negev, Israel\\
@@
 
+The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:
+
 \textcolor{magenta}{
-	The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:
 	\begin{equation}
@@
 
-Results in the cylindrical and spherical coordinate systems will be presented in the final version of the article.
+A one-group homogeneous problem is proposed hereafter in order to study the application of the Ronen method with angular redistribution in curvilinear geometries.
+Reference solutions are provided by collision probability method solvers, whose development take advantage of the implementation for the escape probabilities derived in section~\ref{sec:ce}.
+This choice is supported by the use of integral operators in the same Ronen method.
+Again, the implementation follows H\'ebert's textbook.
+The problems are solved in units of optical length, which means by simply setting the input total cross section equal to 1.
+The multiplying source becomes then $q = (c + \nu f) \phi_0 / 4\pi$, thus isotropic in angle, and with $c$ and $\nu f$ respectively as positive real numbers of secondaries per scattering and fission events.
+These numbers can be interpreted as conditional probabilities as well.
+The multiplicity $\nu$ acts as the eigenvalue of the problem.
+After the fundamental eigen-pair is known for given values of the constants and for a given size $L$, it is worthless to change $f$ alone to study the problem since only the product $\nu f$ counts for the balance (associated to the same eigenfunction).
+We choose then $f = 1$, ending up in only two free parameters for our study: $c_s$ and $L$.
+Even if this choice is unphysical for the assumed value of the total cross section together with $c > 0$, physical meaning is recovered by the fundamental value of $\nu$.
+
+\textcolor{red}{Roy will be able to check these assertions in the coming days.}
+
+\textcolor{blue}{The source assumes this form because the integration variables also have to the normalized by the mean free path (i.e. multiplied by the total cross section).}
+
+\textcolor{green}{The use of the integral transport eqn.
+to get reference solutions is motivated by two main reasons.
+The first is to use again what we're implementing now for the escape probabilities.
+The second is to get the reference solution by inverting the operator used in the RM.
+So that we'll really know what is the solution to match.
+Furthermore, this won't be affected by ray effects of any kind.
+Lastly, we'll have to be very careful to the endpoint singularity when computing the collision probabilities.}
 

### 2019-10-02 docs/ICTT2019/RMethod_ictt26.tex
Update ICTT src files and upload the slides shown at the conference

@@
 \end{equation*}
+These quantities can be computed only for $i > j$ since the others are simply opposite in sign.
+
+{\color{red}Roy-Erez: Please add a paragraph or reformulate the previous one to introduce the escape probabilities in the slab.}
 
@@
 \begin{equation}
-\varphi(\mathbf{r}, \mathbf{\Omega}) = \int_0^S{ds\, \frac{q(\mathbf{r} - s \mathbf{\Omega}_p, \mathbf{\Omega})}{\sin \theta} \exp(-\frac{\tau(\mathbf{r}, \mathbf{r} - s \mathbf{\Omega}_p)}{\sin \theta})}.
+\varphi(\mathbf{r}, \mathbf{\Omega}) = \int_0^S{ds\, \frac{q(\mathbf{r} - s \mathbf{\Omega}_p, \mathbf{\Omega})}{\sin \theta} \exp \left[ -\frac{\tau(\mathbf{r}, \mathbf{r} - s \mathbf{\Omega}_p)}{\sin \theta} \right]}.
 % + \varphi(\mathbf{r} - S \mathbf{\Omega}_p, \mathbf{\Omega}) \exp(-\frac{\tau(\mathbf{r}, \mathbf{r} - S' \mathbf{\Omega})}{\sin \theta}).
@@
 The theory of collision probability methods originates from the use of isotropic sources, which are also considered as uniform in the cells of the spatial mesh.
-Two integration in space arise for each direction $\mathbf{\Omega}$, connecting the source in region $j$ to the flux (or its total reaction rate) in region $i$ by means of its collision probability.
+Two integrations in space arise for each direction $\mathbf{\Omega}$, connecting the source in region $j$ to the flux (or its total reaction rate) in region $i$ by means of its collision probability.
 The incoming flux is considered as isotropic too, or linearly anisotropic in angle as in \cite{hebert2009applied} to relate the partial entering and outgoing currents to the only first flux moments.
@@
 \end{equation}
-with $W^+ = \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p > 0\right\}$. Using the surface element $dA' = s d\omega ds$ and $\mathbf{r}'_p = s \mathbf{\Omega}_p$, it is also:
+with $W^+ = \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p > 0\right\}$. Using the surface element $dA' = s d\omega ds$ and $\mathbf{r}'_p = \mathbf{r} - s \mathbf{\Omega}_p$, it is also:
 \begin{equation}
@@
 
-\textcolor{magenta}{
 The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:
@@
     \displaystyle ~\int_0^{r_{i+1/2}} { dh\, y
-		\int_0^{\ell_j}{ d\ell 
-			\text{Ki}_2\left(\tau_{ji} + \sigma_j \ell \right)
+        \int_0^{\ell_j}{
+            d\ell \text{Ki}_2 \left(\tau_{ji} + \sigma_j \ell \right)
         }
-	} \,\, ,
+	},
 \end{equation}
-	for $i<j$, where $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergo a collision.
-}
+for $i<j$, where $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergoing a collision.
 
@@
 \ref{eq:esc_prob_cyij}.
+
+\subsection{Derivation of collision probabilities}
+\label{sec:cp}
+
+After all escape and inscape probabilities are known, the first flight collision probabilities can be determined by conservation properties in order to reduce the amount of total operations.
+For instance, the probability for a neutron emitted isotropically in the region $i$ to collide in the same region must fulfill the following relation:
+\begin{subequations}
+\begin{equation}
+p_{ii} + e^+_{i+1/2,i} + e^-_{i-1/2,i} = 1 \; \forall i.
+\label{eq:pii}
+\end{equation}
+This can be generalized with neutrons coming from region $j$ and colliding in region $i$ as:
+\begin{equation}
+p_{ij} = e^+_{i-1/2,j} - e^+_{i+1/2,j} + e^-_{i+1/2,j} - e^-_{i-1/2,j},
+\label{eq:pij}
+\end{equation}
+\label{eq:cps}
+\end{subequations}
+with $e^+_{i-1/2,i} = e^-_{i+1/2,i} = 0$ to find again Eq. \ref{eq:pii}.
+
+Particle conservation on the full domain requires $\sum_i p_{ij} + e^+_{I+1/2,j} = 1$, $\forall j$. At last, reciprocity implies
+\[
+  \frac{p_{ij}}{V_i \sigma_i} = \frac{p_{ji}}{V_j \sigma_j} \quad \text{and} \quad
+  \frac{p_{j, i+1/2}}{V_j \sigma_j} = \frac{4 e_{i+1/2, j}}{S_{i+1/2}} \quad \text{for } 1 \leq i,j, \leq I,
+\]
+with the escape probability counting for both contributions from partial currents. These expressions can be used to verify Eqs. \ref{eq:cps}.
+
+Transmission probabilities between surfaces are also needed with boundary conditions different from vacuum. We do not derive them in this work because we only treat bare problems.
 

### 2019-10-02 docs/ICTT2019/slides/RM1Dgeoms_ictt26.tex
Update ICTT src files and upload the slides shown at the conference

\documentclass[black]{slideCEA}

\usetikzlibrary{decorations.text}
\usepackage{multicol}
%\usepackage{etoolbox}
\usepackage{mathrsfs}
%\usepackage{mathtools}
\usepackage[overload]{empheq}

\newcommand{\bOm}{\boldsymbol{\Omega}}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\DeclareMathOperator{\sign}{sign}

%% %% Possible specific options:
%% %%   ** notofficial: change few aspect of the style: Front page, font black (not grey),
%% %%        !!! Compulsory to use the following two options
%% %%   ** topbar to get the path as ``section : subsection'' on top
%% %%   ** bottombar to get
%% %%          ==> left: date (with hidden link to toc if it exists, and its name is Menu, as here)
%% %%          ==> middle: subtitle (meeting name) - author
%% %%          ==> right: currentslidenb/totalslidenb (with hidden link to backup toc if it exists and is called MenuBackup, as here)
%% %%   Same links are hidden in official bottombar to avoid unpleasant scrolling
%% %%   CEA in official bottom bar can be changed to display institute like CEA/DIR/DEP/SER/LAB... with \BottomBarInstitute

%% %% Title of the slides and meeting
\YTitleFP{30}
\title{On the Ronen Method
       in simple 1D geometries}% \textcolor{white}{l}}
\FrontPageSubTitleY{55}
\subtitle{\textit{\normalsize Derivation of accurate expressions for the current in the slab and in the curvilinear reference frames}}
\date{September 27\textsuperscript{th}, 2019}
\Event{{\footnotesize 26\textsuperscript{th} International Conference on
       Transport Theory (ICTT26), Paris, France}}
\YEventFP{155}

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% %%%%%%%%%%%%%% Personnal informations (most of which can %%%%%%%%%%%%%%%%%
%% %%%%%%%%% be put by default in the class file once and for all) %%%%%%%%%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% %% Personnal information about the author
\YAuthFP{100}
%\author{Daniele Tomatis}
\author{Daniele Tomatis\\
        {\small \textcolor{ceared3}{CEA SERMA, France}
         \textcolor{blue}{(daniele.tomatis@cea.fr)}}}
%\MailAddress{daniele.tomatis@cea.fr}
%\Telephone{+33 (0)1 69 08 25 26}
%\Fax{(0)1 YY YY YY YY}
%% %% Possible option to add information on the author line (only for non-official for the moment)
\OtherAuthor{\\[6mm]Roy Gross and Erez Gilad\\[2pt]
             \includegraphics[width=50mm]{logos/BGU_transp.png}
             % {\footnotesize University of Ben Gurion, Israel}
             }

%% %% Information about CEA: your service/departement/direction/centre
\Direction{Direction de l'{\'E}nergie Nucl{\'e}aire}
\Departement{D{\'e}partement de Mod{\'e}lisation des Syst{\`e}mes et Structures}
\Service{Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA)}
\Centre{Centre de Saclay}
\CentreAddress{91191 Gif-sur-Yvette Cedex, France}
\BottomBarInstitute{CEA/DEN/DANS/DM2S/SERMA/LPEC}

\CeaLogo{cea-tr.png}
%% %% On can change the logo with \CeaLogo{cea-saclay-tr.png} %% \CeaLogo{cea-den-tr.png}
%% %% One can add a picture in the Title bar of every slide. To do so, define
%% %% *** The path to the picture: \TitleBarPicture{Nobel-Prize-small.png}
%% %% *** The size of the picture (in mm): \TitleBarPictureSize{20} [20 is the default]
%% %% *** The X of the picture (in mm): \TitleBarPictureX{230} [230 is the default]
%% %% *** The Y of the picture (in mm): \TitleBarPictureY{0} [0 is the default]
%\TitleBarPicture{Nobel-Prize-small.png}
\TitleBarPicture{logos/BGU_transp_bk.png}
\TitleBarPictureSize{50}
\TitleBarPictureX{198}
\TitleBarPictureY{2}
\FrameTitleS{48}  % force line break in frametitle after 55 characters

\FrontPagePicture{logos/logo_ICTT26_white.png}
\FrontPagePictureX{10}
\FrontPagePictureY{90}
\FrontPagePictureSize{70}
%% %%%%%%%%%%%%%%%%%%%% Enf of personnal informations %%%%%%%%%%%%%%%%%%%%%%%

\graphicspath{{logos/}{../../../bgu_seminar/figures/}}

%% %% Starting the slide
\begin{document}

%% %% Front page (opening one)
\theframetitle

%% %% One can add a picture in the Front page. To do so, define
%% %% *** The path to the picture: \FrontPagePicture{Nobel-Prize-small.png}
%% %% *** The size of the picture (in mm): \FrontPagePictureSize{70} [70 is the default]
%% %% *** The X of the picture (in mm): \FrontPagePictureX{140} [140 is the default]
%% %% *** The Y of the picture (in mm): \FrontPagePictureY{70} [70 is the default]
%\FrontPagePicture{Nobel-Prize-small.png}
%\theframetitle

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% %% If none of the possible front page fit you, you can create your own doing
%% %% %%%%%%%%%%%% Or directly modify theframetitle in the class %%%%%%%%%%%%%%%
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \begin{frame}[plain] %% begin frame
%%   \FrontPageRedStructure   %% add left bar with CEA logo and cea web address
%%   \begin{changemargin}{90 mm}{0cm} %% restraining the area to white space
%%     \begin{center}
%%       {\LARGE   \textcolor{ceared1}{Nouveau titre de présentation} }
%%     \end{center}
%%   \end{changemargin}
%% \end{frame}

%% the ``sections={1-\totvalue{SectionCounter}},'' comes along with usepackage{totcount}
%% It is used to get the section number of backup (if so) and not display it in this toc.
%% There is a specific toc for backup in \backupbegin
%% If one cannot install totcount, remove \tableofcontents[sections={1-\totvalue{SectionCounter}},

\setcounter{tocdepth}{2}
\setbeamertemplate{section in toc}[ball unnumbered]
\begin{frame}
  \frametitle{Outline}
%\begin{multicols}{2}
%\parbox[t]{.8\textwidth}{
\tableofcontents
%}
%\end{multicols}
\end{frame}

%\frame<4>[label=Menu]{
%  \frametitle{Sommaire}
%  \only<1>{\tableofcontents[sections={1-\totvalue{SectionCounter}},hideallsubsections]}
%  \only<2>{\tableofcontents[sections={1-\totvalue{SectionCounter}},currentsection,hideothersubsections]}
%  \only<3>{\tableofcontents[sections={1-\totvalue{SectionCounter}},currentsection,hideothersubsections,currentsubsection]}
%  \only<4>{\tableofcontents[sections={1-\totvalue{SectionCounter}},subsectionstyle=show]}
%}

\section{Introduction}

\begin{frame}
  \frametitle{Introduction and Motivation}
  \begin{itemize} \large
    \setlength{\itemsep}{5mm}
    \item The use of \textcolor{ceared1}{diffusion theory} is very practical in ordinary \textcolor{ceared1}{full core calculations} in terms of \emph{computational time} and \emph{numerical schemes}\\
    {\hfill \normalsize \color{ceagreen3}
    $\rightarrow$ fast calculations, parabolic/elliptic equations, diagonal dominance
    }
    % \pause
    \item Cross section preparation by \textcolor{ceared1}{homogenization} and \textcolor{ceared1}{equivalence} theory form a consistent frame-work with \textcolor{ceablue1}{nodal expansion} or \textcolor{ceablue1}{finite-element} solving methods\\
    {\hfill \normalsize \color{ceagreen3}
    $\rightarrow$ current standard approach in nuclear industry
    }
    % \pause
    \item Diffusion \textcolor{ceared1}{cannot} reproduce strong transport effects with sufficient accuracy\\%:

%   \begin{itemize} \large
%     \setlength{\itemsep}{3mm}
%     \item presence of void
%     \item regions of high absorption
%     \item materially heterogeneous systems
%     \item substantial scattering anisotropy
%   \end{itemize}

    {\hfill \normalsize \color{ceagreen3}
    $\rightarrow$ fails with strong absorption and flux gradients, rather miss anisotropy
    }
    \item {What's the \emph{best definition} of the diffusion coefficient? Is there any?}\\
    % \pause
    \item Influence of the {\color{ceared1}geometry frame} on the \emph{flux convergence} by Ronen iterations
  \end{itemize}
\end{frame}

%\include{backup_slides/loworder_trapprox}
% ===================================

\section{Core Calculations}

% \subsection{Common features of core design}
% \include{slides/coredesignfeatures}

\subsection{Two-step calculation scheme}
\begin{frame}
  \frametitle{Two-step core calculations}

  \begin{columns}
  \vspace{-5mm}
    \column{0.65\linewidth} \centering
    {\includegraphics[width=\textwidth]{FA_homog.png}}
    \column{0.35\linewidth} \centering
    {\includegraphics[width=0.9\textwidth]{core_quarter.png}}
  \end{columns}

  \begin{tikzpicture}[overlay, remember picture]
  \draw[->, thick, draw=ceagreen2, line width=5mm]
    ([yshift=3cm, xshift=-2cm]current page.south)
    -- ([yshift=3cm, xshift=-8.5cm]current page.south east)
    node[midway, above] {\color{ceagreen3}\large \tt \bf
    \begin{tabular}{c}
    multi-group \\ xs library
    \end{tabular}
    };
%    [xshift=-2cm, yshift=2cm]
  \end{tikzpicture}
\end{frame}

%%% this does not work %%%
%\begin{frame}
%  \frametitle{3D Coarse Mesh Kinetics}
%  \label{sec:fm3D}
%  \input{coarse_mesh3D}
%\end{frame}

\subsection{Transport effects in core calculations}
\begin{frame}
  \frametitle{\insertsubsectionhead}
  \begin{block}{General issues for safety and design calculations}% or warnings?
  { \vspace{3mm}
  %
  \begin{itemize} \large
    \setlength{\itemsep}{3mm}
    \item \textcolor{ceablue1}{High absorption} and \textcolor{ceablue1}{low scattering}: presence of black materials to neutrons (mechanical and chemical shim), weak moderation, spectrum hardening
    %\item \textcolor{ceablue1}{high absorption}, like with the elements close to the thermal energy range causing neutron spectrum hardening (mechanical shim by black control rods, fuel blended with burnable poisons)
    \item \textcolor{ceablue1}{scattering anisotropy}: e.g. forward-peaked moderation in water
    \item potential \textcolor{ceablue1}{occurrence of void} under operation or in accidental transients (LWR/FR)
    \item angle-dependent boundary conditions: free-surfaces-vacuum, anisotropic albedos
    \item \textcolor{ceablue1}{steep flux gradients}: proximity to the reflector in thermal reactor, strong localized absorption
    %\item boundary with selective and anisotropic reflection (e.g. heavy reflector to extend the vessel lifetime or the respose of water reflector in fast groups)
    \item \textcolor{ceablue1}{material heterogeneity}: heterogeneous core loading with material discontinuities at the interfaces between fuel elements (MOX/UO2 mixed cores, with both radial and axial discontinuities)
    \item \emph{memory-effects} due to temporary and localized short reactivity insertion (incore instrumentation, rapid geometry and material changes, presence of noise)
  \end{itemize}
  }
  \end{block}
\end{frame}
% ===================================

\section{Diffusion Theory}

\subsection{Conservation equation and Fick's law}
\begin{frame}
  \frametitle{Continuity equation with approximated transport law}
  %
  \vspace{-5mm}
  \begin{block}{Integro-differential Neutron Transport Equation (NTE)}
  {\hfill \normalsize \cite{duderstadt1979transport}}
  {
  \begin{gather*}
  \left[ \frac{1}{v}\frac{\partial}{\partial t}
  %+ \nabla \cdot (\bOm \,\_) + \Sigma_t(\mathbf{r}, E) \right] \varphi(\mathbf{r}, E, \bOm)
  + \bOm \cdot \nabla + \Sigma_t(\mathbf{r}, E) \right] \varphi(\mathbf{r}, E, \bOm, t)
  = \frac{\chi(E)}{4\pi} \int_0^{\infty} {dE' \nu\Sigma_f(\mathbf{r}, E') \phi(\mathbf{r}, E', t)}
  + s_{\text{ext}}(\mathbf{r}, E, \bOm, t) +\\
  \int_{4\pi} d\bOm'
  \int_0^{\infty} {dE' \Sigma_s(\mathbf{r}, E' \rightarrow E, \bOm' \rightarrow \bOm)
  \varphi(\mathbf{r}, E', \bOm', t)
  } = q(\mathbf{r}, E, \bOm, t).
  \end{gather*}
  }
  \end{block}
  Let us introduce the scalar flux and the current, respectively:
  \[
    \phi = \int_{4\pi}{d \boldsymbol{\Omega}
    \varphi(\mathbf{r}, \boldsymbol{\Omega}[, \ast] )}
    \quad \text{and} \quad
    \mathbf{J} = \int_{4\pi}{d \boldsymbol{\Omega} \boldsymbol{\Omega}
    \varphi(\mathbf{r}, \boldsymbol{\Omega}[, \ast] )},
  \]
  and integrate the NTE to get the continuity equation:
  \[
    \frac{1}{v}\frac{\partial \phi}{\partial t} + \nabla \cdot \mathbf{J}
    + \Sigma_t \phi = \int_{4\pi}{d \bOm \, q(\mathbf{r}, \boldsymbol{\Omega}[, \ast] )}.
  \]
  Use \textcolor{ceared1}{Fick's law} as closure
  \textcolor{ceared1}{$\mathbf{J} = - \mathcal{D}\nabla \phi$}, with the
  vacuum bnd. conds. $- \partial_{\hat{n}} \phi = \phi/
  \zeta$ and the extrapolated length $\zeta = 2\mathcal{D}$ ($\approx 2.13
  \mathcal{D}$ in computer codes).
  \begin{alertblock}{}
    \textit{N.B. A unique family of fissiles is represented here;
    precursors of delayed neutrons are also necessary for kinetics
    with fission; $\Sigma_t(\bOm[, \ast])$ if no rotational symmetry
    in scattering events.}
  \end{alertblock}
\end{frame}

% WARNING: it is important to remind that the source term in the trasnport
% equation is given as sum of moments on spherical harmonics!
% \include{backup_slides/sourcebymoments}

\subsection{About the diffusion coefficient}
%
\begin{frame}%[t] \vspace{5mm}
  \frametitle{The $P_1$ branding of the diffusion coefficient}
  \begin{alertblock}{} \large
  $P_N$: flux expansion on sph. harmonics and projections over $4\pi$ of the NTE on $1$, $\bOm$, $\ldots$
  \end{alertblock}
  \begin{block}{If we limit the expansion to the first moment:}
  {
  %\[ \left\{
  \begin{align}[left=\empheqlbrace]
  \frac{1}{v} \frac{\partial \phi}{\partial t} + \nabla \cdot \mathbf{J} + \Sigma_t\, \phi &=
  \int_0^{\infty} {dE' \Sigma_{s,\ell=0}(E' \rightarrow E)\,\phi(\mathbf{r}, E', t) \ }
  + S_{\text{ext},\ell = 0},\label{eq:sflx}\\[3mm]
  \frac{1}{v} \frac{\partial \mathbf{J}}{\partial t} + \nabla \cdot \boldsymbol{\Pi} + \Sigma_t\, \mathbf{J} &= \int_0^{\infty} {dE' \Sigma_{s,\ell=1}(E' \rightarrow E)\, \mathbf{J}(\mathbf{r}, E', t)} + \mathbf{S}_{\text{ext},\ell = 1},\label{eq:curr}
  \end{align}
  %\right. \]
  }\vspace{5mm}
  with $\boldsymbol{\Pi} = \int_{4\pi}{d \bOm (\bOm \bOm)\varphi(\mathbf{r}, \bOm}[, \ast])$,
  or \textcolor{ceablue1}{$\boldsymbol{\Pi} = \phi / 3$} if
  \textcolor{ceablue1}{$\varphi = \left( \phi + 3 \mathbf{J} \cdot \bOm \right)/4\pi$},
  i.e. the \textcolor{ceared1}{$P_1$ approximation}.\vspace{5mm}

  \pause{
  Use then the \textcolor{ceablue1}{multi-group energy formalism} in Eq. \ref{eq:curr}, assume \textcolor{ceablue1}{stationarity} and an \textcolor{ceablue1}{isotropic external source} to write:
  \[
  \frac{1}{3}\nabla \phi_g + \Sigma_{t,g} \,\mathbf{J}_g = \sum_{g'=1}^G {\Sigma_{s,1,g' \rightarrow g}\, \mathbf{J}_{g'}}
  \]
  }\vspace{5mm}

  \pause{
  In presence of dominant scattering and at \emph{thermal equilibrium} \textcolor{ceagreen3}{$\sum_{g'} {\Sigma_{s,1,g' \rightarrow g} \mathbf{J}_{g'}} \approx \mathbf{J}_{g} \sum_{g'} {\Sigma_{s,1,g \rightarrow g'}}$}, thus yielding a specific diffusion coefficient:
  \[
  \mathbf{J}_g = -D_g \nabla \phi_g \implies
    \textcolor{ceared1}{D_g(\mathbf{r}) = \frac{1}{3\Sigma_{tr,g}}}
    \quad \text{with} \quad \Sigma_{tr,g} = \Sigma_{t,g} - \Sigma_{s,1,g}, \; \forall g.
  \]
  }
  \end{block}
\end{frame}

% \include{backup_slides/otherdiffdefs}

% \subsection{The fundamental leakage model}
% \include{backup_slides/BNlm}

\subsection{Diffusion tensors}
\begin{frame}
  \frametitle{Drift, diffusion tensors, and more$\ldots$}
  %
  \begin{block}{Integral Neutron Transport Equation}
   \begin{gather*}
   \varphi({\mathbf{r}, E, \bOm}) =
     \int_0^{\mathpzc{S}(\mathbf{r},\bOm)}{ds\,
     q(\mathbf{r} - s\, \bOm, E, \bOm) \exp{ \left[
     - \mathscr{L}_{op}(\mathbf{r}, s, E, \bOm) \right]}
   }\text{ with } \mathscr{L}_{op} = \int_0^{s}{ds'\, \Sigma_t(\mathbf{r} - s'\, \bOm, E)},\\
     q(\mathbf{r}', E, \bOm) = \sum_{\ell m} {Y_{\ell m}(\bOm)
       \int_0^{\infty}{dE' \left( \Sigma_{s,\ell}(\mathbf{r}', E' \rightarrow E)
       + \chi(E) \nu\Sigma_f(\mathbf{r}', E')\delta_{\ell 0}\delta_{m 0} \right)
       \phi_\ell^m(\mathbf{r}', E')}} + \text{b.c.}
   \end{gather*}

  \end{block}
  %
  \begin{columns}
  \column{.325\textwidth}
  \def\dx{0.25}
  \begin{tikzpicture}[declare function={f(\x) = (\x - 1)/3+2;}]
   \draw[->, very thick] (1,0) -- (4,{f(4)}) node[below right] {
     \begin{tabular}{c}
       $\mathbf{r}' = \mathbf{r}-s\, \bOm$,\\
       $s = \lVert \mathbf{r}' - \mathbf{r} \rVert$
     \end{tabular}
   };
   \draw[->, very thick] (0,0) -- (1,{f(1)}) node[below right] {$\mathbf{r}$};
   \draw[->, thick] ({4-\dx},{f(4)+\dx}) -- ({3-\dx},{f(3)+\dx}) node[above left] {$s, \bOm$};
   \draw[->,dashed] (0,{f(0)}) -- (1,{f(1)}) -- (4,{f(4)}) -- (5.5,{f(5.5)})
     node[above right] {$\mathpzc{S}$};
   \draw[ultra thick] plot[smooth] coordinates {(3,4) (5.5,{f(5.5)}) (6,3)};
  \end{tikzpicture}
  %
  \column{.675\textwidth}
  \begin{block}{}
  {Assume \textcolor{ceared1}{isotropic} sources (with pure scattering and one group for simplicity), expand the flux by Taylor around $\mathbf{r}$ and integrate to obtain the current:
  \begin{flalign*}
  \begin{split}
  %\mathbf{J}(\mathbf{r}) = \frac{1}{4\pi}
  %  \int{ d \bOm \int_0^{\mathpzc{S}}{
  %    ds\,\bOm\, \Sigma_{s,0}(\ast) \exp\left[ \mathscr{L}_{op} \right] \cdot\\
  %    \left( \phi(\mathbf{r}) - \bOm \cdot \nabla \phi \,s
  %           + \bOm \mathbf{H} \bOm\, s^2 + O(s^3)\right)
  %    }}
  \mathbf{J}(\mathbf{r}) = \int d\mathbf{r}'
    \frac{\mathbf{r}' - \mathbf{r}}
         {4\pi \lVert \mathbf{r}' - \mathbf{r} \rVert^3}
      \Sigma_{s,0}(\ast) e^{ -\mathscr{L}_{op} } \cdot \\
      \left( \phi(\mathbf{r}) - s \, \bOm \cdot \nabla \phi
             + s^2 \, \bOm \mathbf{H} \bOm + O(s^3)\right)\\[3mm]
    \Rightarrow \textcolor{ceared1}{
    \mathbf{J}(\mathbf{r}, E) =
      \underbrace{\vec{\mathpzc{d}}(\mathbf{r}, E) \phi(\mathbf{r}, E)}_\text{
      advection~/~drift}
      - \underbrace{\mathbf{D}(\mathbf{r}, E) \nabla \phi(\mathbf{r}, E)}_\text{
      term w. diffusion tensor}
      + \ldots
    }
  \end{split}
  \end{flalign*}
  }
  \end{block}
  \end{columns}
  %
  \begin{columns}
  \column{.6\textwidth}
  \begin{exampleblock}{Under the following conditions:}
  \begin{enumerate}[i.]
    \item smooth flux gradient and small higher derivatives
    \item weakly absorbing and highly scattering media
    \item \textcolor{ceablue1}{constant cross sections in space}
  \end{enumerate}
  \end{exampleblock}
  %
  \column{.4\textwidth}
  \[ \Rightarrow \textcolor{ceared1}{
    \mathbf{J} = -D \nabla \phi \quad \text{with}
    \quad D = \frac{\Sigma_s}{3 \Sigma_t^2}
  }\]
  \end{columns}
\end{frame}
% ===================================

% \section{Cross section preparation}
% \subsection{Homogenization and Equivalence Theory}
% \include{backup_slides/homogequiv}
% ===================================

\section{The Ronen Method}

\subsection{Principles \& Implementation}
%
\begin{frame}
  \frametitle{\insertsectionhead}
  \begin{block}{Principles \& Implementation}
  {\hfill \cite{ronen2004accurate, tomatis2011application}}
  {
  \begin{itemize} \large
    \setlength{\itemsep}{3mm}
    \item The \textcolor{ceared1}{best diffusion coefficient} would be the one satisfying exactly Fick's law with the same flux and current computed by transport (with the current containing all contributions from higher order moments!)
    \item<2-> Use a higher-order \textcolor{ceablue1}{integral} transport operator to obtain \textcolor{ceared1}{more accurate estimates of the current} \emph{by sources determined with the diffusion flux}
    % \item<2-> An ``\textcolor{ceared1}{equivalent}'' (\textcolor{ceablue1}{integral}) transport problem is defined to determine the diffusion coefficient:
    % \[
    %  D_i = - \frac{\mathbf{J} \cdot \hat{e}_i}
    %    {\nabla \phi \cdot \hat{e}_i},
    %  \text{ where \textcolor{ceared1}{$\mathbf{J}$ is estimated by a higher order transport operator!}}
    % \]
    \item<3-> Solve diffusion \emph{again} with the new coefficients $D_i = - \left[\mathbf{J}(\phi) \cdot \hat{e}_i\right] \big/ \left[ \nabla \phi \cdot \hat{e}_i\right]$
    \item<4-> Such agreement is sought numerically by \textcolor{ceablue1}{non-linear iterations}
    \item<5-> \textcolor{ceared1}{Alternative implementation} by a CMFD-like scheme \cite{smith1983nodal}, with currents at cell interfaces as:
    \[
    J^{(k,+)} \approx
    \underbrace{
    - 2D_\text{DIFF} \frac{\phi^{(k+1,+)} - \phi^{(k,+)}}{\Delta_{k+1} + \Delta_{k}}
    }_\text{Diffusive current}
    -2 \underbrace{
    (\textcolor{ceared1}{\delta D})
      \frac{\phi^{(k+1,+)} \textcolor{ceared1}{+} \phi^{(k,+)}}{\Delta_{k+1} + \Delta_{k}}
    }_\text{Transport correction},
    \]
    where $\textcolor{ceared1}{\delta D} \propto (J_{\text{TRANSP}} - J_\text{DIFF})$.
  \end{itemize}
  }
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Boundary conditions (bc.)}

  \begin{alertblock}{A known issue\ldots}
    bc. apply on the angular flux in transport and we solve only for the scalar flux in diffusion.
  \end{alertblock}
  { Generalized form for finite difference equations:
  \[
    J = - \frac{D \phi_{bc}}{\Delta_{bc} / 2 + \zeta} \text{ with }
    \begin{cases}
      \zeta \propto \lambda_t & \text{extrapolated length for vacuum}, \\
      \zeta = 0 & \text{zero flux}, \\
      \zeta \rightarrow 0^+ & \text{reflection by vanishing current};
    \end{cases} \qquad \delta J_{bc} = \delta D \phi_{bc}.
  \]
  }\vspace{-10mm}

  \visible<2->{
    \flushright \textcolor{ceared1}{\large bc. are given for incoming
    particles\\and we use a transport operator to estimate the current!}\\[3mm]
  }

  \begin{block}{The problem of reflection and periodic translation}
    We expand the angular flux on spherical harmonics to get expressions based
    on moments. Now consider a bare homogeneous slab
    ($\varphi \approx \phi/2 + 3/2 J \mu$) with specular reflection at one side.
    \alert<3>{$J^+ + J^- \neq 0$} at the refl. boundary for $\varphi \approx \phi/2$.
    {
      $\longrightarrow$ Fix $J=0$ by corrections from higher moments as:
      \begin{equation*}
      \begin{split}
      J^+(x) &= \frac{\phi_0(a)}{2}E_3(\tau(a, x)) + \frac{5}{4} \tilde{\phi}_2(a) \left[ 3 E_5(\tau(a, x)) - E_3(\tau(a, x)) \right],\\
             \text{with }& \tilde{\phi}_2(a) = - \frac{16}{5} \left( \frac{1}{4} \phi_0(a) + J^- \right) \text{ and }
      \phi(a, \mu) = \frac{1}{2} \phi_0 + \frac{3}{2} \mu \phi_1 + \frac{5}{4} \left( 3 \mu^2 - 1 \right) \tilde{\phi}_2.
      \end{split}
      \end{equation*}
    }
  \end{block}
\end{frame}

\subsection{Expressions for the current in simple 1D geometries}

\begin{frame}
  \frametitle{Expressions for the current in simple 1D geometries}

  \vspace{-5mm}
  {Derivation of the equation for the current in mono-dimensional problems
  (\emph{bare bodies}) by \textcolor{ceared1}{escape probabilities}.
  The current of particles crossing the surface $S$ at $r$ is
  \[
    J(r) S(r) = \sum_j q_j V_j e_{j}(r), \text{ where}
  \] \vspace{-5mm}
  \begin{itemize}
    \item $q_j$ is the (isotropic) source in the region $j$ of volume $V_j$ and\\
    \item $e_j(r)$ is the probability for a particle isotropically emitted
          in region $j$ to cross S(r) uncollided.
  \end{itemize}
  }
  \begin{figure}[t]
    \centering
    \scalebox{1.5}{
      \input{../figures/mesh1d.tkz}
    }
    \caption{Mesh notation for the 1d problems.}
  \end{figure}
  {
  In \textcolor{ceablue1}{\bf 1D slab}, integration on the polar angle is resolved \emph{analytically} by \textcolor{ceablue1}{exponential integral functions $E_n$}:
  % \[
  %   E_n(\tau) = \int_1^{\infty}{du\, \frac{e^{-|tau|\,u}}{u^n}}
  %     = \int_0^1 {d\mu \, \mu^{n-2} e^{-|\tau| / \mu}}.
  % \]

  \begin{equation*}
  \begin{split}
  J_{i+1/2} =& \int_0^1   {d\mu\, \mu \varphi(a, \mu) e^{-\tau(a, x_{i+1/2})/\mu}}
             - \int_0^{-1}{d\mu\, \mu \varphi(b, \mu) e^{-\tau(b, x_{i+1/2})/\mu}}\\
          +& \sum_{j=0}^{I-1} { \sign(x_{i+1/2} - x_{j+1/2}) \frac{q_{0,j}}{2} \int_{x_{j-1/2}}^{x_{j+1/2}}{dx'
          E_{2} \left(\lvert \tau(x', x_{i+1/2}) \rvert \right) } }.
  \end{split}
  % \label{eq:J_tr}
  \end{equation*}
  }
\end{frame}

\subsubsection{Slab}

\begin{frame}[allowframebreaks]
  \frametitle{An example in the bare homogeneous slab}
  {\hfill \cite{tomatis2011application}}%\\[3mm]

  \begin{block}{}
  % In 1-D, we find the \textcolor{ceablue1}{exponential integral functions $E_n$} and the diffusion tensor simplifies in a single coefficient.
  % \[
  %   \begin{split}
  %   E_n(\mathcal{L}_{op}) = \int_1^{\infty}{du\, \frac{e^{-|\mathcal{L}_{op}|\,u}}{u^n}}\\
  %     = \int_0^1 {d\mu \, \mu^{n-2} e^{-|\mathcal{L}_{op}| / \mu}}.
  %   \end{split}
  % \]
  {\textcolor{ceablue1}{APPROX}: 2G problem with isotropic scattering, extrapolated length $\zeta = 2.13 \mathcal{D}$}\\
  {\textcolor{ceablue1}{b.c.}: reflection at left, vacuum or zero flux at right.}
  \end{block}

  \begin{table}
  \centering
  \caption{Cross section data of the homogenized FA ($k_{\infty} = 1.07838$); scattering cross section comes from sum on columns.}
  \begin{tabular}{*{6}{c}}\hline \hline
  Group $g$ & $\Sigma_{t,g}$ & \multicolumn{2}{c}{$\Sigma_{s,0,g' \rightarrow g}$} &
  $\chi_g$ & $\nu\Sigma_f$ \\ \hline
  1 & 5.31150E-01 & 5.04664E-01 & 2.03884E-03 & 1 & 7.15848E-03 \\
  2 & 1.30058E+00 & 1.62955E-02 & 1.19134E+00 & 0 & 1.41284E-01 \\
  \hline \hline
  \end{tabular}
  \end{table}

  \begin{columns}
  \column{.5\textwidth}
  \begin{table}\centering
  \caption{17$\times$17 PWR UO2 FA data (3.5\% enr. w/o $^{235}$U).}
  \begin{tabular}{lc} \hline \hline
    Slab width & 21.5 cm\\
    Fuel temp. & 900 K\\
    Water temp.& 600 K\\
    Water density& 0.66 g/cm$^3$\\
    Boron conc.& 500 ppm\\ \hline \hline
  \end{tabular}
  \end{table}
  \column{.5\textwidth}
  \begin{table}
  \centering
  \caption{Results on the multiplication factor $k$}
  \begin{tabular}{*{4}{c}} \hline \hline
   Left b.c.: & \multicolumn{2}{c}{vacuum} & zero flux\\
   \cline{2-4}
    & $k$ & $\Delta k$ (pcm) & $\Delta k$ (pcm) \\ \hline
    Ref. S16             & 0.745675 & ~~~0~ &    -    \\
    $D = 1/(3 \Sigma_t)$ & 0.741377 & -429.8& -5800.1 \\
    $D = \Sigma_s/(3 \Sigma_t^2)$ & 0.746360 & ~~68.5& -5150.1 \\
    Ronen corr. & 0.743860 & \textcolor{ceablue1}{-181.5} & \textcolor{ceablue1}{164.4}\\
    \hline \hline
  \end{tabular}
  \end{table}
  \end{columns}
  % \vspace{-5mm}

  \begin{figure}
    \centering
    \includegraphics[width=.75\textwidth]{../figures/kflxconv.pdf}
    \caption{Convergence trend.}
  \end{figure}

  \begin{figure}
    \centering
    \includegraphics[width=.8\textwidth]{../figures/eflxconv.pdf}
    \caption{Relative flux error in optical lengths from the boundary
             through iterations.}
  \end{figure}

  \begin{exampleblock}{Discussion}\tt
  \begin{itemize}
    \item The Ronen method drives the diffusion solution towards a transport-like solution even with unphysical b.c.
    \item The error concentrates at the boundary interface, and asks for many iterations
    \item $D=1/(3\Sigma_t)$ is the $P_1$ diffusion coefficient here
    \item Although $D=\Sigma_s/(3\Sigma_t^2)$ results in a smaller $\Delta k$, $\Delta \phi$ is 20\% off near the left boundary
  \end{itemize}
  \end{exampleblock}
  \vspace{10mm}

  \begin{alertblock}{Same issues and remarks for multi-dimensional $n$-D cases}\tt
  \begin{itemize}
    \item Can we prove convergence?
    \item Can we compute all components of the diffusion tensor in a coarse mesh?
    \item What are the special functions in $n$-D?
    \item Are there regions (like \emph{void} for instance) where the method cannot be applied?
  \end{itemize}
  \end{alertblock}
\end{frame}

\subsubsection{Curvilinear geometries}
\begin{frame}
  \frametitle{Derivation of the current in 1D curvilinear geometries}
  \vspace{-5mm}
  \begin{columns}
  \column{.5\textwidth}
  {
  Escape probability in \textcolor{ceablue1}{\bf 1D cylindrical geometry}:
  \[
    e_j(r) = \frac{2}{r V_j} \int_0^r { dh\, y \int_{L_j}{
    d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right]}},
  \]
  with $y(r, h) = \sqrt{r^2 - h^2}$ and $L_j(h) = [-Y,y] \cap V_j$
  ($Y = y(R, h)$).\\[10mm]
  Escape probability in \textcolor{ceablue1}{\bf 1D spherical geometry}:
  \[
    e_j(r) = \frac{2\pi}{r^2 V_j} \int_0^r { dh\, h y \int_{L_j}{
    d \ell \, \exp\left[-\tau( y, y - \ell )\right]}}.
  \]
  \begin{figure}
    \centering
    \input{../figures/sphere.tkz}
    \caption{Spherical symmetry.}
  \end{figure}
  }
  \column{.5\textwidth}
  \vspace{-10mm}
  \begin{figure}
  \centering
  \scalebox{1.5}{
    \input{../figures/cyltracks.tkz}
  }
  \caption{Tracking integration \cite{hebert2009applied}.}
  \end{figure}
\end{columns}
\end{frame}

%%% %% Introducing the name of ``CEA colors''
%\section{Présentation du style graphique}
%\subsection{Couleurs officielles du CEA}
%\begin{frame}
%  \frametitle{Présentation des couleurs CEA}

%  \begin{center}
%    {\large Implémentées suivant la charte : \textcolor{blue}{\url{http://www-dcom.intra.cea.fr/wp-content/uploads/Logo-regles-applications-charte_CEA-vdef.pdf}} }
%  \end{center}

%  \begin{table}
%    \LARGE
%    \begin{tabular}{l|cccc}
%      Base & & & & \\
%      \hline
%      Rouge & \textcolor{ceared1}{ceared1} & \textcolor{ceared2}{ceared2} & \textcolor{ceared3}{ceared3} & \\
%      Vert & \textcolor{ceagreen1}{ceagreen1} & \textcolor{ceagreen2}{ceagreen2} & \textcolor{ceagreen3}{ceagreen3} & \textcolor{ceagreen4}{ceagreen4} \\
%      Bleu & \textcolor{ceablue1}{ceablue1} & \textcolor{ceablue2}{ceablue2} & \textcolor{ceablue3}{ceablue3} & \\
%      Orange & \textcolor{ceaorange1}{ceaorange1} & \textcolor{ceaorange2}{ceaorange2} & & \\
%      Violet & \textcolor{ceapurple1}{ceapurple1} & \textcolor{ceapurple2}{ceapurple2} & & \\
%      Rose & \textcolor{ceapink1}{ceapink1} & \textcolor{ceapink2}{ceapink2} & & \\

%    \end{tabular}

%  \end{table}

%\end{frame}

%\subsection{Introduction aux raccourcis}
%%% %% Proposed shortcut to create slides
%\theframe{Ce titre de transparent est déjà trop long pour tenir sur une seule ligne}{

%  \begin{itemize}
%  \item Ce slide est fait avec un shortcut pour aller plus vite (voir ``shortcut'')
%  \end{itemize}

%}

%\begin{frame}[allowframebreaks]
%  \frametitle{Test de slide avec allowpagebreak}

%    \begin{block}{Contenu du premier transparent}{
%        \begin{itemize}
%        \item Des choses...
%        \item
%        \item
%        \item
%        \end{itemize}
%      }
%    \end{block}

%  \framebreak

%  \begin{block}{Contenu du second transparent}{
%      \begin{itemize}
%      \item ... et d'autres
%      \end{itemize}
%    }
%  \end{block}

%\end{frame}

%\intercalaire{Titre intercalaire}
%\intercalaireplus{Intercalaire avec du texte}{
%  {\Large Pour dire plus de chose}
%  {\normalsize
%    \begin{itemize}
%    \item Même si c'est pas forcément intéressant
%    \item Même avec des fautes d'orthographe
%    \end{itemize}
%  }
%}

\section{Conclusion}
\theframe{Conclusion}{
%
\begin{exampleblock}{Summary}
%\vspace{3mm}
\begin{itemize} \large
  %\setlength{\itemsep}{3mm}
  \item Diffusion theory is practical for (fast) core calculations
  \item Possible improvements by second-order transport approximations (SP$_N$, A$_N$, \ldots)
  % \item Presentation of transport effects in full core calculation and various diffusive-like transport approximations
  \item The use of \textcolor{ceablue1}{equivalence theory} compensates the lack of physical information in the diffusive model
  \item Introduction of the Ronen Method: principles \& implementation options
  \item Similarities with collision probability methods (see the escape probabilities), without solving CPM, i.e. no matrix inversion
  \item The Ronen Method could provide an \textcolor{ceared1}{online equivalence} between diffusion and integral transport on \textcolor{ceablue1}{coarse meshes}
\end{itemize}
\end{exampleblock}
%\vfill
\begin{alertblock}{Future development}
%\vspace{3mm}
\begin{enumerate}[(i)] \large
  %\setlength{\itemsep}{3mm}
  \item Convergence and stability analysis (using the CMFD scheme)
  \item Formal and numerical investigation of the Ronen Method as a mean for an online equivalence
  % \item Comparison with other deterministic techniques based on integral transport (mainly the collision probability method)
  \item 3D implementation of the Ronen method in nodal codes
  \item Extension to time-dependent problem
\end{enumerate}
\end{alertblock}
}

\section*{References}
\begin{frame}{\insertsectionhead}
%\nocite{*}
\begin{multicols}{2}
\small
\bibliographystyle{plainnat}
\bibliography{RonenMethod}
\end{multicols}
\end{frame}

%% %% Possibility to add a sentence as for intercalaire
\theclosingframe{
  Thanks for your attention!\\[2cm]
  \begin{flushright}\textcolor{white}{
    \visible<2>{
    \emph{Bòja brigant\\[5mm] Ciao Piero!}}
    % \hspace{3cm}
    }
  \end{flushright}
}

%% %% End of main part, beginning of backup (this is used to count the number of slides)
\backupbegin
%% %% New section for backup... the SectionCounter is used (along with totcount) to display at main toc all
%% %% sections but backups
%%\section{Backup}
\setcounter{SectionCounter}{\thesection}
\addtocounter{SectionCounter}{-1}
%% %% Back up menu accessible from any slide where the number of pages is displayed
%%\frame[label=MenuBackup]{\frametitle{Sommaire}
%%  \tableofcontents[sections=\thesection]
%%}

\section*{Other derivation of the diffusion coefficient}
\subsection*{The fundamental leakage model}
\include{backup_slides/BNlm}
\subsection*{Diffusive-like approximations from radiative transfer}
\include{backup_slides/otherdiffdefs}
\subsection*{Homogenization and Equivalence Theory}
\include{backup_slides/homogequiv}
\subsection*{Special functions}
\include{backup_slides/specfuncs}

%% %% End of backup mode....
\backupend

\end{document}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/BNlm.tex
Update ICTT src files and upload the slides shown at the conference

\begin{frame}
  \frametitle{The $B_N$ leakage model}
  \begin{alertblock}{Objective}
    Get a critical flux by adjusting the leakage in each group, and obtain a consistent definition of the diffusion coefficient \cite{benoist1964theorie, hebert2009applied}.
  \end{alertblock}
  %
  \begin{block}{Assumptions}
  {
  \begin{itemize} \normalsize
    \item Closed system by \emph{reflective} or \emph{periodic} bnd. conds. in a \textcolor{ceagreen1}{finite lattice of cells or assemblies}.
    \item Flux factorization with a \emph{macroscopic} quantity $\phi$ and a \emph{homogeneous} or \emph{periodic} \textcolor{ceablue1}{fundamental flux} $\psi$, \[\textcolor{ceared1}{\varphi(\mathbf{r}[, \ast]) = \phi(\mathbf{r})\, \psi(\mathbf{r}[, \ast])},\] where $\phi$ fulfills the Helmholtz eqn. $\nabla^2 \phi + B^2 \phi = 0$ with the (\underline{critical}) buckling $B^2 \in \mathbb{R}$. It follows that $\phi \propto \exp(i \mathbf{B} \cdot \mathbf{r})\; (B^2 = \mathbf{B} \cdot \mathbf{B})$.
    \item homogeneous or heterogeneous variants (acc. to the dependence of $\psi$ on $\mathbf{r}$)
  \end{itemize}
  }
  \end{block}
  %
  \begin{exampleblock}{Homogeneous $B_1$ Equations}
  {
  After a flux-volume homogenization of the NTE, substitute $\varphi = \psi(E, \bOm)\exp(i \mathbf{B} \cdot \mathbf{r})$ and integrate on angle to obtain the system of eqs. (with $\gamma$ as polynomial function of $(B/\Sigma_t)^2$):
  %\[ \left\{ \begin{split}
  \begin{align*}[left=\empheqlbrace]
    (\Sigma_t(E) + D(B, E)B^2) \psi(E) = \int_{0}^{\infty}{dE' \left(\Sigma_{s,0}(E' \rightarrow E) + \chi(E) \nu\Sigma_f(E') \right)\psi(E')}\\
    \textcolor{ceared1}{
    D(B, E) = \frac{1}{3\gamma(B, \Sigma_t)\Sigma_t}\left[ 1 + 3\int_{0}^{\infty} {dE' \Sigma_{s,1}(E' \rightarrow E) D(B, E') \frac{\psi(E')}{\psi(E)}} \right]}
  \end{align*}
  %\end{split} \right. \]
  }
  \end{exampleblock}
\end{frame}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/coredesignfeatures.tex
Update ICTT src files and upload the slides shown at the conference

\begin{frame}
  \frametitle{Regularity, Periodicity and Modularity}
  \begin{columns}
  \vspace{-5mm}
    \column{0.425\linewidth}
    \begin{block}{}{ \sl
    ``A rich range of reactor types has been developed in years to accomplish various operating objectives and to overcome technological limitations, thus using different coolants and nuclear fuels''.}
    \end{block}
    %\vspace{5mm}
    %
    \begin{exampleblock}{}
    \begin{flushright}
      \textsc{LWR (PWR \& BWR), HWR, Gas-cooled and Graphite-moderated, LMFBR / SFR}, (+ \emph{research reactors}).
    \end{flushright}
    \end{exampleblock}
    \vspace{5mm}
    %
    \fbox{\parbox{\textwidth}{ \centering
    Homogeneous~vs.~\emph{Heterogeneous systems}\\
    $\implies$ higher resonance escape probability.
    }}\vspace{5mm}
    %
    \begin{block}{\sl Features of the active core geometry}
      \textcolor{ceared1}{lattice} (\emph{regularity}) and \textcolor{ceared1}{assemblies} (\emph{modularity}), \emph{periodically} filling the multiplying system to achieve the target power.
    \end{block}
    %
    \column{0.575\linewidth} \centering
    {
    Hierarchical structure of a water reactor (PWR top, BWR bottom).}\\
    \includegraphics[width=0.8\textwidth]{figures/HierarcicalStructurePWR.png}\\[2mm]
    \includegraphics[width=0.8\textwidth]{figures/bwr_bundle.jpeg}
  \end{columns}
\end{frame}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/homogequiv.tex
Update ICTT src files and upload the slides shown at the conference

\begin{frame}
  \frametitle{Homogenization and Equivalence Theory}
  %
  \begin{block}{} \begin{flushright}
  \textcolor{ceared1}{\Large What for?} Prepare \emph{in advance} all reactor data for later core calculations in \textcolor{ceablue1}{low-order transport} (diffusion, $SP_N$ and others). \end{flushright}
  \end{block}\vspace{5mm}
  %
  \begin{alertblock}{Main rational of Homogenization}
    Conservation of reaction rates in the volume $\mathcal{V}$ of
    \emph{spatial homogenization} and
    in the $g$-th group of \emph{energy condensation} with
    $E \in [E_g, E_{g+1}]$, $g = 1, \ldots, G$.
  \end{alertblock}
  %
  \[
  \Sigma_g = \frac{\displaystyle
    \int_{\mathcal{V}} d\mathbf{r} \int_{E_{g+1}}^{E_g} dE \,
      \Sigma(\mathbf{r}, E) \, \phi(\mathbf{r}, E) }{\displaystyle
    \int_{\mathcal{V}} d\mathbf{r} \int_{E_{g+1}}^{E_g} dE \, \phi(\mathbf{r}, E)
    } \quad \text{with} \quad \chi_g = \int_{E_{g+1}}^{E_g} dE \, \chi(E).
  \]
  %
  \begin{columns}
    \column{.6\textwidth}
      \begin{block}{Equivalence}
      \textcolor{ceared1}{\Large Why?} $\ldots$Diffusion $\not\equiv$ transport, conservation of reaction rates does not imply to reproduce the \emph{same currents} at the boundaries of $\mathcal{V}$. Available techniques:
      \begin{itemize}
        \item (A)DF$ = \phi_{\text{het}}/\phi_{\text{hom}} $ (discontinuity factors), \emph{two per direction}
        \item SPH (SuPer-Homogenization) factors, \emph{one per group and homog. region}: $(\Sigma^{(k)}_g / s)(s\phi^{(k)}_g)$
      \end{itemize}
    \end{block}
    %
    \column{.4\textwidth} \centering
    \def\wdt{2.5}
    \def\ymin{0.25}
    \begin{tikzpicture}
      \draw[->, thin, help lines] ({-\wdt-0.5},{\ymin+0.1})
        -- ({\wdt+1},{\ymin+0.1}) node[right] {$\hat{e}_k$};
      \draw[-] (-\wdt,\ymin) node[below] {$k-1/2$} -- (-\wdt,3);
      \draw[-] ({\wdt-1/4},\ymin) node[below] {$k+1/2$} -- ({\wdt-1/4},3);
      \draw[->] ({-\wdt-0.5}, 2.4) -- ({-\wdt-0.1}, 2.4)
        node[midway,above] {$J^+_{\text{in}}$};
      \draw[black, domain={-\wdt}:{\wdt-1/4}]
        plot[samples=100]
        ({\x}, {2+0.2*sin(((\x+2)*4)*3.141592 r)-0.2*\x})
        node[right] {$\phi_{\text{het}}$};
      \draw[red, domain={-\wdt}:{\wdt-1/4}, thick]
        plot[samples=100] ({\x}, {0.5+exp(-0.35*\x)})
        node[right] {$\phi_{\text{hom}}$};
      \node[red,below] (D) at (\ymin,1.35) {$D^{(k)}$};
      \node (title) at (0,3) {$k$'th cell};
    \end{tikzpicture}
  \end{columns}
\end{frame}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/loworder_trapprox.tex
Update ICTT src files and upload the slides shown at the conference

\begin{frame}
  \frametitle{Approaches to improve diffusion}

  \begin{block}{\bf Second-order transport approximations}
    {\vspace{3mm}
    \begin{itemize} \Large
      \setlength{\itemsep}{5mm}
      \item Different ``diffusive-like'' approximations of transport exist
      \item They can be implemented in existing diffusion-codes
    \end{itemize}
    }
  \end{block}
  \vfill
  \begin{exampleblock}{\bf \ldots{a} few examples:}
  {\vspace{3mm}
  \begin{itemize} \large
    \setlength{\itemsep}{5mm}
    \item \textcolor{ceablue1}{Diffusion tensors} to treat material heterogeneities with a \emph{drift component} \cite{boffi1972tensorial}
    \item Simplified $P_N$ or \textcolor{ceablue1}{$SP_N$} \cite{gelbard1960application, brantley2000simplified}, the \textcolor{ceablue1}{$A_N$} formulation \cite{PieroSNandAN, coppa2016an}
    \item \textcolor{ceablue1}{Quasi-diffusion} with the Eddington factor \cite{pounders2009diffusion}
    \item more accurate evaluation of the current in the actual system, i.e. the \textcolor{ceablue1}{Ronen Method} \cite{ronen2004accurate}
  \end{itemize}
  }
  \end{exampleblock}
\end{frame}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/otherdiffdefs.tex
Update ICTT src files and upload the slides shown at the conference

\begin{frame}
  \frametitle{Other diffusive-like approximations from radiative transfer problems}
  \begin{block}{Flux-limited diffusion}
  {
  The angular flux is factored in a term slowly varying in space and a normalized angular component \cite{levermore1981flux}:
  \[
  \varphi \approx \phi(\mathbf{r}, E) \psi(\mathbf{r}, \bOm) \quad \text{with} \quad \int_{4\pi} {d \bOm \psi} = 1,
  \quad \implies \mathbf{J}_g = \mathbf{f}(\mathbf{r})\,\phi_g \; \wedge \;
  \frac{\lVert \mathbf{J}_g \rVert}{\phi_g} = \text{const},\; \forall g.
  \]
  The diffusion coefficient (``the flux-limiting parameter'') come from the solution of a \emph{transcendental equation}. In the limit of weak gradients, the diffusion coefficient is obtained as (for all groups):
  \[ \textcolor{ceared1}{
  D_g(\mathbf{r}) = \frac{1}{3} \left[ \Sigma_{t,g} - \sum_{g'}{\Sigma_{s,1,g' \rightarrow g} \,\frac{\phi_{g'}}{\phi_g}} \right]^{-1}}
  \]
  }
  \end{block}
  %
  \begin{block}{Variable Eddington factor}
  {
  Postulate a factorization of the second moment by another factor (or \emph{tensor}) slowly varying in space \cite{pomraning1982flux}:
  \[
  \varphi \approx E(\mathbf{r}[, \ast]) \phi(\mathbf{r}[, \ast]),
  \text{ and }
  \partial_{\mathbf{r}} E \approx 0 \hfill \implies
  \textcolor{ceared1}{
  D_{i,g}(\mathbf{r}) = E_g(\mathbf{r}) \left[ \Sigma_{t,g} - \sum_{g'}{\Sigma_{s,1,g' \rightarrow g} \,\frac{J_{i,g'}}{J_{i,g}}} \right]^{-1}, i \in (\hat{e}_x, \hat{e}_y, \hat{e}_z).}
  \]
  }
  \end{block}
\end{frame}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/slabex_Tomatis2011.tex
Update ICTT src files and upload the slides shown at the conference

--- 2019-10-02 docs/ICTT2019/slides/RM1Dgeoms_ictt26.tex
@@
-\documentclass[black]{slideCEA}
-
-\usetikzlibrary{decorations.text}
-\usepackage{multicol}
-%\usepackage{etoolbox}
-\usepackage{mathrsfs}
-%\usepackage{mathtools}
-\usepackage[overload]{empheq}
-
-\newcommand{\bOm}{\boldsymbol{\Omega}}
-\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
-\DeclareMathOperator{\sign}{sign}
-
-%% %% Possible specific options:
-%% %%   ** notofficial: change few aspect of the style: Front page, font black (not grey),
-%% %%        !!! Compulsory to use the following two options
-%% %%   ** topbar to get the path as ``section : subsection'' on top
-%% %%   ** bottombar to get
-%% %%          ==> left: date (with hidden link to toc if it exists, and its name is Menu, as here)
-%% %%          ==> middle: subtitle (meeting name) - author
-%% %%          ==> right: currentslidenb/totalslidenb (with hidden link to backup toc if it exists and is called MenuBackup, as here)
-%% %%   Same links are hidden in official bottombar to avoid unpleasant scrolling
-%% %%   CEA in official bottom bar can be changed to display institute like CEA/DIR/DEP/SER/LAB... with \BottomBarInstitute
-
-%% %% Title of the slides and meeting
-\YTitleFP{30}
-\title{On the Ronen Method
-       in simple 1D geometries}% \textcolor{white}{l}}
-\FrontPageSubTitleY{55}
-\subtitle{\textit{\normalsize Derivation of accurate expressions for the current in the slab and in the curvilinear reference frames}}
-\date{September 27\textsuperscript{th}, 2019}
-\Event{{\footnotesize 26\textsuperscript{th} International Conference on
-       Transport Theory (ICTT26), Paris, France}}
-\YEventFP{155}
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% %%%%%%%%%%%%%% Personnal informations (most of which can %%%%%%%%%%%%%%%%%
-%% %%%%%%%%% be put by default in the class file once and for all) %%%%%%%%%%
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% %% Personnal information about the author
-\YAuthFP{100}
-%\author{Daniele Tomatis}
-\author{Daniele Tomatis\\
-        {\small \textcolor{ceared3}{CEA SERMA, France}
-         \textcolor{blue}{(daniele.tomatis@cea.fr)}}}
-%\MailAddress{daniele.tomatis@cea.fr}
-%\Telephone{+33 (0)1 69 08 25 26}
-%\Fax{(0)1 YY YY YY YY}
-%% %% Possible option to add information on the author line (only for non-official for the moment)
-\OtherAuthor{\\[6mm]Roy Gross and Erez Gilad\\[2pt]
-             \includegraphics[width=50mm]{logos/BGU_transp.png}
-             % {\footnotesize University of Ben Gurion, Israel}
-             }
-
-%% %% Information about CEA: your service/departement/direction/centre
-\Direction{Direction de l'{\'E}nergie Nucl{\'e}aire}
-\Departement{D{\'e}partement de Mod{\'e}lisation des Syst{\`e}mes et Structures}
-\Service{Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA)}
-\Centre{Centre de Saclay}
-\CentreAddress{91191 Gif-sur-Yvette Cedex, France}
-\BottomBarInstitute{CEA/DEN/DANS/DM2S/SERMA/LPEC}
-
-\CeaLogo{cea-tr.png}
-%% %% On can change the logo with \CeaLogo{cea-saclay-tr.png} %% \CeaLogo{cea-den-tr.png}
-%% %% One can add a picture in the Title bar of every slide. To do so, define
-%% %% *** The path to the picture: \TitleBarPicture{Nobel-Prize-small.png}
-%% %% *** The size of the picture (in mm): \TitleBarPictureSize{20} [20 is the default]
-%% %% *** The X of the picture (in mm): \TitleBarPictureX{230} [230 is the default]
-%% %% *** The Y of the picture (in mm): \TitleBarPictureY{0} [0 is the default]
-%\TitleBarPicture{Nobel-Prize-small.png}
-\TitleBarPicture{logos/BGU_transp_bk.png}
-\TitleBarPictureSize{50}
-\TitleBarPictureX{198}
-\TitleBarPictureY{2}
-\FrameTitleS{48}  % force line break in frametitle after 55 characters
-
-\FrontPagePicture{logos/logo_ICTT26_white.png}
-\FrontPagePictureX{10}
-\FrontPagePictureY{90}
-\FrontPagePictureSize{70}
-%% %%%%%%%%%%%%%%%%%%%% Enf of personnal informations %%%%%%%%%%%%%%%%%%%%%%%
-
-\graphicspath{{logos/}{../../../bgu_seminar/figures/}}
-
-%% %% Starting the slide
-\begin{document}
-
-%% %% Front page (opening one)
-\theframetitle
-
-%% %% One can add a picture in the Front page. To do so, define
-%% %% *** The path to the picture: \FrontPagePicture{Nobel-Prize-small.png}
-%% %% *** The size of the picture (in mm): \FrontPagePictureSize{70} [70 is the default]
-%% %% *** The X of the picture (in mm): \FrontPagePictureX{140} [140 is the default]
-%% %% *** The Y of the picture (in mm): \FrontPagePictureY{70} [70 is the default]
-%\FrontPagePicture{Nobel-Prize-small.png}
-%\theframetitle
-
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% %% If none of the possible front page fit you, you can create your own doing
-%% %% %%%%%%%%%%%% Or directly modify theframetitle in the class %%%%%%%%%%%%%%%
-%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% \begin{frame}[plain] %% begin frame
-%%   \FrontPageRedStructure   %% add left bar with CEA logo and cea web address
-%%   \begin{changemargin}{90 mm}{0cm} %% restraining the area to white space
-%%     \begin{center}
-%%       {\LARGE   \textcolor{ceared1}{Nouveau titre de présentation} }
-%%     \end{center}
-%%   \end{changemargin}
-%% \end{frame}
-
-%% the ``sections={1-\totvalue{SectionCounter}},'' comes along with usepackage{totcount}
-%% It is used to get the section number of backup (if so) and not display it in this toc.
-%% There is a specific toc for backup in \backupbegin
-%% If one cannot install totcount, remove \tableofcontents[sections={1-\totvalue{SectionCounter}},
-
-\setcounter{tocdepth}{2}
-\setbeamertemplate{section in toc}[ball unnumbered]
-\begin{frame}
-  \frametitle{Outline}
-%\begin{multicols}{2}
-%\parbox[t]{.8\textwidth}{
-\tableofcontents
-%}
-%\end{multicols}
-\end{frame}
-
-%\frame<4>[label=Menu]{
-%  \frametitle{Sommaire}
-%  \only<1>{\tableofcontents[sections={1-\totvalue{SectionCounter}},hideallsubsections]}
-%  \only<2>{\tableofcontents[sections={1-\totvalue{SectionCounter}},currentsection,hideothersubsections]}
-%  \only<3>{\tableofcontents[sections={1-\totvalue{SectionCounter}},currentsection,hideothersubsections,currentsubsection]}
-%  \only<4>{\tableofcontents[sections={1-\totvalue{SectionCounter}},subsectionstyle=show]}
-%}
-
-\section{Introduction}
-
-\begin{frame}
-  \frametitle{Introduction and Motivation}
-  \begin{itemize} \large
-    \setlength{\itemsep}{5mm}
-    \item The use of \textcolor{ceared1}{diffusion theory} is very practical in ordinary \textcolor{ceared1}{full core calculations} in terms of \emph{computational time} and \emph{numerical schemes}\\
-    {\hfill \normalsize \color{ceagreen3}
-    $\rightarrow$ fast calculations, parabolic/elliptic equations, diagonal dominance
-    }
-    % \pause
-    \item Cross section preparation by \textcolor{ceared1}{homogenization} and \textcolor{ceared1}{equivalence} theory form a consistent frame-work with \textcolor{ceablue1}{nodal expansion} or \textcolor{ceablue1}{finite-element} solving methods\\
-    {\hfill \normalsize \color{ceagreen3}
-    $\rightarrow$ current standard approach in nuclear industry
-    }
-    % \pause
-    \item Diffusion \textcolor{ceared1}{cannot} reproduce strong transport effects with sufficient accuracy\\%:
-
-%   \begin{itemize} \large
-%     \setlength{\itemsep}{3mm}
-%     \item presence of void
-%     \item regions of high absorption
-%     \item materially heterogeneous systems
-%     \item substantial scattering anisotropy
-%   \end{itemize}
-
-    {\hfill \normalsize \color{ceagreen3}
-    $\rightarrow$ fails with strong absorption and flux gradients, rather miss anisotropy
-    }
-    \item {What's the \emph{best definition} of the diffusion coefficient? Is there any?}\\
-    % \pause
-    \item Influence of the {\color{ceared1}geometry frame} on the \emph{flux convergence} by Ronen iterations
-  \end{itemize}
-\end{frame}
-
-%\include{backup_slides/loworder_trapprox}
-% ===================================
-
-\section{Core Calculations}
-
-% \subsection{Common features of core design}
-% \include{slides/coredesignfeatures}
-
-\subsection{Two-step calculation scheme}
-\begin{frame}
-  \frametitle{Two-step core calculations}
+\begin{frame}[allowframebreaks]
+  \frametitle{An example in the bare slab}
+  {\hfill \cite{tomatis2011application}}%\\[3mm]
 
   \begin{columns}
-  \vspace{-5mm}
-    \column{0.65\linewidth} \centering
-    {\includegraphics[width=\textwidth]{FA_homog.png}}
-    \column{0.35\linewidth} \centering
-    {\includegraphics[width=0.9\textwidth]{core_quarter.png}}
-  \end{columns}
-
-  \begin{tikzpicture}[overlay, remember picture]
-  \draw[->, thick, draw=ceagreen2, line width=5mm]
-    ([yshift=3cm, xshift=-2cm]current page.south)
-    -- ([yshift=3cm, xshift=-8.5cm]current page.south east)
-    node[midway, above] {\color{ceagreen3}\large \tt \bf
-    \begin{tabular}{c}
-    multi-group \\ xs library
-    \end{tabular}
-    };
-%    [xshift=-2cm, yshift=2cm]
-  \end{tikzpicture}
-\end{frame}
-
-%%% this does not work %%%
-%\begin{frame}
-%  \frametitle{3D Coarse Mesh Kinetics}
-%  \label{sec:fm3D}
-%  \input{coarse_mesh3D}
-%\end{frame}
-
-\subsection{Transport effects in core calculations}
-\begin{frame}
-  \frametitle{\insertsubsectionhead}
-  \begin{block}{General issues for safety and design calculations}% or warnings?
-  { \vspace{3mm}
-  %
-  \begin{itemize} \large
-    \setlength{\itemsep}{3mm}
-    \item \textcolor{ceablue1}{High absorption} and \textcolor{ceablue1}{low scattering}: presence of black materials to neutrons (mechanical and chemical shim), weak moderation, spectrum hardening
-    %\item \textcolor{ceablue1}{high absorption}, like with the elements close to the thermal energy range causing neutron spectrum hardening (mechanical shim by black control rods, fuel blended with burnable poisons)
-    \item \textcolor{ceablue1}{scattering anisotropy}: e.g. forward-peaked moderation in water
-    \item potential \textcolor{ceablue1}{occurrence of void} under operation or in accidental transients (LWR/FR)
-    \item angle-dependent boundary conditions: free-surfaces-vacuum, anisotropic albedos
-    \item \textcolor{ceablue1}{steep flux gradients}: proximity to the reflector in thermal reactor, strong localized absorption
-    %\item boundary with selective and anisotropic reflection (e.g. heavy reflector to extend the vessel lifetime or the respose of water reflector in fast groups)
-    \item \textcolor{ceablue1}{material heterogeneity}: heterogeneous core loading with material discontinuities at the interfaces between fuel elements (MOX/UO2 mixed cores, with both radial and axial discontinuities)
-    \item \emph{memory-effects} due to temporary and localized short reactivity insertion (incore instrumentation, rapid geometry and material changes, presence of noise)
-  \end{itemize}
-  }
-  \end{block}
-\end{frame}
-% ===================================
-
-\section{Diffusion Theory}
-
-\subsection{Conservation equation and Fick's law}
-\begin{frame}
-  \frametitle{Continuity equation with approximated transport law}
-  %
-  \vspace{-5mm}
-  \begin{block}{Integro-differential Neutron Transport Equation (NTE)}
-  {\hfill \normalsize \cite{duderstadt1979transport}}
-  {
-  \begin{gather*}
-  \left[ \frac{1}{v}\frac{\partial}{\partial t}
-  %+ \nabla \cdot (\bOm \,\_) + \Sigma_t(\mathbf{r}, E) \right] \varphi(\mathbf{r}, E, \bOm)
-  + \bOm \cdot \nabla + \Sigma_t(\mathbf{r}, E) \right] \varphi(\mathbf{r}, E, \bOm, t)
-  = \frac{\chi(E)}{4\pi} \int_0^{\infty} {dE' \nu\Sigma_f(\mathbf{r}, E') \phi(\mathbf{r}, E', t)}
-  + s_{\text{ext}}(\mathbf{r}, E, \bOm, t) +\\
-  \int_{4\pi} d\bOm'
-  \int_0^{\infty} {dE' \Sigma_s(\mathbf{r}, E' \rightarrow E, \bOm' \rightarrow \bOm)
-  \varphi(\mathbf{r}, E', \bOm', t)
-  } = q(\mathbf{r}, E, \bOm, t).
-  \end{gather*}
-  }
-  \end{block}
-  Let us introduce the scalar flux and the current, respectively:
+  \column{.5\textwidth}
+  \begin{block}{}
+  In 1-D, we find the \textcolor{ceablue1}{exponential integral functions $E_n$} and the diffusion tensor simplifies in a single coefficient.
   \[
-    \phi = \int_{4\pi}{d \boldsymbol{\Omega}
-    \varphi(\mathbf{r}, \boldsymbol{\Omega}[, \ast] )}
-    \quad \text{and} \quad
-    \mathbf{J} = \int_{4\pi}{d \boldsymbol{\Omega} \boldsymbol{\Omega}
-    \varphi(\mathbf{r}, \boldsymbol{\Omega}[, \ast] )},
+    \begin{split}
+    E_n(\mathcal{L}_{op}) = \int_1^{\infty}{du\, \frac{e^{-|\mathcal{L}_{op}|\,u}}{u^n}}\\
+      = \int_0^1 {d\mu \, \mu^{n-2} e^{-|\mathcal{L}_{op}| / \mu}}.
+    \end{split}
   \]
-  and integrate the NTE to get the continuity equation:
-  \[
-    \frac{1}{v}\frac{\partial \phi}{\partial t} + \nabla \cdot \mathbf{J}
-    + \Sigma_t \phi = \int_{4\pi}{d \bOm \, q(\mathbf{r}, \boldsymbol{\Omega}[, \ast] )}.
-  \]
-  Use \textcolor{ceared1}{Fick's law} as closure
-  \textcolor{ceared1}{$\mathbf{J} = - \mathcal{D}\nabla \phi$}, with the
-  vacuum bnd. conds. $- \partial_{\hat{n}} \phi = \phi/
-  \zeta$ and the extrapolated length $\zeta = 2\mathcal{D}$ ($\approx 2.13
-  \mathcal{D}$ in computer codes).
-  \begin{alertblock}{}
-    \textit{N.B. A unique family of fissiles is represented here;
-    precursors of delayed neutrons are also necessary for kinetics
-    with fission; $\Sigma_t(\bOm[, \ast])$ if no rotational symmetry
-    in scattering events.}
-  \end{alertblock}
-\end{frame}
-
-% WARNING: it is important to remind that the source term in the trasnport
-% equation is given as sum of moments on spherical harmonics!
-% \include{backup_slides/sourcebymoments}
-
-\subsection{About the diffusion coefficient}
-%
-\begin{frame}%[t] \vspace{5mm}
-  \frametitle{The $P_1$ branding of the diffusion coefficient}
-  \begin{alertblock}{} \large
-  $P_N$: flux expansion on sph. harmonics and projections over $4\pi$ of the NTE on $1$, $\bOm$, $\ldots$
-  \end{alertblock}
-  \begin{block}{If we limit the expansion to the first moment:}
-  {
-  %\[ \left\{
-  \begin{align}[left=\empheqlbrace]
-  \frac{1}{v} \frac{\partial \phi}{\partial t} + \nabla \cdot \mathbf{J} + \Sigma_t\, \phi &=
-  \int_0^{\infty} {dE' \Sigma_{s,\ell=0}(E' \rightarrow E)\,\phi(\mathbf{r}, E', t) \ }
-  + S_{\text{ext},\ell = 0},\label{eq:sflx}\\[3mm]
-  \frac{1}{v} \frac{\partial \mathbf{J}}{\partial t} + \nabla \cdot \boldsymbol{\Pi} + \Sigma_t\, \mathbf{J} &= \int_0^{\infty} {dE' \Sigma_{s,\ell=1}(E' \rightarrow E)\, \mathbf{J}(\mathbf{r}, E', t)} + \mathbf{S}_{\text{ext},\ell = 1},\label{eq:curr}
-  \end{align}
-  %\right. \]
-  }\vspace{5mm}
-  with $\boldsymbol{\Pi} = \int_{4\pi}{d \bOm (\bOm \bOm)\varphi(\mathbf{r}, \bOm}[, \ast])$,
-  or \textcolor{ceablue1}{$\boldsymbol{\Pi} = \phi / 3$} if
-  \textcolor{ceablue1}{$\varphi = \left( \phi + 3 \mathbf{J} \cdot \bOm \right)/4\pi$},
-  i.e. the \textcolor{ceared1}{$P_1$ approximation}.\vspace{5mm}
-
-  \pause{
-  Use then the \textcolor{ceablue1}{multi-group energy formalism} in Eq. \ref{eq:curr}, assume \textcolor{ceablue1}{stationarity} and an \textcolor{ceablue1}{isotropic external source} to write:
-  \[
-  \frac{1}{3}\nabla \phi_g + \Sigma_{t,g} \,\mathbf{J}_g = \sum_{g'=1}^G {\Sigma_{s,1,g' \rightarrow g}\, \mathbf{J}_{g'}}
-  \]
-  }\vspace{5mm}
-
-  \pause{
-  In presence of dominant scattering and at \emph{thermal equilibrium} \textcolor{ceagreen3}{$\sum_{g'} {\Sigma_{s,1,g' \rightarrow g} \mathbf{J}_{g'}} \approx \mathbf{J}_{g} \sum_{g'} {\Sigma_{s,1,g \rightarrow g'}}$}, thus yielding a specific diffusion coefficient:
-  \[
-  \mathbf{J}_g = -D_g \nabla \phi_g \implies
-    \textcolor{ceared1}{D_g(\mathbf{r}) = \frac{1}{3\Sigma_{tr,g}}}
-    \quad \text{with} \quad \Sigma_{tr,g} = \Sigma_{t,g} - \Sigma_{s,1,g}, \; \forall g.
-  \]
-  }
-  \end{block}
-\end{frame}
-
-% \include{backup_slides/otherdiffdefs}
-
-% \subsection{The fundamental leakage model}
-% \include{backup_slides/BNlm}
-
-\subsection{Diffusion tensors}
-\begin{frame}
-  \frametitle{Drift, diffusion tensors, and more$\ldots$}
-  %
-  \begin{block}{Integral Neutron Transport Equation}
-   \begin{gather*}
-   \varphi({\mathbf{r}, E, \bOm}) =
-     \int_0^{\mathpzc{S}(\mathbf{r},\bOm)}{ds\,
-     q(\mathbf{r} - s\, \bOm, E, \bOm) \exp{ \left[
-     - \mathscr{L}_{op}(\mathbf{r}, s, E, \bOm) \right]}
-   }\text{ with } \mathscr{L}_{op} = \int_0^{s}{ds'\, \Sigma_t(\mathbf{r} - s'\, \bOm, E)},\\
-     q(\mathbf{r}', E, \bOm) = \sum_{\ell m} {Y_{\ell m}(\bOm)
-       \int_0^{\infty}{dE' \left( \Sigma_{s,\ell}(\mathbf{r}', E' \rightarrow E)
-       + \chi(E) \nu\Sigma_f(\mathbf{r}', E')\delta_{\ell 0}\delta_{m 0} \right)
-       \phi_\ell^m(\mathbf{r}', E')}} + \text{b.c.}
-   \end{gather*}
-
-  \end{block}
-  %
-  \begin{columns}
-  \column{.325\textwidth}
-  \def\dx{0.25}
-  \begin{tikzpicture}[declare function={f(\x) = (\x - 1)/3+2;}]
-   \draw[->, very thick] (1,0) -- (4,{f(4)}) node[below right] {
-     \begin{tabular}{c}
-       $\mathbf{r}' = \mathbf{r}-s\, \bOm$,\\
-       $s = \lVert \mathbf{r}' - \mathbf{r} \rVert$
-     \end{tabular}
-   };
-   \draw[->, very thick] (0,0) -- (1,{f(1)}) node[below right] {$\mathbf{r}$};
-   \draw[->, thick] ({4-\dx},{f(4)+\dx}) -- ({3-\dx},{f(3)+\dx}) node[above left] {$s, \bOm$};
-   \draw[->,dashed] (0,{f(0)}) -- (1,{f(1)}) -- (4,{f(4)}) -- (5.5,{f(5.5)})
-     node[above right] {$\mathpzc{S}$};
-   \draw[ultra thick] plot[smooth] coordinates {(3,4) (5.5,{f(5.5)}) (6,3)};
-  \end{tikzpicture}
-  %
-  \column{.675\textwidth}
-  \begin{block}{}
-  {Assume \textcolor{ceared1}{isotropic} sources (with pure scattering and one group for simplicity), expand the flux by Taylor around $\mathbf{r}$ and integrate to obtain the current:
-  \begin{flalign*}
-  \begin{split}
-  %\mathbf{J}(\mathbf{r}) = \frac{1}{4\pi}
-  %  \int{ d \bOm \int_0^{\mathpzc{S}}{
-  %    ds\,\bOm\, \Sigma_{s,0}(\ast) \exp\left[ \mathscr{L}_{op} \right] \cdot\\
-  %    \left( \phi(\mathbf{r}) - \bOm \cdot \nabla \phi \,s
-  %           + \bOm \mathbf{H} \bOm\, s^2 + O(s^3)\right)
-  %    }}
-  \mathbf{J}(\mathbf{r}) = \int d\mathbf{r}'
-    \frac{\mathbf{r}' - \mathbf{r}}
-         {4\pi \lVert \mathbf{r}' - \mathbf{r} \rVert^3}
-      \Sigma_{s,0}(\ast) e^{ -\mathscr{L}_{op} } \cdot \\
-      \left( \phi(\mathbf{r}) - s \, \bOm \cdot \nabla \phi
-             + s^2 \, \bOm \mathbf{H} \bOm + O(s^3)\right)\\[3mm]
-    \Rightarrow \textcolor{ceared1}{
-    \mathbf{J}(\mathbf{r}, E) =
-      \underbrace{\vec{\mathpzc{d}}(\mathbf{r}, E) \phi(\mathbf{r}, E)}_\text{
-      advection~/~drift}
-      - \underbrace{\mathbf{D}(\mathbf{r}, E) \nabla \phi(\mathbf{r}, E)}_\text{
-      term w. diffusion tensor}
-      + \ldots
-    }
-  \end{split}
-  \end{flalign*}
-  }
-  \end{block}
-  \end{columns}
-  %
-  \begin{columns}
-  \column{.6\textwidth}
-  \begin{exampleblock}{Under the following conditions:}
-  \begin{enumerate}[i.]
-    \item smooth flux gradient and small higher derivatives
-    \item weakly absorbing and highly scattering media
-    \item \textcolor{ceablue1}{constant cross sections in space}
-  \end{enumerate}
-  \end{exampleblock}
-  %
-  \column{.4\textwidth}
-  \[ \Rightarrow \textcolor{ceared1}{
-    \mathbf{J} = -D \nabla \phi \quad \text{with}
-    \quad D = \frac{\Sigma_s}{3 \Sigma_t^2}
-  }\]
-  \end{columns}
-\end{frame}
-% ===================================
-
-% \section{Cross section preparation}
-% \subsection{Homogenization and Equivalence Theory}
-% \include{backup_slides/homogequiv}
-% ===================================
-
-\section{The Ronen Method}
-
-\subsection{Principles \& Implementation}
-%
-\begin{frame}
-  \frametitle{\insertsectionhead}
-  \begin{block}{Principles \& Implementation}
-  {\hfill \cite{ronen2004accurate, tomatis2011application}}
-  {
-  \begin{itemize} \large
-    \setlength{\itemsep}{3mm}
-    \item The \textcolor{ceared1}{best diffusion coefficient} would be the one satisfying exactly Fick's law with the same flux and current computed by transport (with the current containing all contributions from higher order moments!)
-    \item<2-> Use a higher-order \textcolor{ceablue1}{integral} transport operator to obtain \textcolor{ceared1}{more accurate estimates of the current} \emph{by sources determined with the diffusion flux}
-    % \item<2-> An ``\textcolor{ceared1}{equivalent}'' (\textcolor{ceablue1}{integral}) transport problem is defined to determine the diffusion coefficient:
-    % \[
-    %  D_i = - \frac{\mathbf{J} \cdot \hat{e}_i}
-    %    {\nabla \phi \cdot \hat{e}_i},
-    %  \text{ where \textcolor{ceared1}{$\mathbf{J}$ is estimated by a higher order transport operator!}}
-    % \]
-    \item<3-> Solve diffusion \emph{again} with the new coefficients $D_i = - \left[\mathbf{J}(\phi) \cdot \hat{e}_i\right] \big/ \left[ \nabla \phi \cdot \hat{e}_i\right]$
-    \item<4-> Such agreement is sought numerically by \textcolor{ceablue1}{non-linear iterations}
-    \item<5-> \textcolor{ceared1}{Alternative implementation} by a CMFD-like scheme \cite{smith1983nodal}, with currents at cell interfaces as:
-    \[
-    J^{(k,+)} \approx
-    \underbrace{
-    - 2D_\text{DIFF} \frac{\phi^{(k+1,+)} - \phi^{(k,+)}}{\Delta_{k+1} + \Delta_{k}}
-    }_\text{Diffusive current}
-    -2 \underbrace{
-    (\textcolor{ceared1}{\delta D})
-      \frac{\phi^{(k+1,+)} \textcolor{ceared1}{+} \phi^{(k,+)}}{\Delta_{k+1} + \Delta_{k}}
-    }_\text{Transport correction},
-    \]
-    where $\textcolor{ceared1}{\delta D} \propto (J_{\text{TRANSP}} - J_\text{DIFF})$.
-  \end{itemize}
-  }
-  \end{block}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Boundary conditions (bc.)}
-
-  \begin{alertblock}{A known issue\ldots}
-    bc. apply on the angular flux in transport and we solve only for the scalar flux in diffusion.
-  \end{alertblock}
-  { Generalized form for finite difference equations:
-  \[
-    J = - \frac{D \phi_{bc}}{\Delta_{bc} / 2 + \zeta} \text{ with }
-    \begin{cases}
-      \zeta \propto \lambda_t & \text{extrapolated length for vacuum}, \\
-      \zeta = 0 & \text{zero flux}, \\
-      \zeta \rightarrow 0^+ & \text{reflection by vanishing current};
-    \end{cases} \qquad \delta J_{bc} = \delta D \phi_{bc}.
-  \]
-  }\vspace{-10mm}
-
-  \visible<2->{
-    \flushright \textcolor{ceared1}{\large bc. are given for incoming
-    particles\\and we use a transport operator to estimate the current!}\\[3mm]
-  }
-
-  \begin{block}{The problem of reflection and periodic translation}
-    We expand the angular flux on spherical harmonics to get expressions based
-    on moments. Now consider a bare homogeneous slab
-    ($\varphi \approx \phi/2 + 3/2 J \mu$) with specular reflection at one side.
-    \alert<3>{$J^+ + J^- \neq 0$} at the refl. boundary for $\varphi \approx \phi/2$.
-    {
-      $\longrightarrow$ Fix $J=0$ by corrections from higher moments as:
-      \begin{equation*}
-      \begin{split}
-      J^+(x) &= \frac{\phi_0(a)}{2}E_3(\tau(a, x)) + \frac{5}{4} \tilde{\phi}_2(a) \left[ 3 E_5(\tau(a, x)) - E_3(\tau(a, x)) \right],\\
-             \text{with }& \tilde{\phi}_2(a) = - \frac{16}{5} \left( \frac{1}{4} \phi_0(a) + J^- \right) \text{ and }
-      \phi(a, \mu) = \frac{1}{2} \phi_0 + \frac{3}{2} \mu \phi_1 + \frac{5}{4} \left( 3 \mu^2 - 1 \right) \tilde{\phi}_2.
-      \end{split}
-      \end{equation*}
-    }
-  \end{block}
-\end{frame}
-
-\subsection{Expressions for the current in simple 1D geometries}
-
-\begin{frame}
-  \frametitle{Expressions for the current in simple 1D geometries}
-
-  \vspace{-5mm}
-  {Derivation of the equation for the current in mono-dimensional problems
-  (\emph{bare bodies}) by \textcolor{ceared1}{escape probabilities}.
-  The current of particles crossing the surface $S$ at $r$ is
-  \[
-    J(r) S(r) = \sum_j q_j V_j e_{j}(r), \text{ where}
-  \] \vspace{-5mm}
-  \begin{itemize}
-    \item $q_j$ is the (isotropic) source in the region $j$ of volume $V_j$ and\\
-    \item $e_j(r)$ is the probability for a particle isotropically emitted
-          in region $j$ to cross S(r) uncollided.
-  \end{itemize}
-  }
-  \begin{figure}[t]
-    \centering
-    \scalebox{1.5}{
-      \input{../figures/mesh1d.tkz}
-    }
-    \caption{Mesh notation for the 1d problems.}
-  \end{figure}
-  {
-  In \textcolor{ceablue1}{\bf 1D slab}, integration on the polar angle is resolved \emph{analytically} by \textcolor{ceablue1}{exponential integral functions $E_n$}:
-  % \[
-  %   E_n(\tau) = \int_1^{\infty}{du\, \frac{e^{-|tau|\,u}}{u^n}}
-  %     = \int_0^1 {d\mu \, \mu^{n-2} e^{-|\tau| / \mu}}.
-  % \]
-
-  \begin{equation*}
-  \begin{split}
-  J_{i+1/2} =& \int_0^1   {d\mu\, \mu \varphi(a, \mu) e^{-\tau(a, x_{i+1/2})/\mu}}
-             - \int_0^{-1}{d\mu\, \mu \varphi(b, \mu) e^{-\tau(b, x_{i+1/2})/\mu}}\\
-          +& \sum_{j=0}^{I-1} { \sign(x_{i+1/2} - x_{j+1/2}) \frac{q_{0,j}}{2} \int_{x_{j-1/2}}^{x_{j+1/2}}{dx'
-          E_{2} \left(\lvert \tau(x', x_{i+1/2}) \rvert \right) } }.
-  \end{split}
-  % \label{eq:J_tr}
-  \end{equation*}
-  }
-\end{frame}
-
-\subsubsection{Slab}
-
-\begin{frame}[allowframebreaks]
-  \frametitle{An example in the bare homogeneous slab}
-  {\hfill \cite{tomatis2011application}}%\\[3mm]
-
-  \begin{block}{}
-  % In 1-D, we find the \textcolor{ceablue1}{exponential integral functions $E_n$} and the diffusion tensor simplifies in a single coefficient.
-  % \[
-  %   \begin{split}
-  %   E_n(\mathcal{L}_{op}) = \int_1^{\infty}{du\, \frac{e^{-|\mathcal{L}_{op}|\,u}}{u^n}}\\
-  %     = \int_0^1 {d\mu \, \mu^{n-2} e^{-|\mathcal{L}_{op}| / \mu}}.
-  %   \end{split}
-  % \]
   {\textcolor{ceablue1}{APPROX}: 2G problem with isotropic scattering, extrapolated length $\zeta = 2.13 \mathcal{D}$}\\
@@
   \end{block}
-
-  \begin{table}
-  \centering
-  \caption{Cross section data of the homogenized FA ($k_{\infty} = 1.07838$); scattering cross section comes from sum on columns.}
-  \begin{tabular}{*{6}{c}}\hline \hline
-  Group $g$ & $\Sigma_{t,g}$ & \multicolumn{2}{c}{$\Sigma_{s,0,g' \rightarrow g}$} &
-  $\chi_g$ & $\nu\Sigma_f$ \\ \hline
-  1 & 5.31150E-01 & 5.04664E-01 & 2.03884E-03 & 1 & 7.15848E-03 \\
-  2 & 1.30058E+00 & 1.62955E-02 & 1.19134E+00 & 0 & 1.41284E-01 \\
-  \hline \hline
-  \end{tabular}
-  \end{table}
-
-  \begin{columns}
   \column{.5\textwidth}
@@
   \end{table}
-  \column{.5\textwidth}
-  \begin{table}
+  \end{columns}
+
+  \begin{block}{Results for the $k$-eigenvalue and the flux convergence}
   \centering
-  \caption{Results on the multiplication factor $k$}
   \begin{tabular}{*{4}{c}} \hline \hline
@@
   \end{tabular}
-  \end{table}
-  \end{columns}
-  % \vspace{-5mm}
+  \end{block}
 
   \begin{figure}
-    \centering
-    \includegraphics[width=.75\textwidth]{../figures/kflxconv.pdf}
-    \caption{Convergence trend.}
+    \includegraphics[width=.7\textwidth]{figures/Tflx_cnv.png}
+    \caption{Thermal flux}
   \end{figure}
@@
   \begin{figure}
-    \centering
-    \includegraphics[width=.8\textwidth]{../figures/eflxconv.pdf}
-    \caption{Relative flux error in optical lengths from the boundary
-             through iterations.}
+    \includegraphics[width=.7\textwidth]{figures/Fflx_cnv.png}
+    \caption{Fast flux}
   \end{figure}
+
+  \begin{table}
+  \caption{Cross section data of the homogenized FA ($k_{\infty} = 1.07838$); scattering cross section comes from sum on columns.}
+  \begin{tabular}{*{6}{c}}\hline \hline
+  Group $g$ & $\Sigma_{t,g}$ & \multicolumn{2}{c}{$\Sigma_{s,0,g' \rightarrow g}$} &
+  $\chi_g$ & $\nu\Sigma_f$ \\ \hline
+  1 & 5.31150E-01 & 5.04664E-01 & 2.03884E-03 & 1 & 7.15848E-03 \\
+  2 & 1.30058E+00 & 1.62955E-02 & 1.19134E+00 & 0 & 1.41284E-01 \\
+  \hline \hline
+  \end{tabular}
+  \end{table}
 
@@
   \end{exampleblock}
-  \vspace{10mm}
 
@@
 \end{frame}
-
-\subsubsection{Curvilinear geometries}
-\begin{frame}
-  \frametitle{Derivation of the current in 1D curvilinear geometries}
-  \vspace{-5mm}
-  \begin{columns}
-  \column{.5\textwidth}
-  {
-  Escape probability in \textcolor{ceablue1}{\bf 1D cylindrical geometry}:
-  \[
-    e_j(r) = \frac{2}{r V_j} \int_0^r { dh\, y \int_{L_j}{
-    d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right]}},
-  \]
-  with $y(r, h) = \sqrt{r^2 - h^2}$ and $L_j(h) = [-Y,y] \cap V_j$
-  ($Y = y(R, h)$).\\[10mm]
-  Escape probability in \textcolor{ceablue1}{\bf 1D spherical geometry}:
-  \[
-    e_j(r) = \frac{2\pi}{r^2 V_j} \int_0^r { dh\, h y \int_{L_j}{
-    d \ell \, \exp\left[-\tau( y, y - \ell )\right]}}.
-  \]
-  \begin{figure}
-    \centering
-    \input{../figures/sphere.tkz}
-    \caption{Spherical symmetry.}
-  \end{figure}
-  }
-  \column{.5\textwidth}
-  \vspace{-10mm}
-  \begin{figure}
-  \centering
-  \scalebox{1.5}{
-    \input{../figures/cyltracks.tkz}
-  }
-  \caption{Tracking integration \cite{hebert2009applied}.}
-  \end{figure}
-\end{columns}
-\end{frame}
-
-%%% %% Introducing the name of ``CEA colors''
-%\section{Présentation du style graphique}
-%\subsection{Couleurs officielles du CEA}
-%\begin{frame}
-%  \frametitle{Présentation des couleurs CEA}
-
-%  \begin{center}
-%    {\large Implémentées suivant la charte : \textcolor{blue}{\url{http://www-dcom.intra.cea.fr/wp-content/uploads/Logo-regles-applications-charte_CEA-vdef.pdf}} }
-%  \end{center}
-
-%  \begin{table}
-%    \LARGE
-%    \begin{tabular}{l|cccc}
-%      Base & & & & \\
-%      \hline
-%      Rouge & \textcolor{ceared1}{ceared1} & \textcolor{ceared2}{ceared2} & \textcolor{ceared3}{ceared3} & \\
-%      Vert & \textcolor{ceagreen1}{ceagreen1} & \textcolor{ceagreen2}{ceagreen2} & \textcolor{ceagreen3}{ceagreen3} & \textcolor{ceagreen4}{ceagreen4} \\
-%      Bleu & \textcolor{ceablue1}{ceablue1} & \textcolor{ceablue2}{ceablue2} & \textcolor{ceablue3}{ceablue3} & \\
-%      Orange & \textcolor{ceaorange1}{ceaorange1} & \textcolor{ceaorange2}{ceaorange2} & & \\
-%      Violet & \textcolor{ceapurple1}{ceapurple1} & \textcolor{ceapurple2}{ceapurple2} & & \\
-%      Rose & \textcolor{ceapink1}{ceapink1} & \textcolor{ceapink2}{ceapink2} & & \\
-
-%    \end{tabular}
-
-%  \end{table}
-
-%\end{frame}
-
-%\subsection{Introduction aux raccourcis}
-%%% %% Proposed shortcut to create slides
-%\theframe{Ce titre de transparent est déjà trop long pour tenir sur une seule ligne}{
-
-%  \begin{itemize}
-%  \item Ce slide est fait avec un shortcut pour aller plus vite (voir ``shortcut'')
-%  \end{itemize}
-
-%}
-
-%\begin{frame}[allowframebreaks]
-%  \frametitle{Test de slide avec allowpagebreak}
-
-%    \begin{block}{Contenu du premier transparent}{
-%        \begin{itemize}
-%        \item Des choses...
-%        \item
-%        \item
-%        \item
-%        \end{itemize}
-%      }
-%    \end{block}
-
-%  \framebreak
-
-%  \begin{block}{Contenu du second transparent}{
-%      \begin{itemize}
-%      \item ... et d'autres
-%      \end{itemize}
-%    }
-%  \end{block}
-
-%\end{frame}
-
-%\intercalaire{Titre intercalaire}
-%\intercalaireplus{Intercalaire avec du texte}{
-%  {\Large Pour dire plus de chose}
-%  {\normalsize
-%    \begin{itemize}
-%    \item Même si c'est pas forcément intéressant
-%    \item Même avec des fautes d'orthographe
-%    \end{itemize}
-%  }
-%}
-
-\section{Conclusion}
-\theframe{Conclusion}{
-%
-\begin{exampleblock}{Summary}
-%\vspace{3mm}
-\begin{itemize} \large
-  %\setlength{\itemsep}{3mm}
-  \item Diffusion theory is practical for (fast) core calculations
-  \item Possible improvements by second-order transport approximations (SP$_N$, A$_N$, \ldots)
-  % \item Presentation of transport effects in full core calculation and various diffusive-like transport approximations
-  \item The use of \textcolor{ceablue1}{equivalence theory} compensates the lack of physical information in the diffusive model
-  \item Introduction of the Ronen Method: principles \& implementation options
-  \item Similarities with collision probability methods (see the escape probabilities), without solving CPM, i.e. no matrix inversion
-  \item The Ronen Method could provide an \textcolor{ceared1}{online equivalence} between diffusion and integral transport on \textcolor{ceablue1}{coarse meshes}
-\end{itemize}
-\end{exampleblock}
-%\vfill
-\begin{alertblock}{Future development}
-%\vspace{3mm}
-\begin{enumerate}[(i)] \large
-  %\setlength{\itemsep}{3mm}
-  \item Convergence and stability analysis (using the CMFD scheme)
-  \item Formal and numerical investigation of the Ronen Method as a mean for an online equivalence
-  % \item Comparison with other deterministic techniques based on integral transport (mainly the collision probability method)
-  \item 3D implementation of the Ronen method in nodal codes
-  \item Extension to time-dependent problem
-\end{enumerate}
-\end{alertblock}
-}
-
-\section*{References}
-\begin{frame}{\insertsectionhead}
-%\nocite{*}
-\begin{multicols}{2}
-\small
-\bibliographystyle{plainnat}
-\bibliography{RonenMethod}
-\end{multicols}
-\end{frame}
-
-%% %% Possibility to add a sentence as for intercalaire
-\theclosingframe{
-  Thanks for your attention!\\[2cm]
-  \begin{flushright}\textcolor{white}{
-    \visible<2>{
-    \emph{Bòja brigant\\[5mm] Ciao Piero!}}
-    % \hspace{3cm}
-    }
-  \end{flushright}
-}
-
-%% %% End of main part, beginning of backup (this is used to count the number of slides)
-\backupbegin
-%% %% New section for backup... the SectionCounter is used (along with totcount) to display at main toc all
-%% %% sections but backups
-%%\section{Backup}
-\setcounter{SectionCounter}{\thesection}
-\addtocounter{SectionCounter}{-1}
-%% %% Back up menu accessible from any slide where the number of pages is displayed
-%%\frame[label=MenuBackup]{\frametitle{Sommaire}
-%%  \tableofcontents[sections=\thesection]
-%%}
-
-\section*{Other derivation of the diffusion coefficient}
-\subsection*{The fundamental leakage model}
-\include{backup_slides/BNlm}
-\subsection*{Diffusive-like approximations from radiative transfer}
-\include{backup_slides/otherdiffdefs}
-\subsection*{Homogenization and Equivalence Theory}
-\include{backup_slides/homogequiv}
-\subsection*{Special functions}
-\include{backup_slides/specfuncs}
-
-%% %% End of backup mode....
-\backupend
-
-\end{document}

### 2019-10-02 docs/ICTT2019/slides/backup_slides/sourcebymoments.tex
Update ICTT src files and upload the slides shown at the conference

\begin{frame}
  \frametitle{Treatment of scattering anisotropy as in ENDF}
  \begin{block}{Introducing the flux moments on spherical harmonics in the NTE}
  {
  \begin{gather*}
  \left[ \frac{1}{v}\frac{\partial}{\partial t}
  %+ \nabla \cdot (\bOm \,\_) + \Sigma_t(\mathbf{r}, E) \right] \varphi(\mathbf{r}, E, \bOm, t)
  + \bOm \cdot \nabla  + \Sigma_t(\mathbf{r}, E) \right] \varphi(\mathbf{r}, E, \bOm, t)
  = \frac{\chi(E)}{4\pi} \int_0^{\infty} {dE' \nu\Sigma_f(\mathbf{r}, E') \phi(\mathbf{r}, E, t')}
  + S_{ext}(\mathbf{r}, E, \bOm, t) +\\
  \visible<2-3> {\frac{1}{2\pi}}
  \only<-3>{\int_{4\pi} d\bOm'}
  \only<4->{ \sum_{\ell = 0}^{\infty} \sum_{m=-\ell}^{\ell}  Y_{\ell m}(\bOm) }
  \int_0^{\infty} {dE' \only<-3>{\Sigma_s}\only<4->{\Sigma_{s, \ell}}
  (\mathbf{r}, E' \rightarrow E
  \only<1> {, \bOm' \rightarrow \bOm)}
  \only<2-3>{, \textcolor{ceablue1}{\bOm' \cdot \bOm})}
  \only<-3>{\varphi(\mathbf{r}, E', \bOm', t)}
  \only<4->{)\phi_{\ell m}(\mathbf{r}, E', t) }
  },
  \end{gather*}
  }
  {\sl hp.}: a unique family of fissile nuclides, all prompts -- b.c. at $\mathbf{r}_S$: $\varphi(\mathbf{r}_S, E, \bOm) = 0$ if $\hat{n} \cdot \bOm < 0$, $\forall E$. \uncover<2->{$\mu_0 = \bOm \cdot \bOm'$ is the cosine of the scattering angle.} \uncover<3->{Thanks to the addition theorem $P_0$ is written in terms of the spherical harmonics functions $Y_{\ell m}$}
  \uncover<2->{ \[
    \Sigma_s(\mathbf{r}, E' \rightarrow E, \mu_0) = \sum_{\ell = 0}^{\infty}{\frac{2\ell + 1}{2}\Sigma_{s,\ell}(\mathbf{r}, E' \rightarrow E) P_\ell(\mu_0)}
   \visible<3-> {= 2\pi \sum_{\ell = 0}^{\infty} {\sum_{m=-\ell}^{\ell}{ \Sigma_{s,\ell} Y^*_{\ell m}(\bOm') Y_{\ell m}(\bOm)}}}
  \]}
  \uncover<3->{\emph{Spherical harmonics} in $\bOm = (\mu, \theta)$, defined by associated Legendre polynomials $P_{\ell}^m$:
  \[ Y_{\ell m}(\bOm) = \left[ \frac{2 \ell+1}{4\pi} \frac{(\ell - |m|)!}{(\ell + |m|)!} \right]^{1/2} P_{\ell}^m (\mu)e^{i m \theta}
  \uncover<4->{ \quad
  \text{so that } \textcolor{ceablue1}{
  \varphi = \sum_{\ell = 0}^{\infty} \sum_{m=-\ell}^{\ell} \left( \frac{2\ell + 1}{4\pi} \right)^{1/2} \phi_{\ell m}(\mathbf{r}[, \ast]) Y_{\ell m}(\bOm)}}
  \]
  and subject to the orthogonal-normalization property $\int_{4\pi} {d \bOm Y^*_{\ell m}(\bOm) Y_{k n}(\bOm)} = \delta_{\ell k}\delta_{m n}$.}
  \end{block}
\end{frame}

### 2019-10-29 CPM1D/cpm1dcurv.py
check for escape probabilities GT 1

@@ -285,6 +285,8 @@ def ep2cp(ep):
     # escape terms (wrongly called probability sometimes) for the incoming
     # (negative-minus) currents are already stored as negative quantities.
     cp = np.zeros((G, I, I),)
+    if np.any(ep > 1):
+        lg.warn("Detected escape probabilities greater than 1!")
     ep_minus, ep_plus = ep[:,:,:,1], ep[:,:,:,0]
     cp[:, 0,:] = ep_plus[:,0,:] + ep_minus[:,0,:]
     cp[:,1:,:] = ep_plus[:,:-1,:] - ep_plus[:,1:,:] \

### 2019-10-29 CPM1D/cpm1dcurv.py
Code check and review of the calculation of escape probabilities; code improvement and correction.

@@ -194,77 +194,84 @@ def calculate_escape_prob(r, st, tr_data, geometry_type="cylinder"):
     varepsp = vareps[:,:,0]  # first index is i, second index is j (sources)
     varepsm = vareps[:,:,1]  # (defined as negative!)
     # varepsp is for escape whereas varepsm is for in-scape
+
+    # local functions
     cumsum_ks = np.insert(np.cumsum(ks), 0, 0)
     get_ks_in_ring = lambda i0: np.arange(cumsum_ks[i0], cumsum_ks[i0+1])
-    for i in range(I):
+    ji_allk = lambda j, i: np.asarray([jki(j,k,i) for k in range(ks[i])])
+    def get_weights(i, r):
         idx = get_ks_in_ring(i)
         hk, wk = hks[idx], wks[idx]
-        wgts = w(wk, r[i+1], hk)
+        return w(wk, r, hk)
 
-        ji_allk = lambda j, i0=i: \
-            np.asarray([jki(j,k,i0) for k in range(ks[i0])])
+    # process the surfaces outwards
+    for i in range(I):
+        wgts = get_weights(i, r[i+1])
 
         # escape within (r_i-1/2, r_i+1/2)
         # contribution from the i-th ring through its outer surface
-        idx_0 = ji_allk(0)
+        idx_0, invsti = ji_allk(0, i), 1. / st[i]
         tii = 2 * tau[idx_0]  # for all k tracking lines
-        varepsp[i,i] += np.dot(wgts, K_at_0 - K(tii)) / st[i]
+        varepsp[i,i] += np.dot(wgts, K_at_0 - K(tii)) * invsti
 
         # contributions from the rings that are around
-        tij = np.zeros(ks[i])
+        tij = np.zeros_like(wgts)
         for j in range(i+1,I):
-            idx_j = ji_allk(j-i)
+            idx_j, invstj = ji_allk(j-i, i), 1. / st[j]
             a = tii + tij
             diffK = K(a) - K(a + tau[idx_j])
-            varepsp[i,j] += np.dot(wgts, diffK) / st[j]
+            varepsp[i,j] += np.dot(wgts, diffK) * invstj
             diffK = K(tij) - K(tij + tau[idx_j])
-            varepsm[i,j] -= np.dot(wgts, diffK) / st[j]
+            varepsm[i,j] -= np.dot(wgts, diffK) * invstj
             tij += tau[idx_j]
 
         # escape within (0, r_i-1/2)
[…]

### 2019-10-30 docs/PHYSOR2020/full/pCMFD-RM-PHYSOR2020.tex
Tex files for PHYSOR2020 full paper
LaTex files for the PHYSOR2020 full paper. Also, a comprehensive bibtex file (RM-bib.bib) is updated.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  This is a sample LaTeX input file for your contribution to 
%  the PHYSOR2020 topical meeting.
%
%  Please use it as a template for your full paper 
%    Accompanying/related file(s) include: 
%       1. Document class/format file: physor2020.cls
%       2. Sample Postscript Figure:   figure.pdf
%       3. A PDF file showing the desired appearance: physor2020_template.pdf
%       4. cites.sty and citesort.sty that might be needed by some users 
%    Direct questions about these files to: rcarlos.lope@gmail.com
%											armando.gomez@inin.gob.mx
%
%    Notes: 
%      (1) You can use the "dvips" utility to convert .dvi 
%          files to PostScript.  Then, use either Acrobat 
%          Distiller or "ps2pdf" to convert to PDF format. 
%      (2) Different versions of LaTeX have been observed to 
%          shift the page down, causing improper margins.
%          If this occurs, adjust the "topmargin" value in the
%          physor2020.cls file to achieve the proper margins. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{physor2020}
%
%  various packages that you may wish to activate for usage 
\usepackage{tabls}
\usepackage{cites}
\usepackage{epsf}
\usepackage{appendix}
\usepackage{ragged2e}
\usepackage[top=1in, bottom=1.in, left=1.in, right=1.in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\usepackage{caption}
\captionsetup{width=1.0\textwidth,font={bf,normalsize},skip=0.3cm,within=none,justification=centering}

% for quotes
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

\newcommand{\eq}[1]{Eq.~(\ref{#1})}
\newcommand{\eqnolabel}[1]{(\ref{#1})}
\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
\newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
\newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
\newcommand{\tbl}[1]{Table~\ref{#1}}
\newcommand{\tblnolabel}[1]{\ref{#1}}
\newcommand{\tbls}[1]{Tables~\ref{#1}}
\newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
\newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\fignolabel}[1]{\ref{#1}}
\newcommand{\figs}[1]{Figs.~\ref{#1}}
\newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
\newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
\newcommand{\sxn}[1]{Section~\ref{#1}}

\newcommand{\revised}[1]{{\color{red}{#1}}}
\newcommand{\tsup}[1]{\textsuperscript{#1}}
\newcommand{\tsub}[1]{\textsubscript{#1}}

\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}

\newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
\newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
\newcommand{\rr}{\ensuremath{\bm{r}}}
\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
\newcommand{\rE}{\ensuremath{(\rr,E)}}

\newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
\newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
\newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
%\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcL}{\tau}
\newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
\newcommand{\dx}{\ensuremath{\Delta x}}

\newcommand{\jp}{\ensuremath{\bm{J}^+}}
\newcommand{\jm}{\ensuremath{\bm{J}^-}}
\newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
\newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}

%\usepackage[justification=centering]{caption}

%
% Define title...
%
\title{INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL\\ DIFFUSION CALCULATIONS}
%
% ...and authors
%
\author{%
  % FIRST AUTHORS 
  %
  \textbf{Roy Gross$^1$, Daniele Tomatis$^2$, and Erez Gilad$^3$}\footnote{} \\
  $^1$Name of Institution 1  \\
  Corresponding Address \\ 
\\
  $^2$Name of Institution 2  \\ 
    Corresponding Address \\ 
\\
  $^3$Name of Institution 3  \\
     Corresponding Address \\
     \\
  \url{roygross@post.bgu.ac.il}, \url{daniele.tomatis@cea.fr}, \url{gilade@bgu.ac.il}
}
%
% Insert authors' names and short version of title in lines below
%
\newcommand{\authorHead}      % Author's names here use et al. if more than 3
           {Roy Gross, Daniele Tomatis, Erez Gilad}  
\newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
           {INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL DIFFUSION CALCULATIONS}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   BEGIN DOCUMENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\justify

% ------------------------------------------
\begin{abstract}
  The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration. Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new methods for accelerating the convergence are reported. For example, the use of the integral flux intermediate values as new boundary conditions in each iteration and iterative updating of the extrapolated boundary using the corrected local diffusion coefficients. Moreover, the pCMFD scheme is implemented and its performances are compared with those of standard CMFD scheme.
\end{abstract}
\keywords{neutron diffusion ; integral transport ; non-linear transport correction ;
CMFD ; pCMFD }

% ------------------------------------------
\section{INTRODUCTION} 
\label{sec:intro}

The distribution of the neutron flux in the reactor core is described by the neutron transport equation. Transport calculations on a full core scale can be a highly intensive computational task. To overcome this difficulty, faster (but less accurate) multigroup neutron diffusion solvers are often used. However, future Gen-IV reactor designs are characterized by strong heterogeneity in the core and modern calculation schemes evolve towards best-estimate codes, aiming at high accuracy. Hence, the accuracy of diffusion calculations is investigated. A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient. The calculation of this parameter should be based on physical insights from the full transport equation such that the resulting (transport corrected) diffusion approximation can capture the transport phenomena of interest.

The main hypothesis of this research, called the Ronen Method, is based on iterative calculations of the multigroup diffusion coefficients, driven by the accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation. The iterative scheme calculates new flux distribution using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation. However, the direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning. Nonetheless, the integral current can be enforced in the CMFD discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients. This is the option adopted in this study.

% ------------------------------------------
\section{The Ronen method} 
\label{sec:RM}

% ------------------------------------------
\section{Numerical implementation of the Ronen method} 
\label{sec:RM-num}

% ------------------------------------------
\subsection{CMFD implementation of the Ronen method} 
\label{sec:RM-CMFD}

% ------------------------------------------
\subsection{pCMFD implementation of the Ronen method} 
\label{sec:RM-pCMFD}

% ------------------------------------------
\section{Results} 
\label{sec:res}

% ------------------------------------------
\section{CONCLUSIONS}
\label{sec:conc}

Present your summary and conclusions here.

%\begin{figure}[!htb]
%  \centering
%  \includegraphics[scale=0.60]{./Figures/figure.pdf}
%  \caption{SCALE/TRITON-NEWT Model of BWR Assembly in Order to Show and Example of a Figure and a Multi-line Caption}   
%  \label{fig:amdahl}
%\end{figure}

%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
%\item Any number, text or symbol is in Times font and is not smaller than 
%  10-point after reduction to the actual window in your paper
%\item That it can be translated into PDF
%\end{itemize}

%\begin{table}[!htb]
%  \centering
%  \caption{\bf Parallel Performance for the Sample Problem}
%  \label{table:example} 
%  \begin{tabular}{|c|c|c|c|} \hline 
%   Number of & Wall-Clock & Speedup & Efficiency \\
%   Processors & Time$^{a}$ (min) & (T$_{s}$/T$_{p}$) & (\%) \\ \hline
%    \ 1 &  100.0 & \ ---    & ---  \\ \hline
%    \ 2 &   52.6 & \ 1.9    & 95.0 \\ \hline 
%  \end{tabular}
%\end{table}

% ------------------------------------------
\section*{NOMENCLATURE}

If variables are extensively used in the text, a Nomenclature section would be helpful to the readers.

% ------------------------------------------
\section*{ACKNOWLEDGEMENTS}

Acknowledge the help of colleagues and sources of funding, as appropriate.

% ------------------------------------------
% You can enter a bibliography into the document using the following format, or use the 
% bibliography style file "physor.bst" found in the template directory.  You can use the bibliography style file
% by replacing the current bibliography block with:
\setlength{\baselineskip}{12pt}
\bibliographystyle{physor}
\bibliography{RM-bib}

% ------------------------------------------
%\appendix
%\gdef\thesection{APPENDIX \Alph{section}}
%\section{Sample Appendix 1}
%\label{app:a}
%If necessary, include Appendices numbered in upper case alphabetical order. This is \ref{app:a}.

\end{document}

### 2019-10-30 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
upload the physor template to start writing the article

--- 2019-10-30 docs/PHYSOR2020/full/pCMFD-RM-PHYSOR2020.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
@@
 \usepackage{caption}
-\captionsetup{width=1.0\textwidth,font={bf,normalsize},skip=0.3cm,within=none,justification=centering}
+\captionsetup{width=1.0\textwidth,font={bf,normalsize},%
+              skip=0.3cm,within=none,justification=centering}
 
-% for quotes
-\usepackage [english]{babel}
-\usepackage [autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
+% Daniele: I commented this part because it was not present in the original
+% conference template.
+% % for quotes
+% \usepackage[english]{babel}
+% \usepackage[autostyle, english = american]{csquotes}
+% \MakeOuterQuote{"}
+%
+% \newcommand{\eq}[1]{Eq.~(\ref{#1})}
+% \newcommand{\eqnolabel}[1]{(\ref{#1})}
+% \newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
+% \newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
+% \newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
+% \newcommand{\tbl}[1]{Table~\ref{#1}}
+% \newcommand{\tblnolabel}[1]{\ref{#1}}
+% \newcommand{\tbls}[1]{Tables~\ref{#1}}
+% \newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
+% \newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
+% \newcommand{\fig}[1]{Fig.~\ref{#1}}
+% \newcommand{\fignolabel}[1]{\ref{#1}}
+% \newcommand{\figs}[1]{Figs.~\ref{#1}}
+% \newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
+% \newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
+% \newcommand{\sxn}[1]{Section~\ref{#1}}
+%
+% \newcommand{\revised}[1]{{\color{red}{#1}}}
+% \newcommand{\tsup}[1]{\textsuperscript{#1}}
+% \newcommand{\tsub}[1]{\textsubscript{#1}}
+%
+% \newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
+% \newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
+% \newcommand{\rr}{\ensuremath{\bm{r}}}
+% \newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
+% \newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
+% \newcommand{\rE}{\ensuremath{(\rr,E)}}
+%
+% \newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
+% \newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
+% \newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
+% %\newcommand{\mcL}{\mathcal{L}}
+% \newcommand{\mcL}{\tau}
+% \newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
+% \newcommand{\dx}{\ensuremath{\Delta x}}
+%
+% \newcommand{\jp}{\ensuremath{\bm{J}^+}}
+% \newcommand{\jm}{\ensuremath{\bm{J}^-}}
+% \newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
+% \newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
 
-\newcommand{\eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\eqnolabel}[1]{(\ref{#1})}
-\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
-\newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
-\newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
-\newcommand{\tbl}[1]{Table~\ref{#1}}
-\newcommand{\tblnolabel}[1]{\ref{#1}}
-\newcommand{\tbls}[1]{Tables~\ref{#1}}
-\newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
-\newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
-\newcommand{\fig}[1]{Fig.~\ref{#1}}
-\newcommand{\fignolabel}[1]{\ref{#1}}
-\newcommand{\figs}[1]{Figs.~\ref{#1}}
-\newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
-\newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
-\newcommand{\sxn}[1]{Section~\ref{#1}}
-
-\newcommand{\revised}[1]{{\color{red}{#1}}}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsubscript{#1}}
-
+% about notes and comments from each author
 \newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
 \newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
-
-\newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
-\newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
-\newcommand{\rr}{\ensuremath{\bm{r}}}
-\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
-\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
-\newcommand{\rE}{\ensuremath{(\rr,E)}}
-
-\newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
-\newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
-\newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
-%\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcL}{\tau}
-\newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
-\newcommand{\dx}{\ensuremath{\Delta x}}
-
-\newcommand{\jp}{\ensuremath{\bm{J}^+}}
-\newcommand{\jm}{\ensuremath{\bm{J}^-}}
-\newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
-\newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
+\newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
 
@@
 %
-\title{INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL\\ DIFFUSION CALCULATIONS}
+\title{INTEGRAL TRANSPORT CORRECTION \\TO DIFFUSION CALCULATIONS BY pCMFD}
 %
@@
   %
-  \textbf{Roy Gross$^1$, Daniele Tomatis$^2$, and Erez Gilad$^3$}\footnote{} \\
-  $^1$Name of Institution 1  \\
-  Corresponding Address \\ 
+  \textbf{Roy Gross$^1$\footnote{Corresponding author: xxx.},
+          Daniele Tomatis$^2$,
+          and Erez Gilad$^1$} \\
+  $^1$The Unit of Nuclear Engineering, \\
+  Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\
 \\
-  $^2$Name of Institution 2  \\ 
-    Corresponding Address \\ 
-\\
-  $^3$Name of Institution 3  \\
-     Corresponding Address \\
+  $^2$CEA, DEN, Service d’\'etudes des r\'eacteurs et
+      de math\'ematiques appliqu\'ees (SERMA), \\
+    Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France \\
      \\
@@
 \newcommand{\authorHead}      % Author's names here use et al. if more than 3
-           {Roy Gross, Daniele Tomatis, Erez Gilad}  
+           {R. Gross, D. Tomatis, E. Gilad}
 \newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
-           {INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL DIFFUSION CALCULATIONS}  
+           {The Ronen Method by pCMFD}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{abstract}
-\keywords{neutron diffusion ; integral transport ; non-linear transport correction ;
-CMFD ; pCMFD }
+\keywords{neutron diffusion, integral transport, CMFD}
 
@@
 % ------------------------------------------
-\section{The Ronen method} 
+\section{THE RONEN METHOD}
 \label{sec:RM}
@@
 % ------------------------------------------
-\section{Numerical implementation of the Ronen method} 
+\section{NUMERICAL IMPLEMENTATION}
 \label{sec:RM-num}
@@
 % ------------------------------------------
-\subsection{CMFD implementation of the Ronen method} 
+\subsection{CMFD}
 \label{sec:RM-CMFD}
@@
 % ------------------------------------------
-\subsection{pCMFD implementation of the Ronen method} 
+\subsection{pCMFD}
 \label{sec:RM-pCMFD}
@@
 % ------------------------------------------
-\section{Results} 
+\section{RESULTS}
 \label{sec:res}
@@
 % ------------------------------------------
-\section*{NOMENCLATURE}
-
+%\section*{NOMENCLATURE}
+%
 If variables are extensively used in the text, a Nomenclature section would be helpful to the readers.
-
+%
 % ------------------------------------------
-\section*{ACKNOWLEDGEMENTS}
-
-Acknowledge the help of colleagues and sources of funding, as appropriate.
+%\section*{ACKNOWLEDGEMENTS}
+%
+%Acknowledge the help of colleagues and sources of funding, as appropriate.
 
@@
 %If necessary, include Appendices numbered in upper case alphabetical order. This is \ref{app:a}.
-
+%
 \end{document}

### 2019-10-30 docs/ICTT2019/RMethod_ictt26.tex
revert to a proper element tree

@@
 \textbf{Roy Gross and Erez Gilad}\\
-Unit of Nuclear Engineering\\
+The Unit of Nuclear Engineering\\
 Ben-Gurion University of the Negev, Israel\\

### 2019-10-30 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
updated physor manuscript
physor.bst - fixed bug
Rest of the files are updated versions.

--- 2019-10-30 docs/PHYSOR2020/full/pCMFD-RM-PHYSOR2020.tex
@@
 \captionsetup{width=1.0\textwidth,font={bf,normalsize},skip=0.3cm,within=none,justification=centering}
+\usepackage{bm}
+\usepackage{tikz}
+\usepackage{xfrac}
+\usepackage{units}
 
@@
 
-\newcommand{\jp}{\ensuremath{\bm{J}^+}}
-\newcommand{\jm}{\ensuremath{\bm{J}^-}}
-\newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
-\newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
+\newcommand{\jp}{\ensuremath{J^+}}
+\newcommand{\jm}{\ensuremath{J^-}}
+\newcommand{\jpm}{\ensuremath{J^\pm}}
+\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
+\newcommand{\bmj}{\ensuremath{\bm{J}}}
+
+\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
 
@@
 %
-\title{INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL\\ DIFFUSION CALCULATIONS}
+\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\USING pCMFD SCHEME}
 %
@@
 
-The main hypothesis of this research, called the Ronen Method, is based on iterative calculations of the multigroup diffusion coefficients, driven by the accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
+The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by the accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
 The iterative scheme calculates new flux distribution using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
 However, the direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning.
-Nonetheless, the integral current can be enforced in the CMFD discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients.
+Nonetheless, the integral current can be enforced in the Coarse Mesh Finite Difference (CMFD) discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients.
 This is the option adopted in this study.
+
+% ------------------------------------------
+\subsection{Coarse Mesh Finite Difference (CMFD)} 
+\label{sec:CMFD-intro}
+
+The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing the separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
+Recently, multi-dimensional transport codes have used it as acceleration technique and the convergence of different implementations was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
+
+The use of a coarse mesh for the discretization of the problem is generally causing considerable error by truncation applied on the finite difference approximations of the derivative terms.
+On the other hand, it yields very fast calculations.
+The CMFD method recovers corrective terms by exploiting functional relations between the (scalar) flux and the current density, which appear in the neutron balance equation.
+The balance equation is solved for the flux, so that local models seek more accurate estimates of the current in order to derive these corrections.
+In principle, the corrective terms can be computed with a different physics other than diffusion, which is always solved at the coarse level.
+This facilitates its application to accelerate complex multi-dimensional transport codes.
+This acceleration is actually implemented by rebalancing the scalar flux, with the optional use of some relaxation~\cite{Park-2017}.
+Hence, a non-linear iterative scheme arises between the CMFD solver and the computation of the local corrections, which use the latest estimates of the flux available from the diffusion solver.
+
+Second-order SPN equations can be solved by ordinary diffusion codes~\cite{Larsen-1993}.
+Yamamoto et al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
+This is because this quantity is generally smaller than the scalar flux (0-th moment) and can change its sign.
+They propose to modify the balance equation for the second moment in order to fix this numerical behavior.
+The modification consists of a shift with a positive quantity of the second moment so that their difference between neighboring quantities is unchanged, and their sum becomes positive and arbitrarily large.
+
+In case partial currents can be computed, the pCMFD method~\cite{Cho-2003} can be used to determine two distinct corrective terms per positive and negative partial currents, instead of having a single degree of freedom per cell surface.
+Another version of the CMFD called artificial diffusion~\cite{Zhu-2016,Jarrett-2016} redefines the diffusion coefficient as the sum of the original value and a complement derived from the current difference, which is still considered as proportional to the flux gradient.
+This scheme can potentially lead to negative diffusion constants.
+
+The CMFD (and its variants) was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
+Contrary to the previous implementations, no operator was inverted to get a new higher order solution of the flux.
+This offers indeed a fast estimate of the higher order current.
 
@@
 
+In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory.
+Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
+\begin{equation}\label{eq:Fick}
+\bm{J}^D\rE = -D\rE\bnabla\phi\rE = \bm{J}\rE \,\, . 
+\end{equation}
+
+Since these accurate estimates of the currents are based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
+\begin{equation}\label{eq:RM-it}
+D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert} \,\, ,
+\end{equation}
+where $k$ is the iteration index. %The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
+
+The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
+Nevertheless, isotropic scattering remained as a basic postulate.
+For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
+\begin{equation}\label{eq:RM-it-1D-slab}
+D^{(k+1)}(x,E) = -\frac{\frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
+	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
+{\partial \phi^{(k)}(x,E)/\partial x} \,\, .
+\end{equation}
+
+In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration in a simple slab problem.
+They adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
+%
+%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
+%
+This technique can avoid indeterminate divisions in case of vanishing flux gradients.
+It was observed that the RM could drive the flux distribution closer to the transport reference solution.
+As expected, the largest errors were located near the boundary, where the transport effects are most pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
+
 % ------------------------------------------
@@
 
+The CMFD neutron balance equation for a $\keff$-eigenvalue problem on a one-dimensional mesh, shown in Fig.~\ref{fig:mesh1D}, is
+\begin{equation}\label{eq:balance}
+J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_g \phi_{i+\hzi,g} = q_{i+\hzi,g} \,\, , 
+\end{equation}	
+where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section, the subscript $g$ denotes the energy group, and $q$ is the isotropic neutron source defined as
+\begin{equation}\label{eq:qsrc}
+q_{i+\hzi,g} = \sum\limits_{g'=1}^G\sigma_{s,0,g\leftarrow g'}\phi_{i+\hzi,g'} +
+\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i+\hzi,g'}\phi_{i+\hzi,g'} \,\, ,
+\end{equation}	
+where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the eigenvalue, $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
+
+\begin{figure}[htbp!] 
+	\centering
+	\begin{tikzpicture}
+	\tikzstyle{every node}=[font=\footnotesize]
+	\draw[thick] (0,0) -- (3,0);
+	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
+	\draw[thick] (4,0) -- (7,0);
+	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
+	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};
+
+	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-\hzi$};
+	\node[anchor=south] at (1cm,1pt) {0};
+	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+\hzi$};
+
+	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-\hzi$};
+	\node[anchor=south] at (5.5cm,1pt) {$i$};
+	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+\hzi$};
+
+	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-3/2$};
+	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
+	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-\hzi$};
+	\end{tikzpicture}
+	\caption{Notation of the one-dimensional mesh.}
+	\label{fig:mesh1D}
+\end{figure}
+
 % ------------------------------------------
-\subsection{CMFD implementation of the Ronen method} 
+\subsection{CMFD implementation} 
 \label{sec:RM-CMFD}
@@
 % ------------------------------------------
-\subsection{pCMFD implementation of the Ronen method} 
+\subsection{pCMFD implementation} 
 \label{sec:RM-pCMFD}
+
+The partial currents in any point $x$ in a slab are defined according to
+\begin{equation}
+\label{eq:partial-current}
+\jpm (x) \cong \frac{\phi(x)}{4} \pm \frac{\jD (x)}{2} \,\, ,
+\end{equation}
+where $\jD$ denotes the diffusion current.
+%where
+%\begin{equation}
+%\label{eq:diff-current}
+%\bm{J} (x) = \jp(x) - \jm(x) \,\, .
+%\end{equation}
+The partial currents correction factors are defined on cell surface according to
+\begin{equation}
+\label{eq:PCCF}
+\jpm _{i+\hzi} = \frac{1}{4}\phi_{i+\hzi}
+\pm \frac{1}{2} \jD _{i+\hzi} \pm \frac{1}{2} \delta \jpm _{i+\hzi} \,\, ,
+\end{equation}
+where
+\begin{equation}
+\label{eq:jdiff}
+\jD _{i+\hzi} = - 2 D_{i+\hzi} \frac{\phi_{i+1} - \phi_i}{\Delta_{i+1}+\Delta_i} 
+\,\,, %\nonumber \\
+D_{i+\hzi} = \frac{\Delta_i D_i + \Delta_{i+1} D_{i+1}}{\Delta_i + \Delta_{i+1}} 
+\,\,, %\nonumber \\
+\phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}} \, .
+\end{equation}
+Substituting~\cite{Jarrett-2016,Zhu-2016}
+\begin{equation}
+\label{eq:CCF-sub}
+\frac{1}{2} \delta \jp _{i+\hzi} \equiv -\delta D^+ _{i+\hzi} \phi_i \,, 
+\quad
+\frac{1}{2} \delta \jm _{i+\hzi} \equiv -\delta D^- _{i+\hzi} \phi_{i+1}\,\, ,
+\end{equation}
+yields
+\begin{align}
+\label{eq:par4}
+\jp _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
++ \frac{1}{2}\jD _{i+\hzi} - \delta D^+ _{i+\hzi} \phi_i \\
+\jm _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
+- \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1} \,\, .
+\end{align}
+%Recall that $\jpm$ are calculated using the integral expression. 
+%
+Solving for the partial current correction factors gives
+\begin{equation}
+\label{eq:ccfsss1}
+\delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
+	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i} \,, \quad
+\delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
+	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}} \,\, .
+\end{equation}
+
+In case the diffusion current is accurate, e.g., in a weak absorbing medium and several mfp's from the boundary or a strong absorber, the correction factors $\delta D^\pm$ vanish and~\eq{eq:ccfsss1} reduces to~\eq{eq:partial-current}, as expected, which implies for the net (accurate) current
+\begin{equation}
+J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi} \,\, .
+\end{equation}
 
@@
 
-If variables are extensively used in the text, a Nomenclature section would be helpful to the readers.
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item RM - Ronen Method
+\item CMFD - Coarse Mesh Finite Difference
+\item pCMFD - partial current CMFD
+\end{itemize}
 

### 2019-11-05 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
Add and check template and other contents for the PHYSOR2020 article.

@@
 \usepackage{caption}
-\captionsetup{width=1.0\textwidth,font={bf,normalsize},skip=0.3cm,within=none,justification=centering}
+\captionsetup{width=1.0\textwidth,font={bf,normalsize},%
+              skip=0.3cm,within=none,justification=centering}
 \usepackage{bm}
@@
 
-% for quotes
-\usepackage [english]{babel}
-\usepackage [autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
-
+% Daniele: I commented this part because it was not present in the original
+% conference template.
+% % for quotes
+% \usepackage[english]{babel}
+% \usepackage[autostyle, english = american]{csquotes}
+% \MakeOuterQuote{"}
+%
 \newcommand{\eq}[1]{Eq.~(\ref{#1})}
@@
 \newcommand{\sxn}[1]{Section~\ref{#1}}
-
-\newcommand{\revised}[1]{{\color{red}{#1}}}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsubscript{#1}}
-
-\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
-\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
-
+%
+% \newcommand{\revised}[1]{{\color{red}{#1}}}
+% \newcommand{\tsup}[1]{\textsuperscript{#1}}
+% \newcommand{\tsub}[1]{\textsubscript{#1}}
+%
 \newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
@@
 \newcommand{\dx}{\ensuremath{\Delta x}}
-
-\newcommand{\jp}{\ensuremath{J^+}}
-\newcommand{\jm}{\ensuremath{J^-}}
-\newcommand{\jpm}{\ensuremath{J^\pm}}
-\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
-\newcommand{\bmj}{\ensuremath{\bm{J}}}
+%
+\newcommand{\jp}{\ensuremath{\bm{J}^+}}
+\newcommand{\jm}{\ensuremath{\bm{J}^-}}
+\newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
+\newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
 
 \newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
+
+% about notes and comments from each author
+\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
+\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
+\newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
 
@@
 %
-\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\USING pCMFD SCHEME}
+% \title{INTEGRAL TRANSPORT CORRECTION \\TO DIFFUSION CALCULATIONS BY pCMFD}
+\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\USING THE pCMFD SCHEME}
 %
@@
   %
-  \textbf{Roy Gross$^1$, Daniele Tomatis$^2$, and Erez Gilad$^3$}\footnote{} \\
-  $^1$Name of Institution 1  \\
-  Corresponding Address \\ 
+  \textbf{Roy Gross$^1$\footnote{Corresponding author: xxx.},
+          Daniele Tomatis$^2$,
+          and Erez Gilad$^1$} \\
+  $^1$The Unit of Nuclear Engineering, \\
+  Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\
 \\
-  $^2$Name of Institution 2  \\ 
-    Corresponding Address \\ 
+  $^2$CEA, DEN, Service d’\'etudes des r\'eacteurs et
+      de math\'ematiques appliqu\'ees (SERMA), \\
+    Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France \\
      \\
-  $^3$Name of Institution 3  \\
-     Corresponding Address \\
-     \\
-  \url{roygross@post.bgu.ac.il}, \url{daniele.tomatis@cea.fr}, \url{gilade@bgu.ac.il}
+  \url{roygross@post.bgu.ac.il},
+  \url{daniele.tomatis@cea.fr},
+  \url{gilade@bgu.ac.il}
 }
@@
 \newcommand{\authorHead}      % Author's names here use et al. if more than 3
-           {Roy Gross, Daniele Tomatis, Erez Gilad}  
+           {R. Gross, D. Tomatis, E. Gilad}
 \newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
-           {INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL DIFFUSION CALCULATIONS}  
+           {INTEGRAL TRANSPORT CORRECTION TO 1-D DIFFUSION CALCULATIONS by pCMFD}
+%          {The Ronen Method by pCMFD}  % Daniele's suggestion (shorter)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{abstract}
-\keywords{neutron diffusion ; integral transport ; non-linear transport correction ;
-CMFD ; pCMFD }
+\keywords{neutron diffusion, integral transport, non-linear transport correction, CMFD}
+% Daniele suggestion:
+% I would not include pCMFD since it belongs to the CMFD class of methods and shorten the list of keywords
 
@@
 % ------------------------------------------
-\subsection{Coarse Mesh Finite Difference (CMFD)} 
-\label{sec:CMFD-intro}
+%\subsection{Coarse Mesh Finite Difference (CMFD)}
+%\label{sec:CMFD-intro}
+% the content of this section was moved in the section about the implementation
+%
+%
+% ------------------------------------------
+\section{THE RONEN METHOD}
+\label{sec:RM}
+
+In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory.
+Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
+\begin{equation}\label{eq:Fick}
+\bm{J}^D\rE = -D\rE\bnabla\phi\rE = \bm{J}\rE.
+\end{equation}
+
+Since these accurate estimates of the currents are based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
+\begin{equation}\label{eq:RM-it}
+D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert},
+\end{equation}
+where $k$ is the iteration index. %The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
+
+The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
+Nevertheless, isotropic scattering remained as a basic postulate.
+For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
+\begin{equation}\label{eq:RM-it-1D-slab}
+D^{(k+1)}(x,E) = -\frac{\frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
+	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
+{\partial \phi^{(k)}(x,E)/\partial x}.
+\end{equation}
+
+In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration in a simple slab problem.
+They adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
+%
+%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
+%
+This technique can avoid indeterminate divisions in case of vanishing flux gradients.
+It was observed that the RM could drive the flux distribution closer to the transport reference solution.
+As expected, the largest errors were located near the boundary, where the transport effects are most pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
+
+% ------------------------------------------
+\section{NUMERICAL IMPLEMENTATION}
+\label{sec:RM-num}
 
@@
 % ------------------------------------------
-\section{The Ronen method} 
-\label{sec:RM}
+\subsection{CMFD}
+\label{sec:RM-CMFD}
 
-In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
-\begin{equation}\label{eq:Fick}
-\bm{J}^D\rE = -D\rE\bnabla\phi\rE = \bm{J}\rE \,\, . 
+The CMFD neutron balance equation for a $\keff$-eigenvalue problem in a one-dimensional slab problem, whose mesh is shown in Fig.~\ref{fig:mesh1D}, is
+\begin{equation}\label{eq:balance}
+J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_g \phi_{i+\hzi,g} = q_{i+\hzi,g},
 \end{equation}
-
-Since these accurate estimates of the currents are based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
-\begin{equation}\label{eq:RM-it}
-D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert} \,\, ,
-\end{equation}
-where $k$ is the iteration index. %The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
-
-The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
-Nevertheless, isotropic scattering remained as a basic postulate.
-For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
-\begin{equation}\label{eq:RM-it-1D-slab}
-D^{(k+1)}(x,E) = -\frac{\frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
-	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
-{\partial \phi^{(k)}(x,E)/\partial x} \,\, .
-\end{equation}
-
-In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration in a simple slab problem.
-They adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
-%
-%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
-%
-This technique can avoid indeterminate divisions in case of vanishing flux gradients.
-It was observed that the RM could drive the flux distribution closer to the transport reference solution.
-As expected, the largest errors were located near the boundary, where the transport effects are most pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
-
-% ------------------------------------------
-\section{Numerical implementation of the Ronen method} 
-\label{sec:RM-num}
-
-The CMFD neutron balance equation for a $\keff$-eigenvalue problem on a one-dimensional mesh, shown in Fig.~\ref{fig:mesh1D}, is
-\begin{equation}\label{eq:balance}
-J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_g \phi_{i+\hzi,g} = q_{i+\hzi,g} \,\, , 
-\end{equation}	
-where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section, the subscript $g$ denotes the energy group, and $q$ is the isotropic neutron source defined as
+where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. The isotropic neutron source $q$ is defined as
 \begin{equation}\label{eq:qsrc}
 q_{i+\hzi,g} = \sum\limits_{g'=1}^G\sigma_{s,0,g\leftarrow g'}\phi_{i+\hzi,g'} +
-\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i+\hzi,g'}\phi_{i+\hzi,g'} \,\, ,
+\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i+\hzi,g'}\phi_{i+\hzi,g'},
 \end{equation}
@@
 % ------------------------------------------
-\subsection{CMFD implementation} 
-\label{sec:RM-CMFD}
-
-% ------------------------------------------
-\subsection{pCMFD implementation} 
+\subsection{pCMFD}
 \label{sec:RM-pCMFD}
@@
 \label{eq:partial-current}
-\jpm (x) \cong \frac{\phi(x)}{4} \pm \frac{\jD (x)}{2} \,\, ,
+\jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{\jD (x)}{2},
 \end{equation}
@@
 %\label{eq:diff-current}
-%\bm{J} (x) = \jp(x) - \jm(x) \,\, .
+%\bm{J} (x) = \jp(x) - \jm(x).
 %\end{equation}
@@
 \jpm _{i+\hzi} = \frac{1}{4}\phi_{i+\hzi}
-\pm \frac{1}{2} \jD _{i+\hzi} \pm \frac{1}{2} \delta \jpm _{i+\hzi} \,\, ,
+\pm \frac{1}{2} \jD _{i+\hzi} \pm \frac{1}{2} \delta \jpm _{i+\hzi},
 \end{equation}
@@
 \label{eq:jdiff}
-\jD _{i+\hzi} = - 2 D_{i+\hzi} \frac{\phi_{i+1} - \phi_i}{\Delta_{i+1}+\Delta_i} 
-\,\,, %\nonumber \\
-D_{i+\hzi} = \frac{\Delta_i D_i + \Delta_{i+1} D_{i+1}}{\Delta_i + \Delta_{i+1}} 
-\,\,, %\nonumber \\
-\phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}} \, .
+\jD _{i+\hzi} = - 2 D_{i+\hzi} \frac{\phi_{i+1} - \phi_i}{\Delta_{i+1}+\Delta_i}, %\nonumber \\
+D_{i+\hzi} = \frac{\Delta_i D_i + \Delta_{i+1} D_{i+1}}{\Delta_i + \Delta_{i+1}}, %\nonumber \\
+\phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}}.
 \end{equation}
@@
 \label{eq:CCF-sub}
-\frac{1}{2} \delta \jp _{i+\hzi} \equiv -\delta D^+ _{i+\hzi} \phi_i \,, 
+\frac{1}{2} \delta \jp _{i+\hzi} \equiv -\delta D^+ _{i+\hzi} \phi_i,
 \quad
-\frac{1}{2} \delta \jm _{i+\hzi} \equiv -\delta D^- _{i+\hzi} \phi_{i+1}\,\, ,
+\frac{1}{2} \delta \jm _{i+\hzi} \equiv -\delta D^- _{i+\hzi} \phi_{i+1},
 \end{equation}
@@
 \jm _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-- \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1} \,\, .
+- \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1}.
 \end{align}
@@
 \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
-	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i} \,, \quad
+	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}, \quad
 \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
-	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}} \,\, .
+	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}}.
 \end{equation}
@@
 \begin{equation}
-J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi} \,\, .
+J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi}.
 \end{equation}
@@
 % ------------------------------------------
-\section*{NOMENCLATURE}
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item RM - Ronen Method
-\item CMFD - Coarse Mesh Finite Difference
-\item pCMFD - partial current CMFD
-\end{itemize}
-
+% Daniele: I would avoid the following section about the nomenclature because of the 8 pages limit. The acronyms are already explained in the text.
+%\section*{NOMENCLATURE}
+%
+%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+%\item RM - Ronen Method
+%\item CMFD - Coarse Mesh Finite Difference
+%\item pCMFD - partial current CMFD
+%\end{itemize}
+%
 % ------------------------------------------
-\section*{ACKNOWLEDGEMENTS}
-
-Acknowledge the help of colleagues and sources of funding, as appropriate.
-
+%\section*{ACKNOWLEDGEMENTS}
+%
+%Acknowledge the help of colleagues and sources of funding, as appropriate.
+%
 % ------------------------------------------

### 2019-11-05 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
updated manuscript and bib file. still no results.

--- 2019-10-30 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
@@
 \usepackage{tabls}
-\usepackage{cites}
+\usepackage{cite}
 \usepackage{epsf}
@@
   %
-  \textbf{Roy Gross$^1$, Daniele Tomatis$^2$, and Erez Gilad$^3$}\footnote{} \\
-  $^1$Name of Institution 1  \\
-  Corresponding Address \\ 
+  \textbf{Roy Gross$^1$, Daniele Tomatis$^2$, and Erez Gilad$^{1,}$}\footnote{Corresponding author} \\
+  $^1$The Unit of Nuclear Engineering \\
+  Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel\\ 
 \\
-  $^2$Name of Institution 2  \\ 
-    Corresponding Address \\ 
+  $^2$CEA, DEN, Service d’\'etudes des r\'eacteurs et
+  de math\'ematiques appliqu\'ees (SERMA) \\
+  Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France \\ 
 \\
-  $^3$Name of Institution 3  \\
-     Corresponding Address \\
-     \\
-  \url{roygross@post.bgu.ac.il}, \url{daniele.tomatis@cea.fr}, \url{gilade@bgu.ac.il}
+  \url{roygros@post.bgu.ac.il}, \url{daniele.tomatis@cea.fr}, \url{gilade@bgu.ac.il}
 }
@@
 \newcommand{\authorHead}      % Author's names here use et al. if more than 3
-           {Roy Gross, Daniele Tomatis, Erez Gilad}  
+           {R. Gross, D. Tomatis, E. Gilad}  
 \newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
-           {INTEGRAL TRANSPORT CORRECTION TO ONE-DIMENSIONAL DIFFUSION CALCULATIONS}  
+           {The Ronen Method by pCMFD}  
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by the accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
+%The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by the accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
 The iterative scheme calculates new flux distribution using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
@@
 % ------------------------------------------
-\subsection{Coarse Mesh Finite Difference (CMFD)} 
-\label{sec:CMFD-intro}
+%\subsection{Coarse Mesh Finite Difference (CMFD)} 
+%\label{sec:CMFD-intro}
 
@@
 % ------------------------------------------
-\section{The Ronen method} 
+\section{THE RONEN METHOD} 
 \label{sec:RM}
@@
 In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
+Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}^D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
 \begin{equation}\label{eq:Fick}
@@
 	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
-{\partial \phi^{(k)}(x,E)/\partial x} \,\, .
+{\partial \phi^{(k)}(x,E)/\partial x} \,\, ,
 \end{equation}
+where the source term $q^{(k)}(x',E)$ is calculated using the multigroup diffusion model with available diffusion coefficients, and the updated diffusion coefficients $D^{(k+1)}(x,E)$ are evaluated using the integral expression for the transport current.
 
@@
 % ------------------------------------------
-\section{Numerical implementation of the Ronen method} 
+\section{NUMERICAL IMPLEMENTATION} 
 \label{sec:RM-num}
@@
 \begin{equation}\label{eq:balance}
-J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_g \phi_{i+\hzi,g} = q_{i+\hzi,g} \,\, , 
+J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g} \,\, , 
 \end{equation}	
@@
 \begin{equation}\label{eq:qsrc}
-q_{i+\hzi,g} = \sum\limits_{g'=1}^G\sigma_{s,0,g\leftarrow g'}\phi_{i+\hzi,g'} +
-\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i+\hzi,g'}\phi_{i+\hzi,g'} \,\, ,
+q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
+\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} \,\, ,
 \end{equation}	
@@
 
-	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-3/2$};
+	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-\sfrac{3}{2}$};
 	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
@@
 
+The accurate net current and partial current in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
+\begin{align}\label{eq:par-curr-calc}
+\jp_{i+\hzi,g} &=  \frac{1}{2}
+E_3[\mcL_g(x_{-\hzi},x_{i+\hzi})] \phi_{x_{-\hzi},g} \nonumber \\
+&+
+\frac{1}{2}\sum\limits_{j=0}^i \frac{q_{j,g}}{\sigma_{j,g}}
+\left\{ 
+E_3\left[
+\mcL_g(x_{j+\hzi},x_{i+\hzi}) 
+\right]
+- E_3\left[
+\mcL_g(x_{j-\hzi},x_{i+\hzi})
+\right] 
+\right\} 
+\nonumber \\
+\jm_{i+\hzi,g} &=  \frac{1}{2}
+E_3[\mcL_g(x_{i+\hzi},x_{I-\hzi})] \phi_{x_{I-\hzi},g} \nonumber \\
+&+
+\frac{1}{2}\sum\limits_{j=i+1}^{I-1} \frac{q_{j,g}}{\sigma_{j,g}}
+\left\{ 
+E_3\left[
+\mcL_g(x_{i+\hzi},x_{j-\hzi}) 
+\right]
+- E_3\left[ 
+\mcL_g(x_{i+\hzi},x_{j+\hzi})
+\right] 
+\right\} \,\, ,
+\end{align}
+where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$.
+
 % ------------------------------------------
-\subsection{CMFD implementation} 
+\subsection{CMFD IMPLEMENTATION} 
 \label{sec:RM-CMFD}
 
+In standard CMFD implementation, correction terms, e.g., $\delta J_{i+\hzi,g}$, are added to the diffusion current $\jD_{i+\hzi,g}$, such that it is driven towards the accurate net current $J_{i+\hzi,g}$.
+The accurate net current is calculated by the integral expression given in~Eq.~\ref{eq:par-curr-calc} and using the scalar flux for evaluating the emission source $q_{i,g}$.
+The diffusion current is evaluated according to
+\begin{equation}\label{eq:JD}
+\jD_{i+\hzi,g} \cong -D_{i+\hzi,g} 
+\frac{\phi_{i+1,g} - \phi_{i,g}}
+{(\Delta_{i+1} + \Delta_i)/2} \,\, ,
+\end{equation}
+where integer and rational subscripts indicate node-averaged and interface quantities, respectively, and 
+\begin{equation}\label{eq:Ds}
+D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
+{\Delta_i + \Delta_{i+1}} \, \, .
+\end{equation}
+%
+Once the accurate net current and the diffusion current are calculated using the most recent flux values, the correction terms on cell interfaces can be calculated.
+The discretized form of the current $\delta J_{i+\hzi,g}$ must involve the neighboring flux as well, but its representation is changed into a drift-advection term to avoid of possible undefined division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}
+\begin{equation}
+\delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g} 
+\frac{\phi_{i+1,g} + \phi_{i,g}}
+{(\Delta_{i+1} + \Delta_i)/2} 
+= J_{i+\hzi,g} - \jD_{i+\hzi,g}
+\,\, .
+\end{equation}
+
 % ------------------------------------------
-\subsection{pCMFD implementation} 
+\subsection{pCMFD IMPLEMENTATION} 
 \label{sec:RM-pCMFD}
@@
 \label{eq:jdiff}
-\jD _{i+\hzi} = - 2 D_{i+\hzi} \frac{\phi_{i+1} - \phi_i}{\Delta_{i+1}+\Delta_i} 
-\,\,, %\nonumber \\
-D_{i+\hzi} = \frac{\Delta_i D_i + \Delta_{i+1} D_{i+1}}{\Delta_i + \Delta_{i+1}} 
-\,\,, %\nonumber \\
 \phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}} \, .
@@
 % ------------------------------------------
-\section{Results} 
+\section{RESULTS} 
 \label{sec:res}

### 2019-11-05 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex

@@
 \usepackage{tabls}
-\usepackage{cite}
+\usepackage{cites}
 \usepackage{epsf}
@@
 \newcommand{\sxn}[1]{Section~\ref{#1}}
+%
+% \newcommand{\revised}[1]{{\color{red}{#1}}}
+% \newcommand{\tsup}[1]{\textsuperscript{#1}}
+% \newcommand{\tsub}[1]{\textsubscript{#1}}
+%
+\newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
+\newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
+\newcommand{\rr}{\ensuremath{\bm{r}}}
+\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
+\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
+\newcommand{\rE}{\ensuremath{(\rr,E)}}
 
-\newcommand{\revised}[1]{{\color{red}{#1}}}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsubscript{#1}}
+\newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
+\newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
+\newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
+%\newcommand{\mcL}{\mathcal{L}}
+\newcommand{\mcL}{\tau}
+\newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
+\newcommand{\dx}{\ensuremath{\Delta x}}
+%
+\newcommand{\jp}{\ensuremath{\bm{J}^+}}
+\newcommand{\jm}{\ensuremath{\bm{J}^-}}
+\newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
+\newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
 
+\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
+
+% about notes and comments from each author
 \newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
 \newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
+\newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
 
@@
   $^1$The Unit of Nuclear Engineering \\
-  Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel\\ 
+  Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\ 
 \\
   $^2$CEA, DEN, Service d’\'etudes des r\'eacteurs et
-  de math\'ematiques appliqu\'ees (SERMA) \\
+      de math\'ematiques appliqu\'ees (SERMA), \\
     Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France \\
      \\
-  \url{roygros@post.bgu.ac.il}, \url{daniele.tomatis@cea.fr}, \url{gilade@bgu.ac.il}
+  \url{roygros@post.bgu.ac.il},
+  \url{daniele.tomatis@cea.fr},
+  \url{gilade@bgu.ac.il}
 }
@@
 \newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
-           {The Ronen Method by pCMFD}  
+           {INTEGRAL TRANSPORT CORRECTION TO 1-D DIFFUSION CALCULATIONS by pCMFD}
+%          {The Ronen Method by pCMFD}  % Daniele's suggestion (shorter)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{abstract}
-\keywords{neutron diffusion ; integral transport ; non-linear transport correction ;
-CMFD ; pCMFD }
+\keywords{neutron diffusion, integral transport, non-linear transport correction, CMFD, pCMFD}
+% Daniele suggestion:
+% I would not include pCMFD since it belongs to the CMFD class of methods and shorten the list of keywords
 
@@
 \begin{equation}\label{eq:Fick}
-\bm{J}^D\rE = -D\rE\bnabla\phi\rE = \bm{J}\rE \,\, . 
+\bm{J}^D\rE = -D\rE\bnabla\phi\rE = \bm{J}\rE. 
 \end{equation}
@@
 \begin{equation}\label{eq:RM-it}
-D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert} \,\, ,
+D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert},
 \end{equation}
@@
 	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
-{\partial \phi^{(k)}(x,E)/\partial x} \,\, ,
+{\partial \phi^{(k)}(x,E)/\partial x},
 \end{equation}
@@
 \begin{equation}\label{eq:balance}
-J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g} \,\, , 
+J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g}, 
 \end{equation}	
@@
 q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
-\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} \,\, ,
+\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'},
 \end{equation}	
@@
 \frac{\phi_{i+1,g} - \phi_{i,g}}
-{(\Delta_{i+1} + \Delta_i)/2} \,\, ,
+{(\Delta_{i+1} + \Delta_i)/2},
 \end{equation}
@@
 D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
-{\Delta_i + \Delta_{i+1}} \, \, .
+{\Delta_i + \Delta_{i+1}}.
 \end{equation}
@@
 {(\Delta_{i+1} + \Delta_i)/2} 
-= J_{i+\hzi,g} - \jD_{i+\hzi,g}
-\,\, .
+= J_{i+\hzi,g} - \jD_{i+\hzi,g}.
 \end{equation}
@@
 \label{eq:jdiff}
-\phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}} \, .
+\phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}}.
 \end{equation}
@@
 \label{eq:CCF-sub}
-\frac{1}{2} \delta \jp _{i+\hzi} \equiv -\delta D^+ _{i+\hzi} \phi_i \,, 
+\frac{1}{2} \delta \jp _{i+\hzi} \equiv -\delta D^+ _{i+\hzi} \phi_i
 \quad
-\frac{1}{2} \delta \jm _{i+\hzi} \equiv -\delta D^- _{i+\hzi} \phi_{i+1}\,\, ,
+\frac{1}{2} \delta \jm _{i+\hzi} \equiv -\delta D^- _{i+\hzi} \phi_{i+1},
 \end{equation}

### 2019-11-06 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex

--- 2019-11-05 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
@@
 \newcommand{\dx}{\ensuremath{\Delta x}}
-%
-\newcommand{\jp}{\ensuremath{\bm{J}^+}}
-\newcommand{\jm}{\ensuremath{\bm{J}^-}}
-\newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
-\newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
+
+\newcommand{\jp}{\ensuremath{J^+}}
+\newcommand{\jm}{\ensuremath{J^-}}
+\newcommand{\jpm}{\ensuremath{J^\pm}}
+\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
+\newcommand{\bmj}{\ensuremath{\bm{J}}}
+% \newcommand{\jp}{\ensuremath{\bm{J}^+}}
+% \newcommand{\jm}{\ensuremath{\bm{J}^-}}
+% \newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
+% \newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
 
@@
 % \title{INTEGRAL TRANSPORT CORRECTION \\TO DIFFUSION CALCULATIONS BY pCMFD}
-\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\USING THE pCMFD SCHEME}
+\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\
+       USING THE pCMFD SCHEME}
 %
@@
   %
-  \textbf{Roy Gross$^1$\footnote{Corresponding author: xxx.},
-          Daniele Tomatis$^2$,
-          and Erez Gilad$^1$} \\
-  $^1$The Unit of Nuclear Engineering, \\
+  \textbf{Roy Gross$^1$\footnote{Corresponding author.},
+          Daniele Tomatis$^2$, and Erez Gilad$^{1,}$} \\
+  $^1$The Unit of Nuclear Engineering \\
   Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\
@@
 \\
-  \url{roygross@post.bgu.ac.il},
+  \url{roygros@post.bgu.ac.il},
   \url{daniele.tomatis@cea.fr},
@@
 \newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
-           {INTEGRAL TRANSPORT CORRECTION TO 1-D DIFFUSION CALCULATIONS by pCMFD}
-%          {The Ronen Method by pCMFD}  % Daniele's suggestion (shorter)
+%           {INTEGRAL TRANSPORT CORRECTION TO 1-D DIFFUSION CALCULATIONS by pCMFD}
+           {The Ronen Method by pCMFD}  % Daniele's suggestion (shorter)
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
-Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new methods for accelerating the convergence are reported.
-For example, the use of the integral flux intermediate values as new boundary conditions in each iteration and iterative updating of the extrapolated boundary using the corrected local diffusion coefficients.
+Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new techniques for accelerating the convergence are investigated.
+For example, we use integral flux intermediate values as new boundary conditions at each iteration and we update iteratively the extrapolated boundary using the corrected local diffusion coefficient.
 Moreover, the pCMFD scheme is implemented and its performances are compared with those of standard CMFD scheme.
 \end{abstract}
-\keywords{neutron diffusion, integral transport, non-linear transport correction, CMFD}
+\keywords{neutron diffusion, integral transport, non-linear transport correction, CMFD, pCMFD}
 % Daniele suggestion:
@@
 To overcome this difficulty, faster (but less accurate) multigroup neutron diffusion solvers are often used.
-However, future Gen-IV reactor designs are characterized by strong heterogeneity in the core and modern calculation schemes evolve towards best-estimate codes, aiming at high accuracy.
+Indeed, future Gen-IV reactor designs are characterized by strong heterogeneity in the core and modern calculation schemes evolve towards best-estimate codes, aiming at high accuracy for these new configurations.
 Hence, the accuracy of diffusion calculations is investigated.
 A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient.
-The calculation of this parameter should be based on physical insights from the full transport equation such that the resulting (transport corrected) diffusion approximation can capture the transport phenomena of interest.
+The calculation of this parameter should be based on physical insights from the full transport equation, such that the resulting (transport-corrected) diffusion approximation can capture the transport phenomena of interest.
 
-The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by the accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
-The iterative scheme calculates new flux distribution using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
-However, the direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning.
+% Daniele: I found this paragraph commented, but I think that the two following sections should be properly introduced in this section. Therefore, I am uncommenting it.
+The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
+The iterative scheme calculates new flux distributions using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
+Alternatively, the Coarse Mesh Finite Differences (CMFD) scheme can be enforced in the discretized form of the diffusion equation to reproduce the transport current by means of a drift term.
+The implementation of one its variants, the partial current formulation of the CMFD (pCMFD), is studied in this work.
+%
+% The direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning.
 Nonetheless, the integral current can be enforced in the Coarse Mesh Finite Difference (CMFD) discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients.
@@
 
+\daniele{Shall we keep the current order of sections or exchange sec. 2 with sec. 3?}
 % ------------------------------------------
-%\subsection{Coarse Mesh Finite Difference (CMFD)}
-%\label{sec:CMFD-intro}
-% the content of this section was moved in the section about the implementation
-%
-%
-% ------------------------------------------
-\section{THE RONEN METHOD}
-\label{sec:RM}
+\subsection{COARSE MESH FINITE DIFFERENCES}
+\label{sec:CMFD-intro}
 
-In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
-\begin{equation}\label{eq:Fick}
-\bm{J}^D\rE = -D\rE\bnabla\phi\rE = \bm{J}\rE.
-\end{equation}
-
-Since these accurate estimates of the currents are based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
-\begin{equation}\label{eq:RM-it}
-D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert},
-\end{equation}
-where $k$ is the iteration index. %The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
-
-The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
-Nevertheless, isotropic scattering remained as a basic postulate.
-For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
-\begin{equation}\label{eq:RM-it-1D-slab}
-D^{(k+1)}(x,E) = -\frac{\frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
-	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
-{\partial \phi^{(k)}(x,E)/\partial x}.
-\end{equation}
-
-In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration in a simple slab problem.
-They adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
-%
-%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
-%
-This technique can avoid indeterminate divisions in case of vanishing flux gradients.
-It was observed that the RM could drive the flux distribution closer to the transport reference solution.
-As expected, the largest errors were located near the boundary, where the transport effects are most pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
-
-% ------------------------------------------
-\section{NUMERICAL IMPLEMENTATION}
-\label{sec:RM-num}
-
-The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing the separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
+The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing for separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
 Recently, multi-dimensional transport codes have used it as acceleration technique and the convergence of different implementations was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
@@
 Second-order SPN equations can be solved by ordinary diffusion codes~\cite{Larsen-1993}.
-Yamamoto et al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
+Yamamoto et Al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
 This is because this quantity is generally smaller than the scalar flux (0-th moment) and can change its sign.
-They propose to modify the balance equation for the second moment in order to fix this numerical behavior.
-The modification consists of a shift with a positive quantity of the second moment so that their difference between neighboring quantities is unchanged, and their sum becomes positive and arbitrarily large.
+They proposed to modify the balance equation for the second moment in order to fix this numerical behavior.
+The modification consisted of a shift with a positive quantity of the second moment so that their difference between neighboring quantities is unchanged, and their sum becomes positive and arbitrarily large.
 
-In case partial currents can be computed, the pCMFD method~\cite{Cho-2003} can be used to determine two distinct corrective terms per positive and negative partial currents, instead of having a single degree of freedom per cell surface.
+When partial currents can be computed, the pCMFD method~\cite{Cho-2003} can be used to determine two distinct corrective terms per positive and negative partial currents, instead of having a single degree of freedom per cell surface.
 Another version of the CMFD called artificial diffusion~\cite{Zhu-2016,Jarrett-2016} redefines the diffusion coefficient as the sum of the original value and a complement derived from the current difference, which is still considered as proportional to the flux gradient.
@@
 The CMFD (and its variants) was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
-Contrary to the previous implementations, no operator was inverted to get a new higher order solution of the flux.
-This offers indeed a fast estimate of the higher order current.
+Contrary to the previous implementations, no operator was inverted to get a new higher order approximation of the flux solution.
+As well, this offered a fast and more accurate estimate of the current too.
 
 % ------------------------------------------
-\subsection{CMFD}
-\label{sec:RM-CMFD}
+\section{THE RONEN METHOD}
+\label{sec:RM}
 
-The CMFD neutron balance equation for a $\keff$-eigenvalue problem in a one-dimensional slab problem, whose mesh is shown in Fig.~\ref{fig:mesh1D}, is
-\begin{equation}\label{eq:balance}
-J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_g \phi_{i+\hzi,g} = q_{i+\hzi,g},
+In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux was resolved by diffusion theory.
+Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}^D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
+\begin{equation}
+  \label{eq:Fick}
+  \bm{J}^D\rE = -D\rE\bnabla\phi\rE \cong \bm{J}\rE.
 \end{equation}
-where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. The isotropic neutron source $q$ is defined as
-\begin{equation}\label{eq:qsrc}
-q_{i+\hzi,g} = \sum\limits_{g'=1}^G\sigma_{s,0,g\leftarrow g'}\phi_{i+\hzi,g'} +
-\frac{\chi_g}{2\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i+\hzi,g'}\phi_{i+\hzi,g'},
+
+Since these accurate estimates of the currents were based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
+\begin{equation}
+  \label{eq:RM-it}
+  D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE \rvert}{\lvert \bnabla \phi^{(k)}\rE \rvert},
 \end{equation}
-where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the eigenvalue, $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
+where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
 
-\begin{figure}[htbp!]
+The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
+Nevertheless, isotropic scattering remained as a basic postulate.
+For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
+\begin{equation}
+  \label{eq:RM-it-1D-slab}
+  D^{(k+1)}(x,E) = \left. -\frac{1}{2} \int_0^a dx'
+    {E_2[\sigma(E) \lvert x-x' \rvert]\operatorname{sign}(x-x')q^{(k)}(x',E)}
+    \middle/ \frac{\partial}{\partial x}\phi^{(k)}(x,E),\right.
+\end{equation}
+where the source term $q^{(k)}$ is calculated using the multigroup diffusion model with the available scalar flux, and the updated diffusion coefficient $D^{(k+1)}$ is evaluated using the integral expression for the transport current.
+
+In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration of the simple slab problem.
+They chose the CMFD scheme in the diffusion solver for taking into account the new currents estimated by the integral transport operator.
+%
+%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
+%
+This technique can avoid indeterminate divisions in case of vanishing flux gradients and reproduces the transport effects under a drift term.
+It was observed that the RM could drive the flux distribution closer to the transport reference solution.
+As expected, the largest errors were located near the boundary, where the transport effects are more pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
+
+% ------------------------------------------
+\section{NUMERICAL IMPLEMENTATION}
+\label{sec:RM-num}
+
+The neutron balance equation for a $k$-eigenvalue problem integrated in the $i$-th element of a one-dimensional mesh is (see Fig.~\ref{fig:mesh1D})
+\begin{equation}
+  \label{eq:balance}
+  J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
+\end{equation}
+where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
+\begin{equation}
+  \label{eq:qsrc}
+  q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
+  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'},
+\end{equation}
+where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the effective multiplication factor (the eigenvalue), $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
+As well, integer and rational subscripts indicate node-averaged and interface quantities, respectively.
+%
+\begin{figure}[htbp]
 	\centering
-	\begin{tikzpicture}
-	\tikzstyle{every node}=[font=\footnotesize]
-	\draw[thick] (0,0) -- (3,0);
-	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
-	\draw[thick] (4,0) -- (7,0);
-	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
-	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};
-
-	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-\hzi$};
-	\node[anchor=south] at (1cm,1pt) {0};
-	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+\hzi$};
-
-	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-\hzi$};
-	\node[anchor=south] at (5.5cm,1pt) {$i$};
-	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+\hzi$};
-
-	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-3/2$};
-	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
-	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-\hzi$};
-	\end{tikzpicture}
+  \input{figures/mesh1D.tikz}
 	\caption{Notation of the one-dimensional mesh.}
@@
 
+The accurate net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
+\begin{subequations}
+  \label{eq:par-curr-calc}
+  \begin{equation}
+    \label{eq:par-curr-calc-plus}
+    \begin{split}
+      \jp_{i+\hzi,g} &=  \frac{1}{2}
+        E_3[\mcL_g(x_{-\hzi},x_{i+\hzi})] \phi_{x_{-\hzi},g} \\
+        & + \frac{1}{2}\sum\limits_{j=0}^i \frac{q_{j,g}}{\sigma_{j,g}}
+            \left\{ E_3\left[ \mcL_g(x_{j+\hzi},x_{i+\hzi}) \right]
+                  - E_3\left[ \mcL_g(x_{j-\hzi},x_{i+\hzi}) \right]
+            \right\}
+    \end{split}
+  \end{equation}
+  %
+  \begin{equation}
+    \begin{split}
+      \label{eq:par-curr-calc-minus}
+      \jm_{i+\hzi,g} &=  \frac{1}{2}
+        E_3[\mcL_g(x_{i+\hzi},x_{I-\hzi})] \phi_{x_{I-\hzi},g} \\
+        & + \frac{1}{2}\sum\limits_{j=i+1}^{I-1} \frac{q_{j,g}}{\sigma_{j,g}}
+            \left\{ E_3\left[ \mcL_g(x_{i+\hzi},x_{j-\hzi}) \right]
+                  - E_3\left[ \mcL_g(x_{i+\hzi},x_{j+\hzi}) \right]
+            \right\},
+    \end{split}
+  \end{equation}
+where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$.
+\end{subequations}
+
+\daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
+
 % ------------------------------------------
-\subsection{pCMFD}
+\subsection{CMFD IMPLEMENTATION}
+\label{sec:RM-CMFD}
+
+In standard CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
+Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime.
+Besides, the net current can be determined from some other expression which is physically or numerically more accurate.
+Therefore, this new term acts as a correction for the diffusion current.
+The diffusion current is generally approximated by finite differences according to
+\begin{equation}
+  \label{eq:JD}
+  \jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
+    \frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
+\end{equation}
+where the diffusion coefficient at the interface is volume-averaged as
+\begin{equation}
+  \label{eq:Ds}
+  D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
+{\Delta_i + \Delta_{i+1}}.
+\end{equation}
+%
+About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
+Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
+The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
+\begin{equation}
+  \label{eq:dJ}
+  \delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
+    \frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
+  J_{i+\hzi,g} - \jD_{i+\hzi,g}.
+\end{equation}
+The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
+Boundary conditions applies as usual on the diffusion current and on the net (more accurate) current, without any particular change for the definition of the correction term.
+
+\daniele{Although I have used drift-advection many times, somebody may argue that this is not the correct word because advection is often related to a term depending on the first derivative of the unknown.
+It is not the case here.
+One can note however that in heat transfer it is possible find convection terms whose derivative is replaced by a finite difference with a bulk quantity.
+Under that approximation, one recovers our term by a change of variable.
+So, I let you choose the most appropriate word, and if asked, I'll know my answer anyway.}
+
+% ------------------------------------------
+\subsection{pCMFD IMPLEMENTATION}
 \label{sec:RM-pCMFD}
 
-The partial currents in any point $x$ in a slab are defined according to
+The CMFD introduces a free parameter in the numerical scheme through the correction term to adjust the diffusive solution locally.
+Since separate calculations of the partial currents are possible, two free parameters could be used in the discretized form of the diffusion equation.
+
+Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
 \begin{equation}
 \label{eq:partial-current}
-\jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{\jD (x)}{2},
+\jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
 \end{equation}
-where $\jD$ denotes the diffusion current.
+still verifying the expression for the net current $J = J^+ - J^-$.
+% Daniele: the 1st moment is the scalar current and not its diffusion approx
+%where $\jD$ denotes the diffusion current.
 %where
@@
 %\end{equation}
-The partial currents correction factors are defined on cell surface according to
+\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
 \begin{equation}
   \label{eq:PCCF}
-\jpm _{i+\hzi} = \frac{1}{4}\phi_{i+\hzi}
-\pm \frac{1}{2} \jD _{i+\hzi} \pm \frac{1}{2} \delta \jpm _{i+\hzi},
+  \jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
+    \left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
 \end{equation}
-where
-\begin{equation}
-\label{eq:jdiff}
-\jD _{i+\hzi} = - 2 D_{i+\hzi} \frac{\phi_{i+1} - \phi_i}{\Delta_{i+1}+\Delta_i}, %\nonumber \\
-D_{i+\hzi} = \frac{\Delta_i D_i + \Delta_{i+1} D_{i+1}}{\Delta_i + \Delta_{i+1}}, %\nonumber \\
-\phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}{\Delta_i + \Delta_{i+1}}.
-\end{equation}
-Substituting~\cite{Jarrett-2016,Zhu-2016}
+and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
 \begin{equation}
 \label{eq:CCF-sub}
-\frac{1}{2} \delta \jp _{i+\hzi} \equiv -\delta D^+ _{i+\hzi} \phi_i,
-\quad
-\frac{1}{2} \delta \jm _{i+\hzi} \equiv -\delta D^- _{i+\hzi} \phi_{i+1},
+\delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
+\quad \text{and} \quad
+\delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
 \end{equation}
-yields
-\begin{align}
-\label{eq:par4}
-\jp _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-+ \frac{1}{2}\jD _{i+\hzi} - \delta D^+ _{i+\hzi} \phi_i \\
-\jm _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-- \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1}.
-\end{align}
+% yields
+% \begin{align}
+% \label{eq:par4}
+% \jp _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
+% + \frac{1}{2}\jD _{i+\hzi} - \delta D^+ _{i+\hzi} \phi_i \\
+% \jm _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
+% - \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1}.
+% \end{align}
 %Recall that $\jpm$ are calculated using the integral expression.
@@
   \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
-	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}, \quad
+  	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
+  \quad \text{and} \quad
   \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
-	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}}.
+  	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
   \end{equation}
+where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.
+% \begin{equation}
+%   \label{eq:jdiff}
+%   \phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}
+%                        {\Delta_i + \Delta_{i+1}}.
+% \end{equation}
 
-In case the diffusion current is accurate, e.g., in a weak absorbing medium and several mfp's from the boundary or a strong absorber, the correction factors $\delta D^\pm$ vanish and~\eq{eq:ccfsss1} reduces to~\eq{eq:partial-current}, as expected, which implies for the net (accurate) current
-\begin{equation}
-J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi}.
-\end{equation}
+In a weakly absorbing medium and several mean free paths away from the boundary or a strong absorber, all correction factors $\delta D^\pm$ are expected to vanish and the net current must be fully reproduced by the diffusion current.% and~\eq{eq:ccfsss1} reduces to~\eq{eq:partial-current}, as expected, which implies for the net (accurate) current
+% \begin{equation}
+% J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi}.
+% \end{equation}
 

### 2019-11-06 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
Amend mistaken comment
Daniele: I removed a confusing comment.

@@
 
-\daniele{Although I have used drift-advection many times, somebody may argue that this is not the correct word because advection is often related to a term depending on the first derivative of the unknown.
-It is not the case here.
-One can note however that in heat transfer it is possible find convection terms whose derivative is replaced by a finite difference with a bulk quantity.
-Under that approximation, one recovers our term by a change of variable.
-So, I let you choose the most appropriate word, and if asked, I'll know my answer anyway.}
-
 % ------------------------------------------

### 2019-11-08 FD1dMGdiff/FDsDiff1D.py
Start of code upgrade
Initial proposal of code upgrade with comments in the code requesting the developments.

@@ -12,6 +12,9 @@ If it is zero, we have the zero flux b.c., while reflection is reproduced
 by $\zeta \rightarrow \infty$. The b.c. code is in order 0, 1 and 2,
 respectively.
 
+The Ronen Method is implemented on top of the diffusion solver through
+the standard CMFD or the pCMFD version.
+
 The Cartesian (slab) is the default geometry option. Curvilinears can be
 chosen by selecting 'cylindrical' or 'spherical' for the global variable
 geometry_type.
@@ -28,7 +31,7 @@ from scipy.special import expn as En
 __title__ = "Multigroup diffusion in 1D slab by finite differences"
 __author__ = "D. Tomatis"
 __date__ = "02/04/2019"
-__version__ = "1.1.0"
+__version__ = "1.2.0"
 
 max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
@@ -37,6 +40,7 @@ np.set_printoptions(precision=5)
 # possible options of geometry_type are slab, cylindrical, spherical
 geometry_type = "slab"
 fix_reflection_by_flx2 = True
+pCMFD = False  # disabled as default option
 
 
 def get_zeta(bc=0, D=None):
@@ -133,7 +137,13 @@ def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
     # take into account the delta-diffusion-coefficients
     if dD is None:
         dD = np.zeros((G, I+1),)
-    elif dD.shape != (G, I+1):
+    elif dD.shape == (G, I+1):
+        lg.debug('Apply corrections according to classic CMFD.')
+        # copy values to \pm terms in order to use the same implemntation
+        dD = np.concatenate((dD[:, np.newaxis], dD[:, np.newaxis]), axis=2)
+    elif dD.shape == (G, I+1, 2):
+        lg.debug('Apply corrections according to pCMFD.')
+    else:
         raise ValueError('Unexpected shape for the delta D coefficients.')
 
     # determine the diffusion coefficient on the cell borders
@@ -156,6 +166,7 @@ def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
     # print('coeffs from diffusion')
     # print (d.reshape(G,I-1))
     # print(dD)
+    # Daniele: change dD hereafter by adding the correct value of the third index 
     for g in range(G):
[…]

### 2019-11-09 FD1dMGdiff/FDsDiff1D.py
pCMFD implementation - not complete.
1) compute_tran_currents was changed so it returns both net and partial currents. In order to avoid complications with the corrections of the reflective BC (LBC=2), I use full slab with LBC=RBC=0. After the physor paper we can finish the partial currnets w/ reflective BC.
2) compute_delta_D was duplicated for two cases: CMFD (original) and pCMFD. The different dD which is returned is different not only in its formoula, but also in its dimensions. After the physor paper we can develop a more sofisticated single dD.
3) compute_delta_diff_currents was duplicat

@@ -37,11 +37,6 @@ max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
 np.set_printoptions(precision=5)
 
-# possible options of geometry_type are slab, cylindrical, spherical
-geometry_type = "slab"
-fix_reflection_by_flx2 = True
-pCMFD = False  # disabled as default option
-
 
 def get_zeta(bc=0, D=None):
     "Yield the zeta boundary condition according to the input bc code"
@@ -111,19 +106,19 @@ def compute_cell_volumes(xi, geo=geometry_type):
     return Di
 
 
-def vol_averaged_at_interface(D, Vi):
+def vol_averaged_at_interface(f, Vi):
     "Compute surface quantities by volume averaging (slab geometry)."
-    G, I = D.shape
+    G, I = f.shape
     Im1 = I - 1
 
-    # Db, diff. coeff. on cell borders
-    Db = (D[:,1: ] * np.tile(Vi[1: ], G).reshape(G, Im1) +
-          D[:,:-1] * np.tile(Vi[:-1], G).reshape(G, Im1))
-    Db /= np.tile(Vi[1:] + Vi[:-1], G).reshape(G, Im1)
+    # fb, volume-average quantity on cell borders
+    fb = (f[:,1: ] * np.tile(Vi[1: ], G).reshape(G, Im1) +
+          f[:,:-1] * np.tile(Vi[:-1], G).reshape(G, Im1))
+    fb /= np.tile(Vi[1:] + Vi[:-1], G).reshape(G, Im1)
     # Db = np.zeros((G, I-1),)
     # for g in range(G):
     #     Db[g,:] = (D[g,1:] * Vi[1:] + D[g,:-1] * Vi[:-1]) / Dm
-    return Db
+    return fb
 
 
 def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
@@ -140,7 +135,7 @@ def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
     elif dD.shape == (G, I+1):
         lg.debug('Apply corrections according to classic CMFD.')
         # copy values to \pm terms in order to use the same implemntation
-        dD = np.concatenate((dD[:, np.newaxis], dD[:, np.newaxis]), axis=2)
+        #dD = np.concatenate((dD[:, np.newaxis], dD[:, np.newaxis]), axis=2)
     elif dD.shape == (G, I+1, 2):
         lg.debug('Apply corrections according to pCMFD.')
     else:
[…]

### 2019-11-09 FD1dMGdiff/data2Ghomog.py

@@ -22,16 +22,32 @@ chi = np.array([1., 0.])
 D = one_third / (st - np.sum(ss1, axis=1))
 
 # set b.c.
-LBC, RBC = 2, 0
+LBC, RBC = 0, 0
+# pack the b.c. identifiers
+BC = LBC, RBC
 
 # definition of the spatial mesh
-L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
-I = 6  # nb of spatial cells
+L = 21.5  # slab width, equal to half pitch of a fuel assembly
+I = 8  # nb of spatial cells
 G = st.size  # nb of energy groups
 xi = np.linspace(0, L, I+1)  # equidistant mesh
-xim = lambda x: (x[1:] + x[:-1]) / 2. # mid-points
+#xim = lambda x: (x[1:] + x[:-1]) / 2. # mid-points
 
-geometry_type = 'cylindrical'
+# tolerance on the fission rates during outer iterations
+ritmax = 5  # set to 1 to skip the Ronen iterations
+toll = 1.e-6
+oitmax = 100  # max nb of outer iterations
+iitmax = 100  # max nb of inner iterations
+itsmax = oitmax, iitmax
+
+# choose the type of CMFD scheme
+pCMFD = True  # classic CMFD scheme is False
+
+# choose geometry
+geometry_type = 'slab' # 'cylindrical'/'spherical'
+
+# reflective BC fix
+fix_reflection_by_flx2 = True
 
 
 if __name__ == "__main__":

### 2019-11-10 FD1dMGdiff/FDsDiff1D.py
pCMFD is implemented. Still bugs to find.
Ronen iterations diverge for I > 10. Probably forgotten/extra Di

@@ -27,6 +27,10 @@ import sys
 import logging as lg
 import numpy as np
 from scipy.special import expn as En
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+
+from data2Ghomog import *
 
 __title__ = "Multigroup diffusion in 1D slab by finite differences"
 __author__ = "D. Tomatis"
@@ -131,21 +135,25 @@ def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
 
     # take into account the delta-diffusion-coefficients
     if dD is None:
-        dD = np.zeros((G, I+1),)
-    elif dD.shape == (G, I+1):
+        if pCMFD:
+            dD = np.zeros((G, I+1,2))
+        else:
+            dD = np.zeros((G, I+1))
+            
+    if dD.shape == (G, I+1):
         lg.debug('Apply corrections according to classic CMFD.')
-        # copy values to \pm terms in order to use the same implemntation
-        #dD = np.concatenate((dD[:, np.newaxis], dD[:, np.newaxis]), axis=2)
     elif dD.shape == (G, I+1, 2):
         lg.debug('Apply corrections according to pCMFD.')
+        dDp = dD[:,:,0]
+        dDm = dD[:,:,1]
     else:
         raise ValueError('Unexpected shape for the delta D coefficients.')
 
-    # determine the diffusion coefficient on the cell borders
+    # determine the diffusion coefficient on the cell borders - w/o boundaries
     Db = vol_averaged_at_interface(D, Vi)
 
     # compute the coupling coefficients by finite differences
-    iDm = 2. / (Di[1:] + Di[:-1])
+    iDm = 2. / (Di[1:] + Di[:-1]) # 1/(\Delta_i + \Delta_{i+1})/2
     # iDm = 2. / (Vi[2:] + Vi[:-2])
     xb0, xba = 1., 1.
     if geo == 'cylindrical':
@@ -157,30 +165,55 @@ def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
         dD *= xi**2
         xb0, xba = xi[0]**2, xi[-1]**2
 
+    # d = D_{i+1/2}/(\Delta_i + \Delta_{i+1})/2
     d = Db.flatten() * np.tile(iDm, G)
+    
     # print('coeffs from diffusion')
[…]

### 2019-11-10 FD1dMGdiff/data2Ghomog.py

@@ -28,15 +28,16 @@ BC = LBC, RBC
 
 # definition of the spatial mesh
 L = 21.5  # slab width, equal to half pitch of a fuel assembly
-I = 8  # nb of spatial cells
+I = 10  # nb of spatial cells
 G = st.size  # nb of energy groups
 xi = np.linspace(0, L, I+1)  # equidistant mesh
+xm = (xi[1:] + xi[:-1]) / 2. # mid-points
 #xim = lambda x: (x[1:] + x[:-1]) / 2. # mid-points
 
 # tolerance on the fission rates during outer iterations
-ritmax = 5  # set to 1 to skip the Ronen iterations
+ritmax = 50  # set to 1 to skip the Ronen iterations
 toll = 1.e-6
-oitmax = 100  # max nb of outer iterations
+oitmax = 50  # max nb of outer iterations
 iitmax = 100  # max nb of inner iterations
 itsmax = oitmax, iitmax
 

### 2019-11-12 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
Updated version with Daniele's comment accepted.
still no results.
Fix authors
Small fix to authors in titlepage.

@@
   \textbf{Roy Gross$^1$\footnote{Corresponding author.},
-          Daniele Tomatis$^2$, and Erez Gilad$^{1,}$} \\
-  $^1$The Unit of Nuclear Engineering \\
+          Daniele Tomatis$^2$ and Erez Gilad$^1$} \\
+  $^1$The Unit of Nuclear Engineering, \\
   Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\
@@
 
-\daniele{Shall we keep the current order of sections or exchange sec. 2 with sec. 3?}
 % ------------------------------------------
-\subsection{COARSE MESH FINITE DIFFERENCES}
+\section{COARSE MESH FINITE DIFFERENCES}
 \label{sec:CMFD-intro}
@@
 \end{subequations}
-
-\daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
+% \daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
 

### 2019-11-14 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
First implementation of pCMFD and general code enhancement.

--- 2019-11-06 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
@@
 %
-% \title{INTEGRAL TRANSPORT CORRECTION \\TO DIFFUSION CALCULATIONS BY pCMFD}
 \title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\
@@
   %
-  \textbf{Roy Gross$^1$\footnote{Corresponding author.},
-          Daniele Tomatis$^2$, and Erez Gilad$^{1,}$} \\
-  $^1$The Unit of Nuclear Engineering \\
+  \textbf{Roy Gross$^1$,
+          Daniele Tomatis$^2$\footnote{Corresponding author.}
+          and Erez Gilad$^1$} \\
+  $^1$The Unit of Nuclear Engineering, \\
   Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\
 \\
-  $^2$CEA, DEN, Service d’\'etudes des r\'eacteurs et
+  $^2$CEA, DEN, Service d'\'etudes des r\'eacteurs et
       de math\'ematiques appliqu\'ees (SERMA), \\

### 2019-11-14 FD1dMGdiff/FDsDiff1D.py

@@ -27,10 +27,6 @@ import sys
 import logging as lg
 import numpy as np
 from scipy.special import expn as En
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-
-from data2Ghomog import *
 
 __title__ = "Multigroup diffusion in 1D slab by finite differences"
 __author__ = "D. Tomatis"
@@ -40,6 +36,21 @@ __version__ = "1.2.0"
 max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
 np.set_printoptions(precision=5)
+
+# default options
+# possible options of geometry_type are slab, cylindrical, spherical
+geometry_type = "slab"
+# tolerance on the fission rates during outer iterations
+toll = 1.e-6
+oitmax = 100  # max nb of outer iterations
+iitmax = 100  # max nb of inner iterations
+itsmax = oitmax, iitmax
+fix_reflection_by_flx2 = True
+pCMFD = True
+
+
+# get the mid-points of cells defined in the input spatial mesh x
+xim = lambda x: (x[1:] + x[:-1]) / 2.
 
 
 def get_zeta(bc=0, D=None):
@@ -100,7 +111,7 @@ def compute_cell_volumes(xi, geo=geometry_type):
     # must be multiplied by 2*np.pi, 4*np.pi for the sphere.
     Di = xi[1:] - xi[:-1]
     if geo != 'slab':
-        xm = (xi[1:] + xi[:-1]) / 2.
+        xm = xim(xi)
         if geo == 'cylindrical':
             Di *= xm
         elif geo == 'spherical':
@@ -118,43 +129,39 @@ def vol_averaged_at_interface(f, Vi):
     # fb, volume-average quantity on cell borders
     fb = (f[:,1: ] * np.tile(Vi[1: ], G).reshape(G, Im1) +
           f[:,:-1] * np.tile(Vi[:-1], G).reshape(G, Im1))
-    fb /= np.tile(Vi[1:] + Vi[:-1], G).reshape(G, Im1)
-    # Db = np.zeros((G, I-1),)
-    # for g in range(G):
-    #     Db[g,:] = (D[g,1:] * Vi[1:] + D[g,:-1] * Vi[:-1]) / Dm
-    return fb
+    return fb / np.tile(Vi[1:] + Vi[:-1], G).reshape(G, Im1)
 
 
 def set_diagonals(st, D, xv, BC=(0, 0), dD=None):
[…]

### 2019-11-14 FD1dMGdiff/data2Ghomog.py

@@ -22,20 +22,17 @@ chi = np.array([1., 0.])
 D = one_third / (st - np.sum(ss1, axis=1))
 
 # set b.c.
-LBC, RBC = 0, 0
-# pack the b.c. identifiers
-BC = LBC, RBC
+LBC, RBC = 2, 0
 
 # definition of the spatial mesh
-L = 21.5  # slab width, equal to half pitch of a fuel assembly
-I = 10  # nb of spatial cells
+L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
+I = 20  # nb of spatial cells
 G = st.size  # nb of energy groups
 xi = np.linspace(0, L, I+1)  # equidistant mesh
-xm = (xi[1:] + xi[:-1]) / 2. # mid-points
-#xim = lambda x: (x[1:] + x[:-1]) / 2. # mid-points
+# xm = (xi[1:] + xi[:-1]) / 2. # mid-points
 
 # tolerance on the fission rates during outer iterations
-ritmax = 50  # set to 1 to skip the Ronen iterations
+ritmax = 1  # set to 1 to skip the Ronen iterations
 toll = 1.e-6
 oitmax = 50  # max nb of outer iterations
 iitmax = 100  # max nb of inner iterations
@@ -49,7 +46,6 @@ geometry_type = 'slab' # 'cylindrical'/'spherical'
 
 # reflective BC fix
 fix_reflection_by_flx2 = True
-
 
 if __name__ == "__main__":
 

### 2019-11-14 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
Update the manuscript with the implemented version of pCMFD.

--- 2019-11-12 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
@@
   %
-  \textbf{Roy Gross$^1$\footnote{Corresponding author.},
-          Daniele Tomatis$^2$ and Erez Gilad$^1$} \\
+  \textbf{Roy Gross$^1$,
+          Daniele Tomatis$^2$\footnote{Corresponding author.}
+          ~and Erez Gilad$^1$} \\
   $^1$The Unit of Nuclear Engineering, \\
@@
 \end{equation}
-where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
+where $J$ denotes the net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
 \begin{equation}
@@
 
-The accurate net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
+The net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
 \begin{subequations}
@@
   \end{equation}
-where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$.
+where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$, $\forall i$.
+Only the zeroth moment of the angular flux, that is the scalar flux after an expansion in angle on the spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
+\eqs{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
+This is the main assumption of the Ronen Method.
 \end{subequations}
@@
 
-In standard CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
-Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime.
+In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
+Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime \cite{Smith-1983}.
 Besides, the net current can be determined from some other expression which is physically or numerically more accurate.
@@
 About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
+In linearly anisotropic problems, the net current can also be considered to compute the source.
 Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
@@
     \frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
-  J_{i+\hzi,g} - \jD_{i+\hzi,g}.
+  J_{i+\hzi,g} - \jD_{i+\hzi,g},
 \end{equation}
-The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
-Boundary conditions applies as usual on the diffusion current and on the net (more accurate) current, without any particular change for the definition of the correction term.
+for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
+
+Boundary conditions applies on the diffusion current as usual by means of an extrapolated length $\zeta$, $\zeta \jD \cong D \phi$.
+Mark or Marshak approximations, or other constants derived from transport theory can be used for $\zeta$ \cite{meghreblian1960reactor}.
+About the correction terms instead, it is simply $\delta J = -\delta D \phi$ with the boundary flux approximated at first order by the cell-averaged value.
 
@@
 
-The CMFD introduces a free parameter in the numerical scheme through the correction term to adjust the diffusive solution locally.
+The CMFD introduces in the numerical scheme a free parameter per cell surface through the correction term to adjust the diffusive solution locally.
 Since separate calculations of the partial currents are possible, two free parameters could be used in the discretized form of the diffusion equation.
+This idea leads to the development of the pCMFD scheme \cite{cho2003comparison}.
 
-Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
-\begin{equation}
-\label{eq:partial-current}
-\jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
-\end{equation}
-still verifying the expression for the net current $J = J^+ - J^-$.
-% Daniele: the 1st moment is the scalar current and not its diffusion approx
-%where $\jD$ denotes the diffusion current.
-%where
-%\begin{equation}
-%\label{eq:diff-current}
-%\bm{J} (x) = \jp(x) - \jm(x).
-%\end{equation}
-\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
-\begin{equation}
-  \label{eq:PCCF}
-  \jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
-    \left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
-\end{equation}
-and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
+Two corrective terms are then introduced: $J = \jp - \jm = \jD + \delta J^+ + \delta J^-$.
+An upwind definition with respect to the direction of flight of neutrons is used for the corrections~\cite{Jarrett-2016,Zhu-2016}:
 \begin{equation}
   \label{eq:CCF-sub}
-\delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
+  \delta \jp _{i+\hzi} = -\delta D^+ _{i+\hzi} \phi_i
   \quad \text{and} \quad
-\delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
+  \delta \jm _{i+\hzi} = -\delta D^- _{i+\hzi} \phi_{i+1}.
 \end{equation}
-% yields
-% \begin{align}
-% \label{eq:par4}
-% \jp _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-% + \frac{1}{2}\jD _{i+\hzi} - \delta D^+ _{i+\hzi} \phi_i \\
-% \jm _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-% - \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1}.
-% \end{align}
-%Recall that $\jpm$ are calculated using the integral expression.
+The current by diffusion is distributed on the partial currents in equal parts in order to compute the new corrective coefficients $\delta D^{\pm}$,
+\begin{subequations}
+  \label{eq:delta-D-pCMFD}
+  \begin{align}
+    J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= -\delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
+    J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
+  \end{align}
+\end{subequations}
+still for $i=0, \ldots, I-2$.
+The diffusion current is not halved at the boundary, using only \eq{eq:delta-D-pCMFDm} or \eq{eq:delta-D-pCMFDp} at the left and at the right boundaries, respectively.
+Finally, the implementation of CMFD can be upgraded to support the pCMFD scheme with minimal changes.
+% -----------------------------------------------------------------------------
 %
-Solving for the partial current correction factors gives
-\begin{equation}
-  \label{eq:ccfsss1}
-  \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
-  	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
-  \quad \text{and} \quad
-  \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
-  	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
-  \end{equation}
-where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.
+% Daniele: the following proposition has shown to be inconsistent.
+%
+% Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
 % \begin{equation}
-%   \label{eq:jdiff}
-%   \phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}
-%                        {\Delta_i + \Delta_{i+1}}.
+% \label{eq:partial-current}
+% \jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
 % \end{equation}
+% still verifying the expression for the net current $J = J^+ - J^-$.
+\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
+% \begin{equation}
+%   \label{eq:PCCF}
+%   \jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
+%     \left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
+% \end{equation}
+% and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
+% \begin{equation}
+% \label{eq:CCF-sub}
+% \delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
+% \quad \text{and} \quad
+% \delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
+% \end{equation}
+% %
+% Solving for the partial current correction factors gives
+% \begin{equation}
+%   \label{eq:ccfsss1}
+%   \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
+%   	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
+%   \quad \text{and} \quad
+%   \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
+%   	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
+%   \end{equation}
+% where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.
+% -----------------------------------------------------------------------------
 
-In a weakly absorbing medium and several mean free paths away from the boundary or a strong absorber, all correction factors $\delta D^\pm$ are expected to vanish and the net current must be fully reproduced by the diffusion current.% and~\eq{eq:ccfsss1} reduces to~\eq{eq:partial-current}, as expected, which implies for the net (accurate) current
-% \begin{equation}
-% J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi}.
-% \end{equation}
+In a weakly absorbing medium and several mean free paths away from the boundary or a strong absorber, all correction factors $\delta D^\pm$ are expected to vanish and the net current must be fully reproduced by the diffusion current.
+Of course, this must be verified by the classic CMFD scheme too.
 

### 2019-11-15 FD1dMGdiff/FDsDiff1D.py
Reorder main module and setup a proper file structure; fix minor bugs; upgrade code to treat heterogeneous cases.

@@ -19,6 +19,33 @@ The Cartesian (slab) is the default geometry option. Curvilinears can be
 chosen by selecting 'cylindrical' or 'spherical' for the global variable
 geometry_type.
 
+Cross sections data of different materials must be entered according to
+the following dictionary. Please, use zeroed arrays for chi and nsf for
+non-fissile media.
+
+xs_media = {
+    'name_of_media_1':{
+         'st': np.array with G elements
+         'ss': np.array with G*G*(anisotropy_order + 1) elements
+        'chi': np.array with G elements
+        'nsf': np.array with G elements
+    }
+    'name_of_media_2':{ ... }
+    ...
+}
+
+A list of lists is used to assign the materials to the geometry cells
+of the mesh, like for example:
+
+media = [
+    ['name_of_media_1', x_right_medium_1],
+    ['name_of_media_2', x_right_medium_2],
+    ...
+    ['name_of_media_N', x_right_medium_N]
+]
+where by definition it is always x_left_medium_1 = 0, and
+x_right_medium_(i) = x_left_medium_(i+1) for all i < N.
+
 .. todo:: the current version assumes a homogeneous problem. To be
           extended to heterogeneous problems.
 """
@@ -30,23 +57,34 @@ from scipy.special import expn as En
 
 __title__ = "Multigroup diffusion in 1D slab by finite differences"
 __author__ = "D. Tomatis"
-__date__ = "02/04/2019"
-__version__ = "1.2.0"
+__date__ = "15/11/2019"
+__version__ = "1.3.0"
 
 max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
 np.set_printoptions(precision=5)
 
+# log file settings
+logfile = os.path.splitext(os.path.basename(__file__))[0] + '.log'
+# verbose output only with lg.DEBUG mode
+lg.basicConfig(level=lg.INFO)  # filename = logfile
+
 # default options
 # possible options of geometry_type are slab, cylindrical, spherical
 geometry_type = "slab"
+# boundary conditions (0-vacuum, 1-zero flux, 2-reflection)
+LBC, RBC = 0, 0
+pCMFD = False  # classic CMFD is False
 # tolerance on the fission rates during outer iterations
[…]

### 2019-11-15 FD1dMGdiff/data2Ghomog.py

@@ -1,63 +1,0 @@
-import numpy as np
-
-one_third = 1. / 3.
-
-# multigroup xs for the homogeneous 2G problem
-# st = np.array([0.52610422, 1.25161422])
-# ss = np.zeros((2, 2, 2),)
-# ss0 = np.array([[0.5002712, 0.00175241], [0.01537974, 1.14883323]])
-# ss1 = np.array([[0.66171011, 0.00236677], [0.01330484, 0.91455725]])
-# multigroup xs for the homogeneous 2G problem (M&C article)
-st = np.array([0.531150, 1.30058])
-ss = np.zeros((2, 2, 2),)
-ss0 = np.array([[0.504664, 0.00203884], [0.0162955, 1.19134]])
-ss1 = np.array([[0., 0.], [0., 0.]])
-# Nuclear lib integrates already the coefficient of Lagrange polynomial
-ss1 *= one_third
-ss[:,:,0], ss[:,:,1] = ss0, ss1
-nsf = np.array([0.00715848, 0.141284])
-chi = np.array([1., 0.])
-
-# definition of the (P1) diff coefficient
-D = one_third / (st - np.sum(ss1, axis=1))
-
-# set b.c.
-LBC, RBC = 2, 0
-
-# definition of the spatial mesh
-L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
-I = 20  # nb of spatial cells
-G = st.size  # nb of energy groups
-xi = np.linspace(0, L, I+1)  # equidistant mesh
-# xm = (xi[1:] + xi[:-1]) / 2. # mid-points
-
-# tolerance on the fission rates during outer iterations
-ritmax = 1  # set to 1 to skip the Ronen iterations
-toll = 1.e-6
-oitmax = 50  # max nb of outer iterations
-iitmax = 100  # max nb of inner iterations
-itsmax = oitmax, iitmax
-
-# choose the type of CMFD scheme
-pCMFD = True  # classic CMFD scheme is False
-
-# choose geometry
-geometry_type = 'slab' # 'cylindrical'/'spherical'
-
-# reflective BC fix
-fix_reflection_by_flx2 = True
-
-if __name__ == "__main__":
-
-    lg.info("*** Check homogeneous cross sections data ***")
-
-    flx_inf = np.dot(np.linalg.inv(np.diag(st) - ss0), chi)
-    kinf = np.dot(nsf, flx_inf)
-    # np.testing.assert_almost_equal(kinf, 1.1913539017168697, decimal=7,
[…]

### 2019-11-15 FD1dMGdiff/scripts/plot_convergence.py

@@ -4,7 +4,7 @@ import numpy as np
 import matplotlib.pyplot as plt
 import sys
 sys.path.append('..')
-from data2Ghomog import *
+from data.homog2GMC2011 import *
 
 from cycler import cycler
 default_cycler = (cycler(color=['r', 'g', 'b', 'y']) *

### 2019-11-15 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -1,0 +1,42 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
+
+.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
+   transport correction in diffusion calculations", Proc. Int. Conf. on
+   Mathematics and Computational Methods Applied to Nuclear Science and
+   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
+"""
+import sys
+sys.path.append('..')
+from data.homog2GMC2011 import *
+import numpy as np
+
+# definition of the spatial mesh
+L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
+I = 6  # nb of spatial cells
+xi = np.linspace(0, L, I+1)  # equidistant mesh
+
+geometry_type = 'slab'
+
+xs_media = {
+    'HM':{  # homogeneous medium
+        'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
+    }
+}
+media = [['HM', L]]  # i.e. homogeneously filled
+
+# set b.c.
+LBC, RBC = 2, 0
+
+# solver options (to override options in the main module)
+ritmax = 10 # set to 1 to skip Ronen iterations
+
+if __name__ == "__main__":
+
+    import logging as lg
+    lg.info("*** Solve the M&C 2011 problem ***")
+    from FDsDiff1D import run_calc_with_RM_its as run_calc
+    filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
+    run_calc(filename)

### 2019-11-17 FD1dMGdiff/FDsDiff1D.py
Introduce objs input_data and solver_options to use FDsDiff1D as a library and run test cases from the folder tests.

@@ -12,8 +12,10 @@ If it is zero, we have the zero flux b.c., while reflection is reproduced
 by $\zeta \rightarrow \infty$. The b.c. code is in order 0, 1 and 2,
 respectively.
 
-The Ronen Method is implemented on top of the diffusion solver through
-the standard CMFD or the pCMFD version.
+Input data are set in two main objects. The first stores geometry and
+material input data, whereas the second contains the solver options. The
+Ronen Method is implemented on top of the diffusion solver through the
+standard CMFD or its pCMFD version.
 
 The Cartesian (slab) is the default geometry option. Curvilinears can be
 chosen by selecting 'cylindrical' or 'spherical' for the global variable
@@ -45,9 +47,6 @@ media = [
 ]
 where by definition it is always x_left_medium_1 = 0, and
 x_right_medium_(i) = x_left_medium_(i+1) for all i < N.
-
-.. todo:: the current version assumes a homogeneous problem. To be
-          extended to heterogeneous problems.
 """
 import os
 import sys
@@ -69,21 +68,6 @@ logfile = os.path.splitext(os.path.basename(__file__))[0] + '.log'
 # verbose output only with lg.DEBUG mode
 lg.basicConfig(level=lg.INFO)  # filename = logfile
 
-# default options
-# possible options of geometry_type are slab, cylindrical, spherical
-geometry_type = "slab"
-# boundary conditions (0-vacuum, 1-zero flux, 2-reflection)
-LBC, RBC = 0, 0
-pCMFD = False  # classic CMFD is False
-# tolerance on the fission rates during outer iterations
-toll = 1.e-6
-ritmax = 100  # set to 1 to skip Ronen iterations
-oitmax = 100  # max nb of outer iterations
-iitmax = 100  # max nb of inner iterations
-otoll = toll  # tolerance on fiss. rates at outer its.
-itoll = toll  # tolerance on flx at inner its.
-rtoll = toll  # tolerance on flx at RM its.
-
 fix_reflection_by_flx2 = True
 
 
@@ -91,8 +75,95 @@ fix_reflection_by_flx2 = True
 xim = lambda x: (x[1:] + x[:-1]) / 2.
 
 
+class input_data:
+    """Geometry and material input data of the 1D problem. Possible options
+    of geometry_type are slab, cylindrical and spherical. Allowed boundary
+    conditions: 0-vacuum, 1-zero flux and 2-reflection."""
+
[…]

### 2019-11-17 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -11,7 +11,11 @@ This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
 import sys
 sys.path.append('..')
 from data.homog2GMC2011 import *
+from FDsDiff1D import input_data
 import numpy as np
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
 
 # definition of the spatial mesh
 L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
@@ -30,13 +34,14 @@ media = [['HM', L]]  # i.e. homogeneously filled
 # set b.c.
 LBC, RBC = 2, 0
 
-# solver options (to override options in the main module)
-ritmax = 10 # set to 1 to skip Ronen iterations
+Homo2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
 
 if __name__ == "__main__":
 
     import logging as lg
     lg.info("*** Solve the M&C 2011 problem ***")
-    from FDsDiff1D import run_calc_with_RM_its as run_calc
-    filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
-    run_calc(filename)
+    from FDsDiff1D import run_calc_with_RM_its, solver_options
+
+    slvr_opts = solver_options(ritmax=10)
+    # filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
+    flx, k = run_calc_with_RM_its(Homo2GSlab_data, slvr_opts, filename=None)

### 2019-11-18 FD1dMGdiff/FDsDiff1D.py
Minor changes: code enhancement to comply with PEP8 recommendations.

@@ -72,7 +72,8 @@ fix_reflection_by_flx2 = True
 
 
 # get the mid-points of cells defined in the input spatial mesh x
-xim = lambda x: (x[1:] + x[:-1]) / 2.
+def xim(x):
+    return (x[1:] + x[:-1]) / 2.
 
 
 class input_data:
@@ -80,7 +81,8 @@ class input_data:
     of geometry_type are slab, cylindrical and spherical. Allowed boundary
     conditions: 0-vacuum, 1-zero flux and 2-reflection."""
 
-    def __init__(self, xs_media, media, xi, geometry_type='slab', LBC=0, RBC=0):
+    def __init__(self, xs_media, media, xi, geometry_type='slab',
+                 LBC=0, RBC=0):
         self.geometry_type, self.xi = geometry_type, xi
         self.LBC, self.RBC = LBC, RBC
         self.xs_media, self.media = xs_media, media
@@ -100,8 +102,8 @@ class input_data:
 
     def check_input(self):
         if (self.geometry_type != 'slab') and \
-            (self.geometry_type != 'cylindrical') and \
-            (self.geometry_type != 'spherical'):
+           (self.geometry_type != 'cylindrical') and \
+           (self.geometry_type != 'spherical'):
             raise ValueError('Unknown geometry_type ' + self.geometry_type)
         if not isinstance(self.LBC, int):
             raise TypeError('LBC must be integer.')
@@ -128,8 +130,8 @@ class input_data:
 
     def __str__(self):
         print("Geometry type is " + self.geometry_type)
-        print("Boundary conditions: (left) LBC=%d and (right) RBC=%d." % \
-            (self.LBC, self.RBC))
+        print("Boundary conditions: (left) LBC=%d and (right) RBC=%d." %
+              (self.LBC, self.RBC))
         print("B.C. legend: 0-vacuum, 1-zero flux and 2-reflection.")
         print("Number of energy groups: %d" % self.G)
         print("Number of spatial cells: %d" % self.I)
@@ -144,7 +146,6 @@ class solver_options:
     toll = 1.e-6  # default tolerance
     itsmax = 100  # default nb. of max iterations (its)
 
-
[…]

### 2019-11-29 FD1dMGdiff/data/homog2GIlas2003.py
Cross sections for Farzad-1997/Ilas 2003 benchmark
Includes: Water, Fuel I,II,III

@@ -1,0 +1,87 @@
+# --*-- coding:utf-8 --*--
+"""
+Multigroup xs for the homogeneous 2G problem [Tomatis2011]_.
+
+.. note:: remind that the scattering moments are already multiplied by the
+   coefficients of Lagrange polynomials if data are produced by APOLLO.
+
+.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
+   transport correction in diffusion calculations", Proc. Int. Conf. on
+   Mathematics and Computational Methods Applied to Nuclear Science and
+   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
+"""
+
+import numpy as np
+import logging as lg
+
+one_third = 1. / 3.
+
+# Water
+stw = np.array([0.1890, 1.4633])
+ssw = np.zeros((2, 2, 2),)
+ssw_0 = np.array([[0.1507, 0.], [0.0380, 1.4536]])
+ssw_1 = np.array([[0., 0.], [0., 0.]])
+ssw_1 *= one_third
+ssw[:,:,0], ssw[:,:,1] = ssw_0, ssw_1
+nsfw = np.array([0., 0.])
+chiw = np.array([1., 0.])
+
+# Fuel I
+st1 = np.array([0.2263, 1.0119])
+ss1 = np.zeros((2, 2, 2),)
+ss1_0 = np.array([[0.2006, 0.], [0.0161, 0.9355]])
+ss1_1 = np.array([[0., 0.], [0., 0.]])
+ss1_1 *= one_third
+ss1[:,:,0], ss1[:,:,1] = ss1_0, ss1_1
+nsf1 = np.array([0.0067, 0.1241])
+chi1 = np.array([1., 0.])
+
+# Fuel II
+st2 = np.array([0.2252, 0.9915])
+ss2 = np.zeros((2, 2, 2),)
+ss2_0 = np.array([[0.1995, 0.], [0.0156, 0.9014]])
+ss2_1 = np.array([[0., 0.], [0., 0.]])
+ss2_1 *= one_third
+ss2[:,:,0], ss2[:,:,1] = ss2_0, ss2_1
+nsf2 = np.array([0.0078, 0.1542])
+chi2 = np.array([1., 0.])
+
+# Fuel III
+st3 = np.array([0.2173, 1.0606])
+ss3 = np.zeros((2, 2, 2),)
+ss3_0 = np.array([[0.1902, 0.], [0.0136, 0.5733]])
[…]

### 2019-11-29 FD1dMGdiff/tests/homogSlab2GIlas2003.py
Core configuration and spatial mesh for benchmark
This commit includes the:
1) core configurations
2) Coarse spatial mesh - boundaries between materials
3) Fine mesh - the mesh within each material

@@ -1,0 +1,160 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
+
+.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
+   transport correction in diffusion calculations", Proc. Int. Conf. on
+   Mathematics and Computational Methods Applied to Nuclear Science and
+   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
+"""
+import sys
+sys.path.append('..')
+#from data.homog2GMC2011 import *
+from data.homog2GIlas2003 import *
+from FDsDiff1D import input_data
+import numpy as np
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
+
+def get_fa(faid, ifa, L, nz=6):
+   '''returns a list of lists of FA id materials in location ifa in core.
+   ifa = 0,1,2,...,nfa-1 '''
+   
+   i = ifa*nz+1
+   if faid == 1:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELI', L[i+1]],
+            ['FUELII', L[i+2]],
+            ['FUELII', L[i+3]],
+            ['FUELI', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   elif faid == 2:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELI', L[i+1]],
+            ['FUELI', L[i+2]],
+            ['FUELI', L[i+3]],
+            ['FUELI', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   elif faid == 3:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELI', L[i+1]],
+            ['FUELIII', L[i+2]],
+            ['FUELIII', L[i+3]],
+            ['FUELI', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   elif faid == 4:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELIII', L[i+1]],
+            ['FUELIII', L[i+2]],
+            ['FUELIII', L[i+3]],
[…]

### 2019-11-29 FD1dMGdiff/FDsDiff1D.py
Bugs fixes to work with heterogeneous core
Minor bug fixes for complex heterogeneous cores.

@@ -119,13 +119,13 @@ class input_data:
             raise TypeError('The input xs_media is not a dictionary.')
         if not isinstance(self.media, list):
             raise TypeError('The input media is not a list.')
-        if len(self.xs_media) != len(self.media):
-            raise ValueError('xs media dict and list must have the same ' +
-                             'nb. of elements.')
+#        if len(self.xs_media) != len(self.media):
+#            raise ValueError('xs media dict and list must have the same ' +
+#                             'nb. of elements.')
         rbnd = [m[1] for m in self.media]
         if sorted(rbnd) != rbnd:
             raise ValueError('media list must be in order from left to right!')
-        if max(rbnd) > self.L:
+        if max(rbnd) > self.L and abs(max(rbnd) - self.L)>1e-6:
             raise ValueError('Please check the right bounds of media (>L?)')
 
     def __str__(self):
@@ -812,12 +812,13 @@ def unfold_xs(input_data):
     for m in media:
         media_name, rbnd = m
         idx = (lbnd < xm) & (xm < rbnd)
-        st[:, idx] = np.tile(xs_media[media_name]['st'], (I, 1)).T
-        nsf[:, idx] = np.tile(xs_media[media_name]['nsf'], (I, 1)).T
-        chi[:, idx] = np.tile(xs_media[media_name]['chi'], (I, 1)).T
-        D[:, idx] = np.tile(xs_media[media_name]['D'], (I, 1)).T
+        st[:, idx] = np.tile(xs_media[media_name]['st'], (I, 1))[idx].T
+        nsf[:, idx] = np.tile(xs_media[media_name]['nsf'], (I, 1))[idx].T
+        chi[:, idx] = np.tile(xs_media[media_name]['chi'], (I, 1))[idx].T
+        D[:, idx] = np.tile(xs_media[media_name]['D'], (I, 1))[idx].T
         tmp = np.tile(xs_media[media_name]['ss'][:, :, 0].flatten(), (I, 1)).T
-        ss0[:, :, idx] = tmp.reshape(G, G, I)
+        ss0[:, :, idx] = tmp.reshape(G, G, I)[:,:,idx]        
+        lbnd = rbnd
 
     return st, ss0, chi, nsf, D
 
@@ -870,7 +871,8 @@ def run_calc_with_RM_its(idata, slvr_opts, filename=None):
 if __name__ == "__main__":
 
[…]

### 2019-11-30 SNMG1DSlab/snmg1dslab.py
Solve heterogeneous problems.
Changed so it can solve heterogeneous problems using the same format as the RM files. This file is mainly a library now.

@@ -8,6 +8,34 @@ education purposes of students at the Master program in Nuclear Engineering.
 The solving algorithm is based on the transport sweep and the common diamond
 differences scheme, see chapter 3 of [1].
 
+Cross sections data of different materials must be entered according to
+the following dictionary. Please, use zeroed arrays for chi and nsf for
+non-fissile media.
+
+xs_media = {
+    'name_of_media_1':{
+         'st': np.array with G elements
+         'ss': np.array with G*G*(anisotropy_order + 1) elements
+        'chi': np.array with G elements
+        'nsf': np.array with G elements
+    }
+    'name_of_media_2':{ ... }
+    ...
+}
+
+A list of lists is used to assign the materials to the geometry cells
+of the mesh, like for example:
+
+media = [
+    ['name_of_media_1', x_right_medium_1],
+    ['name_of_media_2', x_right_medium_2],
+    ...
+    ['name_of_media_N', x_right_medium_N]
+]
+where by definition it is always x_left_medium_1 = 0, and
+x_right_medium_(i) = x_left_medium_(i+1) for all i < N.
+
+
 ...
 
 Bibliography
@@ -29,16 +57,98 @@ __status__ = "Dev"
 __credits__ = [__author__]
 __version__ = "0.1.0"
 
+import logging as lg
 import sys, os
 import warnings as wrn
 import numpy as np
 from scipy.special import roots_legendre, legendre
 
-# Quadrature choice
-qtype = "Gauss-Legendre"
+class input_data:
+    """Geometry and material input data of the 1D problem. Possible options
+    of geometry_type are slab, cylindrical and spherical. Allowed boundary
+    conditions: 0-vacuum, 1-zero flux and 2-reflection."""
+
+    def __init__(self, xs_media, media, xi, xm, dx, geometry_type='slab',
+                 LBC=0, RBC=0):
+        self.xi, self.xm, self.dx = xi, xm, dx
+        self.geometry_type = geometry_type
+        self.LBC, self.RBC = LBC, RBC
+        self.xs_media, self.media = xs_media, media
+        self.check_input()
+
+    @property
+    def I(self):
+        return self.xi.size - 1
+
+    @property
+    def L(self):
+        return self.xi[-1]
+
+    @property
+    def G(self):
[…]

### 2019-11-30 SNMG1DSlab/data/hetro2GIlas2003.py
cross sections for Ilas-2003 benchmark

@@ -1,0 +1,87 @@
+# --*-- coding:utf-8 --*--
+"""
+Multigroup xs for the homogeneous 2G problem [Tomatis2011]_.
+
+.. note:: remind that the scattering moments are already multiplied by the
+   coefficients of Lagrange polynomials if data are produced by APOLLO.
+
+.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
+   transport correction in diffusion calculations", Proc. Int. Conf. on
+   Mathematics and Computational Methods Applied to Nuclear Science and
+   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
+"""
+
+import numpy as np
+import logging as lg
+
+one_third = 1. / 3.
+
+# Water
+stw = np.array([0.1890, 1.4633])
+ssw = np.zeros((2, 2, 2),)
+ssw_0 = np.array([[0.1507, 0.], [0.0380, 1.4536]])
+ssw_1 = np.array([[0., 0.], [0., 0.]])
+ssw_1 *= one_third
+ssw[:,:,0], ssw[:,:,1] = ssw_0, ssw_1
+nsfw = np.array([0., 0.])
+chiw = np.array([1., 0.])
+
+# Fuel I
+st1 = np.array([0.2263, 1.0119])
+ss1 = np.zeros((2, 2, 2),)
+ss1_0 = np.array([[0.2006, 0.], [0.0161, 0.9355]])
+ss1_1 = np.array([[0., 0.], [0., 0.]])
+ss1_1 *= one_third
+ss1[:,:,0], ss1[:,:,1] = ss1_0, ss1_1
+nsf1 = np.array([0.0067, 0.1241])
+chi1 = np.array([1., 0.])
+
+# Fuel II
+st2 = np.array([0.2252, 0.9915])
+ss2 = np.zeros((2, 2, 2),)
+ss2_0 = np.array([[0.1995, 0.], [0.0156, 0.9014]])
+ss2_1 = np.array([[0., 0.], [0., 0.]])
+ss2_1 *= one_third
+ss2[:,:,0], ss2[:,:,1] = ss2_0, ss2_1
+nsf2 = np.array([0.0078, 0.1542])
+chi2 = np.array([1., 0.])
+
+# Fuel III
+st3 = np.array([0.2173, 1.0606])
+ss3 = np.zeros((2, 2, 2),)
+ss3_0 = np.array([[0.1902, 0.], [0.0136, 0.5733]])
[…]

### 2019-11-30 SNMG1DSlab/tests/hetroSlab2GIlas2003.py
The driver file for calculating Ilas-2003

@@ -1,0 +1,174 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
+
+.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
+   transport correction in diffusion calculations", Proc. Int. Conf. on
+   Mathematics and Computational Methods Applied to Nuclear Science and
+   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
+"""
+import sys
+sys.path.append('..')
+from data.hetro2GIlas2003 import *
+from snmg1dslab import input_data, solver_options, quad_data
+import numpy as np
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
+
+def get_fa(faid, ifa, L, nz=6):
+   '''returns a list of lists of FA id materials in location ifa in core.
+   ifa = 0,1,2,...,nfa-1 '''
+   
+   i = ifa*nz+1
+   if faid == 1:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELI', L[i+1]],
+            ['FUELII', L[i+2]],
+            ['FUELII', L[i+3]],
+            ['FUELI', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   elif faid == 2:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELI', L[i+1]],
+            ['FUELI', L[i+2]],
+            ['FUELI', L[i+3]],
+            ['FUELI', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   elif faid == 3:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELI', L[i+1]],
+            ['FUELIII', L[i+2]],
+            ['FUELIII', L[i+3]],
+            ['FUELI', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   elif faid == 4:
+      media = [ 
+            ['WATER', L[i]],
+            ['FUELIII', L[i+1]],
+            ['FUELIII', L[i+2]],
+            ['FUELIII', L[i+3]],
+            ['FUELIII', L[i+4]],
+            ['WATER', L[i+5]]
+            ]
+   else:
[…]

### 2019-12-01 docs/EPJP2019/response.tex

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
%\usepackage{bm}% bold math
%\usepackage[sectionbib]{natbib}% bold math
\usepackage{letterbib}
\usepackage[sort&compress]{natbib}% bold math
%\bibliographystyle{abbrv}
\bibliographystyle{unsrt}
%\bibliographystyle{sort}
%\usepackage[english,hebrew]{babel}
\usepackage{hyperref}

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

\usepackage[usenames, dvipsnames]{color}
% for quotes
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

% Margins
\topmargin=-1.in % Moves the top of the document 1 inch above the default
\textheight=9.in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=0.2in % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\newcommand{\tsup}[1]{\textsuperscript{#1}}
\newcommand{\tsub}[1]{\textsubscript{#1}}
\newcommand{\revised}[1]{{\color{red}{#1}}}
\newcommand{\revb}[1]{{\color{magenta}{#1}}}

\newcommand{\keff}{\ensuremath{k_{\texttt{\scriptsize{eff}}}}}
\newcommand{\ppf}{\textrm{PPF}}

\newcommand{\eg}{e.g.,}
\newcommand{\ie}{i.e.,}

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{The European Physical Journal Plus \\
Editorial board}

\signature{
	\vspace{-30pt}
	Erez Gilad, PhD \\
	\mbox{Ben-Gurion University of the Negev}\\
	E-mail: gilade@bgu.ac.il
} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------
\opening{Dear Dr. Jozef Ongena, Managing editor\\}

Thank you for the response regarding the manuscript EPJP-D-19-01168 entitled "High-accuracy neutron diffusion calculations based on integral transport theory". We are also grateful for the insightful comments by the reviewer.

The manuscript underwent a revision in light of the reviewer's comments and is hereby resubmitted for publication in \textit{The European Physical Journal Plus}.

In the revised manuscript we address in full the comments by the reviewer, and the revised parts are marked \revised{in red}. Following are the comments by the reviewer in black followed by our responses (\revised{in red}).

We hope that the Editor and the reviewer find the revised manuscript satisfactory and recommend it for publication.

%--------------------------------------------------------------
% LETTERS ENDS HERE ******************************************
\closing{\mbox{Sincerely yours on behalf of all the co-authors,}}

%---------------------------------------------------------------------------------------	-
\newpage

\textbf{Reviewer \#1}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Please re-read the whole paper to check the language and the punctuation. Some sentences are very concise and could be expanded a little for clarity.}
\\ \\
\revised{The manuscript underwent a thorough examination of the language and punctuation, and some sentences were elaborated for clarity. For example, ...}
\\ \\
% --------------------------------------------------------------------------------------
\textit{I have a concern on which the Authors may want to comment. Formula (3) becomes problematic where the gradient of the flux is small, which is usually the zone where diffusion works better.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{I do not think it would be too hard work to report more results. For instance, I think it would be nice to see the effect of the physical size of the domain, to better detect and evidence the effect of the boundary. This would add a lot to the value of the paper.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{I do not think it would be too hard work to report more results. For instance, I think it would be nice to see the effect of the physical size of the domain, to better detect and evidence the effect of the boundary. This would add a lot to the value of the paper.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{In the abstract: I suggest to avoid saying that the results match "extremely well" the reference... while this is true for the eigenvalue, it may be questionable for the flux near the boundary, where effects should be more deeply investigated. Maybe "well" is already enough.}
\\ \\
\revised{T}
\\ \\

\newpage

% --------------------------------------------------------------------------------------
\textit{Page 22, At line 40: largest errors appear near the boundary. This is of course related to the failure of diffusion, however there might be also an additional contribution of the type of boundary conditions adopted (see below). Any comments? In any case, this aspect needs to be investigated.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Line 55: for clarity I would change it to "uncollided neutrons originated from an incoming angular flux at the boundary".}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Page 3, In the title of subsection 2.3 change "\&" with "and".}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{In formula (8) it should be specified that it is assumed x'<x, otherwise it is not consistent with Eqs. (7).}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{There is no definition of the moments of the cross sections, Eq. (10).}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Page 5, At line 42 I suggest to change "terms to get" with "terms, one gets".}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{At line 58: the fission operator is not given by q, but, rather, it can be obtained by the observation of the form of the q term, Eq. (25). Since it is crucial to see the effect of the diffusion coefficient update, the operators could be reported explicitly.}
\\ \\
\revised{T}
\\ \\

\newpage

% --------------------------------------------------------------------------------------
\textit{Page 6, To me the title of subsection 3.2 is not correct (there is no such a thing as "integral currents". Should it rather be something like "evaluation of the currents by the integral form of the transport equation"? I suggest also to change the caption of Fig. 2 accordingly.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Since the whole section consider the multigroup formulation, at line 6 to be consistent I suggest to change $J(x,E)$ to $J_g(x)$. }
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Page 7, About boundary conditions: how is the extrapolated distance chosen with vacuum? For instance, with a Mark or a Marshak approach or according to other recipes? And, in any case, what is the value assumed for the calculations? Furthermore, the Authors should also comment on the problem of the need to update the extrapolated distance since it is in general related to the diffusion coefficient (e.g. 2D in Marshak BC). In this respect, the meaning of the sentence in line 53 and 54 is not clear to me.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{page 8, The statement about boundary conditions should be clarified at line 40. What does "they are constant for each energy group" mean? If it means that the same extrapolated distance is assumed for both groups, the Authors should consider to make a more consistent assumption of group-dependent extrapolated distances. The effect of the choice of the BC is not insignificant, especially for optically thin systems. It could be interesting to see the effect of the different choices.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{In Table 1 units must be indicated.}
\\ \\
\revised{T}
\\ \\

\newpage

% --------------------------------------------------------------------------------------
\textit{At line 50, please change "w/" with "with". At line 55, please change "w/o" with "without". The use of such contractions (such as "\&" above) is not advisable in a scientific paper. I suggest to make these changes throughout the whole paper.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{At line 60, it is advisable to expand on "the corrected diffusion current exhibit(s)non-trivial behaviour near the boundary". Can it be related to BC?}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{General comment on the Figures: it would be nice to explicitly identify the quantities in the graphs rather than letting the reader struggle to interpret them from the legend.}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{In Fig. 8: is there any explanation for the sign change in some curves?}
\\ \\
\revised{T}
\\ \\
% --------------------------------------------------------------------------------------
\textit{Suggestion for further work: it should not be too difficult to study a heterogeneous configuration, since the Ronen method naturally leads to a non-homogeneous system, to see how the Ronen method adapts to interfaces, where strong gradients of the flux might appear.}
\\ \\
\revised{T}
\\ \\

%\bibliography{severe_accident}

\end{letter}

\end{document}

### 2019-12-02 docs/EPJP2019/response/response.tex
Updated tex files for EPJP revision. Work in progress.
The updated ms is Gross-EPJP-2019.tex. The response to reviewer and editor is in new directory response/

--- 2019-12-01 docs/EPJP2019/response.tex
@@
 \\ \\
-\revised{The manuscript underwent a thorough examination of the language and punctuation, and some sentences were elaborated for clarity. For example, ...}
+\revised{The manuscript underwent a thorough examination of the language and punctuation, and some sentences were elaborated for clarity.}
 \\ \\
@@
 \\ \\
-\revised{T}
+\revised{This is correct.
+Ronen did not elaborate on this issue in his technical note from 2004.
+Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current at this location (where the flux gradiaent is weak).
+We did not try to find the analytic limit of this expression for $D$, however we assume that this ratio between two expressions, which vanish at the same location, approaches some constant value.\\ \\ Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
+The (more accuarte) surface current $J_{tr}$, calculated by intergal expression, is written as the sum of the surface current calculated by diffusion, $J_D$, plus a correction $\delta J$.
+Hence, when the current vanishes, the correction $\delta J$ valishes.
+Moreover, the correction is writtten as in Eq.
+(21), avoiding the potential divergence resulting from division by zero.}
 \\ \\
@@
 \\ \\
-\revised{T}
-\\ \\
-% --------------------------------------------------------------------------------------
-\textit{I do not think it would be too hard work to report more results.
-For instance, I think it would be nice to see the effect of the physical size of the domain, to better detect and evidence the effect of the boundary.
-This would add a lot to the value of the paper.}
-\\ \\
-\revised{T}
+\revised{An entire benchark was added to the results section.
+The chosen benchmark is a one-dimensional highly heterogeneous core representing a BWR core.
+The sensitivity of the method to the slab width, especially at the boundaries, will be studied in future work, along with additional effects emanate from the boundaries conditions.}
 \\ \\
@@
 \\ \\
-\revised{T}
+\revised{Fixed.}
 \\ \\
@@
 % --------------------------------------------------------------------------------------
-\textit{Page 22, At line 40: largest errors appear near the boundary.
+\textit{Page 2, At line 40: largest errors appear near the boundary.
 This is of course related to the failure of diffusion, however there might be also an additional contribution of the type of boundary conditions adopted (see below).
@@
 \\ \\
-\revised{T}
+\revised{We agree with the reviewer that the effect of the definition of boundary conditions on the performances of the Ronen method should be further studied.
+This study will be conducted in the near future.
+As for the specific boundary conditions used in this paper, please see below.}
 \\ \\
@@
 \\ \\
-\revised{T}
+\revised{The sentence was chnaged to "...
+$\mathcal{F}$ is the neutron generation operator given by \emph{the second term in} $q_{i,g}$ (see Eqs.
+25-26)".
+The explicit form of the operators is given in Eqs.
+25 and 26.
+}
 \\ \\
-
-\newpage
 
@@
 \\ \\
-\revised{T}
+\revised{Fixed.}
 \\ \\
+
+\newpage
+
 % --------------------------------------------------------------------------------------
@@
 \\ \\
-\revised{T}
+\revised{The extrapolated distance for vacuum is set to $\zeta=2.13D$ (according to Lamarsh 1966).
+The Marshak boundary conditions are reproduced by $\zeta=2D$).
+The values assumed for the calculations are 1.3367 and 0.5459 cm for the fast and thermal groups, respectively.
+\\ \\
+As for the need to update the extrapolated distance, it should be noted that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance.
+Only $\delta D$ is recalculated.
+Note that the correction in our numerical scheme is not by $D = D_0 + \delta D$ nor by $D = \delta D$.
+The correction of the diffusion coefficient is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
+}
 \\ \\

### 2019-12-02 docs/EPJP2019/Gross-EPJP-2019.tex
Update ICTT src files and upload the slides shown at the conference
unstage temporary files and create a directory for figures
Updated tex files for EPJP revision. Work in progress.
The updated ms is Gross-EPJP-2019.tex. The response to reviewer and editor is in new directory response/

--- 2019-10-02 docs/EPJP-2019/Gross-EPJP-2019 - rev1.tex
@@
 %
-\begin{filecontents}{leer.eps}
-!PS-Adobe-2.0 EPSF-2.0
-%%CreationDate: Mon Jul 13 16:51:17 1992
-%%DocumentFonts: (atend)
-%%Pages: 0 1
-%%BoundingBox: 72 31 601 342
-%%EndComments
-
-gsave
-72 31 moveto
-72 342 lineto
-601 342 lineto
-601 31 lineto
-72 31 lineto
-showpage
-grestore
-%%Trailer
-%%DocumentFonts: Helvetica
-\end{filecontents}
+%\begin{filecontents}{leer.eps}
+%!PS-Adobe-2.0 EPSF-2.0
+%%%CreationDate: Mon Jul 13 16:51:17 1992
+%%%DocumentFonts: (atend)
+%%%Pages: 0 1
+%%%BoundingBox: 72 31 601 342
+%%%EndComments
+%
+%gsave
+%72 31 moveto
+%72 342 lineto
+%601 342 lineto
+%601 31 lineto
+%72 31 lineto
+%showpage
+%grestore
+%%%Trailer
+%%%DocumentFonts: Helvetica
+%\end{filecontents}
 %
@@
 %
+\graphicspath{ {./figures/} }
 % ---------------------------------------------------
@@
 \abstract{
-In this paper, the Ronen method is developed, implemented and applied to resolve the neutron flux and the criticality eigenvalue in a simple homogeneous problem.
-The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and driven by the solutions of the integral transport equation.
-The local diffusion constants are modified in order to reproduce new estimates of the surface currents by a transport operator.
-The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme by means of drift terms.
+In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue \revised{in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks}.
+The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and \revised{is} driven by the solutions of the integral transport equation.
+The \revised{spatially-dependent} diffusion constants are modified \revised{locally} in order to produce new estimates of the surface currents \revised{using an integral transport expression}.
+The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme \revised{using} drift terms.
 The corrected solutions are compared against reference results obtained by a discrete ordinate code.
-Boundary conditions are discussed and proper approximations are introduced in order to conserve the particle balance.
-The results match extremely well the reference solutions, especially in the limit of fine meshes, but slow convergence of the scalar flux is reported.
+Boundary conditions are discussed and proper approximations are introduced to conserve the particle balance.
+The results match well with the reference solutions, especially in the limit of fine meshes, but slow convergence of the scalar flux is reported.
 % 
@@
 High-fidelity core design optimization or transient analyses can quickly become computationally impractical when using transport methods~\cite{Kim-2019}.
-For example, in order to achieve a 1\% accuracy in the local flux/power estimation, an order of 10\tsup{11} histories is needed in a full-core Monte Carlo calculation~\cite{Martin-2012}.
+For example, to achieve a 1\% accuracy in the local flux/power estimation, an order of 10\tsup{11} histories is needed in a full-core Monte Carlo calculation~\cite{Martin-2012}.
 Another problem is the huge number of variables and parameters to be stored and used during computation, e.g., tallies, geometry, cross sections, and depletion data.
 A conservative estimation of the memory needed for reasonably accurate full-core Monte Carlo neutronic calculation is in the range of terabytes (TBs)~\cite{Martin-2012}.
-
-%The growing demand for high-accuracy and high-precision full-core computations challenges not only today’s high-end computing systems but will also challenge the near future (e.g., Exascale) computers~\cite{Martin-2012,Smith-2011,Kim-2019}.
+\revised{The growing demand for high-accuracy and high-precision full-core computations challenges not only today’s high-end computing systems but will also challenge the near future (e.g., Exascale) computers~\cite{Martin-2012,Smith-2011,Kim-2019}.}
 
@@
 
-In this paper, the development, implementation, and qualification of the Ronen Method~\cite{Ronen-2004} in one-dimensional homogeneous plane geometry is reported.
+In this paper, the development, implementation, and qualification of the Ronen Method~\cite{Ronen-2004} in one-dimensional homogeneous \revised{and heterogeneous} plane geometry is reported.
 This method is implemented as a highly accurate multigroup neutron diffusion solver based on novel transport corrections.
@@
 
-The theoretical background is detailed in~\sxn{sec:theory}, the numerical implementation is described in~\sxn{sec:imp}, the results are presented in~\sxn{sec:res} and conclusions are brought in~\sxn{sec:conc}.
+The theoretical background is detailed in~\sxn{sec:theory}, the numerical implementation is described in~\sxn{sec:imp}, the results are presented in~\sxn{sec:res}, and conclusions are brought in~\sxn{sec:conc}.
 
@@
 \begin{equation}\label{eq:RM-it}
-D^{(k+1)}\rE = - \jtr^{(k)}\rE \left[\bnabla\phi^{(k)}\rE\right]^{-1} \,\, ,
-\end{equation}
-where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
+D^{(k+1)}\rE = -\frac{\lvert\jtr^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert} \,\, ,
+\end{equation}
+where $k$ is the iteration index. \revised{The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.}
 
@@
 Nevertheless, isotropic scattering remained as a basic postulate.
-For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004} 
+For example, in a homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004} 
 \begin{equation}\label{eq:RM-it-1D-slab}
@@
 \end{eqnarray}
+
 where $E_1(x)$ is a first order exponential integral~\cite{Abramowitz-1964}.
-Note that this expression does not include the contribution of uncollided neutrons originate from the flux at the boundaries.
+Note that this expression does not include the contribution of uncollided neutrons \revised{originated from an incoming angular} flux at the boundaries.
 
@@
 % ---------------------------------------------------
-\subsection{Integral expressions for the neutron flux \& current}
+\subsection{Integral expressions for the neutron flux \revised{and} current}
 \label{sec:int-flux-J}
 
-Consider an infinite one-dimensional slab of width $a$. The angular flux in the slab is given by~\cite{Lewis-1984}
+Consider an infinite slab of width $a$. The angular flux in the slab is given by~\cite{Lewis-1984}
 \begin{subequations}\label{eq:int-ang-flx}
@@
 \mcL(x',x,E) \equiv 
-\int_{x'}^x {\sigma(x'',E) dx''} \,\, 
+\int_{x'}^x {\sigma(x'',E) dx''} \,\,, \quad \text{assuming }(x'<x)
 \end{equation}
@@
 \sigma_{s,l}(x,E\leftarrow E')dE'
-+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, 
-\end{equation}
-and the source term is expanded 
++ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, ,
+\end{equation}
+\revised{where
+\begin{equation}\label{eq:src-mmnts-explicit}
+\sigma_{s,l}(x,E\leftarrow E') = \int_{-1}^1 d\mu' P_l(\mu')\sigma_s(x,E\leftarrow E',\mu_0)
+\end{equation}
+with $\mu_0=\OO'\cdot\OO$} and the source term is expanded 
 \begin{eqnarray}\label{eq:src}
@@
 \end{eqnarray}
-Rearranging terms to get
+Rearranging \revised{terms, one gets}
 \begin{eqnarray}\label{eq:FD_diff_org}
@@
 \end{equation}
-where $\mathcal{M}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by $q_{i,g}$.
+where $\mathcal{M}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by \revised{the second term in} $q_{i,g}$ \revised{(see Eqs.~\ref{eq:FD_diff_full}-\ref{eq:FD_diff_org})}.
 Note that $\mathcal{M}$ can be written as $\mathcal{M}=\mathcal{M}_0+\delta\mathcal{M}$ distinguishing the diffusion corrections from the constant diffusion coefficients derived from the transport problem.
@@
 % ---------------------------------------------------
-\subsection{Calculation of the integral currents}
+\subsection{\revised{Evaluation of the currents by the integral form of the transport equation}}
 \label{sec:calc-int-curr}
 
-The numerical evaluation of the neutron current $J(x,E)$ at cell interfaces requires spatial integration of~\eq{eq:tot-J}.
+The numerical evaluation of the neutron current $J_g(x)$ at cell interfaces requires spatial integration of~\eq{eq:tot-J}.
 The neutron current at any interface can be calculated by considering separately contributions from all cells who are to the left or to the right of the interface.
@@
 	\bigbreak
-	\caption{Notation for numerical evaluation of integral interface currents.}
+	\caption{\revised{Notation for numerical evaluation of interface currents by the integral form of the transport equation.}}
 	\label{fig:Xi}
@@
 \begin{equation}\label{eq:BC}
-J_D(x=0) = \frac{\phi_{i=0}}{\Delta x_0/2 + \zeta} \,\, ,
-\end{equation} 
-where $\zeta$ is the extrapolation length in case of vacuum. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
+J_D(x=0) = \revised{-D_0}\frac{\phi_0}{\Delta x_0/2 + \zeta} \,\, ,
+\end{equation} 
+where $\zeta$ is the extrapolation length in case of vacuum. \revised{The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is
+taken to match transport with better agreement~\cite{Lamarsh-1966}}. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
 %
@@
 The expression for the right boundary is straightforward, implying a non-negative current.
+\revised{One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance.
+Only $\delta D$ is recalculated and the correction of the diffusion coefficient is implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.}
 
@@
 
-The reference solution for the one-dimensional homogeneous slab is generated using a Python3 discrete ordinates ($S_n$) code with $N=16$~\cite{Lewis-1984}.
+\revised{Two one-dimensional test cases are considered, homogeneous and heterogeneous.
+The reference solutions are calculated using a Python3 discrete ordinates ($S_N$) code with $N=16$~\cite{Lewis-1984}.
 The diffusion solutions and the Ronen iterations are produced using original codes developed in Pyhton3.
-All simulations utilize regular mesh in a slab of width $a=21.5$ cm.
 All thresholds are set to 1E-6 and no (over/under)-relaxation is done.
 The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$.
-Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group.
-The two-group dataset used in this study is taken from~\cite{Tomatis-2011} and is shown in Table~\ref{tab:xs}.
+Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group.}
+
+\subsection{Homogeneous case}
+\label{sec:homog}
+
+A homogeneous slab of width $a=21.5$ cm is considered, with the two-group dataset shown in Table~\ref{tab:xs} (taken from~\cite{Tomatis-2011}). 
 %
@@
 
-Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (w/ extrapolated length) and the Ronen method.
+Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (with extrapolated length) and the Ronen method.
 The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and the Ronen method, respectively.
@@
 
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion w/o RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} for half-slab.
+A comparison of the fast and thermal fluxes, as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} for half-slab.
 The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_n$ flux is also shown in Fig.~\ref{fig:fluxes}.
@@
 	\includegraphics[width=0.45\linewidth]{flux_deviation_half.pdf}	
-	\caption{Comparison of the fluxes as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion w/o RM correction ($D_0$).
+	\caption{Comparison of the fluxes as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
 Results shown here after 250 Ronen iterations.}
@@
 % ---------------------------------------------------
+\subsection{Heterogeneous case}
+\label{subsec:heterog}
+
+	\begin{figure}[htbp!] 
+	\centering
+	\begin{tikzpicture}
+	% -------------- Assembly 1 --------------
+	\node[above] at (-2,1.5) {Assembly 1};
+	\draw [fill=blue!60]   (-3,0) 	rectangle (-2.8,1.5);
+	\draw [fill=yellow!50] (-2.8,0) rectangle (-2.4,1.5);
+	\draw [fill=red!90]    (-2.4,0) rectangle (-2,1.5);
+	\draw [fill=red!90]    (-2,0) 	rectangle (-1.6,1.5);
+	\draw [fill=yellow!50] (-1.6,0) rectangle (-1.2,1.5);
+	\draw [fill=blue!60]   (-1.2,0) rectangle (-1,1.5);
+	% -------------- Assembly 2 --------------
+	\node[above] at (1,1.5) {Assembly 2};
+	\draw [fill=blue!60]   (0,0) 	rectangle (0.2,1.5);
+	\draw [fill=yellow!50] (0.2,0) rectangle (0.6,1.5);
+	\draw [fill=yellow!50] (0.6,0) rectangle (1,1.5);
+	\draw [fill=yellow!50] (1,0) 	rectangle (1.4,1.5);
+	\draw [fill=yellow!50] (1.4,0) rectangle (1.8,1.5);
+	\draw [fill=blue!60]   (1.8,0) rectangle (2,1.5);
+	% -------------- Assembly 3 --------------
+	\node[above] at (-2,-1) {Assembly 3};
+	\draw [fill=blue!60]   (-3,-2.5) 	 rectangle (-2.8,-1);
+	\draw [fill=yellow!50] (-2.8,-2.5)  rectangle (-2.4,-1);
+	\draw [fill=green!50]  (-2.4,-2.5)  rectangle (-2,-1);
+	\draw [fill=green!50]  (-2,-2.5) 	 rectangle (-1.6,-1);
+	\draw [fill=yellow!50] (-1.6,-2.5)  rectangle (-1.2,-1);
+	\draw [fill=blue!60]   (-1.2,-2.5)  rectangle (-1,-1);
+	\draw [<->] (-3,-2.7) -- node[below]{$15.24[cm]$}	(-1,-2.7);
+	% -------------- Assembly 4 --------------
+	\node[above] at (1,-1) {Assembly 4};
+	\draw [fill=blue!60]   (0,-2.5)   rectangle (0.2,-1);
+	\draw [fill=green!50] (0.2,-2.5)  rectangle (0.6,-1);
+	\draw [fill=green!50] (0.6,-2.5)  rectangle (1,-1);
+	\draw [fill=green!50] (1,-2.5)    rectangle (1.4,-1);
+	\draw [fill=green!50] (1.4,-2.5)  rectangle (1.8,-1);
+	\draw [fill=blue!60]  (1.8,-2.5)  rectangle (2,-1);
+	% -------------- Core 1 --------------
+	\node[] at (3.2,1) {Core 1};
+	\draw [fill=orange!80]   (4,0.5)   rectangle node{A1} 	(5,1.5);
+	\draw [fill=gray!90] 	 (5,0.5)   rectangle node{A2}	(6,1.5);
+	\draw [fill=orange!80]   (6,0.5)   rectangle node{A1}	(7,1.5);
+	\draw [fill=gray!90] 	 (7,0.5)   rectangle node{A2}	(8,1.5);
+	\draw [fill=orange!80]   (8,0.5)   rectangle node{A1}	(9,1.5);
+	\draw [fill=gray!90] 	 (9,0.5)   rectangle node{A2}	(10,1.5);
+	\draw [fill=orange!80]   (10,0.5)  rectangle node{A1}	(11,1.5);
+	% -------------- Core 2 --------------
+	\node[] at (3.2,-0.5) {Core 2};
+	\draw [fill=orange!80]   (4,-1)   rectangle node{A1}	(5,-0);
+	\draw [fill=gray!40] 	 (5,-1)   rectangle node{A3}	(6,-0);
+	\draw [fill=orange!80]   (6,-1)   rectangle node{A1}	(7,-0);
+	\draw [fill=gray!40] 	 (7,-1)   rectangle node{A3}	(8,-0);
+	\draw [fill=orange!80]   (8,-1)   rectangle node{A1}	(9,-0);
+	\draw [fill=gray!40] 	 (9,-1)   rectangle node{A3}	(10,-0);
+	\draw [fill=orange!80]   (10,-1)  rectangle node{A1}	(11,-0);
+	% -------------- Core 3 --------------
+	\node[] at (3.2,-2) {Core 3};
+	\draw [fill=orange!80]  (4,-2.5)  rectangle node{A1} 	(5,-1.5);
+	\draw [fill=white] 		(5,-2.5)  rectangle node{A4}	(6,-1.5);
+	\draw [fill=orange!80]  (6,-2.5)  rectangle node{A1}	(7,-1.5);
+	\draw [fill=white] 		(7,-2.5)  rectangle node{A4}	(8,-1.5);
+	\draw [fill=orange!80]  (8,-2.5)  rectangle node{A1}	(9,-1.5);
+	\draw [fill=white] 		(9,-2.5)  rectangle node{A4}	(10,-1.5);
+	\draw [fill=orange!80]  (10,-2.5) rectangle node{A1}	(11,-1.5);
+	\draw [<->] (4,-2.8) -- node[below]{$106.68[cm]$}	(11,-2.8);
+	\end{tikzpicture}
+\end{figure}
+
+\begin{table}[!htbp]	
+	\centering
+	\caption{Two-group data-set of material properties for different type of materials used in this study.} %~\cite{Rahnema-1997}
+	\label{tab:xs}
+	\begin{tabular}{lcccccccr}
+		Material&$\sigma_1$&$\sigma_2$&$\nu\sigma_{f,1}$&$\nu\sigma_{f,2}$&$\sigma_{s,1\leftarrow 1}$&$\sigma_{s,2\leftarrow 1}$&$\sigma_{s,2\leftarrow 2}$&$x[cm]$\\
+		\midrule
+		Water  (Blue)	&0.1890	 &1.4633  &0.0000	 &0.0000	 &0.1507   &0.0380		&1.4536		 &1.158\\
+		Fuel 1 (Red)	&0.2263  &1.0119  &0.0067	 &0.1241	 &0.2006   &0.0161		&0.9355		 &3.231\\
+		Fuel 2 (Yellow)	&0.2252  &0.9915  &0.0078	 &0.1542 	 &0.1995   &0.0156		&0.9014		 &3.231\\
+		Fuel 3 (Green)	&0.2173  &1.0606  &0.0056	 &0.0187	 &0.1902   &0.0136		&0.5733 	 &3.231\\
+	\end{tabular}
+\end{table}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.45\linewidth]{RM_100it_8_20_728.pdf}
+	\caption{Comparison of the fluxes as calculated by RM scheme. Results shown here after 100 Ronen iterations and 728 mesh points.}
+	\label{fig:Dcoef}
+\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.48\linewidth]{RM_dD1_100it_8_22_728.pdf}
+	\includegraphics[width=0.48\linewidth]{RM_dD2_100it_8_22_728.pdf}
+	\caption{Behavior of the correction $dD$ along the cores, of the fast and thermal energy groups. Results shown here after 100 Ronen iterations and 728 mesh points.}
+	\label{fig:Dcoef}
+\end{figure}
+
+\begin{table}[!htbp]
+	\centering
+	\caption{Reactivity differences as a function of number of iterations using the Ronen method. 728 nodes.}
+	\label{tab:dx_drho}
+	\begin{tabular}{lcccccr}
+		%\midrule
+		Benchmark & \multicolumn{2}{c}{Core 1} & \multicolumn{2}{c}{Core 2} & \multicolumn{2}{c}{Core 3}  \\ 
+		\midrule
+		{}				& $\keff$& $\Delta\rho [pcm]$& $\keff$	&$\Delta\rho [pcm]$& $\keff$	 & $\Delta\rho [pcm]$ \\
+		$S_{16}$			&1.25614	&-			 &1.00094   &-				  &0.79878		&-		\\
+		Diffusion		&1.25902	&182		 &0.99325	&-773			  &0.77805		&-3335	\\
+		RM-10			&1.25677	&40			 &1.00107	&13			 	  &0.79824		&-85	\\
+		RM-20			&1.25648	&22			 &1.00091	&-3			  	  &0.79837		&-64	\\
+		RM-50			&1.25625	&7			 &1.00076	&-18			  &0.79839		&-61	\\
+		RM-100			&1.25618	&3			 &1.00070	&-24			  &0.79838		&-62	\\
+		RM-150			&			&			 &			&				  &				&		\\
+	\end{tabular}
+\end{table}
+
+%
+% ---------------------------------------------------
 \section{Conclusions}

### 2019-12-02 FD1dMGdiff/FDsDiff1D.py
integrate heterogeneous test case from Erez; first verification of heterogeneous problem implementation

@@ -119,13 +119,14 @@ class input_data:
             raise TypeError('The input xs_media is not a dictionary.')
         if not isinstance(self.media, list):
             raise TypeError('The input media is not a list.')
-#        if len(self.xs_media) != len(self.media):
-#            raise ValueError('xs media dict and list must have the same ' +
-#                             'nb. of elements.')
+        media_set = set(m[0] for m in self.media)
+        if len(self.xs_media) != len(media_set):
+            raise ValueError('xs media dict and list must have the same ' +
+                             'nb. of elements.')
         rbnd = [m[1] for m in self.media]
         if sorted(rbnd) != rbnd:
             raise ValueError('media list must be in order from left to right!')
-        if max(rbnd) > self.L and abs(max(rbnd) - self.L)>1e-6:
+        if not np.isclose(max(rbnd), self.L):
             raise ValueError('Please check the right bounds of media (>L?)')
 
     def __str__(self):
@@ -812,12 +813,13 @@ def unfold_xs(input_data):
     for m in media:
         media_name, rbnd = m
         idx = (lbnd < xm) & (xm < rbnd)
-        st[:, idx] = np.tile(xs_media[media_name]['st'], (I, 1))[idx].T
-        nsf[:, idx] = np.tile(xs_media[media_name]['nsf'], (I, 1))[idx].T
-        chi[:, idx] = np.tile(xs_media[media_name]['chi'], (I, 1))[idx].T
-        D[:, idx] = np.tile(xs_media[media_name]['D'], (I, 1))[idx].T
-        tmp = np.tile(xs_media[media_name]['ss'][:, :, 0].flatten(), (I, 1)).T
-        ss0[:, :, idx] = tmp.reshape(G, G, I)[:,:,idx]        
+        n = sum(idx)  # nb. of True values or non-zero elements
+        st[:, idx] = np.tile(xs_media[media_name]['st'], (n, 1)).T
+        nsf[:, idx] = np.tile(xs_media[media_name]['nsf'], (n, 1)).T
+        chi[:, idx] = np.tile(xs_media[media_name]['chi'], (n, 1)).T
+        D[:, idx] = np.tile(xs_media[media_name]['D'], (n, 1)).T
+        tmp = np.tile(xs_media[media_name]['ss'][:, :, 0].flatten(), (n, 1)).T
+        ss0[:, :, idx] = tmp.reshape(G, G, n)
[…]

### 2019-12-02 FD1dMGdiff/tests/heterSlab2GIlas2003.py

@@ -10,8 +10,7 @@ This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
 """
 import sys
 sys.path.append('..')
-#from data.homog2GMC2011 import *
-from data.homog2GIlas2003 import *
+from data.heter2GIlas2003 import *
 from FDsDiff1D import input_data
 import numpy as np
 
@@ -19,103 +18,87 @@ def MyWho():
      print([v for v in globals().keys() if not v.startswith('_')])
 
 def get_fa(faid, ifa, L, nz=6):
-   '''returns a list of lists of FA id materials in location ifa in core.
-   ifa = 0,1,2,...,nfa-1 '''
-   
-   i = ifa*nz+1
+   '''Returns a list of lists of FA id materials in location ifa in core.
+   ifa = 0, 1, 2, ..., nfa-1.'''
+
+   i = ifa * nz + 1
    if faid == 1:
-      media = [ 
+      media = [
             ['WATER', L[i]],
             ['FUELI', L[i+1]],
             ['FUELII', L[i+2]],
             ['FUELII', L[i+3]],
             ['FUELI', L[i+4]],
             ['WATER', L[i+5]]
-            ]
+              ]
    elif faid == 2:
-      media = [ 
+      media = [
             ['WATER', L[i]],
             ['FUELI', L[i+1]],
             ['FUELI', L[i+2]],
             ['FUELI', L[i+3]],
             ['FUELI', L[i+4]],
             ['WATER', L[i+5]]
-            ]
+              ]
    elif faid == 3:
-      media = [ 
+      media = [
             ['WATER', L[i]],
             ['FUELI', L[i+1]],
             ['FUELIII', L[i+2]],
             ['FUELIII', L[i+3]],
             ['FUELI', L[i+4]],
             ['WATER', L[i+5]]
-            ]
+              ]
    elif faid == 4:
-      media = [ 
+      media = [
             ['WATER', L[i]],
             ['FUELIII', L[i+1]],
             ['FUELIII', L[i+2]],
             ['FUELIII', L[i+3]],
             ['FUELIII', L[i+4]],
             ['WATER', L[i+5]]
-            ]
+              ]
    else:
[…]

### 2019-12-03 docs/EPJP2019/response/response.tex
A (almost final) revised version of the ms.
Tex file is updated:
	modified:   Gross-EPJP-2019.tex

New figures were added:
	modified:   figures/RM_dD1_100it_8_22_728.pdf
	modified:   figures/RM_dD2_100it_8_22_728.pdf
	new file:   figures/RM_flx_100it_8_22_728.pdf
	new file:   figures/Sn_Diff_RM_Tomatis2011.pdf
	new file:   figures/Sn_Diff_RM_core_1.pdf
	new file:   figures/Sn_Diff_RM_core_2.pdf
	new file:   figures/Sn_Diff_RM_core_3.pdf
	new file:   figures/dD_Tomatis2011_400_250it.pdf
	new file:   figures/flx_err_Tomatis2011_400_250.pdf
	new file:   figures/flx_err_diff_C1.pdf
	new file:   fi

@@
 Ronen did not elaborate on this issue in his technical note from 2004.
-Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current at this location (where the flux gradiaent is weak).
+Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current at this location (where the flux gradient is weak).
 We did not try to find the analytic limit of this expression for $D$, however we assume that this ratio between two expressions, which vanish at the same location, approaches some constant value.\\ \\ Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
-The (more accuarte) surface current $J_{tr}$, calculated by intergal expression, is written as the sum of the surface current calculated by diffusion, $J_D$, plus a correction $\delta J$.
-Hence, when the current vanishes, the correction $\delta J$ valishes.
-Moreover, the correction is writtten as in Eq.
+The (more accurate) surface current $J_{tr}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_D$, plus a correction $\delta J$.
+Hence, when the current vanishes, the correction $\delta J$ vanishes.
+Moreover, the correction is written as in Eq.
 (21), avoiding the potential divergence resulting from division by zero.}
@@
 \\ \\
-\revised{An entire benchark was added to the results section.
+\revised{An entire benchmark was added to the results section.
 The chosen benchmark is a one-dimensional highly heterogeneous core representing a BWR core.
@@
 \\ \\
-\revised{The sentence was chnaged to "...
+\revised{The sentence was changed to "...
 $\mathcal{F}$ is the neutron generation operator given by \emph{the second term in} $q_{i,g}$ (see Eqs.

### 2019-12-03 docs/EPJP2019/Gross-EPJP-2019.tex
A (almost final) revised version of the ms.
Tex file is updated:
	modified:   Gross-EPJP-2019.tex

New figures were added:
	modified:   figures/RM_dD1_100it_8_22_728.pdf
	modified:   figures/RM_dD2_100it_8_22_728.pdf
	new file:   figures/RM_flx_100it_8_22_728.pdf
	new file:   figures/Sn_Diff_RM_Tomatis2011.pdf
	new file:   figures/Sn_Diff_RM_core_1.pdf
	new file:   figures/Sn_Diff_RM_core_2.pdf
	new file:   figures/Sn_Diff_RM_core_3.pdf
	new file:   figures/dD_Tomatis2011_400_250it.pdf
	new file:   figures/flx_err_Tomatis2011_400_250.pdf
	new file:   figures/flx_err_diff_C1.pdf
	new file:   fi

@@
 \usepackage{cite}
+\usepackage{subcaption} % For subfigure
+\captionsetup{compatibility=false}
+\usepackage{wrapfig}
+%\usepackage{caption} % Caption in subfigure
 \usepackage{tikz}
@@
 % Define block styles
-\usepackage{tikz}
+
+\usetikzlibrary{patterns}
 \usetikzlibrary{shapes,arrows}
@@
 \abstract{
-In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue \revised{in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks}.
-The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and \revised{is} driven by the solutions of the integral transport equation.
-The \revised{spatially-dependent} diffusion constants are modified \revised{locally} in order to produce new estimates of the surface currents \revised{using an integral transport expression}.
-The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme \revised{using} drift terms.
+In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks.
+The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and is driven by the solutions of the integral transport equation.
+The spatially-dependent diffusion constants are modified locally in order to produce new estimates of the surface currents using an integral transport expression.
+The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme using drift terms.
 The corrected solutions are compared against reference results obtained by a discrete ordinate code.
@@
 A conservative estimation of the memory needed for reasonably accurate full-core Monte Carlo neutronic calculation is in the range of terabytes (TBs)~\cite{Martin-2012}.
-\revised{The growing demand for high-accuracy and high-precision full-core computations challenges not only today’s high-end computing systems but will also challenge the near future (e.g., Exascale) computers~\cite{Martin-2012,Smith-2011,Kim-2019}.}
+The growing demand for high-accuracy and high-precision full-core computations challenges not only today’s high-end computing systems but will also challenge the near future (e.g., Exascale) computers~\cite{Martin-2012,Smith-2011,Kim-2019}.
 
@@
 
-In this paper, the development, implementation, and qualification of the Ronen Method~\cite{Ronen-2004} in one-dimensional homogeneous \revised{and heterogeneous} plane geometry is reported.
+In this paper, the development, implementation, and qualification of the Ronen Method~\cite{Ronen-2004} in one-dimensional homogeneous and heterogeneous plane geometry is reported.
 This method is implemented as a highly accurate multigroup neutron diffusion solver based on novel transport corrections.
@@
 \end{equation}
-where $k$ is the iteration index. \revised{The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.}
+where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
 
@@
 where $E_1(x)$ is a first order exponential integral~\cite{Abramowitz-1964}.
-Note that this expression does not include the contribution of uncollided neutrons \revised{originated from an incoming angular} flux at the boundaries.
+Note that this expression does not include the contribution of uncollided neutrons originated from an incoming angular flux at the boundaries.
 
@@
 % ---------------------------------------------------
-\subsection{Integral expressions for the neutron flux \revised{and} current}
+\subsection{Integral expressions for the neutron flux and current}
 \label{sec:int-flux-J}
@@
 \end{equation}
-\revised{where
+where
 \begin{equation}\label{eq:src-mmnts-explicit}
@@
 \end{equation}
-with $\mu_0=\OO'\cdot\OO$} and the source term is expanded 
+with $\mu_0=\OO'\cdot\OO$ and the source term is expanded 
 \begin{eqnarray}\label{eq:src}
@@
 \end{eqnarray}
-Rearranging \revised{terms, one gets}
+Rearranging terms, one gets
 \begin{eqnarray}\label{eq:FD_diff_org}
@@
 \end{equation}
-where $\mathcal{M}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by \revised{the second term in} $q_{i,g}$ \revised{(see Eqs.~\ref{eq:FD_diff_full}-\ref{eq:FD_diff_org})}.
+where $\mathcal{M}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by the second term in $q_{i,g}$ (see Eqs.~\ref{eq:FD_diff_full}-\ref{eq:FD_diff_org}).
 Note that $\mathcal{M}$ can be written as $\mathcal{M}=\mathcal{M}_0+\delta\mathcal{M}$ distinguishing the diffusion corrections from the constant diffusion coefficients derived from the transport problem.
@@
 % ---------------------------------------------------
-\subsection{\revised{Evaluation of the currents by the integral form of the transport equation}}
+\subsection{Evaluation of the currents by the integral form of the transport equation}
 \label{sec:calc-int-curr}
@@
 	\bigbreak
-	\caption{\revised{Notation for numerical evaluation of interface currents by the integral form of the transport equation.}}
+	\caption{Notation for numerical evaluation of interface currents by the integral form of the transport equation.}
 	\label{fig:Xi}
@@
 \begin{equation}\label{eq:BC}
-J_D(x=0) = \revised{-D_0}\frac{\phi_0}{\Delta x_0/2 + \zeta} \,\, ,
-\end{equation} 
-where $\zeta$ is the extrapolation length in case of vacuum. \revised{The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is
-taken to match transport with better agreement~\cite{Lamarsh-1966}}. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
+J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta} \,\, ,
+\end{equation} 
+where $\zeta$ is the extrapolation length in case of vacuum. The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is
+taken to match transport with better agreement~\cite{Lamarsh-1966}. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
 %
@@
 The expression for the right boundary is straightforward, implying a non-negative current.
-\revised{One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance.
-Only $\delta D$ is recalculated and the correction of the diffusion coefficient is implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.}
+One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance.
+Only $\delta D$ is recalculated and the correction of the diffusion coefficient is implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
 
@@
 
-\revised{Two one-dimensional test cases are considered, homogeneous and heterogeneous.
+Two one-dimensional test cases are considered, homogeneous and heterogeneous.
 The reference solutions are calculated using a Python3 discrete ordinates ($S_N$) code with $N=16$~\cite{Lewis-1984}.
@@
 The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$.
-Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group.}
-
+Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group.
+
+%
+% ---------------------------------------------------
 \subsection{Homogeneous case}
@@
 
-A homogeneous slab of width $a=21.5$ cm is considered, with the two-group dataset shown in Table~\ref{tab:xs} (taken from~\cite{Tomatis-2011}). 
+A homogeneous slab of width $a=21.5$ cm is considered, with the two-group macroscopic cross sections shown in Table~\ref{tab:xs} (taken from~\cite{Tomatis-2011}). 
 %
@@
 	\centering
-	\caption{Two-group dataset used in this study~\cite{Tomatis-2011}.}
+	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] used for the homogeneous case~\cite{Tomatis-2011}.}
 	\label{tab:xs}
@@
 
-%\begin{table}[htp!]
+A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} (left panel) for half-slab.
+The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:fluxes} (upper right panel).
+The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.
+
+%The diffusion and transport currents calculated using the converged Ronen solution are plotted in Fig.~\ref{fig:current}.
+The full slab solution exhibits anti-symmetry, as expected, whereas the corrected diffusion current exhibit non-trivial behavior near the boundary.
+%Fig.~\ref{fig:Dcoef} show the original standard diffusion coefficients ($D=(3\sigma_{tr})^{-1}$), The RM correction terms ($\delta D$), and the corrected (spatially-dependent) diffusion $D$.
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{subfigure}[b]{.44\linewidth}
+		% First figure
+		\includegraphics[width=\linewidth]{Sn_Diff_RM_Tomatis2011.pdf}
+		%\caption{A tall figure}
+	\end{subfigure}
+	~
+	\begin{subfigure}[b]{.54\linewidth}
+		% Second figure
+		~\includegraphics[width=0.97\linewidth]{flx_err_Tomatis2011_400_250.pdf}
+		%\caption{A short figure}		
+		%\vspace{2ex}
+		% Third figure
+		\includegraphics[width=\linewidth]{dD_Tomatis2011_400_250it.pdf}
+		%\caption{A short figure}
+	\end{subfigure}
+	\caption{Left: Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
+Right, up: Deviation of the fluxes with respect to the reference solution.
+Right, down: The RM correction terms ($\delta D$).
+Results shown here after 250 Ronen iterations.}
+	\label{fig:fluxes}
+\end{figure}
+
+%\begin{wrapfigure}{r}[0pt]{0.3\textwidth}
 %	\centering
-%	\caption{Reactivity differences in pcm by refining the mesh.}
-%	\label{tab:kconv}
-%	\begin{tabular}{crr}
-%		\multirow{2}{*}{$I$} & \multicolumn{2}{c}{$\Delta \rho$ [pcm]} \\ \cline{2-3}
-%		& $it=0$ & $it=100$ \\ \hline
-%		~50 & 550.22 & 170.35 \\
-%		100 & 556.85 & ~36.08 \\
-%		200 & 558.50 & ~~1.72
-%	\end{tabular}
-%\end{table}
-
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} for half-slab.
-The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_n$ flux is also shown in Fig.~\ref{fig:fluxes}.
-The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.
-
-The diffusion and transport currents calculated using the converged Ronen solution are plotted in Fig.~\ref{fig:current}.
-The full slab solution exhibits anti-symmetry, as expected, whereas the corrected diffusion current exhibit non-trivial behavior near the boundary.
-Fig.~\ref{fig:Dcoef} show the original standard diffusion coefficients ($D=(3\sigma_{tr})^{-1}$), the RM correction terms ($\delta D$), and the corrected (spatially-dependent) diffusion $D$.
+%	\includegraphics[width=\linewidth]{convergence.pdf}
+%	\caption{Convergence of the flux (max deviation) and the criticality eigenvalue.}
+%	\label{fig:conv}
+%\end{wrapfigure}
+
+\begin{figure}[h!]
+	% convergence
+	\centering
+	\includegraphics[width=0.4\linewidth]{convergence.pdf}
+	\caption{Convergence of the flux (max deviation) and the criticality
+		eigenvalue.}
+	\label{fig:conv}
+\end{figure}
+The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:fluxes} (lower right panel).
 It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary.
@@
 The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
-The spatial flux convergence of the Ronen iterations with respect to the reference $S_n$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.
-
-% fluxes
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.45\linewidth]{flux0_half.pdf}
-	\includegraphics[width=0.45\linewidth]{flux_deviation_half.pdf}	
-	\caption{Comparison of the fluxes as calculated by the reference $S_n$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
-Results shown here after 250 Ronen iterations.}
-	\label{fig:fluxes}
-\end{figure}
-
-% current
-\begin{figure}[htbp!]
-	\centering
-	%\includegraphics[width=0.45\linewidth]{current.pdf}
-	\includegraphics[width=0.45\linewidth]{current_half.pdf}	
-	\caption{The diffusion and transport currents calculated using the converged Ronen solution.}
-	\label{fig:current}
-\end{figure}
-
-% D-coef
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.45\linewidth]{D_coeffs.pdf}
-	%\includegraphics[width=0.45\linewidth]{D_coeffs_half.pdf}	
-	\caption{The original standard diffusion coefficients ($D=(3\sigma_{tr})^{-1}$),
-		the RM correction terms ($\delta D$), and the corrected (spatially-dependent)
-		diffusion $D$. Results shown here after 250 Ronen iterations.}
-	\label{fig:Dcoef}
-\end{figure}
+The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.
 
 % convergence
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.45\linewidth]{convergence.pdf}
-	\caption{Convergence of the flux (max deviation) and the criticality
-		eigenvalue.}
-	\label{fig:conv}
-\end{figure}
-
-% convergence
-\begin{figure}[htbp!]
+\begin{figure}[h!]
 	\centering
@@
 	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2_sn.pdf}
-	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_n$ solution for the left half slab.}
+	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab.}
 	\label{fig:conv3}
@@
 \label{subsec:heterog}
+
+The heterogeneous benchmark defines three heterogeneous cores, each is 7 fuel assemblies long and comprised of four different fuel assemblies made of four different materials~\cite{Rahnema-1997}, as shown in Fig.~\ref{fig:hetro-core}.
+Material properties for each region of the assemblies are given in
+Table~\ref{tab:xs2}.
+Configuration 1 represents the least heterogeneous core with rather smooth flux gradients.
+On the contrary, configuration 3 represents the most heterogeneous core with the steepest flux gradients and can serve as a limiting case.
+Void boundary conditions are imposed on both ends of the core.
 
@@
 	\node[above] at (-2,1.5) {Assembly 1};
-	\draw [fill=blue!60]   (-3,0) 	rectangle (-2.8,1.5);
-	\draw [fill=yellow!50] (-2.8,0) rectangle (-2.4,1.5);
-	\draw [fill=red!90]    (-2.4,0) rectangle (-2,1.5);
-	\draw [fill=red!90]    (-2,0) 	rectangle (-1.6,1.5);
-	\draw [fill=yellow!50] (-1.6,0) rectangle (-1.2,1.5);
-	\draw [fill=blue!60]   (-1.2,0) rectangle (-1,1.5);
+	\draw[pattern=north west lines, preaction={fill=blue!70}] (-3,0)   rectangle (-2.8,1.5);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		  (-2.8,0) rectangle (-2.4,1.5);
+	\draw[fill=red!80] 										  (-2.4,0) rectangle (-2,1.5);
+	\draw[fill=red!80]	  									  (-2,0)   rectangle (-1.6,1.5);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		  (-1.6,0) rectangle (-1.2,1.5);
+	\draw[pattern=north west lines, preaction={fill=blue!70}] (-1.2,0) rectangle (-1,1.5);
 	% -------------- Assembly 2 --------------
 	\node[above] at (1,1.5) {Assembly 2};
-	\draw [fill=blue!60]   (0,0) 	rectangle (0.2,1.5);
-	\draw [fill=yellow!50] (0.2,0) rectangle (0.6,1.5);
-	\draw [fill=yellow!50] (0.6,0) rectangle (1,1.5);
-	\draw [fill=yellow!50] (1,0) 	rectangle (1.4,1.5);
-	\draw [fill=yellow!50] (1.4,0) rectangle (1.8,1.5);
-	\draw [fill=blue!60]   (1.8,0) rectangle (2,1.5);
+	\draw[pattern=north west lines, preaction={fill=blue!70}] (0,0)	  rectangle (0.2,1.5);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		  (0.2,0) rectangle (0.6,1.5);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		  (0.6,0) rectangle (1,1.5);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		  (1,0)   rectangle (1.4,1.5);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		  (1.4,0) rectangle (1.8,1.5);
+	\draw[pattern=north west lines, preaction={fill=blue!70}] (1.8,0) rectangle (2,1.5);
 	% -------------- Assembly 3 --------------
 	\node[above] at (-2,-1) {Assembly 3};
-	\draw [fill=blue!60]   (-3,-2.5) 	 rectangle (-2.8,-1);
-	\draw [fill=yellow!50] (-2.8,-2.5)  rectangle (-2.4,-1);
-	\draw [fill=green!50]  (-2.4,-2.5)  rectangle (-2,-1);
-	\draw [fill=green!50]  (-2,-2.5) 	 rectangle (-1.6,-1);
-	\draw [fill=yellow!50] (-1.6,-2.5)  rectangle (-1.2,-1);
-	\draw [fill=blue!60]   (-1.2,-2.5)  rectangle (-1,-1);
+	\draw[pattern=north west lines, preaction={fill=blue!70}]  (-3,-2.5)   rectangle (-2.8,-1);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		   (-2.8,-2.5) rectangle (-2.4,-1);
+	\draw[pattern=north east lines, preaction={fill=green!50}] (-2.4,-2.5) rectangle (-2,-1);
+	\draw[pattern=north east lines, preaction={fill=green!50}] (-2,-2.5)   rectangle (-1.6,-1);
+	\draw[pattern=dots, preaction={fill=yellow!50}] 		   (-1.6,-2.5) rectangle (-1.2,-1);
+	\draw[pattern=north west lines, preaction={fill=blue!70}] (-1.2,-2.5)  rectangle (-1,-1);
 	\draw [<->] (-3,-2.7) -- node[below]{$15.24[cm]$}	(-1,-2.7);
@@
 	\node[above] at (1,-1) {Assembly 4};
-	\draw [fill=blue!60]   (0,-2.5)   rectangle (0.2,-1);
-	\draw [fill=green!50] (0.2,-2.5)  rectangle (0.6,-1);
-	\draw [fill=green!50] (0.6,-2.5)  rectangle (1,-1);
-	\draw [fill=green!50] (1,-2.5)    rectangle (1.4,-1);
-	\draw [fill=green!50] (1.4,-2.5)  rectangle (1.8,-1);
-	\draw [fill=blue!60]  (1.8,-2.5)  rectangle (2,-1);
+	\draw[pattern=north west lines, preaction={fill=blue!70}]  (0,-2.5)    rectangle (0.2,-1); 
+	\draw[pattern=north east lines, preaction={fill=green!50}] (0.2,-2.5)  rectangle (0.6,-1);
+	\draw[pattern=north east lines, preaction={fill=green!50}] (0.6,-2.5)  rectangle (1,-1);
+	\draw[pattern=north east lines, preaction={fill=green!50}] (1,-2.5)    rectangle (1.4,-1);
+	\draw[pattern=north east lines, preaction={fill=green!50}] (1.4,-2.5)  rectangle (1.8,-1);
+	\draw[pattern=north west lines, preaction={fill=blue!70}]  (1.8,-2.5)  rectangle (2,-1);
 	% -------------- Core 1 --------------
@@
 	\end{tikzpicture}
+	\caption{Schematic illustration of the fuel assemblies and core composition and geometry~\cite{Rahnema-1997}.}
+	\label{fig:hetro-core}	
 \end{figure}
 
-\begin{table}[!htbp]	
-	\centering
-	\caption{Two-group data-set of material properties for different type of materials used in this study.} %~\cite{Rahnema-1997}
-	\label{tab:xs}
+\begin{table}[htbp!]	
+	\centering
+	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] used for the heterogeneous case~\cite{Rahnema-1997}. Colors are in accordance with Fig.~\ref{fig:hetro-core}.} 
+	\label{tab:xs2}
 	\begin{tabular}{lcccccccr}
@@
 
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.45\linewidth]{RM_100it_8_20_728.pdf}
-	\caption{Comparison of the fluxes as calculated by RM scheme. Results shown here after 100 Ronen iterations and 728 mesh points.}
-	\label{fig:Dcoef}
-\end{figure}
-
-\begin{figure}[htbp!]
-	\centering
-	\includegraphics[width=0.48\linewidth]{RM_dD1_100it_8_22_728.pdf}
-	\includegraphics[width=0.48\linewidth]{RM_dD2_100it_8_22_728.pdf}
-	\caption{Behavior of the correction $dD$ along the cores, of the fast and thermal energy groups. Results shown here after 100 Ronen iterations and 728 mesh points.}
-	\label{fig:Dcoef}
-\end{figure}
+Table~\ref{tab:dx_drho2} shows the reactivity differences between standard diffusion (with extrapolated length) and the Ronen method (at increasing number of iterations) with respect to the reference solution for each of the three core configurations.
+The standard diffusion solution perform rather well for core 1 with deviation of 182 pcm, but fails for cores 2 and 3 with deviation of 773 and 3335 pcm, respectively.
+This is explained by the fact that cores 2 and 3 are more heterogeneous with respect to core 1.
+The Ronen method performs better than standard diffusion for all three cores, even after merely 10 iterations.
+Additional Ronen iterations further improve the estimated multiplication factor but less with milder changes.
 
@@
 	\caption{Reactivity differences as a function of number of iterations using the Ronen method. 728 nodes.}
-	\label{tab:dx_drho}
+	\label{tab:dx_drho2}
 	\begin{tabular}{lcccccr}
 		%\midrule
-		Benchmark & \multicolumn{2}{c}{Core 1} & \multicolumn{2}{c}{Core 2} & \multicolumn{2}{c}{Core 3}  \\ 
+		Method & \multicolumn{2}{c}{Core 1} & \multicolumn{2}{c}{Core 2} & \multicolumn{2}{c}{Core 3}  \\ 
 		\midrule
-		{}				& $\keff$& $\Delta\rho [pcm]$& $\keff$	&$\Delta\rho [pcm]$& $\keff$	 & $\Delta\rho [pcm]$ \\
+		{}				& $\keff$& $\Delta\rho$ [pcm]& $\keff$	&$\Delta\rho$ [pcm]& $\keff$ &$\Delta\rho$ [pcm] \\
 		$S_{16}$		&1.25614	&-			 &1.00094   &-				  &0.79878		&-		\\
@@
 		RM-100			&1.25618	&3			 &1.00070	&-24			  &0.79838		&-62	\\		
-		RM-150			&			&			 &			&				  &				&		\\
 	\end{tabular}
@@
 
+The two-group flux distribution across each core is shown in Fig.~\ref{fig:hetero-flux} for standard diffusion ($D_0$), Ronen method (RM) and the S16 reference solution.
+RM results are shown for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.
+On a first glance, it is easy to see that standard diffusion fails to produce the steep flux gradients across material interfaces, especially between fuel and water.
+This is more pronounced for the fast flux, where even in core 1 it is not described correctly.
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_1.pdf}
+	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_2.pdf}
+	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_3.pdf}
+	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S16 reference solution.
+Vertical grid lines are located at assemblies interfaces.
+RM results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
+	\label{fig:hetero-flux}
+\end{figure}
+
+The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions are shown in Fig.~\ref{fig:hetero-flux-dev} for each core.
+For all cores, the fast flux is poorly reproduced by standard diffusion, with up to $\sim$10\% deviations at the inner interfaces and $\sim$20\% at the outer boundaries (in agreement with the homogeneous case).
+Deviations of the thermal flux calculated by diffusion increase from $\sim$4\% to $\sim$10\% as the heterogeneity of the core increases.
+The deviations of the fast and thermal flux calculated by Ronen method are much smaller (practically negligible), and are smaller than $\sim$2\%.
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.6\linewidth]{flx_err_diff_C1.pdf}
+	\includegraphics[width=0.6\linewidth]{flx_err_diff_C2.pdf}
+	\includegraphics[width=0.6\linewidth]{flx_err_diff_C3.pdf}
+	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions for each core.
+Vertical grid lines are located at assemblies interfaces.
+RM results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
+	\label{fig:hetero-flux-dev}
+\end{figure}
+
+It is illustrative to examine the spatial distribution of the Ronen method correction factors for the heterogeneous case.
+The behavior of the correction factor may seem a bit erratic, but can be explained.
+In regions where the flux gradients are small, the correction factors tend to vanish and actually produce solutions similar to standard diffusion.
+However, in regions where the flux gradients are steep, the correction factors do not vanish and play an important role in reproducing the correct flux shape.
+
+% convergence
+%\begin{figure}[htbp!]
+%	\centering
+%	\includegraphics[width=0.55\linewidth]{k_over_i_C3_10RMit.pdf}
+%	\caption{Convergence of $\keff$ over number of grid points along core no. 3, for 100 RM iterations, and standard diffusion calculation.}
+%	\label{fig:k_vs_I}
+%\end{figure}
+
+%\begin{figure}[htbp!]
+%	\centering
+%	\includegraphics[width=0.45\linewidth]{RM_flx_100it_8_22_728.pdf}
+%	\caption{Fluxes as calculated by RM scheme. Results shown here after 100 Ronen iterations and 728 mesh points.}
+%	\label{fig:Cores_RMflx}
+%\end{figure}
+
+\begin{figure}[htbp!]
+	\centering
+	\includegraphics[width=0.6\linewidth]{RM_dD1_100it_8_22_728.pdf}
+	\includegraphics[width=0.6\linewidth]{RM_dD2_100it_8_22_728.pdf}
+	\caption{Behavior of the Ronen method correction factor $dD$ along the core, for the fast and thermal fluxes.
+Vertical grid lines are located at assemblies interfaces, results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
+	\label{fig:Dcoef}
+\end{figure}
+
 %
@@
 The Ronen Method was first proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux.
-This yielded an iterative scheme leading to new flux distributions solved by a diffusion solver but with a (spatially) modified diffusion coefficient driving the diffusion solution to that of the integral transport equation.
+This yielded an iterative scheme leading to new flux distributions solved by a diffusion solver but with additional (spatially) corrected diffusion terms, driving the diffusion solution to that of the integral transport equation.
 The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning.
@@
 
-More accurate results are obtained for the two-group benchmark problem reported in \cite{Tomatis-2011}.
-In general, slow convergence is observed for the scalar flux, whose larger discrepancy with respect to the reference is always located on the vacuum boundary.
+More accurate results are obtained for the two-group benchmark problem reported in \cite{Tomatis-2011} and new results are reported for a heterogeneous benchmark.
+In general, slow convergence is observed for the scalar flux with the larger discrepancies, comparing to the reference, located on the vacuum boundary and on the material interfaces.
 Although the method is converging to the reference results provided by a discrete ordinate transport code, the improvement of the convergence rate and the use of coarser meshes are crucial for the advancement of the methodology in practical applications.
-These topics will be addressed as future developments, as well as heterogeneous systems and higher-order anisotropy.
+These topics will be addressed as future developments, as well as higher-order anisotropy.
 
@@
 \label{sec:acknow}
-
 The authors express their gratitude to Prof. Yigal Ronen who initiated the idea for this study. R.G. is partially supported by the Israel Ministry of Energy, contract no. 216-11-008.

### 2019-12-04 docs/EPJP2019/response/response.tex
Final revision for comments from Daniele and Roy

@@
 Moreover, the correction is written as in Eq.
-(21), avoiding the potential divergence resulting from division by zero.}
+(21), avoiding the potential divergence resulting from division by zero.
+This comment was added to the text.}
 \\ \\
@@
 The Marshak boundary conditions are reproduced by $\zeta=2D$).
-The values assumed for the calculations are 1.3367 and 0.5459 cm for the fast and thermal groups, respectively.
+The values assumed for the homogeneous slab calculations are 1.3367 and 0.5459 cm for the fast and thermal groups, respectively.
 \\ \\
@@
 Note that the correction in our numerical scheme is not by $D = D_0 + \delta D$ nor by $D = \delta D$.
-The correction of the diffusion coefficient is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
+The correction is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
 }
@@
 \\ \\
-\revised{T}
+\revised{The above statement was changed to: "Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$.".\\ \\We completely agree that the choice of BC matters and it affects the numerical solutions, since BC should adequately describe the physical problem.
+We also speculate that the slow convergence rate of the flux (by RM iterations) near the boundaries is linked to the choice of proper BC.
+We intend to study this issue in the near future.
+}
 \\ \\
@@
 \\ \\
-\revised{T}
+\revised{Fig. 5 and any reference to it are omitted from the revised manuscript.}
 \\ \\
@@
 \\ \\
-\revised{T}
+\revised{We have added (where possible) explicit text indications on the figure itself to distinguish between the different quantities.}
 \\ \\
@@
 \\ \\
-\revised{T}
+\revised{The following text was added to the manuscript:\\ The initial diffusion solution is smoother than the transport one.
+Hence, as can be seen in Fig.
+4 (in the original and revised ms), the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
+The Ronen iterations "push" the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
+Hence, $\phi^{k-1}$ is smaller in the center and larger at the boundary comparing to $\phi^(k)$.	This effect of the Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
+}
 \\ \\

### 2019-12-04 docs/EPJP2019/Gross-EPJP-2019.tex
Final revision for comments from Daniele and Roy

@@
 \end{equation} 
-where $\zeta$ is the extrapolation length in case of vacuum. The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is
-taken to match transport with better agreement~\cite{Lamarsh-1966}. Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$. 
+where $\zeta$ is the extrapolation length in case of vacuum.
+The Marshak boundary conditions are reproduced by $\zeta=2D$, but the more accurate value $\zeta\approx 2.13D$ is taken to match transport with better agreement~\cite{Lamarsh-1966}.
+Reflection can be reproduced by $\zeta\rightarrow\infty$, whereas the condition of zero-flux is realized by $\zeta=0$.
 %
@@
 One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance.
-Only $\delta D$ is recalculated and the correction of the diffusion coefficient is implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
+Only $\delta D$ is recalculated and the correction is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
 
@@
 The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$.
-Void boundary conditions are used (extrapolated distance) at the edges of the slab and they are constant for each energy group.
+Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$.
 
@@
 
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:fluxes} (left panel) for half-slab.
-The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:fluxes} (upper right panel).
+A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for half-slab.
+The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:slab-fluxes-dev}.
+The corresponding Ronen method correction factors $\delta D$ are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
+
 The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.
@@
 	\centering
-	\begin{subfigure}[b]{.44\linewidth}
-		% First figure
-		\includegraphics[width=\linewidth]{Sn_Diff_RM_Tomatis2011.pdf}
-		%\caption{A tall figure}
-	\end{subfigure}
-	~
-	\begin{subfigure}[b]{.54\linewidth}
-		% Second figure
-		~\includegraphics[width=0.97\linewidth]{flx_err_Tomatis2011_400_250.pdf}
-		%\caption{A short figure}		
-		%\vspace{2ex}
-		% Third figure
-		\includegraphics[width=\linewidth]{dD_Tomatis2011_400_250it.pdf}
-		%\caption{A short figure}
-	\end{subfigure}
-	\caption{Left: Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
-Right, up: Deviation of the fluxes with respect to the reference solution.
-Right, down: The RM correction terms ($\delta D$).
+	\includegraphics[width=0.65\linewidth]{Sn_Diff_RM_Tomatis2011.pdf}
+	\caption{Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
 Results shown here after 250 Ronen iterations.}
-	\label{fig:fluxes}
+	\label{fig:slab-fluxes}		
+\end{figure}
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.65\linewidth]{flx_err_Tomatis2011_400_250.pdf}
+	\caption{Deviation of the fluxes with respect to the reference solution after 250 Ronen iterations.}
+	\label{fig:slab-fluxes-dev}
+\end{figure}
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.65\linewidth]{dD_Tomatis2011_400_250it.pdf}
+	\caption{The Ronen method correction factors ($\delta D$). Results shown here after 250 Ronen iterations.}
+	\label{fig:slab-RM-corr-factor}
 \end{figure}
@@
 \end{figure}
-The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:fluxes} (lower right panel).
+
+The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
 It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary.
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_1.pdf}
-	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2.pdf}
-	\caption{The spatial flux convergence between two successive Ronen iterations for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].}
+	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1.pdf}
+	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2.pdf}
+	\caption{The spatial flux convergence between two successive Ronen iterations for the left half slab, according to $\Delta\phi = (\phi^{(k-1)}-\phi^{(k)})/\phi^{(k-1)}$ [\%].}
 	\label{fig:conv2}
@@
 	\centering
-	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_1_sn.pdf}
-	\includegraphics[width=0.45\linewidth]{flux_deviation_half_it_2_sn.pdf}
+	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1_sn.pdf}
+	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2_sn.pdf}
 	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab.}
@@
 
+Notice the change of sign in the flux convergence $\Delta \phi$ in Fig.~\ref{fig:conv2} between the center (negative) and the boundary (positive) of the slab.
+The initial diffusion solution is smoother than the transport one.
+Hence, as can be seen in Fig.~\ref{fig:slab-fluxes}, the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
+The Ronen iterations "push" the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
+Hence, $\phi^{(k-1)}$ is smaller in the center and larger at the boundary comparing to $\phi^{(k)}$.
+This effect of the Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
 %
@@
 The heterogeneous benchmark defines three heterogeneous cores, each is 7 fuel assemblies long and comprised of four different fuel assemblies made of four different materials~\cite{Rahnema-1997}, as shown in Fig.~\ref{fig:hetro-core}.
-Material properties for each region of the assemblies are given in
-Table~\ref{tab:xs2}.
+Material properties for each region of the assemblies are given in Table~\ref{tab:xs2}.
 Configuration 1 represents the least heterogeneous core with rather smooth flux gradients.
@@
 	\centering
-	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_1.pdf}
-	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_2.pdf}
-	\includegraphics[width=0.32\linewidth]{Sn_Diff_RM_core_3.pdf}
+	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_1.pdf}
+	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_2.pdf}
+	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_3.pdf}
 	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S16 reference solution.
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{flx_err_diff_C1.pdf}
-	\includegraphics[width=0.6\linewidth]{flx_err_diff_C2.pdf}
-	\includegraphics[width=0.6\linewidth]{flx_err_diff_C3.pdf}
+	\includegraphics[width=0.65\linewidth]{flx_err_diff_C1.pdf}
+	\includegraphics[width=0.65\linewidth]{flx_err_diff_C2.pdf}
+	\includegraphics[width=0.65\linewidth]{flx_err_diff_C3.pdf}
 	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions for each core.
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{RM_dD1_100it_8_22_728.pdf}
-	\includegraphics[width=0.6\linewidth]{RM_dD2_100it_8_22_728.pdf}
+	\includegraphics[width=0.65\linewidth]{RM_dD1_100it_8_22_728.pdf}
+	\includegraphics[width=0.65\linewidth]{RM_dD2_100it_8_22_728.pdf}
 	\caption{Behavior of the Ronen method correction factor $dD$ along the core, for the fast and thermal fluxes.
@@
 The solution of the diffusion equation, on the other hand, offers many numerical advantages, e.g., speed and robustness.
-Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues resulting from small flux gradients.
+
+The relation in Eq.~\eqref{eq:RM-it-1D-slab} becomes problematic where the gradient of the flux is small, which is usually the zone where diffusion works better.
+Ronen did not elaborate on this issue in his technical note from 2004.
+Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current where the flux gradient is weak.
+We hypothesize that this ratio, between two expressions which tend to zero at the same location, approaches some constant value since there exist a diffusion coefficient at that location.
+
+Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
+The (more accurate) surface current $J_{\texttt{tr}}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_\texttt{D}$, plus a correction $\delta J$.
+Hence, when the current vanishes, the correction $\delta J$ vanishes as well.
+Moreover, the correction is written as in Eq.~\eqref{eq:JD-dJ}, avoiding the potential divergence resulting from division by zero.
+
+%Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues resulting from small flux gradients.
 This is the option adopted in this study.

### 2019-12-05 docs/EPJP2019/Gross-EPJP-2019.tex
Minor changes to abstract and introduction
Changed iterative calculations of the diffusion coefficient - TO: diffusion correction factors.

@@
 In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks.
-The Ronen method is based on iterative calculations of the multigroup diffusion coefficients using a multigroup diffusion model and is driven by the solutions of the integral transport equation.
+The Ronen method is based on iterative calculations of the multigroup diffusion correction factors using a multigroup diffusion model and is driven by the solutions of the integral transport equation.
 The spatially-dependent diffusion constants are modified locally in order to produce new estimates of the surface currents using an integral transport expression.
@@
 The first class is based on extending the $P_1$ model equations (and the associated boundary conditions) along with some closure scheme, such as the well-known $SP_3$ approximation~\cite{Brantley-2000}.
-The second class, to which this study belongs, is based on the re-calculation of the diffusion coefficients within the multigroup diffusion framework~\cite{Tomatis-2011}.
+The second class, to which this study belongs, is based on the re-calculation of the diffusion correction factors within the multigroup diffusion framework~\cite{Tomatis-2011}.
 

### 2019-12-05 docs/EPJP2019/Gross-EPJP-2019.tex
Updated figures
Merged the following figures into 1:
1. dD correction of heterogeneous case, fast and thermal group.
2. flux deviation of heterogeneous case, all three cores.
removed old plots of these graphs which was separate.
3. updated flux plot of the flux, homogeneous case.
4. updated flux plot of the flux, heterogeneous case.

@@
 	\centering
-	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_1.pdf}
-	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_2.pdf}
-	\includegraphics[width=0.46\linewidth]{Sn_Diff_RM_core_3.pdf}
+	\includegraphics[width=0.49\linewidth]{Sn_Diff_RM_core_1.pdf}
+	\includegraphics[width=0.49\linewidth]{Sn_Diff_RM_core_2.pdf}
+	\includegraphics[width=0.49\linewidth]{Sn_Diff_RM_core_3.pdf}
 	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S16 reference solution.
@@
 
-The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions are shown in Fig.~\ref{fig:hetero-flux-dev} for each core.
-For all cores, the fast flux is poorly reproduced by standard diffusion, with up to $\sim$10\% deviations at the inner interfaces and $\sim$20\% at the outer boundaries (in agreement with the homogeneous case).
+The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions are shown for each core, in Fig.~\ref{fig:hetero-flux-dev}.
+The fast flux is poorly reproduced by standard diffusion, with up to $\sim$10\% deviations at the inner interfaces and $\sim$20\% at the outer boundaries (in agreement with the homogeneous case).
 Deviations of the thermal flux calculated by diffusion increase from $\sim$4\% to $\sim$10\% as the heterogeneity of the core increases.
@@
 	\centering
-	\includegraphics[width=0.65\linewidth]{flx_err_diff_C1.pdf}
-	\includegraphics[width=0.65\linewidth]{flx_err_diff_C2.pdf}
-	\includegraphics[width=0.65\linewidth]{flx_err_diff_C3.pdf}
+	\includegraphics[width=0.75\linewidth]{flx_err_diff_C123.pdf}
 	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions for each core.
@@
 It is illustrative to examine the spatial distribution of the Ronen method correction factors for the heterogeneous case.
-The behavior of the correction factor may seem a bit erratic, but can be explained.
+The behavior of the correction factor (Fig.~\ref{fig:Dcoef}) may seem a bit erratic, but can be explained.
 In regions where the flux gradients are small, the correction factors tend to vanish and actually produce solutions similar to standard diffusion.
@@
 
-% convergence
-%\begin{figure}[htbp!]
-%	\centering
-%	\includegraphics[width=0.55\linewidth]{k_over_i_C3_10RMit.pdf}
-%	\caption{Convergence of $\keff$ over number of grid points along core no. 3, for 100 RM iterations, and standard diffusion calculation.}
-%	\label{fig:k_vs_I}
-%\end{figure}
-
-%\begin{figure}[htbp!]
-%	\centering
-%	\includegraphics[width=0.45\linewidth]{RM_flx_100it_8_22_728.pdf}
-%	\caption{Fluxes as calculated by RM scheme. Results shown here after 100 Ronen iterations and 728 mesh points.}
-%	\label{fig:Cores_RMflx}
-%\end{figure}
-
 \begin{figure}[htbp!]
 	\centering
-	\includegraphics[width=0.65\linewidth]{RM_dD1_100it_8_22_728.pdf}
-	\includegraphics[width=0.65\linewidth]{RM_dD2_100it_8_22_728.pdf}
+	\includegraphics[width=0.75\linewidth]{RM_dD_100it_8_22_728_C123.pdf}
 	\caption{Behavior of the Ronen method correction factor $dD$ along the core, for the fast and thermal fluxes.

### 2019-12-05 FD1dMGdiff/FDsDiff1D.py
Fix bug noticed in reflection fixup at bnd and introduced in the 1st implementation of pCMFD; Fix pCMFD corrections dDm and dDp at bnd that caused a bug by mistakenly leaking particles; revise the whole structure of the FD* py module; fix minor bug in tests/homogSlab2GMC2011.py (a typo in the name of a variable); implement the function compute_D which is computing new estimates of the diffusion coefficients by Fick-s law after determining the J_transport current; upgrade the function with RM iterations to call compute_D instead of using the CMFD, that is using Fick-s law to obtain new estimate

@@ -79,7 +79,7 @@ def xim(x):
 class input_data:
     """Geometry and material input data of the 1D problem. Possible options
     of geometry_type are slab, cylindrical and spherical. Allowed boundary
-    conditions: 0-vacuum, 1-zero flux and 2-reflection."""
+    conditions: 0-vacuum, 1-zero flux and 2-reflection. Units are in cm."""
 
     def __init__(self, xs_media, media, xi, geometry_type='slab',
                  LBC=0, RBC=0):
@@ -87,6 +87,8 @@ class input_data:
         self.LBC, self.RBC = LBC, RBC
         self.xs_media, self.media = xs_media, media
         self.check_input()
+        self.compute_cell_width()
+        self.compute_cell_volumes()
 
     @property
     def I(self):
@@ -97,10 +99,21 @@ class input_data:
         return self.xi[-1]
 
     @property
+    def BC(self):
+        return self.LBC, self.RBC
+
+    @property
     def G(self):
         return self.xs_media[next(iter(self.xs_media))]['st'].size
+    
+    def compute_cell_width(self):
+        self.Di = self.xi[1:] - self.xi[:-1]
+    
+    def compute_cell_volumes(self):
+        self.Vi = compute_cell_volumes(self.xi, geo=self.geometry_type)
 
     def check_input(self):
+        lg.info("Geometry type is " + self.geometry_type)
         if (self.geometry_type != 'slab') and \
            (self.geometry_type != 'cylindrical') and \
            (self.geometry_type != 'spherical'):
@@ -147,34 +160,52 @@ class solver_options:
     toll = 1.e-6  # default tolerance
     itsmax = 100  # default nb. of max iterations (its)
 
-    def __init__(self, iitmax=itsmax, oitmax=itsmax, ritmax=itsmax,
-                 pCMFD=False, otoll=toll, itoll=toll, rtoll=toll):
+    def __init__(self, iitmax=itsmax, oitmax=itsmax, ritmax=10,
+                 pCMFD=False, otoll=toll, itoll=toll, rtoll=toll,
+                 CMFD=True):
         self.ritmax = ritmax  # set to 1 to skip Ronen iterations
[…]

### 2019-12-05 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -19,7 +19,7 @@ def MyWho():
 
 # definition of the spatial mesh
 L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
-I = 6  # nb of spatial cells
+I = 20  # nb of spatial cells
 xi = np.linspace(0, L, I+1)  # equidistant mesh
 
 geometry_type = 'slab'
@@ -34,7 +34,7 @@ media = [['HM', L]]  # i.e. homogeneously filled
 # set b.c.
 LBC, RBC = 2, 0
 
-Homo2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
+Homog2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
 
 if __name__ == "__main__":
 
@@ -44,4 +44,4 @@ if __name__ == "__main__":
 
     slvr_opts = solver_options(ritmax=10)
     # filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
-    flx, k = run_calc_with_RM_its(Homo2GSlab_data, slvr_opts, filename=None)
+    flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename=None)

### 2019-12-06 docs/EPJP2019/Gross-EPJP-2019.tex
Changes in the abstract by D. Tomatis; add a readme about how-to get the revised marked copy.

@@
 % for quotes
-\usepackage [english]{babel}
-\usepackage [autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
+% \usepackage [english]{babel}
+% \usepackage [autostyle, english = american]{csquotes}
+% \MakeOuterQuote{"}
 
@@
 \abstract{
-In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue in one-dimensional simple homogeneous problem and in more complex heterogeneous benchmarks.
-The Ronen method is based on iterative calculations of the multigroup diffusion correction factors using a multigroup diffusion model and is driven by the solutions of the integral transport equation.
-The spatially-dependent diffusion constants are modified locally in order to produce new estimates of the surface currents using an integral transport expression.
-The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme using drift terms.
-The corrected solutions are compared against reference results obtained by a discrete ordinate code.
-Boundary conditions are discussed and proper approximations are introduced to conserve the particle balance.
+In this paper, the Ronen method is developed, implemented, and applied to resolve the neutron flux and the criticality eigenvalue in simple one-dimensional homogeneous and heterogeneous problems.
+The Ronen method is based on iterative calculations of correction factors to use in a multigroup diffusion model, where the factors are actually given by the integral transport equation.
+In particular, spatially-dependent diffusion constants are modified locally in order to reproduce new estimates of the surface currents obtained by the integral transport operator.
+The diffusion solver employed in this study uses finite differences and the transport-corrected currents are introduced into the numerical scheme as drift terms.
+The corrected solutions are compared against reference results from a discrete ordinate code.
+%Boundary conditions are discussed and proper approximations are introduced to conserve the particle balance.
+%% commented because this is treated in another article indeed.
 The results match well with the reference solutions, especially in the limit of fine meshes, but slow convergence of the scalar flux is reported.
@@
 High-fidelity core design optimization or transient analyses can quickly become computationally impractical when using transport methods~\cite{Kim-2019}.
-For example, to achieve a 1\% accuracy in the local flux/power estimation, an order of 10\tsup{11} histories is needed in a full-core Monte Carlo calculation~\cite{Martin-2012}.
+For example, about 10\tsup{11} histories are needed in a full-core Monte Carlo calculation to achieve a 1\% accuracy on local flux/power estimation~\cite{Martin-2012}.
 Another problem is the huge number of variables and parameters to be stored and used during computation, e.g., tallies, geometry, cross sections, and depletion data.
@@
 Instead of computing new diffusion coefficients on the interfaces by Fick's law, $J_D(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\delta J(x_s,E) = \jtrr(x_s,E) - J_D(x_s,E)$ are obtained on cell interfaces $x_s$.
-Here, $J_D(x,E)$ is called the "diffusion current" and is obtained using Fick's law, with the original values of the homogeneous diffusion coefficients and with the derivative approximated by finite differences.
+Here, $J_D(x,E)$ is called the ``diffusion current'' and is obtained using Fick's law, with the original values of the homogeneous diffusion coefficients and with the derivative approximated by finite differences.
 In one-dimensional
@@
 The discretized form of the current $\delta J$ must involve the neighboring flux as well, but its representation is changed into a drift-advection term to get rid of possible undefined division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}.
-The so-called "transport current" $\jtrr(x_s,E)$ is evaluated using the integral expression derived in~\sxn{sec:int-flux-J} as described in~\sxn{sec:calc-int-curr}.
+The so-called ``transport current'' $\jtrr(x_s,E)$ is evaluated using the integral expression derived in~\sxn{sec:int-flux-J} as described in~\sxn{sec:calc-int-curr}.
 
@@
 Hence, as can be seen in Fig.~\ref{fig:slab-fluxes}, the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
-The Ronen iterations "push" the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
+The Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
 Hence, $\phi^{(k-1)}$ is smaller in the center and larger at the boundary comparing to $\phi^{(k)}$.

### 2019-12-09 docs/EPJP2019/Gross-EPJP-2019.tex
partial advancement of revision by Tomatis

@@
 However, future Gen-IV reactor designs are characterized by strong heterogeneity in the core, e.g., axial and radial seed-blanket structures, as in the French ASTRID SFR CVF design~\cite{Bertrand-2016}, challenging the accuracy of diffusion calculations.
-Moreover, modern calculation schemes evolve towards so-called "best-estimate" codes, aiming at high accuracy~\cite{IAEA-BE-2008}.
+Moreover, modern calculation schemes evolve towards so-called ``best-estimate'' codes, aiming at high accuracy~\cite{IAEA-BE-2008}.
 
 A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient~\cite{Bell-1970,Pounders-2009}.
-The calculation of this parameter should be based on physical insights from the transport equation such that the resulting improved ("transport corrected") diffusion approximation can capture the transport phenomena of interest.
-Such transport corrections can be divided into two main classes.
+The calculation of this parameter should be based on physical insights from the transport equation, such that the resulting diffusion approximation can really capture the transport phenomena of interest.
+Improved diffusion models obtained through transport corrections can be divided into two main classes.
 The first class is based on extending the $P_1$ model equations (and the associated boundary conditions) along with some closure scheme, such as the well-known $SP_3$ approximation~\cite{Brantley-2000}.
-The second class, to which this study belongs, is based on the re-calculation of the diffusion correction factors within the multigroup diffusion framework~\cite{Tomatis-2011}.
+The second class, to which this study belongs, is based on the re-calculation of correction factors within the multigroup diffusion framework~\cite{Tomatis-2011}.
 
@@
 \begin{equation}\label{eq:Fick}
-\bm{J}_D\rE = -D\rE\bnabla\phi\rE = \jtr\rE \,\, . 
+\bm{J}_D\rE = -D\rE\bnabla\phi\rE = \jtr\rE. 
 \end{equation}
@@
 \begin{equation}\label{eq:RM-it}
-D^{(k+1)}\rE = -\frac{\lvert\jtr^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert} \,\, ,
+D^{(k+1)}\rE = -\frac{\lvert\jtr^{(k)}\rE\rvert}{\lvert\bnabla\phi^{(k)}\rE\rvert} ,
 \end{equation}
@@
 \begin{equation}\label{eq:RM-it-1D-slab}
-D^{(k+1)}(x,E) = -\frac{\frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
+D^{(k+1)}(x,E) = -\frac{\displaystyle \frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
 	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
-{\partial \phi^{(k)}(x,E)/\partial x} \,\, .
+{\partial \phi^{(k)}(x,E)/\partial x}.
 \end{equation}
@@
 This idea was later used by Tomatis and Dall'Osso~\cite{Tomatis-2011}, who provided a numerical demonstration in a simple slab problem.
-Instead of updating the diffusion coefficient by the ratio of the current and the flux gradient, as in Fick's law, they adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
+Instead of updating the diffusion coefficient by the ratio of the current and the flux gradient, as in Fick's law, they adopted the Coarse Mesh Finite Differences method (CMFD) for taking into account in the diffusion solver the new currents estimated by the integral transport operator.
 %
@@
 It was observed that the Ronen method (RM) could drive the flux distribution away from diffusion and closer to the reference solution of the integral Boltzmann transport equation, regardless of the initial formulation used for the diffusion coefficient.
-As expected, the largest errors were located near the boundary, where the transport effects are most pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
+As expected, the largest errors were located near the boundary where the transport effects are more pronounced, but slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
 
@@
 
-There are several ways to drive the integral expression for the flux in slab geometry.
+There are several ways to derive the integral expression for the flux in slab geometry.
 Most of them start with assuming homogeneous and isotropic scattering and sources, yielding the \emph{Peierls equation} \cite{Davison-1957,Case-1967,Bell-1970,Pomraning-1973,Duderstadt-1979,Lewis-1984}.
 The derivation of expression for slab geometry (of thickness $a$) is straightforward, yielding
-\begin{eqnarray}\label{eq:flux-slab-l-0-no-bndry-terms}
-\phi(x,E)&=&\frac{1}{2}\int_0^a { dx'
-	E_1\left[\sigma(E)\lvert x-x'\rvert\right] q(x',E) 
-}\nonumber \\
-&=& \frac{1}{2}\int_0^a { \!\!\! dx'
-	E_1\left[\sigma(E)\lvert x-x'\rvert\right]
-	\left[
-	\int_0^\infty { \!\!\! dE'
-		\sigma_s(E\leftarrow E')\phi(x',E') 
-	} + S(x',E)
-	\right] 
-} \,\, ,
-\end{eqnarray}
-
-where $E_1(x)$ is a first order exponential integral~\cite{Abramowitz-1964}.
+\begin{equation}\label{eq:flux-slab-l-0-no-bndry-terms}
+\begin{split}
+\phi(x,E)=&\frac{1}{2}\int_0^a { dx'
+	E_1\left[\sigma(E)\lvert x-x'\rvert\right] Q(x',E)
+} \text{, with} \\
+Q(x,E) =& \int_0^\infty { dE'
+		\sigma_s(E \leftarrow E')\phi(x,E') + S(x,E)
+}
+\end{split}
+\end{equation}
+and $E_1(x)$ as first order exponential integral~\cite{Abramowitz-1964}.
 Note that this expression does not include the contribution of uncollided neutrons originated from an incoming angular flux at the boundaries.
 
-Another starting point for the derivation of the integral expression for the flux in slab geometry is to directly integrate along a line the transport equation~\cite{Davison-1957,Pomraning-1973,Duderstadt-1979,Lewis-1984}
-\begin{eqnarray}\label{eq:full-ITE-w-bndry-terms}
-\psi(\rr,\OO) &=& \int_0^R { dR'
-	q(\rr-R'\OO,\OO) e^{-\mcL(\rr,\rr-R'\OO)}
-} 
-%\nonumber \\
-%&+& 
-+\psi(\rr-R\OO,\OO) e^{-\mcL(\rr,\rr-R\OO)}
-\,\, ,
-\end{eqnarray}
+The starting point for the derivation of the integral expression for the flux in slab geometry is to directly integrate along a line the transport equation~\cite{Davison-1957,Pomraning-1973,Duderstadt-1979,Lewis-1984}
+\begin{equation}\label{eq:full-ITE-w-bndry-terms}
+\psi(\rr,\OO) = \int_0^R { dR'
+	Q(\rr-R'\OO,\OO) e^{-\mcL(\rr,\rr-R'\OO)}
+} + \psi(\rr-R\OO,\OO) e^{-\mcL(\rr,\rr-R\OO)},
+\end{equation}
 where $\mcL(\rr,\rr-R'\OO)$ is the \emph{optical length}, defined as
 \begin{equation}\label{eq:opl}
-\mcL(\rr,\rr-R'\OO) \equiv 
-\int_0^{R'} {\sigma(\rr-R''\OO)dR'} \,\, .
+\mcL(\rr,\rr-R'\OO) \equiv \int_0^{R'} {\sigma(\rr-R''\OO)dR'} .
 \end{equation}
@@
   \psi(x,E,\mu) &=& \psi(0,E,\mu) e^{-\mcL(0,x,E)/\mu}
-	+ \int_0^x { dx' \,\,
+  + \int_0^x { dx'
           \frac{Q(x',E,\mu)}{\mu} 
           e^{-\mcL(x',x,E)/\mu} 
-	} \,\, , \qquad \mu>0 \,\, ,   \label{eq:int-ang-flx-a}\\
+  } , \qquad \mu>0 ,   \label{eq:int-ang-flx-a}\\
   \psi(x,E,\mu) &=& \psi(a,E,\mu)e^{\mcL(x,a,E)/\mu} 
-	-\int_x^a { dx' \,\,
+  -\int_x^a { dx'
           \frac{Q(x',E,\mu)}{\mu} 
           e^{\mcL(x,x',E)/\mu} 
-	} \,\, , \qquad \mu<0 \,\, , \label{eq:int-ang-flx-b}
+  } , \qquad \mu<0 , \label{eq:int-ang-flx-b}
   \end{eqnarray}
@@
 \begin{equation}\label{eq:opl2}
-\mcL(x',x,E) \equiv 
-\int_{x'}^x {\sigma(x'',E) dx''} \,\,, \quad \text{assuming }(x'<x)
-\end{equation}
-and $Q(x,E,\mu)$ denotes all sources.
-
-The angular dependence of the source and the uncollided boundary flux terms is expanded in a series of orthogonal Legendre polynomials
-\begin{eqnarray}\label{eq:Q-series}
-\psi(0,E,\mu) &=& \sum\limits_{l=0}^\infty {
-	\frac{2l+1}{2} \psi_l(0,E) \pl{\mu} 	
-} \nonumber \\
-\psi(a,E,\mu) &=& \sum\limits_{l=0}^\infty {
-	\frac{2l+1}{2} \psi_l(a,E) \pl{\mu} 	
-} \,\, .
-\end{eqnarray}
-The source cross sections are written explicitly as~\cite{Tomatis-2011}
+\mcL(x',x,E) \equiv \operatorname{Sgn}(x-x') \int_{x'}^x {\sigma(x'',E) dx''}
+\end{equation}
+and $Q(x,E,\mu)$ denotes total emission.
+
+Only scattering in isotropic media is considered here: $\sigma_s(\ast, \OO' \rightarrow \OO) = \sigma_s(\ast, \mu_0)/2\pi$ with the angle cosine $\mu_0 = \OO' \cdot \OO$.
+The source terms are written by moments of Legendre polynomials after the usual expansion of the scattering cross sections in Legendre Polynomials of $\mu_0$, followed by the application of the addition theoreom and by integration on spherical harmonics using the symmetries and rotational invariance of the slab geometry~\cite{Bell-1970}.
+The cross sections of the source term are grouped for simplicity by introducing the $l$-th moments of the production cross section~\cite{Tomatis-2011}
 \begin{equation}\label{eq:src-mmnts}
-\sigma_l(x,E\leftarrow E')dE' = 
-\sigma_{s,l}(x,E\leftarrow E')dE'
-+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, ,
-\end{equation}
-where
+\sigma_l(x,E\leftarrow E') = \sigma_{s,l}(x,E\leftarrow E')
++ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E'),
+\end{equation}
+with the Legendre moments of the scattering cross section
 \begin{equation}\label{eq:src-mmnts-explicit}
-\sigma_{s,l}(x,E\leftarrow E') = \int_{-1}^1 d\mu' P_l(\mu')\sigma_s(x,E\leftarrow E',\mu_0)
-\end{equation}
-with $\mu_0=\OO'\cdot\OO$ and the source term is expanded 
-\begin{eqnarray}\label{eq:src}
-Q(x,E,\mu)&=& \sum\limits_{l=0}^\infty {
+\sigma_{s,l}(x,E\leftarrow E') = \int_{-1}^1 d\mu_0 P_l(\mu_0)\sigma_s(x,E\leftarrow E',\mu_0).
+\end{equation}
+$\delta_{l0}$ in~\eq{eq:src-mmnts} is the Kronecker function equal to 1 only for $l=0$ and zero otherwise.
+The multiplication factor $\keff$ applies here on the fission production since external sources are missing.
+The source term is then rewritten as
+% Daniele: the following equation could be simplified with fewer lines thank to the previous eqs.
+\begin{equation}\label{eq:src}
+\begin{split}
+Q(x,E,\mu)=& \sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} \int_0^\infty { dE'
@@
 	\nu\sigma_f(x,E') \psi_0(x,E')
-}  \nonumber \\
-&=&\sum\limits_{l=0}^\infty {
+} \\
+=&\sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} \int_0^\infty { dE'
@@
 	}
-} \nonumber \\
-&=&\sum\limits_{l=0}^\infty {
+} \\
+=&\sum\limits_{l=0}^\infty {
 \frac{2l+1}{2} \int_0^\infty { dE'
@@
 	}
-} \nonumber \\
-&=&\sum\limits_{l=0}^\infty {
+} \\
+=&\sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
-} 
-\,\, ,
-\end{eqnarray}
+},
+\end{split}
+\end{equation}
 where the source angular moments are defined as
@@
 q_l(x,E) \equiv \int_0^\infty dE' q_l(x,E\leftarrow E') \equiv 
-\int_0^\infty dE' \sigma_l(x,E\leftarrow E')\psi_l(x,E') dE' \,\, .
-\end{equation}
+\int_0^\infty dE' \sigma_l(x,E\leftarrow E')\psi_l(x,E') dE' .
+\end{equation}
+
+Finally, we also expand the angular dependence of the uncollided boundary flux in a series of orthogonal Legendre polynomials:
+%\begin{eqnarray}\label{eq:Q-series}
+%\psi(0,E,\mu) &=& \sum\limits_{l=0}^\infty {
+%	\frac{2l+1}{2} \psi_l(0,E) \pl{\mu} 	
+%} \nonumber \\
+%\psi(a,E,\mu) &=& \sum\limits_{l=0}^\infty {
+%	\frac{2l+1}{2} \psi_l(a,E) \pl{\mu} 	
+%}.
+%\end{eqnarray}
+\begin{equation}\label{eq:Q-series}
+\psi(x,E,\mu) = \sum\limits_{l=0}^\infty {
+	\frac{2l+1}{2} \pl{\mu} \psi_l(x,E)
+}.
+\end{equation}
+This allows dealing only with flux moments at the right hand side of~\eqs{eq:src-mmnts}.
 
@@
 %	\psi(a,\mu)\pl{\mu} 
-%} \,\, .
+%} .
 %\end{eqnarray}
@@
 %
-In order to calculate the scalar flux $\phi^+$ at $x$ resulting from neutrons coming from the left, i.e., $x'<x$ ($\mu>0$), substitute Eqs.~\eqref{eq:Q-series} in Eq.~\eqref{eq:int-ang-flx-a} and integrate over the angle
-\begin{eqnarray}\label{eq:phi+}
-\phi^+(x,E)&\equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \nonumber \\
+The scalar flux $\phi^+$ at $x$ resulting from neutrons coming from the left, i.e., $x'<x$ $(\mu>0)$, is determined by substituting Eqs.~\eqref{eq:Q-series} in Eq.~\eqref{eq:int-ang-flx-a} and integrating over the angle
+\begin{equation}\label{eq:phi+}
+\begin{split}
+\phi^+(x,E) \equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \\
 %&=& \int_0^1 {d\mu \psi(0,\mu) e^{-\mcL(0,x)/\mu} } 
@@
 %\nonumber \\
-&=& \sum\limits_{l=0}^\infty {
+=& \sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} 
@@
 	}
-	+	\int_0^x {\!\!\! dx'
+	+	\int_0^x { dx'
 		q_l(x',E)
@@
 \right\}
-} \,\, .
-\end{eqnarray}
-
+}.
+\end{split}
+\end{equation}
 In order to solve the angular integrals we resort to the following result~\cite{Cengel-1984,Settle-1994}
@@
 	\mu^i \pl{\mu} e^{-y/\mu} d\mu
-}
-= \sum\limits_{m=0}^{[l/2]} {
+} = \sum\limits_{m=0}^{[l/2]} {
 	h_m E_{l+2+i-2m}(y)
-} \,\, ,
-\end{equation}
-where $h_m$ is defined according to 
+},
+\end{equation}
+where the coefficients $h_m$ are used to rewrite the Legendre polynomials as simple sums of weighted monomials, like
 \begin{equation}\label{eq:h_i}
@@
 	h_m x^{n-2m}
-}
-\end{equation}
-and given explicitly by
-\begin{equation}\label{eq:h_i-explicit}
+}, \quad
+% \end{equation}
+% and given explicitly by
+% \begin{equation}\label{eq:h_i-explicit}
 h_m = \frac{(-1)^m (2l-2m)!}{2^l m! (l-m)! (l-2m)!}
-\end{equation}
-where
-\begin{equation}\label{eq:l_2}
+%\end{equation}
+%where
+%\begin{equation}\label{eq:l_2}
+\quad \text{and} \quad
 [l/2] = 
@@
 	}
-} \,\, .
-\end{equation}
-The contribution to the flux from $x'>x$ ($\mu<0$) can be calculated in a similar manner, using the change of variables $\eta=-\mu$ for the angular integrals and the fact that $\pl{-\mu}=(-1)^l\pl{\mu}$, resulting in an expression for the scalar flux which accounts for anisotropic scattering and heterogeneous medium
-\begin{eqnarray}\label{eq:int-scalar-flux}
-\phi(x,E) &=& \phi^+(x,E)+\phi^-(x,E) \nonumber \\
-&=& 
-\sum\limits_{l=0}^\infty  \frac{2l+1}{2} 
+}.
+\end{equation}
+The contribution to the flux from $x'>x$ ($\mu<0$) can be calculated in a similar manner, using the change of variables $\eta=-\mu$ for the angular integrals and the fact that $\pl{-\mu}=(-1)^l\pl{\mu}$.
+Hence, the expression for the scalar flux which accounts for anisotropic scattering and heterogeneous medium is
+\begin{equation}\label{eq:int-scalar-flux}
+\begin{split}
+\phi(x,E) =& \phi^+(x,E)+\phi^-(x,E) \\
+=& \sum\limits_{l=0}^\infty  \frac{2l+1}{2} 
 \sum\limits_{m=0}^{[l/2]} h_m
@@
 E_{l+2-2m}[\mcL(0,x,E)]	\psi_l(0,E) 
-+(-1)^l E_{l+2-2m}[\mcL(x,a,E)] \psi_l(a,E) 
-\nonumber \\
-&&+
-		\int_0^x dx' E_{l+1-2m}[\mcL(x',x,E)] q_l(x',E)
++(-1)^l E_{l+2-2m}[\mcL(x,a,E)] \psi_l(a,E) \\
+&+ \int_0^x dx' E_{l+1-2m}[\mcL(x',x,E)] q_l(x',E)
       +(-1)^l \int_x^a dx' 
       E_{l+1-2m}[\mcL(x,x',E)] q_l(x',E)
-\bigg\}	\,\, .		
-\end{eqnarray}
+\bigg\}.
+\end{split}
+\end{equation}
 
@@
 The generalization of~\eq{eq:int-scalar-flux} to current is obtained in a similar procedure according to
-\begin{eqnarray}\label{eq:tot-J}
-J(x,E) &=& J^+(x,E) - J^-(x,E) = \int_0^1 {d\mu \mu \psi(x,E,\mu)} 
-- \int_0^{-1} {d\mu \mu \psi(x,E,\mu)} \nonumber \\
-&=&\sum\limits_{l=0}^\infty  \frac{2l+1}{2}
+\begin{equation}\label{eq:tot-J}
+\begin{split}
+J(x,E) =& J^+(x,E) - J^-(x,E) = \int_0^1 {d\mu \mu \psi(x,E,\mu)} 
+- \int_0^{-1} {d\mu \mu \psi(x,E,\mu)} \\
+=&\sum\limits_{l=0}^\infty  \frac{2l+1}{2}
 \sum\limits_{m=0}^{[l/2]}  h_m
@@
 E_{l+3-2m}[\mcL(0,x,E)]	\psi_l(0,E) 
-+(-1)^{l+1} E_{l+3-2m}[\mcL(x,a,E)]\psi_l(a,E)  \nonumber \\
-&&+
++(-1)^{l+1} E_{l+3-2m}[\mcL(x,a,E)]\psi_l(a,E) \\
+&+
 \int_0^x dx' E_{l+2-2m}[\mcL(x',x,E)] q_l(x',E)
 +(-1)^{l+1} \int_x^a dx' E_{l+2-2m}[\mcL(x,x',E)] q_l(x',E)
-\bigg\}	\,\, . 
-\end{eqnarray}
+\bigg\}.
+\end{split}
+\end{equation}
 %
@@
 %+ \frac{1}{2}\int_0^a { dx' q_0(x',E)
-%	 E_1\left[\lvert\mcL(x',x,E)\rvert\right]} \,\, , \nonumber \\
+%	 E_1\left[\lvert\mcL(x',x,E)\rvert\right]} , \nonumber \\
 %\jtr(x,E) &=& \frac{1}{2}\left\{\psi_0^0(E) E_3[\mcL(0,x,E)] 
@@
 %	 E_2\left[\lvert\mcL(x',x,E)\rvert\right]
-%	sign(x-x') } \,\, .
+%	sign(x-x') } .
 %\end{eqnarray} 
@@
 \frac{\phi(x_{i+1},E) + \phi(x_i,E)}
-{(\Delta x_{i+1} + \Delta x_i)/2} \,\, ,
+{(\Delta x_{i+1} + \Delta x_i)/2} ,
 \end{eqnarray}
@@
 	+ \Delta x_{i+1} D(x_{i+1},E)}
-{ \Delta x_i + \Delta x_{i+1}} \,\, .
+{ \Delta x_i + \Delta x_{i+1}} .
 \end{equation}
@@
 \begin{equation}\label{eq:diff1}
-J_{D,g}^+(x) + \delta J_{D,g}^+(x) -  J_{D,g}^-(x) - \delta J_{D,g}^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x) \,\, ,
+J_{D,g}^+(x) + \delta J_{D,g}^+(x) -  J_{D,g}^-(x) - \delta J_{D,g}^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x) ,
 \end{equation}
@@
 \begin{equation}\label{eq:op-not}
-\mathcal{M}\Phi=\frac{1}{\keff}\mathcal{F}\Phi \,\, ,
+\mathcal{M}\Phi=\frac{1}{\keff}\mathcal{F}\Phi ,
 \end{equation}
@@
 \begin{equation}\label{eq:BC}
-J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta} \,\, ,
+J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta} ,
 \end{equation} 

### 2019-12-09 docs/EPJP2019/old_version.tex
partial advancement of revision by Tomatis

--- 2019-10-02 docs/EPJP-2019/Gross-EPJP-2019 - rev1.tex
@@
 \begin{equation}\label{eq:RM-it}
-D^{(k+1)}\rE = - \jtr^{(k)}\rE \left[\bnabla\phi^{(k)}\rE\right]^{-1} \,\, ,
-\end{equation}
-where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
+D^{(k+1)}\rE = -\frac{\jtr^{(k)}\rE}{\bnabla\phi^{(k)}\rE} \,\, ,
+\end{equation}
+where $k$ is the iteration index.
 
@@
 The derivation of expression for slab geometry (of thickness $a$) is straightforward, yielding
-\begin{eqnarray}\label{eq:flux-slab-l-0-no-bndry-terms}
-\phi(x,E)&=&\frac{1}{2}\int_0^a { dx'
+\begin{equation}\label{eq:flux-slab-l-0-no-bndry-terms}
+\begin{split}
+\phi(x,E)=&\frac{1}{2}\int_0^a { dx'
 	E_1\left[\sigma(E)\lvert x-x'\rvert\right] q(x',E)
-}\nonumber \\
-&=& \frac{1}{2}\int_0^a { \!\!\! dx'
-	E_1\left[\sigma(E)\lvert x-x'\rvert\right]
-	\left[
-	\int_0^\infty { \!\!\! dE'
-		\sigma_s(E\leftarrow E')\phi(x',E') 
-	} + S(x',E)
-	\right] 
-} \,\, ,
-\end{eqnarray}
+} \text{, with} \\
+q(x',E) =& \int_0^\infty { dE'
+		\sigma_s(E \leftarrow E')\phi(x',E') + S(x',E)
+}
+\end{split}
+\end{equation}
+% commented to overcome an error of latexdiff
+%\begin{eqnarray}\label{eq:flux-slab-l-0-no-bndry-terms}
+%\phi(x,E)&=&\frac{1}{2}\int_0^a { dx'
+%	E_1\left[\sigma(E)\lvert x-x'\rvert\right] q(x',E) 
+%}\nonumber \\
+%&=& \frac{1}{2}\int_0^a { \!\!\! dx'
+%	E_1\left[\sigma(E)\lvert x-x'\rvert\right]
+%	\left[
+%	\int_0^\infty { \!\!\! dE'
+%		\sigma_s(E\leftarrow E')\phi(x',E') 
+%	} + S(x',E)
+%	\right] 
+%} \,\, ,
+%\end{eqnarray}
 where $E_1(x)$ is a first order exponential integral~\cite{Abramowitz-1964}.
@@
 Another starting point for the derivation of the integral expression for the flux in slab geometry is to directly integrate along a line the transport equation~\cite{Davison-1957,Pomraning-1973,Duderstadt-1979,Lewis-1984}
-\begin{eqnarray}\label{eq:full-ITE-w-bndry-terms}
-\psi(\rr,\OO) &=& \int_0^R { dR'
+\begin{equation}\label{eq:full-ITE-w-bndry-terms}
+\psi(\rr,\OO) = \int_0^R { dR'
 	q(\rr-R'\OO,\OO) e^{-\mcL(\rr,\rr-R'\OO)}
-} 
-%\nonumber \\
-%&+& 
-+\psi(\rr-R\OO,\OO) e^{-\mcL(\rr,\rr-R\OO)}
-\,\, ,
-\end{eqnarray}
+} + \psi(\rr-R\OO,\OO) e^{-\mcL(\rr,\rr-R\OO)},
+\end{equation}
+% commented to avoid an error by latexdiff
+%\begin{eqnarray}\label{eq:full-ITE-w-bndry-terms}
+%\psi(\rr,\OO) &=& \int_0^R { dR'
+%	q(\rr-R'\OO,\OO) e^{-\mcL(\rr,\rr-R'\OO)}
+%} 
+%%\nonumber \\
+%%&+& 
+%+\psi(\rr-R\OO,\OO) e^{-\mcL(\rr,\rr-R\OO)}
+%\,\, ,
+%\end{eqnarray}
 where $\mcL(\rr,\rr-R'\OO)$ is the \emph{optical length}, defined as
@@
 The source cross sections are written explicitly as~\cite{Tomatis-2011}
-\begin{equation}\label{eq:src-mmnts}
-\sigma_l(x,E\leftarrow E')dE' = 
-\sigma_{s,l}(x,E\leftarrow E')dE'
-+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, 
-\end{equation}
-and the source term is expanded 
-\begin{eqnarray}\label{eq:src}
-Q(x,E,\mu)&=& \sum\limits_{l=0}^\infty {
+\begin{equation}\label{eq:src}
+\begin{split}
+Q(x,E,\mu)=& \sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} \int_0^\infty { dE'
@@
 	}
-} \nonumber \\
-&=&\sum\limits_{l=0}^\infty {
+} \\
+=&\sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
-} 
-\,\, ,
-\end{eqnarray}
+},
+\end{split}
+\end{equation}
+%\begin{equation}\label{eq:src-mmnts}
+%\sigma_l(x,E\leftarrow E')dE' = 
+%\sigma_{s,l}(x,E\leftarrow E')dE'
+%+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, 
+%\end{equation}
+%and the source term is expanded 
+%\begin{eqnarray}\label{eq:src}
+%Q(x,E,\mu)&=& \sum\limits_{l=0}^\infty {
+%	\frac{2l+1}{2} \int_0^\infty { dE'
+%		\sigma_{s,l}(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
+%	}
+%} 
+%+ \frac{\chi(E)}{2\keff} \int_0^\infty { dE'
+%	\nu\sigma_f(x,E') \psi_0(x,E')
+%}  \nonumber \\
+%&=&\sum\limits_{l=0}^\infty {
+%	\frac{2l+1}{2} \int_0^\infty { dE'
+%		\sigma_l(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
+%	}
+%} \nonumber \\
+%&=&\sum\limits_{l=0}^\infty {
+%\frac{2l+1}{2} \int_0^\infty { dE'
+%	q_l(x,E\leftarrow E')\pl{\mu} 			
+%	}
+%} \nonumber \\
+%&=&\sum\limits_{l=0}^\infty {
+%	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
+%} 
+%\,\, ,
+%\end{eqnarray}
 where the source angular moments are defined as

### 2019-12-09 docs/EPJP2019/Gross-EPJP-2019.tex
partial advancement of revision by Tomatis

@@
 
-The starting point for the derivation of the integral expression for the flux in slab geometry is to directly integrate along a line the transport equation~\cite{Davison-1957,Pomraning-1973,Duderstadt-1979,Lewis-1984}
+Another starting point for the derivation of the integral expression for the flux in slab geometry is to directly integrate along a line the transport equation~\cite{Davison-1957,Pomraning-1973,Duderstadt-1979,Lewis-1984}
 \begin{equation}\label{eq:full-ITE-w-bndry-terms}
@@
 
-Only scattering in isotropic media is considered here: $\sigma_s(\ast, \OO' \rightarrow \OO) = \sigma_s(\ast, \mu_0)/2\pi$ with the angle cosine $\mu_0 = \OO' \cdot \OO$.
-The source terms are written by moments of Legendre polynomials after the usual expansion of the scattering cross sections in Legendre Polynomials of $\mu_0$, followed by the application of the addition theoreom and by integration on spherical harmonics using the symmetries and rotational invariance of the slab geometry~\cite{Bell-1970}.
-The cross sections of the source term are grouped for simplicity by introducing the $l$-th moments of the production cross section~\cite{Tomatis-2011}
-\begin{equation}\label{eq:src-mmnts}
-\sigma_l(x,E\leftarrow E') = \sigma_{s,l}(x,E\leftarrow E')
-+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E'),
-\end{equation}
-with the Legendre moments of the scattering cross section
-\begin{equation}\label{eq:src-mmnts-explicit}
-\sigma_{s,l}(x,E\leftarrow E') = \int_{-1}^1 d\mu_0 P_l(\mu_0)\sigma_s(x,E\leftarrow E',\mu_0).
-\end{equation}
-$\delta_{l0}$ in~\eq{eq:src-mmnts} is the Kronecker function equal to 1 only for $l=0$ and zero otherwise.
-The multiplication factor $\keff$ applies here on the fission production since external sources are missing.
-The source term is then rewritten as
-% Daniele: the following equation could be simplified with fewer lines thank to the previous eqs.
-\begin{equation}\label{eq:src}
-\begin{split}
-Q(x,E,\mu)=& \sum\limits_{l=0}^\infty {
-	\frac{2l+1}{2} \int_0^\infty { dE'
-		\sigma_{s,l}(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
-	}
-} 
-+ \frac{\chi(E)}{2\keff} \int_0^\infty { dE'
-	\nu\sigma_f(x,E') \psi_0(x,E')
-} \\
-=&\sum\limits_{l=0}^\infty {
-	\frac{2l+1}{2} \int_0^\infty { dE'
-		\sigma_l(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
-	}
-} \\
-=&\sum\limits_{l=0}^\infty {
-\frac{2l+1}{2} \int_0^\infty { dE'
-	q_l(x,E\leftarrow E')\pl{\mu} 			
-	}
-} \\
-=&\sum\limits_{l=0}^\infty {
-	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
-},
-\end{split}
-\end{equation}
-where the source angular moments are defined as
-\begin{equation}\label{eq:q_l}
-q_l(x,E) \equiv \int_0^\infty dE' q_l(x,E\leftarrow E') \equiv 
-\int_0^\infty dE' \sigma_l(x,E\leftarrow E')\psi_l(x,E') dE' .
-\end{equation}
-
-Finally, we also expand the angular dependence of the uncollided boundary flux in a series of orthogonal Legendre polynomials:
+The angular dependence of the source terms and of the uncollided boundary flux is expanded in a series of orthogonal Legendre polynomials as a consequence of the expansion of the scattering term in a series of orthogonal spherical harmonics, simply reducing to Legendre polynomials in slab geometry.
+For instance, for the angular flux it is:
 %\begin{eqnarray}\label{eq:Q-series}
@@
 \end{equation}
-This allows dealing only with flux moments at the right hand side of~\eqs{eq:src-mmnts}.
+The cross sections in the source terms are written explicitly as~\cite{Tomatis-2011}
+\begin{equation}\label{eq:src-mmnts}
+\sigma_l(x,E\leftarrow E') = \sigma_{s,l}(x,E\leftarrow E')
++ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E'),
+\end{equation}
+with the $l$-th Legendre moments of the scattering cross section
+\begin{equation}\label{eq:src-mmnts-explicit}
+\sigma_{s,l}(x,E\leftarrow E') = \int_{-1}^1 d\mu' P_l(\mu')\sigma_s(x,E\leftarrow E',\mu_0),
+\end{equation}
+where $\mu_0=\OO'\cdot\OO$ is the cosine between the incoming and outgoing directions $\OO'$ and $\OO$ in a collision. The source term is then expanded as
+\begin{eqnarray}\label{eq:src}
+Q(x,E,\mu)&=& \sum\limits_{l=0}^\infty {
+	\frac{2l+1}{2} \int_0^\infty { dE'
+		\sigma_{s,l}(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
+	}
+} 
++ \frac{\chi(E)}{2\keff} \int_0^\infty { dE'
+	\nu\sigma_f(x,E') \psi_0(x,E')
+}  \nonumber \\
+&=&\sum\limits_{l=0}^\infty {
+	\frac{2l+1}{2} \int_0^\infty { dE'
+		\sigma_l(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
+	}
+} \nonumber \\
+&=&\sum\limits_{l=0}^\infty {
+\frac{2l+1}{2} \int_0^\infty { dE'
+	q_l(x,E\leftarrow E')\pl{\mu} 			
+	}
+} \nonumber \\
+&=&\sum\limits_{l=0}^\infty {
+	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
+} 
+\,\, ,
+\end{eqnarray}
+where the source angular moments are defined as
+\begin{equation}\label{eq:q_l}
+q_l(x,E) \equiv \int_0^\infty dE' q_l(x,E\leftarrow E') \equiv 
+\int_0^\infty dE' \sigma_l(x,E\leftarrow E')\psi_l(x,E') dE' .
+\end{equation}
 
@@
 %
-The scalar flux $\phi^+$ at $x$ resulting from neutrons coming from the left, i.e., $x'<x$ $(\mu>0)$, is determined by substituting Eqs.~\eqref{eq:Q-series} in Eq.~\eqref{eq:int-ang-flx-a} and integrating over the angle
-\begin{equation}\label{eq:phi+}
-\begin{split}
-\phi^+(x,E) \equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \\
+In order to calculate the scalar flux $\phi^+$ at $x$ resulting from neutrons coming from the left, i.e., $x'<x$ ($\mu>0$), substitute Eqs.~\eqref{eq:Q-series} in Eq.~\eqref{eq:int-ang-flx-a} and integrate over the angle
+\begin{eqnarray}\label{eq:phi+}
+\phi^+(x,E)&\equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \nonumber \\
 %&=& \int_0^1 {d\mu \psi(0,\mu) e^{-\mcL(0,x)/\mu} } 
@@
 %\nonumber \\
-=& \sum\limits_{l=0}^\infty {
+&=& \sum\limits_{l=0}^\infty {
 	\frac{2l+1}{2} 
@@
 	}
-	+	\int_0^x { dx'
+	+	\int_0^x {\!\!\! dx'
 		q_l(x',E)
@@
 \right\}
-}.
-\end{split}
-\end{equation}
+} .
+\end{eqnarray}
+
 In order to solve the angular integrals we resort to the following result~\cite{Cengel-1984,Settle-1994}
@@
 	\mu^i \pl{\mu} e^{-y/\mu} d\mu
-} = \sum\limits_{m=0}^{[l/2]} {
+}
+= \sum\limits_{m=0}^{[l/2]} {
 	h_m E_{l+2+i-2m}(y)
-},
-\end{equation}
-where the coefficients $h_m$ are used to rewrite the Legendre polynomials as simple sums of weighted monomials, like
+} ,
+\end{equation}
+where $h_m$ is defined according to 
 \begin{equation}\label{eq:h_i}
@@
 	h_m x^{n-2m}
-}, \quad
-% \end{equation}
-% and given explicitly by
-% \begin{equation}\label{eq:h_i-explicit}
+}
+\end{equation}
+and given explicitly by
+\begin{equation}\label{eq:h_i-explicit}
 h_m = \frac{(-1)^m (2l-2m)!}{2^l m! (l-m)! (l-2m)!}
-%\end{equation}
-%where
-%\begin{equation}\label{eq:l_2}
-\quad \text{and} \quad
+\end{equation}
+where
+\begin{equation}\label{eq:l_2}
 [l/2] = 
@@
 \end{equation}
-The contribution to the flux from $x'>x$ ($\mu<0$) can be calculated in a similar manner, using the change of variables $\eta=-\mu$ for the angular integrals and the fact that $\pl{-\mu}=(-1)^l\pl{\mu}$.
-Hence, the expression for the scalar flux which accounts for anisotropic scattering and heterogeneous medium is
-\begin{equation}\label{eq:int-scalar-flux}
-\begin{split}
-\phi(x,E) =& \phi^+(x,E)+\phi^-(x,E) \\
-=& \sum\limits_{l=0}^\infty  \frac{2l+1}{2} 
+The contribution to the flux from $x'>x$ ($\mu<0$) can be calculated in a similar manner, using the change of variables $\eta=-\mu$ for the angular integrals and the fact that $\pl{-\mu}=(-1)^l\pl{\mu}$, resulting in an expression for the scalar flux which accounts for anisotropic scattering and heterogeneous medium
+\begin{eqnarray}\label{eq:int-scalar-flux}
+\phi(x,E) &=& \phi^+(x,E)+\phi^-(x,E) \nonumber \\
+&=& 
+\sum\limits_{l=0}^\infty  \frac{2l+1}{2} 
 \sum\limits_{m=0}^{[l/2]}  h_m
@@
 E_{l+2-2m}[\mcL(0,x,E)]	\psi_l(0,E) 
-+(-1)^l E_{l+2-2m}[\mcL(x,a,E)] \psi_l(a,E) \\
-&+ \int_0^x dx' E_{l+1-2m}[\mcL(x',x,E)] q_l(x',E)
++(-1)^l E_{l+2-2m}[\mcL(x,a,E)] \psi_l(a,E) 
+\nonumber \\
+&&+
+		\int_0^x dx' E_{l+1-2m}[\mcL(x',x,E)] q_l(x',E)
 		+(-1)^l \int_x^a dx' 
 		E_{l+1-2m}[\mcL(x,x',E)] q_l(x',E)
-\bigg\}.
-\end{split}
-\end{equation}
+\bigg\}	\,\, .		
+\end{eqnarray}
 
@@
 The generalization of~\eq{eq:int-scalar-flux} to current is obtained in a similar procedure according to
-\begin{equation}\label{eq:tot-J}
-\begin{split}
-J(x,E) =& J^+(x,E) - J^-(x,E) = \int_0^1 {d\mu \mu \psi(x,E,\mu)} 
-- \int_0^{-1} {d\mu \mu \psi(x,E,\mu)} \\
-=&\sum\limits_{l=0}^\infty  \frac{2l+1}{2}
+\begin{eqnarray}\label{eq:tot-J}
+J(x,E) &=& J^+(x,E) - J^-(x,E) = \int_0^1 {d\mu \mu \psi(x,E,\mu)} 
+- \int_0^{-1} {d\mu \mu \psi(x,E,\mu)} \nonumber \\
+&=&\sum\limits_{l=0}^\infty  \frac{2l+1}{2}
 \sum\limits_{m=0}^{[l/2]}  h_m
@@
 E_{l+3-2m}[\mcL(0,x,E)]	\psi_l(0,E) 
-+(-1)^{l+1} E_{l+3-2m}[\mcL(x,a,E)]\psi_l(a,E) \\
-&+
++(-1)^{l+1} E_{l+3-2m}[\mcL(x,a,E)]\psi_l(a,E)  \nonumber \\
+&&+
 \int_0^x dx' E_{l+2-2m}[\mcL(x',x,E)] q_l(x',E)
 +(-1)^{l+1} \int_x^a dx' E_{l+2-2m}[\mcL(x,x',E)] q_l(x',E)
-\bigg\}.
-\end{split}
-\end{equation}
+\bigg\}	\,\, . 
+\end{eqnarray}
 %

### 2019-12-10 docs/EPJP2019/Gross-EPJP-2019.tex
Fixed Eq. 16 - removed n index (->l)
Updated flux figures Tomatis&Dallosso2011
Deleted the fluxes plot of the homogeneous benchmark of Tomatis&Dall'osso2011, by a new one, splitted the fluxes on the same figure, added zoom-in plot near the boundary.
revision of the theory part by Tomatis

--- 2019-12-09 docs/EPJP2019/Gross-EPJP-2019.tex
@@
 D^{(k+1)}(x,E) = -\frac{\displaystyle \frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
-	x-x'\rvert]\text{sign}(x-x')q^{(k)}(x',E)}
+	x-x'\rvert]\operatorname{Sgn}(x-x')q^{(k)}(x',E)}
 {\partial \phi^{(k)}(x,E)/\partial x}.
@@
 	E_1\left[\sigma(E)\lvert x-x'\rvert\right] Q(x',E)
-} \text{, with} \\
+}, \text{ with} \\
 Q(x,E) =& \int_0^\infty { dE'
@@
 \pl{x}=\sum\limits_{m=0}^{[l/2]} {
-	h_m x^{n-2m}
+	h_m x^{l-2m}
 }, \quad
@@
 
-Instead of computing new diffusion coefficients on the interfaces by Fick's law, $J_D(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\delta J(x_s,E) = \jtrr(x_s,E) - J_D(x_s,E)$ are obtained on cell interfaces $x_s$.
-Here, $J_D(x,E)$ is called the ``diffusion current'' and is obtained using Fick's law, with the original values of the homogeneous diffusion coefficients and with the derivative approximated by finite differences.
+Instead of computing new diffusion coefficients at the interfaces by Fick's law, $J_D(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\delta J(x_s,E) = \jtrr(x_s,E) - J_D(x_s,E)$ are obtained at cell interfaces $x_s$.
+Here, $J_D(x,E)$ is called the ``diffusion current'' and is obtained using Fick's law, with the original values of the diffusion coefficients and with the derivative approximated by finite differences.
 In one-dimensional
 geometry and using the notation in \fig{fig:mesh1D}, the diffusion current and the corrective current are evaluated according to
-\begin{eqnarray}\label{eq:JD-dJ}
-J_D(x_{i+1/2},E) &\cong& -D(x_{i+1/2},E) 
+\begin{subequations}\label{eq:JD-dJ}
+\begin{align}
+J_D(x_{i+1/2},E) \cong& -D(x_{i+1/2},E) 
 \frac{\phi(x_{i+1},E) - \phi(x_i,E)}
-{(\Delta x_{i+1} + \Delta x_i)/2} \nonumber \\
-\delta J(x_{i+1/2},E) &=& -\delta D(x_{i+1/2},E) 
+{(\Delta x_{i+1} + \Delta x_i)/2}, \label{eq:JD} \\
+\delta J(x_{i+1/2},E) =& -\delta D(x_{i+1/2},E) 
 \frac{\phi(x_{i+1},E) + \phi(x_i,E)}
-{(\Delta x_{i+1} + \Delta x_i)/2} ,
-\end{eqnarray}
+{(\Delta x_{i+1} + \Delta x_i)/2}, \label{eq:dJ}
+\end{align}
+\end{subequations}
 where integer and rational subscripts indicate node-averaged and interface quantities, respectively.
@@
 
-\begin{figure}[htbp!] 
+\begin{figure}[htbp] 
 	\centering
@@
 %
-Since the input diffusion coefficients are provided as node averaged, and they are always needed at interfaces, they are approximated by local volume averages:
+The input diffusion coefficients are provided as cell averaged quantities, but they are always needed at interfaces. Therefore, they are approximated here by local volume averages:
 \begin{equation}\label{eq:Ds}
@@
 
-The new numerical corrections $\delta D$ are obtained on the interfaces using~\eq{eq:JD-dJ} to be used in the finite differences solver, together with the diffusive currents from~\eq{eq:JD-dJ}.
+The new numerical corrections $\delta D$ are obtained at the interfaces using~\eqs{eq:dJ} to be used in the finite differences solver, together with the diffusive currents from~\eq{eq:JD}.
 Hence, the neutron balance resolved by the CMFD takes into account both types of currents $J_D$ and $\delta J$.
 %Non-linear iterations with new corrections given by $\delta J$ are needed because of their dependence on the unknown flux.
-Hence, the one-dimensional multigroup neutron balance CMFD diffusion equations actually solved are
+In particular, the one-dimensional multigroup neutron balance CMFD diffusion equations actually solved are
 \begin{equation}\label{eq:diff1}
-J_{D,g}^+(x) + \delta J_{D,g}^+(x) -  J_{D,g}^-(x) - \delta J_{D,g}^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x) ,
+J_{D,g}^+(x) + \delta J_{D,g}^+(x) -  J_{D,g}^-(x) - \delta J_{D,g}^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x),
 \end{equation}
@@
 
-Using the definitions in~\eqsand{eq:JD-dJ}{eq:Ds} and~\fig{fig:mesh1D}, the discretized form of~\eq{eq:diff1} is
-\begin{eqnarray}\label{eq:FD_diff_full}
+Using the definitions in~\eqsand{eq:JD-dJ}{eq:Ds} with the notation shown in~\fig{fig:mesh1D}, the discretized form of~\eq{eq:diff1} is
+\begin{equation}\label{eq:FD_diff_full}
+\begin{split}
 - 2D_{i+1/2}^g\frac{\phi_{i+1,g}-\phi_{i,g}}{\dx_{i+1} + \dx_i}
 - 2\delta D_{i+1/2}^g\frac{\phi_{i+1,g}+\phi_{i,g}}{(\dx_{i+1}+\dx_i)}
-&+& 2D_{i-1/2}^g\frac{\phi_{i,g}-\phi_{i-1,g}}{\dx_{i} + \dx_{i-1}}  
-+ 2\delta D_{i-1/2}^g\frac{\phi_{i,g}+\phi_{i-1,g}}{(\dx_i+\dx_{i-1})} 
-\nonumber \\
-&+& \sigma_{i}^g \phi_{i,g} 
+&+ 2D_{i-1/2}^g\frac{\phi_{i,g}-\phi_{i-1,g}}{\dx_{i} + \dx_{i-1}}  
++ 2\delta D_{i-1/2}^g\frac{\phi_{i,g}+\phi_{i-1,g}}{(\dx_i+\dx_{i-1})} \\
+&+ \sigma_{i}^g \phi_{i,g} 
 = \sum\limits_{g'=1}^G \sigma_{s,i}^{g\leftarrow g'}\phi_{i,g'}
 + \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G
- \nu\sigma_{f,i}^{g'}\phi_{i,g'} 
-\,\,.
-\end{eqnarray}
+ \nu\sigma_{f,i}^{g'}\phi_{i,g'}.
+\end{split}
+\end{equation}
 Rearranging terms, one gets
-\begin{eqnarray}\label{eq:FD_diff_org}
+\begin{equation}\label{eq:FD_diff_org}
+\begin{split}
 \left(
 \frac{-D_{i-1/2}^g + \delta D_{i-1/2}^g }{\dx_{i-1}+\dx_{i}}
-\right)
-\phi_{i-1,g}
-&+&\left[
+\right) \phi_{i-1,g}
+&+ \left[
 \frac{D_{i+1/2}^g - \delta D_{i+1/2}^g}{\dx_{i+1}+\dx_i}
@@
 +\frac{\sigma_{i}^g}{2}
-\right]
-\phi_{i,g}
-\nonumber \\
-&+&\left(
+\right] \phi_{i,g} \\
+&+ \left(
 \frac{-D_{i+1/2}^g -\delta D_{i+1/2}^g }{\dx_{i+1}+\dx_{i}}
-\right)
-\phi_{i+1,g} =
-\frac{1}{2}q_{i,g}\,\, ,
-\end{eqnarray}
+\right) \phi_{i+1,g} = \frac{1}{2}q_{i,g},
+\end{split}
+\end{equation}
 where $q_{i,g}$ is the RHS of~\eq{eq:FD_diff_full}.
@@
 \begin{equation}\label{eq:op-not}
-\mathcal{M}\Phi=\frac{1}{\keff}\mathcal{F}\Phi ,
-\end{equation}
-where $\mathcal{M}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by the second term in $q_{i,g}$ (see Eqs.~\ref{eq:FD_diff_full}-\ref{eq:FD_diff_org}).
-Note that $\mathcal{M}$ can be written as $\mathcal{M}=\mathcal{M}_0+\delta\mathcal{M}$ distinguishing the diffusion corrections from the constant diffusion coefficients derived from the transport problem.
-In the homogeneous case, $\mathcal{M}(x)=\mathcal{M}_0+\delta\mathcal{M}(x)$.
+\mathcal{A}\Phi=\frac{1}{\keff}\mathcal{F}\Phi,
+\end{equation}
+where $\mathcal{A}$ is the migration operator, whose entries are given by~\eq{eq:FD_diff_org} making it a three-diagonal banded matrix, and $\mathcal{F}$ is the neutron generation operator given by the second term in $q_{i,g}$ (see Eqs.~\ref{eq:FD_diff_full}-\ref{eq:FD_diff_org}).
+Note that $\mathcal{A}$ can be written as $\mathcal{A}=\mathcal{A}_0+\delta\mathcal{A}$ distinguishing the diffusion corrections from the constant diffusion coefficients derived from the transport problem.
+In the homogeneous case, $\mathcal{A}(x)=\mathcal{A}_0+\delta\mathcal{A}(x)$.
 %
@@
 
-The numerical evaluation of the neutron current $J_g(x)$ at cell interfaces requires spatial integration of~\eq{eq:tot-J}.
-The neutron current at any interface can be calculated by considering separately contributions from all cells who are to the left or to the right of the interface.
+The numerical evaluation of the neutron current $J_g(x)$ at the cell interfaces requires spatial integration of~\eq{eq:tot-J}.
+The neutron current at any interface can be calculated by considering separately contributions from all cells which are to the left or to the right of the interface itself.
 The current at a cell interface is discretized as follows
-\begin{eqnarray}\label{eq:tot-J-disc}
-J_g(x_{i+1/2}) &=& \sum\limits_{l=0}^\infty  \frac{2l+1}{2}
+\begin{equation}\label{eq:tot-J-disc}
+\begin{split}
+J_g(x_{i+1/2}) &= \sum\limits_{l=0}^\infty \frac{2l+1}{2}
 \sum\limits_{m=0}^{[l/2]} h_m
@@
 E_{n_{l,m}+1}[\mcL_g(0,x_{i+1/2})] \psi_{l,g}(0) 
-+(-1)^{l+1} E_{n_{l,m}+1}[\mcL_g(x_{i+1/2},a)]\psi_{l,g}(a)  \nonumber \\
-&+&
++(-1)^{l+1} E_{n_{l,m}+1}[\mcL_g(x_{i+1/2},a)]\psi_{l,g}(a) \\
+&+
 \sum\limits_{j=0}^i q_{l,g,j}\int\limits_{x_{j-1/2}}^{x_{j+1/2}} dx'
-E_{n_{l,m}}[\mcL_g(x',x_{i+1/2})]
-%\nonumber \\
-%&&
-+(-1)^{l+1} 
+E_{n_{l,m}}[\mcL_g(x',x_{i+1/2})] + (-1)^{l+1} 
 \sum\limits_{j=i+1}^{I-1} q_{l,g,j}\int\limits_{x_{j-1/2}}^{x_{j+1/2}} dx'
 E_{n_{l,m}}[\mcL_g(x_{i+1/2},x')]
-\bigg\}	\,\, , 
-\end{eqnarray}
+\bigg\},
+\end{split}
+\end{equation}
 where $n_{l,m}\equiv l+2-2m$.
@@
 The optical lengths show the subscript $g$ because they are evaluated with the corresponding total cross section $\sigma_g$.
-Note that for void boundary conditions, the boundary terms vanish by definition.
-The spatial integrals in~\eq{eq:tot-J-disc} can be solved analytically knowing that $E'_{n+1}(u)=-E_n(u)$~\cite{Gradshteyn-2007}.
-Using the notation in Fig.~\ref{fig:Xi}, the optical length between the right surfaces of cell $j$ and cell $i$ is
+Note that for void boundary conditions, the boundary terms must vanish by definition.
+The spatial integrals in~\eq{eq:tot-J-disc} can be solved analytically knowing that $E'_{n+1}(u) = -E_n(u)$~\cite{Gradshteyn-2007}.
+The optical length between the right surfaces of cell $j$ and cell $i$ is
 \begin{equation}\label{eq:psi_w_left_right}
-\Xi^g_{i,j} \equiv \begin{cases}
-\Xi^g_{i\geqslant j} = \sum\limits_{k=j+1}^i \sigma_{g,k}\Delta x_k 
-& x\geqslant x' \quad (i\geqslant j) \\
-\Xi^g_{i<j} = \sum\limits_{k=i+1}^{j-1} \sigma_{g,k}\Delta x_k & x<x' \quad (i<j)\,\, .
+\tau^g_{i,j} \equiv \begin{cases}
+\sum\limits_{k=j+1}^i \sigma_{g,k}\Delta x_k 
+& \text{if } i > j, \\
+\quad 0 & \text{if } i = j, \\
+\sum\limits_{k=i+1}^{j} \sigma_{g,k}\Delta x_k &\text{if } i < j.
 \end{cases}
 \end{equation}
-
-\begin{figure}[htbp!] 
-	\centering
-	For $x\geqslant x'$.	
+The general case follows in \fig{fig:tau}.
+
+\begin{figure}[htbp]
+	\centering
+	For $x_{j+1/2} \geqslant x'$,
 	\begin{tikzpicture}
@@
 	\draw[>=triangle 45, <->] (7cm,-1.2cm) -- (14cm,-1.2cm);
-	\node[anchor=south] at (10.5cm,-1.2cm) {$\Xi_{i,j}^g$};
+	\node[anchor=south] at (10.5cm,-1.2cm) {$\tau_{i,j}^g$};
 
 	\draw[>=triangle 45, <->] (4cm,-2.1cm) -- (14cm,-2.1cm);
-	\node[anchor=south] at (9cm,-2.1cm) {$\Xi_{i,j}^g + \sigma_{g,j}\left(x_{j+1/2} - x'\right)$};
+	\node[anchor=south] at (9cm,-2.1cm) {$\tau_{i,j}^g + \sigma_{g,j}\left(x_{j+1/2} - x'\right)$};
 
@@
 	\bigbreak
-	For $x<x'$.
+	For $x_{j-1/2} \leqslant x'$,
 	\begin{tikzpicture}
@@
 	\draw[>=triangle 45, <->] (7cm,-1.2cm) -- (10cm,-1.2cm);
-	\node[anchor=south] at (8.5cm,-1.2cm) {$\Xi_{i,j}^g$};
+	\node[anchor=south] at (8.5cm,-1.2cm) {$\tau_{i,j}^g$};
 
 	\draw[>=triangle 45, <->] (7cm,-2.1cm) -- (13cm,-2.1cm);
-	\node[anchor=south] at (10cm,-2.1cm) {$\Xi_{i,j}^g + \sigma_{g,j}\left(x'-x_{j-1/2}\right)$};
+	\node[anchor=south] at (10cm,-2.1cm) {$\tau_{i,j}^g + \sigma_{g,j}\left(x'-x_{j-1/2}\right)$};
 	\end{tikzpicture}
@@
 	\caption{Notation for numerical evaluation of interface currents by the integral form of the transport equation.}
-	\label{fig:Xi}
+	\label{fig:tau}
 \end{figure}
 
-Substituting 
-\begin{equation}\label{eq:usub}
-u = \begin{cases}
-\Xi^g_{i\geqslant j} + \sigma_{g,j}(x_{j+1/2}-x') & x'\leqslant x \quad (j\leqslant i) \\
-\Xi^g_{i<j} + \sigma_{g,j}(x'-x_{j-1/2}) & x'>x \quad (j>i)\,\, ,
-\end{cases}
-\end{equation} 
-and integrating the $E_{n_{l,m}}$ terms in~\eq{eq:tot-J-disc} yields
-\begin{eqnarray}\label{eq:E-int}
+% Substituting 
+% \begin{equation}\label{eq:usub}
+% u = \begin{cases}
+% \Xi^g_{i\geqslant j} + \sigma_{g,j}(x_{j+1/2}-x') & x'\leqslant x \quad (j\leqslant i) \\
+% \Xi^g_{i<j} + \sigma_{g,j}(x'-x_{j-1/2}) & x'>x \quad (j>i)\,\, ,
+% \end{cases}
+% \end{equation}
+After substitution, the integration of the $E_{n_{l,m}}$ terms in~\eq{eq:tot-J-disc} yields
+\begin{subequations}\label{eq:E-int}
+\begin{equation}\label{eq:E-int-1}
+\begin{split}
 \int_{x_{j-1/2}}^{x_{j+1/2}}  dx'
-E_{n_{l,m}}[\mcL_g(x',x_{i+1/2})] &=& \frac{1}{\sigma_{g,j}}
+E_{n_{l,m}}[\mcL_g(x',x_{i+1/2})] =& \frac{1}{\sigma_{g,j}}
 	\left[
-	E_{n_{l,m}+1}(\Xi^g_{i\geqslant j}) 
-	- E_{n_{l,m}+1}(\Xi^g_{i\geqslant j	}+\sigma_{g,j}\Delta x_j)
-	\right] \nonumber \\
-	&=&
+	E_{n_{l,m}+1}(\tau^g_{i \geqslant j}) 
+	- E_{n_{l,m}+1}(\tau^g_{i \geqslant j}+\sigma_{g,j}\Delta x_j)
+	\right] \\
+	=&
 	\frac{1}{\sigma_{g,j}}
@@
 	\right] 
-	\right\} \nonumber \\	
+	\right\},
+\end{split}
+\end{equation}
+\begin{equation}\label{eq:E-int-2}
+\begin{split}
 \int_{x_{j-1/2}}^{x_{j+1/2}} dx'
-E_{n_{l,m}}[\mcL_g(x_{i+1/2},x')] &=& \frac{1}{\sigma_{g,j}}
+E_{n_{l,m}}[\mcL_g(x_{i+1/2},x')] =& \frac{1}{\sigma_{g,j}}
 \left[
-E_{n_{l,m}+1}(\Xi^g_{i<j}) 
-- E_{n_{l,m}+1}(\Xi^g_{i<j	}+\sigma_{g,j}\Delta x_j)
-\right]\nonumber \\	
-	&=&
+E_{n_{l,m}+1}(\tau^g_{i<j}) 
+- E_{n_{l,m}+1}(\tau^g_{i<j}+\sigma_{g,j}\Delta x_j)
+\right] \\	
+	=&
 \frac{1}{\sigma_{g,j}}
@@
 \right]
-\right\}
-\,\, .
-\end{eqnarray}
+\right\}.
+\end{split}
+\end{equation}
+\end{subequations}
 Hence, the interface currents can be written as
-\begin{eqnarray}\label{eq:tot-J-disc2}
-J_g(x_{i+1/2}) &=& \sum\limits_{l=0}^\infty  \frac{2l+1}{2}
+\begin{equation}\label{eq:tot-J-disc2}
+\begin{split}
+J_g(x_{i+1/2}) &= \sum\limits_{l=0}^\infty  \frac{2l+1}{2}
 \sum\limits_{m=0}^{[l/2]}  h_m
@@
 E_{n_{l,m}+1}[\mcL_g(0,x_{i+1/2})] \psi_{l,g}(0) 
-+(-1)^{l+1} E_{n_{l,m}+1}[\mcL_g(x_{i+1/2},a)]\psi_{l,g}(a)  \nonumber \\
-&+&
-\sum\limits_{j=0}^i \frac{q_{l,g,j}}{\sigma_{g,j}} 
++(-1)^{l+1} E_{n_{l,m}+1}[\mcL_g(x_{i+1/2},a)]\psi_{l,g}(a) \\
+&+\sum\limits_{j=0}^i \frac{q_{l,g,j}}{\sigma_{g,j}} 
 \left\{
@@
 \right] 
-\right\}
-\nonumber \\
-&+&(-1)^{l+1} 
+\right\} \\
+&+(-1)^{l+1} 
 \sum\limits_{j=i+1}^{I-1} \frac{q_{l,g,j}}{\sigma_{g,j}} 
@@
 \right\}
-\bigg\}	\,\, . 
-\end{eqnarray}
+\bigg\}.
+\end{split}
+\end{equation}
 Note that for the isotropic case ($l=0$) Eq.~\eqref{eq:tot-J-disc2} reduces to
-\begin{eqnarray}\label{eq:tot-J-disc2-l=0}
-J_g(x_{i+1/2}) &=& \frac{1}{2}
+\begin{equation}\label{eq:tot-J-disc2-l=0}
+\begin{split}
+J_g(x_{i+1/2}) &= \frac{1}{2}
 \bigg\{
 E_3[\mcL_g(0,x_{i+1/2})] \psi_{0,g}(0) 
-- E_3[\mcL_g(x_{i+1/2},a)]\psi_{0,g}(a)  \nonumber \\
-&&+
+- E_3[\mcL_g(x_{i+1/2},a)]\psi_{0,g}(a) \\
+&+
 \sum\limits_{j=0}^i \frac{q_{0,g,j}}{\sigma_{g,j}} 
@@
 \right] 
-\right\}
-\nonumber \\
-&&-
+\right\} \\
+&-
 \sum\limits_{j=i+1}^{I-1} \frac{q_{0,g,j}}{\sigma_{g,j}} 
@@
 \right\}
-\bigg\}	\nonumber \\
-&=&\frac{1}{2}
+\bigg\}	\\
+&=\frac{1}{2}
 \bigg\{
 E_3[\mcL_g(0,x_{i+1/2})] \psi_{0,g}(0) 
-- E_3[\mcL_g(x_{i+1/2},a)]\psi_{0,g}(a)  \nonumber \\
-&&+
+- E_3[\mcL_g(x_{i+1/2},a)]\psi_{0,g}(a) \\
+&+
 \sum\limits_{j=0}^{I-1} \frac{q_{0,g,j}}{\sigma_{g,j}} 
@@
 \right] 
-\right\}\text{sign}(i-j)
-\bigg\}
-\,\, . 
-\end{eqnarray}
-These transfer probabilities $E_{n_{l,m}}[\tau_g(x_i,x_j)]$ are pre-calculated once and are stored in a multi-dimensional array.
+\right\}\operatorname{Sgn}(i-j)
+\bigg\}. 
+\end{split}
+\end{equation}
+It is possible to identify in these equations transfer probabilities of neutrons emitted by the sources $q_{l,g,j}$ and crossing the right interface of cell $i$ without colliding.
+The quantities $E_{n_{l,m}}[\tau_g(x_i,x_j)]$ allowing to compute these probabilities can be pre-calculated once and stored in multi-dimensional arrays for later use.
 
@@
 \begin{equation}\label{eq:BC}
-J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta} ,
+J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta},
 \end{equation} 
@@
 \begin{enumerate}
-	\item\label{it:init} Initialize - the algorithm receives the geometry and the cross sections of the problem as input.
-At this stage, the corrections to the diffusion coefficients $\delta D^{(0)}(x,E)$ are set to zero and the initial pure-diffusion operator $\mathcal{A}_0(E)$ is constructed.
-Initial guesses for the flux $\phi^{(0)}(x,E)$ and multiplication factor $k^{(0)}_\texttt{eff}$ are set.
-	\item\label{it:DF-solve} Diffusion Solver - a one-dimensional multigroup diffusion solver is executed until convergence using the diffusion corrections from the previous iteration $\delta D^{(k)}(x,E)$ through the diffusion operator $\mathcal{A}^{(k)}(x,E)=\mathcal{A}_0(E)+\delta A^{(k)}(x,E)$.
-The results are an updated estimation of the diffusion flux $\phi^{(k)}(x,E)$ and the multiplication factor $k^{(k)}_\texttt{eff}$.
-	\item\label{it:Js} Calculate Currents - using the updated diffusion flux $\phi^{(k)}(x,E)$, both the diffusion current $J^{(k)}_D(x,E)$ (Eq.~\ref{eq:JD-dJ}) and the transport current $J^{(k)}_\texttt{tr}(x,E)$ (Eq.~\ref{eq:tot-J}) are calculated.
-	\item\label{it:dD} Calculate corrections - the diffusion correction $\delta D^{(k+1)}(x,E)$ (Eq.~\ref{eq:JD-dJ}) is obtained using $\delta J^{(k)}(x,E)$ and Eq.~\eqref{eq:JD-dJ}.
+	\item\label{it:init} Initialize - the algorithm receives the geometry and the cross sections (XS) of the problem as input.
+At this stage, the corrections to the diffusion coefficients $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator $\mathcal{A}_0$ is constructed.
+Initial guesses for the flux $\phi^{(0)}$ and multiplication factor $k^{(0)}_\texttt{eff}$ are set.
+	\item\label{it:DF-solve} Diffusion Solver - a one-dimensional multigroup diffusion solver is executed until convergence using the diffusion corrections from the previous iteration $\delta D^{(k)}$ through the diffusion operator $\mathcal{A}^{(k)}=\mathcal{A}_0+\delta A^{(k)}$.
+The results are an updated estimation of the diffusion flux $\phi^{(k)}$ and the multiplication factor $k^{(k)}_\texttt{eff}$.
+	\item\label{it:Js} Calculate Currents - using the updated diffusion flux $\phi^{(k)}$, both the diffusion current $J^{(k)}_D$ (Eq.~\ref{eq:JD-dJ}) and the transport current $J^{(k)}_\texttt{tr}$ (Eq.~\ref{eq:tot-J}) are calculated.
+	\item\label{it:dD} Calculate corrections - the diffusion correction $\delta D^{(k+1)}$ (Eq.~\ref{eq:JD-dJ}) is obtained using $\delta J^{(k)}$ and Eq.~\eqref{eq:JD-dJ}.
 	\item\label{it:dA} Update diffusion coefficients - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
@@
 	\node [block, right of=start, xshift=0cm,yshift=0cm] (input) {Input\\parameters};
-	\node [block, right of=input, xshift=0cm,yshift=0cm] (geoXS) {Geometry \& XS};
+	\node [block, right of=input, xshift=0cm,yshift=0cm] (geoXS) {Geometry and XS};
 	\node [block, below of=geoXS, xshift=0cm,yshift=1.5cm] (Diff)  {Diffusion\\solver};
@@
 Two one-dimensional test cases are considered, homogeneous and heterogeneous.
-The reference solutions are calculated using a Python3 discrete ordinates ($S_N$) code with $N=16$~\cite{Lewis-1984}.
-The diffusion solutions and the Ronen iterations are produced using original codes developed in Pyhton3.
-All thresholds are set to 1E-6 and no (over/under)-relaxation is done.
-The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$.
-Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$.
+The reference solutions are calculated using a Python3 discrete ordinates $S_N$ code with $N=16$~\cite{Lewis-1984}.
+The diffusion solutions and the Ronen iterations are produced using original codes still developed in Python3.
+All tolerances on relative residuals are set to 1E-6 in the iterative solving schemes and no (over/under)-relaxation is done.
+The initial diffusion coefficient is set to $D=1/(3\sigma_{tr}) = 1/(3\sigma)$ since we only consider here isotropic scattering.
+Anisotropic scattering cases are deferred to future studies.
+Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$, see~\sxn{sec:BC}.
 
@@
 
-A homogeneous slab of width $a=21.5$ cm is considered, with the two-group macroscopic cross sections shown in Table~\ref{tab:xs} (taken from~\cite{Tomatis-2011}). 
-%
-\begin{table}[!htbp]	
-	\centering
-	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] used for the homogeneous case~\cite{Tomatis-2011}.}
+A homogeneous slab of width $a=21.5$ cm is considered, with the two-group macroscopic cross sections shown in Table~\ref{tab:xs}. 
+%
+\begin{table}[htbp]
+	\centering
+	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] of the homogeneous case~\cite{Tomatis-2011}.}
 	\label{tab:xs}
@@
 		%\midrule
-		Group g &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
+		Group $g$ &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
 		\midrule
@@
 Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (with extrapolated length) and the Ronen method.
-The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and the Ronen method, respectively.
+The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
 The reference $k_\texttt{ref}$ value from S\tsub{16} is 0.744417 ($I = 400$).
 
-\begin{table}[!htbp]
+\begin{table}[htbp]
 	\centering
@@
 	\label{tab:dx_drho}
-	\begin{tabular}{lccccr}
+	\begin{tabular}{lcccccr}
 		%\midrule
-		$dx\quad (I)$ [cm]  &  $k_{\texttt{ref}}$ & $k_{\texttt{D}}$ & $\Delta\rho_\texttt{D}$ [pcm] & $k_{\texttt{RM}}$ & $\Delta\rho_\texttt{RM}$ [pcm]\\ 
+		$dx$[cm] & $I$ &  $k_{\texttt{ref}}$ & $k_{\texttt{D}}$ & $\Delta\rho_\texttt{D}$ [pcm] & $k_{\texttt{RM}}$ & $\Delta\rho_\texttt{RM}$ [pcm]\\ 
 		\midrule
-		0.43 (50)     & 0.744307 & 0.741417 & -524 & 0.740552  & -681\\
+		0.43 & ~50     & 0.744307 & 0.741417 & -524 & 0.740552  & -681\\
 		%\midrule
-		0.215 (100)    & 0.744391 & 0.741355 & -550 & 0.743447 & -171\\
+		0.215 & 100    & 0.744391 & 0.741355 & -550 & 0.743447 & -171\\
 		%\midrule
-		0.1075 (200)   & 0.744412 & 0.741339 & -557 & 0.744212 & -36\\
+		0.1075 & 200   & 0.744412 & 0.741339 & -557 & 0.744212 & -36\\
 		%\midrule
-		0.07167 (300) & 0.744416 & 0.741336 & -558 & 0.744356 & -11\\
+		0.07167 & 300 & 0.744416 & 0.741336 & -558 & 0.744356 & -11\\
 		%\midrule
-		0.05375 (400)  & 0.744417 & 0.741335 & -558 & 0.744407 & -2\\
+		0.05375 & 400  & 0.744417 & 0.741335 & -558 & 0.744407 & -2\\
 		%\midrule
@@
 
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for half-slab.
-The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:slab-fluxes-dev}.
+A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and the standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
+The deviations (in [\%]) of the RM-corrected flux and of the standard diffusion flux from the reference $S_N$ flux are also shown in Fig.~\ref{fig:slab-fluxes-dev}.
 The corresponding Ronen method correction factors $\delta D$ are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
@@
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.65\linewidth]{Sn_Diff_RM_Tomatis2011.pdf}
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.7\linewidth]{Sn_Diff_Rm_flux_Tomatis2011.pdf}
 	\caption{Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[htbp]
 	\centering
@@
 
-\begin{figure}[h!]
+\begin{figure}[htbp]
 	% convergence
@@
 	\includegraphics[width=0.4\linewidth]{convergence.pdf}
-	\caption{Convergence of the flux (max deviation) and the criticality
+	\caption{Convergence of the flux (max deviation) and of the criticality
 		eigenvalue.}
@@
 
-The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
+The RM correction terms ($\delta D$) along the slab are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
 It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary.
-The convergence of the flux (max deviation) and the criticality eigenvalue are shown in Fig.~\ref{fig:conv}.
-While the eigenvalue converges within a few iterations, the flux exhibit slow convergence near the boundaries.
-The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
-The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.
+The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}.
+While the eigenvalue converges fast within a few iterations, the flux exhibit slow convergence in general with higher differences against the reference $S_{16}$ solution near the boundaries.
+The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta \phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
+The spatial flux convergence of the Ronen iterations with respect to the reference solution for the left half slab is shown in Fig.~\ref{fig:conv3} instead.
 
 % convergence
-\begin{figure}[h!]
+\begin{figure}[htbp]
 	\centering
@@
 % convergence
-\begin{figure}[htbp!]
+\begin{figure}[hbtp]
 	\centering
@@
 The initial diffusion solution is smoother than the transport one.
-Hence, as can be seen in Fig.~\ref{fig:slab-fluxes}, the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
-The Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
-Hence, $\phi^{(k-1)}$ is smaller in the center and larger at the boundary comparing to $\phi^{(k)}$.
-This effect of the Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
+Hence, it can be seen in Fig.~\ref{fig:slab-fluxes} that the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
+Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
+Hence, $\phi^{(k-1)}$ is smaller at the center and higher at the boundary compared to $\phi^{(k)}$.
+This effect caused by Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
 %

### 2019-12-10 docs/EPJP2019/Gross-EPJP-2019.tex
revision of the theory part by Tomatis

@@
 
-\begin{figure}[htbp] 
+\begin{figure}[htbp!] 
 	\centering
@@
 The reference solutions are calculated using a Python3 discrete ordinates $S_N$ code with $N=16$~\cite{Lewis-1984}.
-The diffusion solutions and the Ronen iterations are produced using original codes still developed in Python3.
+The diffusion solutions and the Ronen iterations are produced using original codes developed in Python3.
 All tolerances on relative residuals are set to 1E-6 in the iterative solving schemes and no (over/under)-relaxation is done.
-The initial diffusion coefficient is set to $D=1/(3\sigma_{tr}) = 1/(3\sigma)$ since we only consider here isotropic scattering.
+The initial diffusion coefficient is set to $D=(3\sigma_{tr})^{-1}=(3\sigma)^{-1}$ since we only consider here anisotropic scattering.
 Anisotropic scattering cases are deferred to future studies.
-Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$, see~\sxn{sec:BC}.
+Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$.
 
@@
 Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (with extrapolated length) and the Ronen method.
-The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
+The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and the Ronen method, respectively.
 The reference $k_\texttt{ref}$ value from S\tsub{16} is 0.744417 ($I = 400$).
@@
 
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and the standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
-The deviations (in [\%]) of the RM-corrected flux and of the standard diffusion flux from the reference $S_N$ flux are also shown in Fig.~\ref{fig:slab-fluxes-dev}.
+A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
+The deviations (in [\%]) of the RM-corrected flux and the standard diffusion ($D_0$) flux from the reference $S_N$ flux is also shown in Fig.~\ref{fig:slab-fluxes-dev}.
 The corresponding Ronen method correction factors $\delta D$ are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
@@
 	\includegraphics[width=0.4\linewidth]{convergence.pdf}
-	\caption{Convergence of the flux (max deviation) and of the criticality
+	\caption{Convergence of the flux (max deviation) and the criticality
 		eigenvalue.}
@@
 
-The RM correction terms ($\delta D$) along the slab are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
+The RM correction terms ($\delta D$) along the plane are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
 It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary.
-The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}.
-While the eigenvalue converges fast within a few iterations, the flux exhibit slow convergence in general with higher differences against the reference $S_{16}$ solution near the boundaries.
-The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta \phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
-The spatial flux convergence of the Ronen iterations with respect to the reference solution for the left half slab is shown in Fig.~\ref{fig:conv3} instead.
+The convergence of the flux (max deviation) and the criticality eigenvalue are shown in Fig.~\ref{fig:conv}.
+While the eigenvalue converges within a few iterations, the flux exhibit slow convergence near the boundaries.
+The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta\phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
+The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab is shown in Fig.~\ref{fig:conv3}.
 
 % convergence
-\begin{figure}[htbp]
+\begin{figure}[h!]
 	\centering
@@
 % convergence
-\begin{figure}[hbtp]
+\begin{figure}[htbp!]
 	\centering
@@
 The initial diffusion solution is smoother than the transport one.
-Hence, it can be seen in Fig.~\ref{fig:slab-fluxes} that the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
-Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
-Hence, $\phi^{(k-1)}$ is smaller at the center and higher at the boundary compared to $\phi^{(k)}$.
-This effect caused by Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
+Hence, as can be seen in Fig.~\ref{fig:slab-fluxes}, the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
+The Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
+Hence, $\phi^{(k-1)}$ is smaller in the center and larger at the boundary comparing to $\phi^{(k)}$.
+This effect of the Ronen iterations produces less smooth flux shape with steeper gradients comparing to the diffusion solution.
 %

### 2019-12-11 docs/EPJP2019/Gross-EPJP-2019.tex
Update Gross-EPJP-2019.tex
Updated flow chart and description.
Some text and newcommants update.

--- 2019-12-10 docs/EPJP2019/Gross-EPJP-2019.tex
@@
 \tikzstyle{decision} = [diamond, draw, fill=white!20, 
-text width=3em, text badly centered, node distance=2cm, inner sep=1pt, line width=1pt]
+text width=4em, text badly centered, node distance=2cm, inner sep=2pt, line width=1pt]
 \tikzstyle{block} = [rectangle, draw, fill=white!20, 
@@
 \newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
+\newcommand{\kref}{{\ensuremath{k_{\textrm{\scriptsize{ref}}}}}}
+\newcommand{\krm}{{\ensuremath{k_{\textrm{\scriptsize{RM}}}}}}
+\newcommand{\kd}{{\ensuremath{k_{\textrm{\scriptsize{D}}}}}}
 \newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
@@
 \newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
+\newcommand{\jd}{\ensuremath{J_{\textrm{\scriptsize{D}}}}}
+\newcommand{\delj}{\ensuremath{\delta J}}
 %\newcommand{\mcL}{\mathcal{L}}
@@
 
-Instead of computing new diffusion coefficients at the interfaces by Fick's law, $J_D(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\delta J(x_s,E) = \jtrr(x_s,E) - J_D(x_s,E)$ are obtained at cell interfaces $x_s$.
-Here, $J_D(x,E)$ is called the ``diffusion current'' and is obtained using Fick's law, with the original values of the diffusion coefficients and with the derivative approximated by finite differences.
+Instead of computing new diffusion coefficients at the interfaces by Fick's law, $\jd(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\jd(x_s,E) = \jtrr(x_s,E) - \jd(x_s,E)$ are obtained at cell interfaces $x_s$.
+Here, $\jd(x,E)$ is called the ``diffusion current'' and is obtained using Fick's law, with the original values of the diffusion coefficients and with the derivative approximated by finite differences.
 In one-dimensional
@@
 \begin{align}
-J_D(x_{i+1/2},E) \cong& -D(x_{i+1/2},E) 
+\jd(x_{i+1/2},E) \cong& -D(x_{i+1/2},E) 
 \frac{\phi(x_{i+1},E) - \phi(x_i,E)}
@@
 where integer and rational subscripts indicate node-averaged and interface quantities, respectively.
-The discretized form of the current $\delta J$ must involve the neighboring flux as well, but its representation is changed into a drift-advection term to get rid of possible undefined division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}.
+The discretized form of the current $\delj$ must involve the neighboring flux as well, but its representation is changed into a drift-advection term to get rid of possible undefined division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}.
 The so-called ``transport current'' $\jtrr(x_s,E)$ is evaluated using the integral expression derived in~\sxn{sec:int-flux-J} as described in~\sxn{sec:calc-int-curr}.
@@
 The new numerical corrections $\delta D$ are obtained at the interfaces using~\eqs{eq:dJ} to be used in the finite differences solver, together with the diffusive currents from~\eq{eq:JD}.
-Hence, the neutron balance resolved by the CMFD takes into account both types of currents $J_D$ and $\delta J$.
-%Non-linear iterations with new corrections given by $\delta J$ are needed because of their dependence on the unknown flux.
+Hence, the neutron balance resolved by the CMFD takes into account both types of currents $\jd$ and $\delj$.
+%Non-linear iterations with new corrections given by $\delj$ are needed because of their dependence on the unknown flux.
 In particular, the one-dimensional multigroup neutron balance CMFD diffusion equations actually solved are
 \begin{equation}\label{eq:diff1}
-J_{D,g}^+(x) + \delta J_{D,g}^+(x) -  J_{D,g}^-(x) - \delta J_{D,g}^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x),
+J_{D,g}^+(x) + \delj_g^+(x) -  J_{D,g}^-(x) - \delj_g^-(x) + \sigma_{g}\phi_g(x) =  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,g'}(x)\phi_{g'}(x) + \sum\limits_{g'=1}^G\sigma_{s,g\leftarrow g'}\phi_{g'}(x),
 \end{equation}
@@
 \begin{equation}\label{eq:BC}
-J_D(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta},
+\jd(x=0) = -D_0\frac{\phi_0}{\Delta x_0/2 + \zeta},
 \end{equation} 
@@
 %
-The quantity $\delta J$ at the boundary takes the simpler form of $\delta J = -\delta D_{-1/2}\phi_0$, without dividing by the spatial width, since no particular extrapolation length is appropriate for the correction.
+The quantity $\delj$ at the boundary takes the simpler form of $\delj = -\delta D_{-1/2}\phi_0$, without dividing by the spatial width, since no particular extrapolation length is appropriate for the correction.
 The expression for the right boundary is straightforward, implying a non-negative current.
 One should recall that the diffusion coefficient remains constant throughout the calculation, and so is the extrapolated distance.
-Only $\delta D$ is recalculated and the correction is actually implemented through the currents, i.e., $J_{tr} = J_D + \delta J$.
+Only $\delta D$ is recalculated and the correction is actually implemented through the currents, i.e., $\jtrr = \jd + \delj$.
 
@@
 	\item\label{it:init} Initialize - the algorithm receives the geometry and the cross sections (XS) of the problem as input.
-At this stage, the corrections to the diffusion coefficients $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator $\mathcal{A}_0$ is constructed.
-Initial guesses for the flux $\phi^{(0)}$ and multiplication factor $k^{(0)}_\texttt{eff}$ are set.
-	\item\label{it:DF-solve} Diffusion Solver - a one-dimensional multigroup diffusion solver is executed until convergence using the diffusion corrections from the previous iteration $\delta D^{(k)}$ through the diffusion operator $\mathcal{A}^{(k)}=\mathcal{A}_0+\delta A^{(k)}$.
-The results are an updated estimation of the diffusion flux $\phi^{(k)}$ and the multiplication factor $k^{(k)}_\texttt{eff}$.
-	\item\label{it:Js} Calculate Currents - using the updated diffusion flux $\phi^{(k)}$, both the diffusion current $J^{(k)}_D$ (Eq.~\ref{eq:JD-dJ}) and the transport current $J^{(k)}_\texttt{tr}$ (Eq.~\ref{eq:tot-J}) are calculated.
-	\item\label{it:dD} Calculate corrections - the diffusion correction $\delta D^{(k+1)}$ (Eq.~\ref{eq:JD-dJ}) is obtained using $\delta J^{(k)}$ and Eq.~\eqref{eq:JD-dJ}.
-	\item\label{it:dA} Update diffusion coefficients - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
-	\item\label{it:conv} If flux and eigenvalue are not converged, go to step~\ref{it:DF-solve}.
+At this stage, the correction factors $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator $\mathcal{A}_0$ is constructed.
+Initial guesses for the flux $\phi^{(0)}$ and multiplication factor $\keff^{(0)}$ are set.
+	\item\label{it:Js} Calculate currents - using the diffusion flux $\phi^{(k)}$, both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD-dJ}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated.
+	\item\label{it:dD} Calculate correction factors - the correction factors $\delta D^{(k+1)}$ (Eq.~\ref{eq:JD-dJ}) is obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:JD-dJ}.
+	\item\label{it:dA} Update diffusion operator - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
+	\item\label{it:DF-solve} Diffusion solver - a one-dimensional multigroup diffusion solver is executed until convergence.
+The results are an updated estimation of the diffusion flux $\phi^{(k+1)}$ and the multiplication factor $\keff^{(k+1)}$.
+	\item\label{it:cvg} Check convergence - check if the flux $\phi^{(k)}$ and the multiplication factor $\keff^{(k)}$ converged. If yes, stop, otherwise, step~\ref{it:Js}.
 \end{enumerate}
@@
 	\node [cloud] 					 						(start) {START};
-	\node [block, right of=start, xshift=0cm,yshift=0cm] (input) {Input\\parameters};
-	\node [block, right of=input, xshift=0cm,yshift=0cm] (geoXS) {Geometry and XS};
-	\node [block, below of=geoXS, xshift=0cm,yshift=1.5cm] (Diff)  {Diffusion\\solver};
-	\node [block, below of=Diff, xshift=0cm,yshift=1.5cm] (J)  {Calculate $J^{(k)}_{\texttt{tr}},J^{(k)}_D,\delta J^{(k)}$};
-	\node [block, left  of=J,    xshift=0cm,yshift=0cm] (dD) {Obtain\\$\delta D^{(k+1)}$};
-	\node [block, left  of=dD,   xshift=0cm,yshift=0cm](dA) {Calculate\\$\delta \mathcal{A}^{(k+1)}$};
-	\node [block, above of=dA,   xshift=0cm,yshift=-1.5cm] (Anew) {Construct\\$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};
+	\node [block, below of=start, xshift=0cm,yshift=1.5cm]  (input) {Input\\parameters};
+	\node [block, below of=input, xshift=0cm,yshift=1.5cm]  (geoXS) {Geometry, XS};
+	\node [block, below of=geoXS, xshift=0cm,yshift=1.5cm]  (J)     {Calculate $\jtrr^{(k)},\jd^{(k)},\delj^{(k)}$};
+	\node [block, below of=J,     xshift=0cm,yshift=1.5cm]  (dDA)   {Obtain $\delta D^{(k+1)}$, $\delta \mathcal{A}^{(k+1)}$};
+	\node [block, below of=dDA,  xshift=0cm,yshift=1.5cm]  	(Anew)  {Construct\\$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};
+	\node [block, below of=Anew, xshift=0cm,yshift=1.5cm]  	(Diff)  {Diffusion\\solver};
+	\node [decision, below of=Diff,xshift=0cm,yshift=-1cm]	(cvg)   {$\phi^{(k+1)}$, $k^{(k+1)}$ \\ converged?};
+	\node [cloud, below of=cvg,xshift=0cm,yshift=1.5cm] 	(stp)  {STOP};
 
@@
 	\path [line] (input) -- (geoXS);
-	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\mathcal{A}_0$}(Diff);
-	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k)},k^{(k)}$}(J);
-	\path [line] (J)  -- node[anchor= north]{}(dD);
-	\path [line] (dD) -- node[anchor= north]{}(dA);
-	\path [line] (dA)  -- node[anchor= north]{}(Anew);
-	\path [line] (Anew)  -- node[near end,anchor= south west,xshift=-1.7cm]{$\mathcal{A}^{(k+1)}$}(Diff);
+	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(0)}$, $k^{(0)}$, $\mathcal{A}_0$}(J);
+	\path [line] (J) 	 -- (dDA);
+	\path [line] (dDA) 	 -- (Anew);
+	\path [line] (Anew)  -- node[near end,anchor= south west,xshift=0cm]{$\mathcal{A}^{(k+1)}$}(Diff);
+	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k+1)},k^{(k+1)}$}(cvg);
+	\path [line] (cvg)   -- node[anchor= south west]{YES}(stp);
+	\path [line] (cvg)   -| node[near start,yshift=0.2cm]{NO}(-3,-6.0) -- node[near end]{}(J);
 
@@
 Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (with extrapolated length) and the Ronen method.
-The reactivity difference is given by $(\Delta\rho = 1/k_\texttt{ref} - 1/k_\texttt{D/RM})\times 10^5$, where $k_D$ and $k_{RM}$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
-The reference $k_\texttt{ref}$ value from S\tsub{16} is 0.744417 ($I = 400$).
+The reactivity difference is given by $(\Delta\rho = 1/\kref - 1/k_\texttt{D/RM})\times 10^5$, where $\kd$ and $\krm$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
+The reference $\kref$ value from S\tsub{16} is 0.744417 ($I = 400$).
 
@@
 		%\midrule
-		$dx$[cm] & $I$ &  $k_{\texttt{ref}}$ & $k_{\texttt{D}}$ & $\Delta\rho_\texttt{D}$ [pcm] & $k_{\texttt{RM}}$ & $\Delta\rho_\texttt{RM}$ [pcm]\\ 
+		$dx$[cm] & $I$ &  $\kref$ & $\kd$ & $\Delta\rho_\texttt{D}$ [pcm] & $\krm$ & $\Delta\rho_\texttt{RM}$ [pcm]\\ 
 		\midrule
@@
 Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
-The (more accurate) surface current $J_{\texttt{tr}}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_\texttt{D}$, plus a correction $\delta J$.
-Hence, when the current vanishes, the correction $\delta J$ vanishes as well.
+The (more accurate) surface current $\jtrr$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $\jd$, plus a correction $\delj$.
+Hence, when the current vanishes, the correction $\delj$ vanishes as well.
 Moreover, the correction is written as in Eq.~\eqref{eq:JD-dJ}, avoiding the potential divergence resulting from division by zero.

### 2019-12-12 FD1dMGdiff/FDsDiff1D.py
Minor modification to save flux and k convergence errors Modified:   FDsDiff1D.py In function solve_RMits: Added two arrays to save convergence errors - kerr_save, ferr_save. These arrays are saved into .npy file i output directory.

@@ -809,6 +809,8 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
     # keep track of partial solutions on external files
     flx_save = np.empty([G, I, ritmax + 1])
     k_save = np.full(ritmax + 1, -1.)
+    kerr_save = np.full(ritmax, -1.)
+    ferr_save = np.full(ritmax, -1.)
 
     err, itr, kinit = 1.e+20, 0, k
     Dflxm1 = np.zeros_like(flx)
@@ -851,11 +853,17 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
         Dflxm2 = np.array(Dflxm1, copy=True)
         Dflxm1 = flx - flxold
         ferr = np.where(flx > 0., 1. - flxold / flx, Dflxm1)
-
+        kerr = (k-kold)/k
+        
         err = abs(ferr[np.unravel_index(abs(ferr).argmax(), (G, I))])
+        
+        kerr_save[itr] = kerr
+        ferr_save[itr] = err
+        
         itr += 1
-        lg.info("+RM+ it={:^4d}, k={:<13.6g}, err={:<+13.6e}".format(
-            itr, k, err
+        
+        lg.info("+RM+ it={:^4d}, k={:<13.6g}, kerr={:<+13.6e}, ferr={:<+13.6e}".format(
+            itr, k, kerr, err
         ))
         lg.info("{:^4s}{:^13s}{:^6s}{:^13s}".format(
             "G", "max(err)", "at i", "std(err)"
@@ -875,8 +883,8 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
 
     k_save[itr], flx_save[:, :, itr] = k, flx  # store final values
     lg.info("Initial value of k was %13.6g." % kinit)
-    if filename is not None:
-        # filename = "output/kflx_LBC%dRBC%d_I%d" % (*BC,I)
+    if filename is not None:        
+        np.save(filename.replace('kflx','err'), [kerr_save, ferr_save], allow_pickle=True)
         np.save(filename + ".npy", [k_save, flx_save], allow_pickle=True)
         with open(filename + ".dat", 'w') as f:
             i = 0

### 2019-12-12 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -19,7 +19,7 @@ def MyWho():
 
 # definition of the spatial mesh
 L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
-I = 20  # nb of spatial cells
+I = 200  # nb of spatial cells
 xi = np.linspace(0, L, I+1)  # equidistant mesh
 
 geometry_type = 'slab'
@@ -32,7 +32,7 @@ xs_media = {
 media = [['HM', L]]  # i.e. homogeneously filled
 
 # set b.c.
-LBC, RBC = 2, 0
+LBC, RBC = 0, 2
 
 Homog2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
 
@@ -42,6 +42,6 @@ if __name__ == "__main__":
     lg.info("*** Solve the M&C 2011 problem ***")
     from FDsDiff1D import run_calc_with_RM_its, solver_options
 
-    slvr_opts = solver_options(ritmax=10)
-    # filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
-    flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename=None)
+    slvr_opts = solver_options(ritmax=2)
+    filename = "../output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
+    flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename)

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
Further minor text fixes towards final version.

@@
 In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux is resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\jtr\rE$ and $\bm{J}_D\rE$, respectively, the Ronen idea is based on changing the diffusion coefficient such that
+Denoting the currents obtained by integral transport as ``integral currents'' $\jtr\rE$ and the currents obtained by Fick's law as ``diffusion currents'' $\bm{J}_D\rE$, the Ronen idea is based on changing the diffusion coefficient such that
 \begin{equation}\label{eq:Fick}
@@
 
-Instead of computing new diffusion coefficients at the interfaces by Fick's law, $\jd(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\jd(x_s,E) = \jtrr(x_s,E) - \jd(x_s,E)$ are obtained at cell interfaces $x_s$.
+Instead of computing new diffusion coefficients at the interfaces by Fick's law, $\jd(x,E) = -D(E) \partial_x \phi(x,E)$, new corrective currents $\delta J(x_s,E) = \jtrr(x_s,E) - \jd(x_s,E)$ are obtained at cell interfaces $x_s$.
 Here, $\jd(x,E)$ is called the ``diffusion current'' and is obtained using Fick's law, with the original values of the diffusion coefficients and with the derivative approximated by finite differences.
-In one-dimensional
-geometry and using the notation in \fig{fig:mesh1D}, the diffusion current and the corrective current are evaluated according to
-\begin{subequations}\label{eq:JD-dJ}
-\begin{align}
-\jd(x_{i+1/2},E) \cong& -D(x_{i+1/2},E) 
+In one-dimensional geometry and using the notation in \fig{fig:mesh1D}, the diffusion current is evaluated according to
+\begin{equation}\label{eq:JD}
+\jd(x_{i+1/2},E) \cong -D(x_{i+1/2},E) 
 \frac{\phi(x_{i+1},E) - \phi(x_i,E)}
-{(\Delta x_{i+1} + \Delta x_i)/2}, \label{eq:JD} \\
-\delta J(x_{i+1/2},E) =& -\delta D(x_{i+1/2},E) 
+{(\Delta x_{i+1} + \Delta x_i)/2},
+\end{equation}
+and the corrective current is defined according to
+\begin{equation}\label{eq:dJ}
+\delta J(x_{i+1/2},E) = -\delta D(x_{i+1/2},E) 
 \frac{\phi(x_{i+1},E) + \phi(x_i,E)}
-{(\Delta x_{i+1} + \Delta x_i)/2}, \label{eq:dJ}
-\end{align}
-\end{subequations}
+{(\Delta x_{i+1} + \Delta x_i)/2},
+\end{equation}
 where integer and rational subscripts indicate node-averaged and interface quantities, respectively.
+It is Eq.~\eqref{eq:dJ} from which the correction factors $\delta D$ are obtained.
 The discretized form of the current $\delj$ must involve the neighboring flux as well, but its representation is changed into a drift-advection term to get rid of possible undefined division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}.
@@
 
-Using the definitions in~\eqsand{eq:JD-dJ}{eq:Ds} with the notation shown in~\fig{fig:mesh1D}, the discretized form of~\eq{eq:diff1} is
+Using the definitions in Eqs.~\eqsthru{eq:JD}{eq:Ds} with the notation shown in~\fig{fig:mesh1D}, the discretized form of~\eq{eq:diff1} is
 \begin{equation}\label{eq:FD_diff_full}
@@
 Initial guesses for the flux $\phi^{(0)}$ and multiplication factor $\keff^{(0)}$ are set.
-	\item\label{it:Js} Calculate currents - using the diffusion flux $\phi^{(k)}$, both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD-dJ}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated.
-	\item\label{it:dD} Calculate correction factors - the correction factors $\delta D^{(k+1)}$ (Eq.~\ref{eq:JD-dJ}) is obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:JD-dJ}.
-	\item\label{it:dA} Update diffusion operator - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
+	\item\label{it:Js} Calculate currents - using the flux $\phi^{(k)}$ obtained from the diffusion solver, both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated.
+	\item\label{it:dD} Calculate correction factors - the correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ}.
+	\item\label{it:dA} Update the diffusion operator - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
 	\item\label{it:DF-solve} Diffusion solver - a one-dimensional multigroup diffusion solver is executed until convergence.
-The results are an updated estimation of the diffusion flux $\phi^{(k+1)}$ and the multiplication factor $\keff^{(k+1)}$.
+The results are an updated estimation of the flux $\phi^{(k+1)}$ and the multiplication factor $\keff^{(k+1)}$.
 	\item\label{it:cvg} Check convergence - check if the flux $\phi^{(k)}$ and the multiplication factor $\keff^{(k)}$ converged. If yes, stop, otherwise, step~\ref{it:Js}.
@@
 	\node [cloud] 					 						(start) {START};
-	\node [block, below of=start, xshift=0cm,yshift=1.5cm]  (input) {Input\\parameters};
-	\node [block, below of=input, xshift=0cm,yshift=1.5cm]  (geoXS) {Geometry, XS};
-	\node [block, below of=geoXS, xshift=0cm,yshift=1.5cm]  (J)     {Calculate $\jtrr^{(k)},\jd^{(k)},\delj^{(k)}$};
-	\node [block, below of=J,     xshift=0cm,yshift=1.5cm]  (dDA)   {Obtain $\delta D^{(k+1)}$, $\delta \mathcal{A}^{(k+1)}$};
-	\node [block, below of=dDA,  xshift=0cm,yshift=1.5cm]  	(Anew)  {Construct\\$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};
-	\node [block, below of=Anew, xshift=0cm,yshift=1.5cm]  	(Diff)  {Diffusion\\solver};
-	\node [decision, below of=Diff,xshift=0cm,yshift=-1cm]	(cvg)   {$\phi^{(k+1)}$, $k^{(k+1)}$ \\ converged?};
-	\node [cloud, below of=cvg,xshift=0cm,yshift=1.5cm] 	(stp)  {STOP};
+	\node [block, below of=start, xshift=0cm,yshift=2.2cm]  (geoXS) {Geometry, XS};
+	\node [block, below of=geoXS, xshift=0cm,yshift=1.8cm]  (J)     {Calculate $\jtrr^{(k)},\jd^{(k)},\delj^{(k)}$};
+	\node [block, below of=J,     xshift=0cm,yshift=2.0cm]  (dDA)   {Obtain $\delta D^{(k+1)}$ $\delta \mathcal{A}^{(k+1)}$};
+	\node [block, below of=dDA,  xshift=0cm,yshift=2.0cm]  	(Anew)  {Construct\\$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};
+	\node [block, below of=Anew, xshift=0cm,yshift=1.8cm]  	(Diff)  {Diffusion\\solver};
+	\node [decision, below of=Diff,xshift=0cm,yshift=-.5cm]	(cvg)   {$\phi^{(k+1)}$ $k_\textrm{eff}^{(k+1)}$ \\ converged?};
+	\node [cloud, below of=cvg,xshift=0cm,yshift=1.8cm] 	(stp)  {STOP};
 
 % Draw edges
-	\path [line] (start) -- (input);
-	\path [line] (input) -- (geoXS);
-	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(0)}$, $k^{(0)}$, $\mathcal{A}_0$}(J);
+	\path [line] (start) -- (geoXS);
+	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(0)}$, $k_\textrm{eff}^{(0)}$, $\mathcal{A}_0$}(J);
 	\path [line] (J) 	 -- (dDA);
@@
 	\path [line] (Anew)  -- node[near end,anchor= south west,xshift=0cm]{$\mathcal{A}^{(k+1)}$}(Diff);
-	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k+1)},k^{(k+1)}$}(cvg);
-	\path [line] (cvg)   -- node[anchor= south west]{YES}(stp);
-	\path [line] (cvg)   -| node[near start,yshift=0.2cm]{NO}(-3,-6.0) -- node[near end]{}(J);
+	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k+1)},k_\textrm{eff}^{(k+1)}$}(cvg);
+	\path [line] (cvg)   -- node[anchor= south west,yshift=-0.1cm]{YES}(stp);
+	\path [line] (cvg)   -| node[near start,yshift=0.2cm]{NO}(-3,-3.0) -- node[near end]{}(J);
 
@@
 The reference solutions are calculated using a Python3 discrete ordinates $S_N$ code with $N=16$~\cite{Lewis-1984}.
-The diffusion solutions and the Ronen iterations are produced using original codes still developed in Python3.
+The diffusion solutions and the Ronen iterations are produced using original codes in Python3.
 All tolerances on relative residuals are set to 1E-6 in the iterative solving schemes and no (over/under)-relaxation is done.
-The initial diffusion coefficient is set to $D=1/(3\sigma_{tr}) = 1/(3\sigma)$ since we only consider here isotropic scattering.
+The initial diffusion coefficient is set to $D=1/(3\sigma_{tr}) = 1/(3\sigma)$ since only isotropic scattering is considered in this case.
 Anisotropic scattering cases are deferred to future studies.
-Void boundary conditions are used at the edges of the slab, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$, see~\sxn{sec:BC}.
+Void boundary conditions are used at the outer edges of the core, which are implemented for the diffusion solver in the form of a group-dependent extrapolated distance, i.e., $d_g = 2.13 D_g$, see~\sxn{sec:BC}.
 
@@
 		%\midrule
-		2 & 1.30058$\times$10\tsup{+0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{+0}	& 0 & 1.41284$\times$10\tsup{-1} \\
+		2 & 1.30058$\times$10\tsup{0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{0}	& 0 & 1.41284$\times$10\tsup{-1} \\
 		%\midrule
@@
 Table~\ref{tab:dx_drho} shows the reactivity differences as a function of mesh refinement using standard diffusion (with extrapolated length) and the Ronen method.
-The reactivity difference is given by $(\Delta\rho = 1/\kref - 1/k_\texttt{D/RM})\times 10^5$, where $\kd$ and $\krm$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
+The reactivity difference is given by $(\Delta\rho = 1/\kref - 1/k_\textrm{D/RM})\times 10^5$ pcm, where $\kd$ and $\krm$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
 The reference $\kref$ value from S\tsub{16} is 0.744417 ($I = 400$).
@@
 		%\midrule
-		$dx$[cm] & $I$ &  $\kref$ & $\kd$ & $\Delta\rho_\texttt{D}$ [pcm] & $\krm$ & $\Delta\rho_\texttt{RM}$ [pcm]\\ 
+		$dx$[cm] & $I$ &  $\kref$ & $\kd$ & $\Delta\rho_\textrm{D}$ [pcm] & $\krm$ & $\Delta\rho_\textrm{RM}$ [pcm]\\ 
 		\midrule
@@
 
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and the standard multigroup diffusion without RM correction ($D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
+A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and the standard multigroup diffusion without RM correction (denoted by $D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
 The deviations (in [\%]) of the RM-corrected flux and of the standard diffusion flux from the reference $S_N$ flux are also shown in Fig.~\ref{fig:slab-fluxes-dev}.
@@
 
-The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0\%, respectively.
+The deviation from the reference solution is decreased by the Ronen iterations from approximately 20\% near the boundary and 1\% at the slab center to 2\% and 0.01\%, respectively.
 
@@
 	\caption{Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
+The insets show a zoom-in of the fluxes near the boundary.
 Results shown here after 250 Ronen iterations.}
@@
 The RM correction terms ($\delta D$) along the slab are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
-It is clear that the diffusion correction assumes zero values at the slab center and exhibit non-trivial behavior near the boundary.
+It is clear that the diffusion correction assumes near-zero values at the slab center and exhibits non-trivial behavior near the boundary.
 The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}.
-While the eigenvalue converges fast within a few iterations, the flux exhibit slow convergence in general with higher differences against the reference $S_{16}$ solution near the boundaries.
+While the eigenvalue converges within a few iterations, the flux exhibit relatively slow convergence with higher differences against the reference $S_{16}$ solution near the boundaries.
 The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta \phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
@@
 	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2_sn.pdf}
-	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_N$ solution for the left half slab.}
+	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_{16}$ solution for the left half slab.}
 	\label{fig:conv3}
@@
 Hence, it can be seen in Fig.~\ref{fig:slab-fluxes} that the diffusion solution underestimates the peak flux at the center of the slab and overestimates the flux near the boundary.
-Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
+The Ronen iterations ``push'' the diffusion solution towards the transport one by increasing the flux level at the center of the slab and decreasing the flux level at the boundary.
 Hence, $\phi^{(k-1)}$ is smaller at the center and higher at the boundary compared to $\phi^{(k)}$.
@@
 	% -------------- Assembly 1 --------------
-	\node[above] at (-2,1.5) {Assembly 1};
+	\node[above] at (-2,1.5) {Assembly A1};
 	\draw[pattern=north west lines, preaction={fill=blue!70}] (-3,0)   rectangle (-2.8,1.5);
@@
 	% -------------- Assembly 2 --------------
-	\node[above] at (1,1.5) {Assembly 2};
+	\node[above] at (1,1.5) {Assembly A2};
 	\draw[pattern=north west lines, preaction={fill=blue!70}] (0,0)	  rectangle (0.2,1.5);
@@
 	% -------------- Assembly 3 --------------
-	\node[above] at (-2,-1) {Assembly 3};
+	\node[above] at (-2,-1) {Assembly A3};
 	\draw[pattern=north west lines, preaction={fill=blue!70}]  (-3,-2.5)   rectangle (-2.8,-1);
@@
 	\draw[pattern=north west lines, preaction={fill=blue!70}] (-1.2,-2.5)  rectangle (-1,-1);
-	\draw [<->] (-3,-2.7) -- node[below]{$15.24[cm]$}	(-1,-2.7);
+	\draw [<->] (-3,-2.7) -- node[below]{15.24 [cm]}	(-1,-2.7);
 	% -------------- Assembly 4 --------------
-	\node[above] at (1,-1) {Assembly 4};
+	\node[above] at (1,-1) {Assembly A4};
 	\draw[pattern=north west lines, preaction={fill=blue!70}]  (0,-2.5)    rectangle (0.2,-1); 
@@
 	\draw [fill=orange!80]  (10,-2.5) rectangle node{A1}	(11,-1.5);
-	\draw [<->] (4,-2.8) -- node[below]{$106.68[cm]$}	(11,-2.8);
+	\draw [<->] (4,-2.8) -- node[below]{106.68 [cm]}	(11,-2.8);
 	\end{tikzpicture}
@@
 
-\begin{table}[htbp!]	
+\begin{table}[htbp]	
 	\centering
@@
 	\begin{tabular}{lcccccccr}
-		Material&$\sigma_1$&$\sigma_2$&$\nu\sigma_{f,1}$&$\nu\sigma_{f,2}$&$\sigma_{s,1\leftarrow 1}$&$\sigma_{s,2\leftarrow 1}$&$\sigma_{s,2\leftarrow 2}$&$x[cm]$\\
+		Material&$\sigma_1$&$\sigma_2$&$\nu\sigma_{f,1}$&$\nu\sigma_{f,2}$&$\sigma_{s,1\leftarrow 1}$&$\sigma_{s,2\leftarrow 1}$&$\sigma_{s,2\leftarrow 2}$&$x$ [cm]\\
 		\midrule
@@
 
+%\newpage
 Table~\ref{tab:dx_drho2} shows the reactivity differences between standard diffusion (with extrapolated length) and the Ronen method (at increasing number of iterations) with respect to the reference solution for each of the three core configurations.
@@
 The Ronen method performs better than standard diffusion for all three cores, even after merely 10 iterations.
-Additional Ronen iterations further improve the estimated multiplication factor but less with milder changes.
+Additional Ronen iterations further improve the estimated multiplication factor until convergence.
 
@@
 Hence, when the current vanishes, the correction $\delj$ vanishes as well.
-Moreover, the correction is written as in Eq.~\eqref{eq:JD-dJ}, avoiding the potential divergence resulting from division by zero.
+Moreover, the correction is written as in Eq.~\eqref{eq:dJ}, avoiding the potential divergence resulting from division by zero.
 

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
Finished revising text. Added 3 revised figures.

@@
 The reactivity difference is given by $(\Delta\rho = 1/\kref - 1/k_\textrm{D/RM})\times 10^5$ pcm, where $\kd$ and $\krm$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
-The reference $\kref$ value from S\tsub{16} is 0.744417 ($I = 400$).
+The reference $\kref$ value from S16 is 0.744417 ($I = 400$).
 
@@
 	\centering
-	\includegraphics[width=0.4\linewidth]{convergence.pdf}
+	\includegraphics[width=0.65\linewidth]{epsilon.pdf}	
+	%\includegraphics[width=0.4\linewidth]{convergence.pdf}
 	\caption{Convergence of the flux (max deviation) and of the criticality
-		eigenvalue.}
+		eigenvalue during 200 Ronen iterations.}
 	\label{fig:conv}
@@
 It is clear that the diffusion correction assumes near-zero values at the slab center and exhibits non-trivial behavior near the boundary.
-The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}.
-While the eigenvalue converges within a few iterations, the flux exhibit relatively slow convergence with higher differences against the reference $S_{16}$ solution near the boundaries.
+The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}, where $\epsilon_\phi = \operatorname{max} [\phi^{(k)}-\phi^{(k-1)})/\phi^{(k-1)}]$ and $\epsilon_k = (k_\textrm{eff}^{(k)}-k_\textrm{eff}^{(k-1)})/k_\textrm{eff}^{(k-1)}$.
+The flux exhibits relatively slow convergence with respect to the convergence rate of the eigenvalue.
+The largest differences between the flux and the reference $S_{16}$ solution appear near the boundaries.
 The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta \phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
@@
 	\centering
-	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1.pdf}
-	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2.pdf}
+	\includegraphics[width=0.65\linewidth]{fast_flx_err_RM.pdf}
+	\includegraphics[width=0.65\linewidth]{thermal_flx_err_RM.pdf}	%\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1.pdf}
+	%\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2.pdf}
 	\caption{The spatial flux convergence between two successive Ronen iterations for the left half slab, according to $\Delta\phi = (\phi^{(k-1)}-\phi^{(k)})/\phi^{(k-1)}$ [\%].}
@@
 Configuration 1 represents the least heterogeneous core with rather smooth flux gradients.
-On the contrary, configuration 3 represents the most heterogeneous core with the steepest flux gradients and can serve as a limiting case.
+On the contrary, configuration 3 represents the most heterogeneous core with the steepest flux gradients and can serve as a limiting case~\cite{Rahnema-1997}.
 Void boundary conditions are imposed on both ends of the core.
@@
 Table~\ref{tab:dx_drho2} shows the reactivity differences between standard diffusion (with extrapolated length) and the Ronen method (at increasing number of iterations) with respect to the reference solution for each of the three core configurations.
-The standard diffusion solution perform rather well for core 1 with deviation of 182 pcm, but fails for cores 2 and 3 with deviation of 773 and 3335 pcm, respectively.
+The standard diffusion solution perform rather well for core 1 with deviation of 182 pcm, but fails for cores 2 and 3 with deviations of 773 and 3335 pcm, respectively.
 This is explained by the fact that cores 2 and 3 are more heterogeneous with respect to core 1.
@@
 This is more pronounced for the fast flux, where even in core 1 it is not described correctly.
-
+%
 \begin{figure}[htbp!]
@@
 Deviations of the thermal flux calculated by diffusion increase from $\sim$4\% to $\sim$10\% as the heterogeneity of the core increases.
-The deviations of the fast and thermal flux calculated by Ronen method are much smaller (practically negligible), and are smaller than $\sim$2\%.
+The deviations of the fast and thermal flux calculated by Ronen method are much smaller, with practically negligible values in the fuel and less than $\sim$2\% in the water.
 
@@
 	\includegraphics[width=0.75\linewidth]{RM_dD_100it_8_22_728_C123.pdf}
-	\caption{Behavior of the Ronen method correction factor $dD$ along the core, for the fast and thermal fluxes.
+	\caption{Behavior of the Ronen method correction factor $\delta D$ along the core, for the fast and thermal fluxes.
 Vertical grid lines are located at assemblies interfaces, results are for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.}
@@
 This yielded an iterative scheme leading to new flux distributions solved by a diffusion solver but with additional (spatially) corrected diffusion terms, driving the diffusion solution to that of the integral transport equation.
-The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning.
+%However, the direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning.
 The solution of the diffusion equation, on the other hand, offers many numerical advantages, e.g., speed and robustness.
 
-The relation in Eq.~\eqref{eq:RM-it-1D-slab} becomes problematic where the gradient of the flux is small, which is usually the zone where diffusion works better.
+Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
+The (more accurate) surface current $J_{tr}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_D$, plus a correction $\delta J$.
+Hence, when the current vanishes, the correction $\delta J$ vanishes.
+Moreover, the correction is written as in Eq.
+(21), avoiding the potential divergence resulting from division by zero.
+This comment was added to the text.
+
+The basic relation proposed by Ronen, i.e., Eq.~\eqref{eq:RM-it-1D-slab}, becomes problematic where the gradient of the flux is small, which is usually the region where diffusion works generally perform well.
 Ronen did not elaborate on this issue in his technical note from 2004.
@@
 Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
-The (more accurate) surface current $\jtrr$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $\jd$, plus a correction $\delj$.
+The (more accurate) surface current $\jtrr$, calculated by the integral expression, are written as the sum of the surface current calculated by diffusion, $\jd$, plus a correction $\delj$.
 Hence, when the current vanishes, the correction $\delj$ vanishes as well.

### 2019-12-12 FD1dMGdiff/tests/heterSlab2GIlas2003.py
Minor fixes to save k and flx convergence epsilon

@@ -132,10 +132,9 @@ Heter2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
 if __name__ == "__main__":
 
     import logging as lg
-    #lg.info("*** Solve the M&C 2011 problem ***")
     lg.info("*** Solve the Ilas 2003 problem ***")
     from FDsDiff1D import run_calc_with_RM_its, solver_options
 
-    slvr_opts = solver_options(ritmax=10)
-    # filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
-    flx, k = run_calc_with_RM_its(Heter2GSlab_data, slvr_opts, filename=None)
+    slvr_opts = solver_options(ritmax=400)
+    filename = "../output/kflx_LBC%dRBC%d_I%d_400" % (LBC, RBC, I)
+    flx, k = run_calc_with_RM_its(Heter2GSlab_data, slvr_opts, filename)

### 2019-12-12 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -42,6 +42,6 @@ if __name__ == "__main__":
     lg.info("*** Solve the M&C 2011 problem ***")
     from FDsDiff1D import run_calc_with_RM_its, solver_options
 
-    slvr_opts = solver_options(ritmax=2)
-    filename = "../output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
+    slvr_opts = solver_options(ritmax=1001)
+    filename = "../output/kflx_LBC%dRBC%d_I%d_it1001" % (LBC, RBC, I)
     flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename)

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
Updated figures of convergence
Modified plots
Changed caption
Fixed caption from 200 iterations -> 1000 iterations

@@
 	\centering
-	\includegraphics[width=0.65\linewidth]{epsilon.pdf}	
+	\includegraphics[width=0.65\linewidth]{epsilon1000.pdf}	
 	%\includegraphics[width=0.4\linewidth]{convergence.pdf}
 	\caption{Convergence of the flux (max deviation) and of the criticality
-		eigenvalue during 200 Ronen iterations.}
+		eigenvalue during 1000 Ronen iterations.}
 	\label{fig:conv}
@@
 	\centering
-	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_1_sn.pdf}
-	\includegraphics[width=0.48\linewidth]{flux_deviation_half_it_2_sn.pdf}
+	\includegraphics[width=0.65\linewidth]{RM_Sn_converg_FAST.pdf}
+	\includegraphics[width=0.65\linewidth]{RM_Sn_converg_THERMAL.pdf}
 	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_{16}$ solution for the left half slab.}

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
Daniele-s check of conclusion, results and response 2 reviewer.

@@
 	\and
-	CEA, DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),
+	CEA, DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
 	Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France}
@@
 
-The Ronen algorithm is described as follows (see Fig.~\ref{fig:RM-algo}):
+The Ronen algorithm used to solve the critical eigenvalue problem in the slab is described as follows (see Fig.~\ref{fig:RM-algo}):
 \begin{enumerate}
-	\item\label{it:init} Initialize - the algorithm receives the geometry and the cross sections (XS) of the problem as input.
-At this stage, the correction factors $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator $\mathcal{A}_0$ is constructed.
-Initial guesses for the flux $\phi^{(0)}$ and multiplication factor $\keff^{(0)}$ are set.
-	\item\label{it:Js} Calculate currents - using the flux $\phi^{(k)}$ obtained from the diffusion solver, both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated.
-	\item\label{it:dD} Calculate correction factors - the correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ}.
-	\item\label{it:dA} Update the diffusion operator - reconstruct the diffusion operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}).
-	\item\label{it:DF-solve} Diffusion solver - a one-dimensional multigroup diffusion solver is executed until convergence.
-The results are an updated estimation of the flux $\phi^{(k+1)}$ and the multiplication factor $\keff^{(k+1)}$.
-	\item\label{it:cvg} Check convergence - check if the flux $\phi^{(k)}$ and the multiplication factor $\keff^{(k)}$ converged. If yes, stop, otherwise, step~\ref{it:Js}.
+	\item{\sl Initialize}\label{it:init} The algorithm receives the geometry and the cross sections (XS) of the problem as input data.
+At this stage, the correction factors $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator is constructed, that is $\mathcal{A}^{(0)} = \mathcal{A}_0$.
+Initial guesses for the flux $\phi^{(0)}$ and the multiplication factor $k_\textrm{eff}^{(0)}$ are set.
+	\item{\sl Diffusion solver}\label{it:DF-solve} A one-dimensional multigroup diffusion solver is executed with the migration operator $\mathcal{A}^{(k)} = \mathcal{A}_0 + \delta A^{(k)}$ to determine new estimates of the flux $\phi^{(k)}$ and of the multiplication factor $k_\textrm{eff}^{(k)}$.
+	\item{\sl Convergence check}\label{it:cvg} Convergence is checked with the relative residuals on the flux and on the multiplication factor between iteration $k$ and $(k-1)$; Ronen iterations are stopped if the relative residuals fall within the input tolerances.
+	\item{\sl Estimate currents}\label{it:Js} Both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated using $\phi^{(k)}$ and $k_\textrm{eff}^{(k)}$.
+	\item{\sl Update correction}\label{it:dD} The correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ} in order to update the migration operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}), and continue with step~\ref{it:DF-solve}.
 \end{enumerate}
 
-\begin{figure}[htbp!] 
+\begin{figure}[htbp] 
 	\centering
@@
 	\node [cloud] 					 			(start) {START};
-	\node [block, below of=start, xshift=0cm,yshift=2.2cm]  (geoXS) {Geometry, XS};
-	\node [block, below of=geoXS, xshift=0cm,yshift=1.8cm]  (J)     {Calculate $\jtrr^{(k)},\jd^{(k)},\delj^{(k)}$};
-	\node [block, below of=J,     xshift=0cm,yshift=2.0cm]  (dDA)   {Obtain $\delta D^{(k+1)}$ $\delta \mathcal{A}^{(k+1)}$};
-	\node [block, below of=dDA,  xshift=0cm,yshift=2.0cm]  	(Anew)  {Construct\\$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};
-	\node [block, below of=Anew, xshift=0cm,yshift=1.8cm]  	(Diff)  {Diffusion\\solver};
-	\node [decision, below of=Diff,xshift=0cm,yshift=-.5cm]	(cvg)   {$\phi^{(k+1)}$ $k_\textrm{eff}^{(k+1)}$ \\ converged?};
-	\node [cloud, below of=cvg,xshift=0cm,yshift=1.8cm] 	(stp)  {STOP};
+	\node [block, right of=start, xshift=0cm,yshift=0cm] (input) {Input\\parameters};
+	\node [block, right of=input, xshift=0cm,yshift=0cm] (geoXS) {Geometry and XS};
+	\node [block, below of=geoXS, xshift=0cm,yshift=1.5cm] (Diff)  {Diffusion\\solver};
+	\node [block, below of=Diff, xshift=0cm,yshift=1.5cm, diamond, aspect=2.5] (Chk)  {Converged?};
+	\node [block, below of=Chk, xshift=0cm,yshift=1.5cm] (J)  {Calculate $J^{(k)}_{\texttt{tr}},J^{(k)}_D,\delta J^{(k)}$};
+	\node [block, left  of=J,    xshift=0cm,yshift=0cm] (dD) {Obtain\\$\delta D^{(k+1)}$};
+	\node [cloud, left  of=Chk,  xshift=0cm,yshift=0cm] (end) {END};
+	\node [block, left  of=dD,   xshift=0cm,yshift=0cm](dA) {Calculate\\$\delta \mathcal{A}^{(k+1)}$};
+	\node [block, below of=start, xshift=0cm,yshift=1.5cm] (Anew) {$\mathcal{A}^{(k+1)}=$\\[1mm]$\mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$};
 
 % Draw edges
-	\path [line] (start) -- (geoXS);
-	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(0)}$, $k_\textrm{eff}^{(0)}$, $\mathcal{A}_0$}(J);
-	\path [line] (J) 	 -- (dDA);
-	\path [line] (dDA) 	 -- (Anew);
-	\path [line] (Anew)  -- node[near end,anchor= south west,xshift=0cm]{$\mathcal{A}^{(k+1)}$}(Diff);
-	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k+1)},k_\textrm{eff}^{(k+1)}$}(cvg);
-	\path [line] (cvg)   -- node[anchor= south west,yshift=-0.1cm]{YES}(stp);
-	\path [line] (cvg)   -| node[near start,yshift=0.2cm]{NO}(-3,-3.0) -- node[near end]{}(J);
+	\path [line] (start) -- (input);
+	\path [line] (input) -- (geoXS);
+	\path [line] (geoXS) -- node[anchor= south west,yshift=-0.2cm]{$\mathcal{A}_0$}(Diff);
+	\path [line] (Diff)  -- node[anchor= south west,yshift=-0.2cm]{$\phi^{(k)},k^{(k)}$}(Chk);
+	\path [line] (Chk)  -- node[anchor= south west]{NO}(J);
+	\path [line] (Chk)  -- node[anchor= south west]{YES}(end);
+	\path [line] (J)  -- node[anchor= north]{}(dD);
+	\path [line] (dD) -- node[anchor= north]{}(dA);
+	\path [line] (dA)  -- node[anchor= north]{}(Anew);
+	\path [line] (Anew)  -- node[near end,anchor= south west,xshift=-1.7cm]{$k \leftarrow (k+1)$}(Diff);
 
@@
 Two one-dimensional test cases are considered, homogeneous and heterogeneous.
-The reference solutions are calculated using a Python3 discrete ordinates $S_N$ code with $N=16$~\cite{Lewis-1984}.
+The reference solutions are calculated using a Python3 discrete ordinates S$_N$ code with $N=16$~\cite{Lewis-1984}.
 The diffusion solutions and the Ronen iterations are produced using original codes in Python3.
@@
 The reactivity difference is given by $(\Delta\rho = 1/\kref - 1/k_\textrm{D/RM})\times 10^5$ pcm, where $\kd$ and $\krm$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
-The reference $\kref$ value from S16 is 0.744417 ($I = 400$).
+The reference $\kref$ value from S$_{16}$ is 0.744417 ($I = 400$).
 
@@
 
-A comparison of the fast and thermal fluxes, as calculated by the reference $S_N$ code, the RM code, and the standard multigroup diffusion without RM correction (denoted by $D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
-The deviations (in [\%]) of the RM-corrected flux and of the standard diffusion flux from the reference $S_N$ flux are also shown in Fig.~\ref{fig:slab-fluxes-dev}.
+A comparison of the fast and thermal fluxes, as calculated by the reference S$_N$ code, the RM code, and the standard multigroup diffusion without RM correction (denoted by $D_0$), is shown in Fig.~\ref{fig:slab-fluxes} for the half slab.
+The deviations (in [\%]) of the RM-corrected flux and of the standard diffusion flux from the reference S$_N$ flux are also shown in Fig.~\ref{fig:slab-fluxes-dev}.
 The corresponding Ronen method correction factors $\delta D$ are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
@@
 	\includegraphics[width=0.7\linewidth]{Sn_Diff_Rm_flux_Tomatis2011.pdf}
-	\caption{Comparison of the fluxes as calculated by the reference $S_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
+	\caption{Comparison of the fluxes as calculated by the reference S$_N$ code, the RM code, and a standard multigroup diffusion without RM correction ($D_0$).
 The insets show a zoom-in of the fluxes near the boundary.
@@
 	%\includegraphics[width=0.4\linewidth]{convergence.pdf}
-	\caption{Convergence of the flux (max deviation) and of the criticality
-		eigenvalue during 1000 Ronen iterations.}
+	\caption{Convergence of the flux (max deviation) and of the criticality eigenvalue during 1000 Ronen iterations.}
 	\label{fig:conv}
@@
 The RM correction terms ($\delta D$) along the slab are shown in Fig.~\ref{fig:slab-RM-corr-factor}.
-It is clear that the diffusion correction assumes near-zero values at the slab center and exhibits non-trivial behavior near the boundary.
+It is possible to observe that the diffusion correction almost vanishes at the slab center and exhibits non-trivial behavior near the boundary.
 The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}, where $\epsilon_\phi = \operatorname{max} [\phi^{(k)}-\phi^{(k-1)})/\phi^{(k-1)}]$ and $\epsilon_k = (k_\textrm{eff}^{(k)}-k_\textrm{eff}^{(k-1)})/k_\textrm{eff}^{(k-1)}$.
-The flux exhibits relatively slow convergence with respect to the convergence rate of the eigenvalue.
-The largest differences between the flux and the reference $S_{16}$ solution appear near the boundaries.
+While the eigenvalue converges within a few iterations, relatively slow convergence is noticed for the flux with higher differences against the reference S$_{16}$ solution near the boundaries.
 The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta \phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
@@
 	\includegraphics[width=0.65\linewidth]{RM_Sn_converg_THERMAL.pdf}
-	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference $S_{16}$ solution for the left half slab.}
+	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference S$_{16}$ solution for the left half slab.}
 	\label{fig:conv3}
@@
 Table~\ref{tab:dx_drho2} shows the reactivity differences between standard diffusion (with extrapolated length) and the Ronen method (at increasing number of iterations) with respect to the reference solution for each of the three core configurations.
-The standard diffusion solution perform rather well for core 1 with deviation of 182 pcm, but fails for cores 2 and 3 with deviations of 773 and 3335 pcm, respectively.
-This is explained by the fact that cores 2 and 3 are more heterogeneous with respect to core 1.
+The standard diffusion solution perform rather well for core 1 with deviation of 182 pcm, but fails for cores 2 and 3 with deviation of 773 and 3335 pcm, respectively.
+This is explained by the fact that cores 2 and 3 are more heterogeneous compared to core 1.
 The Ronen method performs better than standard diffusion for all three cores, even after merely 10 iterations.
-Additional Ronen iterations further improve the estimated multiplication factor until convergence.
-
-\begin{table}[!htbp]
+Additional Ronen iterations further improve the estimated multiplication factor until convergence within the prescribed tolerance.
+
+\begin{table}[htbp]
 	\centering
@@
 		{}				& $\keff$& $\Delta\rho$ [pcm]& $\keff$	&$\Delta\rho$ [pcm]& $\keff$ &$\Delta\rho$ [pcm] \\
-		$S_{16}$		&1.25614	&-			 &1.00094   &-				  &0.79878		&-		\\
+		S$_{16}$		&1.25614	&-			 &1.00094   &-				  &0.79878		&-		\\
 		Diffusion		&1.25902	&182		 &0.99325	&-773			  &0.77805		&-3335	\\
@@
 
-The two-group flux distribution across each core is shown in Fig.~\ref{fig:hetero-flux} for standard diffusion ($D_0$), Ronen method (RM) and the S16 reference solution.
+The two-group flux distribution across each core is shown in Fig.~\ref{fig:hetero-flux} for standard diffusion ($D_0$), Ronen method (RM) and the S$_{16}$ reference solution.
 RM results are shown for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.
@@
 	\includegraphics[width=0.49\linewidth]{Sn_Diff_RM_core_3.pdf}
-	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S16 reference solution.
+	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S$_{16}$ reference solution.
 Vertical grid lines are located at assemblies interfaces.
@@
 
-The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions are shown for each core, in Fig.~\ref{fig:hetero-flux-dev}.
+The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S$_{16}$ reference solutions are shown for each core in Fig.~\ref{fig:hetero-flux-dev}.
 The fast flux is poorly reproduced by standard diffusion, with up to $\sim$10\% deviations at the inner interfaces and $\sim$20\% at the outer boundaries (in agreement with the homogeneous case).
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htbp]
 	\centering
 	\includegraphics[width=0.75\linewidth]{flx_err_diff_C123.pdf}
-	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S16 reference solutions for each core.
+	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S$_{16}$ reference solutions for each core.
 Vertical grid lines are located at assemblies interfaces.
@@
 
-\begin{figure}[htbp!]
+\begin{figure}[htbp]
 	\centering
@@
 
-Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
-The (more accurate) surface current $J_{tr}$, calculated by integral expression, is written as the sum of the surface current calculated by diffusion, $J_D$, plus a correction $\delta J$.
-Hence, when the current vanishes, the correction $\delta J$ vanishes.
-Moreover, the correction is written as in Eq.
-(21), avoiding the potential divergence resulting from division by zero.
-This comment was added to the text.
-
-The basic relation proposed by Ronen, i.e., Eq.~\eqref{eq:RM-it-1D-slab}, becomes problematic where the gradient of the flux is small, which is usually the region where diffusion works generally perform well.
+The basic relation proposed by Ronen, i.e., Eq.~\eqref{eq:RM-it-1D-slab}, becomes problematic in the regions where the gradient of the flux is small, that is usually where diffusion performs well.
 Ronen did not elaborate on this issue in his technical note from 2004.
-Theoretically, both the numerator and the denominator should vanish at the same location, since both are accurate expressions for the neutron current where the flux gradient is weak.
-We hypothesize that this ratio, between two expressions which tend to zero at the same location, approaches some constant value since there exist a diffusion coefficient at that location.
-
-Numerically, Tomatis and Dall'Osso 2011 chose to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
-The (more accurate) surface current $\jtrr$, calculated by the integral expression, are written as the sum of the surface current calculated by diffusion, $\jd$, plus a correction $\delj$.
+Theoretically, both the numerator and the denominator should vanish at the same location since both are accurate expressions for the neutron current with weak flux gradients.
+We assume that this ratio, considered as a ratio between two quantities which tend to zero at the same location, approaches some constant value since there exist a diffusion coefficient at that location.
+However, any value would be possible in Fick's law because of the vanishing flux grandient.
+
+Numerically, Tomatis and Dall'Osso chose in 2011 to deal with this potential singularity by using the well-known drift terms, which serve as a \emph{numerical feature}.
+The (more accurate) surface current $\jtrr$, calculated by the integral expression, is written as the sum of the surface current calculated by diffusion, $\jd$, plus a correction $\delj$.
 Hence, when the current vanishes, the correction $\delj$ vanishes as well.

### 2019-12-12 docs/EPJP2019/response/response.tex
Final version (except minor changes)

@@
 \\ \\
-\revised{T}
+\revised{Indeed, the Ronen method is highly suited for non-homogeneous systems.
+An entire benchmark was added to the results section.
+The chosen benchmark is a one-dimensional highly heterogeneous core representing a BWR core.
+As nicely pointed out by the reviewer, the new figures 11-13 in the revised manuscript demonstrate the natural capability of the Ronen method to deal with material interfaces and strong flux gradients.}
 \\ \\

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
Final version (except minor changes)

@@
 The reactivity difference is given by $(\Delta\rho = 1/\kref - 1/k_\textrm{D/RM})\times 10^5$ pcm, where $\kd$ and $\krm$ are the multiplication factors of standard diffusion and of the Ronen method, respectively.
-The reference $\kref$ value from S$_{16}$ is 0.744417 ($I = 400$).
+The reference $\kref$ value from S\tsub{16} is 0.744417 ($I = 400$).
 
@@
 The convergence of the flux (max deviation) and of the criticality eigenvalue are shown in Fig.~\ref{fig:conv}, where $\epsilon_\phi = \operatorname{max} [\phi^{(k)}-\phi^{(k-1)})/\phi^{(k-1)}]$ and $\epsilon_k = (k_\textrm{eff}^{(k)}-k_\textrm{eff}^{(k-1)})/k_\textrm{eff}^{(k-1)}$.
-While the eigenvalue converges within a few iterations, relatively slow convergence is noticed for the flux with higher differences against the reference S$_{16}$ solution near the boundaries.
+While the eigenvalue converges within a few iterations, relatively slow convergence is noticed for the flux with higher differences against the reference S\tsub{16} solution near the boundaries.
 The spatial flux convergence between two successive Ronen iterations is shown in Fig.~\ref{fig:conv2} for the left half slab, according to $\Delta \phi = (\phi^{k-1}-\phi^k)/\phi^{k-1}$ [\%].
@@
 	\includegraphics[width=0.65\linewidth]{RM_Sn_converg_THERMAL.pdf}
-	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference S$_{16}$ solution for the left half slab.}
+	\caption{The spatial flux convergence of the Ronen iterations with respect to the reference S\tsub{16} solution for the left half slab.}
 	\label{fig:conv3}
@@
 		{}				& $\keff$& $\Delta\rho$ [pcm]& $\keff$	&$\Delta\rho$ [pcm]& $\keff$ &$\Delta\rho$ [pcm] \\
-		S$_{16}$		&1.25614	&-			 &1.00094   &-				  &0.79878		&-		\\
+		S\tsub{16}		&1.25614	&-			 &1.00094   &-				  &0.79878		&-		\\
 		Diffusion		&1.25902	&182		 &0.99325	&-773			  &0.77805		&-3335	\\
@@
 
-The two-group flux distribution across each core is shown in Fig.~\ref{fig:hetero-flux} for standard diffusion ($D_0$), Ronen method (RM) and the S$_{16}$ reference solution.
+The two-group flux distribution across each core is shown in Fig.~\ref{fig:hetero-flux} for standard diffusion ($D_0$), Ronen method (RM) and the S\tsub{16} reference solution.
 RM results are shown for 100 iterations and the spatial mesh spans 8 nodes in the water and 22 nodes in each fuel element.
@@
 	\includegraphics[width=0.49\linewidth]{Sn_Diff_RM_core_3.pdf}
-	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S$_{16}$ reference solution.
+	\caption{Fast and thermal flux for each core using standard diffusion ($D_0$), Ronen method (RM) and S\tsub{16} reference solution.
 Vertical grid lines are located at assemblies interfaces.
@@
 
-The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S$_{16}$ reference solutions are shown for each core in Fig.~\ref{fig:hetero-flux-dev}.
+The fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S\tsub{16} reference solutions are shown for each core, in Fig.~\ref{fig:hetero-flux-dev}.
 The fast flux is poorly reproduced by standard diffusion, with up to $\sim$10\% deviations at the inner interfaces and $\sim$20\% at the outer boundaries (in agreement with the homogeneous case).
@@
 	\includegraphics[width=0.75\linewidth]{flx_err_diff_C123.pdf}
-	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S$_{16}$ reference solutions for each core.
+	\caption{Fast and thermal flux deviation of standard diffusion ($D_0$) and Ronen method (RM) with respect to S\tsub{16} reference solutions for each core.
 Vertical grid lines are located at assemblies interfaces.
@@
 More accurate results are obtained for the two-group benchmark problem reported in \cite{Tomatis-2011} and new results are reported for a heterogeneous benchmark.
+The performances of the Ronen method, especially for the heterogeneous benchmark (as shown in Figs.~\ref{fig:hetero-flux}--\ref{fig:Dcoef}), strongly indicate that it is inherently suitable to deal with non-homogeneous systems and can naturally adapt to interfaces, where strong gradients of the flux might appear.
+
 In general, slow convergence is observed for the scalar flux with the larger discrepancies, comparing to the reference, located on the vacuum boundary and on the material interfaces.

### 2019-12-12 docs/EPJP2019/old_version.tex
Revert "Revert "Merge branch 'EPJP_revision' of https://github.com/ndarmage/RonenMethod1D into EPJP_revision""
This reverts commit add7e6efbc6edd5e9f9d66dc432bbd44b9883bad.

@@
 \end{equation}
-%\begin{equation}\label{eq:src-mmnts}
-%\sigma_l(x,E\leftarrow E')dE' = 
-%\sigma_{s,l}(x,E\leftarrow E')dE'
-%+ \delta_{l0}\frac{\chi(E)}{\keff}\nu\sigma_f(x,E')dE' \,\, 
-%\end{equation}
-%and the source term is expanded 
-%\begin{eqnarray}\label{eq:src}
-%Q(x,E,\mu)&=& \sum\limits_{l=0}^\infty {
-%	\frac{2l+1}{2} \int_0^\infty { dE'
-%		\sigma_{s,l}(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
-%	}
-%} 
-%+ \frac{\chi(E)}{2\keff} \int_0^\infty { dE'
-%	\nu\sigma_f(x,E') \psi_0(x,E')
-%}  \nonumber \\
-%&=&\sum\limits_{l=0}^\infty {
-%	\frac{2l+1}{2} \int_0^\infty { dE'
-%		\sigma_l(x,E\leftarrow E')\psi_l(x,E')\pl{\mu} 			
-%	}
-%} \nonumber \\
-%&=&\sum\limits_{l=0}^\infty {
-%\frac{2l+1}{2} \int_0^\infty { dE'
-%	q_l(x,E\leftarrow E')\pl{\mu} 			
-%	}
-%} \nonumber \\
-%&=&\sum\limits_{l=0}^\infty {
-%	\frac{2l+1}{2} q_l(x,E)\pl{\mu} 			
-%} 
-%\,\, ,
-%\end{eqnarray}
 where the source angular moments are defined as
@@
 In order to calculate the scalar flux $\phi^+$ at $x$ resulting from neutrons coming from the left, i.e., $x'<x$ ($\mu>0$), substitute Eqs.~\eqref{eq:Q-series} in Eq.~\eqref{eq:int-ang-flx-a} and integrate over the angle
-\begin{eqnarray}\label{eq:phi+}
-\phi^+(x,E)&\equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \nonumber \\
+\begin{equation}\label{eq:phi+}
+\begin{split}
+\phi^+(x,E) \equiv& \int_0^1 {d\mu \psi(x,E,\mu)} \\
 %&=& \int_0^1 {d\mu \psi(0,\mu) e^{-\mcL(0,x)/\mu} } 

### 2019-12-12 docs/EPJP2019/Gross-EPJP-2019.tex
latest modification and production of marked copy

@@
 \begin{enumerate}
-	\item{\sl Initialize}\label{it:init} The algorithm receives the geometry and the cross sections (XS) of the problem as input data.
+	\item{\sl Initialize}\label{it:init} - The algorithm receives the geometry and the cross sections (XS) of the problem as input data.
 At this stage, the correction factors $\delta D^{(0)}$ are set to zero and the initial pure-diffusion operator is constructed, that is $\mathcal{A}^{(0)} = \mathcal{A}_0$.
 Initial guesses for the flux $\phi^{(0)}$ and the multiplication factor $k_\textrm{eff}^{(0)}$ are set.
-	\item{\sl Diffusion solver}\label{it:DF-solve} A one-dimensional multigroup diffusion solver is executed with the migration operator $\mathcal{A}^{(k)} = \mathcal{A}_0 + \delta A^{(k)}$ to determine new estimates of the flux $\phi^{(k)}$ and of the multiplication factor $k_\textrm{eff}^{(k)}$.
-	\item{\sl Convergence check}\label{it:cvg} Convergence is checked with the relative residuals on the flux and on the multiplication factor between iteration $k$ and $(k-1)$; Ronen iterations are stopped if the relative residuals fall within the input tolerances.
-	\item{\sl Estimate currents}\label{it:Js} Both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated using $\phi^{(k)}$ and $k_\textrm{eff}^{(k)}$.
-	\item{\sl Update correction}\label{it:dD} The correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ} in order to update the migration operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}), and continue with step~\ref{it:DF-solve}.
+	\item{\sl Diffusion solver}\label{it:DF-solve} - A one-dimensional multigroup diffusion solver is executed with the migration operator $\mathcal{A}^{(k)} = \mathcal{A}_0 + \delta A^{(k)}$ to determine new estimates of the flux $\phi^{(k)}$ and of the multiplication factor $k_\textrm{eff}^{(k)}$.
+	\item{\sl Convergence check}\label{it:cvg} - Convergence is checked with the relative residuals on the flux and on the multiplication factor between iteration $k$ and $(k-1)$; Ronen iterations are stopped if the relative residuals fall within the input tolerances.
+	\item{\sl Estimate currents}\label{it:Js} - Both the diffusion current $\jd^{(k)}$ (Eq.~\ref{eq:JD}) and the transport current $\jtrr^{(k)}$ (Eq.~\ref{eq:tot-J}) are calculated using $\phi^{(k)}$ and $k_\textrm{eff}^{(k)}$.
+	\item{\sl Update correction}\label{it:dD} - The correction factors $\delta D^{(k+1)}$ are obtained using $\delj^{(k)}$ and Eq.~\eqref{eq:dJ} in order to update the migration operator $\mathcal{A}^{(k+1)} = \mathcal{A}_0+\delta \mathcal{A}^{(k+1)}$ (Eq.~\ref{eq:FD_diff_org}), and continue with step~\ref{it:DF-solve}.
 \end{enumerate}

### 2020-01-05 docs/PHYSOR2020/ANE-RM-2020.tex
ANE template - pCMFD
Copied the text from PHYSOR's tex file to a new tex file, ANE template.

--- 2019-11-14 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  This is a sample LaTeX input file for your contribution to
-%  the PHYSOR2020 topical meeting.
-%
-%  Please use it as a template for your full paper
-%    Accompanying/related file(s) include:
-%       1. Document class/format file: physor2020.cls
-%       2. Sample Postscript Figure:   figure.pdf
-%       3. A PDF file showing the desired appearance: physor2020_template.pdf
-%       4. cites.sty and citesort.sty that might be needed by some users
-%    Direct questions about these files to: rcarlos.lope@gmail.com
-%											armando.gomez@inin.gob.mx
-%
-%    Notes:
-%      (1) You can use the "dvips" utility to convert .dvi
-%          files to PostScript.  Then, use either Acrobat
-%          Distiller or "ps2pdf" to convert to PDF format.
-%      (2) Different versions of LaTeX have been observed to
-%          shift the page down, causing improper margins.
-%          If this occurs, adjust the "topmargin" value in the
-%          physor2020.cls file to achieve the proper margins.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[letterpaper]{physor2020}
+\documentclass[review,3p,onecolumn,sort&compress]{elsarticle}
 %
 %  various packages that you may wish to activate for usage 
-\usepackage{tabls}
-\usepackage{cites}
-\usepackage{epsf}
-\usepackage{appendix}
-\usepackage{ragged2e}
-\usepackage[top=1in, bottom=1.in, left=1.in, right=1.in]{geometry}
-\usepackage{enumitem}
-\setlist[itemize]{leftmargin=*}
-\usepackage{caption}
-\captionsetup{width=1.0\textwidth,font={bf,normalsize},%
-              skip=0.3cm,within=none,justification=centering}
+\usepackage{booktabs}
+\usepackage{natbib}
+%\usepackage{cite}
+%\usepackage{epsf}
 \usepackage{bm}
-\usepackage{tikz}
+\usepackage[english]{babel}
+\usepackage[autostyle, english = american]{csquotes}
+\MakeOuterQuote{"}
+\usepackage{color}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{calrsfs}
+\usepackage{lineno}
+\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
+linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
 \usepackage{xfrac}
 \usepackage{units}
+\usepackage{tikz}
 
-% Daniele: I commented this part because it was not present in the original
-% conference template.
-% % for quotes
-% \usepackage[english]{babel}
-% \usepackage[autostyle, english = american]{csquotes}
-% \MakeOuterQuote{"}
-%
+\usepackage[printonlyused]{acronym}
+
+\modulolinenumbers[1]
+
+\journal{Annals of Nuclear Energy}
+
 \newcommand{\eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\eqnolabel}[1]{(\ref{#1})}
 \newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
-\newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
-\newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
-\newcommand{\tbl}[1]{Table~\ref{#1}}
-\newcommand{\tblnolabel}[1]{\ref{#1}}
-\newcommand{\tbls}[1]{Tables~\ref{#1}}
-\newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
-\newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
-\newcommand{\fig}[1]{Fig.~\ref{#1}}
-\newcommand{\fignolabel}[1]{\ref{#1}}
-\newcommand{\figs}[1]{Figs.~\ref{#1}}
-\newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
-\newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
-\newcommand{\sxn}[1]{Section~\ref{#1}}
-%
-% \newcommand{\revised}[1]{{\color{red}{#1}}}
-% \newcommand{\tsup}[1]{\textsuperscript{#1}}
-% \newcommand{\tsub}[1]{\textsubscript{#1}}
-%
-\newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
-\newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
-\newcommand{\rr}{\ensuremath{\bm{r}}}
-\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
-\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
-\newcommand{\rE}{\ensuremath{(\rr,E)}}
-
-\newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
-\newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
-\newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
-%\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcL}{\tau}
-\newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
-\newcommand{\dx}{\ensuremath{\Delta x}}
-
+\newcommand{\tsup}[1]{\textsuperscript{#1}}
+\newcommand{\tsub}[1]{\textsuberscript{#1}}
+\newcommand{\keff}{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}
+\newcommand{\kinf}{\ensuremath{k_{\textrm{\scriptsize{$\infty$}}}}}
+\newcommand{\pf}{\textrm{PPF}}
+\newcommand{\eg}{e.g.,}
+\newcommand{\ie}{i.e.,}
+\newcommand{\OO}{\hat{\bm{\Omega}}}
+\newcommand{\rr}{\bm{r}}
 \newcommand{\jp}{\ensuremath{J^+}}
@@
 \newcommand{\bmj}{\ensuremath{\bm{J}}}
-% \newcommand{\jp}{\ensuremath{\bm{J}^+}}
-% \newcommand{\jm}{\ensuremath{\bm{J}^-}}
-% \newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
-% \newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}
-
+\newcommand{\rE}{\ensuremath{(\rr,E)}}
+\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
 \newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
-
+\newcommand{\mcL}{\tau}
 % about notes and comments from each author
@@
 \newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
+\newcommand{\revised}[1]{{\color{red}{#1}}}
 
-%\usepackage[justification=centering]{caption}
+%\newcommand{\authorHead}      % Author's names here
+%           {Israeli, Ravetto \& Gilad}  
+%\newcommand{\shortTitle}      % Short title here
+%           {Adjoint Problem as Physical Heuristic for Loading Pattern Optimization}
 
-%
-% Define title...
-%
-% \title{INTEGRAL TRANSPORT CORRECTION \\TO DIFFUSION CALCULATIONS BY pCMFD}
-\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\
-       USING THE pCMFD SCHEME}
-%
-% ...and authors
-%
-\author{%
-  % FIRST AUTHORS
-  %
-  \textbf{Roy Gross$^1$,
-          Daniele Tomatis$^2$\footnote{Corresponding author.}
-          ~and Erez Gilad$^1$} \\
-  $^1$The Unit of Nuclear Engineering, \\
-  Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel \\
-\\
-  $^2$CEA, DEN, Service d’\'etudes des r\'eacteurs et
-      de math\'ematiques appliqu\'ees (SERMA), \\
-    Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France \\
-\\
-  \url{roygros@post.bgu.ac.il},
-  \url{daniele.tomatis@cea.fr},
-  \url{gilade@bgu.ac.il}
-}
-%
-% Insert authors' names and short version of title in lines below
-%
-\newcommand{\authorHead}      % Author's names here use et al. if more than 3
-           {R. Gross, D. Tomatis, E. Gilad}
-\newcommand{\shortTitle}      % Short title here (Shorten to fit all into a single line)
-%           {INTEGRAL TRANSPORT CORRECTION TO 1-D DIFFUSION CALCULATIONS by pCMFD}
-           {The Ronen Method by pCMFD}  % Daniele's suggestion (shorter)
+\newcommand\mscriptsize[1]{\mbox{\scriptsize\ensuremath{#1}}}
+\newcommand\mtiny[1]{\mbox{\tiny\ensuremath{#1}}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{document}
-\maketitle
-\justify
 
-% ------------------------------------------
+	\begin{frontmatter}
+
+		\linenumbers
+
+		\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS USING THE pCMFD SCHEME}
+
+		%% or include affiliations in footnotes:
+		\author[bgu]{R.~Gross}
+		\author[cea]{D.~Tomatis}
+		\author[bgu]{E.~Gilad\corref{cor1}}
+		\ead{gilade@bgu.ac.il}
+
+		\cortext[cor1]{Corresponding author}
+
+		\address[bgu]{The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
+		\address[cea]{CEA, DEN, Service d’\'etudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA), 	
+						Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France}
+
+		%------------------------------------------------------------
 		\begin{abstract}
+		\modulolinenumbers[1]
+		\linenumbers
 		The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
@@
 		\end{abstract}
-\keywords{neutron diffusion, integral transport, non-linear transport correction, CMFD, pCMFD}
-% Daniele suggestion:
-% I would not include pCMFD since it belongs to the CMFD class of methods and shorten the list of keywords
+		%------------------------------------------------------------
+		\begin{keyword}
+		Neutron diffusion \sep Integral transport \sep Non-linear transport correction \sep CMFD \sep pCMFD
+		\end{keyword}
+		%------------------------------------------------------------
+	\end{frontmatter}
 
-% ------------------------------------------
+\linenumbers
+
+\newpage
+
 \section{INTRODUCTION}
@@
 \label{eq:balance}
-  J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
+J_{i+\hzi ,g} - J_{i-\hzi ,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
 \end{equation}
@@
 	\centering
-  \input{figures/mesh1D.tikz}
+	\begin{tikzpicture}
+	\tikzstyle{every node}=[font=\footnotesize]
+	\draw[thick] (0,0) -- (3,0);
+	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
+	\draw[thick] (4,0) -- (7,0);
+	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
+	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};
+
+	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-\hzi$};
+	\node[anchor=south] at (1cm,1pt) {0};
+	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+\hzi$};
+
+	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-\hzi$};
+	\node[anchor=south] at (5.5cm,1pt) {$i$};
+	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+\hzi$};
+
+	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-\sfrac{3}{2}$};
+	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
+	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-\hzi$};
+	\end{tikzpicture}
 	\caption{Notation of the one-dimensional mesh.}

### 2020-01-05 docs/PHYSOR2020/ANE-RM-2020.tex
Update ANE-RM-2020.tex
Adding pCMFD equations.

@@
 linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
+
+% for algorithms
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+
 \usepackage{xfrac}
@@
 \newcommand{\jpm}{\ensuremath{J^\pm}}
+\newcommand{\delj}{\ensuremath{\delta J}}
 \newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
@@
 \newcommand{\mcL}{\tau}
+\newcommand{\dx}{\Delta}
 % about notes and comments from each author
@@
 
-		\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS USING THE pCMFD SCHEME}
+		\title{Integral Transport Correction to Diffusion Calculations \\ Using the pCMFD Scheme}
 
@@
 
-\section{INTRODUCTION}
+\section{Intoduction}
 \label{sec:intro}
@@
 % ------------------------------------------
-\section{COARSE MESH FINITE DIFFERENCES}
+\section{Coarse Mesh Finite Differences}
 \label{sec:CMFD-intro}
@@
 % ------------------------------------------
-\section{THE RONEN METHOD}
+\section{The Ronen Method}
 \label{sec:RM}
@@
 % ------------------------------------------
-\section{NUMERICAL IMPLEMENTATION}
+\section{Numerical Implementation}
 \label{sec:RM-num}
@@
 % ------------------------------------------
-\subsection{CMFD IMPLEMENTATION}
+\subsection{CMFD Implementation}
 \label{sec:RM-CMFD}
@@
 Therefore, this new term acts as a correction for the diffusion current.
-The diffusion current is generally approximated by finite differences according to
+The diffusion current is generally approximated by discretizing Fick's law, and by finite differences, according to
 \begin{equation}
@@
 %
-About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
+About the RM, more accurate estimates of the net current come from the integral expressions of \eq{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
 In linearly anisotropic problems, the net current can also be considered to compute the source.
@@
 % ------------------------------------------
-\subsection{pCMFD IMPLEMENTATION}
+\subsection{pCMFD Implementation}
 \label{sec:RM-pCMFD}
@@
 % -----------------------------------------------------------------------------
+The descretized form of the diffusion equations, with pCMFD implementations, is
+\begin{equation}
+	\label{eq:pCMFD-diff1}
+	\begin{split}
+	J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+ &+ \left( + \delj_{i-\hzi,g}^+ - 
+	\delj_{i-\hzi,g}^- \right) + \sigma_{i,g}\phi_{i,g} = \\
+	&\frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}\,\,.
+	\end{split}
+\end{equation}
+By using \eqs{eq:CCF-sub}, one gets
+\begin{equation}
+	\label{eq:pCMFD-diff2}
+	-2D_{i+\hzi}\frac{\phi_{i+1,g} - \phi{i,g}}{\dx_{i+1}+\dx_{i}} 
+\end{equation}
 
@@
 % ------------------------------------------
-\section{RESULTS}
+\section{Results}
 \label{sec:res}
@@
 % ------------------------------------------
-\section{CONCLUSIONS}
+\section{Conclusions}
 \label{sec:conc}

### 2020-01-06 docs/PHYSOR2020/ANE-RM-2020.tex
Update ANE-RM-2020.tex

@@
 \newcommand{\dx}{\Delta}
+\newcommand{\dd}{\delta D}
+\newcommand{\tild}{\tilde{D}}
 % about notes and comments from each author
@@
 Only the zeroth moment of the angular flux, that is the scalar flux after an expansion in angle on the spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
-\eqs{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
+\eq{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
 This is the main assumption of the Ronen Method.
 \end{subequations}
-% \daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
+% \daniele{In case additional space will be needed, it will be possible to write \eq{eq:par-curr-calc} in a condensed form by using $\pm$.}
 
@@
 
-Two corrective terms are then introduced: $J = \jp - \jm = \jD + \delta J^+ + \delta J^-$.
+Two corrective terms are then introduced: $J = \jp - \jm = \jD + \left(\delta J^+ - \delta J^-\right)$.
 An upwind definition with respect to the direction of flight of neutrons is used for the corrections~\cite{Jarrett-2016,Zhu-2016}:
@@
 \label{eq:CCF-sub}
-\delta \jp _{i+\hzi} = -\delta D^+ _{i+\hzi} \phi_i
+\delta \jp _{i+\hzi} = \delta D^+ _{i+\hzi} \phi_i
 \quad \text{and} \quad
@@
 	\begin{align}
-	J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= -\delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
-	J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
+	J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= \delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
+	J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= \delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
 	\end{align}
@@
 	\label{eq:pCMFD-diff1}
+	J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+ + \left( + \delj_{i-\hzi,g}^+ - 
+	\delj_{i-\hzi,g}^- \right) + \sigma_{i,g}\phi_{i,g} = q_{i,g}\,\,,
+\end{equation}
+where
+\begin{equation}
+	\label{eq:q}
+	q_{i,g} = \frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}\,\,.
+\end{equation}
+By using Eqs.~\eqref{eq:CCF-sub}--\eqref{eq:q}, one gets
+\begin{equation}
+	\label{eq:pCMFD-diff2}
 	\begin{split}
-	J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+ &+ \left( + \delj_{i-\hzi,g}^+ - 
-	\delj_{i-\hzi,g}^- \right) + \sigma_{i,g}\phi_{i,g} = \\
-	&\frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}\,\,.
+	-2D_{i+\hzi}\frac{\phi_{i+1,g} - \phi_{i,g}}{\dx_{i+1}+\dx_{i}} +\left( \dd^+_{i+\hzi,g}\phi_{i,g} \right.&\left. - \dd^-_{i+\hzi,g }\phi_{i+1,g}\right)
+	+2D_{i-\hzi}\frac{\phi_{i,g} - \phi_{i-1,g}}{\dx_{i}+\dx_{i-1}} \\ 
+	&- \left( \dd^+_{i-\hzi,g}\phi_{i-1,g} -\dd^-_{i-\hzi,g}\phi_{i,g}\right) +\sigma_{i,g}\phi_{i,g} = q_{i,g}\,\,.
 	\end{split}
 \end{equation}
-By using \eqs{eq:CCF-sub}, one gets
+Setting $\tild_{i+\hzi,g} = \frac{2D_{i+\hzi,g}}{\dx_{i+1}+\dx_{i}}$, and rearranging the above term, 
 \begin{equation}
-	\label{eq:pCMFD-diff2}
-	-2D_{i+\hzi}\frac{\phi_{i+1,g} - \phi{i,g}}{\dx_{i+1}+\dx_{i}} 
+	\label{eq:pCMFD-rearrange}
+	\begin{split}
+	\left(-\tild_{i-\hzi,g}-\dd^+_{i-\hzi,g}\right)\phi_{i-\hzi,g} + &\left( \tild_{i+\hzi,g} + \dd^+_{i+\hzi,g}+ \tild_{i-\hzi,g} + \sigma_{i,g}\right)\phi_{i,g} \\
+	&+ \left( -\tild_{i+\hzi,g} - \dd^-_{i+\hzi,g}\right)\phi_{i+1,g} = q_{i,g}\,\,.
+	\end{split}
 \end{equation}

### 2020-01-06 FD1dMGdiff/FDsDiff1D.py
Modify the SN code to share common services with the Finite Differences solver after Roy's modifications to support heterogeneous cases.

@@ -105,6 +105,13 @@ class input_data:
     @property
     def G(self):
         return self.xs_media[next(iter(self.xs_media))]['st'].size
+
+    @property
+    def Lss(self):
+        random_ss, L = self.xs_media[next(iter(self.xs_media))]['ss'], 1
+        if random_ss.ndim == 3:
+            L = max([self.xs_media[m]['ss'].shape[-1] for m in self.xs_media])
+        return L - 1
     
     def compute_cell_width(self):
         self.Di = self.xi[1:] - self.xi[:-1]
@@ -809,8 +816,6 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
     # keep track of partial solutions on external files
     flx_save = np.empty([G, I, ritmax + 1])
     k_save = np.full(ritmax + 1, -1.)
-    kerr_save = np.full(ritmax, -1.)
-    ferr_save = np.full(ritmax, -1.)
 
     err, itr, kinit = 1.e+20, 0, k
     Dflxm1 = np.zeros_like(flx)
@@ -853,17 +858,11 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
         Dflxm2 = np.array(Dflxm1, copy=True)
         Dflxm1 = flx - flxold
         ferr = np.where(flx > 0., 1. - flxold / flx, Dflxm1)
-        kerr = (k-kold)/k
-        
+
         err = abs(ferr[np.unravel_index(abs(ferr).argmax(), (G, I))])
-        
-        kerr_save[itr] = kerr
-        ferr_save[itr] = err
-        
         itr += 1
-        
-        lg.info("+RM+ it={:^4d}, k={:<13.6g}, kerr={:<+13.6e}, ferr={:<+13.6e}".format(
-            itr, k, kerr, err
+        lg.info("+RM+ it={:^4d}, k={:<13.6g}, err={:<+13.6e}".format(
+            itr, k, err
         ))
         lg.info("{:^4s}{:^13s}{:^6s}{:^13s}".format(
             "G", "max(err)", "at i", "std(err)"
@@ -883,8 +882,8 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
 
     k_save[itr], flx_save[:, :, itr] = k, flx  # store final values
     lg.info("Initial value of k was %13.6g." % kinit)
-    if filename is not None:        
[…]

### 2020-01-06 FD1dMGdiff/tests/heterSlab2GIlas2003.py

@@ -1,7 +1,7 @@
 #!/usr/bin/env python3
 # --*-- coding:utf-8 --*--
 """
-This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
+This test case runs the 2G heterogeneous slab problem from [Ilas2003]_.
 
 .. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
    transport correction in diffusion calculations", Proc. Int. Conf. on
@@ -135,6 +135,6 @@ if __name__ == "__main__":
     lg.info("*** Solve the Ilas 2003 problem ***")
     from FDsDiff1D import run_calc_with_RM_its, solver_options
 
-    slvr_opts = solver_options(ritmax=400)
-    filename = "../output/kflx_LBC%dRBC%d_I%d_400" % (LBC, RBC, I)
-    flx, k = run_calc_with_RM_its(Heter2GSlab_data, slvr_opts, filename)
+    slvr_opts = solver_options(ritmax=10)
+    # filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
+    flx, k = run_calc_with_RM_its(Heter2GSlab_data, slvr_opts, filename=None)

### 2020-01-06 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -19,7 +19,7 @@ def MyWho():
 
 # definition of the spatial mesh
 L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
-I = 200  # nb of spatial cells
+I = 20  # nb of spatial cells
 xi = np.linspace(0, L, I+1)  # equidistant mesh
 
 geometry_type = 'slab'
@@ -32,7 +32,7 @@ xs_media = {
 media = [['HM', L]]  # i.e. homogeneously filled
 
 # set b.c.
-LBC, RBC = 0, 2
+LBC, RBC = 2, 0
 
 Homog2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
 
@@ -42,6 +42,6 @@ if __name__ == "__main__":
     lg.info("*** Solve the M&C 2011 problem ***")
     from FDsDiff1D import run_calc_with_RM_its, solver_options
 
-    slvr_opts = solver_options(ritmax=1001)
-    filename = "../output/kflx_LBC%dRBC%d_I%d_it1001" % (LBC, RBC, I)
-    flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename)
+    slvr_opts = solver_options(ritmax=10)
+    # filename = "output/kflx_LBC%dRBC%d_I%d" % (LBC, RBC, I)
+    flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename=None)

### 2020-01-06 SNMG1DSlab/data/hetro2GIlas2003.py

@@ -1,87 +1,0 @@
-# --*-- coding:utf-8 --*--
-"""
-Multigroup xs for the homogeneous 2G problem [Tomatis2011]_.
-
-.. note:: remind that the scattering moments are already multiplied by the
-   coefficients of Lagrange polynomials if data are produced by APOLLO.
-
-.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
-   transport correction in diffusion calculations", Proc. Int. Conf. on
-   Mathematics and Computational Methods Applied to Nuclear Science and
-   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
-"""
-
-import numpy as np
-import logging as lg
-
-one_third = 1. / 3.
-
-# Water
-stw = np.array([0.1890, 1.4633])
-ssw = np.zeros((2, 2, 2),)
-ssw_0 = np.array([[0.1507, 0.], [0.0380, 1.4536]])
-ssw_1 = np.array([[0., 0.], [0., 0.]])
-ssw_1 *= one_third
-ssw[:,:,0], ssw[:,:,1] = ssw_0, ssw_1
-nsfw = np.array([0., 0.])
-chiw = np.array([1., 0.])
-
-# Fuel I
-st1 = np.array([0.2263, 1.0119])
-ss1 = np.zeros((2, 2, 2),)
-ss1_0 = np.array([[0.2006, 0.], [0.0161, 0.9355]])
-ss1_1 = np.array([[0., 0.], [0., 0.]])
-ss1_1 *= one_third
-ss1[:,:,0], ss1[:,:,1] = ss1_0, ss1_1
-nsf1 = np.array([0.0067, 0.1241])
-chi1 = np.array([1., 0.])
-
-# Fuel II
-st2 = np.array([0.2252, 0.9915])
-ss2 = np.zeros((2, 2, 2),)
-ss2_0 = np.array([[0.1995, 0.], [0.0156, 0.9014]])
-ss2_1 = np.array([[0., 0.], [0., 0.]])
-ss2_1 *= one_third
-ss2[:,:,0], ss2[:,:,1] = ss2_0, ss2_1
-nsf2 = np.array([0.0078, 0.1542])
-chi2 = np.array([1., 0.])
-
-# Fuel III
-st3 = np.array([0.2173, 1.0606])
-ss3 = np.zeros((2, 2, 2),)
-ss3_0 = np.array([[0.1902, 0.], [0.0136, 0.5733]])
[…]

### 2020-01-06 SNMG1DSlab/snmg1dslab.py

@@ -63,89 +63,8 @@ import warnings as wrn
 import numpy as np
 from scipy.special import roots_legendre, legendre
 
-class input_data:
-    """Geometry and material input data of the 1D problem. Possible options
-    of geometry_type are slab, cylindrical and spherical. Allowed boundary
-    conditions: 0-vacuum, 1-zero flux and 2-reflection."""
-
-    def __init__(self, xs_media, media, xi, xm, dx, geometry_type='slab',
-                 LBC=0, RBC=0):
-        self.xi, self.xm, self.dx = xi, xm, dx
-        self.geometry_type = geometry_type
-        self.LBC, self.RBC = LBC, RBC
-        self.xs_media, self.media = xs_media, media
-        self.check_input()
-
-    @property
-    def I(self):
-        return self.xi.size - 1
-
-    @property
-    def L(self):
-        return self.xi[-1]
-
-    @property
-    def G(self):
-        return self.xs_media[next(iter(self.xs_media))]['st'].size
-
-
-    def check_input(self):
-        if (self.geometry_type != 'slab') and \
-           (self.geometry_type != 'cylindrical') and \
-           (self.geometry_type != 'spherical'):
-            raise ValueError('Unknown geometry_type ' + self.geometry_type)
-        if not isinstance(self.LBC, int):
-            raise TypeError('LBC must be integer.')
-        if (self.LBC < 0) and (self.LBC > 2):
-            raise ValueError('Check LBC, allowed options ')
-        if not isinstance(self.RBC, int):
-            raise TypeError('RBC must be integer.')
-        if (self.RBC < 0) and (self.RBC > 2):
-            raise ValueError('Check RBC, allowed options ')
-        if (self.geometry_type != 'slab') and (self.LBC != 2):
-            raise ValueError('Curvilinear geometries need LBC = 2.')
-        if not isinstance(self.xs_media, dict):
-            raise TypeError('The input xs_media is not a dictionary.')
-        if not isinstance(self.media, list):
-            raise TypeError('The input media is not a list.')
-#        if len(self.xs_media) != len(self.media):
[…]

### 2020-01-06 SNMG1DSlab/tests/heterSlab2GIlas2003.py

@@ -1,0 +1,47 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This test case runs the 2G heterogeneous slab problem from [GIlas2003]_.
+
+.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
+   transport correction in diffusion calculations", Proc. Int. Conf. on
+   Mathematics and Computational Methods Applied to Nuclear Science and
+   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
+"""
+import sys, os
+sys.path.append('..X..XFD1dMGdiff'.replace('X', os.path.sep))
+from data.heter2GIlas2003 import *
+from tests.heterSlab2GIlas2003 import *
+from snmg1dslab import input_data, solver_options, quad_data
+import numpy as np
+
+
+# set b.c.
+# LBC, RBC = 0, 0
+
+# Initiate inpur data object
+Heter2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
+
+# Initiate solver options object
+slvr_opts = solver_options()
+
+# Initiate quadratures object
+N, L = 16, 0
+qdata = quad_data(N, L)
+
+if __name__ == "__main__":
+
+    import logging as lg
+    lg.info("*** Solve the Ilas 2003 problem ***")
+    from snmg1dslab import solve_sn
+
+    flxm, k = solve_sn(Heter2GSlab_data, slvr_opts, qdata)
+
+    basefilen = "../output/CORE%dLBC%dRBC%d_I%d_N%d" % (core_config,
+                                                        Heter2GSlab_data.LBC,
+                                                        Heter2GSlab_data.RBC,
+                                                        Heter2GSlab_data.I,
+                                                        qdata.N)
+    np.save(basefilen + ".npy", np.array([k, flxm]), allow_pickle=True)
+    #np.savez(basefilen + ".npz", k=k, flxm=flxm)
+    

### 2020-01-06 SNMG1DSlab/tests/hetroSlab2GIlas2003.py

@@ -1,174 +1,0 @@
-#!/usr/bin/env python3
-# --*-- coding:utf-8 --*--
-"""
-This test case runs the 2G homogeneous slab problem from [Tomatis2011]_.
-
-.. [Tomatis2011] Tomatis, D. and Dall'Osso, A., "Application of a numerical
-   transport correction in diffusion calculations", Proc. Int. Conf. on
-   Mathematics and Computational Methods Applied to Nuclear Science and
-   Engineering (M&C 2011), Rio de Janeiro, RJ, Brazil, May 8-12, 2011.
-"""
-import sys
-sys.path.append('..')
-from data.hetro2GIlas2003 import *
-from snmg1dslab import input_data, solver_options, quad_data
-import numpy as np
-
-def MyWho():
-     print([v for v in globals().keys() if not v.startswith('_')])
-
-def get_fa(faid, ifa, L, nz=6):
-   '''returns a list of lists of FA id materials in location ifa in core.
-   ifa = 0,1,2,...,nfa-1 '''
-   
-   i = ifa*nz+1
-   if faid == 1:
-      media = [ 
-            ['WATER', L[i]],
-            ['FUELI', L[i+1]],
-            ['FUELII', L[i+2]],
-            ['FUELII', L[i+3]],
-            ['FUELI', L[i+4]],
-            ['WATER', L[i+5]]
-            ]
-   elif faid == 2:
-      media = [ 
-            ['WATER', L[i]],
-            ['FUELI', L[i+1]],
-            ['FUELI', L[i+2]],
-            ['FUELI', L[i+3]],
-            ['FUELI', L[i+4]],
-            ['WATER', L[i+5]]
-            ]
-   elif faid == 3:
-      media = [ 
-            ['WATER', L[i]],
-            ['FUELI', L[i+1]],
-            ['FUELIII', L[i+2]],
-            ['FUELIII', L[i+3]],
-            ['FUELI', L[i+4]],
-            ['WATER', L[i+5]]
-            ]
-   elif faid == 4:
-      media = [ 
-            ['WATER', L[i]],
-            ['FUELIII', L[i+1]],
-            ['FUELIII', L[i+2]],
-            ['FUELIII', L[i+3]],
-            ['FUELIII', L[i+4]],
-            ['WATER', L[i+5]]
-            ]
-   else:
[…]

### 2020-01-07 docs/PHYSOR2020/contents.tex
Set order files in folder PHYSOR2020, which also hosts the src files for the ANE article now.

--- 2020-01-05 docs/PHYSOR2020/ANE-RM-2020.tex
@@
-\documentclass[review,3p,onecolumn,sort&compress]{elsarticle}
-%
-%  various packages that you may wish to activate for usage 
-\usepackage{booktabs}
-\usepackage{natbib}
-%\usepackage{cite}
-%\usepackage{epsf}
-\usepackage{bm}
-\usepackage[english]{babel}
-\usepackage[autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
-\usepackage{color}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{calrsfs}
-\usepackage{lineno}
-\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
-linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
-\usepackage{xfrac}
-\usepackage{units}
-\usepackage{tikz}
-
-\usepackage[printonlyused]{acronym}
-
-\modulolinenumbers[1]
-
-\journal{Annals of Nuclear Energy}
-
-\newcommand{\eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsuberscript{#1}}
-\newcommand{\keff}{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}
-\newcommand{\kinf}{\ensuremath{k_{\textrm{\scriptsize{$\infty$}}}}}
-\newcommand{\pf}{\textrm{PPF}}
-\newcommand{\eg}{e.g.,}
-\newcommand{\ie}{i.e.,}
-\newcommand{\OO}{\hat{\bm{\Omega}}}
-\newcommand{\rr}{\bm{r}}
-\newcommand{\jp}{\ensuremath{J^+}}
-\newcommand{\jm}{\ensuremath{J^-}}
-\newcommand{\jpm}{\ensuremath{J^\pm}}
-\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
-\newcommand{\bmj}{\ensuremath{\bm{J}}}
-\newcommand{\rE}{\ensuremath{(\rr,E)}}
-\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
-\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
-\newcommand{\mcL}{\tau}
-% about notes and comments from each author
-\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
-\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
-\newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
-\newcommand{\revised}[1]{{\color{red}{#1}}}
-
-%\newcommand{\authorHead}      % Author's names here
-%           {Israeli, Ravetto \& Gilad}  
-%\newcommand{\shortTitle}      % Short title here
-%           {Adjoint Problem as Physical Heuristic for Loading Pattern Optimization}
-
-\newcommand\mscriptsize[1]{\mbox{\scriptsize\ensuremath{#1}}}
-\newcommand\mtiny[1]{\mbox{\tiny\ensuremath{#1}}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%   BEGIN DOCUMENT
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-	\begin{frontmatter}
-
-		\linenumbers
-
-		\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS USING THE pCMFD SCHEME}
-
-		%% or include affiliations in footnotes:
-		\author[bgu]{R.~Gross}
-		\author[cea]{D.~Tomatis}
-		\author[bgu]{E.~Gilad\corref{cor1}}
-		\ead{gilade@bgu.ac.il}
-
-		\cortext[cor1]{Corresponding author}
-
-		\address[bgu]{The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
-		\address[cea]{CEA, DEN, Service d’\'etudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA), 	
-						Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France}
-
-		%------------------------------------------------------------
-		\begin{abstract}
-		\modulolinenumbers[1]
-		\linenumbers
-		The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
-Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new techniques for accelerating the convergence are investigated.
-For example, we use integral flux intermediate values as new boundary conditions at each iteration and we update iteratively the extrapolated boundary using the corrected local diffusion coefficient.
-Moreover, the pCMFD scheme is implemented and its performances are compared with those of standard CMFD scheme.
-		\end{abstract}
-		%------------------------------------------------------------
-		\begin{keyword}
-		Neutron diffusion \sep Integral transport \sep Non-linear transport correction \sep CMFD \sep pCMFD
-		\end{keyword}
-		%------------------------------------------------------------
-	\end{frontmatter}
-
-\linenumbers
-
-\newpage
-
-\section{INTRODUCTION}
+\section{Introduction}
 \label{sec:intro}
@@
   \label{eq:RM-it-1D-slab}
-D^{(k+1)}(x,E) = \left. -\frac{1}{2} \int_0^a dx'
+  \begin{gathered}
+  D^{(k+1)}(x,E) =\\ \left. -\frac{1}{2} \int_0^a dx'
     {E_2[\sigma(E) \lvert x-x' \rvert]\operatorname{sign}(x-x')q^{(k)}(x',E)}
     \middle/ \frac{\partial}{\partial x}\phi^{(k)}(x,E),\right.
+  \end{gathered}
 \end{equation}
@@
   \label{eq:balance}
-J_{i+\hzi ,g} - J_{i-\hzi ,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
+  J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
 \end{equation}
@@
   \centering
-	\begin{tikzpicture}
-	\tikzstyle{every node}=[font=\footnotesize]
-	\draw[thick] (0,0) -- (3,0);
-	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
-	\draw[thick] (4,0) -- (7,0);
-	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
-	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};
-
-	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-\hzi$};
-	\node[anchor=south] at (1cm,1pt) {0};
-	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+\hzi$};
-
-	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-\hzi$};
-	\node[anchor=south] at (5.5cm,1pt) {$i$};
-	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+\hzi$};
-
-	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-\sfrac{3}{2}$};
-	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
-	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-\hzi$};
-	\end{tikzpicture}
+  \input{figures/mesh1D.tikz}
   \caption{Notation of the one-dimensional mesh.}
@@
 
-Boundary conditions applies on the diffusion current as usual by means of an extrapolated length $\zeta$, $\zeta \jD \cong D \phi$.
-Mark or Marshak approximations, or other constants derived from transport theory can be used for $\zeta$ \cite{meghreblian1960reactor}.
+The CMFD, eigenvalue balance equation are 
+\begin{equation}
+  \label{eq:CMFD-diff}
+  \begin{gathered}
+  J^+_{D,i+\hzi,g} + \delj^+_{i+\hzi,g} - J^-_{D,i-\hzi,g} - \delj^-_{i-\hzi,g} + \sigma_{i,g}\phi_{i,g}=\\
+  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G\sigma_{s,i,g\leftarrow g'}\phi_{i,g'}.
+  \end{gathered}
+\end{equation}
+Using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ}, and rearranging, yields
+\begin{equation}
+  \label{eq:CMFD-diff-rearranged}
+  \begin{split}
+  \left( \frac{-D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_{i-1} + \dx_i}\right) &\phi_{i-1,g} \\
+  + \left(\frac{D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} + \frac{D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_i + \dx_{i-1}} + \frac{\sigma_{i,g}}{2}\right) &\phi_{i,g} \\
+  + \left( \frac{-D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} \right) &\phi_{i+1,g} = \frac{1}{2}q_{i,g}.
+  \end{split}
+\end{equation}
+
+Boundary conditions applies on the diffusion current as usual by means of an extrapolated length $\zeta$, \ie{} $\zeta \jD \cong D \phi$.
+The constant $\zeta$ can follow from Mark or Marshak approximations, or others derived again from transport theory \cite{meghreblian1960reactor}.
 About the correction terms instead, it is simply $\delta J = -\delta D \phi$ with the boundary flux approximated at first order by the cell-averaged value.
@@
 % -----------------------------------------------------------------------------
+The descretized form of the diffusion equations, with pCMFD implementations, is
+\begin{equation}
+  \label{eq:pCMFD-diff1}
+  \begin{gathered}
+  J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+
+  + \left( + \delj_{i-\hzi,g}^+ - \delj_{i-\hzi,g}^- \right) \\ + \sigma_{i,g}\phi_{i,g} = q_{i,g},
+  \end{gathered}
+\end{equation}
+where
+\begin{equation}
+  \label{eq:q}
+  q_{i,g} = \frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}.
+\end{equation}
+By using Eqs.~\eqref{eq:CCF-sub}--\eqref{eq:q}, one gets
+\begin{equation}
+  \label{eq:pCMFD-diff2}
+  \begin{split}
+  -2D_{i+\hzi}\frac{\phi_{i+1,g} - \phi_{i,g}}{\dx_{i+1}+\dx_{i}} &+\left( \dd^+_{i+\hzi,g}\phi_{i,g}  - \dd^-_{i+\hzi,g }\phi_{i+1,g}\right)
+  +2D_{i-\hzi}\frac{\phi_{i,g} - \phi_{i-1,g}}{\dx_{i}+\dx_{i-1}} \\ 
+  &- \left( \dd^+_{i-\hzi,g}\phi_{i-1,g} -\dd^-_{i-\hzi,g}\phi_{i,g}\right) +\sigma_{i,g}\phi_{i,g} = q_{i,g}.
+  \end{split}
+\end{equation}
+Setting $\tild_{i+\hzi,g} = \left. 2D_{i+\hzi,g} \middle/ (\dx_{i+1}+\dx_{i})\right.$, and rearranging the above term, 
+\begin{equation}
+  \label{eq:pCMFD-rearrange}
+  \begin{split}
+  \left(-\tild_{i-\hzi,g}-\dd^+_{i-\hzi,g}\right)&\phi_{i-\hzi,g} \\
+  + \left( \tild_{i+\hzi,g} + \dd^+_{i+\hzi,g}+ \tild_{i-\hzi,g} + \sigma_{i,g}\right)&\phi_{i,g} \\
+  + \left( -\tild_{i+\hzi,g} - \dd^-_{i+\hzi,g}\right)&\phi_{i+1,g} = q_{i,g}.
+  \end{split}
+\end{equation}
 
@@
 % ------------------------------------------
-\section{RESULTS}
+\section{Results}
 \label{sec:res}
 
+xy
+
 % ------------------------------------------
-\section{CONCLUSIONS}
+\section{Conclusions}
 \label{sec:conc}
@@
 
-%\begin{figure}[!htb]
-%  \centering
-%  \includegraphics[scale=0.60]{./Figures/figure.pdf}
-%  \caption{SCALE/TRITON-NEWT Model of BWR Assembly in Order to Show and Example of a Figure and a Multi-line Caption}
-%  \label{fig:amdahl}
-%\end{figure}
-
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item Any number, text or symbol is in Times font and is not smaller than
-%  10-point after reduction to the actual window in your paper
-%\item That it can be translated into PDF
-%\end{itemize}
-
-%\begin{table}[!htb]
-%  \centering
-%  \caption{\bf Parallel Performance for the Sample Problem}
-%  \label{table:example}
-%  \begin{tabular}{|c|c|c|c|} \hline
-%   Number of & Wall-Clock & Speedup & Efficiency \\
-%   Processors & Time$^{a}$ (min) & (T$_{s}$/T$_{p}$) & (\%) \\ \hline
-%    \ 1 &  100.0 & \ ---    & ---  \\ \hline
-%    \ 2 &   52.6 & \ 1.9    & 95.0 \\ \hline
-%  \end{tabular}
-%\end{table}
-
 % ------------------------------------------
-% Daniele: I would avoid the following section about the nomenclature because of the 8 pages limit. The acronyms are already explained in the text.
 %\section*{NOMENCLATURE}
@@
 %\end{itemize}
-%
-% ------------------------------------------
-%\section*{ACKNOWLEDGEMENTS}
-%
-%Acknowledge the help of colleagues and sources of funding, as appropriate.
-%
-% ------------------------------------------
-% You can enter a bibliography into the document using the following format, or use the
-% bibliography style file "physor.bst" found in the template directory.  You can use the bibliography style file
-% by replacing the current bibliography block with:
-\setlength{\baselineskip}{12pt}
-\bibliographystyle{physor}
-\bibliography{RM-bib}
-
-% ------------------------------------------
-%\appendix
-%\gdef\thesection{APPENDIX \Alph{section}}
-%\section{Sample Appendix 1}
-%\label{app:a}
-%If necessary, include Appendices numbered in upper case alphabetical order. This is \ref{app:a}.
-%
-\end{document}

### 2020-01-07 docs/PHYSOR2020/contents_from_RoysANE_file.tex
Set order files in folder PHYSOR2020, which also hosts the src files for the ANE article now.

--- 2020-01-06 docs/PHYSOR2020/ANE-RM-2020.tex
@@
-\documentclass[review,3p,onecolumn,sort&compress]{elsarticle}
 %
-%  various packages that you may wish to activate for usage 
-\usepackage{booktabs}
-\usepackage{natbib}
-%\usepackage{cite}
-%\usepackage{epsf}
-\usepackage{bm}
-\usepackage[english]{babel}
-\usepackage[autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
-\usepackage{color}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{calrsfs}
-\usepackage{lineno}
-\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
-linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
+% Daniele: this file is only temporary for Roy's disposal and understanding.
+%
 
-% for algorithms
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-
-\usepackage{xfrac}
-\usepackage{units}
-\usepackage{tikz}
-
-\usepackage[printonlyused]{acronym}
-
-\modulolinenumbers[1]
-
-\journal{Annals of Nuclear Energy}
-
-\newcommand{\eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsuberscript{#1}}
-\newcommand{\keff}{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}
-\newcommand{\kinf}{\ensuremath{k_{\textrm{\scriptsize{$\infty$}}}}}
-\newcommand{\pf}{\textrm{PPF}}
-\newcommand{\eg}{e.g.,}
-\newcommand{\ie}{i.e.,}
-\newcommand{\OO}{\hat{\bm{\Omega}}}
-\newcommand{\rr}{\bm{r}}
-\newcommand{\jp}{\ensuremath{J^+}}
-\newcommand{\jm}{\ensuremath{J^-}}
-\newcommand{\jpm}{\ensuremath{J^\pm}}
-\newcommand{\delj}{\ensuremath{\delta J}}
-\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
-\newcommand{\bmj}{\ensuremath{\bm{J}}}
-\newcommand{\rE}{\ensuremath{(\rr,E)}}
-\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
-\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
-\newcommand{\mcL}{\tau}
-\newcommand{\dx}{\Delta}
-\newcommand{\dd}{\delta D}
-\newcommand{\tild}{\tilde{D}}
-% about notes and comments from each author
-\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
-\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
-\newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
-\newcommand{\revised}[1]{{\color{red}{#1}}}
-
-%\newcommand{\authorHead}      % Author's names here
-%           {Israeli, Ravetto \& Gilad}  
-%\newcommand{\shortTitle}      % Short title here
-%           {Adjoint Problem as Physical Heuristic for Loading Pattern Optimization}
-
-\newcommand\mscriptsize[1]{\mbox{\scriptsize\ensuremath{#1}}}
-\newcommand\mtiny[1]{\mbox{\tiny\ensuremath{#1}}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%   BEGIN DOCUMENT
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-	\begin{frontmatter}
-
-		\linenumbers
-
-		\title{Integral Transport Correction to Diffusion Calculations \\ Using the pCMFD Scheme}
-
-		%% or include affiliations in footnotes:
-		\author[bgu]{R.~Gross}
-		\author[cea]{D.~Tomatis}
-		\author[bgu]{E.~Gilad\corref{cor1}}
-		\ead{gilade@bgu.ac.il}
-
-		\cortext[cor1]{Corresponding author}
-
-		\address[bgu]{The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
-		\address[cea]{CEA, DEN, Service d’\'etudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA), 	
-						Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France}
-
-		%------------------------------------------------------------
-		\begin{abstract}
-		\modulolinenumbers[1]
-		\linenumbers
-		The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
-Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new techniques for accelerating the convergence are investigated.
-For example, we use integral flux intermediate values as new boundary conditions at each iteration and we update iteratively the extrapolated boundary using the corrected local diffusion coefficient.
-Moreover, the pCMFD scheme is implemented and its performances are compared with those of standard CMFD scheme.
-		\end{abstract}
-		%------------------------------------------------------------
-		\begin{keyword}
-		Neutron diffusion \sep Integral transport \sep Non-linear transport correction \sep CMFD \sep pCMFD
-		\end{keyword}
-		%------------------------------------------------------------
-	\end{frontmatter}
-
-\linenumbers
-
-\newpage
-
-\section{Intoduction}
+\section{Introduction}
 \label{sec:intro}
@@
 Only the zeroth moment of the angular flux, that is the scalar flux after an expansion in angle on the spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
-\eq{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
+\eqs{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
 This is the main assumption of the Ronen Method.
 \end{subequations}
-% \daniele{In case additional space will be needed, it will be possible to write \eq{eq:par-curr-calc} in a condensed form by using $\pm$.}
+% \daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
 
@@
 %
-About the RM, more accurate estimates of the net current come from the integral expressions of \eq{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
+About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
 In linearly anisotropic problems, the net current can also be considered to compute the source.
@@
 for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
+
+The CMFD, eigenvalue balance equation are 
+\begin{equation}
+  \label{eq:CMFD-diff}
+  J^+_{D,i+\hzi,g} + \delj^+_{i+\hzi,g} - J^-_{D,i-\hzi,g} - \delj^-_{i-\hzi,g} + \sigma_{i,g}\phi_{i,g}=
+  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G\sigma_{s,i,g\leftarrow g'}\phi_{i,g'}. 
+\end{equation}
+Using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ}, and rearranging, yields
+\begin{equation}
+  \label{eq:CMFD-diff-rearranged}
+  \begin{split}
+  \left( \frac{-D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_{i-1} + \dx_i}\right)\phi_{i-1,g}
+  & + \left(\frac{D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} + \frac{D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_i + \dx_{i-1}} + \frac{\sigma_{i,g}}{2}\right) \phi_{i,g} \\
+  & + \left( \frac{-D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} \right) \phi_{i+1,g} = \frac{1}{2}q_{i,g}.
+  \end{split}
+\end{equation}
 
@@
 	\begin{align}
-	J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= \delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
-	J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= \delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
+	J^+_{i+\hzi} &= \frac{1}{2}\jD_{i+\hzi} + \delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
+	J^-_{i+\hzi} &= - \frac{1}{2}\jD_{i+\hzi} + \delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
 	\end{align}
@@
   J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+ + \left( + \delj_{i-\hzi,g}^+ - 
-	\delj_{i-\hzi,g}^- \right) + \sigma_{i,g}\phi_{i,g} = q_{i,g}\,\,,
+  \delj_{i-\hzi,g}^- \right) + \sigma_{i,g}\phi_{i,g} = q_{i,g},
 \end{equation}
@@
   \label{eq:q}
-	q_{i,g} = \frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}\,\,.
+  q_{i,g} = \frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}.
 \end{equation}
@@
   +2D_{i-\hzi}\frac{\phi_{i,g} - \phi_{i-1,g}}{\dx_{i}+\dx_{i-1}} \\ 
-	&- \left( \dd^+_{i-\hzi,g}\phi_{i-1,g} -\dd^-_{i-\hzi,g}\phi_{i,g}\right) +\sigma_{i,g}\phi_{i,g} = q_{i,g}\,\,.
+  &- \left( \dd^+_{i-\hzi,g}\phi_{i-1,g} -\dd^-_{i-\hzi,g}\phi_{i,g}\right) +\sigma_{i,g}\phi_{i,g} = q_{i,g}.
   \end{split}
@@
   \left(-\tild_{i-\hzi,g}-\dd^+_{i-\hzi,g}\right)\phi_{i-\hzi,g} + &\left( \tild_{i+\hzi,g} + \dd^+_{i+\hzi,g}+ \tild_{i-\hzi,g} + \sigma_{i,g}\right)\phi_{i,g} \\
-	&+ \left( -\tild_{i+\hzi,g} - \dd^-_{i+\hzi,g}\right)\phi_{i+1,g} = q_{i,g}\,\,.
+  &+ \left( -\tild_{i+\hzi,g} - \dd^-_{i+\hzi,g}\right)\phi_{i+1,g} = q_{i,g}.
   \end{split}
@@
 
+xy
+
 % ------------------------------------------
@@
 Present your summary and conclusions here.
-
-%\begin{figure}[!htb]
-%  \centering
-%  \includegraphics[scale=0.60]{./Figures/figure.pdf}
-%  \caption{SCALE/TRITON-NEWT Model of BWR Assembly in Order to Show and Example of a Figure and a Multi-line Caption}
-%  \label{fig:amdahl}
-%\end{figure}
-
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item Any number, text or symbol is in Times font and is not smaller than
-%  10-point after reduction to the actual window in your paper
-%\item That it can be translated into PDF
-%\end{itemize}
-
-%\begin{table}[!htb]
-%  \centering
-%  \caption{\bf Parallel Performance for the Sample Problem}
-%  \label{table:example}
-%  \begin{tabular}{|c|c|c|c|} \hline
-%   Number of & Wall-Clock & Speedup & Efficiency \\
-%   Processors & Time$^{a}$ (min) & (T$_{s}$/T$_{p}$) & (\%) \\ \hline
-%    \ 1 &  100.0 & \ ---    & ---  \\ \hline
-%    \ 2 &   52.6 & \ 1.9    & 95.0 \\ \hline
-%  \end{tabular}
-%\end{table}
-
-% ------------------------------------------
-% Daniele: I would avoid the following section about the nomenclature because of the 8 pages limit. The acronyms are already explained in the text.
-%\section*{NOMENCLATURE}
-%
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item RM - Ronen Method
-%\item CMFD - Coarse Mesh Finite Difference
-%\item pCMFD - partial current CMFD
-%\end{itemize}
-%
-% ------------------------------------------
-%\section*{ACKNOWLEDGEMENTS}
-%
-%Acknowledge the help of colleagues and sources of funding, as appropriate.
-%
-% ------------------------------------------
-% You can enter a bibliography into the document using the following format, or use the
-% bibliography style file "physor.bst" found in the template directory.  You can use the bibliography style file
-% by replacing the current bibliography block with:
-\setlength{\baselineskip}{12pt}
-\bibliographystyle{physor}
-\bibliography{RM-bib}
-
-% ------------------------------------------
-%\appendix
-%\gdef\thesection{APPENDIX \Alph{section}}
-%\section{Sample Appendix 1}
-%\label{app:a}
-%If necessary, include Appendices numbered in upper case alphabetical order. This is \ref{app:a}.
-%
-\end{document}

### 2020-01-08 docs/PHYSOR2020/contents.tex
minor changes to the current version of the text

@@
 Second-order SPN equations can be solved by ordinary diffusion codes~\cite{Larsen-1993}.
-Yamamoto et Al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
+Yamamoto et Al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP$_3$ flux.
 This is because this quantity is generally smaller than the scalar flux (0-th moment) and can change its sign.
@@
 
-The CMFD (and its variants) was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
+The CMFD scheme was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
 Contrary to the previous implementations, no operator was inverted to get a new higher order approximation of the flux solution.
-As well, this offered a fast and more accurate estimate of the current too.
+Thereafter, this offered a fast and more accurate estimate of the current too.
 
@@
 \end{equation}
-where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
+where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems \cite{boffi1972tensorial}.
 
@@
 where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the effective multiplication factor (the eigenvalue), $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
-As well, integer and rational subscripts indicate node-averaged and interface quantities, respectively.
+Integer and rational subscripts indicate node-averaged and interface quantities, respectively.
 %
@@
 
-The net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
+The partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}:
 \begin{subequations}
@@
   \end{equation}
-where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$, $\forall i$.
-Only the zeroth moment of the angular flux, that is the scalar flux after an expansion in angle on the spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
+where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length.
+The net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$, $\forall i$.
+Only the zeroth moment of the angular flux, that is the scalar flux yet occurring after its expansion in angle on spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
 \eqs{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
@@
 
-In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
+In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$ used in \eq{eq:balance}.
 Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime \cite{Smith-1983}.
@@
 \end{equation}
-for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
-
-The CMFD, eigenvalue balance equation are 
-\begin{equation}
-  \label{eq:CMFD-diff}
-  \begin{gathered}
-  J^+_{D,i+\hzi,g} + \delj^+_{i+\hzi,g} - J^-_{D,i-\hzi,g} - \delj^-_{i-\hzi,g} + \sigma_{i,g}\phi_{i,g}=\\
-  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G\sigma_{s,i,g\leftarrow g'}\phi_{i,g'}.
-  \end{gathered}
-\end{equation}
-Using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ}, and rearranging, yields
+for $i = 0, \ldots, I-2$.
+The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
+By retrieving the net current from \eq{eq:dJ} and substitution in \eq{eq:balance} with the source from \eq{eq:qsrc} yields the CMFD balance equation.
+Finally, using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ} and rearranging, the flux follows by solving a system of linear equations:
+%
+% Daniele: the signs at superscript are not valid here. This is removed to get shorter text. A sentence is added to the previous paragraph to introduce implicitly the eqn to solove.
+%
+%The CMFD, eigenvalue balance equation are 
+%\begin{equation}
+%  \label{eq:CMFD-diff}
+%  \begin{gathered}
+%  J^+_{D,i+\hzi,g} + \delj^+_{i+\hzi,g} - J^-_{D,i-\hzi,g} - \delj^-_{i-\hzi,g} + \sigma_{i,g}\phi_{i,g}=\\
+%  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G\sigma_{s,i,g\leftarrow g'}\phi_{i,g'}.
+%  \end{gathered}
+%\end{equation}
+%Using Eqs.~\eqref{eq:JD}, \eqref{eq:dJ}, and rearranging, yields
 \begin{equation}
@@
   + \left(\frac{D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} + \frac{D_{i-\hzi,g} + \dd_{i-\hzi,g}}{\dx_i + \dx_{i-1}} + \frac{\sigma_{i,g}}{2}\right) &\phi_{i,g} \\
-  + \left( \frac{-D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} \right) &\phi_{i+1,g} = \frac{1}{2}q_{i,g}.
+  + \left( \frac{-D_{i+\hzi,g} - \dd_{i+\hzi,g}}{\dx_{i+1} + \dx_i} \right) &\phi_{i+1,g} = \frac{1}{2}q_{i,g},
   \end{split}
 \end{equation}
+for $0 < i < I-1$.
 
@@
 About the correction terms instead, it is simply $\delta J = -\delta D \phi$ with the boundary flux approximated at first order by the cell-averaged value.
+The introduction of these closures in the equations for $i=0$ and $i=I-1$ is straightforward.
 
@@
 \end{equation}
+%
+% Daniele: the signs used for the \pm J corrections is not so important because
+% of the arbitrarity of the corrections themselves. But whatever the choice
+% has been made, the implementation must stick closely with it.
+%
 The current by diffusion is distributed on the partial currents in equal parts in order to compute the new corrective coefficients $\delta D^{\pm}$,
@@
 still for $i=0, \ldots, I-2$.
-The diffusion current is not halved at the boundary, using only \eq{eq:delta-D-pCMFDm} or \eq{eq:delta-D-pCMFDp} at the left and at the right boundaries, respectively.
-Finally, the implementation of CMFD can be upgraded to support the pCMFD scheme with minimal changes.
 % -----------------------------------------------------------------------------
@@
 % -----------------------------------------------------------------------------
-The descretized form of the diffusion equations, with pCMFD implementations, is
-\begin{equation}
-  \label{eq:pCMFD-diff1}
-  \begin{gathered}
-  J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+
-  + \left( + \delj_{i-\hzi,g}^+ - \delj_{i-\hzi,g}^- \right) \\ + \sigma_{i,g}\phi_{i,g} = q_{i,g},
-  \end{gathered}
-\end{equation}
-where
-\begin{equation}
-  \label{eq:q}
-  q_{i,g} = \frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}.
-\end{equation}
-By using Eqs.~\eqref{eq:CCF-sub}--\eqref{eq:q}, one gets
-\begin{equation}
-  \label{eq:pCMFD-diff2}
-  \begin{split}
-  -2D_{i+\hzi}\frac{\phi_{i+1,g} - \phi_{i,g}}{\dx_{i+1}+\dx_{i}} &+\left( \dd^+_{i+\hzi,g}\phi_{i,g}  - \dd^-_{i+\hzi,g }\phi_{i+1,g}\right)
-  +2D_{i-\hzi}\frac{\phi_{i,g} - \phi_{i-1,g}}{\dx_{i}+\dx_{i-1}} \\ 
-  &- \left( \dd^+_{i-\hzi,g}\phi_{i-1,g} -\dd^-_{i-\hzi,g}\phi_{i,g}\right) +\sigma_{i,g}\phi_{i,g} = q_{i,g}.
-  \end{split}
-\end{equation}
-Setting $\tild_{i+\hzi,g} = \left. 2D_{i+\hzi,g} \middle/ (\dx_{i+1}+\dx_{i})\right.$, and rearranging the above term, 
+%
+% Daniele: removed to get shorter text and avoid repetitions
+%
+%The descretized form of the diffusion equations, with pCMFD implementations, is
+%\begin{equation}
+%  \label{eq:pCMFD-diff1}
+%  \begin{gathered}
+%  J_{D,i+\hzi,g}^+ +\left( \delj_{i+\hzi,g}^+ - \delj_{i+\hzi,g}^- \right) - J_{D,i-\hzi,g}^+
+%  + \left( + \delj_{i-\hzi,g}^+ - \delj_{i-\hzi,g}^- \right) \\ + \sigma_{i,g}\phi_{i,g} = q_{i,g},
+%  \end{gathered}
+%\end{equation}
+%where
+%\begin{equation}
+%  \label{eq:q}
+%  q_{i,g} = \frac{\chi_g}{\keff}\sum\limits^G_{g'=1}\nu\sigma_{f,g'}\phi_{i,g'} + \sum\limits_{g'=1}^G \sigma_{s,i,0,g\leftarrow g'}\phi_{i,g'}.
+%\end{equation}
+The same substitutions indicated in section \ref{sec:RM-CMFD} lead to the pCMFD balance equation, where after introducing Eqs.
+\ref{eq:JD} and \ref{eq:CCF-sub} for the currents it is in the $i$-th cell
+%\begin{equation}
+%  \label{eq:pCMFD-diff2}
+%  \begin{split}
+%  -2D_{i+\hzi}\frac{\phi_{i+1,g} - \phi_{i,g}}{\dx_{i+1}+\dx_{i}} &+\left( \dd^+_{i+\hzi,g}\phi_{i,g}  - \dd^-_{i+\hzi,g }\phi_{i+1,g}\right)
+%  +2D_{i-\hzi}\frac{\phi_{i,g} - \phi_{i-1,g}}{\dx_{i}+\dx_{i-1}} \\ 
+%  &- \left( \dd^+_{i-\hzi,g}\phi_{i-1,g} -\dd^-_{i-\hzi,g}\phi_{i,g}\right) +\sigma_{i,g}\phi_{i,g} = q_{i,g}.
+%  \end{split}
+%\end{equation}
 \begin{equation}
@@
   \begin{split}
-  \left(-\tild_{i-\hzi,g}-\dd^+_{i-\hzi,g}\right)&\phi_{i-\hzi,g} \\
-  + \left( \tild_{i+\hzi,g} + \dd^+_{i+\hzi,g}+ \tild_{i-\hzi,g} + \sigma_{i,g}\right)&\phi_{i,g} \\
-  + \left( -\tild_{i+\hzi,g} - \dd^-_{i+\hzi,g}\right)&\phi_{i+1,g} = q_{i,g}.
+  \left(-\tild_{i-\hzi,g}+\dd^+_{i-\hzi,g}\right)&\phi_{i-1,g} \\
+  + \left( \tild_{i+\hzi,g} - \dd^+_{i+\hzi,g} + \tild_{i-\hzi,g} + \dd^-_{i-\hzi,g} + \sigma_{i,g}\right)&\phi_{i,g} \\
+  + \left( -\tild_{i+\hzi,g} - \dd^-_{i+\hzi,g}\right)&\phi_{i+1,g} = q_{i,g},
   \end{split}
 \end{equation}
+with $\tild_{i+\hzi,g} = \left.
+2D_{i+\hzi,g} \middle/ (\dx_{i+1}+\dx_{i})\right.$.
+The diffusion current is not halved at the boundary, using only \eq{eq:delta-D-pCMFDm} or \eq{eq:delta-D-pCMFDp} at the left and at the right boundaries, respectively.
+Indeed, the implementation of CMFD can be upgraded to support the pCMFD scheme with minimal changes.
 

### 2020-01-08 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex

--- 2019-11-12 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
@@
 %
-% \newcommand{\revised}[1]{{\color{red}{#1}}}
 % \newcommand{\tsup}[1]{\textsuperscript{#1}}
@@
 \newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
+\newcommand{\kinf}{\ensuremath{k_{\textrm{\scriptsize{$\infty$}}}}}
 \newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
+\newcommand{\eg}{e.g.,}
+\newcommand{\ie}{i.e.,}
+\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
 \newcommand{\rr}{\ensuremath{\bm{r}}}
-\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
 \newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
@@
 %\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcL}{\tau}
 \newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
-\newcommand{\dx}{\ensuremath{\Delta x}}
 
@@
 \newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
+\newcommand{\mcL}{\tau}
+\newcommand{\dx}{\Delta}
+\newcommand{\dd}{\delta D}
+\newcommand{\tild}{\tilde{D}}
+\newcommand{\sep}{\unskip,~}
 
@@
 \newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
+\newcommand{\revised}[1]{{\color{red}{#1}}}
+
+\newcommand\mscriptsize[1]{\mbox{\scriptsize\ensuremath{#1}}}
+\newcommand\mtiny[1]{\mbox{\tiny\ensuremath{#1}}}
 
@@
 \justify
-
 % ------------------------------------------
-\begin{abstract}
-  The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
-Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new techniques for accelerating the convergence are investigated.
-For example, we use integral flux intermediate values as new boundary conditions at each iteration and we update iteratively the extrapolated boundary using the corrected local diffusion coefficient.
-Moreover, the pCMFD scheme is implemented and its performances are compared with those of standard CMFD scheme.
-\end{abstract}
-\keywords{neutron diffusion, integral transport, non-linear transport correction, CMFD, pCMFD}
-% Daniele suggestion:
-% I would not include pCMFD since it belongs to the CMFD class of methods and shorten the list of keywords
-
+\input{abstract/abstract}
+\keywords{\input{keywords}}
 % ------------------------------------------
-\section{INTRODUCTION}
-\label{sec:intro}
-
-The distribution of the neutron flux in the reactor core is described by the neutron transport equation.
-Transport calculations on a full core scale can be a highly intensive computational task.
-To overcome this difficulty, faster (but less accurate) multigroup neutron diffusion solvers are often used.
-Indeed, future Gen-IV reactor designs are characterized by strong heterogeneity in the core and modern calculation schemes evolve towards best-estimate codes, aiming at high accuracy for these new configurations.
-Hence, the accuracy of diffusion calculations is investigated.
-A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient.
-The calculation of this parameter should be based on physical insights from the full transport equation, such that the resulting (transport-corrected) diffusion approximation can capture the transport phenomena of interest.
-
-% Daniele: I found this paragraph commented, but I think that the two following sections should be properly introduced in this section. Therefore, I am uncommenting it.
-The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
-The iterative scheme calculates new flux distributions using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
-Alternatively, the Coarse Mesh Finite Differences (CMFD) scheme can be enforced in the discretized form of the diffusion equation to reproduce the transport current by means of a drift term.
-The implementation of one its variants, the partial current formulation of the CMFD (pCMFD), is studied in this work.
-%
-% The direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning.
-Nonetheless, the integral current can be enforced in the Coarse Mesh Finite Difference (CMFD) discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients.
-This is the option adopted in this study.
-
-% ------------------------------------------
-\section{COARSE MESH FINITE DIFFERENCES}
-\label{sec:CMFD-intro}
-
-The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing for separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
-Recently, multi-dimensional transport codes have used it as acceleration technique and the convergence of different implementations was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
-
-The use of a coarse mesh for the discretization of the problem is generally causing considerable error by truncation applied on the finite difference approximations of the derivative terms.
-On the other hand, it yields very fast calculations.
-The CMFD method recovers corrective terms by exploiting functional relations between the (scalar) flux and the current density, which appear in the neutron balance equation.
-The balance equation is solved for the flux, so that local models seek more accurate estimates of the current in order to derive these corrections.
-In principle, the corrective terms can be computed with a different physics other than diffusion, which is always solved at the coarse level.
-This facilitates its application to accelerate complex multi-dimensional transport codes.
-This acceleration is actually implemented by rebalancing the scalar flux, with the optional use of some relaxation~\cite{Park-2017}.
-Hence, a non-linear iterative scheme arises between the CMFD solver and the computation of the local corrections, which use the latest estimates of the flux available from the diffusion solver.
-
-Second-order SPN equations can be solved by ordinary diffusion codes~\cite{Larsen-1993}.
-Yamamoto et Al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
-This is because this quantity is generally smaller than the scalar flux (0-th moment) and can change its sign.
-They proposed to modify the balance equation for the second moment in order to fix this numerical behavior.
-The modification consisted of a shift with a positive quantity of the second moment so that their difference between neighboring quantities is unchanged, and their sum becomes positive and arbitrarily large.
-
-When partial currents can be computed, the pCMFD method~\cite{Cho-2003} can be used to determine two distinct corrective terms per positive and negative partial currents, instead of having a single degree of freedom per cell surface.
-Another version of the CMFD called artificial diffusion~\cite{Zhu-2016,Jarrett-2016} redefines the diffusion coefficient as the sum of the original value and a complement derived from the current difference, which is still considered as proportional to the flux gradient.
-This scheme can potentially lead to negative diffusion constants.
-
-The CMFD (and its variants) was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
-Contrary to the previous implementations, no operator was inverted to get a new higher order approximation of the flux solution.
-As well, this offered a fast and more accurate estimate of the current too.
-
-% ------------------------------------------
-\section{THE RONEN METHOD}
-\label{sec:RM}
-
-In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux was resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}^D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
-\begin{equation}
-  \label{eq:Fick}
-  \bm{J}^D\rE = -D\rE\bnabla\phi\rE \cong \bm{J}\rE.
-\end{equation}
-
-Since these accurate estimates of the currents were based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
-\begin{equation}
-  \label{eq:RM-it}
-  D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE \rvert}{\lvert \bnabla \phi^{(k)}\rE \rvert},
-\end{equation}
-where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
-
-The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
-Nevertheless, isotropic scattering remained as a basic postulate.
-For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
-\begin{equation}
-  \label{eq:RM-it-1D-slab}
-  D^{(k+1)}(x,E) = \left. -\frac{1}{2} \int_0^a dx'
-    {E_2[\sigma(E) \lvert x-x' \rvert]\operatorname{sign}(x-x')q^{(k)}(x',E)}
-    \middle/ \frac{\partial}{\partial x}\phi^{(k)}(x,E),\right.
-\end{equation}
-where the source term $q^{(k)}$ is calculated using the multigroup diffusion model with the available scalar flux, and the updated diffusion coefficient $D^{(k+1)}$ is evaluated using the integral expression for the transport current.
-
-In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration of the simple slab problem.
-They chose the CMFD scheme in the diffusion solver for taking into account the new currents estimated by the integral transport operator.
-%
-%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
-%
-This technique can avoid indeterminate divisions in case of vanishing flux gradients and reproduces the transport effects under a drift term.
-It was observed that the RM could drive the flux distribution closer to the transport reference solution.
-As expected, the largest errors were located near the boundary, where the transport effects are more pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
-
-% ------------------------------------------
-\section{NUMERICAL IMPLEMENTATION}
-\label{sec:RM-num}
-
-The neutron balance equation for a $k$-eigenvalue problem integrated in the $i$-th element of a one-dimensional mesh is (see Fig.~\ref{fig:mesh1D})
-\begin{equation}
-  \label{eq:balance}
-  J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
-\end{equation}
-where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
-\begin{equation}
-  \label{eq:qsrc}
-  q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
-  \frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'},
-\end{equation}
-where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the effective multiplication factor (the eigenvalue), $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
-As well, integer and rational subscripts indicate node-averaged and interface quantities, respectively.
-%
-\begin{figure}[htbp]
-	\centering
-  \input{figures/mesh1D.tikz}
-	\caption{Notation of the one-dimensional mesh.}
-	\label{fig:mesh1D}
-\end{figure}
-
-The accurate net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
-\begin{subequations}
-  \label{eq:par-curr-calc}
-  \begin{equation}
-    \label{eq:par-curr-calc-plus}
-    \begin{split}
-      \jp_{i+\hzi,g} &=  \frac{1}{2}
-        E_3[\mcL_g(x_{-\hzi},x_{i+\hzi})] \phi_{x_{-\hzi},g} \\
-        & + \frac{1}{2}\sum\limits_{j=0}^i \frac{q_{j,g}}{\sigma_{j,g}}
-            \left\{ E_3\left[ \mcL_g(x_{j+\hzi},x_{i+\hzi}) \right]
-                  - E_3\left[ \mcL_g(x_{j-\hzi},x_{i+\hzi}) \right]
-            \right\}
-    \end{split}
-  \end{equation}
-  %
-  \begin{equation}
-    \begin{split}
-      \label{eq:par-curr-calc-minus}
-      \jm_{i+\hzi,g} &=  \frac{1}{2}
-        E_3[\mcL_g(x_{i+\hzi},x_{I-\hzi})] \phi_{x_{I-\hzi},g} \\
-        & + \frac{1}{2}\sum\limits_{j=i+1}^{I-1} \frac{q_{j,g}}{\sigma_{j,g}}
-            \left\{ E_3\left[ \mcL_g(x_{i+\hzi},x_{j-\hzi}) \right]
-                  - E_3\left[ \mcL_g(x_{i+\hzi},x_{j+\hzi}) \right]
-            \right\},
-    \end{split}
-  \end{equation}
-where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$.
-\end{subequations}
-% \daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
-
-% ------------------------------------------
-\subsection{CMFD IMPLEMENTATION}
-\label{sec:RM-CMFD}
-
-In standard CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
-Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime.
-Besides, the net current can be determined from some other expression which is physically or numerically more accurate.
-Therefore, this new term acts as a correction for the diffusion current.
-The diffusion current is generally approximated by finite differences according to
-\begin{equation}
-  \label{eq:JD}
-  \jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
-    \frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
-\end{equation}
-where the diffusion coefficient at the interface is volume-averaged as
-\begin{equation}
-  \label{eq:Ds}
-  D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
-{\Delta_i + \Delta_{i+1}}.
-\end{equation}
-%
-About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
-Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
-The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
-\begin{equation}
-  \label{eq:dJ}
-  \delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
-    \frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
-  J_{i+\hzi,g} - \jD_{i+\hzi,g}.
-\end{equation}
-The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
-Boundary conditions applies as usual on the diffusion current and on the net (more accurate) current, without any particular change for the definition of the correction term.
-
-% ------------------------------------------
-\subsection{pCMFD IMPLEMENTATION}
-\label{sec:RM-pCMFD}
-
-The CMFD introduces a free parameter in the numerical scheme through the correction term to adjust the diffusive solution locally.
-Since separate calculations of the partial currents are possible, two free parameters could be used in the discretized form of the diffusion equation.
-
-Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
-\begin{equation}
-\label{eq:partial-current}
-\jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
-\end{equation}
-still verifying the expression for the net current $J = J^+ - J^-$.
-% Daniele: the 1st moment is the scalar current and not its diffusion approx
-%where $\jD$ denotes the diffusion current.
-%where
-%\begin{equation}
-%\label{eq:diff-current}
-%\bm{J} (x) = \jp(x) - \jm(x).
-%\end{equation}
-\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
-\begin{equation}
-  \label{eq:PCCF}
-  \jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
-    \left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
-\end{equation}
-and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
-\begin{equation}
-\label{eq:CCF-sub}
-\delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
-\quad \text{and} \quad
-\delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
-\end{equation}
-% yields
-% \begin{align}
-% \label{eq:par4}
-% \jp _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-% + \frac{1}{2}\jD _{i+\hzi} - \delta D^+ _{i+\hzi} \phi_i \\
-% \jm _{i+\hzi} &= \frac{1}{4}\phi_{i+\hzi}
-% - \frac{1}{2}\jD _{i+\hzi} + \delta D^- _{i+\hzi} \phi_{i+1}.
-% \end{align}
-%Recall that $\jpm$ are calculated using the integral expression.
-%
-Solving for the partial current correction factors gives
-\begin{equation}
-  \label{eq:ccfsss1}
-  \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
-  	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
-  \quad \text{and} \quad
-  \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
-  	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
-  \end{equation}
-where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.
-% \begin{equation}
-%   \label{eq:jdiff}
-%   \phi_{i+\hzi} = \frac{\Delta_i \phi_i + \Delta_{i+1} \phi_{i+1}}
-%                        {\Delta_i + \Delta_{i+1}}.
-% \end{equation}
-
-In a weakly absorbing medium and several mean free paths away from the boundary or a strong absorber, all correction factors $\delta D^\pm$ are expected to vanish and the net current must be fully reproduced by the diffusion current.% and~\eq{eq:ccfsss1} reduces to~\eq{eq:partial-current}, as expected, which implies for the net (accurate) current
-% \begin{equation}
-% J _{i+\hzi} = \jp _{i+\hzi} - \jm _{i+\hzi} = \jD _{i+\hzi}.
-% \end{equation}
-
-% ------------------------------------------
-\section{RESULTS}
-\label{sec:res}
-
-% ------------------------------------------
-\section{CONCLUSIONS}
-\label{sec:conc}
-
-Present your summary and conclusions here.
-
-%\begin{figure}[!htb]
-%  \centering
-%  \includegraphics[scale=0.60]{./Figures/figure.pdf}
-%  \caption{SCALE/TRITON-NEWT Model of BWR Assembly in Order to Show and Example of a Figure and a Multi-line Caption}
-%  \label{fig:amdahl}
-%\end{figure}
-
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item Any number, text or symbol is in Times font and is not smaller than
-%  10-point after reduction to the actual window in your paper
-%\item That it can be translated into PDF
-%\end{itemize}
-
-%\begin{table}[!htb]
-%  \centering
-%  \caption{\bf Parallel Performance for the Sample Problem}
-%  \label{table:example}
-%  \begin{tabular}{|c|c|c|c|} \hline
-%   Number of & Wall-Clock & Speedup & Efficiency \\
-%   Processors & Time$^{a}$ (min) & (T$_{s}$/T$_{p}$) & (\%) \\ \hline
-%    \ 1 &  100.0 & \ ---    & ---  \\ \hline
-%    \ 2 &   52.6 & \ 1.9    & 95.0 \\ \hline
-%  \end{tabular}
-%\end{table}
-
-% ------------------------------------------
-% Daniele: I would avoid the following section about the nomenclature because of the 8 pages limit. The acronyms are already explained in the text.
-%\section*{NOMENCLATURE}
-%
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item RM - Ronen Method
-%\item CMFD - Coarse Mesh Finite Difference
-%\item pCMFD - partial current CMFD
-%\end{itemize}
+\input{contents}
 %
@@
 \bibliography{RM-bib}
-
 % ------------------------------------------

### 2020-01-12 FD1dMGdiff/FDsDiff1D.py
Bug fix
1. Fixed SN to run with data file from FD1dMGdiff folder
2. Some bug fix within FDsDiff1D
3. added plot script to physor  - status: dev
4. added results of the homogeneous case (pCMFD and CMFD)

@@ -88,6 +88,7 @@ class input_data:
         self.xs_media, self.media = xs_media, media
         self.check_input()
         self.compute_cell_width()
+        self.compute_mid_cell_coordinate()
         self.compute_cell_volumes()
 
     @property
@@ -115,6 +116,10 @@ class input_data:
     
     def compute_cell_width(self):
         self.Di = self.xi[1:] - self.xi[:-1]
+    
+    def compute_mid_cell_coordinate(self):
+        self.xm = (self.xi[1:] + self.xi[:-1]) / 2.
+    
     
     def compute_cell_volumes(self):
         self.Vi = compute_cell_volumes(self.xi, geo=self.geometry_type)
@@ -657,7 +662,7 @@ def compute_D(Di, flx, pJ, BC=(0, 0), zero=1.e-6, chk=False):
         if not np.allclose(Jcmp, J[:, 1:-1]):
             lg.debug("Computed/input currents mismatch")
             lg.debug('Jout', Jcmp)
-            ld.debug('Jin ', J[:, 1:-1])
+            lg.debug('Jin ', J[:, 1:-1])
         JL = -Db[:,  0] * flx[:, 0] / (0.5 * Di[ 0] + zetal * Db[:, 0])
         JR =  Db[:, -1] * flx[:,-1] / (0.5 * Di[-1] + zetar * Db[:,-1])
         if not np.allclose(JL, J[:, 0]):
@@ -884,11 +889,11 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
     lg.info("Initial value of k was %13.6g." % kinit)
     if filename is not None:
         # filename = "output/kflx_LBC%dRBC%d_I%d" % (*BC,I)
-        np.save(filename + ".npy", [k_save, flx_save], allow_pickle=True)
+        np.save(filename + ".npy", [k_save, flx_save, xi, xs[0], dD], allow_pickle=True)
         # np.save(filename.replace('kflx','err'), [kerr_save, ferr_save], \
-                  allow_pickle=True)
+        #          allow_pickle=True)
         # np.save(filename + ".npy", [k_save, flx_save, xi, xs[0], dD], \
-                  allow_pickle=True)
+        #          allow_pickle=True)
         with open(filename + ".dat", 'w') as f:
             i = 0
             while k_save[i] >= 0:

### 2020-01-12 SNMG1DSlab/snmg1dslab.py

@@ -63,7 +63,7 @@ import warnings as wrn
 import numpy as np
 from scipy.special import roots_legendre, legendre
 
-sys.path.append('..XFD1dMGdiff'.replace('X', os.path.sep))
+sys.path.append('../..XFD1dMGdiff'.replace('X', os.path.sep))
 from FDsDiff1D import input_data, solver_options, unfold_xs
 
 

### 2020-01-12 SNMG1DSlab/tests/HomogSlab2GMC2011.py

@@ -10,7 +10,10 @@ This test case runs the 2G homogeneous slab problem from [Tomatis2011].
 """
 import sys
 sys.path.append('..')
+sys.path.append('../../FD1dMGdiff')
 from data.homog2GMC2011 import *
+
+
 from snmg1dslab import input_data, solver_options, quad_data
 import numpy as np
 
@@ -18,11 +21,11 @@ import numpy as np
 # after import
 
 L = 21.5 # Core width
-I = 200 # No. of spatial cells
+I = 100 # No. of spatial cells
 xi = np.linspace(0, L, I+1)  # equidistant mesh      
 # definition of the spatial mesh
-xm = (xi[1:] + xi[:-1]) / 2.
-dx = xi[1:] - xi[:-1]
+#xm = (xi[1:] + xi[:-1]) / 2.
+#dx = xi[1:] - xi[:-1]
 
 geometry_type = 'slab'
 
@@ -38,8 +41,8 @@ media = [['HM', L]]  # i.e. homogeneously filled
 LBC, RBC = 0, 0
 
 # Initiate inpur data object
-Homog2GSlab_data = input_data(xs_media, media, xi, xm, dx, geometry_type, LBC, RBC)
-
+Homog2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
+#xm, dx,
 # Initiate solver options object
 slvr_opts = solver_options()
 
@@ -60,6 +63,6 @@ if __name__ == "__main__":
                                                         Homog2GSlab_data.I,
                                                         Homog2GSlab_data.xi[-1],
                                                         qdata.N)
-    np.save(basefilen + ".npy", np.array([k, flxm]), allow_pickle=True)
-    #np.savez(basefilen + ".npz", k=k, flxm=flxm)
+    np.save(basefilen + ".npy", np.array([[k], flxm]), allow_pickle=True)
+    #np.save(basefilen + ".npy", k, flxm)
     

### 2020-01-13 docs/ANE2020/abstract/abstract.tex
rename the PHYSOR2020 folder to agree with the new publication goal

--- 2020-01-05 docs/PHYSOR2020/ANE-RM-2020.tex
@@
-\documentclass[review,3p,onecolumn,sort&compress]{elsarticle}
-%
-%  various packages that you may wish to activate for usage 
-\usepackage{booktabs}
-\usepackage{natbib}
-%\usepackage{cite}
-%\usepackage{epsf}
-\usepackage{bm}
-\usepackage[english]{babel}
-\usepackage[autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
-\usepackage{color}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{calrsfs}
-\usepackage{lineno}
-\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
-linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
-\usepackage{xfrac}
-\usepackage{units}
-\usepackage{tikz}
-
-\usepackage[printonlyused]{acronym}
-
-\modulolinenumbers[1]
-
-\journal{Annals of Nuclear Energy}
-
-\newcommand{\eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsuberscript{#1}}
-\newcommand{\keff}{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}
-\newcommand{\kinf}{\ensuremath{k_{\textrm{\scriptsize{$\infty$}}}}}
-\newcommand{\pf}{\textrm{PPF}}
-\newcommand{\eg}{e.g.,}
-\newcommand{\ie}{i.e.,}
-\newcommand{\OO}{\hat{\bm{\Omega}}}
-\newcommand{\rr}{\bm{r}}
-\newcommand{\jp}{\ensuremath{J^+}}
-\newcommand{\jm}{\ensuremath{J^-}}
-\newcommand{\jpm}{\ensuremath{J^\pm}}
-\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
-\newcommand{\bmj}{\ensuremath{\bm{J}}}
-\newcommand{\rE}{\ensuremath{(\rr,E)}}
-\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
-\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
-\newcommand{\mcL}{\tau}
-% about notes and comments from each author
-\newcommand{\erez}[1]{{\color{blue}{\textsuperscript{EREZ:}#1}}}
-\newcommand{\roy}[1]{{\color{blue}{\textsuperscript{ROY:}#1}}}
-\newcommand{\daniele}[1]{{\color{blue}{\textsuperscript{DANIELE:}#1}}}
-\newcommand{\revised}[1]{{\color{red}{#1}}}
-
-%\newcommand{\authorHead}      % Author's names here
-%           {Israeli, Ravetto \& Gilad}  
-%\newcommand{\shortTitle}      % Short title here
-%           {Adjoint Problem as Physical Heuristic for Loading Pattern Optimization}
-
-\newcommand\mscriptsize[1]{\mbox{\scriptsize\ensuremath{#1}}}
-\newcommand\mtiny[1]{\mbox{\tiny\ensuremath{#1}}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%   BEGIN DOCUMENT
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-	\begin{frontmatter}
-
-		\linenumbers
-
-		\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS USING THE pCMFD SCHEME}
-
-		%% or include affiliations in footnotes:
-		\author[bgu]{R.~Gross}
-		\author[cea]{D.~Tomatis}
-		\author[bgu]{E.~Gilad\corref{cor1}}
-		\ead{gilade@bgu.ac.il}
-
-		\cortext[cor1]{Corresponding author}
-
-		\address[bgu]{The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
-		\address[cea]{CEA, DEN, Service d’\'etudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA), 	
-						Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France}
-
-		%------------------------------------------------------------
-		\begin{abstract}
-		\modulolinenumbers[1]
-		\linenumbers
+\begin{abstract}%
 The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
@@
 \end{abstract}
-		%------------------------------------------------------------
-		\begin{keyword}
-		Neutron diffusion \sep Integral transport \sep Non-linear transport correction \sep CMFD \sep pCMFD
-		\end{keyword}
-		%------------------------------------------------------------
-	\end{frontmatter}
-
-\linenumbers
-
-\newpage
-
-\section{INTRODUCTION}
-\label{sec:intro}
-
-The distribution of the neutron flux in the reactor core is described by the neutron transport equation.
-Transport calculations on a full core scale can be a highly intensive computational task.
-To overcome this difficulty, faster (but less accurate) multigroup neutron diffusion solvers are often used.
-Indeed, future Gen-IV reactor designs are characterized by strong heterogeneity in the core and modern calculation schemes evolve towards best-estimate codes, aiming at high accuracy for these new configurations.
-Hence, the accuracy of diffusion calculations is investigated.
-A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient.
-The calculation of this parameter should be based on physical insights from the full transport equation, such that the resulting (transport-corrected) diffusion approximation can capture the transport phenomena of interest.
-
-% Daniele: I found this paragraph commented, but I think that the two following sections should be properly introduced in this section. Therefore, I am uncommenting it.
-The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
-The iterative scheme calculates new flux distributions using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
-Alternatively, the Coarse Mesh Finite Differences (CMFD) scheme can be enforced in the discretized form of the diffusion equation to reproduce the transport current by means of a drift term.
-The implementation of one its variants, the partial current formulation of the CMFD (pCMFD), is studied in this work.
-%
-% The direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning.
-Nonetheless, the integral current can be enforced in the Coarse Mesh Finite Difference (CMFD) discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients.
-This is the option adopted in this study.
-
-% ------------------------------------------
-\section{COARSE MESH FINITE DIFFERENCES}
-\label{sec:CMFD-intro}
-
-The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing for separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
-Recently, multi-dimensional transport codes have used it as acceleration technique and the convergence of different implementations was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
-
-The use of a coarse mesh for the discretization of the problem is generally causing considerable error by truncation applied on the finite difference approximations of the derivative terms.
-On the other hand, it yields very fast calculations.
-The CMFD method recovers corrective terms by exploiting functional relations between the (scalar) flux and the current density, which appear in the neutron balance equation.
-The balance equation is solved for the flux, so that local models seek more accurate estimates of the current in order to derive these corrections.
-In principle, the corrective terms can be computed with a different physics other than diffusion, which is always solved at the coarse level.
-This facilitates its application to accelerate complex multi-dimensional transport codes.
-This acceleration is actually implemented by rebalancing the scalar flux, with the optional use of some relaxation~\cite{Park-2017}.
-Hence, a non-linear iterative scheme arises between the CMFD solver and the computation of the local corrections, which use the latest estimates of the flux available from the diffusion solver.
-
-Second-order SPN equations can be solved by ordinary diffusion codes~\cite{Larsen-1993}.
-Yamamoto et Al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
-This is because this quantity is generally smaller than the scalar flux (0-th moment) and can change its sign.
-They proposed to modify the balance equation for the second moment in order to fix this numerical behavior.
-The modification consisted of a shift with a positive quantity of the second moment so that their difference between neighboring quantities is unchanged, and their sum becomes positive and arbitrarily large.
-
-When partial currents can be computed, the pCMFD method~\cite{Cho-2003} can be used to determine two distinct corrective terms per positive and negative partial currents, instead of having a single degree of freedom per cell surface.
-Another version of the CMFD called artificial diffusion~\cite{Zhu-2016,Jarrett-2016} redefines the diffusion coefficient as the sum of the original value and a complement derived from the current difference, which is still considered as proportional to the flux gradient.
-This scheme can potentially lead to negative diffusion constants.
-
-The CMFD (and its variants) was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
-Contrary to the previous implementations, no operator was inverted to get a new higher order approximation of the flux solution.
-As well, this offered a fast and more accurate estimate of the current too.
-
-% ------------------------------------------
-\section{THE RONEN METHOD}
-\label{sec:RM}
-
-In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux was resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}^D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
-\begin{equation}
-\label{eq:Fick}
-\bm{J}^D\rE = -D\rE\bnabla\phi\rE \cong \bm{J}\rE.
-\end{equation}
-
-Since these accurate estimates of the currents were based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
-\begin{equation}
-\label{eq:RM-it}
-D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE \rvert}{\lvert \bnabla \phi^{(k)}\rE \rvert},
-\end{equation}
-where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
-
-The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
-Nevertheless, isotropic scattering remained as a basic postulate.
-For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
-\begin{equation}
-\label{eq:RM-it-1D-slab}
-D^{(k+1)}(x,E) = \left. -\frac{1}{2} \int_0^a dx'
-{E_2[\sigma(E) \lvert x-x' \rvert]\operatorname{sign}(x-x')q^{(k)}(x',E)}
-\middle/ \frac{\partial}{\partial x}\phi^{(k)}(x,E),\right.
-\end{equation}
-where the source term $q^{(k)}$ is calculated using the multigroup diffusion model with the available scalar flux, and the updated diffusion coefficient $D^{(k+1)}$ is evaluated using the integral expression for the transport current.
-
-In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration of the simple slab problem.
-They chose the CMFD scheme in the diffusion solver for taking into account the new currents estimated by the integral transport operator.
-%
-%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
-%
-This technique can avoid indeterminate divisions in case of vanishing flux gradients and reproduces the transport effects under a drift term.
-It was observed that the RM could drive the flux distribution closer to the transport reference solution.
-As expected, the largest errors were located near the boundary, where the transport effects are more pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
-
-% ------------------------------------------
-\section{NUMERICAL IMPLEMENTATION}
-\label{sec:RM-num}
-
-The neutron balance equation for a $k$-eigenvalue problem integrated in the $i$-th element of a one-dimensional mesh is (see Fig.~\ref{fig:mesh1D})
-\begin{equation}
-\label{eq:balance}
-J_{i+\hzi ,g} - J_{i-\hzi ,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
-\end{equation}
-where $J$ denotes the net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
-\begin{equation}
-\label{eq:qsrc}
-q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
-\frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'},
-\end{equation}
-where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the effective multiplication factor (the eigenvalue), $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
-As well, integer and rational subscripts indicate node-averaged and interface quantities, respectively.
-%
-\begin{figure}[htbp]
-	\centering
-	\begin{tikzpicture}
-	\tikzstyle{every node}=[font=\footnotesize]
-	\draw[thick] (0,0) -- (3,0);
-	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
-	\draw[thick] (4,0) -- (7,0);
-	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
-	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};
-
-	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-\hzi$};
-	\node[anchor=south] at (1cm,1pt) {0};
-	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+\hzi$};
-
-	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-\hzi$};
-	\node[anchor=south] at (5.5cm,1pt) {$i$};
-	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+\hzi$};
-
-	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-\sfrac{3}{2}$};
-	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
-	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-\hzi$};
-	\end{tikzpicture}
-	\caption{Notation of the one-dimensional mesh.}
-	\label{fig:mesh1D}
-\end{figure}
-
-The net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
-\begin{subequations}
-	\label{eq:par-curr-calc}
-	\begin{equation}
-	\label{eq:par-curr-calc-plus}
-	\begin{split}
-	\jp_{i+\hzi,g} &=  \frac{1}{2}
-	E_3[\mcL_g(x_{-\hzi},x_{i+\hzi})] \phi_{x_{-\hzi},g} \\
-	& + \frac{1}{2}\sum\limits_{j=0}^i \frac{q_{j,g}}{\sigma_{j,g}}
-	\left\{ E_3\left[ \mcL_g(x_{j+\hzi},x_{i+\hzi}) \right]
-	- E_3\left[ \mcL_g(x_{j-\hzi},x_{i+\hzi}) \right]
-	\right\}
-	\end{split}
-	\end{equation}
-	%
-	\begin{equation}
-	\begin{split}
-	\label{eq:par-curr-calc-minus}
-	\jm_{i+\hzi,g} &=  \frac{1}{2}
-	E_3[\mcL_g(x_{i+\hzi},x_{I-\hzi})] \phi_{x_{I-\hzi},g} \\
-	& + \frac{1}{2}\sum\limits_{j=i+1}^{I-1} \frac{q_{j,g}}{\sigma_{j,g}}
-	\left\{ E_3\left[ \mcL_g(x_{i+\hzi},x_{j-\hzi}) \right]
-	- E_3\left[ \mcL_g(x_{i+\hzi},x_{j+\hzi}) \right]
-	\right\},
-	\end{split}
-	\end{equation}
-	where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$, $\forall i$.
-Only the zeroth moment of the angular flux, that is the scalar flux after an expansion in angle on the spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
-\eqs{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
-This is the main assumption of the Ronen Method.
-\end{subequations}
-% \daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
-
-% ------------------------------------------
-\subsection{CMFD IMPLEMENTATION}
-\label{sec:RM-CMFD}
-
-In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
-Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime \cite{Smith-1983}.
-Besides, the net current can be determined from some other expression which is physically or numerically more accurate.
-Therefore, this new term acts as a correction for the diffusion current.
-The diffusion current is generally approximated by finite differences according to
-\begin{equation}
-\label{eq:JD}
-\jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
-\frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
-\end{equation}
-where the diffusion coefficient at the interface is volume-averaged as
-\begin{equation}
-\label{eq:Ds}
-D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
-{\Delta_i + \Delta_{i+1}}.
-\end{equation}
-%
-About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
-In linearly anisotropic problems, the net current can also be considered to compute the source.
-Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
-The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
-\begin{equation}
-\label{eq:dJ}
-\delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
-\frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
-J_{i+\hzi,g} - \jD_{i+\hzi,g},
-\end{equation}
-for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
-
-Boundary conditions applies on the diffusion current as usual by means of an extrapolated length $\zeta$, $\zeta \jD \cong D \phi$.
-Mark or Marshak approximations, or other constants derived from transport theory can be used for $\zeta$ \cite{meghreblian1960reactor}.
-About the correction terms instead, it is simply $\delta J = -\delta D \phi$ with the boundary flux approximated at first order by the cell-averaged value.
-
-% ------------------------------------------
-\subsection{pCMFD IMPLEMENTATION}
-\label{sec:RM-pCMFD}
-
-The CMFD introduces in the numerical scheme a free parameter per cell surface through the correction term to adjust the diffusive solution locally.
-Since separate calculations of the partial currents are possible, two free parameters could be used in the discretized form of the diffusion equation.
-This idea leads to the development of the pCMFD scheme \cite{cho2003comparison}.
-
-Two corrective terms are then introduced: $J = \jp - \jm = \jD + \delta J^+ + \delta J^-$.
-An upwind definition with respect to the direction of flight of neutrons is used for the corrections~\cite{Jarrett-2016,Zhu-2016}:
-\begin{equation}
-\label{eq:CCF-sub}
-\delta \jp _{i+\hzi} = -\delta D^+ _{i+\hzi} \phi_i
-\quad \text{and} \quad
-\delta \jm _{i+\hzi} = -\delta D^- _{i+\hzi} \phi_{i+1}.
-\end{equation}
-The current by diffusion is distributed on the partial currents in equal parts in order to compute the new corrective coefficients $\delta D^{\pm}$,
-\begin{subequations}
-	\label{eq:delta-D-pCMFD}
-	\begin{align}
-	J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= -\delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
-	J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
-	\end{align}
-\end{subequations}
-still for $i=0, \ldots, I-2$.
-The diffusion current is not halved at the boundary, using only \eq{eq:delta-D-pCMFDm} or \eq{eq:delta-D-pCMFDp} at the left and at the right boundaries, respectively.
-Finally, the implementation of CMFD can be upgraded to support the pCMFD scheme with minimal changes.
-% -----------------------------------------------------------------------------
-%
-% Daniele: the following proposition has shown to be inconsistent.
-%
-% Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
-% \begin{equation}
-% \label{eq:partial-current}
-% \jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
-% \end{equation}
-% still verifying the expression for the net current $J = J^+ - J^-$.
-\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
-% \begin{equation}
-%   \label{eq:PCCF}
-%   \jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
-%     \left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
-% \end{equation}
-% and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
-% \begin{equation}
-% \label{eq:CCF-sub}
-% \delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
-% \quad \text{and} \quad
-% \delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
-% \end{equation}
-% %
-% Solving for the partial current correction factors gives
-% \begin{equation}
-%   \label{eq:ccfsss1}
-%   \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
-%   	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
-%   \quad \text{and} \quad
-%   \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
-%   	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
-%   \end{equation}
-% where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.
-% -----------------------------------------------------------------------------
-
-In a weakly absorbing medium and several mean free paths away from the boundary or a strong absorber, all correction factors $\delta D^\pm$ are expected to vanish and the net current must be fully reproduced by the diffusion current.
-Of course, this must be verified by the classic CMFD scheme too.
-
-% ------------------------------------------
-\section{RESULTS}
-\label{sec:res}
-
-% ------------------------------------------
-\section{CONCLUSIONS}
-\label{sec:conc}
-
-Present your summary and conclusions here.
-
-%\begin{figure}[!htb]
-%  \centering
-%  \includegraphics[scale=0.60]{./Figures/figure.pdf}
-%  \caption{SCALE/TRITON-NEWT Model of BWR Assembly in Order to Show and Example of a Figure and a Multi-line Caption}
-%  \label{fig:amdahl}
-%\end{figure}
-
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item Any number, text or symbol is in Times font and is not smaller than
-%  10-point after reduction to the actual window in your paper
-%\item That it can be translated into PDF
-%\end{itemize}
-
-%\begin{table}[!htb]
-%  \centering
-%  \caption{\bf Parallel Performance for the Sample Problem}
-%  \label{table:example}
-%  \begin{tabular}{|c|c|c|c|} \hline
-%   Number of & Wall-Clock & Speedup & Efficiency \\
-%   Processors & Time$^{a}$ (min) & (T$_{s}$/T$_{p}$) & (\%) \\ \hline
-%    \ 1 &  100.0 & \ ---    & ---  \\ \hline
-%    \ 2 &   52.6 & \ 1.9    & 95.0 \\ \hline
-%  \end{tabular}
-%\end{table}
-
-% ------------------------------------------
-% Daniele: I would avoid the following section about the nomenclature because of the 8 pages limit. The acronyms are already explained in the text.
-%\section*{NOMENCLATURE}
-%
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item RM - Ronen Method
-%\item CMFD - Coarse Mesh Finite Difference
-%\item pCMFD - partial current CMFD
-%\end{itemize}
-%
-% ------------------------------------------
-%\section*{ACKNOWLEDGEMENTS}
-%
-%Acknowledge the help of colleagues and sources of funding, as appropriate.
-%
-% ------------------------------------------
-% You can enter a bibliography into the document using the following format, or use the
-% bibliography style file "physor.bst" found in the template directory.  You can use the bibliography style file
-% by replacing the current bibliography block with:
-\setlength{\baselineskip}{12pt}
-\bibliographystyle{physor}
-\bibliography{RM-bib}
-
-% ------------------------------------------
-%\appendix
-%\gdef\thesection{APPENDIX \Alph{section}}
-%\section{Sample Appendix 1}
-%\label{app:a}
-%If necessary, include Appendices numbered in upper case alphabetical order. This is \ref{app:a}.
-%
-\end{document}

### 2020-01-13 docs/ANE2020/pCMFD_notes/pCMFD-Erez-impl.tex
rename the PHYSOR2020 folder to agree with the new publication goal

\documentclass[%
%reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
%aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{xfrac}
\usepackage{mathtools}

\newcommand{\eq}[1]{Eq.~(\ref{#1})}
\newcommand{\eqnolabel}[1]{(\ref{#1})}
\newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
\newcommand{\eqsthru}[2]{Eqs.~(\ref{#1})--(\ref{#2})}
\newcommand{\eqsand}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
\newcommand{\tbl}[1]{Table~\ref{#1}}
\newcommand{\tblnolabel}[1]{\ref{#1}}
\newcommand{\tbls}[1]{Tables~\ref{#1}}
\newcommand{\tblsthru}[2]{Tables~\ref{#1}--\ref{#2}}
\newcommand{\tblsand}[2]{Tables~\ref{#1} and \ref{#2}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\fignolabel}[1]{\ref{#1}}
\newcommand{\figs}[1]{Figs.~\ref{#1}}
\newcommand{\figsthru}[2]{Figs.~\ref{#1}--\ref{#2}}
\newcommand{\figsand}[2]{Figs.~\ref{#1} and \ref{#2}}
\newcommand{\sxn}[1]{Section~\ref{#1}}

\newcommand{\keff}{{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}}
\newcommand{\beff}{\ensuremath{\beta_{\textrm{eff}}}}
\newcommand{\rr}{\ensuremath{\bm{r}}}
\newcommand{\OO}{\ensuremath{\hat{\bm{\Omega}}}}
\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
\newcommand{\rE}{\ensuremath{(\rr,E)}}

\newcommand{\ftr}{\ensuremath{\phi_{\textrm{\scriptsize{tr}}}}}
\newcommand{\jtr}{\ensuremath{\bm{J}_{\textrm{\scriptsize{tr}}}}}
\newcommand{\jtrr}{\ensuremath{J_{\textrm{\scriptsize{tr}}}}}
%\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcL}{\tau}
%\newcommand{\pl}[1]{\ensuremath{P_l(#1)}}
\newcommand{\dx}{\ensuremath{\Delta x}}

\newcommand{\jp}{\ensuremath{J^+}}
\newcommand{\jm}{\ensuremath{J^-}}
\newcommand{\jpm}{\ensuremath{J^\pm}}
\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
\newcommand{\bmj}{\ensuremath{\bm{J}}}
% \newcommand{\jp}{\ensuremath{\bm{J}^+}}
% \newcommand{\jm}{\ensuremath{\bm{J}^-}}
% \newcommand{\jpm}{\ensuremath{\bm{J}^\pm}}
% \newcommand{\jD}{\ensuremath{\bm{J}^{\textrm{\scriptsize{D}}}}}

\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}

\begin{document}

%	\preprint{APS/123-QED}

	\title{The Ronen Method by pCMFD}% Force line breaks with \\
%	\thanks{A footnote to the article title}%

	\author{Roy Gross}
	\affiliation{The Unit of Nuclear Engineering \\
		Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel}	
	\author{Daniele Tomatis}
	\affiliation{CEA, DEN, Service d’\'etudes des r\'eacteurs et
		de math\'ematiques appliqu\'ees (SERMA) \\
		Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France}%	
	\author{Erez Gilad}
	\email{gilade@bgu.ac.il}
	\affiliation{The Unit of Nuclear Engineering \\
		Ben-Gurion University of the Negev, 8410501 Beer-Sheva, Israel}%

	\date{\today}% It is always \today, today,
	%  but any date may be explicitly specified

	\begin{abstract}
		Numerical details of the implementation of the pCMFD for the RM.
	\end{abstract}

	%\keywords{Suggested keywords}%Use showkeys class option if keyword
	%display desired
	\maketitle

	%\tableofcontents

% ------------------------------------------	
\section{The balance equation}

	The neutron balance equation for a $k$-eigenvalue problem integrated in the $i$-th element of a one-dimensional mesh is
	\begin{equation}
		\label{eq:balance}
		J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
	\end{equation}
	where $J$ denotes the accurate net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
	\begin{equation}
		\label{eq:qsrc}
		q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
		\frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'},
	\end{equation}
	where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the effective multiplication factor (the eigenvalue), $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section. As well, integer and rational subscripts indicate node-averaged and interface quantities, respectively.

% ------------------------------------------
\subsection{CMFD IMPLEMENTATION} 
\label{sec:RM-CMFD}

	In standard CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$. Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime. Besides, the net current can be determined from some other expression which is physically or numerically more accurate. Therefore, this new term acts as a correction for the diffusion current. The diffusion current is generally approximated by finite differences according to
\begin{equation}
	\label{eq:JD}
	\jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
	\frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
\end{equation}
where the diffusion coefficient at the interface is volume-averaged as
\begin{equation}
	\label{eq:Ds}
	D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
	{\Delta_i + \Delta_{i+1}}.
\end{equation}
%
About the RM, more accurate estimates of the net current come from the integral expressions, still using the scalar flux in the emission source $q_{i,g}$. Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces. The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
\begin{equation}
	\label{eq:dJ}
	\delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
	\frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
	J_{i+\hzi,g} - \jD_{i+\hzi,g}.
\end{equation}
The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary. Boundary conditions applies as usual on the diffusion current and on the net (more accurate) current, without any particular change for the definition of the correction term.

% ------------------------------------------
\subsection{pCMFD IMPLEMENTATION} 
\label{sec:RM-pCMFD}

The CMFD introduces a free parameter in the numerical scheme through the correction term to adjust the diffusive solution locally. Since separate calculations of the partial currents are possible, two free parameters could be used in the discretized form of the diffusion equation.

Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
\begin{equation}
	\label{eq:partial-current}
	\jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
\end{equation}
still verifying the expression for the net current $J = J^+ - J^-$.
\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
\begin{equation}
	\label{eq:PCCF}
	\jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
	\left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
\end{equation}
and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
\begin{equation}
	\label{eq:CCF-sub}
	\delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
	\quad \text{and} \quad
	\delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
\end{equation}
Solving for the partial current correction factors gives
\begin{equation}
	\label{eq:ccfsss1}
	\delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
		+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
	\quad \text{and} \quad
	\delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
		+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
\end{equation}
where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.

% ------------------------------------------
\section{The discretized equation} 
\label{sec:disc}

Substituting~\eq{eq:PCCF} into the balance equation~\eq{eq:balance}
\begin{equation}
\label{eq:balance+jpm}
\frac{1}{4} \phi_{i+\hzi} + \frac{1}{2}
\left(\jD_{i+\hzi} + \delta \jp_{i+\hzi}\right)
-\left[
\frac{1}{4} \phi_{i-\hzi} - \frac{1}{2}
\left(\jD_{i-\hzi} + \delta \jm_{i-\hzi}\right)
\right]
+\sigma_i\phi_i = q_i.
\end{equation}
Recalling Eqs.~\eqref{eq:JD},~\eqref{eq:Ds}, and~\eqref{eq:CCF-sub}
\begin{align}
\label{eq:balance-2}
\frac{1}{4} \phi_{i+\hzi} &+ \frac{1}{2}
\left(
- D_{i+\hzi}
\frac{\phi_{i+1} - \phi_{i}}{(\Delta_{i+1} + \Delta_i)/2}  -2\delta D^+ _{i+\hzi} \phi_i
\right) \nonumber \\
&-\left[
\frac{1}{4} \phi_{i-\hzi} - \frac{1}{2}
\left(
- D_{i-\hzi}
\frac{\phi_{i} - \phi_{i-1}}{(\Delta_{i} + \Delta_{i-1})/2}
 -2\delta D^- _{i-\hzi} \phi_{i}
 \right)
\right]
+\sigma_i\phi_i = q_i.
\end{align}
Define $\tilde{D}_{i+\hzi}\coloneqq D_{i+\hzi} / (\Delta_{i+1}+\Delta_i)$, 
\begin{align}
\label{eq:balance-3}
\frac{1}{4} \phi_{i+\hzi} 
&-\tilde{D}_{i+\hzi}(\phi_{i+1} - \phi_{i})
  -\delta D^+ _{i+\hzi} \phi_i
\nonumber \\
&-\frac{1}{4} \phi_{i-\hzi} 
- \tilde{D}_{i-\hzi}(\phi_{i} - \phi_{i-1}) 
-\delta D^- _{i-\hzi} \phi_{i}
+\sigma_i\phi_i = q_i.
\end{align}
Recalling that the flux on the interface is volume-averaged, i.e.,
\begin{equation}
\label{eq:flxs}
\phi_{i+\hzi} = \frac{\Delta_i \phi_{i} + \Delta_{i+1} \phi_{i+1}}
{\Delta_i + \Delta_{i+1}},
\end{equation} 
then
\begin{eqnarray}
\label{eq:quarter-flx}
\frac{1}{4} \phi_{i+\hzi} &=& \frac{1}{4} \frac{1}{\Delta_i + \Delta_{i+1}}
(\Delta_i \phi_{i} + \Delta_{i+1} \phi_{i+1}) \nonumber \\
-\frac{1}{4} \phi_{i-\hzi} &=& -\frac{1}{4} \frac{1}{\Delta_{i-1} + \Delta_{i}}
(\Delta_{i-1} \phi_{i-1} + \Delta_{i} \phi_{i}) .
\end{eqnarray}
Substituting Eq.~\eqref{eq:quarter-flx} into Eq.~\eqref{eq:balance-3} and collecting terms
\begin{align}
\label{eq:balance-4}
&\left[
- \tilde{D}_{i-\hzi} - \frac{1}{4} \frac{\Delta_{i-1}}{\Delta_{i-1} + \Delta_{i}}
\right] \phi_{i-1} 
+ 
\left[
- \tilde{D}_{i+\hzi} + \frac{1}{4} \frac{\Delta_{i+1}}{\Delta_{i} + \Delta_{i+1}}
\right] \phi_{i+1} \nonumber \\
&+	
\left[
\frac{1}{4} \frac{\Delta_{i}}{\Delta_{i} + \Delta_{i+1}}
- \frac{1}{4} \frac{\Delta_{i}}{\Delta_{i-1} + \Delta_{i}}
+\tilde{D}_{i+\hzi}
-\tilde{D}_{i-\hzi}
-\delta D^+ _{i+\hzi}
-\delta D^- _{i-\hzi}
+ \sigma_i
\right] \phi_i = q_i .
\end{align}

% ------------------------------------------
\bibliography{../RM-bib}% Produces the bibliography via BibTeX.

\end{document}

### 2020-01-19 docs/PHYSOR2020/figures/plot_data.py
Update plot_data.py

@@ -34,8 +34,8 @@ Plot_flx_cvg  = False
 Plot_dD       = False
 Plot_err      = False
 Plot_k        = False
-plot_flx_zoom = False
-Plot_rho      = True
+plot_flx_zoom = True
+Plot_rho      = False
 
 I = 400 # No. of mesh points
 dx = 21.5/I
@@ -281,71 +281,120 @@ if Plot_k:
 # ================== Flux zoon-in ================== #
 # ================================================== #
 if plot_flx_zoom:
-    fig = plt.subplots(figsize=(14,11))
-    ax1 = plt.subplot(2,1,1)
-    ax1.tick_params(axis='both', which='major', labelsize=24)
-    ax1.tick_params(axis='both', which='minor', labelsize=24)
-    plt.plot(xim[199::5], flx_RM1[0,199::5,-1],':r^',label='RM-CMFD')
-    plt.plot(xim[199:],   flx_RM1[0,199:,0],'g--',label='$D_0$')
-    plt.plot(xim[199::5], flx_RM2[0,199::5,-1],'b-*',label='RM-pCMFD')
-    plt.plot(xim[199:],   flx_SN[0,199:],'k-',label='S16')
-    #plt.yticks(np.linspace(-0.1,0.1,5)) # x-axis valus represent fuel assembly
-    plt.setp(ax1.get_xticklabels(), visible=False)
-    plt.ylabel(r'$\phi_1$ $[AU]$',fontsize=24)
-    plt.grid(True,'both','both')
-    ax1.legend(loc='lower left',fontsize=20,ncol=4)
-    #plt.yticks(np.linspace(6, 50,5)) # apply the y-limits
-    plt.ylim(min(flx_SN[0,:]-0.5), max(flx_SN[0,:])+1.5)
-    # -------------------- 1st zoomin --------------------
-    axins1 = zoomed_inset_axes(ax1, 3.3, loc="upper right")
-    axins1.plot(xim[379::5], flx_RM1[0,379::5,-1],':r^')
-    axins1.plot(xim[379:],   flx_RM1[0,379:,0],'g--')
-    axins1.plot(xim[379::5], flx_RM2[0,379::5,-1],'b-*')
-    axins1.plot(xim[379:],   flx_SN[0,379:],'k-')
-    axins1.set_xlim(xim[383], xim[-1]+0.05) # apply the x-limits
[…]

### 2020-01-19 docs/ANE2020/figures/plot_data.py
Moved files
Moved plot_data to ANE2020.
Added plot of the left boundary over iteration no.

@@ -36,7 +36,7 @@ Plot_err      = False
 Plot_k        = False
 plot_flx_zoom = True
 Plot_rho      = False
-
+Plot_LB       = False
 I = 400 # No. of mesh points
 dx = 21.5/I
 itr = 250 # No. of iterations
@@ -358,43 +358,62 @@ if plot_flx_zoom:
     
     plt.figure(figsize=(14, 5)) 
     fig, ax = plt.subplots(G,figsize=(14, 9))
-    
+    #axins = 
+    #axins = fig.add_subplot(ax[G-1], 3.3)
     for g in range (0,G):
     
         ax[g].tick_params(axis='both', which='major', labelsize=fsz)
         ax[g].tick_params(axis='both', which='minor', labelsize=fsz)
         ax[g].set_prop_cycle(default_cycler)
         
-        ax[g].plot(tau_m[g,0:I//2+1], flx_RM1[g,0:I//2+1,-1],label='RM-CMFD')
-        ax[g].plot(tau_m[g,0:I//2+1], flx_RM1[g,0:I//2+1,0],label='$D_0$')
-        ax[g].plot(tau_m[g,0:I//2+1], flx_RM2[g,0:I//2+1,-1],label='RM-pCMFD')
-        ax[g].plot(tau_m[g,0:I//2+1], flx_SN[g,0:I//2+1],label='S16')
-        ax[g].set_xticks(tau_m[g,0:(I//2+1):25])
+        ax[g].plot(tau_m[g,I//2::5], flx_RM1[g,I//2::5,-1],label='RM-CMFD')
+        ax[g].plot(tau_m[g,I//2:], flx_RM1[g,I//2:,0],label='$D_0$')
+        ax[g].plot(tau_m[g,I//2::5], flx_RM2[g,I//2::5,-1],label='RM-pCMFD')
+        ax[g].plot(tau_m[g,I//2:], flx_SN[g,I//2:],label='S16')
+        ax[g].set_xticks(tau_m[g,199::25])
         #ax[g].set_xticks(tau_m[g,I//2],tau_m[g,-1])
-        ax[g].set_xlim(tau_m[g,0], tau_m[g,I//2+1])
+        ax[g].set_xlim(tau_m[g,199], tau_m[g,-1])
         ax[g].grid(True,'both','both')
         ax[g].legend(loc='lower center',fontsize=fsz//1.5,ncol=4)
         ax[g].xaxis.set_major_formatter(mtick.FormatStrFormatter('%.2f'))
[…]

### 2020-01-20 docs/ICTT2019/RMethod_ictt26.tex

@@
 Contrary to other formulations, we do not include $\mu$ in the definition of the optical length to ease the numerical integrations in the following.
-$x_b = x_{-1/2} = a$ if $\mu > 0$, $x_b = x_{I-1/2} = b$ otherwise.
+$x_0 = x_{-1/2} = a$ if $\mu > 0$, $x_0 = x_{I-1/2} = b$ otherwise.
 The inclusion of the energy variable in Eq.
-\ref{eq:NTE} is straightforward; we use hereafter the multi-group theory, writing the source $q_g$ as\footnote{Curly brackets remind the possible use of the $k$-eigenvalue with vanishing external sources.}:
+\ref{eq:NTE} is straightforward; we use hereafter the multi-group theory, writing the source $q_g$ as\footnote{Curly brackets remind the possible use of the $k$-eigenvalue in case of vanishing external sources.}:
 \begin{equation*}
@@
 where the subscript $l$ refers to the moments of the expansions of the flux and of the scattering cross section on the Legendre polynomials $P_l$.
-Fission emission is isotropic, so that the scalar flux $\phi$ is equal to half of the first moment $\varphi_0$.
+Fission emission is isotropic, so that the scalar flux $\phi$ is equal to the first moment $\varphi_0$.
 Without the external source $S$, the multiplication factor $k$ is used as eigenvalue to avoid the trivial vanishing solution.

### 2020-01-21 docs/ANE2020/contents.tex
rename the PHYSOR2020 folder to agree with the new publication goal
Results of homogeneous case
Added results to ANE-2020 tex file.

--- 2020-01-08 docs/PHYSOR2020/contents.tex
@@
 \end{equation}
+It can be noted that the signs before the correction terms are arbitrary, with no need to follow a specific physical meaning. 
 %
@@
 
-xy
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_I400_RMitr250.pdf}
+	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD, RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$).
+The insets show a zoom-in of the fluxes near the boundary.
+Results shown here after 250 Ronen iterations and 400 cells.}
+	\label{fig:slab-fluxes}		
+\end{figure}
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
+	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($\delta D^+, \delta D^-$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
+	\label{fig:slab-RM-corr-factor}
+\end{figure}
+
+\begin{figure}[htbp]
+	% convergence
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_k_over_I400_RMitr250.pdf}	
+	\caption{Convergence of the criticality eigenvalue along 250 Ronen iterations.}
+	\label{fig:conv}
+\end{figure}
+
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
+	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
+	\label{fig:conv3}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
+	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
+	\label{fig:slab-fluxes-dev}
+\end{figure}
 % ------------------------------------------

### 2020-01-21 docs/ANE2020/figures/Tomatis2011_ANE2020.py

@@ -22,7 +22,7 @@ default_cycler = (cycler(color=['r', 'g', 'b', 'y']) *
                   #*
                   cycler(linestyle=['-', '--', ':', '-.']) 
                   )
-                  
+
 rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
 rc('text', usetex=True)
 fsz = 24. # font size
@@ -38,19 +38,20 @@ plot_flx_zoom = True
 Plot_rho      = False
 Plot_LB       = False
 I = 400 # No. of mesh points
-dx = 21.5/I
+#dx = 21.5/I
 itr = 250 # No. of iterations
 #ccng = 3 # Core configuration (Rahnema1997)
 # ------ Load flx_RM? ------
 plot_RM = True
 if plot_RM:
     ''' Upload one file '''
-    path_RM_flx_file1 = "../../../FD1dMGdiff/output/kflx_MC2011_LBC0RBC0_CMFD_I400_ritr250.npy"
-    path_RM_flx_file2 = "../../../FD1dMGdiff/output/kflx_MC2011_LBC0RBC0_pCMFD_I400_ritr250.npy"
-    
+    path_RM_flx_file1 = "kflx_MC2011_LBC0RBC0_CMFD_I400_it250.npy"
+    path_RM_flx_file2 = "kflx_MC2011_LBC0RBC0_pCMFD_I400_it250.npy"
+    #path_RM_flx_file3 = "../../../FD1dMGdiff/output/kflx_MC2011_LBC0RBC0_I400_it10.npy"
         #data = np.load(path_RM_flx_file)
     k_RM1, flx_RM1, xi1, st, dD1 = np.load(path_RM_flx_file1,allow_pickle=True)
     k_RM2, flx_RM2, xi2, st, dD2 = np.load(path_RM_flx_file2,allow_pickle=True)
+    #cCMFD = np.load(path_RM_flx_file3,allow_pickle=True)
     xi = xi2
 
 # ------ Load flx_SN? ------
@@ -71,7 +72,7 @@ if plot_SN:
     RR_SN = sum(np.multiply(flxm,st).flatten())
     RR_RM1 = sum(np.multiply(flx_RM1[:,:,-1],st).flatten())
     flx_SN = (RR_RM1/RR_SN)*flxm
-       
+
 # ------ General ------
 xim = (xi[1:] + xi[:-1]) / 2.# mid-cell points
 G = st.shape[0]
@@ -86,7 +87,7 @@ G = st.shape[0]
[…]

### 2020-01-22 docs/ICTT2019/RMethod_ictt26.tex
fix a few mistakes and typoes in the ICTT manuscript; add the linearly anisotropic scattering term in the source of the integral equation estimating the current.

@@
 
-\DeclareMathOperator{\sign}{sign}
+\DeclareMathOperator{\sign}{sgn}
 \newcommand{\pluseq}{\mathrel{+}=}
@@
 with the optical length $\tau(x_1, x_2) = \int_{x_1}^{x_2}{dx' \sigma_t(x')}$.
-Contrary to other formulations, we do not include $\mu$ in the definition of the optical length to ease the numerical integrations in the following.
-$x_0 = x_{-1/2} = a$ if $\mu > 0$, $x_0 = x_{I-1/2} = b$ otherwise.
+Contrary to other formulations, we do not include the direction cosine of the neutron velocity $\mu$ in the definition of the optical length to ease the numerical integrations in the following.
+Eq.
+\ref{eq:NTE} holds for both positive directions $(\mu > 0)$ where $x_0 = x_{-1/2} = a$, and negative ones $(\mu > 0)$ where $x_0 = x_{I-1/2} = b$.
 The inclusion of the energy variable in Eq.
 \ref{eq:NTE} is straightforward; we use hereafter the multi-group theory, writing the source $q_g$ as\footnote{Curly brackets remind the possible use of the $k$-eigenvalue in case of vanishing external sources.}:
-\begin{equation*}
+\begin{equation}
+\label{eq:srcg}
 q_g = \sum_{g'=1}^G{\left[
@@
                  },
-\end{equation*}
+\end{equation}
 where the subscript $l$ refers to the moments of the expansions of the flux and of the scattering cross section on the Legendre polynomials $P_l$.
-Fission emission is isotropic, so that the scalar flux $\phi$ is equal to the first moment $\varphi_0$.
+Fission emission is isotropic, so that only the scalar flux $\phi$ being equal to the first moment $\varphi_0$ is retained for the fission term.
 Without the external source $S$, the multiplication factor $k$ is used as eigenvalue to avoid the trivial vanishing solution.
-Since $q$ is computed by the results of the diffusion equation in the Ronen method, $l$ can only assume the values 0 and 1.
-Hereafter we consider only isotropic sources.
+Since $q$ is computed by the results of the diffusion equation in the Ronen method, $l$ can only assume the values 0 and 1.% Hereafter we consider only isotropic sources.
 
 Multiplication of Eq.
-\ref{eq:NTE} by the direction cosine of the neutron velocity $\mu$ and the integration over $[-1, 1]$ provides the expression for the current, see \cite{tomatis2011application}.
+\ref{eq:NTE} by $\mu$ and the integration over $[-1, 1]$ provides the expression for the current, see \cite{tomatis2011application}.
 The integration on $\mu$ yields integral exponential functions by a simple change of variable ($\mu = \pm 1/u$, according to the sign of $\mu$) \cite{AS1964handbook}:
@@
 % J_g(x_{i+1/2}) &=
-J_{g,i+1/2} &= \int_0^1 {d\mu\, \mu \varphi_g(a, \mu) e^{-\tau_g(a, x_{i+1/2})/\mu}}
+J_{g,i+1/2} &= \int_0^{ 1}{d\mu\, \mu \varphi_g(a, \mu) e^{-\tau_g(a, x_{i+1/2})/\mu}}
              - \int_0^{-1}{d\mu\, \mu \varphi_g(b, \mu) e^{-\tau_g(b, x_{i+1/2})/\mu}}\\
-       & + \sum_{j=0}^{I-1} { \sign(x_{i+1/2} - x_{j+1/2}) \frac{q_{0,g,j}}{2} \int_{x_{j-1/2}}^{x_{j+1/2}}{dx' E_{2}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) } }.
+  & + \sum_{j=0}^{I-1} \left[  \sign(x_{i+1/2} - x_{j+1/2}) \frac{q_{0,g,j}}{2} \int_{x_{j-1/2}}^{x_{j+1/2}}{dx' E_{2}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) } \right.\\
+  & \left. \qquad+ \frac{3}{2}q_{1,g,j} \int_{x_{j-1/2}}^{x_{j+1/2}}{dx' E_{3}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) }\right],
 \end{split}
@@
 \end{equation}
-The $g$-th source $q_{g,j}$ is the volume-average in the cell $j$.
+where $q_{(.),g,j}$ are the moments of the souce $q_g$ from Eq. \ref{eq:srcg} averaged in the volume of the $j$-th cell:
+\begin{equation*}
+\label{eq:srclg}
+\begin{split}
+   q_{0,g,j} &= \sum_{g'}\left(\sigma_{s,0,g' \rightarrow g,j} +
+                              \chi_g \nu\sigma_{f,g',j}
+                        \right) \phi_{g',j},\\
+   q_{1,g,j} &= \sum_{g'}\sigma_{s,1,g' \rightarrow g,j}J_{g',j}.
+\end{split}
+\end{equation*}
+The current appearing in $q_{1,g,j}$, that is in case of linearly anisotropic scattering, is also to be considered as volume-averaged in the cell $j$.
 The optical lengths show the subscript $g$ because they are evaluated with the corresponding total cross section $\sigma_{t,g}$.
-For the property $E'_{n+1}(\ell) = -E_n(\ell)$, the spatial integral of the $E_2$ function can be solved analytically by integrating on $\tau$:
+For the property $E'_{n+1}(\ell) = -E_n(\ell)$, the spatial integrals of the integral exponential functions can be solved analytically by integrating on $\tau$:
 \begin{equation*}
@@
 \int_{x_{j-1/2}}^{x_{j+1/2}}{ dx' E_{n}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) } =
-\frac{\sign(x_{i+1/2} - x_{j+1/2})}{\sigma_{t,g}} \cdot \\
+\frac{\sign(x_{i+1/2} - x_{j+1/2})}{\sigma_{t,g,j}} \cdot \\
 \left[
@@
 \end{equation*}
-These quantities can be computed only for $i > j$ since the others are simply opposite in sign.
+These quantities can be computed for $i > j$ only, because the others are simply opposite in sign.
 

### 2020-01-22 FD1dMGdiff/FDsDiff1D.py
upgrade the module FD*.py to use (linear) scattering anisotropy in the source of the integral transport equation (for the current); restore former tests.

@@ -247,12 +247,12 @@ def solveTDMA(a, b, c, d):
 
 
 def compute_fission_source(chi, nsf, flx):
-    # the input flux must be volume-integrated
+    # warning: the input flux can be volume-integrated or not
     return (chi * np.sum(nsf * flx, axis=0)).flatten()
 
 
 def compute_scattering_source(ss0, flx):
-    # the input flux must be volume-integrated
+    # warning: the input flux can be volume-integrated or not
     return np.sum(ss0 * flx, axis=1).flatten()
 
 
@@ -277,6 +277,17 @@ def compute_cell_volumes(xi, geo=None):
         else:
             raise ValueError("Unknown geometry type " + geo)
     return Di
+
+
+def first_order_coeff_at_interfaces(f, Vi):
+    """Compute the diffusion coefficient by 1st order finite-difference
+    currents determined at both sides of an interface."""
+    G, I = f.shape
+    Im1 = I - 1
+    
+    fb = 2 * f[:, 1:] * f[:, :-1]
+    return fb / (f[:, 1: ] * np.tile(Vi[:-1], G).reshape(G, Im1) +
+                 f[:, :-1] * np.tile(Vi[1: ], G).reshape(G, Im1))
 
 
 def vol_averaged_at_interface(f, Vi):
@@ -422,60 +433,78 @@ def opl(j, i, Ptg):
     return np.sum(Ptg[j:i+1])
 
 
-def compute_tran_currents(flx, k, Di, xs, BC=(0, 0), L=1):
+def compute_tran_currents(flx, k, Di, xs, BC=(0, 0), curr=None):
     """Compute the partial currents given by the integral transport equation
     with the input flux flx. An artificial second moment is used to match
-    vanishing current at the boundary in case of reflection."""
+    vanishing current at the boundary in case of reflection. When the input
+    current curr is provided, the linearly anisotropic term is accounted in
+    the source if anisotropic scattering cross section data are available."""
     LBC, RBC = BC
-    st, ss0, chi, nsf, Db = xs
+    st, ss, chi, nsf, Db = xs
     G, I = st.shape
-    # J = np.zeros((G,I+1),)  # currents at the cell bounds
-    Jp = np.zeros((G, I+1),)  # plus partial currents at the cell bounds
-    Jm = np.zeros_like(Jp)  # minus partial currents at the cell bounds
 
-    q = compute_source(ss0, chi, nsf, flx, k).reshape(G, I)
[…]

### 2020-01-22 FD1dMGdiff/data/homog2GMC2011.py

@@ -17,11 +17,10 @@ import logging as lg
 one_third = 1. / 3.
 
 st = np.array([0.531150, 1.30058])
-ss = np.zeros((2, 2, 2),)
+ss = np.zeros((2, 2, 1),)
 ss0 = np.array([[0.504664, 0.00203884], [0.0162955, 1.19134]])
-ss1 = np.array([[0., 0.], [0., 0.]])
-ss1 *= one_third
-ss[:,:,0], ss[:,:,1] = ss0, ss1
+ss1 = np.array([[0., 0.], [0., 0.]]) * one_third
+ss[:,:,0] = ss0  # ss[:,:,0], ss[:,:,1] = ss0, ss1
 nsf = np.array([0.00715848, 0.141284])
 chi = np.array([1., 0.])
 

### 2020-01-22 FD1dMGdiff/FDsDiff1D.py
upgrade the module FD*.py to use (linear) scattering anisotropy in the source of the integral transport equation (for the current); restore former tests.

@@ -247,12 +247,12 @@ def solveTDMA(a, b, c, d):
 
 
 def compute_fission_source(chi, nsf, flx):
-    # the input flux must be volume-integrated
+    # warning: the input flux can be volume-integrated or not
     return (chi * np.sum(nsf * flx, axis=0)).flatten()
 
 
 def compute_scattering_source(ss0, flx):
-    # the input flux must be volume-integrated
+    # warning: the input flux can be volume-integrated or not
     return np.sum(ss0 * flx, axis=1).flatten()
 
 
@@ -422,60 +422,78 @@ def opl(j, i, Ptg):
     return np.sum(Ptg[j:i+1])
 
 
-def compute_tran_currents(flx, k, Di, xs, BC=(0, 0), L=1):
+def compute_tran_currents(flx, k, Di, xs, BC=(0, 0), curr=None):
     """Compute the partial currents given by the integral transport equation
     with the input flux flx. An artificial second moment is used to match
-    vanishing current at the boundary in case of reflection."""
+    vanishing current at the boundary in case of reflection. When the input
+    current curr is provided, the linearly anisotropic term is accounted in
+    the source if anisotropic scattering cross section data are available."""
     LBC, RBC = BC
-    st, ss0, chi, nsf, Db = xs
+    st, ss, chi, nsf, Db = xs
     G, I = st.shape
-    # J = np.zeros((G,I+1),)  # currents at the cell bounds
-    Jp = np.zeros((G, I+1),)  # plus partial currents at the cell bounds
-    Jm = np.zeros_like(Jp)  # minus partial currents at the cell bounds
 
-    q = compute_source(ss0, chi, nsf, flx, k).reshape(G, I)
+    ss0 = ss[:, :, 0, :]
+    q0 = 0.5 * compute_source(ss0, chi, nsf, flx, k).reshape(G, I)
     # divide the volume-integrated source by the cell volumes if the input
     # flux is volume-integrated
     # q /= np.tile(Di, G).reshape(G, I)
-    # The current implementation does not support yet any flux anisotropy, so
-    # q is fixed as in the following.
-    q = np.expand_dims(q, axis=0)
+    # warning: divide the source by st for the next numerical integration
+    q0 /= st  # term-by-term division
+    if curr is not None:
+        # the following will raise IndexError if ss1 is not available
[…]

### 2020-01-22 SNMG1DSlab/snmg1dslab.py

@@ -262,7 +262,7 @@ def solve_sn(idata, slvr_opts, qdata):
     '''Run SN solver.'''
     lg.info("Prepare input data")
     # xs = [st, ss, chi, nsf]
-    xs = unfold_xs(idata, isotropic_scattering=False, diff_calc=False)
+    xs = unfold_xs(idata, diff_calc=False)
     # initialize the cell-integrated flux moments
     # (which are the only unknowns stored in memory at this higher level)
     # and the multiplication factor (eigenvalue)

### 2020-01-27 docs/ANE2020/contents.tex
Added results to ANE-2020 tex file.

@@
 About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
-In linearly anisotropic problems, the net current can also be considered to compute the source.
+% In linearly anisotropic problems, the net current can also be considered to compute the source.
+<-- pure bullshit !
+Can't happen in diffusion.
 Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
@@
 \label{sec:res}
+Two test cases are shown in this section.
+The first is a one-dimensional (1-D) homogeneous plane, representing a typical fuel assembly~\cite{Tomatis-2011}.
+The second benchmark include three different cores, which are 1-D representation of a Boiling Water Reactor (BWR) configuration~\cite{Rahnema-1997}.
+Both test cases are calculated and compared by two-group nodal diffusion code (denoted as $D_0$) and the Ronen method (with the implementation of CMFD and pCMFD), and are verified against a discrete ordinates S$_N$ code, with N=16.
+For all test cases, isotropic scattering are considered.
+Therefore, the diffusion coefficients for the homogeneous case, calculated by $D_g = (3\sigma_{tr,g})^{-1} = (3\sigma_g)^{-1}$.
+Void boundary conditions, which are implemented within the diffusion solver, in terms of extrapolated distance for each energy group, and calculated by $d_{ext,g} = 2.13 D_g$.
+For sake of clarity, the fast and thermal energy groups are denoted by 1 and 2, respectively.
 
-\begin{figure}[htbp]
+\subsection{Homogeneous case}
+\label{sec:homog}
+Considering a bare slab of width 21.5 cm, representing a Pressurized Water Reactor (PWR) fuel assembly, homogenized into two energy groups with corresponding cross sections, which are shown in Table~\ref{tab:xs_hom}.
+Calculations were performed with $I=400$ (No.
+of cells).
+
+\begin{table}[!htbp]
+	\centering
+	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] of the homogeneous case~\cite{Tomatis-2011}.}
+	\label{tab:xs_hom}
+	\begin{tabular}{cccccc}
+		%\midrule
+		Group $g$ &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
+		\midrule
+		1 & 5.3115$\times$10\tsup{-1} & 5.04664$\times$10\tsup{-1} & 2.03884$\times$10\tsup{-3} & 1 & 7.15848$\times$10\tsup{-3} \\
+		%\midrule
+		2 & 1.30058$\times$10\tsup{0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{0}	& 0 & 1.41284$\times$10\tsup{-1} \\
+		%\midrule
+	\end{tabular}
+\end{table}
+
+Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_16$ of the left half slab.
+The abscissa shows values of the group-dependent neutron mean free path (mfp) $\tau$.
+
+\begin{figure}[!htbp]
 	\centering
 	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_I400_RMitr250.pdf}
-	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD, RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$).
+	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD - RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$).
 The insets show a zoom-in of the fluxes near the boundary.
@@
 
-\begin{figure}[htbp]
+One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results.
+On the other hand, closer to the boundary, the Ronen method shows better results.
+The flux deviations of the left half slab, are shown in Fig.~\ref{fig:flx_err_homg}, calculated by $\Delta\keff = \left(\keff^{-1}-k_{\text{ref}}^{-1}\right)\times 10^5$ pcm.
+
+\begin{figure}[!hbtp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
+	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
+	\label{fig:flx_err_homg}
+\end{figure}
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_rho_I400_RMitr250.pdf}	
+	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
+	\label{fig:rho_homg}
+\end{figure}
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
+	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
+	\label{fig:slab-fluxes-dev}
+\end{figure}
+
+\begin{figure}[!htbp]
 	\centering
@@
 
-\begin{figure}[htbp]
-	% convergence
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_k_over_I400_RMitr250.pdf}	
-	\caption{Convergence of the criticality eigenvalue along 250 Ronen iterations.}
-	\label{fig:conv}
-\end{figure}
-
-\begin{figure}[hbtp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
-	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
-	\label{fig:conv3}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
-	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
-	\label{fig:slab-fluxes-dev}
-\end{figure}
 % ------------------------------------------

### 2020-01-27 docs/ANE2020/figures/Tomatis2011_ANE2020.py

@@ -34,8 +34,8 @@ Plot_flx_cvg  = False
 Plot_dD       = False
 Plot_err      = False
 Plot_k        = False
-plot_flx_zoom = True
-Plot_rho      = False
+plot_flx_zoom = False
+Plot_rho      = True
 Plot_LB       = False
 I = 400 # No. of mesh points
 #dx = 21.5/I
@@ -45,8 +45,8 @@ itr = 250 # No. of iterations
 plot_RM = True
 if plot_RM:
     ''' Upload one file '''
-    path_RM_flx_file1 = "kflx_MC2011_LBC0RBC0_CMFD_I400_it250.npy"
-    path_RM_flx_file2 = "kflx_MC2011_LBC0RBC0_pCMFD_I400_it250.npy"
+    path_RM_flx_file1 = "kflx_Tomatis2011_CMFD_LBC0RBC0_I400_it250.npy"
+    path_RM_flx_file2 = "kflx_Tomatis2011_pCMFD_LBC0RBC0_I400_it250.npy"
     #path_RM_flx_file3 = "../../../FD1dMGdiff/output/kflx_MC2011_LBC0RBC0_I400_it10.npy"
         #data = np.load(path_RM_flx_file)
     k_RM1, flx_RM1, xi1, st, dD1 = np.load(path_RM_flx_file1,allow_pickle=True)
@@ -64,7 +64,7 @@ if plot_SN:
     #path_Sn_flx_file = "../../SNMG1DSlab/output/CORE%dLBC0RBC0_I%d_N%d.npy"  % (ccng,I,N)
     
     # Homogeneous case - slab width (based on  Tomatis&Dall'Osso MC2011)
-    path_SN_flx_file = "../../../SNMG1DSlab/output/kflx_MC2011_LBC0RBC0_I400_L21_N16.npy"
+    path_SN_flx_file = "kflx_Tomatis2011_SN_LBC0RBC0_I400_L21_N16.npy"
     ref_data = np.load(path_SN_flx_file,allow_pickle=True)
     k_SN, flxm = ref_data[0], ref_data[1][:,0,:]
 
@@ -192,16 +192,16 @@ if Plot_dD:
         ax[g].tick_params(axis='both', which='minor', labelsize=fsz)
         ax[g].set_prop_cycle(default_cycler)
         ax[g].plot(xi, dD1[g,:],label='CMFD')
[…]

### 2020-01-27 docs/ANE2020/contents.tex
ANE2020 tex file update

@@
 
-Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_16$ of the left half slab.
-The abscissa shows values of the group-dependent neutron mean free path (mfp) $\tau$.
+Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_{16}$ of the left half slab.
+The abscissa's values are the group-dependent neutron mean free path (mfp) $\tau$.
+One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results.
+On the other hand, closer to the boundary, the Ronen method shows better results.
 
@@
 
-One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results.
-On the other hand, closer to the boundary, the Ronen method shows better results.
-The flux deviations of the left half slab, are shown in Fig.~\ref{fig:flx_err_homg}, calculated by $\Delta\keff = \left(\keff^{-1}-k_{\text{ref}}^{-1}\right)\times 10^5$ pcm.
+In Fig~\ref{fig:flx_err_homg}, the flux deviation (calculated by $\Delta \phi = \left[\left(\phirm-\phiref\right)/\phiref\right]\times 100$) at the first 40 cells of the left slab has approximately $\sim 20\%$ difference between diffusion and RM calculations.
+The difference observed closer to the boundary, due to the fact that the major transport effect occur near the boundary of the homogeneous slab.
 
@@
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_rho_I400_RMitr250.pdf}	
-	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
-	\label{fig:rho_homg}
-\end{figure}
+A comparison of the flux deviation, calculated by the two implementations of the RM, within the left-most (I=0) cell is shown in Fig.~\ref{fig:slab-fluxes-dev-LB}.
+The deviation of CMFD and pCMFD has very close trend along the 250 iterations, reaching approximately $\sim 2\%$ compared to the reference solution.
 
@@
 	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
-	\label{fig:slab-fluxes-dev}
+	\label{fig:slab-fluxes-dev-LB}
 \end{figure}
+
+In Fig~\ref{fig:rho_homg}, the behavior of the eigenvalue difference $\Delta\keff$ in pcm, along RM iterations are represented, and calculated by $\Delta\keff = \left(\keff^{-1}-\kref^{-1}\right)\times 10^5$ pcm.
+The value of the eigenvalues reported by the reference S$_{16}$ solution is  $\kref = 0.74441$,  and by diffusion calculation $\keff = 0.74133$, which gives the value $\Delta\keff \approx 558$ pcm.
+One RM iteration resulting in tens of pcm, but CMFD perform well than pCMFD at the very first few iterations.
+After a steep decline of $\Delta\keff$, achieving by 10 iterations, both numerical implementations converging at the same rate, with a typical linear equation, approximated by $\Delta\keff \approx 4.545\cdot 10^-7 \times (\#\text{it}) + 0.744363$, it stands for iteration.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.9\linewidth]{Tomatis2011_dk_I400_RMitr250.pdf}	
+	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
+	\label{fig:rho_homg}
+\end{figure}
+
+The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{+\setminus -}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.
 
@@
 	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
-	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($\delta D^+, \delta D^-$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
-	\label{fig:slab-RM-corr-factor}
+	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($dD^{+\setminus -}$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
+	\label{fig:slab-RM-dD}
 \end{figure}

### 2020-01-27 docs/ANE2020/figures/Tomatis2011_ANE2020.py

@@ -33,9 +33,10 @@ plot_flx      = False
 Plot_flx_cvg  = False
 Plot_dD       = False
 Plot_err      = False
+Plot_MAX_err  = False # Under development
 Plot_k        = False
 plot_flx_zoom = False
-Plot_rho      = True
+Plot_rho      = False
 Plot_LB       = False
 I = 400 # No. of mesh points
 #dx = 21.5/I
@@ -247,7 +248,40 @@ if Plot_err:
     filename = 'Tomatis2011_flx_err_I%d_RMitr%d.pdf' %(I,itr)
     fig.savefig(filename,dpi=300,bbox_inches='tight')
     os.system("pdfcrop %s %s" %(filename,filename))    
+
+# ============================================================== #
+# ========================= MAX Flux Error ========================= #
+# ============================================================== #
+if Plot_MAX_err: 
+
+    max_flx_err_CMFD = (flx_RM1[:,:,2:] - flx_RM1[:,:,1:-1])/ flx_RM1[:,:,1:-1]
+    max_flx_err_pCMFD = (flx_RM2[:,:,2:] - flx_RM2[:,:,1:-1])/ flx_RM2[:,:,1:-1]
+
+    RMitr = np.linspace(1,250,250)
     
+    plt.figure(figsize=(14, 5)) 
+    fig, ax = plt.subplots(G,figsize=(14, 6))
+    
+    for g in range (0,G):
+        ax[g].set_prop_cycle(default_cycler)
+        for i in range (0,np.size(I)):
+            ax[g].tick_params(axis='both', which='major', labelsize=fsz)
+            ax[g].tick_params(axis='both', which='minor', labelsize=fsz)
+            ax[g].plot(RMitr, max_flx_err_CMFD[g,:],label='CMFD' if g == 0 else "")
+            ax[g].plot(RMitr, max_flx_err_pCMFD[g,:],'r-d',label='pCMFD' if g == 0 else "")
+            ax[g].grid(True,'both','both')
+            ax[g].set_xscale('log')
+            ax[g].set_yscale('log')
+            ax[g].legend(loc='upper right',fontsize=fsz//1.5,ncol=3)
+            #ax[g].set_xlim(tau_m[g,0], tau_m[g,39])
+    
+    ax[0].set_ylabel(r'$\epsilon^1_{\phi} $ [AU]',fontsize = fsz)        
+    ax[1].set_ylabel(r'$\epsilon^2_{\phi} $ [AU]',fontsize = fsz)        
[…]

### 2020-01-28 docs/ANE2020/contents.tex
Update contents.tex

@@
 The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{+\setminus -}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.
+The correction factor $\dd$ calculated by CMFD, are equal to zero within the slab, but have different behavior closer to the boundaries.
+On the other hand, the current corrections are about $\dd^{p/-} \sim \mp 1/4$ at the center of the slab, and have particular behavior close to the boundaries.
+The flat steady values of the factors at the center of the slab (or few mfp's away from the boundary) can be explained by the following simple relations.
+within the definition of the current $J(x,\mu)^\pm$ as follows
+\begin{equation}
+\label{eq:current_def}
+J(x,\mu)^\pm = \int\limits_0^1 d\mu\,\muvarphi(x,\mu)
+\end{equation}
+Expanding the angular flux $\phi(x,\mu)$ by $P_1$ approximation
+\begin{equation}
+\label{eq:p1}
+\varphi(x,\mu) = \sum\limits_{l=0}^{L=1}\frac{2l+1}{2}P_l(\mu)\varphi_l(x) = \frac{1}{2}\phi_0(x) + \frac{3}{2}\mu\varphi_1(x)\,\,,
+\end{equation}
+rearranging and segregating the current corrections on one side of the equation, yield
+\begin{equation}
+	\begin{split}
+		\label{eq:current_p1}
+		J(x,\mu)^\pm &= \int\limits_0^1 d\mu\mu\left[\frac{1}{2}\varphi_0(x) + \frac{3}{2}\mu\varphi_1(x)\right] \\
+		&= \frac{1}{4}\phi_0(x) + \frac{1}{2}\varphi_1(x)\,\,.
+	\end{split}
+\end{equation}
+Assuming that Fick's law is accurate, i.e.
+several mfp's away from significant gradients (boundary in a homogeneous slab), and in weakly absorbing medium, by equalizing Eq.~\ref{eq:delta-D-pCMFD} and Eq.~\ref{eq:current_p1}, and rearranging, one gets
+%\begin{equation}
+%	\label{eq:dd_quarter}
+%	\begin{split}
+%	\dd\pm \approx \frac{\left[ \frac{\varphi(x)}{den} \right]}{den}
+%	\end{split}
+%\end{equation}
 

### 2020-01-28 docs/ANE2020/contents.tex
Update contents.tex
Need to check the signs  of the last equations.

--- 2020-01-27 docs/ANE2020/contents.tex
@@
     J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= -\delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
-    J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
+    J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm} \\
+    J^\pm_{i+\hzi} = \pm \frac{1}{2}\jD_{i+\hzi} \mp \delta D^{\pm} _{i+\hzi} \phi_{i+(1\mp 1)/2}\label{eq:delta-D-pCMFDpm} \,\,,
   \end{align}
@@
 The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{+\setminus -}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.
+The correction factor $\dd$ calculated by CMFD, are equal to zero within the slab, but have different behavior closer to the boundaries.
+On the other hand, the current corrections are about $\dd^{p/-} \sim \mp 1/4$ at the center of the slab, and have particular behavior close to the boundaries.
+The flat steady values of the factors at the center of the slab (or few mfp's away from the boundary) can be explained by the following simple relations.
+within the definition of the current $J(x,\mu)^\pm$ as follows
+\begin{equation}
+\label{eq:current_def}
+J(x,\mu)^\pm = \int\limits_0^1 d\mu\,\mu\varphi(x,\mu)
+\end{equation}
+Expanding the angular flux $\phi(x,\mu)$ by $P_1$ approximation
+\begin{equation}
+\label{eq:p1}
+\varphi(x,\mu) = \sum\limits_{l=0}^{L=1}\frac{2l+1}{2}P_l(\mu)\varphi_l(x) = \frac{1}{2}\varphi_0(x) + \frac{3}{2}\mu\varphi_1(x)\,\,,
+\end{equation}
+Substituing into Eq.~\ref{eq:current_def}, and integrating
+\begin{equation}
+	\begin{split}
+		\label{eq:current_p1}
+		J^\pm(x,\mu) &= \int\limits_0^{\pm 1} d\mu\mu\left[\frac{1}{2}\varphi_0(x) + \frac{3}{2}\mu\varphi_1(x)\right] \\
+		J^\pm(x) &= \frac{1}{4}\phi_0(x) \mp \frac{1}{2}\varphi_1(x)\,\,.
+	\end{split}
+\end{equation}
+The descretized form is
+\begin{equation}
+\label{eq:curent_p1_i}
+J^\pm_{i+\hzi} = \frac{1}{4}\phi_{0,i} \mp \frac{1}{2}J^{\pm}_{i+\hzi}\,\,.
+\end{equation}
+The first moment of the flux ($\varphi_1$) is the current $J$.
+Assuming that Fick's law is accurate, i.e.
+several mfp's away from significant gradients (boundary in a homogeneous slab), and in weakly absorbing medium,
+by equalizing Eq.~\ref{eq:delta-D-pCMFDpm} and Eq.~\ref{eq:curent_p1_i}, rearranging and segregating the current corrections on one side of the equation, one gets
+\begin{equation}
+	\label{eq:dd_quarter}
+	\begin{split}
+	\pm \frac{1}{2}\jD_{i+\hzi} \mp \delta D^{\pm} _{i+\hzi} \phi_{0,i+(1\mp 1)/2} & = \frac{1}{4}\phi_{0,i} \mp \frac{1}{2} J^{\pm}_{D,i+\hzi} \\
+	\dd^\pm_{i+\hzi} \approx \frac{1}{4}\cdot\frac{\phi_{0,i}}{\phi_{0,i+(1\mp 1)/2}} & \approx \frac{1}{4}\,\,.
+	\end{split}
+\end{equation}
 

### 2020-01-29 docs/ANE2020/contents.tex
Updated contents.tex - homogeneous case
1. Finished the homogeneous case under the Chapter - Results.
2. Added Heterogeneous results to ANE2020 folder in order to reproduce figures.

@@
     J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm} \\
-    J^\pm_{i+\hzi} = \pm \frac{1}{2}\jD_{i+\hzi} \mp \delta D^{\pm} _{i+\hzi} \phi_{i+(1\mp 1)/2}\label{eq:delta-D-pCMFDpm} \,\,,
+    J^\pm_{i+\hzi} = \pm \frac{1}{2}\jD_{i+\hzi}& \mp \delta D^{\pm} _{i+\hzi} \phi_{i+(1\mp 1)/2}\label{eq:delta-D-pCMFDpm} \,\,,
   \end{align}
@@
 
-The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{+\setminus -}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.
+The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{\pm}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.
 The correction factor $\dd$ calculated by CMFD, are equal to zero within the slab, but have different behavior closer to the boundaries.
-On the other hand, the current corrections are about $\dd^{p/-} \sim \mp 1/4$ at the center of the slab, and have particular behavior close to the boundaries.
+On the other hand, the current corrections are about $\dd^{\pm} \sim \mp 1/4$ at the center of the slab, and have particular behavior close to the boundaries.
 The flat steady values of the factors at the center of the slab (or few mfp's away from the boundary) can be explained by the following simple relations.
@@
 \label{eq:current_def}
-J(x,\mu)^\pm = \int\limits_0^1 d\mu\,\mu\varphi(x,\mu)
+J^\pm(x,\mu) = \int\limits_0^{\pm 1} d\mu\,\mu\,\varphi(x,\mu)\,\,.
 \end{equation}
@@
 		J^\pm(x,\mu) &= \int\limits_0^{\pm 1} d\mu\mu\left[\frac{1}{2}\varphi_0(x) + \frac{3}{2}\mu\varphi_1(x)\right] \\
-		J^\pm(x) &= \frac{1}{4}\phi_0(x) \mp \frac{1}{2}\varphi_1(x)\,\,.
+		J^\pm(x) &= \frac{1}{4}\phi_0(x) \pm \frac{1}{2}\varphi_1(x)\,\,.
 	\end{split}
@@
 \label{eq:curent_p1_i}
-J^\pm_{i+\hzi} = \frac{1}{4}\phi_{0,i} \mp \frac{1}{2}J^{\pm}_{i+\hzi}\,\,.
+J^\pm_{i+\hzi} = \frac{1}{4}\phi_{0,i+\hzi} \pm \frac{1}{2}J^{\pm}_{i+\hzi}\,\,.
 \end{equation}
@@
 	\begin{split}
-	\pm \frac{1}{2}\jD_{i+\hzi} \mp \delta D^{\pm} _{i+\hzi} \phi_{0,i+(1\mp 1)/2} & = \frac{1}{4}\phi_{0,i} \mp \frac{1}{2} J^{\pm}_{D,i+\hzi} \\
-	\dd^\pm_{i+\hzi} \approx \frac{1}{4}\cdot\frac{\phi_{0,i}}{\phi_{0,i+(1\mp 1)/2}} & \approx \frac{1}{4}\,\,.
+	\pm \frac{1}{2}\jD_{i+\hzi} \mp \delta D^{\pm} _{i+\hzi} \phi_{0,i+(1\mp 1)/2} & = \frac{1}{4}\phi_{0,i+\hzi} \pm \frac{1}{2} J^{\pm}_{D,i+\hzi} \\
+	\dd^\pm_{i+\hzi} \approx \mp \frac{1}{4}\cdot\frac{\phi_{0,i+\hzi}}{\phi_{0,i+(1\mp 1)/2}} & \approx \mp\frac{1}{4}\,\,.
 	\end{split}
@@
 	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
-	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($dD^{+\setminus -}$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
+	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($dD^{\pm}$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
 	\label{fig:slab-RM-dD}
 \end{figure}
+
+\subsection{Heterogeneous case}
+\label{sec:heterog}
 

### 2020-01-29 docs/ANE2020/contents.tex
minor bug fix

--- 2020-01-28 docs/ANE2020/contents.tex
@@
 The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing for separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
-Recently, multi-dimensional transport codes have used it as acceleration technique and the convergence of different implementations was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
+In the last decade, multi-dimensional transport codes have also used it as acceleration technique and the convergence of different implementation schemes was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
 
@@
 In principle, the corrective terms can be computed with a different physics other than diffusion, which is always solved at the coarse level.
-This facilitates its application to accelerate complex multi-dimensional transport codes.
-This acceleration is actually implemented by rebalancing the scalar flux, with the optional use of some relaxation~\cite{Park-2017}.
-Hence, a non-linear iterative scheme arises between the CMFD solver and the computation of the local corrections, which use the latest estimates of the flux available from the diffusion solver.
+This facilitates its application to accelerate complex multi-dimensional transport codes~\cite{Zhu-2016,Shen-2019,Zhang-2019}.
+This acceleration is actually implemented by rebalancing the scalar flux, with the optional use of some relaxation~\cite{Park-2017,Shen-2019}.
+Hence, a non-linear iterative scheme arises between the CMFD solver and the computation of local corrections that use the latest estimates of the flux available from the diffusion solver.
 
@@
 \label{sec:res}
-Two test cases are shown in this section.
-The first is a one-dimensional (1-D) homogeneous plane, representing a typical fuel assembly~\cite{Tomatis-2011}.
-The second benchmark include three different cores, which are 1-D representation of a Boiling Water Reactor (BWR) configuration~\cite{Rahnema-1997}.
-Both test cases are calculated and compared by two-group nodal diffusion code (denoted as $D_0$) and the Ronen method (with the implementation of CMFD and pCMFD), and are verified against a discrete ordinates S$_N$ code, with N=16.
-For all test cases, isotropic scattering are considered.
-Therefore, the diffusion coefficients for the homogeneous case, calculated by $D_g = (3\sigma_{tr,g})^{-1} = (3\sigma_g)^{-1}$.
-Void boundary conditions, which are implemented within the diffusion solver, in terms of extrapolated distance for each energy group, and calculated by $d_{ext,g} = 2.13 D_g$.
-For sake of clarity, the fast and thermal energy groups are denoted by 1 and 2, respectively.
 
-\subsection{Homogeneous case}
-\label{sec:homog}
-Considering a bare slab of width 21.5 cm, representing a Pressurized Water Reactor (PWR) fuel assembly, homogenized into two energy groups with corresponding cross sections, which are shown in Table~\ref{tab:xs_hom}.
-Calculations were performed with $I=400$ (No.
-of cells).
-
-\begin{table}[!htbp]
-	\centering
-	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] of the homogeneous case~\cite{Tomatis-2011}.}
-	\label{tab:xs_hom}
-	\begin{tabular}{cccccc}
-		%\midrule
-		Group $g$ &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
-		\midrule
-		1 & 5.3115$\times$10\tsup{-1} & 5.04664$\times$10\tsup{-1} & 2.03884$\times$10\tsup{-3} & 1 & 7.15848$\times$10\tsup{-3} \\
-		%\midrule
-		2 & 1.30058$\times$10\tsup{0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{0}	& 0 & 1.41284$\times$10\tsup{-1} \\
-		%\midrule
-	\end{tabular}
-\end{table}
-
-Fig.~\ref{fig:slab-fluxes} shows the fast and thermal fluxes calculated by diffusion, CMFD, pCMFD and S$_{16}$ of the left half slab.
-The abscissa's values are the group-dependent neutron mean free path (mfp) $\tau$.
-One or two mpf's from the boundary towards the center of the slab are enough for diffusion, to match well the reference S$_16$ results.
-On the other hand, closer to the boundary, the Ronen method shows better results.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_I400_RMitr250.pdf}
-	\caption{Comparison of the fluxes as calculated by the reference S$_N$, RM-CMFD - RM-pCMFD codes, and a standard multigroup diffusion without RM correction ($D_0$).
-The insets show a zoom-in of the fluxes near the boundary.
-Results shown here after 250 Ronen iterations and 400 cells.}
-	\label{fig:slab-fluxes}		
-\end{figure}
-
-In Fig~\ref{fig:flx_err_homg}, the flux deviation (calculated by $\Delta \phi = \left[\left(\phirm-\phiref\right)/\phiref\right]\times 100$) at the first 40 cells of the left slab has approximately $\sim 20\%$ difference between diffusion and RM calculations.
-The difference observed closer to the boundary, due to the fact that the major transport effect occur near the boundary of the homogeneous slab.
-
-\begin{figure}[!hbtp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_I400_RMitr250.pdf}
-	\caption{The spatial flux deviation of the RM-CMFD and RM-pCMFD iterations with respect to the reference S$_{16}$ solution for the left half slab.}
-	\label{fig:flx_err_homg}
-\end{figure}
-
-A comparison of the flux deviation, calculated by the two implementations of the RM, within the left-most (I=0) cell is shown in Fig.~\ref{fig:slab-fluxes-dev-LB}.
-The deviation of CMFD and pCMFD has very close trend along the 250 iterations, reaching approximately $\sim 2\%$ compared to the reference solution.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_flx_err_LB_I400_RMitr250.pdf}
-	\caption{Deviation of the fluxes at the left-most cell, calculated by RM-CMFD and RM-pCMFD codes, with respect to the reference solution after 250 Ronen iterations.}
-	\label{fig:slab-fluxes-dev-LB}
-\end{figure}
-
-In Fig~\ref{fig:rho_homg}, the behavior of the eigenvalue difference $\Delta\keff$ in pcm, along RM iterations are represented, and calculated by $\Delta\keff = \left(\keff^{-1}-\kref^{-1}\right)\times 10^5$ pcm.
-The value of the eigenvalues reported by the reference S$_{16}$ solution is  $\kref = 0.74441$,  and by diffusion calculation $\keff = 0.74133$, which gives the value $\Delta\keff \approx 558$ pcm.
-One RM iteration resulting in tens of pcm, but CMFD perform well than pCMFD at the very first few iterations.
-After a steep decline of $\Delta\keff$, achieving by 10 iterations, both numerical implementations converging at the same rate, with a typical linear equation, approximated by $\Delta\keff \approx 4.545\cdot 10^-7 \times (\#\text{it}) + 0.744363$, it stands for iteration.
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_dk_I400_RMitr250.pdf}	
-	\caption{Convergence of the reactivity along 250 Ronen iterations, with respect to S$_N$.}
-	\label{fig:rho_homg}
-\end{figure}
-
-The correction factors of CMFD and pCMFD (denoted by $\dd$, $dD^{+\setminus -}$, respectively) are shown in Fig~\ref{fig:slab-RM-dD}.
-The correction factor $\dd$ calculated by CMFD, are equal to zero within the slab, but have different behavior closer to the boundaries.
-On the other hand, the current corrections are about $\dd^{p/-} \sim \mp 1/4$ at the center of the slab, and have particular behavior close to the boundaries.
-The flat steady values of the factors at the center of the slab (or few mfp's away from the boundary) can be explained by the following simple relations.
-within the definition of the current $J(x,\mu)^\pm$ as follows
-\begin{equation}
-\label{eq:current_def}
-J(x,\mu)^\pm = \int\limits_0^1 d\mu\,\muvarphi(x,\mu)
-\end{equation}
-Expanding the angular flux $\phi(x,\mu)$ by $P_1$ approximation
-\begin{equation}
-\label{eq:p1}
-\varphi(x,\mu) = \sum\limits_{l=0}^{L=1}\frac{2l+1}{2}P_l(\mu)\varphi_l(x) = \frac{1}{2}\phi_0(x) + \frac{3}{2}\mu\varphi_1(x)\,\,,
-\end{equation}
-rearranging and segregating the current corrections on one side of the equation, yield
-\begin{equation}
-	\begin{split}
-		\label{eq:current_p1}
-		J(x,\mu)^\pm &= \int\limits_0^1 d\mu\mu\left[\frac{1}{2}\varphi_0(x) + \frac{3}{2}\mu\varphi_1(x)\right] \\
-		&= \frac{1}{4}\phi_0(x) + \frac{1}{2}\varphi_1(x)\,\,.
-	\end{split}
-\end{equation}
-Assuming that Fick's law is accurate, i.e.
-several mfp's away from significant gradients (boundary in a homogeneous slab), and in weakly absorbing medium, by equalizing Eq.~\ref{eq:delta-D-pCMFD} and Eq.~\ref{eq:current_p1}, and rearranging, one gets
-%\begin{equation}
-%	\label{eq:dd_quarter}
-%	\begin{split}
-%	\dd\pm \approx \frac{\left[ \frac{\varphi(x)}{den} \right]}{den}
-%	\end{split}
-%\end{equation}
-
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.9\linewidth]{Tomatis2011_dD_I400_RMitr250.pdf}
-	\caption{The Ronen method correction factors ($\delta D$), calculated by CMFD code, and ($dD^{+\setminus -}$), calculated by pCMFD code. Results shown here after 250 Ronen iterations.}
-	\label{fig:slab-RM-dD}
-\end{figure}
+xy
 

### 2020-01-29 FD1dMGdiff/FDsDiff1D.py

@@ -165,9 +165,9 @@ class input_data:
         if not isinstance(self.media, list):
             raise TypeError('The input media is not a list.')
         media_set = set(m[0] for m in self.media)
-        if len(self.xs_media) != len(media_set):
-            raise ValueError('xs media dict and list must have the same ' +
-                             'nb. of elements.')
+        xs_media_set = set(self.xs_media.keys())
+        if xs_media_set.union(media_set) != xs_media_set:
+            raise ValueError('xs media dict has missing keys, check media.')
         rbnd = [m[1] for m in self.media]
         if sorted(rbnd) != rbnd:
             raise ValueError('media list must be in order from left to right!')

### 2020-03-23 SNMG1DSlab/tests/homogSlab2GMC2011.py
simple text changes

@@ -19,7 +19,7 @@ import numpy as np
 # after import
 
 L = 21.5  # Core width
-I = 400  # No. of spatial cells
+I = 100  # No. of spatial cells
 xi = np.linspace(0, L, I+1)  # equidistant mesh      
 # definition of the spatial mesh
 
@@ -52,12 +52,12 @@ if __name__ == "__main__":
     from snmg1dslab import solve_sn
 
     flxm, k = solve_sn(Homog2GSlab_data, slvr_opts, qdata)
-    basefilen = "../output/kflx_Tomatis2011_LBC%dRBC%d_I%d_L%d_N%d" % (
+    basefilen = "../output/kflx_MC2011_LBC%dRBC%d_I%d_L%d_N%d" % (
                                                         Homog2GSlab_data.LBC,
                                                         Homog2GSlab_data.RBC,
                                                         Homog2GSlab_data.I,
                                                         Homog2GSlab_data.xi[-1],
                                                         qdata.N)
-    np.save(basefilen + ".npy", np.array([k, flxm],object), allow_pickle=True)
+    np.save(basefilen + ".npy", np.array([k, flxm]), allow_pickle=True)
     #np.savez(basefilen + ".npz", k=k, flxm=flxm)
     

### 2020-03-23 SNMG1DSlab/tests/heterSlab2GRahnema1997.py
complete merge after many weeks of absence

@@ -37,11 +37,12 @@ if __name__ == "__main__":
 
     flxm, k = solve_sn(Heter2GSlab_data, slvr_opts, qdata)
 
-    basefilen = "../output/kflx_Rahnema1997_SN_CORE%dLBC%dRBC%d_I%d_N%d" % (core_config,
+    basefilen = "../output/kflx_Rahnema1997_SN_CORE%dLBC%dRBC%d_I%d_N%d" % (
+                                                        core_config,
                                                         Heter2GSlab_data.LBC,
                                                         Heter2GSlab_data.RBC,
                                                         Heter2GSlab_data.I,
                                                         qdata.N)
-    np.save(basefilen + ".npy", np.array([k, flxm],object), allow_pickle=True)
+    np.save(basefilen + ".npy", np.array([k, flxm]), allow_pickle=True)
     #np.savez(basefilen + ".npz", k=k, flxm=flxm)
     

### 2020-03-24 FD1dMGdiff/FDsDiff1D.py
propose a test for CMFD

@@ -893,7 +893,7 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
         # (not used later in isotropic problems without CMFD)
         J_diff = compute_diff_currents(flxd, Db, Di, BC)
         if lin_anis:
-            Jd = J_diff + compute_delta_diff_currents(flxd, dD, Di, BC, \
+            Jd = J_diff + compute_delta_diff_currents(flxd, dD, Di, BC,
                                                       slvr_opts.pCMFD)
             Jd = (Jd[:, 1:] + Jd[:, :-1]) / 2.  # simple cell-average
 
@@ -953,11 +953,12 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
     lg.info("Initial value of k was %13.6g." % kinit)
     if filename is not None:
         # filename = "output/kflx_LBC%dRBC%d_I%d" % (*BC,I)
-        np.save(filename + ".npy", [k_save, flx_save, xi, xs[0], dD], allow_pickle=True)
-        # np.save(filename.replace('kflx','err'), [kerr_save, ferr_save], \
-        #          allow_pickle=True)
-        # np.save(filename + ".npy", [k_save, flx_save, xi, xs[0], dD], \
-        #          allow_pickle=True)
+        np.save(filename + ".npy",
+            [k_save, flx_save, xi, xs[0], dD], allow_pickle=True)
+        # np.save(filename.replace('kflx','err'), [kerr_save, ferr_save],
+        #         allow_pickle=True)
+        # np.save(filename + ".npy", [k_save, flx_save, xi, xs[0], dD],
+        #         allow_pickle=True)
         with open(filename + ".dat", 'w') as f:
             i = 0
             while k_save[i] >= 0:
@@ -992,7 +993,7 @@ def unfold_xs(input_data, diff_calc=True):
         D[:, idx] = np.tile(xs_media[media_name]['D'], (n, 1)).T
         Lmed = xs_media[media_name]['ss'].shape[-1]
         if Lmed > Lssp1:
-            raise ValueError("Media %s has ss with L > %d!" % \
+            raise ValueError("Media %s has ss with L > %d!" %
                              (media_name, Lss))
         tmp = np.tile(xs_media[media_name]['ss'].flatten(), (n, 1)).T
         ss[:, :, :, idx] = tmp.reshape(G, G, Lssp1, n)

### 2020-03-24 FD1dMGdiff/data/homog2GMC2011.py

@@ -29,12 +29,22 @@ D = one_third / (st - np.sum(ss1, axis=1))
 G = st.size  # nb of energy groups
 
 
+def calc_flx_inf(st, ss0, chi):
+    return np.dot(np.linalg.inv(np.diag(st) - ss0), chi)
+
+
+def calc_kinf(nsf, st=None, ss0=None, chi=None, flx_inf=None):
+    if flx_inf is None:
+        flx_inf = calc_flx_inf(st, ss0, chi)
+    return np.dot(nsf, flx_inf)
+
+
 if __name__ == "__main__":
 
     lg.info("*** Check homogeneous cross sections data ***")
 
-    flx_inf = np.dot(np.linalg.inv(np.diag(st) - ss0), chi)
-    kinf = np.dot(nsf, flx_inf)
+    flx_inf = calc_flx_inf(st, ss0, chi)
+    kinf = calc_kinf(nsf, flx_inf=flx_inf)
     # np.testing.assert_almost_equal(kinf, 1.1913539017168697, decimal=7,
     #     err_msg="kinf not verified.")
     np.testing.assert_almost_equal(kinf, 1.0783813599102687, decimal=7,

### 2020-03-25 docs/ICTT2019/RMethod_ictt26.tex
minor modifications to ictt text

@@
 The diffusion solver employs here finite differences and the transport-corrected currents are forced in the numerical scheme by means of drift terms, like in the CMFD technique.
-The solution is compared against reference results provided by a discrete ordinate computer code.
+The solution is compared against reference results provided by the collision probability method.
 Boundary conditions are discussed introducing proper approximations to save the particle balance.
-Slow convergence is reported on the scalar flux, although the results match the reference solutions in the limit of fine meshes.
+Slow convergence is reported on the scalar flux, although the results match the reference solutions in the limit of fine meshes and far from the bare boundary.
 %
@@
 This idea was later used by Tomatis and Dall'Osso, who provided a numerical demonstration in a simple slab problem \cite{tomatis2011application}.
-Instead of updating the diffusion coefficient by the ratio of the current exchange and the flux gradient, as in Fick's law, they recurred to the coarse mesh finite differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
+Instead of updating the diffusion coefficient by the ratio of the current exchange and the flux gradient, as in Fick's law, they recurred to the scheme of the coarse mesh finite differences method (CMFD) for taking into account the new currents estimated by the integral transport operator in the diffusion solver.
 %
@@
 The cross sections, as well as the diffusion coefficient, are usually available as volume-averaged data per cell in the mesh.
+A lattice transport computer code can prepare these data by homogenization.
 Once the scalar flux is known from the finite differences solver using the original diffusion coefficients, the integral expressions derived in section \ref{sec:ce} can be used to get new estimates of the current $J$ at the cell interfaces.
@@
 Fission emission is isotropic, so that only the scalar flux $\phi$ being equal to the first moment $\varphi_0$ is retained for the fission term.
-Without the external source $S$, the multiplication factor $k$ is used as eigenvalue to avoid the trivial vanishing solution.
-Since $q$ is computed by the results of the diffusion equation in the Ronen method, $l$ can only assume the values 0 and 1.% Hereafter we consider only isotropic sources.
+Without the external source $S$, the multiplication factor $k$ is used as eigenvalue to avoid the only trivial vanishing solution.
+Since $q$ is computed by the results of the diffusion equation in the Ronen method, $l$ can only assume the values 0 and 1, with the second moment $\varphi_1$ equal to the net current $J$.% Hereafter we consider only isotropic sources.
 
@@
 \begin{equation*}
-E_n(\tau) = \int_0^1{d\mu\, e^{-\tau / \mu} \mu^{n-2}} = \int_1^\infty{du\, e^{-\tau u}u^{-n}}.
+E_n(\tau) = \int_0^1{d\mu\, e^{-\tau / \mu} \mu^{n-2}} = \int_1^\infty{du\, e^{-\tau u}u^{-n}}, \: n \geq 0.
 \end{equation*}
@@
 \begin{equation}
-\text{Ki}_n(\tau) = \int_0^{\pi/2}{ d\theta \sin^{n-1} \theta \exp\left(-\frac{\tau}{\sin \theta}\right) }.
+\text{Ki}_n(\tau) = \int_0^{\pi/2}{ d\theta \sin^{n-1} \theta \exp\left(-\frac{\tau}{\sin \theta}\right) },\: n \geq 0.
 \label{eq:Kin}
@@
 \end{subequations}
-$J^-$ is obtained with $w \in W^- =  \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p < 0\right\}$ instead.
+$J^-$ is obtained with integration over $w \in W^- =  \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p < 0\right\}$ instead.
 
@@
 
-The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:
+The corresponding form for the reduced escape probability for the incoming current is:
 \begin{equation}
@@
 \end{equation}
-for $i<j$, where $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergoing a collision.
+for $i<j$, whereas $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergoing a collision.
 
@@
 The integral in $h$ can be resolved numerically with weights and points by the Gauss-Legendre quadrature in absence of endpoint singularities.
-Gauss-Jacobi quadrature is recommended in that case.
+Gauss-Jacobi quadrature is recommended otherwise.
 

### 2020-04-10 docs/ICTT2019/RMethod_ictt26.tex
First implementation of the collision probability solver in annular geometries; ICTT26 doc update; bug fix of tracking algorithm; add a test in bare and empty bodies for escape and collision probs.

@@
 %\usepackage{epsf}
-\usepackage{amsmath, amssymb}
+\usepackage{amsmath, amssymb, bm}
 \usepackage{multirow}
@@
 This method demands successive resolutions of the diffusion equation, where the local diffusion constants are modified in order to reproduce new estimates of the currents by a transport operator.
-The diffusion solver employs here finite differences and the transport-corrected currents are forced in the numerical scheme by means of drift terms, like in the CMFD technique.
-The solution is compared against reference results provided by the collision probability method.
-Boundary conditions are discussed introducing proper approximations to save the particle balance.
-Slow convergence is reported on the scalar flux, although the results match the reference solutions in the limit of fine meshes and far from the bare boundary.
+The diffusion solver employs here finite differences and the transport-corrected currents are forced in the numerical scheme by means of drift terms, like in the CMFD scheme.
+Boundary conditions are discussed introducing proper approximations to save the particle balance in case of reflection in the slab.
+The solution from the Ronen iterations is compared against reference results provided by the collision probability method (CPM).
+More accurate estimates of the currents are provided by integral equations using first flight escape probabilities.
+Slow convergence on the scalar flux is analyzed, although the results match the reference solutions in the limit of fine meshes and far from the bare boundary.
 %
@@
 \end{abstract}
+%
+\clearpage
+\tableofcontents
+\clearpage
 %
@@
 
-%\section{NODAL DIFFUSION}
-%\label{sec:nd}
-%
-%Daniele: this topic is postponed to future works.
-%
 \section{CURRENT ESTIMATION}
@@
 where $q_{(.),g,j}$ are the moments of the souce $q_g$ from Eq. \ref{eq:srcg} averaged in the volume of the $j$-th cell:
-\begin{equation*}
+\begin{subequations}
 \label{eq:srclg}
-\begin{split}
+\begin{align}
    q_{0,g,j} &= \sum_{g'}\left(\sigma_{s,0,g' \rightarrow g,j} +
                               \chi_g \nu\sigma_{f,g',j}
-                        \right) \phi_{g',j},\\
-   q_{1,g,j} &= \sum_{g'}\sigma_{s,1,g' \rightarrow g,j}J_{g',j}.
-\end{split}
-\end{equation*}
+                        \right) \phi_{g',j},\label{eq:srclg0}\\
+   q_{1,g,j} &= \sum_{g'}\sigma_{s,1,g' \rightarrow g,j}J_{g',j}.\label{eq:srclg1}
+\end{align}
+\end{subequations}
 The current appearing in $q_{1,g,j}$, that is in case of linearly anisotropic scattering, is also to be considered as volume-averaged in the cell $j$.
@@
 \end{equation*}
-These quantities can be computed for $i > j$ only, because the others are simply opposite in sign.
-
-{\color{red}Roy-Erez: Please add a paragraph or reformulate the previous one to introduce the escape probabilities in the slab.}
+These quantities can be computed for $i > j$ only, because the others are simply opposite in sign (anti-symmetric).
+Eq.
+\ref{eq:J_tr} can be reformulated for the partial currents, thus considering only the contributions coming from the different sides of $x_{i+1/2}$.
+Omitting the index on groups and keeping only isotropic sources, this is:
+\begin{equation}
+\label{eq:pcslab}
+  J^\pm_{i+1/2} = \sum_{j=1}^I{q_{0,j} \Delta_i \tilde{e}^\pm_{i+1/2,j} + J^\pm(x_b) \tilde{t}_{i+1/2, x_b}}.
+\end{equation}
+$\tilde{e}_{i+1/2, j}$ represents the probability of a neutron emitted isotropically in $\Delta_i$ to escape uncollided at $x_{i+1/2}$, along its positive or negative direction of flight.
+$\tilde{t}_{i+1/2, x_b}$ is the transmission probability of a neutron to enter isotropically at $x_b$ and to cross the interface at $x_{i+1/2}$ without colliding hitherto.
 
@@
 As well, integration of Eq.
-\ref{eq:ITE_xy} over the solid angle $d\mathbf{\Omega} = \sin \theta d\omega d \theta$ yields the scalar flux.
+\ref{eq:ITE_xy} over the solid angle $d\mathbf{\Omega} = \sin \theta d\omega d \theta$ yields the scalar flux at the point $\mathbf{r}$.
 The theory of collision probability methods originates from the use of isotropic sources, which are also considered as uniform in the cells of the spatial mesh.
+The use of anisotropic sources with spatial variation in the same cells, for instance polynomial-like, is possible but leads to much more difficult expressions to solve.
 Two integrations in space arise for each direction $\mathbf{\Omega}$, connecting the source in region $j$ to the flux (or its total reaction rate) in region $i$ by means of its collision probability.
 The incoming flux is considered as isotropic too, or linearly anisotropic in angle as in \cite{hebert2009applied} to relate the partial entering and outgoing currents to the only first flux moments.
-These partial currents on the boundary must satisfy a condition of albedo.
-Transfer probabilities across this outer surface are then derived to take into account of incoming particles in the equation for the $i$-th scalar flux.
-Escape probabilities accounts for neutrons produced in every region and leaving the outer surface uncollided.
+These partial currents on the boundary must satisfy a general condition of albedo.
+
+Using standard nomenclature of collision probability methods, transfer probabilities are derived to take into account of the contributions in the equation for the $i$-th scalar flux (or total rate) of neutrons leaving a given surface.
+Escape probabilities account for neutrons produced in a given region and leaving a surface uncollided instead.
 
 The projections of partial currents on the outward normal $\hat{n}$ to a given surface are obtained from integration of Eq.
-\ref{eq:ITE_xy} with the weight $| \hat{n} \cdot \mathbf{\Omega} | = \sin \theta | \hat{n} \cdot \mathbf{\Omega}_p |$ on $\hat{n} \cdot \mathbf{\Omega} \lessgtr 0$.
-Higher moments are obtained by the weights associated to the corresponding spherical harmonics.
+\ref{eq:ITE_xy} in $d\mathbf{\Omega}$ with the weight $| \hat{n} \cdot \mathbf{\Omega} | = \sin \theta | \hat{n} \cdot \mathbf{\Omega}_p |$ on $\hat{n} \cdot \mathbf{\Omega} \lessgtr 0$.
+Higher moments can be obtained by the weights associated to the corresponding spherical harmonics.
 Integrations along the polar angle are resolved with the introduction of the Bickley-Naylor functions \cite{amos1983uniform}:
@@
 \end{subequations}
-$J^-$ is obtained with integration over $w \in W^- =  \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p < 0\right\}$ instead.
+$J^-$ is obtained with integration over $w \in W^- =  \left\{\omega \mid \hat{n}\cdot \mathbf{\Omega}_p < 0\right\}$ instead.% The coefficient $1/2\pi$ comes from the probability of isotropic angular redistribution applied to the source $q$.
 
-Another integration on the total surface $S(r) = 2\pi r$ is necessary to obtain the current in the 1-D frame.
+Another integration on the total surface $S(r) = 2\pi r$ is necessary to obtain the current density in the 1-D frame.
 For a given angle $\omega$, we have then volume integrals to solve numerically along many parallel lines called tracks, see Fig.
@@
 After multiplication by $S(r)$ and still with uniform sources, Eq.
-\ref{eq:currp_cyl_atr} can be written in terms of the escape probability $e_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided the semicylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
+\ref{eq:currp_cyl_atr} can be written in terms of the escape probability $e_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided along the normal direction the semicylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
 \begin{equation}
-J^\pm(r)S(r) = \sum_j q_j V_j e^\pm_j(r) \mbox{ with }
-e^\pm_j(r) = \pm \frac{2}{r V_j} \int_0^r { dh\, y \int_{L^\pm_j}{
+J^\pm(r)S(r) = \sum_j q_j V_j \left[ \pm e^\pm_j(r) \right] \mbox{ with }
+e^\pm_j(r) = \frac{2}{r V_j} \int_0^r { dh\, y \int_{L^\pm_j}{
   d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right]}},
@@
 $L^\pm_j(h) = [-Y,\pm y] \cap V_j$ and where $V_j$ is the ring area.
+$\text{Ki}_2\left[\tau( y, y - \ell )\right]$ is the transport kernel expressing the probability of a neutron to travel uncollided along $\omega$ for a lenght $\tau$, given in mean free path units, from $(y - \ell)$ to $y$ \cite{stamm1983methods}.
 The integral on the track $\ell$ is written differently for the convex and for the concave parts of the rings with respect to the direction of flight, see for instance track 1 and 2 in Fig.
@@
 $\tau_{ij}$ and $\tau_{ii}$ are respectively the optical lengths between the rings $i$ and $j$, and across the outer diameter of ring $i$.
+The radial integral includes all rings within $r_{i+1/2}$.
 Reciprocity and conservation properties can be applied only after calculating the collision probabilities.
@@
 
-Singularity of the integrand for the $h$-integration is noticed in the convex part while computing the collision probabilities \cite{hebert2009applied}; this notably happens at the outer radius of $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$.
-However, that integral can be regularized by a suitable change of variable.
-% $\varrho = \sqrt{r - h}$.
-The calculation of the escape probabilities is not affected by this problem because of the factor $y$ that comes from the cosine of the angle described by the normal $\hat{n}$ and $\mathbf{\Omega}_p$, which cancels the endpoint singularity.
-The integral in $h$ can be resolved numerically with weights and points by the Gauss-Legendre quadrature in absence of endpoint singularities.
+Singularity of the integrand for the $h$-integration is noticed in the convex part while computing the collision probabilities \cite{hebert2009applied,stamm1983methods}; this notably happens at the outer radius of the $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$.
+However, that integral can be regularized by a suitable change of variable, see appendix \ref{sec:apx_Flurig}.
+The calculation of the escape probabilities as presented in this section is not affected by this problem because of the factor $y$ that comes from the cosine of the angle described by the normal $\hat{n}$ and $\mathbf{\Omega}_p$, which cancels the endpoint singularity.
+The integral in $h$ can be resolved numerically with weights and points by the Gauss-Legendre quadrature in absence of the singularity.
 Gauss-Jacobi quadrature is recommended otherwise.
@@
 \begin{equation}
-\varepsilon_j(r) = \frac{2\pi}{r^2} \int_0^r { dh\, h y \int_{L_j}{
+\varepsilon_j(r) = \frac{2\pi}{r} \int_0^r { dh\, h y \int_{L_j}{
   d \ell \, \exp\left[-\tau( y, y - \ell )\right]}}.
@@
 
+The probabilities used to solve the integral transport equation can treat a volume or surface source, and similarly for the target quantity after emission.
+Indeed, they consider only the first flight of particles until collision in the target or leakage from its boundary (being still uncollided).
+The first flight collision probability is then the probability that a neutron emitted isotropically in a cell volume suffers its first collision in another or within itself.
+This is equivalent to count the number of first collisions in the same target volume produced by a unitary source in the starting volume.
+This number cannot be an integer of course.
+
 After all escape and inscape probabilities are known, the first flight collision probabilities can be determined by conservation properties in order to reduce the amount of total operations.
-For instance, the probability for a neutron emitted isotropically in the region $i$ to collide in the same region must fulfill the following relation:
+The escape probabilities obtained from Eqs.
+\ref{eq:esc_prob_cyij} and \ref{eq:esc_prob_cyij-} yield the number of neutrons leaving a surface uncollided along its normal direction, that is by weighting with the director cosine between their current direction of flight and the normal itself.
+This does not yield the total escape probabilities used hereafter to conserve the neutron balance in the cells of the mesh.
+We must count all contributions arriving to a given point on a surface by $(\mathbf{\Omega}_p \cdot \mathbf{\Omega})$ instead of $(\hat{n} \cdot \mathbf{\Omega})$.
+Hence, the factor corresponding to the director cosine must be removed from integration in order to get the total escape probabilities.
+Gauss-Jacobi integration becomes then necessary to overcome the endpoint singularity, see appendix \ref{sec:apx_Flurig}.
+For instance, the probability $\tilde{p}$ for a neutron emitted isotropically in the region $i$ to collide in the same region must fulfill the following relation:
 \begin{subequations}
 \begin{equation}
-p_{ii} + e^+_{i+1/2,i} + e^-_{i-1/2,i} = 1 \; \forall i.
+\tilde{p}_{ii} + \tilde{e}^+_{i+1/2,i} + \tilde{e}^-_{i-1/2,i} = 1, \: \forall i.
 \label{eq:pii}
 \end{equation}
-This can be generalized with neutrons coming from region $j$ and colliding in region $i$ as:
+$\tilde{e}$ denotes a total escape probability introduced above. This can be generalized with neutrons coming from region $j$ and colliding in region $i$ as:
 \begin{equation}
-p_{ij} = e^+_{i-1/2,j} - e^+_{i+1/2,j} + e^-_{i+1/2,j} - e^-_{i-1/2,j},
+\tilde{p}_{ij} = \tilde{e}^+_{i-1/2,j} - \tilde{e}^+_{i+1/2,j} + \tilde{e}^-_{i+1/2,j} - \tilde{e}^-_{i-1/2,j} + \delta_{ij},
 \label{eq:pij}
@@
 \end{subequations}
-with $e^+_{i-1/2,i} = e^-_{i+1/2,i} = 0$ to find again Eq. \ref{eq:pii}.
+with $\tilde{e}^\pm_{\mp 1/2,j} = 0$, $\forall j$ in the sphere and in the cylinder.
+A formulation resolving the integral Boltzmann equation by first-flight escape probabilities was already introduced by Bitelli and Turrin, who first noticed the advantage of simpler numerical integration for avoiding poles at endpoints \cite{bitelli1974evaluation,bitelli1976collision}.
 
-Particle conservation on the full domain requires $\sum_i p_{ij} + e^+_{I+1/2,j} = 1$, $\forall j$. At last, reciprocity implies
-\[
-  \frac{p_{ij}}{V_i \sigma_i} = \frac{p_{ji}}{V_j \sigma_j} \quad \text{and} \quad
-  \frac{p_{j, i+1/2}}{V_j \sigma_j} = \frac{4 e_{i+1/2, j}}{S_{i+1/2}} \quad \text{for } 1 \leq i,j, \leq I,
-\]
-with the escape probability counting for both contributions from partial currents. These expressions can be used to verify Eqs. \ref{eq:cps}.
+Particle conservation on the full domain requires $\sum_i \tilde{p}_{ij} + \tilde{e}^+_{I+1/2,j} = 1$, $\forall j$. At last, reciprocity implies
+\begin{subequations}
+\label{eq:reciprocity}
+\begin{gather}
+  \frac{\tilde{p}_{ij}}{V_i \sigma_i} = \frac{\tilde{p}_{ji}}{V_j \sigma_j} \quad \text{and} \label{eq:reciprocity1}\\
+  \frac{\tilde{p}_{j, i+1/2}}{V_j \sigma_j} = \frac{\tilde{e}^+_{i+1/2, j} + \tilde{e}^-_{i+1/2, j}}{S_{i+1/2}}, % / 4 ?
+  \label{eq:reciprocity2}
+\end{gather}
+\end{subequations}
+for $1 \leq i,j, \leq I$. % and with the escape probability counting for both contributions from partial currents. These expressions
+Eq.
+\ref{eq:reciprocity1} can also be used to verify the implementation of the escape probabilities.
+Collision probabilities with surface source emission from Eq.
+\ref{eq:reciprocity2} are needed with non-zero entering currents of neutrons at the boundary $x_{I+1/2}$.
+This probability refers to an entering angular flux.
+It must be divided by 4 when using an isotropic entering current, also known as cosine current.
 
-Transmission probabilities between surfaces are also needed with boundary conditions different from vacuum. We do not derive them in this work because we only treat bare problems.
+Transmission probabilities between surfaces are also needed in response matrix formulations and with boundary conditions different from vacuum.
+The response matrix formulation partitions the calculation domain in separate blocks, which exchange out-going and entering partial currents to update their internal distributions of reaction rates.
+We do not derive them in this work because we only treat bare problems.
+The method to solve the integral transport equation by the collision probability method providing reference solutions for the Ronen method is reported in appendix \ref{sec:CPMsolution}.
+
+It might not be possible to compute the escape probabilities as derived in this work using existing computer codes that employ the collision probability method without code modifications.
+In fact, existing codes usually calculate directly the collision probabilities, by which all other probabilities are determined next using reciprocity and conservation properties.
+Besides, these codes only need to calculate the escape probability from the outer boundary surface.
 
@@
 
+\appendix
+\section{APPENDIX. Gauss-quadratures}
+\label{sec:apx_Flurig}
+
+The integrals used in the calculation of the probabilities in the cylindrical and spherical frames are in the form:
+\[
+  I = \int_{r_{i-1/2}}^{r_{i+1/2}}{dh K(\ell(h))},
+\]
+and they are often evaluated numerically by Gauss-quadratures.
+The integrand can show an endpoint singularity in the first derivative when integrating in the convex regions, since $d_h K = \partial_{\ell} K\, \partial_{\ell}h$ and
+\[
+  \lim_{h \rightarrow r_{i+1/2}}
+    \frac{-2h}{\sqrt{r_{i+1/2}^2 - h^2}} = -\infty,
+\]
+for $\ell = 2\sqrt{r_{i+1/2}^2 - h^2}$ \cite{hebert2009applied}.
+The use of a Gauss-Legendre quadrature with $N$ points in the integration interval is a good choice only if the integrand is continuous over the interval up to order $2N$.
+Gauss-Legendre quadrature integrates exactly polynomials of degree less than $2N$.
+The definite integrals can be regularized by a proper change of variable, known as the Flurig scheme, which yields a Gauss-Jacobi quadrature scheme.
+We propose herafter a general change of variable to obtain both schemes at once:
+\begin{equation}
+\label{eq:varchange}
+  \varrho = 1 - 2 \left(
+      \frac{r_{i+1/2} - h}{\Delta r_i} \right)^{(1-\alpha/2)}
+\end{equation}
+with $\Delta r_i = r_{i+1/2} - r_{i-1/2}$ that yields
+\begin{equation}
+\label{eq:quad}
+  I = \frac{\Delta r_i}{2}\int_{-1}^{1}{
+    d\varrho (1-\varrho)^\alpha
+%             (1+\varrho)^\beta
+             K(\ell(\varrho))}
+    = \sum_{n=1}^N{w_n K(\ell(h_n))},
+\end{equation}
+with the Gauss-Legendre scheme for $\alpha = 0$ and the Gauss-Jacobi scheme for $\alpha = 1$.
+%with the Gauss-Legendre scheme for $a=1$ ($\alpha = 0$, $\beta = 0$) and the Gauss-Jacobi scheme for $a=1/2$ ($\alpha = 1$, $\beta = 0$).
+After retrieving the weights $v_n$ and the roots $\varrho_n$ of the selected $N$-point quadrature in $[-1, +1]$, the weights and roots to use in Eq. \ref{eq:quad} are respectively:
+\begin{equation}
+\label{eq:wnrn}
+  w_n = \frac{\Delta r_i}{2} v_n \quad \text{and} \quad
+  h_n = r_{i+1/2}
+      - \left(\frac{1-\varrho_n}{2}\right)^{(1+\alpha)}
+        \Delta r_i.        
+\end{equation}
+Weights and roots are obtained by the Scipy v1.4.1 library (special.roots\_jacobi) and Numpy v1.18.2 (polynomial.legendre.leggauss).
+We note that the values from these libraries are different from the ones printed in the cited textbooks \cite{hebert2009applied,stamm1983methods}.
+
+\section{APPENDIX. Direct solution of integral transport by the collision probabilty method}
+\label{sec:CPMsolution}
+
+The integral transport equation for the scalar flux can be written using the first flight collision probabilities as \cite{hebert2009applied}:
+\begin{subequations}
+\label{eq:cmp_eqn}
+\begin{equation}
+\label{eq:cmp1_eqn}
+V_i \sigma_i \phi_i = \sum_{j=1}^I {q_j V_j \tilde{p}_{ij}}
+                    + J^{(-)}_{b}S_{b} \tilde{p}_{ib},
+\end{equation}
+where $b$ stands for any boundary with a non-zero entering current.
+$b=I+1/2$ for the cylindrical and for the spherical geometries, whereas two incoming currents can be present in the slab.
+This equation can be simplified further by using the reciprocity property from Eqs.
+\ref{eq:reciprocity},
+\begin{equation}
+\label{eq:cmp2_eqn}
+\phi_i = \sum_{j=1}^I {q_j p_{ji}} + J^{(-)}_{b} \tilde{e}_{bi}
+\end{equation}
+\end{subequations}
+with the reduced escape probability $p_{ji} = \tilde{p}_{ji} / \sigma_j$ and the escape probability counting for both the signed terms.
+The incoming current at the boundary can be given as fixed external source, or being expressed as proportional to the out-going current by means of the albedo $0 \leq \beta \leq 1$, like
+\begin{equation}
+\label{eq:albedo}
+  J^- = \beta J^+ = \beta \left(
+      \sum_{j=1}^I {q_j p_{jb}} + \tilde{t} J^-
+    \right),
+\end{equation}
+with the reduced collision probability from the surface at $x_b$ thanks again to reciprocity.
+About \ref{eq:reciprocity2}, reciprocity considers entering neutrons distributed according to the cosine described by the direction of flight and the normal to the same surface, yielding a cosine current by $J^\pm = \phi/4$, suitable to reproduce white reflection with $\beta = 1$.
+%yields the white reflection, that is isotropic inwards redistribution of the outgoing current, regardless of the outgoing direction.
+The transmission $\tilde{t}$ is the probability that a neutron enters the outer surface with the cosine distribution, travels  inwards and leaves it back again without colliding.
+Conservation implies that $\tilde{t} = 1 - \sum_j{\tilde{p}_{jb}}$.
+
+The source term considers only isotropic emission, and it is composed by scattering and fission production as in Eq.
+\ref{eq:srclg0}.
+In absence of external sources, the problem becomes homogeneous with the multiplication factor $k$ assuming the role of eigenvalue to avoid the only vanishing solution.
+Eqs.
+\ref{eq:cmp_eqn} hold for any energy group, whose index is dropped for simplicity.
+
+We setup hereafter an algebraic system equations for the unknown flux array $\vec{\phi}$ of size $(I \times G)$, flattened with the index of the spatial mesh running first.
+The extension of the solution method to problems with external sources in submultiplicative media is straightforward.
+Eq.
+\ref{eq:cmp2_eqn} for bare bodies, that is in presence of vacuum boundary condition, is rewritten as:
+\begin{equation}
+\label{eq:cpm_syseqns}
+(\mathbf{I} - \mathbf{P}\mathbf{S}) \vec{\phi}^{(n+1)} = \mathbf{P} (\chi \otimes \mathbf{F}) \vec{\phi}^{(n)} / k^{(n)},
+\end{equation}
+where the index $n$ addresses power method iterations to solve the eigenvalue problem.
+All matrices in Eq.
+\ref{eq:cpm_syseqns} are constructed by blocks.
+The matrix $\mathbf{P}$ is block diagonal with all (transposed) matrices of reduced collision probabilities per group, placed in increasing order from the fast groups, which are assigned to the lowest values of the index $g$ as usual.
+The matrix $\mathbf{S}$ is composed by $G \times G$ diagonal blocks with elements $[\sigma_{s, g \leftarrow g',j}\delta_{ij}, \, i, j=1, \ldots, I]$, contrary to the matrix $\mathbf{F}$ which has only G blocks set by columns and with elements $[\nu\sigma_{f, g, j}\delta_{ij}, \, i, j=1, \ldots, I]$.
+The new estimate of the flux vector is computed by multiplying the left side of the equation by the inverse of the removal matrix, i.e.
+$(\mathbf{I} - \mathbf{S} \mathbf{P})^{-1}$, assuming that it is invertible.
+The new estimate of the eigenvalue can be obtained by enforcing neutron conservation through the iterations, while achieving the convergence:
+\[
+  k^{(n+1)} = k^{(n)}
+    \frac{\langle \vec{\phi}^{(n+1)} | \mathbf{F} \vec{\phi}^{(n+1)} \rangle}{\langle \vec{\phi}^{(n+1)} | \mathbf{F} \vec{\phi}^{(n)} \rangle}.
+\]
+The full eigen-spectrum can be obtained by resolving the problem for the fission production reaction rates, showing smaller rank.
+First, note that $(\chi \otimes \mathbf{F}) = \mathbf{X} \mathbf{F}$, with $\mathbf{X}$ built by $G$ diagonal blocks stacked per row of the form $[\chi_{g,j}\delta_{ij}, \, i, j=1, \ldots, I]$.
+The eigen-solver operates then on the matrix $\mathbf{F}(\mathbf{I} - \mathbf{S} \mathbf{P})^{-1} \mathbf{P} \mathbf{X}$.
+
+In case of partial currents given by an albedo relation at the boundary, the same solving scheme still holds after redefinition of the matrix $\mathbf{P}$:
+\[
+\mathbf{P} \leftarrow \mathbf{P} + \frac{\beta}{1 - \beta \tilde{t}} \mathbf{E},
+\]
+with $\mathbf{E}=[\tilde{e}_{bi} p_{jb},\; 1 \leq i,j \leq I]$.
+
 \setlength{\baselineskip}{12pt}

### 2020-04-10 CPM1D/KinPy/wrap_f77_to_pylib_mingw64.sh

@@ -1,0 +1,24 @@
+# how to produce the wrapped algo609 lib
+FOPTS='-ffixed-line-length-72 -std=legacy'
+#  -Wextra -Wall -fPIC
+ONLYS='dbskin bskin'
+
+# Daniele uses gfortran from gcc 8.3.0
+# GCCPATH=/data/tmplca/dtomatis/tools/gcc/gcc-8.3.0
+F77=gfortran
+F90=gfortran
+# INC=$GCCPATH/lib64
+# INC=/c/msys64/mingw64/x86_64-w64-mingw32/lib/
+INC=/c/msys64/mingw64/lib/gcc/x86_64-w64-mingw32/9.3.0/
+#INC=/c/msys64/mingw64/x86_64-w64-mingw32/lib/
+#PYT=c:/Users/dt247226/AppData/Local/Programs/Python/Python38/python.exe
+PYT=python
+LIBS=-llibquadmath
+
+unset LD_LIBRARY_FLAGS   # just in case was set before
+export LDFLAGS=-Wl,-rpath=$INC
+export NPY_DISTUTILS_APPEND_FLAGS=1
+#  --f77exec=$F77 --f90exec=$F90
+$PYT -m numpy.f2py -c --f77flags="$FOPTS" --f90flags="$FOPTS" \
+  --fcompiler=gnu95 --compiler=mingw32 algo609.f \
+  only: $ONLYS : -m algo609

### 2020-04-10 CPM1D/cpm1dcurv.py

@@ -10,6 +10,12 @@ probabilities in 1D curvilinear geometries.
           to have the target value Ki_n(x) (n is the order of Ki). This is not
           necessary when calculating Ki_n(0) for any order n.
 """
+# Owned
+__title__ = "Calculation of CP in 1D curvilinear geometries"
+__author__ = "D. Tomatis"
+__date__ = "30/08/2019"
+__version__ = "1.0.0"
+
 import os
 import sys
 import logging as lg
@@ -18,10 +24,11 @@ from scipy.special import expn as En
 from scipy.special import roots_jacobi
 from KinPy.algo609 import dbskin as Ki
 
-__title__ = "Calculation of CP in 1D curvilinear geometries"
-__author__ = "D. Tomatis"
-__date__ = "30/08/2019"
-__version__ = "1.0.0"
+sys.path.append(
+    os.path.join(os.path.dirname(__file__), '..', 'FD1dMGdiff')
+)
+from FDsDiff1D import input_data, unfold_xs, compute_cell_volumes, \
+                      compute_cell_surfaces
 
 
 # useful constants
@@ -29,21 +36,81 @@ Ki1_at_0, Ki2_at_0, Ki3_at_0 = Ki(0.,1,1,1)[0], Ki(0.,2,1,1)[0], Ki(0.,3,1,1)[0]
 geometry_type = "cylinder"  # cylinder or sphere only
 max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
-np.set_printoptions(precision=5)
+np.set_printoptions(precision=10)
+
+
+class solver_options:
+    """Object collecting (input) solver options."""
+    toll = 1.e-6  # default tolerance
+    nbitsmax = 100  # default nb. of max iterations (its)
+
+    def __init__(self, iitmax=nbitsmax, oitmax=nbitsmax,
+                 otoll=toll, itoll=toll, ks=None, GQ="Gauss-Jacobi"):
+        self.oitmax = oitmax  # max nb of outer iterations
+        self.iitmax = iitmax  # max nb of inner iterations
+        self.otoll = otoll  # tolerance on fiss. rates at outer its.
+        self.itoll = itoll  # tolerance on flx at inner its.
+        self.ks = ks  # nb. of quadrature point per cell
+        self.GaussQuadrature = GQ  # type of Guass quadrature along
+                                   # the h axis in curvilinear coords.
+        self.betaL = 0  # partial current albedo left
+                        # (not used in curv. geoms)
[…]

### 2020-04-10 CPM1D/tests/CP_empty_cylinder.py

@@ -1,0 +1,56 @@
+# --*-- coding:utf-8 --*--
+"""
+Calculate the collision probabilities in the empty cylinder.
+They must be equal to the area in the circle subtended by the
+radial arcs.
+"""
+import os, sys
+import logging as lg
+import numpy as np
+sys.path.insert(0, os.path.join(os.getcwd(), ".."))
+from cpm1dcurv import *
+
+
+if __name__ == "__main__":
+
+    logfile = os.path.splitext(os.path.basename(__file__))[0] + '.log'
+    lg.basicConfig(level=lg.INFO)  # filename = logfile
+    lg.info("* verbose output only in DEBUG logging mode *")
+    geometry_type = "cylinder"
+
+    # nb of rings in the cylinder
+    L = 1. / np.pi**.5  # cm, body thickness
+    I = 2  # number of cells in the spatial mesh
+    # r = np.linspace(0, L, I+1)
+    r = equivolume_mesh(I, 0, L, geometry_type)
+    # r = np.array([0., .075, .15]); I = r.size - 1;  # test
+    V = calculate_volumes(r, geometry_type)
+    np.testing.assert_allclose(V, np.ones(I) / float(I),
+        err_msg="Equal volumes are not verified")
+    ks = np.full(I, 8)  # quadrature order for each spatial cell
+
+    G = 1  # nb of energy groups
+    # c = 0.5  # number of secondaries by scattering
+    st = np.ones(G) * 1.e-8
+    st_r = np.tile(st, (I, 1)).T
+    # ss_r = c * st_r
+    # # we use st / 8 for nsf
+    # nsf_r = 0.125 * st_r
+
+    tr_data = calculate_tracking_data(r, ks, quadrule="Gauss-Jacobi")
+
+    eP, cP = calculate_probs(r, st_r, tr_data, V, geometry_type)
+    
+    print('CP :\n' + str(cP[0, :, :]))
+    print('EP+:\n' + str(eP[0, :, :, 0]))
+    print('EP-:\n' + str(eP[0, :, :, 1]))
+    
+    ePp, ePm = np.ones((I, I),), np.zeros((I, I),)
+    ePp[0, 1] = 0.3183098
+    ePm[0, 1] = -ePp[0, 1]
+    np.testing.assert_allclose(cP[0, :, :], np.zeros((I, I),),
+        atol=1.e-7, err_msg="CP should be all zeros!")
[…]

### 2020-04-10 CPM1D/tests/MC2011_2G_cylinder_test.py

@@ -1,0 +1,60 @@
+# --*-- coding:utf-8 --*--
+"""
+Solve the integral transport equation in the cylinder by CPM
+using the two group data from the MC2011 article.
+"""
+import os, sys
+import logging as lg
+import numpy as np
+sys.path.append(os.path.join(os.getcwd(), ".."))
+from cpm1dcurv import *
+
+sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
+from data.homog2GMC2011 import *
+
+# from FDsDiff1D import input_data
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
+
+
+if __name__ == "__main__":
+
+    lg.basicConfig(level=lg.INFO)  # filename = logfile
+    lg.info("Solve the MC2011 problem by CPM in the cylinder")
+    geometry_type = "cylinder"
+
+    # definition of the spatial mesh
+    L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
+    I = 4  # number of cells in the spatial mesh
+    # r = np.linspace(0, L, I+1)
+    r = equivolume_mesh(I, 0, L, geometry_type)
+    # r = np.array([0., .075, .15]); I = r.size - 1;  # test
+    # volumes in input_data are per steradiant angle and differ from
+    # the following ones
+    # V = calculate_volumes(r, geometry_type)
+    
+    ks = np.full(I, 2)  # quadrature order for each spatial cell
+    GaussQuadrature = "Gauss-Jacobi"  # type of Gauss quadrature
+    
+    xs_media = {
+        'HM':{  # homogeneous medium
+            'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
+        }
+    }
+    media = [['HM', L]]  # i.e. homogeneously filled
+
+    Homog2GSlab_data = input_data(xs_media, media, r,
+                                  geometry_type, LBC=2, RBC=2,
+                                  per_unit_angle=False)
+    slvr_opts = solver_options(GQ=GaussQuadrature, ks=ks)
+    
+    k, flx = solve_cpm1D(Homog2GSlab_data, slvr_opts)
+    
+    flxinf = np.dot(np.linalg.inv(np.diag(st) - ss[:,:,0]), chi)
+    kinf = np.dot(nsf, flxinf)  # 1.07838136
+    flxinf *= np.linalg.norm(flx[:, 0]) / np.linalg.norm(flxinf)
[…]

### 2020-04-10 CPM1D/tests/MC2011_2Gtest.py

@@ -1,0 +1,60 @@
+# --*-- coding:utf-8 --*--
+"""
+Solve the integral transport equation in the cylinder by CPM
+using the two group data from the MC2011 article.
+"""
+import os, sys
+import logging as lg
+import numpy as np
+sys.path.append(os.path.join(os.getcwd(), ".."))
+from cpm1dcurv import *
+
+sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
+from data.homog2GMC2011 import *
+
+# from FDsDiff1D import input_data
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
+
+
+if __name__ == "__main__":
+
+    lg.basicConfig(level=lg.INFO)  # filename = logfile
+    lg.info("Solve the MC2011 problem by CPM in the cylinder")
+    geometry_type = "sphere"
+
+    # definition of the spatial mesh
+    L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
+    I = 4  # number of cells in the spatial mesh
+    # r = np.linspace(0, L, I+1)
+    r = equivolume_mesh(I, 0, L, geometry_type)
+    # r = np.array([0., .075, .15]); I = r.size - 1;  # test
+    # volumes in input_data are per steradiant angle and differ from
+    # the following ones
+    # V = calculate_volumes(r, geometry_type)
+    
+    ks = np.full(I, 2)  # quadrature order for each spatial cell
+    GaussQuadrature = "Gauss-Jacobi"  # type of Gauss quadrature
+    
+    xs_media = {
+        'HM':{  # homogeneous medium
+            'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
+        }
+    }
+    media = [['HM', L]]  # i.e. homogeneously filled
+
+    Homog2GSlab_data = input_data(xs_media, media, r,
+                                  geometry_type, LBC=2, RBC=2,
+                                  per_unit_angle=False)
+    slvr_opts = solver_options(GQ=GaussQuadrature, ks=ks)
+    
+    k, flx = solve_cpm1D(Homog2GSlab_data, slvr_opts)
+    
+    flxinf = np.dot(np.linalg.inv(np.diag(st) - ss[:,:,0]), chi)
+    kinf = np.dot(nsf, flxinf)  # 1.07838136
+    flxinf *= np.linalg.norm(flx[:, 0]) / np.linalg.norm(flxinf)
[…]

### 2020-04-10 FD1dMGdiff/FDsDiff1D.py

@@ -102,14 +102,15 @@ class input_data:
     conditions: 0-vacuum, 1-zero flux and 2-reflection. Units are in cm."""
 
     def __init__(self, xs_media, media, xi, geometry_type='slab',
-                 LBC=0, RBC=0):
-        self.geometry_type, self.xi = geometry_type, xi
+                 LBC=0, RBC=0, per_unit_angle=True):
+        self.geometry_type, self.xi = geometry_type.lower(), xi
         self.LBC, self.RBC = LBC, RBC
         self.xs_media, self.media = xs_media, media
         self.check_input()
         self.compute_cell_width()
         # self.compute_mid_cell_coordinate()
-        self.compute_cell_volumes()
+        self.compute_cell_surfaces(per_unit_angle)
+        self.compute_cell_volumes(per_unit_angle)
 
     @property
     def I(self):
@@ -137,18 +138,24 @@ class input_data:
     def compute_cell_width(self):
         self.Di = self.xi[1:] - self.xi[:-1]
     
-    # def compute_mid_cell_coordinate(self):
-    #     self.xim = xim(self.xi)
+    def compute_mid_cell_coordinate(self):
+        self.xim = xim(self.xi)
     
+    def compute_cell_surfaces(self, per_unit_angle=True):
+        self.Si = compute_cell_surfaces(self.xi, geo=self.geometry_type,
+                                        per_unit_angle=per_unit_angle)
     
-    def compute_cell_volumes(self):
-        self.Vi = compute_cell_volumes(self.xi, geo=self.geometry_type)
+    def compute_cell_volumes(self, per_unit_angle=True):
+        self.Vi = compute_cell_volumes(self.xi, geo=self.geometry_type,
+                                       per_unit_angle=per_unit_angle)
 
     def check_input(self):
         lg.info("Geometry type is " + self.geometry_type)
         if (self.geometry_type != 'slab') and \
+           (self.geometry_type != 'cylinder') and \
            (self.geometry_type != 'cylindrical') and \
-           (self.geometry_type != 'spherical'):
+           (self.geometry_type != 'spherical') and \
+           (self.geometry_type != 'sphere'):
             raise ValueError('Unknown geometry_type ' + self.geometry_type)
         if not isinstance(self.LBC, int):
[…]

### 2020-04-10 SNMG1DSlab/snmg1dslab.py

@@ -63,11 +63,9 @@ import warnings as wrn
 import numpy as np
 from scipy.special import roots_legendre, legendre
 
-# INFO: the following makes execution working only when running the
-# module within this same directory
-sys.path.append('..XFD1dMGdiff'.replace('X', os.path.sep))
-# WARNING: before importing snmg1dslab, check the pythonpath for the
-# following import to properly work.
+sys.path.append(
+    os.path.join(os.path.dirname(__file__), '..', 'FD1dMGdiff')
+)
 from FDsDiff1D import input_data, solver_options, unfold_xs
 
 

### 2020-04-10 docs/ICTT2019/RMethod_ictt26.tex
Fix code and doc (ICTT26 paper) after noticing the mistaken use of the director cosine as weight at integration of escape probabilities in the annular geometries.

@@
 \end{equation}
-that is considering the contribution of the source $q$ within the distance $S'(\mathbf{r}, \mathbf{\Omega})$ from the boundary, and the possible entering amount of particles therein.
-We examine first the case of the cylinder.
-In planar geometry the angular flux and the source do not depend on the coordinate $z$.
+that is considering the contribution of the source $q$ within the distance $S'(\mathbf{r}, \mathbf{\Omega})$ from the boundary and the possible entering amount of particles therein.
+All contributions are collected at $\mathbf{r}$ by exponential attenuation along the travelled optical path, that is according to the probability of still continuing the first flight after emission.
+We examine first the case of the cylinder as a particular case of the 2-D frame.
+In planar geometry the angular flux and the source do not depend on the axial coordinate $z$.
 Hence, the position on the characteristic line identified by $\mathbf{\Omega}$ is projected on the $x$-$y$ plane (see Fig.
-\ref{fig:fullframe}): $\varphi(\mathbf{r} - s' \mathbf{\Omega},\mathbf{\Omega}) = \varphi(\mathbf{r} - s \mathbf{\Omega}_p,\mathbf{\Omega})$ and likewise for $q$, with the unit vector $\mathbf{\Omega}_p$ lying on the $x$-$y$ plane.
+\ref{fig:fullframe}): $\varphi(\mathbf{r} - s' \mathbf{\Omega},\mathbf{\Omega}) =\allowbreak \varphi(\mathbf{r} - s \mathbf{\Omega}_p,\mathbf{\Omega})$ and likewise for $q$, with the unit vector $\mathbf{\Omega}_p$ lying on the $x$-$y$ plane.
 $\theta$ is the polar angle measured between $\hat{e}_z$ and $\mathbf{\Omega}$.
@@
 \ref{eq:ITE_xy} over the solid angle $d\mathbf{\Omega} = \sin \theta d\omega d \theta$ yields the scalar flux at the point $\mathbf{r}$.
-The theory of collision probability methods originates from the use of isotropic sources, which are also considered as uniform in the cells of the spatial mesh.
+The theory of collision probability methods originates from the use of flat isotropic sources in the cells of the spatial mesh.
 The use of anisotropic sources with spatial variation in the same cells, for instance polynomial-like, is possible but leads to much more difficult expressions to solve.
 Two integrations in space arise for each direction $\mathbf{\Omega}$, connecting the source in region $j$ to the flux (or its total reaction rate) in region $i$ by means of its collision probability.
-The incoming flux is considered as isotropic too, or linearly anisotropic in angle as in \cite{hebert2009applied} to relate the partial entering and outgoing currents to the only first flux moments.
+The incoming flux is usually considered as isotropic too, or linearly anisotropic in angle as in \cite{hebert2009applied} to relate the partial entering and outgoing currents to the only first flux moments.
 These partial currents on the boundary must satisfy a general condition of albedo.
 
-Using standard nomenclature of collision probability methods, transfer probabilities are derived to take into account of the contributions in the equation for the $i$-th scalar flux (or total rate) of neutrons leaving a given surface.
-Escape probabilities account for neutrons produced in a given region and leaving a surface uncollided instead.
+Using standard nomenclature of collision probability methods, transfer probabilities refer to particles entering the problem domain and leaving it without incurring into any collision.
+They can provide the probability of reflection in case the entering and the leaving surfaces are the same.
+The probability of escape deals with neutrons produced in a given region and leaving a surface, still uncollided.
+These probabilities are employed to write the integral transport equations for the volume-averaged scalar flux (or its total reaction rate) in each cell, and the surface-averaged currents at the cell interfaces.
 
@@
 Higher moments can be obtained by the weights associated to the corresponding spherical harmonics.
-Integrations along the polar angle are resolved with the introduction of the Bickley-Naylor functions \cite{amos1983uniform}:
+Integration along the polar angle is resolved analytically by the Bickley-Naylor functions \cite{amos1983uniform}:
 \begin{equation}
@@
 \end{equation}
-The properties used for the computation of these functions are available elsewhere \cite{lewis1984computational,hebert2009applied,amos1983algorithm}.
+The properties used for the computation of these functions are available elsewhere \cite{lewis1984computational,hebert2009applied}.
+We use the fortran library by Amos from 1983 in this work \cite{amos1983algorithm}.
 
@@
 
-Another integration on the total surface $S(r) = 2\pi r$ is necessary to obtain the current density in the 1-D frame.
+Another integration on the total surface $S(r) = \int{r d\theta'} = 2\pi r$, with $\theta' = \hat{n}\cdot \mathbf{\Omega}_p$, is necessary to obtain the current density in the 1-D frame.
 For a given angle $\omega$, we have then volume integrals to solve numerically along many parallel lines called tracks, see Fig.
-\ref{fig:cyltracks}.
-Furthermore, the tracks are identical for any angle $\omega$ in the 1-D cylindrical geometry simplifying the integrals in Eqs.
+\ref{fig:cyltracks}, for $r d\theta' = dh/\cos \theta'$.
+Furthermore, the tracks are identical for any angle $\omega$ in the 1-D cylindrical geometry factoring out $2\pi$ from the integrals in Eqs.
 \ref{eq:currp_cylinder}, which can also be limited to half portion of the cylinder thanks to its symmetry.
@@
 \begin{equation}
-J^\pm(r) = \pm \frac{1}{\pi r^2} \int_0^r { dh\, y \int_{-Y}^{\pm y}{
-  d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right] q(h, y - \ell)}}
+% J^\pm(r) = \pm \frac{1}{\pi r^2} \int_0^r { dh\, y
+J^\pm(r) = \pm \frac{1}{\pi r} \int_0^r { dh\,
+    \int_{-Y}^{\pm y}{d \ell \,
+      \text{Ki}_2\left[\tau( y, y - \ell )\right] q(h, y - \ell)}}
 \label{eq:currp_cyl_atr}
@@
 After multiplication by $S(r)$ and still with uniform sources, Eq.
-\ref{eq:currp_cyl_atr} can be written in terms of the escape probability $e_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided along the normal direction the semicylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
+\ref{eq:currp_cyl_atr} can be written in terms of the escape probability $\tilde{e}_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided along the normal direction the semicylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
 \begin{equation}
-J^\pm(r)S(r) = \sum_j q_j V_j \left[ \pm e^\pm_j(r) \right] \mbox{ with }
-e^\pm_j(r) = \frac{2}{r V_j} \int_0^r { dh\, y \int_{L^\pm_j}{
-  d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right]}},
+J^\pm(r)S(r) = \sum_j q_j V_j \left[ \pm \tilde{e}^\pm_j(r) \right] \mbox{ with }
+% e^\pm_j(r) = \frac{2}{r V_j} \int_0^r { dh\, y
+\tilde{e}^\pm_j(r) = \frac{2}{V_j} \int_0^r { dh\,
+  \int_{L^\pm_j}{d \ell \, \text{Ki}_2\left[\tau( y, y - \ell )\right]}},
 \label{eq:esc_prob_cyl}
@@
 \ref{fig:mesh1D} is used for the radial mesh.
-The current leaving the $i$-th ring at $r_{i+1/2}$ gets all source contributions weighted with the quantities $\varepsilon^+_{i+1/2,j} = V_j e^+_{i+1/2,j}$:
+The current leaving the $i$-th ring at $r_{i+1/2}$ gets all source contributions weighted with the quantities $\varepsilon^+_{i+1/2,j} = V_j \tilde{e}^+_{i+1/2,j}$:
 %
@@
   \begin{gathered}
-  \varepsilon^+_{i+1/2,j} = \frac{2}{r_{i+1/2}} \cdot\\
+  % \varepsilon^+_{i+1/2,j} = \frac{2}{r_{i+1/2}} \cdot\\
+  \varepsilon^+_{i+1/2,j} = 2\: \cdot\\
   %\left\{
   \begin{cases}
-  \displaystyle ~\int_0^{r_{i-1/2}} { dh\, y
+%  \displaystyle ~\int_0^{r_{i-1/2}} { dh\, y
+  \displaystyle ~\int_0^{r_{i-1/2}} { dh\,
     \int_0^{\ell_j}{ d\ell \bigg[ }}\\[3mm] \qquad
@@
 The radial integral includes all rings within $r_{i+1/2}$.
-Reciprocity and conservation properties can be applied only after calculating the collision probabilities.
 The integrals involving the Ki function are solved thanks to the property $d_{\tau}\text{Ki}_n(\tau) = -\text{Ki}_{n-1}(\tau)$.
@@
 \label{eq:esc_prob_cyij-}
-  \varepsilon^-_{i+1/2,j} = \frac{2}{r_{i+1/2}}
-    \displaystyle ~\int_0^{r_{i+1/2}} { dh\, y
+%  \varepsilon^-_{i+1/2,j} = \frac{2}{r_{i+1/2}}
+  \varepsilon^-_{i+1/2,j} = 2
+    \displaystyle ~\int_0^{r_{i+1/2}} { dh\, % y
         \int_0^{\ell_j}{
@@
 for $i<j$, whereas $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergoing a collision.
+The useful reciprocity and conservation properties commonly used in CPM solvers to save the total computational effort can be applied only after calculating the first flight collision probabilities.
 
-Singularity of the integrand for the $h$-integration is noticed in the convex part while computing the collision probabilities \cite{hebert2009applied,stamm1983methods}; this notably happens at the outer radius of the $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$.
+Singularity of the integrand for the $h$-integration is known in the convex part while computing the collision probabilities \cite{hebert2009applied,stamm1983methods}; this notably happens at the outer radius of the $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$.
 However, that integral can be regularized by a suitable change of variable, see appendix \ref{sec:apx_Flurig}.
-The calculation of the escape probabilities as presented in this section is not affected by this problem because of the factor $y$ that comes from the cosine of the angle described by the normal $\hat{n}$ and $\mathbf{\Omega}_p$, which cancels the endpoint singularity.
-The integral in $h$ can be resolved numerically with weights and points by the Gauss-Legendre quadrature in absence of the singularity.
-Gauss-Jacobi quadrature is recommended otherwise.
+The calculation of the escape probabilities as presented in this section is %not affected by this problem because of the factor $y$ that comes from the cosine of the angle described by the normal $\hat{n}$ and $\mathbf{\Omega}_p$, which cancels the endpoint singularity.
+also affected by this endpoint singularity.
+Because of this singularity, the integral in $h$ can then be resolved numerically with weights and points by the Gauss-Jacobi quadrature, which is one order more accurate than the common Gauss-Legendre quadrature.
 
@@
     \input{figures/sphere.tkz}
-    \caption{Use of symmetry in the sphere for integration in angle.}
+    \caption{Use of symmetry in the sphere for integration over the surface.}
     \label{fig:sphere_tracks}
@@
 
-The derivation of the scalar flux and current in the sphere follows the same rational adopted in section \ref{sec:cylinder} by angular integration of Eq.
+The derivation of the scalar flux and of the current in the sphere follows the same rational adopted in section \ref{sec:cylinder} by angular integration of Eq.
 \ref{eq:ITE_angflx} and exploiting the symmetries available in the given coordinate frame.
-It is now convenient to start counting the polar coordinate $\theta$ from the normal $\hat{n}=\hat{e}_r$ and to have the azymuthal angle $\omega$ lying on a plane perpendicular to it, see Fig.
+Because of the rotational symmetry any direction of flight lays on a spherical cut passing through the origin ($\mathbf{\Omega}_p = \mathbf{\Omega}$), see Fig.
 \ref{fig:sphere_tracks}.
-It can be noticed then that by symmetry all tracks crossing a spherical surface in a point with the same polar angle are the same for any azymuthal angle.
-Therefore, when integrating over the unit solid angle ($d\mathbf{\Omega}=\sin \theta d\omega d\theta$), the integration on $\omega$ is promptly factored out, becoming simply $2\pi$.
-Positive and negative radial partial currents are obtained respectively by integrating on $\theta \in [0, \pi/2)$ and $\theta \in (\pi/2, \pi]$ with weight $\hat{n} \cdot \mathbf{\Omega} = \cos \theta$.
-The final integration on the sphere of radius $r$ %and division by the spherical surface $S(r)=4\pi r^2$
-to get the total partial currents yields a situation similar to the case of the cylinder.
-The integration on the polar angle can be resolved again by the use of regularly spaced tracks at different values of $\theta$ covering the circular cut of the sphere that passes through the origin.
-Thanks to the central symmetry tracking integrals are the same for all directions, so that integration is carried on a semi-circle only, as in the case of the cylinder in Fig.
+The integration to carry for each direction $\mathbf{\Omega}$ over the spherical surface $S(r) = \int{r^2\sin \theta' d\theta' d\omega'} = 4\pi r^2$ shows a case similar to the cylinder of Fig.
+\ref{fig:cyltracks}, with integration on the semi-circle along the coordinate $h$, thanks to the axial symmetry around $\omega'$ that factors out $2\pi$, but with the new weight $h = r\sin \theta'$.
+The tracking integrals up to the spherical surface are the same for all directions, so that the integration over the unit solid angle yields simply $4\pi$, cancelling out the probability of isotropic emission used for the source.
+Fig.
+\ref{fig:sphere_tracks} is specific to the calculation of the positive radial partial currents.
+Negative partial currents need to consider the sources outside the depicted sphere of integration.
+
+%Thanks to the central symmetry tracking integrals are the same for all directions, so that integration is carried on a semi-circle only, as in the case of the cylinder in Fig.
 \ref{fig:cyltracks}.
@@
 \ref{eq:currp_cyl_atr}.
-Finally, Eq.
-\ref{eq:esc_prob_cyl} holds also for the sphere but using the new reduced escape probability:
+Using the same quantities defined in Eq. \ref{eq:currp_cyl_atr}, Eq. \ref{eq:esc_prob_cyl} holds also for the sphere but using the new reduced escape probability:
 \begin{equation}
-\varepsilon_j(r) = \frac{2\pi}{r} \int_0^r { dh\, h y \int_{L_j}{
-  d \ell \, \exp\left[-\tau( y, y - \ell )\right]}}.
+% \varepsilon_j(r) = \frac{2\pi}{r} \int_0^r { dh\, y
+\varepsilon_j(r) = 2\pi \int_0^r { dh\,
+  h \int_{L_j}{d \ell \, \exp\left[-\tau( y, y - \ell )\right]}}.
 \label{eq:esc_prob_sph}
 \end{equation}
-Endpoint singularities are avoided also in this case.
+Endpoint singularities at integration stand also in this case.
 The derivation of the equation for the current leaving the $i$-th spherical surface can be obtained straightforwardly from Eq.
@@
 The escape probabilities obtained from Eqs.
-\ref{eq:esc_prob_cyij} and \ref{eq:esc_prob_cyij-} yield the number of neutrons leaving a surface uncollided along its normal direction, that is by weighting with the director cosine between their current direction of flight and the normal itself.
+\ref{eq:esc_prob_cyij} and \ref{eq:esc_prob_cyij-} yield the number of neutrons leaving a surface uncollided.
+% along its normal direction, that is by weighting with the director cosine between their current direction of flight and the normal itself.
 This does not yield the total escape probabilities used hereafter to conserve the neutron balance in the cells of the mesh.
@@
 with $\tilde{e}^\pm_{\mp 1/2,j} = 0$, $\forall j$ in the sphere and in the cylinder.
-A formulation resolving the integral Boltzmann equation by first-flight escape probabilities was already introduced by Bitelli and Turrin, who first noticed the advantage of simpler numerical integration for avoiding poles at endpoints \cite{bitelli1974evaluation,bitelli1976collision}.
+A formulation resolving the integral Boltzmann equation by first-flight escape probabilities was already introduced by Bitelli and Turrin%, who also noticed the advantage of simpler numerical integration for avoiding poles at endpoints
+ \cite{bitelli1974evaluation,bitelli1976collision}.
 
@@
 \ref{eq:reciprocity2} are needed with non-zero entering currents of neutrons at the boundary $x_{I+1/2}$.
-This probability refers to an entering angular flux.
-It must be divided by 4 when using an isotropic entering current, also known as cosine current.
+This probability refers to an entering angular flux that must be still divided by 4 in case the flux is isotropic, yielding a cosine current typical of white reflection.
 
@@
 The response matrix formulation partitions the calculation domain in separate blocks, which exchange out-going and entering partial currents to update their internal distributions of reaction rates.
-We do not derive them in this work because we only treat bare problems.
 The method to solve the integral transport equation by the collision probability method providing reference solutions for the Ronen method is reported in appendix \ref{sec:CPMsolution}.
@@
 Gauss-Legendre quadrature integrates exactly polynomials of degree less than $2N$.
-The definite integrals can be regularized by a proper change of variable, known as the Flurig scheme, which yields a Gauss-Jacobi quadrature scheme.
+The definite integrals can be regularized by a proper change of variable following the Flurig scheme, which yields a Gauss-Jacobi quadrature scheme \cite{carlvik1966integral}.
 We propose herafter a general change of variable to obtain both schemes at once:

### 2020-04-10 CPM1D/cpm1dcurv.py

@@ -211,6 +211,8 @@ def calculate_escape_prob(r, st, tr_data, geometry_type="cylinder",
     curvilinear frames. The flag wcos allows to get escape probabilities
     weighted with the director cosines."""
     lg.debug("Calculate the reduced escape probabilities.")
+    if wcos == True:
+        raise RuntimeError("Attention, the cosine weight seems mistaken!")
     I = r.size - 1  # nb of rings
     if not np.all(np.diff(r) > 0):
         raise ValueError("Input values in r are not in increasing order")

### 2020-04-28 docs/ICTT2019/RMethod_ictt26.tex
Implement the CPM solver in the slab; the function calculating the (reduced) escape probabilities in the slab are still in the FDsDiff1D program - a reorganization of the code would help code readability; minor changes to the text of the ICTT26 article to follow the implementation.

@@
 \ref{eq:J_tr}.
-In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \phi_0(a) / 2$, yielding $J^+(x) = \phi_0(a)/2\, E_3 \left(\tau(a, x)\right)$.
+In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \phi_0(a) / 2$, yielding $J^+(x) = E_3 \left(\tau(a, x)\right)\phi_0(a)/2$.
 This approximation does not guarantee to obtain the expected vanishing current at the boundary when computing the same current at the boundary with symmetric flux distributions.
@@
 The derivation of the correction at the other boundary of the slab can easily be derived.
-Although this correction improves the results, it cannot yield exactly the same results of the unfolded geometry, that is without reproducing the half symmetry by reflection.
-This occurs because the small current difference is assumed only on the second moment, neglecting the others which may become relevant on case-dependent basis.
+Although this correction definitely improves the results, it cannot yield exactly the same results of the unfolded geometry, that is without reproducing the half symmetry by reflection.
+This occurs because the small current difference is allotted only to the second moment, neglecting the others which may become relevant on a case-dependent basis.
 
@@
 
-We resume here briefly the results of the two-group slab problem from \cite{tomatis2011application}.
-New results are also available for having new computer codes implemented with Python3.
+%We resume here briefly the results of the two-group slab problem from \cite{tomatis2011application}.
+New results are also available for having new computer codes implemented in Python v3.8.2 with the numerical libraries NumPy v1.18.2 and SciPy v1.3.2.
 The reference solution is provided by a S$_{16}$ discrete ordinate computer code.
@@
 %
-\begin{table}[htbp]
-\centering
-\caption{Reactivity differences in pcm by refining the mesh.\label{tab:kconv}}
-\begin{tabular}{c|r|r}
-\multirow{2}{*}{$I$} & \multicolumn{2}{|c}{$\Delta \rho$} \\ \cline{2-3}
-     & $it=0$ & $it=100$ \\ \hline
- ~50 & 550.22 & 170.35 \\
- 100 & 556.85 & ~36.08 \\
- 200 & 558.50 & ~~1.72
-\end{tabular}
-\end{table}
-
-The convergence on the flux is rather slow as shown in Fig.
+%\begin{table}[htbp]
+%\centering
+%\caption{Reactivity differences in pcm by refining the mesh.\label{tab:kconv}}
+%\begin{tabular}{c|r|r}
+%\multirow{2}{*}{$I$} & \multicolumn{2}{|c}{$\Delta \rho$} \\ \cline{2-3}
+%     & $it=0$ & $it=100$ \\ \hline
+% ~50 & 550.22 & 170.35 \\
+% 100 & 556.85 & ~36.08 \\
+% 200 & 558.50 & ~~1.72
+%\end{tabular}
+%\end{table}
+%
+%The convergence on the flux is rather slow as shown in Fig.
 \ref{fig:kflx} and Fig.
@@
 The corrections of the flux become smaller when iterating and a considerable number of iterations is necessary to approach the target results of the S$_{16}$ calculation.
+%
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics[width=.8\linewidth]{figures/kflxconv.pdf}
+%  \caption{Behavior of the convergence on the flux (right) and on the reacitivity (left) for $I = 200$.}
+%  \label{fig:kflx}
+%\end{figure}
+%%
+%\begin{figure}[hbtp]
+%  \centering
+%  \includegraphics[width=.8\linewidth]{figures/eflxconv.pdf}
+%  \caption{Relative variation of the flux though the RM iterations ($I = 200$).}
+%  \label{fig:eflx}
+%\end{figure}
 
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=.8\linewidth]{figures/kflxconv.pdf}
-  \caption{Behavior of the convergence on the flux (right) and on the reacitivity (left) for $I = 200$.}
-  \label{fig:kflx}
-\end{figure}
-%
-\begin{figure}[hbtp]
-  \centering
-  \includegraphics[width=.8\linewidth]{figures/eflxconv.pdf}
-  \caption{Relative variation of the flux though the RM iterations ($I = 200$).}
-  \label{fig:eflx}
-\end{figure}
+New computer programs have been developed in Python v3.8.2 with the numerical libraries NumPy v1.18.2 and SciPy v1.3.2 in order to solve the diffusion and the transport problems after calculating the first flight escape probabilities in the three geometries.
+The programs can treat heterogeneous media and use the multigroup formalism in energy, being intended for educational purposes.
 
-A one-group homogeneous problem is proposed hereafter in order to study the application of the Ronen method with angular redistribution in curvilinear geometries.
-Reference solutions are provided by collision probability method solvers, whose development take advantage of the implementation for the escape probabilities derived in section~\ref{sec:ce}.
-This choice is supported by the use of integral operators in the same Ronen method.
-Again, the implementation follows H\'ebert's textbook.
-The problems are solved in units of optical length, which means by simply setting the input total cross section equal to 1.
-The multiplying source becomes then $q = (c + \nu f) \phi_0 / 4\pi$, thus isotropic in angle, and with $c$ and $\nu f$ respectively as positive real numbers of secondaries per scattering and fission events.
-These numbers can be interpreted as conditional probabilities as well.
-The multiplicity $\nu$ acts as the eigenvalue of the problem.
-After the fundamental eigen-pair is known for given values of the constants and for a given size $L$, it is worthless to change $f$ alone to study the problem since only the product $\nu f$ counts for the balance (associated to the same eigenfunction).
-We choose then $f = 1$, ending up in only two free parameters for our study: $c_s$ and $L$.
-Even if this choice is unphysical for the assumed value of the total cross section together with $c > 0$, physical meaning is recovered by the fundamental value of $\nu$.
+We present in this section a one-group homogeneous problem with isotropic scatterinig to study qualititatively the behavior of the Ronen method with angular redistribution in the curvilinear geometries.
+The setup of a complete test suite with problems of increasing levels of complexity is planned as future research action.
+Reference solutions are provided by the collision probability method, whose implementation takes advantage of the escape probabilities derived in section~\ref{sec:ce}, and whose numerical solution is explained in appendix \ref{sec:CPMsolution}.
 
-\textcolor{red}{Roy will be able to check these assertions in the coming days.}
+The problem is resolved in units of optical length according to the change of variable $x \leftarrow \sigma x$, obtained after dividing the balance equation by the total cross section $\sigma$.
+The isotropically multiplying source becomes then $q = c \phi_0 / 4\pi$ with the number of secondaries from scattering or fission events $c = (\sigma_s + \nu \sigma_f)/\sigma$.
+The multiplicity $\nu$ assumes the role of eigenvalue in abscence of external sources.
+The size of the problem is simply $b$ with $a=0$.
+$c$ and $b$ are then the free parameters in the problem.
 
-\textcolor{blue}{The source assumes this form because the integration variables also have to the normalized by the mean free path (i.e. multiplied by the total cross section).}
+%\textcolor{blue}{The source assumes this form because the integration variables also have to the normalized by the mean free path (i.e. multiplied by the total cross section).}
 
-\textcolor{green}{The use of the integral transport eqn.
+%\textcolor{green}{The use of the integral transport eqn.
 to get reference solutions is motivated by two main reasons.

### 2020-04-28 CPM1D/cpm1dcurv.py

@@ -27,8 +27,9 @@ from KinPy.algo609 import dbskin as Ki
 sys.path.append(
     os.path.join(os.path.dirname(__file__), '..', 'FD1dMGdiff')
 )
-from FDsDiff1D import input_data, unfold_xs, compute_cell_volumes, \
-                      compute_cell_surfaces
+from FDsDiff1D import input_data, unfold_xs, \
+                      compute_cell_volumes, compute_cell_surfaces, \
+                      calculate_escape_prob_slab
 
 
 # useful constants
@@ -36,7 +37,7 @@ Ki1_at_0, Ki2_at_0, Ki3_at_0 = Ki(0.,1,1,1)[0], Ki(0.,2,1,1)[0], Ki(0.,3,1,1)[0]
 geometry_type = "cylinder"  # cylinder or sphere only
 max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
-np.set_printoptions(precision=10)
+np.set_printoptions(precision=6)
 
 
 class solver_options:
@@ -59,6 +60,10 @@ class solver_options:
         self.check_input()
 
     def check_input(self):
+        if self.betaL < 0 or self.betaL > 1:
+            raise InputError('left albedo not in [0, 1]')
+        if self.betaR < 0 or self.betaR > 1:
+            raise InputError('right albedo not in [0, 1]')
         if self.ks is None:
             raise InputError('Missing input nb. of quadrature points')
         if self.oitmax < 0:
@@ -78,6 +83,11 @@ class solver_options:
     def tolls(self):
         "pack tolerances on residual errors in outer and inner iterations"
         return self.otoll, self.itoll
+
+    @property
+    def albedos(self):
+        "pack albedos at the left and right boundaries"
+        return self.betaL, self.betaR
 
 
 def equivolume_mesh(I, a=0, b=1, geometry_type="cylinder"):
@@ -265,7 +275,7 @@ def calculate_escape_prob(r, st, tr_data, geometry_type="cylinder",
     # remind that the current vanishes at the center, and likewise the partial
     # currents (assumption, but it shall be enough to say that they're equal!).
     vareps = np.zeros((I, I, 2),)
-    # reference the partial currents to the main data container
+    # references to the main data container
     varepsp = vareps[:,:,0]  # first index is i, second index is j (sources)
[…]

### 2020-04-28 CPM1D/tests/MC2011_2G_cylinder_test.py

@@ -1,60 +1,0 @@
-# --*-- coding:utf-8 --*--
-"""
-Solve the integral transport equation in the cylinder by CPM
-using the two group data from the MC2011 article.
-"""
-import os, sys
-import logging as lg
-import numpy as np
-sys.path.append(os.path.join(os.getcwd(), ".."))
-from cpm1dcurv import *
-
-sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
-from data.homog2GMC2011 import *
-
-# from FDsDiff1D import input_data
-
-def MyWho():
-     print([v for v in globals().keys() if not v.startswith('_')])
-
-
-if __name__ == "__main__":
-
-    lg.basicConfig(level=lg.INFO)  # filename = logfile
-    lg.info("Solve the MC2011 problem by CPM in the cylinder")
-    geometry_type = "cylinder"
-
-    # definition of the spatial mesh
-    L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
-    I = 4  # number of cells in the spatial mesh
-    # r = np.linspace(0, L, I+1)
-    r = equivolume_mesh(I, 0, L, geometry_type)
-    # r = np.array([0., .075, .15]); I = r.size - 1;  # test
-    # volumes in input_data are per steradiant angle and differ from
-    # the following ones
-    # V = calculate_volumes(r, geometry_type)
-    
-    ks = np.full(I, 2)  # quadrature order for each spatial cell
-    GaussQuadrature = "Gauss-Jacobi"  # type of Gauss quadrature
-    
-    xs_media = {
-        'HM':{  # homogeneous medium
-            'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
-        }
-    }
-    media = [['HM', L]]  # i.e. homogeneously filled
-
-    Homog2GSlab_data = input_data(xs_media, media, r,
-                                  geometry_type, LBC=2, RBC=2,
-                                  per_unit_angle=False)
-    slvr_opts = solver_options(GQ=GaussQuadrature, ks=ks)
-    
-    k, flx = solve_cpm1D(Homog2GSlab_data, slvr_opts)
-    
-    flxinf = np.dot(np.linalg.inv(np.diag(st) - ss[:,:,0]), chi)
-    kinf = np.dot(nsf, flxinf)  # 1.07838136
-    flxinf *= np.linalg.norm(flx[:, 0]) / np.linalg.norm(flxinf)
[…]

### 2020-04-28 CPM1D/tests/MC2011_2G_infhom_curvlins_test.py

@@ -1,0 +1,60 @@
+# --*-- coding:utf-8 --*--
+"""
+Solve the integral transport equation in the cylinder by CPM
+using the two group data from the MC2011 article.
+"""
+import os, sys
+import logging as lg
+import numpy as np
+sys.path.append(os.path.join(os.getcwd(), ".."))
+from cpm1dcurv import *
+
+sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
+from data.homog2GMC2011 import *
+
+L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
+I = 4  # number of cells in the spatial mesh
+    
+ks = np.full(I, 2)  # quadrature order for each spatial cell
+GaussQuadrature = "Gauss-Jacobi"  # type of Gauss quadrature
+slvr_opts = solver_options(GQ=GaussQuadrature, ks=ks)
+
+xs_media = {
+    'HM':{  # homogeneous medium
+        'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
+    }
+}
+media = [['HM', L]]  # i.e. homogeneously filled
+
+
+def solve_problem(geometry_type = "cylinder"):
+    lg.info("Solve the MC2011 problem by CPM in the " +
+            geometry_type)
+    # definition of the spatial mesh
+    r = equivolume_mesh(I, 0, L, geometry_type)
+    # remind that volumes in input_data are per steradiant angle and
+    # differ from the following ones
+    # V = calculate_volumes(r, geometry_type)
+
+    Homog2GSlab_data = input_data(xs_media, media, r,
+                                  geometry_type, LBC=2, RBC=2,
+                                  per_unit_angle=False)
+        
+    return solve_cpm1D(Homog2GSlab_data, slvr_opts)
+
+
+if __name__ == "__main__":
+
+    lg.basicConfig(level=lg.INFO)  # filename = logfile
+    
+    # solve the infinite homogeneous medium problem
+    flxinf = np.dot(np.linalg.inv(np.diag(st) - ss[:,:,0]), chi)
+    kinf = np.dot(nsf, flxinf)  # 1.07838136
+    
+    for geo in ["cylinder", "sphere"]:
+        k, flx = solve_problem(geo)
+        flx *= np.linalg.norm(flxinf) / np.linalg.norm(flx[:, 0])
+        np.testing.assert_allclose(flx, np.tile(flxinf, (I, 1)).T,
[…]

### 2020-04-28 CPM1D/tests/MC2011_2G_infhom_slab_test.py

@@ -1,0 +1,67 @@
+# --*-- coding:utf-8 --*--
+"""
+Solve the integral transport equation in the cylinder by CPM
+using the two group data from the MC2011 article.
+"""
+import os, sys
+import logging as lg
+import numpy as np
+sys.path.append(os.path.join(os.getcwd(), ".."))
+from cpm1dcurv import *
+
+sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
+from data.homog2GMC2011 import *
+
+L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
+
+xs_media = {
+    'HM':{  # homogeneous medium
+        'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
+    }
+}
+media = [['HM', L]]  # i.e. homogeneously filled
+
+geometry_type = "slab"
+
+if __name__ == "__main__":
+
+    lg.basicConfig(level=lg.INFO)  # filename = logfile
+    lg.info("Reproduce the inf-hom medium with MC2011 data " +
+            " by CPM in the " + geometry_type)
+
+    # test a general mesh for the infinite homog medium
+    r = np.array([0, 1 / 8., 1 / 6., 0.9, 1]) * L
+    I = r.size - 1  # number of cells in the spatial mesh
+    Homog2GSlab_data = input_data(xs_media, media, r,
+                                  geometry_type, LBC=2, RBC=2)
+    
+    # ks is needed anyway when validating the input solver options
+    k, flx = solve_cpm1D(Homog2GSlab_data, solver_options(ks=np.full(I, 0)))
+    
+    flxinf = np.dot(np.linalg.inv(np.diag(st) - ss[:,:,0]), chi)
+    kinf = np.dot(nsf, flxinf)  # 1.07838136
+    flxinf *= np.linalg.norm(flx[:, 0]) / np.linalg.norm(flxinf)
+    np.testing.assert_allclose(flx, np.tile(flxinf, (I, 1)).T,
+                               err_msg="flx-inf not verified")
+    np.testing.assert_allclose(k, kinf, atol=1.e-7,
+                               err_msg="k-inf not verified")
+
+    # solve the MC2011 problem
+    lg.info("Solve the MC2011 problem by CPM in the " + geometry_type)
+    # L *= 2
+    # media = [['HM', L]]
+    I = 100  # number of cells in the spatial mesh
+    r = equivolume_mesh(I, 0, L, geometry_type)
+    # warning: remind that the solution in half slab use white reflection
[…]

### 2020-04-28 CPM1D/tests/MC2011_2Gtest.py

@@ -1,60 +1,0 @@
-# --*-- coding:utf-8 --*--
-"""
-Solve the integral transport equation in the cylinder by CPM
-using the two group data from the MC2011 article.
-"""
-import os, sys
-import logging as lg
-import numpy as np
-sys.path.append(os.path.join(os.getcwd(), ".."))
-from cpm1dcurv import *
-
-sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
-from data.homog2GMC2011 import *
-
-# from FDsDiff1D import input_data
-
-def MyWho():
-     print([v for v in globals().keys() if not v.startswith('_')])
-
-
-if __name__ == "__main__":
-
-    lg.basicConfig(level=lg.INFO)  # filename = logfile
-    lg.info("Solve the MC2011 problem by CPM in the cylinder")
-    geometry_type = "sphere"
-
-    # definition of the spatial mesh
-    L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
-    I = 4  # number of cells in the spatial mesh
-    # r = np.linspace(0, L, I+1)
-    r = equivolume_mesh(I, 0, L, geometry_type)
-    # r = np.array([0., .075, .15]); I = r.size - 1;  # test
-    # volumes in input_data are per steradiant angle and differ from
-    # the following ones
-    # V = calculate_volumes(r, geometry_type)
-    
-    ks = np.full(I, 2)  # quadrature order for each spatial cell
-    GaussQuadrature = "Gauss-Jacobi"  # type of Gauss quadrature
-    
-    xs_media = {
-        'HM':{  # homogeneous medium
-            'st': st, 'ss': ss, 'nsf': nsf, 'chi': chi, 'D': D
-        }
-    }
-    media = [['HM', L]]  # i.e. homogeneously filled
-
-    Homog2GSlab_data = input_data(xs_media, media, r,
-                                  geometry_type, LBC=2, RBC=2,
-                                  per_unit_angle=False)
-    slvr_opts = solver_options(GQ=GaussQuadrature, ks=ks)
-    
-    k, flx = solve_cpm1D(Homog2GSlab_data, slvr_opts)
-    
-    flxinf = np.dot(np.linalg.inv(np.diag(st) - ss[:,:,0]), chi)
-    kinf = np.dot(nsf, flxinf)  # 1.07838136
-    flxinf *= np.linalg.norm(flx[:, 0]) / np.linalg.norm(flxinf)
[…]

### 2020-04-28 CPM1D/tests/Sood_PUx-1-0-x.py

@@ -1,0 +1,106 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+Test cases by Sood et al. [Sood2003]_.
+
+.. [Sood2003] Sood, A., Forster, R. A., & Parsons, D. K. (2003). Analytical
+              benchmark test set for criticality code verification. Progress
+              in Nuclear Energy, 42(1), 55-106.
+"""
+import sys, os
+import numpy as np
+
+sys.path.append(os.path.join(os.getcwd(), ".."))
+from cpm1dcurv import *
+
+sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
+from data.SoodPNE2003 import *
+from FDsDiff1D import input_data
+
+
+# Table 3
+# Critical Dimensions, rc, for One-Group Bare Pu-239 (c=1.50)
+# Problem Identifier Geometry r, (mfp) rc (cm) Reference
+# 2 PUa-l-0-SL Slab 0.605055 1.853722 [161
+# Table 4
+# Critical Dimensions, rc, for One-Group Bare Pu-239 (c=1.40)
+# Problem Identifier Geometry rc (mfp) rc (cm) Reference
+# 6 Pub-l-0-SL Slab     0.73660355   2.256751 [351
+# 7 Pub-I-0-CY Cylinder 1.396979     4.279960 [361,[371
+# 8 Pub-l-0-SP Sphere   1.9853434324 6.082547 [351
+# Table 5
+# Normalized Scalar Fluxes for One-Group Bare Pu-239 (c=1.40)
+# Problem Identifier Geometry r/rc = 0.25, r/rc = 0.5, r/rc = 0.75, r/rc = 1
+# 6 Pub-l-0-SL Slab     0.9701734  0.8810540  0.7318131  0.4902592
+# 7 Pub-l-0-CY Cylinder     -      0.8093         -      0.2926
+# 8 Pub-l-0-SP Sphere   0.93538006 0.75575352 0.49884364 0.19222603
+
+
+def get_geoid(geo):
+    if geo == 'slab':
+        g = 'SL'
+    elif 'cylind' in geo:
+        g = 'CY'
+    elif 'spher' in geo:
+        g = 'SP'
+    else:
+        raise InputError('unknown input geometry type')
+    return g
+
+
+def set_media(m, L, name):
+    xs_media = {name:{  # homogeneous medium
[…]

### 2020-04-28 FD1dMGdiff/FDsDiff1D.py

@@ -486,6 +486,45 @@ def opl(j, i, Ptg):
     return np.sum(Ptg[j:i+1])
 
 
+def calculate_escape_prob_slab(x, st, Di=None):
+    """Calculate the escape probabilities of neutrons emitted isotropically
+    in a cell to collide after the first flight in another one of the slab.
+    """
+    lg.debug("Calculate the reduced escape probabilities in the slab.")
+    I = x.size - 1  # nb of rings
+    if not np.all(np.diff(x) > 0):
+        raise ValueError("Input values in x are not in increasing order")
+    if st.size != I:
+        raise InputError("size mismatch of input sigma_t")
+    if Di is None:
+        Di = calculate_volumes(x, "slab")
+    if len(Di) != I:
+        raise ValueError('Nb. of cells differ from nb. of volumes')
+
+    vareps = np.zeros((I+1, I, 2),)
+    # first index is i (surfaces), second index is j (sources)
+    # references to the main data container
+    varepsp = vareps[:,:,0]  # for positive current
+    varepsm = vareps[:,:,1]  # for negative current (negative quantity)
+    
+    # compute the total removal probability per cell or cell width in unit
+    # of optical length
+    tau = Di * st
+
+    for i in range(I+1):
+        for j in range(i):
+            varepsp[i, j] = (En(3, opl(j+1, i-1, tau))
+                           - En(3, opl( j , i-1, tau)))
+        for j in range(i, I):
+            varepsm[i, j] = (En(3, opl(i,  j , tau))
+                           - En(3, opl(i, j-1, tau)))
+    
+    varepsp /= st
+    varepsm /= st
+    
+    return 0.5 * vareps
+
+
 def compute_tran_currents(flx, k, Di, xs, BC=(0, 0), curr=None):
     """Compute the partial currents given by the integral transport equation
     with the input flux flx. An artificial second moment is used to match

### 2020-04-28 FD1dMGdiff/data/SoodPNE2003.py

@@ -1,0 +1,67 @@
+# --*-- coding:utf-8 --*--
+"""
+Data by Sood et al. used to verify MCNP and DANTSYS in the past [Sood2003]_.
+
+.. [Sood2003] Sood, A., Forster, R. A., & Parsons, D. K. (2003). Analytical
+              benchmark test set for criticality code verification. Progress
+              in Nuclear Energy, 42(1), 55-106.
+"""
+
+import numpy as np
+import logging as lg
+
+one_third = 1. / 3.
+
+Table2 = \
+"""
+# Material nu Sf Sc Ss St c
+Pu-239 (a) 3.24 0.081600 0.019584 0.225216 0.32640 1.50
+Pu-239 (b) 2.84 0.081600 0.019584 0.225216 0.32640 1.40
+H20 (refl) 0.0  0.0      0.032640 0.293760 0.32640 0.90
+"""
+def set_xs(dstr):
+    d = dict()
+    d['nu'], d['sf'], d['sc'], d['ss'], d['st'], d['c'] = \
+        [np.array([float(v)]) for v in dstr.split()[2:]]
+    d['chi'], d['nsf'] = np.ones(1), d['nu'] * d['sf']
+    d['ss'] = np.ones((1,1,1),) * d['ss']
+    # definition of the (P1) diff coefficient with isotropic scat.
+    # for k, v in d.items():
+        # v /= d['st']
+    d['D'] = one_third / d['st']
+    return d
+
+tlines = [l for l in Table2.split('\n')[1:-1] if not l.startswith('#')]
+get_line = lambda lines, key: [l for l in lines if key in l][0]
+
+materials = {
+    'PUa': set_xs(get_line(tlines, 'Pu-239 (a)')),
+    'PUb': set_xs(get_line(tlines, 'Pu-239 (b)')),
+    'H20': set_xs(get_line(tlines, 'H20 (refl)'))
+}
+
+G = 1  # nb of energy groups
+
+
+def calc_flx_inf(st, ss0, chi):
+    return np.dot(np.linalg.inv(np.diag(st) - ss0), chi)
+
+
+def calc_kinf(nsf, st=None, ss0=None, chi=None, flx_inf=None):
+    if flx_inf is None:
+        flx_inf = calc_flx_inf(st, ss0, chi)
+    return np.dot(nsf, flx_inf)
+
+
+if __name__ == "__main__":
+
+    lg.info("*** Check homogeneous cross sections data ***")
[…]

### 2020-04-28 SNMG1DSlab/tests/homogSlab2GMC2011.py

@@ -42,8 +42,8 @@ Homog2GSlab_data = input_data(xs_media, media, xi, geometry_type, LBC, RBC)
 slvr_opts = solver_options()
 
 # Initiate quadratures object
-N, L = 16, 0
-qdata = quad_data(N, L)
+N = 16
+qdata = quad_data(N, L=0)
 
 if __name__ == "__main__":
 

### 2020-05-13 docs/ICTT2019/RMethod_ictt26.tex
Upgrade AA by DAAREM (without the use of a merit function of interest); fix b.c. and transmission/reflection in the balance equation for the current in CPM1D - this includes correcting the documentation; implement the homogeneous cases by Sood PUa-x/PUb-x in both transport and diffusion+RM; implement the RM through escape probabilities; verify the CPM1D solver in the homogeneous cases; reorganize sources by adding a new module to manage material and geometry data.

@@
 \textbf{Daniele Tomatis}\\
-DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
+DES, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
 CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\
@@
   \frac{\tilde{p}_{ij}}{V_i \sigma_i} = \frac{\tilde{p}_{ji}}{V_j \sigma_j} \quad \text{and} \label{eq:reciprocity1}\\
-  \frac{\tilde{p}_{j, i+1/2}}{V_j \sigma_j} = \frac{\tilde{e}^+_{i+1/2, j} + \tilde{e}^-_{i+1/2, j}}{S_{i+1/2}}, % / 4 ?
+  \frac{\tilde{p}_{j, i+1/2}}{V_j \sigma_j} = 4 \frac{\tilde{e}^+_{i+1/2, j} + \tilde{e}^-_{i+1/2, j}}{S_{i+1/2}},
   \label{eq:reciprocity2}
@@
 \ref{eq:reciprocity2} are needed with non-zero entering currents of neutrons at the boundary $x_{I+1/2}$.
-This probability refers to an entering angular flux that must be still divided by 4 in case the flux is isotropic, yielding a cosine current typical of white reflection.
+This probability refers again to an angular flux entering the surface $(i+1/2)$ isotropically, yielding the cosine current typical of white reflection.
 
@@
 A generalized form for the boundary condition of the diffusion equation applying at the left side of the slab follows as $\Upsilon = - D_0 \phi_0 / (\Delta_0 / 2 + \zeta)$, where $\zeta$ is the extrapolation length in case of vacuum.
+$\zeta = 2D$ yields the Marshak boundary conditions for instance, but the value $\zeta = 2.13D$ is usually recommended in slab geometry \cite{stamm1983methods}.
 Reflection can be reproduced by $\zeta \rightarrow \infty$, whereas the condition of zero-flux comes with $\zeta = 0$.
@@
 This approximation may not reproduce a vanishing current with reflection reproducing a symmetric distribution.
+Only situations with perfectly isotropic angular flux at the boundary will be described correctly.
 At the left boundary for instance, the current can be expressed as $J(a) =  J^+ + J^- = 0$ with the entering current $J^+ = \int_0^1 { d\mu \mu \phi(a, \mu) } = - J^-$.
@@
 \ref{eq:J_tr}.
-In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \phi_0(a) / 2$, yielding $J^+(x) = E_3 \left(\tau(a, x)\right)\phi_0(a)/2$.
-This approximation does not guarantee to obtain the expected vanishing current at the boundary when computing the same current at the boundary with symmetric flux distributions.
+In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \phi_0(a) / 2$, yielding $J^+(x) = E_3 \left(\tau(a, x)\right)\phi_0(a)/2$, or $J^+(x) = \tilde{t}_a(x) \phi(a)/4$ using the CPM formalism (white reflection at $a$).
+Here, $\tilde{t}$ is the transmission probability of neutrons crossing uniformly and isotropically the surface $a$ to get to the position $x$ uncollided.
+The value of this probability can be obtained through reciprocity and conservation properties, as shown in section \ref{sec:cp}.
+Hence, this approximation does not guarantee to obtain the expected vanishing current at the boundary when computing the same current at the boundary with symmetric flux distributions.
 However, it is possible to determine the difference between the partial currents (remind that $J^-$ is negative).
@@
 \[ \phi(a, \mu) = \frac{1}{2} \phi_0 + \frac{3}{2} \mu \phi_1 + \frac{5}{4} \left( 3 \mu^2 - 1 \right) \tilde{\phi}_2, \]
-with $\phi_1 = J = 0$ with reflection.
-The derivation of the correction at the other boundary of the slab can easily be derived.
+with $\phi_1 = J = 0$ with reflection. The derivation of the correction at the other boundary of the slab can easily be derived.
+
+Transmission probabilities of neutrons entering with anisotropic (even) distributions are now needed, but this time they can not be derived from the escape probabilities based on isotropic emission.
+We only give the expression to calculate these quantities in the slab, since white reflection is generally preferred in the 1-D curvilinear geometries for reproducing more accurate physical results.
+
 Although this correction definitely improves the results, it cannot yield exactly the same results of the unfolded geometry, that is without reproducing the half symmetry by reflection.
@@
 
-The integral transport equation for the scalar flux can be written using the first flight collision probabilities as \cite{hebert2009applied}:
+The integral transport equation for the scalar flux with isotropic sources can be written using the first flight collision probabilities as \cite{lewis1984computational,hebert2009applied}:
 \begin{subequations}
@@
 \end{equation}
-where $b$ stands for any boundary with a non-zero entering current.
-$b=I+1/2$ for the cylindrical and for the spherical geometries, whereas two incoming currents can be present in the slab.
+where $b$ stands for any boundary with a non-zero entering current $J^{(-)}_{b} = \phi_b / 4$, given as well by an isotropic angular flux.
+$\tilde{p}_{ij}$ and $\tilde{p}_{ib}$ are the probabilities of a neutron to have its first collision in the volume $V_i$ after being emitted isotropically in the volume $V_j$ or from the surface $S_b$, respectively.
+$b=I+1/2$ for the cylindrical and for the spherical geometries after placing the center at $x_a = 0$ ($a=-1/2$), whereas two incoming currents can be present in the slab.
 This equation can be simplified further by using the reciprocity property from Eqs.
@@
 \label{eq:cmp2_eqn}
-\phi_i = \sum_{j=1}^I {q_j p_{ji}} + J^{(-)}_{b} \tilde{e}_{bi}
+\phi_i = \sum_{j=1}^I {q_j p_{ji}} + 4 J^{(-)}_{b} \tilde{e}_{bi}
 \end{equation}
@@
 with the reduced escape probability $p_{ji} = \tilde{p}_{ji} / \sigma_j$ and the escape probability counting for both the signed terms.
-The incoming current at the boundary can be given as fixed external source, or being expressed as proportional to the out-going current by means of the albedo $0 \leq \beta \leq 1$, like
-\begin{equation}
+The incoming current at the boundary can be given as fixed external source, or being expressed as proportional to the out-going current by means of an albedo $0 \leq \beta \leq 1$, like
+\begin{subequations}
 \label{eq:albedo}
-  J^- = \beta J^+ = \beta \left(
-      \sum_{j=1}^I {q_j p_{jb}} + \tilde{t} J^-
+\begin{align}
+\label{eq:albedo_b}
+ % J^- = \beta J^+ = \beta \left(
+ %     \sum_{j=1}^I {\frac{q_j p_{jb}}{4}} + \tilde{t} J^-
+ %   \right),
+  J_b^- &= \beta_b J_b^+ = \beta_b \left(
+      \sum_{j=1}^I {\frac{q_j p_{jb}}{4}} + \tilde{r}_b J_b^- + \tilde{t}_{ba} \frac{S_a}{S_b} J_a^+
+    \right), \text{ and}\\
+\label{eq:albedo_a}
+  J_a^+ &= \beta_a J_a^- = \beta_a \left(
+      \sum_{j=1}^I {\frac{q_j p_{ja}}{4}} + \tilde{r}_a J_a^+ + \tilde{t}_{ab} \frac{S_b}{S_a} J_b^-
     \right),
-\end{equation}
+\end{align}
+\end{subequations}
 with the reduced collision probability from the surface at $x_b$ thanks again to reciprocity.
-About \ref{eq:reciprocity2}, reciprocity considers entering neutrons distributed according to the cosine described by the direction of flight and the normal to the same surface, yielding a cosine current by $J^\pm = \phi/4$, suitable to reproduce white reflection with $\beta = 1$.
+About \ref{eq:reciprocity2}, reciprocity always considers entering neutrons distributed according to the cosine described by the direction of flight and the normal to the same surface, yielding a cosine current by $J^\pm = \phi/4$, suitable to reproduce white reflection with $\beta = 1$.
 %yields the white reflection, that is isotropic inwards redistribution of the outgoing current, regardless of the outgoing direction.
-The transmission $\tilde{t}$ is the probability that a neutron enters the outer surface with the cosine distribution, travels  inwards and leaves it back again without colliding.
-Conservation implies that $\tilde{t} = 1 - \sum_j{\tilde{p}_{jb}}$.
+The reflection $\tilde{r}$ is the probability that a neutron enters the outer surface with the cosine distribution, travels inwards and leaves it back again without colliding.
+It must be zero in the slab, but not in the cylinder or in the sphere.
+Transmission is used instead when the leaving surface to be crossed is different from the entering one, and it is non-vanishing here only in the slab.
+Conservation applied in the cylinder or in the sphere implies that $\tilde{r}_b = 1 - \sum_j{\tilde{p}_{jb}}$, where we have also assumed implicitly no possible transmission in the derivation of their escape probabilities.
+Similarly in the slab, it is $\tilde{t}_{ab} = 1 - \sum_j{\tilde{p}_{jb}}$ for instance.
+Eq.
+\ref{eq:albedo_a} can be used for Eq.
+\ref{eq:albedo_b} to obtain an expression for $J_b^-$ that is suitable for substitution in Eq.
+\ref{eq:cmp1_eqn}.
+Eqs.
+\ref{eq:albedo} are in a general form for 1-D geometries, which simplify either in the slab or in the others.
 
@@
 
-In case of partial currents given by an albedo relation at the boundary, the same solving scheme still holds after redefinition of the matrix $\mathbf{P}$:
+In case the partial current is given by an albedo relation at the boundary of the cylinder (or of the sphere), the same solving scheme still holds after redefinition of the matrix $\mathbf{P}$:
 \[
-\mathbf{P} \leftarrow \mathbf{P} + \frac{\beta}{1 - \beta \tilde{t}} \mathbf{E},
+\mathbf{P} \leftarrow \mathbf{P} + \frac{\beta_b}{1 - \beta_b \tilde{r}} \mathbf{E}_b,
 \]
-with $\mathbf{E}=[\tilde{e}_{bi} p_{jb},\; 1 \leq i,j \leq I]$.
+with $\mathbf{E}_b = [\tilde{e}_{bi} p_{jb},\; 1 \leq i,j \leq I]$.
+This redefinition holds also for the slab in case of periodic boundary condition, i.e.
+$J_b^- = J_a^+$.
+Lastly for the slab, a general relation for the right boundary is
+%\[
+%J_b^- = \beta_b \left[
+%      \sum_{j=1}^I {\frac{q_j p_{jb}}{4}} + \tilde{t} \beta_a \left(
+%      \sum_{j=1}^I {\frac{q_j p_{ja}}{4}} + \tilde{t} J_b^- \right)
+%    \right]
+%\]
+\[ \mathbf{P} \leftarrow \mathbf{P} + 
+\frac{\beta_b}{1 - \beta_a \beta_b \tilde{t}^2}
+\left( \mathbf{E}_b + \beta_a \tilde{t} \mathbf{E}_a \right)
+\]
+with $\mathbf{E}_a = [\tilde{e}_{bi} p_{ja},\; 1 \leq i,j \leq I]$. The corresponding expression at the left boundary is easy to obtain.
 

### 2020-05-13 CPM1D/cpm1dcurv.py

@@ -28,8 +28,7 @@ from KinPy.algo609 import dbskin as Ki
 sys.path.append(
     os.path.join(os.path.dirname(__file__), '..', 'FD1dMGdiff')
 )
-from FDsDiff1D import input_data, unfold_xs, \
-                      compute_cell_volumes, compute_cell_surfaces
+from GeoMatTools import *
 
 
 # useful constants
@@ -46,7 +45,8 @@ class solver_options:
     nbitsmax = 100  # default nb. of max iterations (its)
 
     def __init__(self, iitmax=nbitsmax, oitmax=nbitsmax,
-                 otoll=toll, itoll=toll, ks=None, GQ="Gauss-Jacobi"):
+                 otoll=toll, itoll=toll, ks=None, GQ="Gauss-Jacobi",
+                 betaL=0, betaR=0):
         self.oitmax = oitmax  # max nb of outer iterations
         self.iitmax = iitmax  # max nb of inner iterations
         self.otoll = otoll  # tolerance on fiss. rates at outer its.
@@ -54,9 +54,9 @@ class solver_options:
         self.ks = ks  # nb. of quadrature point per cell
         self.GaussQuadrature = GQ  # type of Guass quadrature along
                                    # the h axis in curvilinear coords.
-        self.betaL = 0  # partial current albedo left
-                        # (not used in curv. geoms)
-        self.betaR = 0  # must be <= 1, see RBC in input_data
+        self.betaL = betaL  # partial current albedo left
+                            # (not used in curv. geoms)
+        self.betaR = betaR  # must be <= 1, see RBC in input_data
         self.check_input()
 
     def check_input(self):
@@ -64,15 +64,15 @@ class solver_options:
             raise InputError('left albedo not in [0, 1]')
         if self.betaR < 0 or self.betaR > 1:
             raise InputError('right albedo not in [0, 1]')
-        if self.ks is None:
-            raise InputError('Missing input nb. of quadrature points')
         if self.oitmax < 0:
             raise InputError('Detected negative max nb. of outer its.')  
         if self.iitmax < 0:
             raise InputError('Detected negative max nb. of inner its.')
+        if self.ks is None:
+            raise InputError('Missing input nb. of quadrature points')
         if self.GaussQuadrature != "Gauss-Jacobi" and \
[…]

### 2020-05-13 CPM1D/tests/CP_empty_cylinder.py

@@ -47,8 +47,7 @@ if __name__ == "__main__":
     lg.info('EP+:\n' + str(eP[0, :, :, 0]))
     lg.info('EP-:\n' + str(eP[0, :, :, 1]))
     
-    ePp, ePm = np.ones((I, I),), np.zeros((I, I),)
     np.testing.assert_allclose(np.zeros((I, I),), cP[0, :, :],
         atol=1.e-6, rtol=np.inf, err_msg="CP should be all zeros!")
-    np.testing.assert_allclose(-np.triu(eP[0, :, :, 0], k=1),
-        eP[0, :, :, 1], atol=1.e-7, err_msg="- triu(EP+) != EP-")
+    np.testing.assert_allclose(-np.triu(eP[0, 1:, :, 0], k=1),
+        eP[0, 1:, :, 1], atol=1.e-7, err_msg="- triu(EP+) != EP-")

### 2020-05-13 CPM1D/tests/MC2011_2G_infhom_slab_test.py

@@ -11,6 +11,7 @@ from cpm1dcurv import *
 
 sys.path.insert(0, os.path.join("..", "..", "FD1dMGdiff"))
 from data.homog2GMC2011 import *
+from GeoMatTools import equivolume_mesh, geomprogr_mesh
 
 L = 21.5 / 2.  # outer radius, equal to half pitch of a fuel assembly
 
@@ -45,17 +46,16 @@ if __name__ == "__main__":
                                err_msg="flx-inf not verified")
     np.testing.assert_allclose(k, kinf, atol=1.e-7,
                                err_msg="k-inf not verified")
-
     # solve the MC2011 problem
     lg.info("Solve the MC2011 problem by CPM in the " + geometry_type)
-    # L *= 2
-    # media = [['HM', L]]
+    # L *= 2; media = [['HM', L]]
     I = 100  # number of cells in the spatial mesh
     r = equivolume_mesh(I, 0, L, geometry_type)
+    # r = geomprogr_mesh(I, 0, L, ratio=1.005)
     # warning: remind that the solution in half slab use white reflection
     # at the center, introducing some error!
     Homog2GSlab_data = input_data(xs_media, media, r,
-                                  geometry_type, LBC=2, RBC=0)
+                                  geometry_type, LBC=0, RBC=2)
     
     # ks is needed anyway when validating the input solver options
     k, flx = solve_cpm1D(Homog2GSlab_data,

### 2020-05-13 FD1dMGdiff/FDsDiff1D.py

@@ -60,16 +60,25 @@ x_right_medium_(i) = x_left_medium_(i+1) for all i < N.
                    accelerating EM and EM-like algorithms. Journal of
                    Computational and Graphical Statistics, 1-13.
 """
+# Owned
+__title__ = "Multigroup diffusion and RM in 1D geometries by finite differences"
+__author__ = "D. Tomatis"
+__date__ = "15/11/2019"
+__version__ = "1.4.0"
+
 import os
 import sys
 import logging as lg
 import numpy as np
 from scipy.special import expn as En
+from scipy.optimize import brentq
+from GeoMatTools import *
 
-__title__ = "Multigroup diffusion in 1D slab by finite differences"
-__author__ = "D. Tomatis"
-__date__ = "15/11/2019"
-__version__ = "1.3.0"
+sys.path.append(
+    os.path.join(os.getcwd(), os.path.dirname(__file__), '..', 'CPM1D')
+)
+from cpm1dcurv import calculate_tracking_data, calculate_sprobs, \
+                      calculate_eprobs, calculate_tprobs
 
 max_float = np.finfo(float).max  # float is float64!
 min_float = np.finfo(float).min
@@ -103,106 +112,9 @@ def opt_theta(tau):
     return t
 
 
-# get the mid-points of cells defined in the input spatial mesh x
-def xim(x):
-    return (x[1:] + x[:-1]) / 2.
-
-
-class input_data:
-    """Geometry and material input data of the 1D problem. Possible options
-    of geometry_type are slab, cylindrical and spherical. Allowed boundary
-    conditions: 0-vacuum, 1-zero flux and 2-reflection. Units are in cm."""
-
-    def __init__(self, xs_media, media, xi, geometry_type='slab',
-                 LBC=0, RBC=0, per_unit_angle=True):
-        self.geometry_type, self.xi = geometry_type.lower(), xi
-        self.LBC, self.RBC = LBC, RBC
-        self.xs_media, self.media = xs_media, media
-        self.check_input()
-        self.compute_cell_width()
-        self.compute_mid_cell_coordinate()
-        self.compute_cell_surfaces(per_unit_angle)
-        self.compute_cell_volumes(per_unit_angle)
-
-    @property
-    def I(self):
-        return self.xi.size - 1
-
-    @property
-    def L(self):
-        return self.xi[-1]
-
-    @property
-    def BC(self):
-        return self.LBC, self.RBC
-
-    @property
-    def G(self):
[…]

### 2020-05-13 FD1dMGdiff/GeoMatTools.py

@@ -1,0 +1,331 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This module contains objects and methods to handle input geometry and material
+data. All solvers should use the data format given by this module.
+"""
+
+__title__ = "Specifications and tools for geometry and material data"
+__author__ = "D. Tomatis"
+__date__ = "07/05/2020"
+__version__ = "1.0.0"
+
+import os
+import sys
+import logging as lg
+import numpy as np
+
+# log file settings
+logfile = os.path.splitext(os.path.basename(__file__))[0] + '.log'
+# verbose output only with lg.DEBUG mode
+lg.basicConfig(level=lg.INFO)  # filename = logfile
+
+
+def xim(x):
+    "Get the mid-points of cells defined in the input spatial mesh x"
+    return (x[1:] + x[:-1]) / 2.
+
+
+class input_data:
+    """Geometry and material input data of the 1D problem. Possible options
+    of geometry_type are slab, cylindrical and spherical. Allowed boundary
+    conditions: 0-vacuum, 1-zero flux and 2-reflection. Units are in cm."""
+
+    def __init__(self, xs_media, media, xi, geometry_type='slab',
+                 LBC=0, RBC=0, per_unit_angle=True):
+        self.geometry_type, self.xi = geometry_type.lower(), xi
+        self.LBC, self.RBC = LBC, RBC
+        self.xs_media, self.media = xs_media, media
+        self.check_input()
+        self.compute_cell_width()
+        self.compute_mid_cell_coordinate()
+        self.compute_cell_surfaces(per_unit_angle)
+        self.compute_cell_volumes(per_unit_angle)
+
+    @property
+    def I(self):
+        return self.xi.size - 1
+
+    @property
+    def L(self):
+        return self.xi[-1]
+
+    @property
+    def BC(self):
+        return self.LBC, self.RBC
+
+    @property
+    def G(self):
+        return self.xs_media[next(iter(self.xs_media))]['st'].size
+
+    @property
+    def Lss(self):
+        random_ss, L = self.xs_media[next(iter(self.xs_media))]['ss'], 1
+        if random_ss.ndim == 3:
+            L = max([self.xs_media[m]['ss'].shape[-1] for m in self.xs_media])
+        return L - 1
+    
+    def compute_cell_width(self):
+        self.Di = self.xi[1:] - self.xi[:-1]
+    
+    def compute_mid_cell_coordinate(self):
[…]

### 2020-05-13 FD1dMGdiff/data/SoodPNE2003.py

@@ -47,12 +47,33 @@ def set_xs(dstr):
     d['nu'], d['sf'], d['sc'], d['ss'], d['st'], d['c'] = \
         [np.array([float(v)]) for v in dstr.split()[2:]]
     d['chi'], d['nsf'] = np.ones(1), d['nu'] * d['sf']
+    d['sa'] = d['sc'] + d['sf']  # = d['st'] - d['ss']
     d['ss'] = np.ones((1,1,1),) * d['ss']
+    d['kinf'] = (d['nsf'] / d['sa'])[0]
     # definition of the (P1) diff coefficient with isotropic scat.
     # for k, v in d.items():
         # v /= d['st']
     d['D'] = one_third / d['st']
     return d
+
+
+def BM2(m, k=1):
+    "return the material buckling in the 1g homogeneous problem"
+    nsf, sa, D = m['nsf'][0], m['sa'][0], m['D'][0]
+    if (nsf.size != sa.size) or (nsf.size != D.size):
+        raise ValueError('Input data have different size')
+    if nsf.size != 1:
+        raise ValueError('One-group data are needed')
+    return (nsf/k - sa) / D
+
+
+def diffk_ref(BG2, m):
+    "Return the multiplication factor provided the geometrical buckling"
+    nsf, sa, D = m['nsf'][0], m['sa'][0], m['D'][0]
+    L2, kinf = D / sa, nsf / sa
+    PNL = 1 / (1 + L2 * BG2)  # non leakage probability
+    return kinf * PNL
+    
 
 tlines = [l for l in Table2.split('\n')[1:-1] if not l.startswith('#')]
 get_line = lambda lines, key: [l for l in lines if key in l][0]

### 2020-05-13 FD1dMGdiff/tests/Sood_PUx-1-0-x.py

@@ -13,15 +13,13 @@ accuracy, being in order, in the slab, in the cylinder and in the sphere.
 import sys, os
 import numpy as np
 from scipy import interpolate
+from scipy.special import jv as Jv  # Bessel function of teh first kind
+J0 = lambda z: Jv(0, z)
 
 sys.path.append(os.path.join(os.getcwd(), ".."))
 from data.SoodPNE2003 import *
 from FDsDiff1D import input_data, solver_options, run_calc_with_RM_its
-
-sys.path.insert(0, os.path.join(os.getcwd(), "..", "..", "CPM1D"))
-# sys.path.insert(0, os.path.join(os.getcwd(), "..", "..", "CPM1D", "KinPy"))
-# import algo609
-from cpm1dcurv import equivolume_mesh
+from GeoMatTools import geomprogr_mesh, equivolume_mesh
 
 odir = "output"
 refdir = os.path.join("..", "..", "CPM1D", "tests", "output")
@@ -50,6 +48,8 @@ refflx = {
 }
 
 
+
+
 geoms = ["slab", "cylinder", "sphere"]
 
 
@@ -61,10 +61,16 @@ if __name__ == "__main__":
     
     # positions (fractions r/rc) to verify the flux results
     rf = np.linspace(0, 1, 5)
+    flx_tolerance = np.ones(4)  # tolerances are in percent
+    flx_tolerance[-1] = 2  # RM cannot fit transport at bare boundary
     
+    # --------------------------------------------------------------------------    
     m = 'PUa'  # only one case in the test suite
-    L = rc = 1.853722 * 2 # cm, critical length
+    BM2m, extrap_len = BM2(materials[m]), 2.13 * materials[m]['D'][0]
+    lg.info("Material buckling %.5f" % BM2m)
+    L = rc = 1.853722 # * 2 # cm, critical length
     # L = rc = 0.605055  # mfp
+    L_e = L + extrap_len
     xs_media, media = set_media(materials[m], L, m)
         
     geo = "slab"
@@ -75,25 +81,36 @@ if __name__ == "__main__":
     k_ref, flx_ref  = np.load(os.path.join(refdir, case + "_ref.npy"),
                               allow_pickle=True)
 
-    I = 20  # number of cells in the spatial mesh
+    I = 40  # number of cells in the spatial mesh (20 in complete slab)
     r = equivolume_mesh(I, 0, L, geo)
[…]

### 2020-05-13 FD1dMGdiff/tests/homogSlab2GMC2011.py

@@ -19,7 +19,7 @@ def MyWho():
 
 # definition of the spatial mesh
 L = 21.5 / 2.  # slab width, equal to half pitch of a fuel assembly
-I = 20  # nb of spatial cells
+I = 80  # nb of spatial cells
 xi = np.linspace(0, L, I+1)  # equidistant mesh
 
 geometry_type = 'slab'
@@ -42,8 +42,13 @@ if __name__ == "__main__":
     lg.info("*** Solve the M&C 2011 problem ***")
     from FDsDiff1D import run_calc_with_RM_its, solver_options
 
-    ritmax = 10
+    ritmax = 100
     CMFD, pCMFD = True, False
     slvr_opts = solver_options(ritmax=ritmax, CMFD=CMFD, pCMFD=pCMFD)
     filename = "./kflx_LBC%dRBC%d_I%d_it%d" % (LBC, RBC, I, ritmax)
     flx, k = run_calc_with_RM_its(Homog2GSlab_data, slvr_opts, filename)
+    kS16, kCPM = 0.744417, 0.743978
+    lg.info("Reference k from S16 is %.6f" % kS16)
+    np.testing.assert_allclose(k, kCPM, atol=1.e-4,
+                               err_msg="ref k of MC2011 not verified")
+    

### 2020-05-15 FD1dMGdiff/FDsDiff1D.py
Implementation of a new closure for vacuum (and zero flux) b.c. - this closure consists of adding the eqn. flx = \pm \zeta J to the system of equations to solve where the derivative of the flux in the current J is determined after interpolating the flux itself by a quadratic polynomial that is passing for the midpoints of the two nearest cells to the boundary, and that fulfills the previous relation with the extrapolated distance.

@@ -291,8 +291,7 @@ class AndersonAcceleration:
                 uf = np.dot(fk, Uk[:, :mk])
                 s = lambda lmbda: np.dot(np.dot(Vk.T,
                     np.diag(dk / (dk**2 + lmbda))), uf)
-                self.sk += 1
-                self.sk = min(self.sk, type(self).kappa - mk)
+                self.sk = min(self.sk + 1, type(self).kappa - mk)
                 deltak = self.delta(self.sk)
                 vk = np.sqrt(deltak) * np.linalg.norm(s(0))
                 phi = lambda lmbda: np.linalg.norm(s(lmbda)) - vk
@@ -423,6 +422,15 @@ def set_diagonals(st, Db, data, dD=None):
     # print(dDp, dDm)
     # get extrapolated length
     zetal, zetar = get_zeta(LBC), get_zeta(RBC)
+    c1l = c2l = c1r = c2r = 0.
+    if zetal < max_float:
+        c1l, c2l = quadratic_fit_zD(xi[0],
+                                    np.insert(data.xim[:2], 0, xi[0]),
+                                    zetal)
+    if zetar < max_float:
+        c1r, c2r = quadratic_fit_zD(xi[-1],
+                                    np.insert(data.xim[-2:][::-1], 0, xi[-1]),
+                                    -zetar)
     for g in range(G):
         # d contains only I-1 elements, flattened G times
         idd = np.arange(g*(I-1), (g+1)*(I-1))
@@ -439,13 +447,18 @@ def set_diagonals(st, Db, data, dD=None):
         # add b.c. (remind to be consistent with compute_diff_currents)
         # option (a) - attempt to get higher order accuracy
         # option (b) is 1st order
+        # option (c) fit by 2nd order polynomial
         if zetal < max_float:
-            # b[id0] += xb0 / zetal  # (a)
-            b[id0] += Db[g,0] * xb0 / (0.5 * Di[0] + zetal * Db[g, 0])  # (b)
+            # b[id0] -= xb0 / zetal  # (a)
+            # b[id0] += xb0 * Db[g,0] / (0.5 * Di[0] + zetal * Db[g, 0])  # (b)
+            b[id0] += xb0 * Db[g,0] *c1l # (c)
+            c[id0] += xb0 * Db[g,0] *c2l / Vi[1] # (c)
[…]

### 2020-05-15 FD1dMGdiff/GeoMatTools.py

@@ -212,7 +212,7 @@ def unfold_xs(input_data, diff_calc=True):
     Db = vol_averaged_at_interface(D, input_data.Vi)
     # --------------------------------------------------------------------------
     # # option 2.
-    # # use the definition of the diffusion coefficient at the boundary given
+    # # use the definition of the diffusion coefficient at the boundary with
     # # the current approximated by 1st order finite differences at both sides
     # # an interface
     # DioD = 1 / (D / input_data.Di)  # to exploit element-wise division
@@ -329,3 +329,150 @@ def opl(j, i, tau):
     # "Calculate the (dimensionless) optical length between j-1/2 and i+1/2."
     # # if j > i, the slicing returns an empty array, and np.sum returns zero.
     # return np.sum(Ptg[j:i+1])
+
+
+def estimate_derivative(flx, Di):
+    """Fit flx by quadratic interpolation at the cell centers and return the
+    value of its derivative at the initial point."""
+    if len(Di) != 3:
+        raise ValueError("invalid input cell-width vector Di")
+    if flx.size % 3 != 0:
+        raise ValueError("invalid input flux flx")
+    r = Di[1] / Di[0]
+    a1 = 2. + r
+    b1 = a1 + r + Di[2] / Di[0]
+    c = 4. / Di[0]**2 / (1. - b1) * ((flx[1] - flx[0]) / (a1 - 1.) -
+                                     (flx[2] - flx[1]) / (b1 - 1.))
+    b = 2. / Di[0] * (flx[1] - flx[0]) / (a1 - 1.) - c * Di[0] / 2. * (a1 + 1.)
+    return b
+
+
+def quadratic_extrapolation(flx, Di):
+    """Extrapolate the flux at the boundary by a quadratic polynomial which
+    interpolates the flux at the mid of the input three cells. This assumption
[…]

### 2020-05-25 docs/ICTT2019/RMethod_ictt26.tex
Preparation of the final draft of the ICTT26 article meant for publication on JCTT; analysis of results; general improvements and minor bug fixing; first implementation of quadratic fit with osculatory polynomial (to be improved because it does not work yet as expected).

@@
 \usepackage{subcaption}
+% \usepackage{hyperref}
 %
@@
 \newcommand{\shortTitle}      % Short title here
-   {The Ronen Method in simple 1-D problems}
+   {The Ronen Method in simple 1-D geometries}
 
@@
 \newcommand{\pluseq}{\mathrel{+}=}
+
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords ---}} #1}
+
+\graphicspath{{figures/}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %NEUTRON DIFFUSION BY THE RONEN METHOD IN HETEROGENEOUS MEDIA
-ON THE RONEN METHOD IN SIMPLE 1-D PROBLEMS
+ON THE RONEN METHOD IN SIMPLE 1-D GEOMETRIES
 }
@@
 %
+\keywords{Ronen method, Collision probability method, Neutron transport, CMFD}
 \clearpage
@@
 \end{equation}
-where $q_{(.),g,j}$ are the moments of the souce $q_g$ from Eq. \ref{eq:srcg} averaged in the volume of the $j$-th cell:
+where $q_{(.),g,j}$ are the moments of the source $q_g$ from Eq. \ref{eq:srcg} averaged in the volume of the $j$-th cell:
 \begin{subequations}
@@
 \int_{x_{j-1/2}}^{x_{j+1/2}}{ dx' E_{n}\left(\lvert \tau_g(x', x_{i+1/2}) \rvert \right) } =
-\frac{\sign(x_{i+1/2} - x_{j+1/2})}{\sigma_{t,g,j}} \cdot \\
+\frac{\sign(x_{i+1/2} - x_{j+1/2})}{\sigma_{t,g,j}} \\  \cdot
 \left[
@@
 The properties used for the computation of these functions are available elsewhere \cite{lewis1984computational,hebert2009applied}.
-We use the fortran library by Amos from 1983 in this work \cite{amos1983algorithm}.
+We use the Fortran library by Amos from 1983 in this work \cite{amos1983algorithm}.
 
@@
 After multiplication by $S(r)$ and still with uniform sources, Eq.
-\ref{eq:currp_cyl_atr} can be written in terms of the escape probability $\tilde{e}_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided along the normal direction the semicylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
+\ref{eq:currp_cyl_atr} can be written in terms of the escape probability $\tilde{e}_{j}(r)$ for a neutron to be emitted isotropically in ring $j$ and to leave uncollided along the normal direction the semi-cylinder surface at $r$, being crossed with angle $\omega \in W^\pm$:
 \begin{equation}
@@
 $L^\pm_j(h) = [-Y,\pm y] \cap V_j$ and where $V_j$ is the ring area.
-$\text{Ki}_2\left[\tau( y, y - \ell )\right]$ is the transport kernel expressing the probability of a neutron to travel uncollided along $\omega$ for a lenght $\tau$, given in mean free path units, from $(y - \ell)$ to $y$ \cite{stamm1983methods}.
+$\text{Ki}_2\left[\tau( y, y - \ell )\right]$ is the transport kernel expressing the probability of a neutron to travel uncollided along $\omega$ for a length $\tau$, given in mean free path units, from $(y - \ell)$ to $y$ \cite{stamm1983methods}.
 The integral on the track $\ell$ is written differently for the convex and for the concave parts of the rings with respect to the direction of flight, see for instance track 1 and 2 in Fig.
@@
 New computer programs have been developed in Python v3.8.2 with the numerical libraries NumPy v1.18.2 and SciPy v1.3.2 in order to solve the diffusion and the transport problems after calculating the first flight escape probabilities in the three geometries.
-The programs can treat heterogeneous media and use the multigroup formalism in energy, being intended for educational purposes.
+The programs can treat heterogeneous media and use the multigroup formalism in energy, being intended mainly for educational purposes.
 
-We present in this section a one-group homogeneous problem with isotropic scatterinig to study qualititatively the behavior of the Ronen method with angular redistribution in the curvilinear geometries.
-The setup of a complete test suite with problems of increasing levels of complexity is planned as future research action.
-Reference solutions are provided by the collision probability method, whose implementation takes advantage of the escape probabilities derived in section~\ref{sec:ce}, and whose numerical solution is explained in appendix \ref{sec:CPMsolution}.
+We present in this section one-group homogeneous critical problems with isotropic scattering to study the behavior of the Ronen method with angular redistribution in the curvilinear geometries.
+These cases belong to a test set of analytical benchmarks for code verification \cite{sood2003analytical}.
+The setup of the complete test suite with problems of increasing level of complexity is planned as future research action.
+Although analytical solutions exist in literature, reference solutions are here provided by the collision probability method, whose implementation takes advantage of the escape probabilities derived in section~\ref{sec:ce}, and whose numerical solution is explained in appendix \ref{sec:CPMsolution}.
+Besides, reference values of the fundamental flux are provided by the benchmark problems at a few positions.
 
-The problem is resolved in units of optical length according to the change of variable $x \leftarrow \sigma x$, obtained after dividing the balance equation by the total cross section $\sigma$.
-The isotropically multiplying source becomes then $q = c \phi_0 / 4\pi$ with the number of secondaries from scattering or fission events $c = (\sigma_s + \nu \sigma_f)/\sigma$.
-The multiplicity $\nu$ assumes the role of eigenvalue in abscence of external sources.
-The size of the problem is simply $b$ with $a=0$.
-$c$ and $b$ are then the free parameters in the problem.
+The problems are resolved in units of optical length according to the change of variable $x \leftarrow \sigma x$.
+The isotropically multiplying source becomes $q = c \phi_0 / 4\pi$ with the number of secondaries from scattering and fission events $c = (\sigma_s + \nu \sigma_f)/\sigma$.
+The transport equation to solve is then:
+\[
+\left( \mu \frac{\partial}{\partial x} + 1\right) \varphi(x,\mu)
+ = \frac{c}{4 \pi}\int_{-1}^{1}{\varphi(x,\mu) d\mu}
+\]
+The multiplicity $\nu$ recovers the role of eigenvalue in absence of external sources. The size of the problem is simply $b=r_c$ with $a=0$. %$c$ and $b$ are then the free parameters in the problem.
+The material specifications of the benchmark cases are reported in Table \ref{tab:xs}.
+The naming convention of the test cases follows by Sood et al., with the critical lengths listed in Table \ref{tab:rc}.
+All problems use the vacuum boundary condition.
+%Problem PUa-1-0-SL reproduces the full slab, while PUb-1-0-SL is calculated as half slab, to study the artificial correction introduced on the second flux moment.
 
-%\textcolor{blue}{The source assumes this form because the integration variables also have to the normalized by the mean free path (i.e. multiplied by the total cross section).}
+\begin{table}[htb]
+\centering
+\caption{One-group cross section values used in the benchmark problems.}\label{tab:xs}
+\begin{tabular}{c|*{6}{l}}
+Material & \multicolumn{1}{c}{$\nu$} & \multicolumn{1}{c}{$\sigma_f$} & \multicolumn{1}{c}{$\sigma_c$} & \multicolumn{1}{c}{$\sigma_s$} & \multicolumn{1}{c}{$\sigma_t$} & \multicolumn{1}{c}{$c$}\\ \hline
+Pu-239 (PUa)& 3.24 & 0.081600 & 0.019584 & 0.225216 & 0.32640 & 1.50\\
+Pu-239 (PUb)& 2.84 & 0.081600 & 0.019584 & 0.225216 & 0.32640 & 1.40\\
+  H20 (refl)& 0.0 & 0.0 & 0.032640 & 0.293760 & 0.32640 & 0.90\\
+\end{tabular}
+\end{table}
 
-%\textcolor{green}{The use of the integral transport eqn.
-to get reference solutions is motivated by two main reasons.
-The first is to use again what we're implementing now for the escape probabilities.
-The second is to get the reference solution by inverting the operator used in the RM.
-So that we'll really know what is the solution to match.
-Furthermore, this won't be affected by ray effects of any kind.
-Lastly, we'll have to be very careful to the endpoint singularity when computing the collision probabilities.}
+\begin{table}[htb]
+\centering
+\caption{Reference critical lengths $r_c$ of the test cases, with the multiplication factor $k_D$ and the geometrical buckling $B^2_G$ of the analytical solution in diffusion.}\label{tab:rc}
+\begin{tabular}{l|c|c|c|c|c}
+\multirow{2}{*}{Problem Id.} & Geometry & \multicolumn{2}{c|}{$r_c$}& \multirow{2}{*}{$k_D$} & \multirow{2}{*}{$B_G^2$}\\ \cline{3-4}
+ & type & (mfp) & (cm) & & \\ \hline
+PUa-l-0-SL  & Slab       & 0.605055     & 1.853722 & 0.891973 & 0.191159\\
+PUb-1-0-SL  & Slab       & 0.736603   & 2.256751 & 0.913739 & 0.149267\\
+%PUb-1-0-SL  & Slab       & 0.73660355   & 2.256751\\
+PUb-1-0-CY  & Cylinder   & 1.396979     & 4.279960 & 0.956090 & 0.138266\\
+PUb-1-0-SP  & Sphere     & 1.985343 & 6.082547 & 0.964129 & 0.136287\\
+%PUb-1-0-SP  & Sphere     & 1.9853434324 & 6.082547\\
+\end{tabular}
+\end{table}
+
+The analytical solutions from diffusion theory are available in Table \ref{tab:adsol}, where the geometrical buckling $B_G^2$ comes as root of the transcendental equations in the last column, see Table \ref{tab:rc}.
+The multiplication factor $k_D$ of the analytical diffusion problem is obtained by equating the geometrical buckling and the material buckling $B^2_M = (\nu\sigma_f/k - \sigma_a)/D = (k_\infty/k - 1)/L^2$, where $k_\infty = \nu\sigma_f / \sigma_a$ is the multiplication factor in the infinite medium and $L^2 = D/\sigma_a$ is the diffusion area.
+The benchmark problems communicate the reference transport fundamental flux at given positions, see Table \ref{tab:rff}.
+The scalar fluxes are all normalized to be unitary at the center.
+
+\begin{table}[hbt]
+\centering
+\caption{Analytical solutions from diffusion in centered, bare and homogeneous one-group problems of length $X$ (vacuum boundary with extrapolation distance $d = \zeta D$).}\label{tab:adsol}
+\begin{tabular}{c|c|c}
+Geometry type & Solution & $B_G$, s.t.\\ \hline[1mm]
+Slab & $\cos{(B_G x)}$ & $\tan{(B_G X)} = 1 / (d B_G), \: B_G \in (0, \pi /(2X))$\\[1mm]
+Cylinder & $J_0 (B_G x)$ & $J_0(B_G X) - d B_G J_1(B_G X), \: B_G \in (0, 2.404825 / X)$ \\[1mm]
+Sphere & $\sin{(B_G x)}/x$ & $B_G X - (1 - X / d) \tan{(B_G X)}, \: B_G \in (\pi/(2X), \pi/X)$ \\
+\end{tabular}
+\end{table}
+
+\begin{table}[hbt]
+\centering
+\caption{Fundamental flux from the reference transport solution of the benchmark.}\label{tab:rff}
+\begin{tabular}{l|c|llll}
+\multirow{2}{*}{Problem Id.} & Geometry & \multicolumn{4}{c}{$r=x/r_c$}\\ \cline{3-6}
+ & type & \multicolumn{1}{c}{$r_1=0.25$} & \multicolumn{1}{c}{$r_2=0.5$} & \multicolumn{1}{c}{$r_3=0.75$} & \multicolumn{1}{c}{$r_4=1$}\\ \hline
+% PUb-1-0-SL & Slab     & 0.9701734 & 0.8810540  & 0.7318131 &  0.4902592\\
+PUb-1-0-SL & Slab     & 0.970173 & 0.881054  & 0.731813 &  0.490259\\
+PUb-1-0-CY & Cylinder & \multicolumn{1}{c}{-} & 0.8093     & \multicolumn{1}{c}{-} & 0.2926\\
+PUb-1-0-SP & Sphere   & 0.935380 & 0.755753 & 0.498843 & 0.192226
+%PUb-1-0-SP & Sphere   & 0.93538006& 0.75575352 & 0.49884364 & 0.19222603
+\end{tabular}
+\end{table}
+
+After computing the numerical solution of the diffusion problem by finite differences without corrections at the cell interfaces, we evaluate new current estimates by using escape, transmission and reflection probabilities according to the given geometry type, as derived from the integral equation in section \ref{sec:ce}.
+Then, the solution by the Ronen method is sought iteratively as explained in section \ref{sec:impl}.
+Anderson acceleration through the DAAREM algorithm is also used during the iteration process \cite{henderson2019damped}, reducing considerably the number of iterations to achieve residuals on the relative flux differences below $10^{-6}$.
+Its use is crucial to find the fixed point solution throughout the non-linear iterations of the RM.
+
+The calculation of half slab by CPM after setting (white) reflection at the center yields poor results due to missing contributions from the higher flux moments, see Figure \ref{fig:cpm_hslab_err}.
+The solution obtained by RM takes into account an artificial correction applied to the only second moment, reducing the flux error, but its eigenvalue solution is higher than 1 of 836 pcm on converged meshes.
+This issue, discussed in section \ref{sec:bc}, is more severe with very thin slab, like in the case PUa-1-0-SL, and disappears when the slab thickness increases beyond a few mean free paths (mfp).
+This forces the modelling of the full slab when verifying the flux distribution for the case PUb-1-0-SL.
+Such issue does not appear at the center of the solid cylinder or sphere.
+% solid = not hollow
+All methods computes a critical configuration for PUa-1-0-SL after unfolding the half-slab. The study to verify the fundamental flux is then only shown for the case PUb-1-0-SL.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=.8\linewidth]{cpm_hslab_err.pdf}
+\caption{Error in the half slab (PUa-1-0-SL) with white reflection at the right and vacuum at the left.}
+\label{fig:cpm_hslab_err}
+\end{figure}
+
+About the cases PUb, the relative error on the critical flux computed by CPM against the values from Table \ref{tab:rff} are shown in Figure \ref{fig:cpm_PUb_flxerr} with increasing number of cells ($I$) always using equivolume meshes.
+The same figure shows also the results obtained by RM.
+The spherical geometry needs finer meshes to decrease the error, which is always higher near the vacuum boundary.
+Refined meshes near the boundary, drawn for instance by a geometric progression with ratio less than one, can lower this error, see the program released with this publication.
+The RM results practically overlaps those obtained by the CPM, but at the vacuum boundary where the monotonic behavior of the error trend is broken with fine meshes, leaving a residual error of about 1-2\% in the slab and in the cylinder, and higher than 3\% in the sphere.
+The flux at the boundary used to reproduce the current by diffusion is approximated by a quadratic polynomial fitting the midpoint fluxes at the nearest three cells, instead of the only flux of the last cell.
+
+The number of cells in the slab is doubled indeed for taking a thickness of $2r_c$ in the calculations.
+The deviation of the multiplication factor from unity by refining the mesh is shown in Figure \ref{fig:cpm_PUb_kerr}, instead.
+The same trend for the three geometries is noticed, with the spherical one needing finer meshes to achieve the same level of error.
+The multiplication factor computed by RM is about the same as the one given by CPM.
+Four integration points are used in the Gauss-Jacobi quadratures, yielding an error lower than 0.1\%.
+
+\begin{figure}[hp]
+\centering
+\includegraphics[width=.8\linewidth]{cpm_PUb_flxerr.pdf}
+\caption{Relative error in percent of the fundamental flux for all PUb cases.}
+\label{fig:cpm_PUb_flxerr}
+\end{figure}
+
+\begin{figure}[hp]
+\centering
+\includegraphics[width=.8\linewidth]{cpm_PUb_kerr.pdf}
+\caption{Error in pcm of the multiplication factor $k$ in the PUb critical benchmark problems.}
+\label{fig:cpm_PUb_kerr}
+\end{figure}
+
+The solution by CPM needs a single inversion of a full matrix with the direct solving scheme from appendix \ref{sec:CPMsolution}.
+This scheme may not be suitable to problems with a high number of energy groups and spatial cells.
+The RM needs to invert several times a tridiagonal matrix, which is efficiently performed in our code by Thomas TDMA algorithm, a simplified form of Gaussian elimination that can be used to solve tridiagonal systems of equations.
+Both methods share the calculation part of the first flight escape/collision probabilities.
+Typical runtimes of the benchmark problems treated in this article are quite fast and they can be run on any laptop computers.
+The calculation of the first flight probabilities is the most expensive part, especially in curvilinear geometries, and it should be reprogrammed in a compiled language to save runtime.
 
@@
 This originates an iterative scheme leading to new flux distributions solved by a diffusion solver yet with the aim to fulfill the integral transport equation.
-The direct resolution of the integral equation would imply the inversion of large matrices, with poor control of their conditioning.
+The direct resolution of the integral equation implies the inversion of full matrices, with poor control of their conditioning.
 The solution of the diffusion equation offers many numerical advantages instead, solution speed and robustness above all.
 
-Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD, which avoids the numerical issues arising with flat flux.
+Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD that avoids the numerical issues arising with flat flux.
 This is the option adopted in this work.
 The implementation of the boundary conditions is improved to reproduce the expected vanishing current in case of reflection.
+However, this correction is not sufficient to fix the limitations due to the use of white reflection, which is particularly serious in problems smaller than a mean free path.
 
-We obtain more accurate results for the two-group benchmark problem reported in \cite{tomatis2011application}.
-The final version of the article will show the results of the application of the method in the curvilinear coordinate systems, still using isotropic sources.
-In general, slow convergence is observed for the scalar flux, whose larger discrepancy with respect to the reference is always located on the vacuum boundary.
-Although the method is converging to the reference results provided by a discrete ordinate transport code, the improvement of the convergence rate and the use of coarser meshes are crucial for the advancement of the methodology in practical applications.
-These topics will be addressed as future developements.
+The RM is developed in this work by following the CPM formalism and theory.
+Only first flight escape probabilities are computed, by which all other kinds of probabilities are derived using conservation and reciprocity properties.
+The solutions are verified with simple one-group homogeneous problems from the benchmark test suite by Sood and al.
+\cite{sood2003analytical}.
+More benchmark problems will be analyzed in a future work to study the RM with material heterogeneity and with many energy groups.
+The application of the RM to problems with anisotropic scattering suffers from the lack of the flux moments higher than the first, since diffusion can count only on the net current.
+This article shows the extension of the RM to linearly anisotropic scattering in the source terms in the case of the slab.
+The study of anisotropy still needs further developments.
+
+The use of Anderson acceleration in the RM iterations was crucial to find converged results, fixing the issue of slow convergence noticed in the previous published works.
+The large discrepancy on the scalar flux observed in previous works at bare vacuum boundaries has now been reduced to a few percent with respect to the reference solutions.
+This suggests that same test problems could have been affected in the past implementations by false convergence for very slowly decreasing convergence rates.
+Additional tests are on-going to verify this assertion.
+The upgrade of the RM to coarser meshes and different implementations of the CMFD scheme will be the objects of future research and development.
+These are considered as central topics for the advancement of the methodology in practical applications.
 
@@
 The authors express their gratitude to Prof. Yigal Ronen who initiated the method.
+
+\section*{ADDITIONAL MATERIAL}
+
+The theory and results of this article were produced by the computer program available at \texttt{https://github.com/ndarmage/RonenMethod1D.git}.
+This program is distributed for educational purposes and basic training in transport theory, without containing any confidential material on nuclear data.
 
@@
 The definite integrals can be regularized by a proper change of variable following the Flurig scheme, which yields a Gauss-Jacobi quadrature scheme \cite{carlvik1966integral}.
-We propose herafter a general change of variable to obtain both schemes at once:
+We propose hereafter a general change of variable to obtain both schemes at once:
 \begin{equation}
@@
 
-\section{APPENDIX. Direct solution of integral transport by the collision probabilty method}
+\section{APPENDIX. Direct solution of integral transport by the collision probability method}
 \label{sec:CPMsolution}

### 2020-05-25 CPM1D/cpm1dcurv.py

@@ -42,7 +42,7 @@ np.set_printoptions(precision=6)
 class solver_options:
     """Object collecting (input) solver options."""
     toll = 1.e-6  # default tolerance
-    nbitsmax = 100  # default nb. of max iterations (its)
+    nbitsmax = 500  # default nb. of max iterations (its)
 
     def __init__(self, iitmax=nbitsmax, oitmax=nbitsmax,
                  otoll=toll, itoll=toll, ks=None, GQ="Gauss-Jacobi",

### 2020-05-25 CPM1D/tests/Sood_PUx-1-0-x.py

@@ -59,66 +59,73 @@ if __name__ == "__main__":
     # positions (fractions r/rc) to verify the flux results
     rf = np.linspace(0, 1, 5)
     
-    m = 'PUa'  # only one case in the test suite
-    L = rc = 1.853722 * 2 # cm, critical length
-    # L = rc = 0.605055  # mfp
-    xs_media, media = set_media(materials[m], L, m)
-        
-    geo = "slab"
-    case = "%s-1-0-%s" % (m, get_geoid(geo))
-    lg.info("Test case: " + case)
-
-    I = 20  # number of cells in the spatial mesh
-    r = equivolume_mesh(I, 0, L, geo)
-    # r = np.array([0, 1 / 8., 1 / 6., 0.9, 1]) * L
-    data = input_data(xs_media, media, r, geo, LBC=0, RBC=0)
+    # cases for the ictt26 article:
+    # [2, 3, 4, 5, 8, 10, 12, 15, 20, 25, 30, 40, 50, 75, 100]
+    for I0 in [40]:
     
-    # ks is needed anyway when validating the input solver options
-    k, flx = solve_cpm1D(data, solver_options(ks=np.full(I, 0)), False)
-    np.testing.assert_allclose(k, 1, atol=1.e-3, err_msg=case +
-                               ": criticality not verified")
-    np.save(os.path.join(odir, case + '_ref.npy'), [k, flx])
-    
-    m = 'PUb'  # only one case in the test suite
-    # critical lengths
-    rc_dict = {'slab': 2.256751, 'cylinder': 4.279960, 'sphere': 6.082547}
-    
-    for geo in geoms:
-        case = "%s-1-0-%s" % (m, get_geoid(geo))
-        lg.info("Test case: " + case)
-        L = rc_dict[geo]
-        rs = rf * L
-        if geo == 'slab':
-            I, nks, LBC, ratio0 = 40, 0, 0, .975
-            rs += L
-            L *= 2
-        else:
-            nks, LBC = 4, 2
-            if 'cylind' in geo:
-                I, ratio = 40, .95
-            else:
-                I, ratio = 50, .9
-        # r = equivolume_mesh(I, 0, L, geo)
-        r = geomprogr_mesh(N=I, L=L, ratio=.95)
+        m = 'PUa'  # only one case in the test suite
+        L = rc = 1.853722 * 2 # cm, critical length
+        # L = rc = 0.605055  # mfp
[…]

### 2020-05-25 FD1dMGdiff/FDsDiff1D.py

@@ -445,6 +445,7 @@ def set_diagonals(st, Db, data, dD=None):
         # different attempts to get higher order accuracy
         # option (a) use J_b = \pm flx_b / zeta, with flx_b = flx_0 (1st order) 
         # option (b) central fin. diff. with extrap distance, at 2nd order
+        #  *** (case b must be debugged because it doesn't work)
         # option (c) fit by 2nd order polynomial
         if zetal < max_float:
             # b[id0] += xb0 / zetal  # (a)
@@ -1163,7 +1164,7 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
 
 
 def run_calc_with_RM_its(idata, slvr_opts, filename=None):
-    lg.info("Prepare input xs data")
+    lg.info("Prepare input xs data")            
     xs = unfold_xs(idata)
     lg.info("-o"*22)
 

### 2020-05-25 FD1dMGdiff/data/SoodPNE2003.py

@@ -20,6 +20,11 @@ Pu-239 (b) 2.84 0.081600 0.019584 0.225216 0.32640 1.40
 H20 (refl) 0.0  0.0      0.032640 0.293760 0.32640 0.90
 """
 
+Lc = {'PUa-1-0-SL': 1.853722,
+      'PUb-1-0-SL': 2.256751,
+      'PUb-1-0-CY': 4.279960,
+      'PUb-1-0-SP': 6.082547}  # critical lengths
+
 
 def get_geoid(geo):
     if geo == 'slab':
@@ -74,6 +79,30 @@ def diffk_ref(BG2, m):
     PNL = 1 / (1 + L2 * BG2)  # non leakage probability
     return kinf * PNL
     
+
+def analytical_sol(geo, L):
+    # only problems with vacuum boundary condition!
+    if geo == 'centered-slab':
+        BG = brentq(lambda b: np.tan(b*L) - 1 / extrap_len / b,
+                    1.e-5, .5 * np.pi / L - 1.e-5)
+        diffsol_ref = lambda x: np.cos(BG * x)
+    elif geo == 'full-slab' or geo == 'slab':
+        BG = brentq(lambda b: np.tan(b*L) - 1 / extrap_len / b,
+            1.e-5, .5 * np.pi / L - 1.e-5)
+        coef = 1 / np.tan(BG * L)  # for symmetric distribution 
+        diffsol_ref = lambda x: np.sin(BG * x) + coef * np.cos(BG * x)
+    elif geo == 'cylinder':
+        BG = brentq(lambda b: J0(b*L) - extrap_len * b * J1(b*L),
+            0, 2.4048255577 / L)
+        diffsol_ref = lambda x: J0(BG * x)
+    elif geo == 'sphere':
+        BG = brentq(lambda b: b*L - (1 - L / extrap_len) * np.tan(b*L),
+            .5 * np.pi / L, np.pi / L)
+        diffsol_ref = lambda x: np.sin(BG * x) / x
+    else:
+        raise ValueError(geo + ' is not supported yet.')
+    return diffsol_ref, BG
+
 
 tlines = [l for l in Table2.split('\n')[1:-1] if not l.startswith('#')]
 get_line = lambda lines, key: [l for l in lines if key in l][0]

### 2020-05-25 FD1dMGdiff/quad_extrap_notes.py

@@ -1,0 +1,88 @@
+def quadratic_fit_3p(rs, fs):
+    """
+    fit a function by quadratic polynomial passing for three points
+
+    f(r) = (
+      f0*(r**2*r1 - r**2*r2 - r*r1**2 + r*r2**2 + r1**2*r2 - r1*r2**2)
+    - f1*(r**2*r0 - r**2*r2 - r*r0**2 + r*r2**2 + r0**2*r2 - r0*r2**2)
+    + f2*(r**2*r0 - r**2*r1 - r*r0**2 + r*r1**2 + r0**2*r1 - r0*r1**2)
+    ) / ((r0 - r1)*(r0 - r2)*(r1 - r2))
+    """
+    r0, r1, r2 = rs
+    f0, f1, f2 = fs
+    rp2 = r**2
+    r0p2, r1p2, r2p2 = r0**2, r1**2, r2**2
+    d = (r0 - r1)*(r0 - r2)*(r1 - r2)
+     
+    # f(r) = (
+    #   f0*((rp2 + r1*r2)*(r1 - r2) - r*(r1p2 + r2p2))
+    # - f1*((rp2 + r0*r2)*(r0 - r2) - r*(r0p2 + r2p2))
+    # + f2*((rp2 + r0*r1)*(r0 - r1) - r*(r0p2 + r1p2))
+    # ) / ((r0 - r1)*(r0 - r2)*(r1 - r2))
+    
+    # f(r) = c0(r) * f0 + c1(r) * f1 + c2(r) * f2
+     
+    # coefficients to use in the system eqs.
+    c0 = ((rp2 + r1*r2)*(r1 - r2) - r*(r1p2 + r2p2)) / d
+    c1 = ((rp2 + r0*r2)*(r0 - r2) - r*(r0p2 + r2p2)) / -d
+    c2 = ((rp2 + r0*r1)*(r0 - r1) - r*(r0p2 + r1p2)) / d
+    return c0, c1, c2
+
+
+# .. note:: the following function was implemented to get more accurate flux at
+#           the vacuum boundary but it does not work yet as expected. Possible
+#           bug. More investigations are necessary. 
+
+def quadratic_fit_zD(rs, fs, zD):
+    """
+    fit a function by quadratic polynomial passing for two points and with
[…]

### 2020-05-25 FD1dMGdiff/tests/Sood_PUx-1-0-x.py

@@ -51,9 +51,14 @@ refflx = {
 }
 
 
-
-
 geoms = ["slab", "cylinder", "sphere"]
+
+
+def update_npy(file, to_append):
+    data = np.load(file, allow_pickle=True)
+    for d in to_append:
+        data = np.insert(data, -1, d)
+    np.save(file, data)
 
 
 if __name__ == "__main__":
@@ -67,170 +72,186 @@ if __name__ == "__main__":
     flx_tolerance = np.ones(4)  # tolerances are in percent
     flx_tolerance[-1] = 2  # RM cannot fit transport at bare boundary
     
-    # --------------------------------------------------------------------------    
-    m = 'PUa'  # only one case in the test suite
-    BM2m, extrap_len = BM2(materials[m]), 2.13 * materials[m]['D'][0]
-    lg.info("Material buckling %.5f" % BM2m)
-    L = rc = 1.853722 # * 2 # cm, critical length
-    # L = rc = 0.605055  # mfp
-    L_e = L + extrap_len
-    xs_media, media = set_media(materials[m], L, m)
-        
-    geo = "slab"
-    case = "%s-1-0-%s" % (m, get_geoid(geo))
-    lg.info("Test case: " + case)
-    
-    # load reference results computed by CPM1D
-    k_ref, flx_ref  = np.load(os.path.join(refdir, case + "_ref.npy"),
-                              allow_pickle=True)
+    # -------------------------------------------------------------------------- 
 
-    I = 25  # number of cells in the spatial mesh (20 in complete slab)
-    r = equivolume_mesh(I, 0, L, geo)
-    # r = np.array([0, 1 / 8., 1 / 6., 0.9, 1]) * L
-    LBC, RBC = 2, 0
-    data = input_data(xs_media, media, r, geo, LBC=LBC, RBC=RBC)
-    lg.info(' -o-'*15)
-    lg.info('analytical solution of the diffusion equation')
-    BG = brentq(lambda b: np.tan(b*L) - 1 / extrap_len / b,
-                1.e-5, .5 * np.pi / L - 1.e-5)
-    diffsol_ref = lambda x: np.cos(BG * x)
-    ansol, DFkref = diffsol_ref(data.xim), diffk_ref(BG**2, materials[m])
-    lg.info('fund. flx\n' + str(ansol / np.sum(ansol * data.Vi) * G * I))
[…]

### 2020-06-05 docs/PHYSOR2020/ANE-RM-2020.tex
Update ANE-RM-2020.tex

--- 2020-01-05 docs/PHYSOR2020/ANE-RM-2020.tex
@@
-\documentclass[review,3p,onecolumn,sort&compress]{elsarticle}
+\documentclass[preprint, authoryear, 12pt, a4paper, onecolumn]{elsarticle}
 %
 %  various packages that you may wish to activate for usage 
-\usepackage{booktabs}
-\usepackage{natbib}
+%\usepackage{booktabs}
+%\usepackage{natbib}
 %\usepackage{cite}
@@
 \usepackage[english]{babel}
-\usepackage[autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
+%\usepackage[autostyle, english = american]{csquotes}
+%\MakeOuterQuote{"}
 \usepackage{color}
@@
 \usepackage{lineno}
-\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,
+\usepackage[colorlinks=true, a4paper=true, pdfstartview=FitV,%
             linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
+
+% for algorithms
+% \usepackage{algorithm}
+% \usepackage{algpseudocode}
+
+\usepackage{tikz}
 \usepackage{xfrac}
 \usepackage{units}
-\usepackage{tikz}
 
 \usepackage[printonlyused]{acronym}
-
-\modulolinenumbers[1]
 
@@
 \newcommand{\eqs}[1]{Eqs.~(\ref{#1})}
-\newcommand{\tsup}[1]{\textsuperscript{#1}}
-\newcommand{\tsub}[1]{\textsuberscript{#1}}
+% \newcommand{\tsup}[1]{\textsuperscript{#1}}
+% \newcommand{\tsub}[1]{\textsuberscript{#1}}
 \newcommand{\keff}{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}
@@
 \newcommand{\mcL}{\tau}
+\newcommand{\dx}{\Delta}
+\newcommand{\dd}{\delta D}
+\newcommand{\tild}{\tilde{D}}
+
 % about notes and comments from each author
@@
 
-%\newcommand{\authorHead}      % Author's names here
-%           {Israeli, Ravetto \& Gilad}  
-%\newcommand{\shortTitle}      % Short title here
-%           {Adjoint Problem as Physical Heuristic for Loading Pattern Optimization}
-
 \newcommand\mscriptsize[1]{\mbox{\scriptsize\ensuremath{#1}}}
 \newcommand\mtiny[1]{\mbox{\tiny\ensuremath{#1}}}
+
+\renewcommand{\cite}{\citep}
 
@@
 
-		\linenumbers
-
-		\title{INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS USING THE pCMFD SCHEME}
+  \title{Integral Transport Correction to Diffusion Calculations \\ Using the pCMFD Scheme}
 
@@
   \address[bgu]{The Unit of Nuclear Engineering, Ben-Gurion University of the Negev, Beer-Sheva 8410501, Israel}
-		\address[cea]{CEA, DEN, Service d’\'etudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA), 	
+  \address[cea]{CEA, DEN, Service d{'}\'etudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA), \\
                 Universit\'e Paris-Saclay, F-91191, Gif-sur-Yvette, France}
@@
   %------------------------------------------------------------
-		\begin{abstract}
-		\modulolinenumbers[1]
-		\linenumbers
-		The Ronen method is implemented and studied numerically in two-group one-dimensional homogeneous slab configuration.
-Since slow convergence is observed for the scalar flux especially near the vacuum boundary, new techniques for accelerating the convergence are investigated.
-For example, we use integral flux intermediate values as new boundary conditions at each iteration and we update iteratively the extrapolated boundary using the corrected local diffusion coefficient.
-Moreover, the pCMFD scheme is implemented and its performances are compared with those of standard CMFD scheme.
-		\end{abstract}
+  \input{abstract/abstract}
   %------------------------------------------------------------
   \begin{keyword}
-		Neutron diffusion \sep Integral transport \sep Non-linear transport correction \sep CMFD \sep pCMFD
+  \input{keywords}
   \end{keyword}
@@
 
+%\clearpage
+
+\modulolinenumbers[5]
 \linenumbers
 
-\newpage
+\input{contents}
 
-\section{INTRODUCTION}
-\label{sec:intro}
-
-The distribution of the neutron flux in the reactor core is described by the neutron transport equation.
-Transport calculations on a full core scale can be a highly intensive computational task.
-To overcome this difficulty, faster (but less accurate) multigroup neutron diffusion solvers are often used.
-Indeed, future Gen-IV reactor designs are characterized by strong heterogeneity in the core and modern calculation schemes evolve towards best-estimate codes, aiming at high accuracy for these new configurations.
-Hence, the accuracy of diffusion calculations is investigated.
-A crucial issue in obtaining an accurate diffusion calculation is the formulation of the diffusion coefficient.
-The calculation of this parameter should be based on physical insights from the full transport equation, such that the resulting (transport-corrected) diffusion approximation can capture the transport phenomena of interest.
-
-% Daniele: I found this paragraph commented, but I think that the two following sections should be properly introduced in this section. Therefore, I am uncommenting it.
-The main hypothesis of this research, called the Ronen Method (RM)~\cite{Ronen-2004,Tomatis-2011}, is based on iterative calculations of the multigroup diffusion coefficients, driven by accurate relations between the neutron current density and the neutron flux as derived from the integral transport equation.
-The iterative scheme calculates new flux distributions using a diffusion solver but with a (spatially) modified diffusion coefficient according to the current calculated using the integral transport equation.
-Alternatively, the Coarse Mesh Finite Differences (CMFD) scheme can be enforced in the discretized form of the diffusion equation to reproduce the transport current by means of a drift term.
-The implementation of one its variants, the partial current formulation of the CMFD (pCMFD), is studied in this work.
-%
-% The direct resolution of the integral relation between the diffusion coefficient and the transport current would imply the inversion of large matrices, with poor control of their conditioning.
-Nonetheless, the integral current can be enforced in the Coarse Mesh Finite Difference (CMFD) discretized form of the diffusion equation, which avoids the numerical issues resulting from small flux gradients.
-This is the option adopted in this study.
-
-% ------------------------------------------
-\section{COARSE MESH FINITE DIFFERENCES}
-\label{sec:CMFD-intro}
-
-The CMFD has been largely used in nodal diffusion codes as a technique for storage reduction, allowing for separate resolution of many two nodes problems in an iterative scheme~\cite{Smith-1983,Lawrence-1986}.
-Recently, multi-dimensional transport codes have used it as acceleration technique and the convergence of different implementations was studied in simple homogeneous slab problems~\cite{Jarrett-2016,Shen-2019}.
-
-The use of a coarse mesh for the discretization of the problem is generally causing considerable error by truncation applied on the finite difference approximations of the derivative terms.
-On the other hand, it yields very fast calculations.
-The CMFD method recovers corrective terms by exploiting functional relations between the (scalar) flux and the current density, which appear in the neutron balance equation.
-The balance equation is solved for the flux, so that local models seek more accurate estimates of the current in order to derive these corrections.
-In principle, the corrective terms can be computed with a different physics other than diffusion, which is always solved at the coarse level.
-This facilitates its application to accelerate complex multi-dimensional transport codes.
-This acceleration is actually implemented by rebalancing the scalar flux, with the optional use of some relaxation~\cite{Park-2017}.
-Hence, a non-linear iterative scheme arises between the CMFD solver and the computation of the local corrections, which use the latest estimates of the flux available from the diffusion solver.
-
-Second-order SPN equations can be solved by ordinary diffusion codes~\cite{Larsen-1993}.
-Yamamoto et Al.~\cite{Yamamoto-2016} noticed numerical instabilities when correcting pseudo-currents obtained solely by the second-order moments of the expanded SP3 flux.
-This is because this quantity is generally smaller than the scalar flux (0-th moment) and can change its sign.
-They proposed to modify the balance equation for the second moment in order to fix this numerical behavior.
-The modification consisted of a shift with a positive quantity of the second moment so that their difference between neighboring quantities is unchanged, and their sum becomes positive and arbitrarily large.
-
-When partial currents can be computed, the pCMFD method~\cite{Cho-2003} can be used to determine two distinct corrective terms per positive and negative partial currents, instead of having a single degree of freedom per cell surface.
-Another version of the CMFD called artificial diffusion~\cite{Zhu-2016,Jarrett-2016} redefines the diffusion coefficient as the sum of the original value and a complement derived from the current difference, which is still considered as proportional to the flux gradient.
-This scheme can potentially lead to negative diffusion constants.
-
-The CMFD (and its variants) was also chosen for the implementation of the RM, where an integral transport operator estimated higher order currents to calculate the correction terms.
-Contrary to the previous implementations, no operator was inverted to get a new higher order approximation of the flux solution.
-As well, this offered a fast and more accurate estimate of the current too.
-
-% ------------------------------------------
-\section{THE RONEN METHOD}
-\label{sec:RM}
-
-In 2004, Ronen~\cite{Ronen-2004} suggested to derive corrected diffusion coefficients using Fick's law and more accurate estimations of the neutron currents by means of integral transport operators, whereas the neutron flux was resolved by diffusion theory.
-Denoting the integral transport and diffusion currents by $\bm{J}\rE$ and $\bm{J}^D\rE$, respectively, the Ronen idea is based on adapting the diffusion coefficient such that
-\begin{equation}
-\label{eq:Fick}
-\bm{J}^D\rE = -D\rE\bnabla\phi\rE \cong \bm{J}\rE.
-\end{equation}
-
-Since these accurate estimates of the currents were based on a known flux distribution, it was also suggested to execute new diffusion calculations, thus updating iteratively the diffusion coefficients in the global calculation according to
-\begin{equation}
-\label{eq:RM-it}
-D^{(k+1)}\rE = - \frac{\lvert \bm{J}^{(k)}\rE \rvert}{\lvert \bnabla \phi^{(k)}\rE \rvert},
-\end{equation}
-where $k$ is the iteration index. The use of a tensor notation is needed for the diffusion coefficient in general multidimensional problems.
-
-The motivation for this method was to overcome the inherent limitation of Fick's law requiring smooth flux gradients and thus weakly absorbing medium.
-Nevertheless, isotropic scattering remained as a basic postulate.
-For example, in a one-dimensional homogeneous slab with void boundary conditions, Eq.~\eqref{eq:RM-it} takes the following form~\cite{Ronen-2004}
-\begin{equation}
-\label{eq:RM-it-1D-slab}
-D^{(k+1)}(x,E) = \left. -\frac{1}{2} \int_0^a dx'
-{E_2[\sigma(E) \lvert x-x' \rvert]\operatorname{sign}(x-x')q^{(k)}(x',E)}
-\middle/ \frac{\partial}{\partial x}\phi^{(k)}(x,E),\right.
-\end{equation}
-where the source term $q^{(k)}$ is calculated using the multigroup diffusion model with the available scalar flux, and the updated diffusion coefficient $D^{(k+1)}$ is evaluated using the integral expression for the transport current.
-
-In 2011, Tomatis and Dall'Osso~\cite{Tomatis-2011} provided a numerical demonstration of the simple slab problem.
-They chose the CMFD scheme in the diffusion solver for taking into account the new currents estimated by the integral transport operator.
-%
-%They proposed to update non-linearly the diffusion coefficients at the cell interfaces of the spatial mesh by the coarse mesh finite differences method (CMFD).
-%
-This technique can avoid indeterminate divisions in case of vanishing flux gradients and reproduces the transport effects under a drift term.
-It was observed that the RM could drive the flux distribution closer to the transport reference solution.
-As expected, the largest errors were located near the boundary, where the transport effects are more pronounced, slowly decreasing even after many iterations.% Their work was limited to the homogeneous slab, and resolved neutron diffusion on the same discretized spatial mesh used for the reference from neutron transport.
-
-% ------------------------------------------
-\section{NUMERICAL IMPLEMENTATION}
-\label{sec:RM-num}
-
-The neutron balance equation for a $k$-eigenvalue problem integrated in the $i$-th element of a one-dimensional mesh is (see Fig.~\ref{fig:mesh1D})
-\begin{equation}
-\label{eq:balance}
-J_{i+\hzi ,g} - J_{i-\hzi ,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
-\end{equation}
-where $J$ denotes the net current at the cell surface, $\sigma$ denotes the total cross section and the subscript $g$ denotes the energy group. $q$ is the isotropic neutron source defined as
-\begin{equation}
-\label{eq:qsrc}
-q_{i,g} = \sum\limits_{g'=1}^G\sigma_{s,0,i,g\leftarrow g'}\phi_{i,g'} +
-\frac{\chi_g}{\keff}\sum\limits_{g'=1}^G\nu\sigma_{f,i,g'}\phi_{i,g'},
-\end{equation}
-where $\sigma_0$ is the isotropic scattering cross section, $\chi$ is the fission spectrum, $\keff$ is the effective multiplication factor (the eigenvalue), $\nu$ is the average number of neutrons emitted per thermal fission, and $\sigma_f$ is the fission cross section.
-As well, integer and rational subscripts indicate node-averaged and interface quantities, respectively.
-%
-\begin{figure}[htbp]
-	\centering
-	\begin{tikzpicture}
-	\tikzstyle{every node}=[font=\footnotesize]
-	\draw[thick] (0,0) -- (3,0);
-	\node[anchor=south] at (3.5cm,-5pt) {$\ldots$};
-	\draw[thick] (4,0) -- (7,0);
-	\node[anchor=south] at (7.5cm,-5pt) {$\ldots$};
-	\draw[thick,->] (8,0) -- (11,0) node[anchor=west] {$x$};
-
-	\draw ( 0 cm,2pt) -- ( 0 cm,-2pt) node[anchor=north] {$-\hzi$};
-	\node[anchor=south] at (1cm,1pt) {0};
-	\draw ( 2 cm,2pt) -- ( 2 cm,-2pt) node[anchor=north] {$+\hzi$};
-
-	\draw ( 4.5 cm,2pt) -- ( 4.5 cm,-2pt) node[anchor=north] {$i-\hzi$};
-	\node[anchor=south] at (5.5cm,1pt) {$i$};
-	\draw ( 6.5 cm,2pt) -- ( 6.5 cm,-2pt) node[anchor=north] {$i+\hzi$};
-
-	\draw ( 8.5 cm,2pt) -- ( 8.5 cm,-2pt) node[anchor=north] {$I-\sfrac{3}{2}$};
-	\node[anchor=south] at (9.5cm,1pt) {$I-1$};
-	\draw ( 10.5 cm,2pt) -- ( 10.5 cm,-2pt) node[anchor=north] {$I-\hzi$};
-	\end{tikzpicture}
-	\caption{Notation of the one-dimensional mesh.}
-	\label{fig:mesh1D}
-\end{figure}
-
-The net and partial currents in the case of isotropic scattering are calculated using the following expressions derived from the integral neutron transport equation~\cite{Tomatis-2011,Tomatis-2019,Gross-2020}
-\begin{subequations}
-	\label{eq:par-curr-calc}
-	\begin{equation}
-	\label{eq:par-curr-calc-plus}
-	\begin{split}
-	\jp_{i+\hzi,g} &=  \frac{1}{2}
-	E_3[\mcL_g(x_{-\hzi},x_{i+\hzi})] \phi_{x_{-\hzi},g} \\
-	& + \frac{1}{2}\sum\limits_{j=0}^i \frac{q_{j,g}}{\sigma_{j,g}}
-	\left\{ E_3\left[ \mcL_g(x_{j+\hzi},x_{i+\hzi}) \right]
-	- E_3\left[ \mcL_g(x_{j-\hzi},x_{i+\hzi}) \right]
-	\right\}
-	\end{split}
-	\end{equation}
-	%
-	\begin{equation}
-	\begin{split}
-	\label{eq:par-curr-calc-minus}
-	\jm_{i+\hzi,g} &=  \frac{1}{2}
-	E_3[\mcL_g(x_{i+\hzi},x_{I-\hzi})] \phi_{x_{I-\hzi},g} \\
-	& + \frac{1}{2}\sum\limits_{j=i+1}^{I-1} \frac{q_{j,g}}{\sigma_{j,g}}
-	\left\{ E_3\left[ \mcL_g(x_{i+\hzi},x_{j-\hzi}) \right]
-	- E_3\left[ \mcL_g(x_{i+\hzi},x_{j+\hzi}) \right]
-	\right\},
-	\end{split}
-	\end{equation}
-	where $\mcL_g(x',x)\equiv \int_{x'}^{x} \sigma_g(x'')dx''$ is the optical length and the net current is $J _{i+\hzi,g} = \jp _{i+\hzi,g} - \jm _{i+\hzi,g}$, $\forall i$.
-Only the zeroth moment of the angular flux, that is the scalar flux after an expansion in angle on the spherical harmonics, is used at the boundary to include the contribution of possible incoming currents.
-\eqs{eq:par-curr-calc} are expected to yield more accurate estimates of the currents even when using a flux distribution obtained from diffusion theory.
-This is the main assumption of the Ronen Method.
-\end{subequations}
-% \daniele{In case additional space will be needed, it will be possible to write \eqs{eq:par-curr-calc} in a condensed form by using $\pm$.}
-
-% ------------------------------------------
-\subsection{CMFD IMPLEMENTATION}
-\label{sec:RM-CMFD}
-
-In classic CMFD implementation, the term $\delta J_{i+\hzi,g}$ is added to the diffusion current $\jD_{i+\hzi,g}$ in order to reproduce the net current $J_{i+\hzi,g}$.
-Currents are only computed on the surface elements of a coarse mesh in space to save memory and runtime \cite{Smith-1983}.
-Besides, the net current can be determined from some other expression which is physically or numerically more accurate.
-Therefore, this new term acts as a correction for the diffusion current.
-The diffusion current is generally approximated by finite differences according to
-\begin{equation}
-\label{eq:JD}
-\jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
-\frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
-\end{equation}
-where the diffusion coefficient at the interface is volume-averaged as
-\begin{equation}
-\label{eq:Ds}
-D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
-{\Delta_i + \Delta_{i+1}}.
-\end{equation}
-%
-About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
-In linearly anisotropic problems, the net current can also be considered to compute the source.
-Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
-The discretized form of the terms $\delta J_{i+\hzi,g}$ reproduce a centered drift-advection term to avoid possible indeterminate division by zeros in case of flat flux~\cite{Smith-1983,Tomatis-2011}:
-\begin{equation}
-\label{eq:dJ}
-\delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
-\frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
-J_{i+\hzi,g} - \jD_{i+\hzi,g},
-\end{equation}
-for $i = 0, \ldots, I-2$. The division by the spatial differences can be removed because the definition of $\delta D$ is arbitrary.
-
-Boundary conditions applies on the diffusion current as usual by means of an extrapolated length $\zeta$, $\zeta \jD \cong D \phi$.
-Mark or Marshak approximations, or other constants derived from transport theory can be used for $\zeta$ \cite{meghreblian1960reactor}.
-About the correction terms instead, it is simply $\delta J = -\delta D \phi$ with the boundary flux approximated at first order by the cell-averaged value.
-
-% ------------------------------------------
-\subsection{pCMFD IMPLEMENTATION}
-\label{sec:RM-pCMFD}
-
-The CMFD introduces in the numerical scheme a free parameter per cell surface through the correction term to adjust the diffusive solution locally.
-Since separate calculations of the partial currents are possible, two free parameters could be used in the discretized form of the diffusion equation.
-This idea leads to the development of the pCMFD scheme \cite{cho2003comparison}.
-
-Two corrective terms are then introduced: $J = \jp - \jm = \jD + \delta J^+ + \delta J^-$.
-An upwind definition with respect to the direction of flight of neutrons is used for the corrections~\cite{Jarrett-2016,Zhu-2016}:
-\begin{equation}
-\label{eq:CCF-sub}
-\delta \jp _{i+\hzi} = -\delta D^+ _{i+\hzi} \phi_i
-\quad \text{and} \quad
-\delta \jm _{i+\hzi} = -\delta D^- _{i+\hzi} \phi_{i+1}.
-\end{equation}
-The current by diffusion is distributed on the partial currents in equal parts in order to compute the new corrective coefficients $\delta D^{\pm}$,
-\begin{subequations}
-	\label{eq:delta-D-pCMFD}
-	\begin{align}
-	J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= -\delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
-	J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}
-	\end{align}
-\end{subequations}
-still for $i=0, \ldots, I-2$.
-The diffusion current is not halved at the boundary, using only \eq{eq:delta-D-pCMFDm} or \eq{eq:delta-D-pCMFDp} at the left and at the right boundaries, respectively.
-Finally, the implementation of CMFD can be upgraded to support the pCMFD scheme with minimal changes.
-% -----------------------------------------------------------------------------
-%
-% Daniele: the following proposition has shown to be inconsistent.
-%
-% Thanks to P$_1$ diffusion theory, the partial currents at any point $x$ of the slab are approximated as
-% \begin{equation}
-% \label{eq:partial-current}
-% \jpm(x) \cong \frac{\phi(x)}{4} \pm \frac{J (x)}{2},
-% \end{equation}
-% still verifying the expression for the net current $J = J^+ - J^-$.
-\eq{eq:partial-current} suggests introducing two different correction terms at each cell interface depending on the sign of the partial currents
-% \begin{equation}
-%   \label{eq:PCCF}
-%   \jpm _{i+\hzi} = \frac{1}{4} \phi_{i+\hzi} \pm \frac{1}{2}
-%     \left(\jD_{i+\hzi} + \delta \jpm_{i+\hzi}\right),
-% \end{equation}
-% and they must fulfill again the net current $J = \jD + (\delta \jp + \delta \jm)/2$. An upwind definition with the respect to the direction of flight of neutrons is~\cite{Jarrett-2016,Zhu-2016}
-% \begin{equation}
-% \label{eq:CCF-sub}
-% \delta \jp _{i+\hzi} = -2\delta D^+ _{i+\hzi} \phi_i
-% \quad \text{and} \quad
-% \delta \jm _{i+\hzi} = -2\delta D^- _{i+\hzi} \phi_{i+1}.
-% \end{equation}
-% %
-% Solving for the partial current correction factors gives
-% \begin{equation}
-%   \label{eq:ccfsss1}
-%   \delta D^+ _{i+\hzi} = \frac{\frac{1}{4}\phi_{i+\hzi}
-%   	+ \frac{1}{2}\jD _{i+\hzi} - \jp _{i+\hzi}}{\phi_i}
-%   \quad \text{and} \quad
-%   \delta D^- _{i+\hzi} = \frac{-\frac{1}{4}\phi_{i+\hzi}
-%   	+ \frac{1}{2}\jD _{i+\hzi} + \jm _{i+\hzi}}{\phi_{i+1}},
-%   \end{equation}
-% where the flux at the interface can be simply volume-averaged too, see~\eq{eq:Ds} for instance.
-% -----------------------------------------------------------------------------
-
-In a weakly absorbing medium and several mean free paths away from the boundary or a strong absorber, all correction factors $\delta D^\pm$ are expected to vanish and the net current must be fully reproduced by the diffusion current.
-Of course, this must be verified by the classic CMFD scheme too.
-
-% ------------------------------------------
-\section{RESULTS}
-\label{sec:res}
-
-% ------------------------------------------
-\section{CONCLUSIONS}
-\label{sec:conc}
-
-Present your summary and conclusions here.
-
-%\begin{figure}[!htb]
-%  \centering
-%  \includegraphics[scale=0.60]{./Figures/figure.pdf}
-%  \caption{SCALE/TRITON-NEWT Model of BWR Assembly in Order to Show and Example of a Figure and a Multi-line Caption}
-%  \label{fig:amdahl}
-%\end{figure}
-
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item Any number, text or symbol is in Times font and is not smaller than
-%  10-point after reduction to the actual window in your paper
-%\item That it can be translated into PDF
-%\end{itemize}
-
-%\begin{table}[!htb]
-%  \centering
-%  \caption{\bf Parallel Performance for the Sample Problem}
-%  \label{table:example}
-%  \begin{tabular}{|c|c|c|c|} \hline
-%   Number of & Wall-Clock & Speedup & Efficiency \\
-%   Processors & Time$^{a}$ (min) & (T$_{s}$/T$_{p}$) & (\%) \\ \hline
-%    \ 1 &  100.0 & \ ---    & ---  \\ \hline
-%    \ 2 &   52.6 & \ 1.9    & 95.0 \\ \hline
-%  \end{tabular}
-%\end{table}
-
-% ------------------------------------------
-% Daniele: I would avoid the following section about the nomenclature because of the 8 pages limit. The acronyms are already explained in the text.
-%\section*{NOMENCLATURE}
-%
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item RM - Ronen Method
-%\item CMFD - Coarse Mesh Finite Difference
-%\item pCMFD - partial current CMFD
-%\end{itemize}
-%
 % ------------------------------------------
@@
 % ------------------------------------------
-% You can enter a bibliography into the document using the following format, or use the
-% bibliography style file "physor.bst" found in the template directory.  You can use the bibliography style file
-% by replacing the current bibliography block with:
-\setlength{\baselineskip}{12pt}
-\bibliographystyle{physor}
+
+\bibliographystyle{elsarticle-harv}
 \bibliography{RM-bib}

### 2020-06-08 docs/ICTT2019/RMethod_ictt26.tex

@@
 \graphicspath{{figures/}}
+
+% The lineno packages adds line numbers. Start line numbering with
+% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it
+% on for the whole article with \linenumbers.
+\usepackage[modulo]{lineno}
+% \linenumbers
+% \modulolinenumbers[5]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \raggedright
+
+\linenumbers
 
@@
 Then, the solution by the Ronen method is sought iteratively as explained in section \ref{sec:impl}.
-Anderson acceleration through the DAAREM algorithm is also used during the iteration process \cite{henderson2019damped}, reducing considerably the number of iterations to achieve residuals on the relative flux differences below $10^{-6}$.
+Anderson acceleration through the DAAREM algorithm (Damped Anderson Acceleration with Epsilon Monotonicity) is also used during the iteration process \cite{henderson2019damped}, reducing considerably the number of iterations to achieve residuals on the relative flux differences below $10^{-6}$.
 Its use is crucial to find the fixed point solution throughout the non-linear iterations of the RM.

### 2020-06-08 docs/ANE2020/figures/Rahnema1997/Rahnema1997_ANE2020.py
Prepare the release of the public repo.

@@ -1,613 +1,0 @@
-#!/usr/bin/env python3
-'''
-Ploting bare slab heterogeneous case by Rahnema-1997 for the ANE2020 paper
-'''
-import os
-import numpy as np
-import matplotlib.pyplot as plt
-import sys
-from matplotlib import gridspec
-from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
-from matplotlib.ticker import FormatStrFormatter
-import matplotlib.ticker as mtick
-#from matplotlib.ticker import ScalarFormatter
-#class ScalarFormatterForceFormat(ScalarFormatter):
-#    def _set_format(self,vmin,vmax):  # Override function that finds format to use.
-#        self.format = "%1.2f"  # Give format here
-
-from matplotlib import rc
-sys.path.append('..')
-
-from cycler import cycler
-default_cycler = (cycler(color=['r', 'g', 'b', 'y']) *
-                  #cycler(marker=['.'])
-                  #*
-                  cycler(linestyle=['-', '--', ':', '-.']) 
-                  )
-
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-fsz = 24. # font size
-
-# ========== What would you like to plot? ==========
-# For heterogeneous case, consider upload several fluxes
-plot_flx      = False
-Plot_flx_cvg  = False
-Plot_dD       = False
-Plot_err      = False
-Plot_MAX_err  = False # Under development
-Plot_k        = False
-plot_flx_zoom = False
-Plot_dkeff    = False
-Plot_LB       = True
-I = 728 # No. of mesh points
-itr = 250 # No. of iterations
-
-# ------ Load flx_RM? ------
-plot_RM = True
-if plot_RM:
-    # Uploading CMFD results
-    path_RM_C1 = "kflx_Rahnema1997_CMFD_C1_LBC0RBC0_I728_itr250.npy"
-    path_RM_C2 = "kflx_Rahnema1997_CMFD_C2_LBC0RBC0_I728_itr250.npy"
-    path_RM_C3 = "kflx_Rahnema1997_CMFD_C3_LBC0RBC0_I728_itr250.npy"
[…]

### 2020-06-08 docs/ANE2020/figures/Tomatis2011/Tomatis2011_ANE2020.py

@@ -1,520 +1,0 @@
-#!/usr/bin/env python3
-
-import os
-import numpy as np
-import matplotlib.pyplot as plt
-import sys
-from matplotlib import gridspec
-from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
-from matplotlib.ticker import FormatStrFormatter
-import matplotlib.ticker as mtick
-#from matplotlib.ticker import ScalarFormatter
-#class ScalarFormatterForceFormat(ScalarFormatter):
-#    def _set_format(self,vmin,vmax):  # Override function that finds format to use.
-#        self.format = "%1.2f"  # Give format here
-
-from matplotlib import rc
-sys.path.append('..')
-
-from cycler import cycler
-default_cycler = (cycler(color=['r', 'g', 'b', 'y']) *
-                  #cycler(marker=['.'])
-                  #*
-                  cycler(linestyle=['-', '--', ':', '-.']) 
-                  )
-
-rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
-rc('text', usetex=True)
-fsz = 24. # font size
-
-# ========== What would you like to plot? ==========
-# For heterogeneous case, consider upload several fluxes
-plot_flx      = False
-Plot_flx_cvg  = False
-Plot_dD       = False
-Plot_err      = False
-Plot_MAX_err  = False # Under development
-Plot_k        = False
-plot_flx_zoom = False
-Plot_rho      = False
-Plot_LB       = False
-I = 400 # No. of mesh points
-#dx = 21.5/I
-itr = 250 # No. of iterations
-#ccng = 3 # Core configuration (Rahnema1997)
-# ------ Load flx_RM? ------
-plot_RM = True
-if plot_RM:
-    ''' Upload one file '''
-    path_RM_flx_file1 = "kflx_Tomatis2011_CMFD_LBC0RBC0_I400_it250.npy"
-    path_RM_flx_file2 = "kflx_Tomatis2011_pCMFD_LBC0RBC0_I400_it250.npy"
-    #path_RM_flx_file3 = "../../../FD1dMGdiff/output/kflx_MC2011_LBC0RBC0_I400_it10.npy"
-        #data = np.load(path_RM_flx_file)
-    k_RM1, flx_RM1, xi1, st, dD1 = np.load(path_RM_flx_file1,allow_pickle=True)
[…]

### 2020-06-08 docs/ICTT2019/scripts/analyze_results.py

@@ -1,326 +1,0 @@
-#!/usr/bin/env python3
-# --*-- coding:utf-8 --*--
-"""
-Analyze the results of the 1g homogeneous test cases by Sood et al. [Sood2003]_.
-
-.. [Sood2003] Sood, A., Forster, R. A., & Parsons, D. K. (2003). Analytical
-              benchmark test set for criticality code verification. Progress
-              in Nuclear Energy, 42(1), 55-106.
-"""
-import sys, os
-import itertools
-import numpy as np
-from scipy import interpolate
-
-import matplotlib.pyplot as plt
-
-rootdir = os.path.join(os.getcwd(), "..", "..", "..")
-cpmdir = os.path.join(rootdir, "CPM1D", "tests", "output")
-rmtdir = os.path.join(rootdir, "FD1dMGdiff", "tests", "output")
-figdir = os.path.join("..", "figures")
-
-sys.path.insert(0, os.path.join("..", "..", "..", "FD1dMGdiff"))
-from data.SoodPNE2003 import *
-from GeoMatTools import *
-
-# plt.rcParams.update({'font.size': 14})
-# SMALL_SIZE = 8
-# MEDIUM_SIZE = 10
-# BIGGER_SIZE = 12
-
-# plt.rc('font', size=SMALL_SIZE)          # controls default text sizes
-# plt.rc('axes', titlesize=SMALL_SIZE)     # fontsize of the axes title
-# plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
-# plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
-# plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
-# plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
-# plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
-
-linestyle_str = [
-     ('solid', 'solid'),      # Same as (0, ()) or '-'
-     ('dotted', 'dotted'),    # Same as (0, (1, 1)) or '.'
-     ('dashed', 'dashed'),    # Same as '--'
-     ('dashdot', 'dashdot')]  # Same as '-.'
-
-linestyle_tuple = [
-     ('loosely dotted',        (0, (1, 10))),
-     ('dotted',                (0, (1, 1))),
[…]

### 2020-07-15 docs/ANE2020/contents.tex
light changes to compile the tex files by texlive2020

@@
 About the RM, more accurate estimates of the net current come from the integral expressions of \eqs{eq:par-curr-calc}, still using the scalar flux in the emission source $q_{i,g}$.
-% In linearly anisotropic problems, the net current can also be considered to compute the source.
-<-- pure bullshit !
-Can't happen in diffusion.
+In linearly anisotropic problems, the net current can also be considered to compute the source.
+
 Once the diffusion currents and the net currents by integral transport are calculated using the most recent flux values, the correction terms can be obtained on the cell interfaces.
@@
     J^+_{i+\hzi} - \frac{1}{2}\jD_{i+\hzi} &= -\delta D^+_{i+\hzi} \phi_i, \label{eq:delta-D-pCMFDp}\\
-    J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm} \\
-    J^\pm_{i+\hzi} = \pm \frac{1}{2}\jD_{i+\hzi}& \mp \delta D^{\pm} _{i+\hzi} \phi_{i+(1\mp 1)/2}\label{eq:delta-D-pCMFDpm} \,\,,
+    J^-_{i+\hzi} + \frac{1}{2}\jD_{i+\hzi} &= +\delta D^-_{i+\hzi} \phi_{i+1}, \label{eq:delta-D-pCMFDm}\\
+    J^\pm_{i+\hzi} = \pm \frac{1}{2}\jD_{i+\hzi}& \mp \delta D^{\pm} _{i+\hzi} \phi_{i+(1\mp 1)/2}\label{eq:delta-D-pCMFDpm},
   \end{align}
@@
 	\centering
-	\caption{Two-group macroscopic cross sections [cm\tsup{-1}] of the homogeneous case~\cite{Tomatis-2011}.}
+	\caption{Two-group macroscopic cross sections [cm$^{-1}$] of the homogeneous case~\cite{Tomatis-2011}.}
 	\label{tab:xs_hom}
 	\begin{tabular}{cccccc}
-		%\midrule
-		Group $g$ &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\ 
-		\midrule
-		1 & 5.3115$\times$10\tsup{-1} & 5.04664$\times$10\tsup{-1} & 2.03884$\times$10\tsup{-3} & 1 & 7.15848$\times$10\tsup{-3} \\
-		%\midrule
-		2 & 1.30058$\times$10\tsup{0}& 1.62955$\times$10\tsup{-2} & 1.19134$\times$10\tsup{0}	& 0 & 1.41284$\times$10\tsup{-1} \\
-		%\midrule
+		Group $g$ &  $\sigma_{g}$ & \multicolumn{2}{c}{$\sigma_{s,0,g\leftarrow g'}$} & $\chi_g$ & $\nu\sigma_{f,g}$ \\[3mm]
+		1 & 5.3115$\times$10$^{-1}$ & 5.04664$\times$10$^{-1}$ & 2.03884$\times$10$^{-3}$ & 1 & 7.15848$\times$10$^{-3}$ \\
+		2 & 1.30058$\times$10$^{0}$& 1.62955$\times$10$^{-2}$ & 1.19134$\times$10$^{0}$	& 0 & 1.41284$\times$10$^{-1}$ \\
 	\end{tabular}

### 2020-07-15 FD1dMGdiff/FDsDiff1D.py
fix RM its by the recalculation of the diffusion coefficient, that is without the additional corrective terms of the CMFD scheme.

@@ -845,8 +845,11 @@ def compute_D(Di, flx, pJ, BC=(0, 0), zero=1.e-6, chk=False):
     J, mflx_diff = Jp - Jm, flx[:, :-1] - flx[:, 1:]
     if J.size != G * (I + 1):
         raise ValueError('Unexpected size of input current.')
-    Db = np.array(J[:,1:-1], copy=True)
-    Db *= np.tile(Di[1:] + Di[:-1], G).reshape(G, I-1) / 2.
+    # the following two lines are simplified right next
+    # Db = np.array(J[:,1:-1], copy=True)
+    # Db *= np.tile(Di[1:] + Di[:-1], G).reshape(G, I-1) / 2.
+    # multiplication occurs always on last index, so:
+    Db = J[:,1:-1] * (Di[1:] + Di[:-1]) / 2
     # Because of the flux-limiting principle, the current must go to
     # zero faster than the flux. This may not happen in simple
     # diffusion. In this case, a division by zero will occur here.
@@ -860,8 +863,8 @@ def compute_D(Di, flx, pJ, BC=(0, 0), zero=1.e-6, chk=False):
     #: JL = -Db[:,  0] * flx[:, 0] / (0.5 * Di[ 0] + zetal * Db[:, 0])
     #: JR =  Db[:, -1] * flx[:,-1] / (0.5 * Di[-1] + zetar * Db[:,-1])
     a, b = J[:, 0] / flx[:, 0], J[:,-1] / flx[:,-1]
-    DbL = - a * 0.5 * Di[0] / (1. + a * zetal)
-    DbR = b * 0.5 * Di[-1] / (1. - b * zetar)
+    DbL, DbR = - a * 0.5 * Di[ 0] / (1. + a * zetal), \
+                 b * 0.5 * Di[-1] / (1. - b * zetar)
     if LBC == 2: DbL.fill(0.)  # but any value would be fine
     if RBC == 2: DbR.fill(0.)  # ...same as above
     Db = np.insert(Db, 0, DbL, axis=1)
@@ -1093,9 +1096,7 @@ def solve_RMits(data, xs, flx, k, slvr_opts, filename=None):
             # compute the corrective delta-diffusion-coefficients
             dD = compute_delta_D(flxd, J_diff, pJ_tran, slvr_opts.pCMFD)
         else:
-            # print('before',Db)
-            Db, dD = compute_D(Di, flx, pJ_tran, BC), None
-            # print('after', Db)
[…]

### 2020-07-16 FD1dMGdiff/data/Sood2003_heterSlab1G_P30_data.py
Sood 2003 1G test and data
Homogeneous and heterogeneous test cases from Sood 2003.
All tests are critical.
Two files contain several test cases. Choosing which problem to solve done by setting the desired value of the parameter P (Problem).
Please see the text at the begining of the test files.

@@ -1,0 +1,66 @@
+# --*-- coding:utf-8 --*--
+"""
+Multigroup xs for the Heterogeneous 1G problem Sood-2003.
+
+.. note:: remind that the scattering moments are already multiplied by the
+   coefficients of Lagrange polynomials if data are produced by APOLLO.
+   
+
+                        Problem 30 - UD2O-H2O(10)-1-0-SL
+                             Symmetrical 3 regions
+
+
+..[Sood2003] Analytical Benchmark Test Set For Criticality code Verification,
+    Los Alamos National Laboratory, Applied Physics (X) Divisions, X-5 Diagnostics
+    Applications Groupm P.O. Box 1663, MS F663, Los Alamos, NM 87545,
+    Avneet Sood, R. Arthur Foster, and D. Kent Parsons, 2003
+"""
+
+import numpy as np
+import logging as lg
+
+one_third = 1. / 3.
+
+# Na
+stNa = np.array([0.086368032])
+ssNa = np.array([0.086368032])
+sfNa = np.array([0.])
+nuNa = np.array([0.])
+chiNa = np.array([0.])
+
+# Clad
+stc = np.array([0.23256])
+ssc = np.array([0.23209488])
+sfc = np.array([0.])
+nuc = np.array([0.])
+chic = np.array([0.])
+
+# Fuel
+stf = np.array([0.407407])
+ssf = np.array([0.328042])
+sff = np.array([0.06922744])
+nuf = 2.5
+chif = np.array([1])
+
+# definition of the diff coefficient
+DNa = one_third / (stNa)
+Dc = one_third / (stc)
+Df = one_third / (stf)
+
+
+G = 1  # nb of energy groups
+
+if __name__ == "__main__":
+
+    lg.info("*** Check homogeneous cross sections data ***")
+
+    flx_inf = np.dot(np.linalg.inv(np.diag(st) - ss0), chi)
+    kinf = np.dot(nsf, flx_inf)
+    # np.testing.assert_almost_equal(kinf, 1.1913539017168697, decimal=7,
+    #     err_msg="kinf not verified.")
+    np.testing.assert_almost_equal(kinf, 1.0783813599102687, decimal=7,
+        err_msg="kinf not verified.")  # M&C article
+    # np.testing.assert_allclose(flx_inf, [39.10711218,  5.85183328],
+    #     err_msg="fundamental flx_inf not verified.")
[…]

### 2020-07-16 FD1dMGdiff/data/Sood2003_heterSlab1G_P3_data.py

@@ -1,0 +1,59 @@
+# --*-- coding:utf-8 --*--
+"""
+Multigroup xs for the Heterogeneous 1G problem Sood-2003.
+
+.. note:: remind that the scattering moments are already multiplied by the
+   coefficients of Lagrange polynomials if data are produced by APOLLO.
+   
+
+                        Problem 3 - PUa-H2O(1)-1-0-SL
+                           Non-symmetrical 2 region
+
+
+..[Sood2003] Analytical Benchmark Test Set For Criticality code Verification,
+    Los Alamos National Laboratory, Applied Physics (X) Divisions, X-5 Diagnostics
+    Applications Groupm P.O. Box 1663, MS F663, Los Alamos, NM 87545,
+    Avneet Sood, R. Arthur Foster, and D. Kent Parsons, 2003
+"""
+
+import numpy as np
+import logging as lg
+
+one_third = 1. / 3.
+
+# Water
+stw = np.array([0.3264])
+ssw = np.array([0.29376])
+sfw = np.array([0.])
+nuw = np.array([0.])
+chiw = np.array([0.])
+
+# Fuel PUa
+# Fuel
+stf = np.array([0.3264])
+ssf = np.array([0.225216])
+sff = np.array([0.081600])
+nuf = 3.24 
+chif = np.array([1])
+
+# definition of the diff coefficient
+Dw = one_third / (stw)
+Df = one_third / (stf)
+
+
+G = 1  # nb of energy groups
+
+if __name__ == "__main__":
+
+    lg.info("*** Check homogeneous cross sections data ***")
+
+    flx_inf = np.dot(np.linalg.inv(np.diag(st) - ss0), chi)
+    kinf = np.dot(nsf, flx_inf)
+    # np.testing.assert_almost_equal(kinf, 1.1913539017168697, decimal=7,
+    #     err_msg="kinf not verified.")
+    np.testing.assert_almost_equal(kinf, 1.0783813599102687, decimal=7,
+        err_msg="kinf not verified.")  # M&C article
+    # np.testing.assert_allclose(flx_inf, [39.10711218,  5.85183328],
+    #     err_msg="fundamental flx_inf not verified.")
+    np.testing.assert_allclose(flx_inf, [38.194379,  5.697515],
+        err_msg="fundamental flx_inf not verified.")  # M&C article

### 2020-07-16 FD1dMGdiff/data/Sood2003_homogSlab1G_data.py

@@ -1,0 +1,66 @@
+# --*-- coding:utf-8 --*--
+"""
+Homogeneous xs for the homogeneous 1G problem [Sood2003].
+
+
+                        Problem 2  - PUa-1-0-SL
+                        Problem 6  - PUb-1-0-SL
+                        Problem 12 - Ua-1-0-SL
+                        Problem 22 - UD2O-1-0-SL 
+                        
+            Cross section strucre [P2, P6, P12, P22], (P=problem)
+                        
+Analytical Benchmark Test Set For Criticality code Verification,
+Los Alamos National Laboratory, Applied Physics (X) Divisions, X-5 Diagnostics
+Applications Groupm P.O. Box 1663, MS F663, Los Alamos, NM 87545,
+Avneet Sood, R. Arthur Foster, and D. Kent Parsons, 2003
+
+
+"""
+
+import numpy as np
+import logging as lg
+
+one_third = 1. / 3.
+problem_for_txt = [2,6,12,22]
+# Fuel
+st = np.array([0.3264, 0.3264, 0.3264, 0.54628])
+ss = np.array([0.225216, 0.225216, 0.248064, 0.464338])
+sf = np.array([0.0816, 0.0816, 0.06528, 0.054628])
+nu = np.array([3.24, 2.84, 2.7, 1.7])
+chi = np.array([1.0, 1.0, 1.0, 1.0])
+
+# definition of the (P1) diff coefficient
+D = one_third / (st)
+G = 1  # nb of energy groups
+
+# Critical radius
+rc_cm = np.array([1.853722, 2.256751, 2.872934, 10.371065])          # Units of [cm]
+rc_mfp = np.array([0.605055, 0.73660355, 0.93772556,5.6655054562])   # Units of mean free path (mfp)
+
+
+
+def calc_flx_inf(st, ss, chi):
+    return nu*sf/(st-ss)
+
+
+def calc_kinf(nsf, st=None, ss=None, chi=None, flx_inf=None):
+    if flx_inf is None:
+        flx_inf = calc_flx_inf(st, ss, chi)
+    return np.dot(nsf, flx_inf)
+
+
+if __name__ == "__main__":
+
+    lg.info("*** Check homogeneous cross sections data ***")
+
+    flx_inf = calc_flx_inf(st, ss)
+    kinf = calc_kinf(nsf, flx_inf=flx_inf)
+    # np.testing.assert_almost_equal(kinf, 1.1913539017168697, decimal=7,
[…]

### 2020-07-16 FD1dMGdiff/tests/Sood2003_HeterSlab1G_test.py

@@ -1,0 +1,167 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This test case runs the 1G heterogeneous slab problem from [Sood2003]_.
+   
+
+                       Index - 0 = Problem 4  - PUa-1-0-SL
+                       Index - 1 = Problem 25 - UD2O-H2O(1)-1-0-SL
+                       Index - 2 = Problem 26 - UD2O-H2O(10)-1-0-SL
+                        
+                       Cross section strucre [P4, P25, P26], (P=problem)
+            
+..[Sood2003] Analytical Benchmark Test Set For Criticality code Verification,
+    Los Alamos National Laboratory, Applied Physics (X) Divisions, X-5 Diagnostics
+    Applications Groupm P.O. Box 1663, MS F663, Los Alamos, NM 87545,
+    Avneet Sood, R. Arthur Foster, and D. Kent Parsons, 2003
+
+"""
+import sys
+sys.path.append('..')
+from data.Sood2003_heterSlab1G_data import *
+from FDsDiff1D import input_data
+import numpy as np
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
+
+def get_fa(faid, ifa, L, nz=3):
+   '''Returns a list of lists of FA id materials in location ifa in core.
+   ifa = 0, 1, 2, ..., nfa-1.'''
+
+   i = ifa * nz + 1
+   if faid == 1:
+           media = [
+               ['WATER', L[i]],
+               ['FUEL', L[i+1]],
+               ['WATER', L[i+2]],
+               ]
+   else:
+      raise TypeError('Invalid FA number [1-4].')
+
+   return media
+
+
+########################################
+'''
+Problem to solve? Insert index number from 0 to 2:
+'''
+P = 2                      # Problem index to solve
+P_txt = problem_for_txt[P] # Problem No. according to benchmark
+
+########################################
+if (P < 0) or (P > 2):
+    raise TypeError('Invalid test case. Choose between no. [0-2].')
+
+
+# definition of the spatial mesh
+
+
+rcf_cm = rcf_cm[P]   # critical length of half fuel region [cm]
[…]

### 2020-07-16 FD1dMGdiff/tests/Sood2003_homogSlab1G_test.py

@@ -1,0 +1,127 @@
+#!/usr/bin/env python3
+# --*-- coding:utf-8 --*--
+"""
+This test case runs the 1G homogeneous slab problem from [Sood2003]_.
+
+
+                       Index - 0 = Problem 2  - PUa-1-0-SL
+                       Index - 1 = Problem 6  - PUb-1-0-SL
+                       Index - 2 = Problem 12 - Ua-1-0-SL
+                       Index - 3 = Problem 22 - UD2O-1-0-SL 
+                        
+            Cross section strucre [P2, P6, P12, P22], (P=problem)
+                        
+            
+.. [Sood2003] Sood, A., Forster, R. A., & Parsons, D. K. (2003). Analytical
+              benchmark test set for criticality code verification. Progress
+              in Nuclear Energy, 42(1), 55-106.
+"""
+
+import sys
+sys.path.append('..')
+from data.Sood2003_homogSlab1G_data import *
+
+from FDsDiff1D import input_data
+import numpy as np
+
+def MyWho():
+     print([v for v in globals().keys() if not v.startswith('_')])
+
+########################################
+'''
+Problem to solve? Insert index number from 0 to 3:
+'''
+P = 1               # Problem index to solve
+P_txt = problem_for_txt[P] # Problem No. according to benchmark
+########################################
+
+if (P < 0) or (P > 3):
+    raise TypeError('Invalid test case. Choose between no. [1-3].')
+
+
+# How many mfp? - No, of r_c:
+irc = 1
+
+# definition of the spatial mesh
+# rc is the length from slab's center to edge |   :-->|
+rc_cm = rc_cm[P] # Critical length [cm]
+rc_mfp = rc_mfp[P] # Critical length [cm]
+
+L = irc*2*rc_cm # Slab's length
+
+I = 30  # nb of spatial cells
+xi = np.linspace(0, L, I+1)  # equidistant mesh
+
+geometry_type = 'slab'
+
+# ------------------------------------------------ #
+#change c?
+c = False
+if c == True:
+        
+    # test the CMFD scheme with different material conditions
+    sd = lambda ss: ss
+    sa = lambda st, ss: st - sd(ss)
+    def check_c(ss, st):
+        s = sd(ss)
+        print('sd = ', s)
[…]

### 2020-09-04 docs/MC2021/Abstract/Gross_mc2021-V2.tex
Draft for extended abstract M&C 2021

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  This is a sample LaTeX input file for your contribution to 
%  the M&C2021 topical meeting.
%
%  Please use it as a template for your full paper 
%    Accompanying/related file(s) include: 
%       1. Document class/format file: mc2021.cls
%       2. Sample PDF/Postscript Figure: figure.pdf,figure.ps
%       3. A PDF file showing the desired appearance: mc2021_template.pdf
%       4. cites.sty and citesort.sty that might be needed by some users 
%    Direct questions about these files to: brantley1@llnl.gov
%
%    Notes: 
%      (1) You can use the "dvips" utility to convert .dvi 
%          files to PostScript.  Then, use either Acrobat 
%          Distiller or "ps2pdf" to convert to PDF format. 
%      (2) Different versions of LaTeX have been observed to 
%          shift the page down, causing improper margins.
%          If this occurs, adjust the "topmargin" value in the
%          mc2021.cls file to achieve the proper margins. 
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{mc2021}
%
%  various packages that you may wish to activate for usage 
\usepackage{tabls}
\usepackage{cites}
\usepackage{epsf}
\usepackage{appendix}
\usepackage{ragged2e}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\usepackage{caption}
\captionsetup{width=1.0\textwidth,font={bf,normalsize},skip=0.3cm,within=none,justification=centering}
\usepackage{bm}
\usepackage{xfrac}
\usepackage{multirow}

%\usepackage[justification=centering]{caption}

%
% Define title...
%
\title{COMPREHENSIVE BENCHMARK OF THE RONEN METHOD\\IN ONE-DIMENSIONAL PLAIN GEOMETRY}
%
% ...and authors
%
\author{%
  % FIRST AUTHORS 
  %
  \textbf{Roy Gross$^1$, Daniele Tomatis$^2$, and Erez Gilad$^1$}\footnote{Corresponding author: Erez Gilad (gilade@bgu.ac.il)} \\
  $^1$The Unit of Nuclear Engineering, Ben-Gurion University of the Negev\\ Beer-Sheva 8410501, Israel\\
\\
  $^2$DES, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA)\\
  CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\ 
\\
  \url{roygros@post.bgu.ac.il}, \url{daniele.tomatis@cea.fr}, \url{gilade@bgu.ac.il}
}
%
% Insert authors' names and short version of title in lines below
%
\newcommand{\authorHead}{Roy Gross, Daniele Tomatis, Erez Gilad}
\newcommand{\shortTitle}{Comprehensive benchmark of the Ronen Method}

\newcommand{\tsup}[1]{\textsuperscript{#1}}
\newcommand{\tsub}[1]{\textsubscript{#1}}
\newcommand{\rr}{\bm{r}}
\newcommand{\rE}{\ensuremath{(\rr,E)}}
\newcommand{\bnabla}{\ensuremath{\bm{\nabla}}}
\newcommand{\hzi}{\ensuremath{\sfrac{1}{2}}}
\newcommand{\jD}{\ensuremath{J^{\textrm{\scriptsize{D}}}}}
\newcommand{\jp}{\ensuremath{J^+}}
\newcommand{\jm}{\ensuremath{J^-}}
\newcommand{\keff}{\ensuremath{k_{\textrm{\scriptsize{eff}}}}}

\newcommand{\kref}{\ensuremath{k_{\textrm{\scriptsize{ref}}}}}
\newcommand{\kd}{\ensuremath{k_{\textrm{\scriptsize{D}}}}}
\newcommand{\krm}{\ensuremath{k_{\textrm{\scriptsize{RM}}}}}
\newcommand{\kinf}{\ensuremath{k_{\textrm{\scriptsize{$\infty$}}}}}
\newcommand{\rcref}{\ensuremath{r_{\textrm{\scriptsize{c,ref}}}}}
\newcommand{\rc}{\ensuremath{r_{\textrm{\scriptsize{c}}}}}
\newcommand{\phiref}{\ensuremath{\phi_{\textrm{\scriptsize{ref}}}}}
\newcommand{\phirm}{\ensuremath{\phi_{\textrm{\scriptsize{RM}}}}}

\graphicspath{ {./figures/} }
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   BEGIN DOCUMENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\justify

\begin{abstract}
  A comprehensive benchmark is performed for the CMFD and pCMFD implementations of the Ronen method in one-dimensional slab geometry. The CMFD/pCMFD implementations are validated against analytic solutions of homogeneous and heterogeneous configurations using one, two, and three energy groups. The validation is performed for the criticality eigenvalue and in some cases also for the spatial distribution of the neutron flux. The scattering is assumed to be isotropic in all cases. The results indicate that the CMFD/pCMFD implementations of the Ronen method achieve high accuracy in this set of problems. The maximal deviation in criticality is less than 20 pcm, and the maximal deviation in the spatial distribution of the flux is less than 2\% and is located on the boundary.  
\end{abstract}
\keywords{Ronen method; Integral transport, CMFD, pCMPFD; Neutron diffusion}

\section{INTRODUCTION} 
\label{sec:intro}

Full core neutron transport calculations are a demanding task and often faster multigroup neutron diffusion solvers are used. However, the diffusion approximation is invalidated near strong absorbing materials, interfaces, and boundaries, where strong gradients appear or in case anisotropic scattering is pronounced.

\vspace{-1.5mm}

The Ronen method (RM) is designed to overcome the inaccuracies of the diffusion approximation by correcting the diffusion currents, using the integral transport theory~\cite{Tomatis-2011,Gross-2020,Tomatis-2020}. The underlying hypothesis of the Ronen method is the modification of the current such that the neutron current approximated by Fick's law, $\bm{J}^D\rE$, will approach the accurate one, calculated by transport theory $\bm{J}\rE$, with the addition of a correction current $\delta\bm{J}\rE$,
\begin{align}
\label{eq:Fick}
& \bm{J}\rE \cong \bm{J}^D\rE + \delta\bm{J}\rE \\ 
& \bm{J}^D\rE = -D\rE\bnabla\phi\rE  \,\,.
\end{align}
Ronen also suggested an iterative update of the diffusion coefficients ($k$ is the iteration index) ~\cite{Ronen-2004},
\begin{equation}
\label{eq:RM-it}
D^{(k+1)}\rE = \left. - \lvert \bm{J}^{(k)}\rE \rvert \middle/ \lvert \bnabla \phi^{(k)}\rE \rvert. \right.
\end{equation}

\vspace{-10.5mm}

The Ronen method was implemented numerically using the Coarse Mesh Finite Difference (CMFD) scheme in the diffusion solver and employing correction factors the for leakage terms in the balance equation~\cite{Tomatis-2011}. The current correction factors were derived from the correction currents, which were estimated by the integral transport theory~\cite{Gross-2020}. This implementation eliminated the divergence problem in Eq.~\eqref{eq:RM-it} for small flux gradients and accurately reproduced the criticality eigenvalue and the associated eigenflux calculated by a reference discrete ordinates code.

\vspace{-1.5mm}

In this study, the Ronen method is implemented using a variant of the CMFD method, i.e., the partial-currents CMFD (pCMFD)~\cite{Cho-2003}. In a sense, the pCMFD is a more natural choice of the Ronen method scheme, since the implementation of pCMFD can be naturally formulated in terms of partial currents. The performances of both implementations, CMFD and pCMFD, are thoroughly evaluated against an analytic benchmarks for the criticality eigenvalue and the spatial distribution of the associated critical eigenflux~\cite{Sood2003}.

\section{NUMERICAL IMPLEMENTATION OF THE RONEN METHOD} 
\label{sec:num-imp}

The neutron balance in the $i$\tsup{th} cell of a one-dimensional mesh is
\begin{equation}
\label{eq:balance}
J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
\end{equation}
where $J$ is the net current at the cell's interfaces, $\sigma$ is the total cross-section, and the subscript $g$ denotes the energy group. The isotropic (scattering and fission) source term is denoted by $q$.

\vspace{-1.5mm}

\subsection{Formulation of the CMFD Scheme} 
\label{sec:cmfd}

In order to obtain a more accurate net current $J_{i+\hzi,g}$, a correction term $\delta J_{i+\hzi,g}$ is added to the diffusion-approximated current $\jD_{i+\hzi,g}$, which is is evaluated by a discretization of Fick's law, 
\begin{equation}
\label{eq:JD}
\jD_{i+\hzi,g} \cong - D_{i+\hzi,g}
\frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
\quad \text{where }
D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
{\Delta_i + \Delta_{i+1}}.
\end{equation}

\vspace{-1.5mm}

The integral expressions for the net current is used with the scalar flux in the emission source to obtain a more accurate estimation of the net current. In the Ronen method implementation, the correction terms $\delta J$ are obtained  iteratively as the difference between the net current $J$ and the diffusion-approximated current $\jD$, 
\begin{equation}
\label{eq:dJ}
\delta J_{i+\hzi,g} = -\delta D_{i+\hzi,g}
\frac{\phi_{i+1,g} + \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2} =
J_{i+\hzi,g} - \jD_{i+\hzi,g},
\end{equation}
where discretized form of the correction term $\delta J_{i+\hzi,g}$ is the centered drift-advection term to avoid divergence due to small flux gradients~\cite{Tomatis-2011,Smith-1983}.

\vspace{-1.5mm}

\subsection{Formulation of the pCMFD Scheme} 
\label{sec:pcmfd}

In the pCMFD implementation~\cite{Cho-2003}, two correction terms are introduced per interface, consistent with the partition of the net current into two partial ones, i.e., $J = \jp - \jm = \jD + \delta J^+ + \delta J^-$, defined by $\delta \jp _{i+\hzi} = -\delta D^+ _{i+\hzi} \phi_i$ and $\delta \jm _{i+\hzi} = -\delta D^- _{i+\hzi} \phi_{i+1}$~\cite{Jarrett-2016,Zhu-2016}. By equally distributing the diffusion-approximated current on the partial currents, the relations between the net current, the diffusion-approximated currents and the correction terms are given by
\begin{equation}
\label{eq:delta-D-pCMFD}
\pm \delta D^{\pm} _{i+\hzi} \phi_{i+(1\mp 1)/2} = 
- J^\pm_{i+\hzi} \pm \frac{1}{2}\jD_{i+\hzi} .
\end{equation}

\vspace{-5.5mm}

%\begin{figure}[!htb]
%  \centering
%  \includegraphics[scale=0.46]{./Figures/MCD-poster-2016}
%  \caption{The Mathematics and Computation Division of the American Nuclear Society}
%  \label{fig:mcd}
%\end{figure}

\section{RESULTS}

The analytic benchmark of Sood et al. (2003)~\cite{Sood2003} presents one-dimensional homogeneous and heterogeneous critical configurations, including the associated one-, two-, and three-group cross-sections. For some problems, the spatial distribution of the flux is given at certain points. 
%
The deviations between the criticality eigenvalues, calculated using the CMFD and pCMFD implementations of the Ronen method ($\krm$, and $\kd$ for pure diffusion), and the reference eigenvalue ($\kref=1$) are shown in Table~\ref{table:res1} for a selected set of problems. The deviations are shown in both units of reactivity ($\Delta\rho = \left(\sfrac{1}{\kref}- \sfrac{1}{\kd,\krm}\right)\times 10^5$ [pcm]), and in relative error in the critical width ($\Delta w = \text{abs}\left[ \sfrac{ \left( \rc-\rcref\right)}{\rcref}\times 100\right]$ [\%]), where $r$ is the critical dimension, i.e., the distance from the fuel's center to one of the boundaries. The number of cells within the water region is $I_w$.
%
The deviations between the CMFD normalized flux and the reference analytic solutions,  $\Delta\phi = \left[\sfrac{\left(\phirm - \phiref\right)}{\phiref}\right]\times 100$ [\%], are shown in Table~\ref{table:res2} for a selected set of problems. 
%
\begin{table}[!htb]
	\vspace{-7.5mm}	
	\centering
	\small
	\caption{\bf Deviations of the eigenvalues \keff \ calculated by the RM from criticality.}
	\label{table:res1} 
  \begin{tabular}{|l|l|c|c|c|c|c|} \hline 
	\multirow{2}{*}{Problem ID} & \multirow{2}{*}{Method} & \multicolumn{4}{c|}{$\Delta\rho$ [pcm], ($\Delta w$ [\%])} & \multirow{2}{*}{Comments} \\ 
	\cline{3-6}
	&  	 & $I_1 = 50$   & $I_2 = 100$ & $I_3 = 150$ & $I_4 = 200$    & \\ 
	\hline
	\multirow{3}{*}{PUa-1-0-SL} 		 & Diffusion  & -12,099,(-)  & -12,108,(-) & -12,109,(-) &-12,110,(-)   & \multirow{2}{*}{}\\ 
	\cline{2-6}
	& RM-CMFD  & -10, (0.016) & -3, (0.005) & -1, (0.002) & 0, (0.002)      & \multirow{2}{*}{}\\ 
	\cline{2-6}
	& RM-pCMFD & -10, (0.016) & -3, (0.005) & -1, (0.002) & -1, (0.0) & \\ 
	\hline
	\multirow{3}{*}{Ua-1-0-SL} 		     & Diffusion  & -7,541, (-)  & -7,550, (-) & -7,552, (-)  & -7553, (-)  & \multirow{2}{*}{}\\ 
	\cline{2-6}
	& RM-CMFD  & -19, (0.027)  & -5, (0.006) & -2, (0.002)  & -1, (0.0)  & \multirow{2}{*}{}\\ 
	\cline{2-6}
	& RM-pCMFD & -19, (0.027)  & -5, (0.006) & -2, (0.002)  & -1, (0.0)	  & \\ 
	\hline
	\multirow{2}{*}{PUa-H2O(0.5)-1-0-SL} & Diffusion  & -15,921, (-) & -15,927, (-) & -15,928, (-) & -15,928, (-) & \multirow{2}{*}{$I_w = 0.5\times I_f$} \\ 
	\cline{2-6}
	& RM-CMFD  & -8, (0.011)  & -3, (0.005) & -3, (0.001)	& -1, (0.001) &  \\ 
	\cline{2-6}
	& RM-pCMFD &-8, (0.011)	& -3, (0.005) & -1, (0.001)	& -1, (0.001) & \\ 
	\hline
\end{tabular}
\end{table}
%
\begin{table}[!htb]
	\vspace{-5.5mm}
	\centering
	\small
	\caption{\bf Deviations of the normalized flux calculated by the RM from the analytic solution.}
	\label{table:res2} 
	\begin{tabular}{|c|c|c|c|c|c|c|} \hline 
	\multirow{2}{*}{Problem ID} & \multirow{2}{*}{Method} & \multicolumn{4}{c|}{$\Delta\phi$ [\%]} & \multirow{2}{*}{Comments} \\
	\cline{3-6}
	& & $r_1 = 0.25$ & $r_2 = 0.5$ & $r_3 = 0.75$ & $r_4 = 1.0$ & \\
	\hline
	\multirow{2}{*}{Pub-1-0-SL} & Diffusion  & 0.63 & 2.88 & 8.46 & 31.25 & \multirow{2}{*}{$I=100$} \\
	\cline{2-6}
	& RM-CMFD 	     & 0.0 & 0.0 & 0.0 & 0.8 & \\ \hline
	\multirow{2}{*}{Ua-1-0-SL}  & Diffusion  & 0.53 & 2.42 & 7.39 & 30.72 & \multirow{2}{*}{$I=100$}\\
	\cline{2-6} 
	& RM-CMFD       & 0.0 & 0.0 & 0.01 & 1.44 & \\ \hline 
	\multirow{2}{*}{UD20-1-0-SL} & Diffusion & 1.14 & 4.1 & 7.85 & 35.58 & \multirow{2}{*}{$I=200$} \\ 
	\cline{2-6} 		
	& RM-CMFD      & 0.0 & 0.0 & 0.0 & 1.89 & \\ \hline 		
\end{tabular}
\vspace{-5.0mm}
\end{table}

\section{CONCLUSIONS}

The Ronen method is implemented as an iterative scheme that employs an integral expression for the current to introduce new corrected currents. These corrections are used in diffusion solver to obtain more accurate solutions. The use of CMFD and pCMFD eliminates the possible division by zero when flux gradient tend to zero. No significant differences are observed between CMFD and pCMFD in terms of relative error in the criticality of the flux.

The preliminary results indicate that the CMFD/pCMFD implementations of the Ronen method achieve high accuracy in this set of problems. The maximal deviation in criticality is $\sim$20 pcm, and the maximal deviation in the spatial distribution of the flux is less than 2\% on the boundary.  
%
The full paper will include a comprehensive benchmark of the Ronen method that will provide better understanding on its performances, also in terms of numerical stability.

%\section*{NOMENCLATURE}
%If variables are extensively used in the text, a Nomenclature section would be helpful to the readers.

\section*{ACKNOWLEDGEMENTS}

This research was supported by the Ministry of Energy as part of the scholarship program for undergraduate and graduate students in energy-related fields, contract no. 219-01-045.
% You can enter a bibliography into the document using either BibTex with the bibliography
% style file "mc2021.bst" found in the template directory or using the standard LaTeX
% thebibliography environment.

\newif\ifusebibtex
%\usebibtexfalse
\usebibtextrue

\ifusebibtex
\setlength{\baselineskip}{12pt}
\bibliographystyle{mc2021}
\bibliography{RM-MC2021}
\else
\setlength{\baselineskip}{12pt}
\begin{thebibliography}{300}
\bibitem{journal} B. Author(s), ``Title,'' \emph{Journal Name in Italic}, 
  \textbf{Volume in Bold}, pp. 34-89 (19xx).
\bibitem{proc_paper} C. D. Author(s), ``Article Title,'' \emph{Proceedings of
  Meeting in Italic}, Location, Dates of Meeting, Vol. n, pp. 134-156 
  (19xx).
\bibitem{book} E. F. Author, \emph{Book Title in Italic}, Publisher, City \&
  Country (19xx). 
\bibitem{website} ``Spallation Neutron Source: The next-generation 
  neutron-scattering facility in the United States,'' 
  \url{http://www.sns.gov/documentation/sns\_brochure.pdf} (2002).
\end{thebibliography}
\fi

%\appendix
%\gdef\thesection{APPENDIX \Alph{section}}
%\section{Sample Appendix 1}
%\label{app:a}
%If necessary, include Appendices numbered in upper case alphabetical order. This is \ref{app:a}.

\end{document}

### 2020-09-04 docs/ICTT2019/review/response2reviewers.txt
start revision of JCTT paper (special issue after ICTT26)

Dear Editor,

The authors are very thankful to the reviewers for their constructive work.
Please find hereafter the authors' response to the reviewers. Authors' replies follow after the keyword "As:".
The revised copy of the article shows all changes by colored text to support the reviewing process.
Best regards,

Daniele Tomatis
(on behalf of all authors)
Saclay, France
August 30th, 2020
***

Reviewer(s)' Comments to Author:

Reviewer: 1

Comments to the Author
There are two line numberings in the article. The comments here refer to the numbering at the far left (from 1 to 60).
As: remark from the authors - the far left numbering provided authomatically by the online system of the journal seems mismatching the position of the lines in the pages. Hence, we provided our own line numbers.

Comment 1
Page 1, line 21. I think that « to solve the neutron transport equation » is better than « to resolve the neutron transport ».
As: ***.

Comment 2
Page 5, line 15. The relation giving the optical length τ is important and deserves a better presentation. Please put this relation into a separate line.
As: Changed as recommended by the reviewer.

Comment 3
Page 5, line 35. At this point it would be very useful for the reader to have the expression of q_g with the sum limited to l=0 and 1. This will allow to better understand the equations that follow.
As: The repetion of eq. 5 with the sum over $l$ truncated to 1 would take additional space with limited amount of new information, which the author would like to avoid. The sentence "Therefore, the sum over $l$ will always be truncated in the following." has been added at the end of the paragraph in order to make the text clearer.

Comment 4
Page 6, line 13. I suggest to replace:
 « The optical lengths … »
with:
« The optical lengths τ in Eq. 6 … ».
As: Suggestion accepted.

Comment 5
Page 6, line 32. Please provide the expression defining e tilde.
As: ***.

Comment 6
Page 6, line 33. Please provide the expression defining t tilde.
As: ***.

Comment 7
Page 6, line 48. Does the term « distance » mean « travel path »?
As: here distance stands for linear extent in space along the given direction between the point at r and the outer surface of a finite body. It means travel path only for neutrons starting their first flight after emission at the specific distance S'.

Comment 8
Page 7, line 11. After the sentence « The theory of collision probability methods » put the acronym (CPM). It is already given in the abstract, but in scientific articles the main text is independent of the abstract.
As: thanks for your remark. The acronym has been inserted in the text as suggested.

Comment 9
Page 7, line 51. Does the expression {ω | …} mean projection on ω? Is this a conventional formalism? Is this equivalent to the convention <… | ….> ?
As: the symbol | stands for 'such that' from set notation, see https://en.wikipedia.org/wiki/List_of_mathematical_symbols.

Comment 10
Page 9, line 10. After « h-integration » please put « in Eq. 16 ».
As: the integration on h is introduced in Eq. 13 and it is used also for the following equations. Please, see the new form of the text that uses 'introduced in Eq. 13...'.

Comment 11
Page 10, line 13. I suggest replacing « to consider » with « to take into account ».
As: replaced with 'taking into account'.

Comment 12
Page 11, line 47. I suggest replacing « reproduced » with « assumed ».
As: text replaced as suggested by the reviewer.

Comment 13
Page 12, line 38. I suggest replacing « can not » with « cannot ».
As: text replaced as suggested by the reviewer.

Comment 14
Page 13, line 30. I suggest replacing « follows by Sood et al. » with « follows Sood et al. [13]».
As: ***.

Comment 15
Page 13, line 55. I suggest replacing « column, see Table II » with « column of Table II ».
As: The sentence has been revised to get a simpler form.

Comment 16
Page 14, line 5. I suggest replacing « communicate » with « provide ».
As: suggestion accepted.

Comment 17
Page 14, line 47. After « slab thickness » put the symbol « (r_c) ».
As: text modified as requested.

Comment 18
Page 15. Fig. 5 is very difficult to understand. 
In the caption it is written: « reflection at the right and vacuum at the left ». Usually a half slab is cut at the left, so the reflexion is expected at left.
As: New elements have been added to the text to understand better the figure, see the revised copy please. We confirm reflection at the right and vacuum at left, as written in the submitted text and performed in our calculations.

- Left figure 15. L_c is never defined. Is it r_c? Moreover, when printed in black and white, it is difficult to assign the CP or RM origin to the two clusters of results. I suggest to indicate with an arrow with RM the green cluster and with CP the orange cluster.
As: L_c --> r_c; marker '+' added to identify the cluster about RM results.

- Right figure 15. The symbol Delta in the abscissa is never defined so the right figure is not easy to understand. Moreover the units of Delta should be reported. I suppose HS-CP means half-slab computed with collision probabilities. What method is used for the FS (full-slab)? I suppose RM. If so, put (FS-RM).
As: Figure completed as requested. New sentence added: 'Equidistant meshes are used by refining gradually the cell width $\Delta$.'.

Comment 19
Page 15, line 55. Please provide a reference for the Thomas TDMA algorithm.
As: citation added as requested.

Comment 20
The RM is intended to improve the diffusion theory. In order to evaluate how much it is improved, please add inside Figs. 5, 6 and 7 the results of diffusion theory: the analytical result from the equation in table 3 and the numerical result, which is the first iteration of RM. The gain in computation time with respect to CP should be done, as well as the loss with respect to pure diffusion theory.
As: The RM was initially proposed to improve diffusion theory without a formal connection to transport. In this article it is presented as a technique to solve neutron transport by means of a diffusion equation **relying on the theory of the collision probability method**. Results from diffusion theory are far from the ones obtained by transport theory, and we only report the analytical solutions for each test case, thus avoiding also the repetition of information which is already known. The evolution of the flux solution throughout the RM iterations has already been presented by Tomatis and Dall'Osso 2011 and Gross et al. 2020.

Comment 21
Page 17, line 48. Please provide a reference to support the sentence « previous published works ».
As: references added as requested.

Comment 22
About the equation numbering inside Appendices. Conventionally the equation numbering inside Appendices does not follow the numbering inside the main text of the article. So Eq. 21 should be Eq. A.1, Eq. 22 should be Eq. A.2, Eq. 24a should be Eq. B.1a, and so on.
As: This article was prepared for the ICTT26 conference using the specific template of the same conference. Some articles presented at the conference were proposed for publication on JCTT, so we continued using the same template for the final paper. The template of the journal will be used for the revised copy.

Comment 23
Page 19, line 5. It is said: « the values from these libraries are different ». Please report approximately the magnitude order of the difference.
As: Authors indicated the numerical functions and the code versions of the scipy and numpy libraries used to calculate the values. The specific commands are also available in the program published online. The advert reader can run the same commands in the python interpreter and get the sought values. Therefore, we would like to avoid printing these roots and weights values. These roots and weights are totally different from the numbers printed in the cited textbooks in reason of the different procedure used to solve the integral by numerical quadrature. It is not relevant to quantify the differences as far as the quadrature is correctly derived and computed (verification test available online at https://github.com/ndarmage/RM1D/blob/public/CPM1D/tests/CP_empty_cylinder.py).

Comment 24
Page 20, line 14. « algebraic system equations » => « algebraic system of equations ».
As: changed as indicated.

Comment 25
Page 20, line 24. For clarity, please add after « are constructed by blocks. » the sentence:
« I is the identity matrix. ».
As: changed as indicated.

Comment 26
Page 20, line 24. I suggest to replace « with all » with « and is constituted of ».
As: changed as indicated.

Comment 27
The format of the article does not match the format required by the journal. The required format can be found at:
https://authorservices.taylorandfrancis.com/tf_quick_guide/
Please verify whether the publisher accepts other formats or it is up to the author to modify the format of his article.
As: We used the template of the conference as mentioned before. Thanks for indicating the url above by which we arrived to the webpage:
https://authorservices.taylorandfrancis.com/formatting-and-templates/
Unfortunately, there are no latex template available at this page. Hence, we contacted the editor to ask for the proper template.
We are going to submit the revised copy with the proper latex template of the journal.

As: The author are very thankful to Reviwer 1 for her/his thorough work.

Reviewer: 2

Comments to the Author
Please see the attached file.

Please find the authors' response below according to the reviewer's numbering.
i) *** do you think that the title change is suitable? ***
ii) Although the numerical tests were performed only for isotropic sources, we allow for linearly anisotropy sources in the derivation of our equations. This limitation is reminded in the conclusion, where authors have added a few changes in the text to enlight the fact that more work will ne needed in the future to study appropriately source anisotropy.
iii) the derivation of the transmission probabilities and the formulae of reciprocity (section 3.4) for entering neutrons at the boundary requires white reflection, with isotropic flux (see the end of the paragraph after eqs. 19).
iv) done

Editor's Comments to Author:

Associate Editor
Comments to the Author:
(There are no comments.)

### 2020-09-04 docs/ICTT2019/RMethod_ictt26_revised.tex
start revision of JCTT paper (special issue after ICTT26)

--- 2020-06-08 docs/ICTT2019/RMethod_ictt26.tex
@@
 \end{equation}
-with the optical length $\tau(x_1, x_2) = \int_{x_1}^{x_2}{dx' \sigma_t(x')}$.
+with the optical length
+\[ \tau(x_1, x_2) = \int_{x_1}^{x_2}{dx' \sigma_t(x')}. \]
 Contrary to other formulations, we do not include the direction cosine of the neutron velocity $\mu$ in the definition of the optical length to ease the numerical integrations in the following.
@@
 Without the external source $S$, the multiplication factor $k$ is used as eigenvalue to avoid the only trivial vanishing solution.
-Since $q$ is computed by the results of the diffusion equation in the Ronen method, $l$ can only assume the values 0 and 1, with the second moment $\varphi_1$ equal to the net current $J$.% Hereafter we consider only isotropic sources.
+Since $q$ is computed by the results of the diffusion equation in the Ronen method, the degree $l$ can only assume the values 0 and 1, with the second moment $\varphi_1$ equal to the net current $J$.
+Therefore, the sum over $l$ will always be truncated in the following.
+% Hereafter we consider only isotropic sources.
 
@@
 \end{equation}
-where $q_{(.),g,j}$ are the moments of the source $q_g$ from Eq. \ref{eq:srcg} averaged in the volume of the $j$-th cell:
+where $q_{(\cdot),g,j}$ are the moments of the source $q_g$ from Eq. \ref{eq:srcg} averaged in the volume of the $j$-th cell:
 \begin{subequations}
@@
 The current appearing in $q_{1,g,j}$, that is in case of linearly anisotropic scattering, is also to be considered as volume-averaged in the cell $j$.
-The optical lengths show the subscript $g$ because they are evaluated with the corresponding total cross section $\sigma_{t,g}$.
+The optical lengths $\tau$ in Eq.
+\ref{eq:J_tr} show the subscript $g$ because they are evaluated with the corresponding total cross section $\sigma_{t,g}$.
 For the property $E'_{n+1}(\ell) = -E_n(\ell)$, the spatial integrals of the integral exponential functions can be solved analytically by integrating on $\tau$:
@@
 $\tilde{t}_{i+1/2, x_b}$ is the transmission probability of a neutron to enter isotropically at $x_b$ and to cross the interface at $x_{i+1/2}$ without colliding hitherto.
+Their expressions can be derived straightforwardly from Eq.
+\ref{eq:J_tr} by rearranging the terms in the sum at the right hand side.
+A discussion about the transmission probability follows in section \ref{sec:bc}.
 
@@
 \ref{eq:ITE_xy} over the solid angle $d\mathbf{\Omega} = \sin \theta d\omega d \theta$ yields the scalar flux at the point $\mathbf{r}$.
-The theory of collision probability methods originates from the use of flat isotropic sources in the cells of the spatial mesh.
+The theory of collision probability methods (CPM) originates from the use of flat isotropic sources in the cells of the spatial mesh.
 The use of anisotropic sources with spatial variation in the same cells, for instance polynomial-like, is possible but leads to much more difficult expressions to solve.
@@
 J^+(\mathbf{r}) = \frac{1}{2\pi}\int_{W^+}{
-  d\omega\, | \hat{n} \cdot \mathbf{\Omega}_p | \,
+  d\omega\: \lvert \hat{n} \cdot \mathbf{\Omega}_p \rvert
   \int_0^S ds\, \text{Ki}_2\left[ \tau\left(\mathbf{r}, \mathbf{r} - s \mathbf{\Omega}_p \right)\right]
@@
         \int_0^{\ell_j}{
-            d\ell \text{Ki}_2 \left(\tau_{ji} + \sigma_j \ell \right)
+            d\ell \, \text{Ki}_2 \left(\tau_{ji} + \sigma_j \ell \right)
         }
@@
 \end{equation}
-for $i<j$, whereas $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergoing a collision.
+for $i < j$, whereas $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergoing a collision.
 The useful reciprocity and conservation properties commonly used in CPM solvers to save the total computational effort can be applied only after calculating the first flight collision probabilities.
 
-Singularity of the integrand for the $h$-integration is known in the convex part while computing the collision probabilities \cite{hebert2009applied,stamm1983methods}; this notably happens at the outer radius of the $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$.
+Singularity of the integrand for the $h$-integration introduced in Eq.
+\ref{eq:currp_cyl_atr} is known in the convex part while computing the collision probabilities \cite{hebert2009applied,stamm1983methods}; this notably happens at the outer radius of the $j$-th ring where $\hat{n}$ is perpendicular to $\mathbf{\Omega}_p$.
 However, that integral can be regularized by a suitable change of variable, see appendix \ref{sec:apx_Flurig}.
@@
 \ref{fig:sphere_tracks} is specific to the calculation of the positive radial partial currents.
-Negative partial currents need to consider the sources outside the depicted sphere of integration.
+Negative partial currents need taking into account the sources outside the depicted sphere of integration.
 
@@
 The expression for the right boundary is straightforward, implying a non-negative current.
-Reflection is always reproduced at the center in curvilinear geometries.
+Reflection is always assumed at the center in curvilinear geometries.
 
@@
 Only situations with perfectly isotropic angular flux at the boundary will be described correctly.
-At the left boundary for instance, the current can be expressed as $J(a) =  J^+ + J^- = 0$ with the entering current $J^+ = \int_0^1 { d\mu \mu \phi(a, \mu) } = - J^-$.
+At the left boundary for instance, the current can be expressed as $J(a) =  J^+ + J^- = 0$ with the entering current $J^+ = \int_0^1 { d\mu \mu \varphi(a, \mu) } = - J^-$.
 $J^-$ takes into account all contributions coming from the right of $a$ up to $b$, see Eq.
 \ref{eq:J_tr}.
-In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \phi_0(a) / 2$, yielding $J^+(x) = E_3 \left(\tau(a, x)\right)\phi_0(a)/2$, or $J^+(x) = \tilde{t}_a(x) \phi(a)/4$ using the CPM formalism (white reflection at $a$).
+In the absence of higher moments, the angular flux at the boundary becomes simply $\phi(a, \mu) \approx \varphi_0(a) / 2$, yielding $J^+(x) = E_3 \left(\tau(a, x)\right) \varphi_0(a)/2$, or $J^+(x) = \tilde{t}_a(x) \phi(a)/4$ using the CPM formalism (white reflection at $a$).
 Here, $\tilde{t}$ is the transmission probability of neutrons crossing uniformly and isotropically the surface $a$ to get to the position $x$ uncollided.
@@
 \begin{split}
-J^+(x) &\pluseq \frac{5}{4} \tilde{\phi}_2(a) \left[ 3 E_5(\tau(a, x)) - E_3(\tau(a, x)) \right],\\ &\text{ with } \tilde{\phi}_2(a) = - \frac{16}{5} \left( \frac{1}{4} \phi_0(a) + J^- \right).
+J^+(x) &\pluseq \frac{5}{4} \tilde{\varphi}_2(a) \left[ 3 E_5(\tau(a, x)) - E_3(\tau(a, x)) \right],\\ &\text{ with } \tilde{\varphi}_2(a) = - \frac{16}{5} \left( \frac{1}{4} \varphi_0(a) + J^- \right).
 \end{split}
@@
 The flux expansion at the left boundary is then
-\[ \phi(a, \mu) = \frac{1}{2} \phi_0 + \frac{3}{2} \mu \phi_1 + \frac{5}{4} \left( 3 \mu^2 - 1 \right) \tilde{\phi}_2, \]
-with $\phi_1 = J = 0$ with reflection. The derivation of the correction at the other boundary of the slab can easily be derived.
-
-Transmission probabilities of neutrons entering with anisotropic (even) distributions are now needed, but this time they can not be derived from the escape probabilities based on isotropic emission.
+\[ \phi(a, \mu) = \frac{1}{2} \varphi_0 + \frac{3}{2} \mu \varphi_1 + \frac{5}{4} \left( 3 \mu^2 - 1 \right) \tilde{\varphi}_2, \]
+with $\varphi_1 = J = 0$ with reflection. The derivation of the correction at the other boundary of the slab can easily be derived.
+
+Transmission probabilities of neutrons entering with anisotropic (even) distributions are now needed, but this time they cannot be derived from the escape probabilities based on isotropic emission.
 We only give the expression to calculate these quantities in the slab, since white reflection is generally preferred in the 1-D curvilinear geometries for reproducing more accurate physical results.
@@
 The problems are resolved in units of optical length according to the change of variable $x \leftarrow \sigma x$.
-The isotropically multiplying source becomes $q = c \phi_0 / 4\pi$ with the number of secondaries from scattering and fission events $c = (\sigma_s + \nu \sigma_f)/\sigma$.
+The isotropically multiplying source becomes $q = c \varphi_0 / 4\pi$ with the number of secondaries from scattering and fission events $c = (\sigma_s + \nu \sigma_f)/\sigma$.
 The transport equation to solve is then:
@@
 Pu-239 (PUb)& 2.84 & 0.081600 & 0.019584 & 0.225216 & 0.32640 & 1.40\\
-  H20 (refl)& 0.0 & 0.0 & 0.032640 & 0.293760 & 0.32640 & 0.90\\
+%  H20 (refl)& 0.0 & 0.0 & 0.032640 & 0.293760 & 0.32640 & 0.90\\
 \end{tabular}
@@
 
-The analytical solutions from diffusion theory are available in Table \ref{tab:adsol}, where the geometrical buckling $B_G^2$ comes as root of the transcendental equations in the last column, see Table \ref{tab:rc}.
+The analytical solutions from diffusion theory are available in Table \ref{tab:adsol}, where the geometrical buckling $B_G^2$ is given by the root of the transcendental equations in the last column.
 The multiplication factor $k_D$ of the analytical diffusion problem is obtained by equating the geometrical buckling and the material buckling $B^2_M = (\nu\sigma_f/k - \sigma_a)/D = (k_\infty/k - 1)/L^2$, where $k_\infty = \nu\sigma_f / \sigma_a$ is the multiplication factor in the infinite medium and $L^2 = D/\sigma_a$ is the diffusion area.
-The benchmark problems communicate the reference transport fundamental flux at given positions, see Table \ref{tab:rff}.
+The benchmark problems provide the reference transport fundamental flux at given positions, see Table \ref{tab:rff}.
 The scalar fluxes are all normalized to be unitary at the center.
@@
 Then, the solution by the Ronen method is sought iteratively as explained in section \ref{sec:impl}.
+Four integration points are used in the Gauss-Jacobi quadratures, yielding an error lower than 0.1\%.
+The solution by diffusion in these particular test cases is very different from the one by transport, which provides the physical solution.
 Anderson acceleration through the DAAREM algorithm (Damped Anderson Acceleration with Epsilon Monotonicity) is also used during the iteration process \cite{henderson2019damped}, reducing considerably the number of iterations to achieve residuals on the relative flux differences below $10^{-6}$.
 Its use is crucial to find the fixed point solution throughout the non-linear iterations of the RM.
+Very low convergence rates have been noticed without DAAREM, potentially leading to detect false convergence after a very high number of iterations, which means obtaining the wrong flux solution afterwards.% that does not satisfy the neutron balance equation.
 
 The calculation of half slab by CPM after setting (white) reflection at the center yields poor results due to missing contributions from the higher flux moments, see Figure \ref{fig:cpm_hslab_err}.
-The solution obtained by RM takes into account an artificial correction applied to the only second moment, reducing the flux error, but its eigenvalue solution is higher than 1 of 836 pcm on converged meshes.
-This issue, discussed in section \ref{sec:bc}, is more severe with very thin slab, like in the case PUa-1-0-SL, and disappears when the slab thickness increases beyond a few mean free paths (mfp).
+Equidistant meshes are used by refining gradually the cell width $\Delta$.
+The solution obtained by RM takes into account the artificial correction applied to the only second moment, reducing the flux error (see the green curves in the left plot), but its eigenvalue solution is higher than 1 of 836 pcm on converged meshes.
+The eigenvalue computed by CPM on half slab is lower than 1 of about 3000 pcm (see the right plot).
+This issue, discussed in section \ref{sec:bc}, is more severe with very thin slab, like in the case PUa-1-0-SL, and disappears when the slab thickness $r_c$ increases beyond a few mean free paths (mfp).
 This forces the modelling of the full slab when verifying the flux distribution for the case PUb-1-0-SL.
@@
 % solid = not hollow
-All methods computes a critical configuration for PUa-1-0-SL after unfolding the half-slab. The study to verify the fundamental flux is then only shown for the case PUb-1-0-SL.
+All methods computes a critical configuration for PUa-1-0-SL after unfolding the half-slab. The study to verify the fundamental flux is then shown only for the case PUb-1-0-SL.
 
@@
 \includegraphics[width=.8\linewidth]{cpm_hslab_err.pdf}
-\caption{Error in the half slab (PUa-1-0-SL) with white reflection at the right and vacuum at the left.}
+\caption{Error in the half slab (PUa-1-0-SL) with white reflection at the right and vacuum at the left; HS and FS indicate half slab and full slab, respectively.}
 \label{fig:cpm_hslab_err}
@@
 
-About the cases PUb, the relative error on the critical flux computed by CPM against the values from Table \ref{tab:rff} are shown in Figure \ref{fig:cpm_PUb_flxerr} with increasing number of cells ($I$) always using equivolume meshes.
+About the cases PUb, the relative error on the critical flux computed by CPM against the values from Table \ref{tab:rff} are shown in Figure \ref{fig:cpm_PUb_flxerr} for increasing number of cells ($I$) with equivolume meshes.
 The same figure shows also the results obtained by RM.
-The spherical geometry needs finer meshes to decrease the error, which is always higher near the vacuum boundary.
+Basically, RM and CPM results overlap but at the vacuum boundary where the monotonic behavior of the error trend is broken with fine meshes, leaving a residual error of about 1-2\% in the slab and in the cylinder, and higher than 3\% in the sphere.
+The spherical geometry needs finer meshes to decrease the error, which is still higher near the outer boundary.
 Refined meshes near the boundary, drawn for instance by a geometric progression with ratio less than one, can lower this error, see the program released with this publication.
-The RM results practically overlaps those obtained by the CPM, but at the vacuum boundary where the monotonic behavior of the error trend is broken with fine meshes, leaving a residual error of about 1-2\% in the slab and in the cylinder, and higher than 3\% in the sphere.
 The flux at the boundary used to reproduce the current by diffusion is approximated by a quadratic polynomial fitting the midpoint fluxes at the nearest three cells, instead of the only flux of the last cell.
 
-The number of cells in the slab is doubled indeed for taking a thickness of $2r_c$ in the calculations.
-The deviation of the multiplication factor from unity by refining the mesh is shown in Figure \ref{fig:cpm_PUb_kerr}, instead.
+The deviation of the multiplication factor from unity by refining the mesh is shown in Figure \ref{fig:cpm_PUb_kerr}.
+When unfolding the reflected slab, the number of cells in the slab is doubled indeed for taking a thickness of $2r_c$ in the calculations.
+This explains why the plotted error for the slab is higher than the one for the cylinder at a given value of $I$.
 The same trend for the three geometries is noticed, with the spherical one needing finer meshes to achieve the same level of error.
 The multiplication factor computed by RM is about the same as the one given by CPM.
-Four integration points are used in the Gauss-Jacobi quadratures, yielding an error lower than 0.1\%.
-
-\begin{figure}[hp]
+
+\begin{figure}[htbp]
 \centering
@@
 \end{figure}
-
-\begin{figure}[hp]
+%
+\begin{figure}[hbtp]
 \centering
@@
 
-The solution by CPM needs a single inversion of a full matrix with the direct solving scheme from appendix \ref{sec:CPMsolution}.
+The solution by CPM needs a single inversion of a full matrix with the direct and fast solving scheme reported in appendix \ref{sec:CPMsolution}.
 This scheme may not be suitable to problems with a high number of energy groups and spatial cells.
-The RM needs to invert several times a tridiagonal matrix, which is efficiently performed in our code by Thomas TDMA algorithm, a simplified form of Gaussian elimination that can be used to solve tridiagonal systems of equations.
-Both methods share the calculation part of the first flight escape/collision probabilities.
-Typical runtimes of the benchmark problems treated in this article are quite fast and they can be run on any laptop computers.
+The RM needs to invert several times a tridiagonal matrix, which is efficiently performed in our code by the Thomas TDMA algorithm, a simplified form of Gaussian elimination that can be used to solve tridiagonal systems of equations \cite{quarteroniNM2007}.
+Both methods share the calculation part of the first flight escape and collision probabilities.
+Typical runtimes of the benchmark problems treated in this article are quite fast (a few seconds or minutes depending on the size of the problem), and they can be easily run on any laptop computer.
 The calculation of the first flight probabilities is the most expensive part, especially in curvilinear geometries, and it should be reprogrammed in a compiled language to save runtime.
@@
 
-The Ronen Method was firstly proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux.
-This originates an iterative scheme leading to new flux distributions solved by a diffusion solver yet with the aim to fulfill the integral transport equation.
-The direct resolution of the integral equation implies the inversion of full matrices, with poor control of their conditioning.
+Initially the Ronen Method was proposed for better estimates of the diffusion coefficient by calculating the current with a higher-order transport operator and a known best-estimate neutron flux \cite{ronen2004accurate}.
+This can originate an iterative scheme leading to new flux distributions solved by a diffusion solver yet with the aim to fulfill the integral transport equation.
+The direct resolution of the integral equation, as in the collision probability method, implies the inversion of full matrices, with poor control of their conditioning.
 The solution of the diffusion equation offers many numerical advantages instead, solution speed and robustness above all.
 
-Nonetheless, the same current can be enforced in the discretized form of the diffusion equation as suggested by the CMFD that avoids the numerical issues arising with flat flux.
-This is the option adopted in this work.
+Furthermore, the same current obtained by the higher-order operator can be enforced in the discretized form of the diffusion equation as suggested by the CMFD scheme, which avoids the numerical issues arising with flat flux.
+This is also the option adopted in this work.
+In particular, the RM is here developed under the common formalism of CPM theory, thus offering a formal derivation in the framework of integral transport with the nonlinear iterations of the CMFD scheme.
+Only first flight escape probabilities are computed, by which all other kinds of probabilities are derived using conservation and reciprocity properties.
+
 The implementation of the boundary conditions is improved to reproduce the expected vanishing current in case of reflection.
-However, this correction is not sufficient to fix the limitations due to the use of white reflection, which is particularly serious in problems smaller than a mean free path.
-
-The RM is developed in this work by following the CPM formalism and theory.
-Only first flight escape probabilities are computed, by which all other kinds of probabilities are derived using conservation and reciprocity properties.
-The solutions are verified with simple one-group homogeneous problems from the benchmark test suite by Sood and al.
+However, this correction is not sufficient to remove the limitations due to the use of white reflection, which is particularly serious in problems smaller than a mean free path.
+
+The solutions are verified with simple one-group homogeneous problems and isotropic sources from the benchmark test suite by Sood and al.
 \cite{sood2003analytical}.
@@
 
-The use of Anderson acceleration in the RM iterations was crucial to find converged results, fixing the issue of slow convergence noticed in the previous published works.
+The use of Anderson acceleration implemented in the RM iterations with the DAAREM algorithm was crucial to find converged results, fixing the issue of slow convergence noticed in the previous published works \cite{tomatis2011application,gross2020high}.
 The large discrepancy on the scalar flux observed in previous works at bare vacuum boundaries has now been reduced to a few percent with respect to the reference solutions.
-This suggests that same test problems could have been affected in the past implementations by false convergence for very slowly decreasing convergence rates.
+However, it is still necessary to investigate these remaining differences at the boundary, like using for instance higher-order numerical approximations of the discretized equations.
+This strong improvement in the flux behavior suggests that the same test problems could have been affected in the past implementations by false convergence for very slowly decreasing convergence rates.
 Additional tests are on-going to verify this assertion.
@@
 
-The theory and results of this article were produced by the computer program available at \texttt{https://github.com/ndarmage/RonenMethod1D.git}.
-This program is distributed for educational purposes and basic training in transport theory, without containing any confidential material on nuclear data.
+The theory and results of this article were produced by the computer program available at \texttt{https://github.com/ndarmage/RM1D.git}.
+This program is freely distributed for educational purposes and basic training in transport theory, without containing any confidential material on nuclear data.
 
@@
 
-We setup hereafter an algebraic system equations for the unknown flux array $\vec{\phi}$ of size $(I \times G)$, flattened with the index of the spatial mesh running first.
+We setup hereafter an algebraic system of equations for the unknown flux array $\vec{\phi}$ of size $(I \times G)$, flattened with the index of the spatial mesh running first.
 The extension of the solution method to problems with external sources in submultiplicative media is straightforward.
@@
 \ref{eq:cpm_syseqns} are constructed by blocks.
-The matrix $\mathbf{P}$ is block diagonal with all (transposed) matrices of reduced collision probabilities per group, placed in increasing order from the fast groups, which are assigned to the lowest values of the index $g$ as usual.
+$\mathbf{I}$ is the identity matrix.
+The matrix $\mathbf{P}$ is block diagonal and it is constituted of (transposed) matrices of reduced collision probabilities per group, placed in increasing order from the fast groups, which are assigned to the lowest values of the index $g$ as usual.
 The matrix $\mathbf{S}$ is composed by $G \times G$ diagonal blocks with elements $[\sigma_{s, g \leftarrow g',j}\delta_{ij}, \, i, j=1, \ldots, I]$, contrary to the matrix $\mathbf{F}$ which has only G blocks set by columns and with elements $[\nu\sigma_{f, g, j}\delta_{ij}, \, i, j=1, \ldots, I]$.

### 2020-09-04 docs/ICTT2019/scripts/analyze_results.py

@@ -79,11 +79,17 @@ refflx = {
 
 def get_allIs(list_of_files, case, RM=False):
     case_files = [f for f in list_of_files if get_case(f, RM) == case]
-    return sorted(list(set([get_I(c) for c in case_files])))
+    allIs = sorted(list(set([get_I(c) for c in case_files])))
+    if 0 in allIs:
+        allIs.remove(0)
+    return allIs
 
 
 def get_I(fn):
-    return int(fn.split('_I')[1].replace('.npy', ''))
+    if '_I' in fn:
+        return int(fn.split('_I')[1].replace('.npy', ''))
+    else:
+        return 0
 
 
 def get_case(fn, RM=False):
@@ -146,16 +152,19 @@ def plot_cpm1d_hslab_error(L, I_hslab, figname):
                     )
             rerr = (1 - flw[0,:][::-1] / flx[0,:I])*100
             a1.plot(xim(x), rerr, label='$\Delta_{RM} = %.3e$' % V[0]
-                    #, marker=next(ms)
+                    , marker='+'
                     , linestyle = next(ls), color='C2'
                     )
         
     a1.legend()
-    a1.set_xlabel('$x/L_c$')
-    a1.set_ylabel('$1 - \phi_{HS}/\phi_{FS} \: (\%)$')
-    a2.plot(Ds[shw], ks[shw], label='full-slab (FS)')
-    a2.plot(Ds[shw], hs[shw], label='half-slab (HS-CP)', ls='--')
-    # a2.plot(Ds[shw], ws[shw], label='half-slab (HS-RM)', ls='-.')
+    a1.set_xlabel('$x/r_c$')
+    a1.set_ylabel('$| 1 - \phi_{HS}/\phi_{FS} | \: (\%)$')
+    a2.plot(Ds[shw], ks[shw], label='FS-CP')
+    a2.plot(Ds[shw], abs(hs[shw]), label='HS-CP', ls='--')
+    # print(ks[shw])
+    # print(hs[shw])
+    # print(ws[shw])
+    a2.plot(Ds[shw], abs(ws[shw]), label='HS-RM', ls='-.')
     a2.set_ylabel('$1-k$ (pcm)')
     a2.set_xlabel('$\Delta$')
     a2.set_xscale('log')
@@ -305,12 +314,12 @@ if __name__ == "__main__":
         # print(I_hslab)
         # raise RuntimeError('lists differ')
 
-    if False:
[…]

### 2020-09-04 docs/MC2021/Abstract/Gross_mc2021-V2.tex

@@
 The CMFD/pCMFD implementations are validated against analytic solutions of homogeneous and heterogeneous configurations using one, two, and three energy groups.
-The validation is performed for the criticality eigenvalue and in some cases also for the spatial distribution of the neutron flux.
+The validation is performed for the criticality eigenvalue and, in some cases, also for the spatial distribution of the neutron flux.
 The scattering is assumed to be isotropic in all cases.
@@
 
-Full core neutron transport calculations are a demanding task and often faster multigroup neutron diffusion solvers are used.
+Full core neutron transport calculations are a demanding task, and often faster multigroup neutron diffusion solvers are used.
 However, the diffusion approximation is invalidated near strong absorbing materials, interfaces, and boundaries, where strong gradients appear or in case anisotropic scattering is pronounced.
@@
 
-The Ronen method was implemented numerically using the Coarse Mesh Finite Difference (CMFD) scheme in the diffusion solver and employing correction factors the for leakage terms in the balance equation~\cite{Tomatis-2011}.
+The Ronen method was implemented numerically using the Coarse Mesh Finite Difference (CMFD) scheme in the diffusion solver and is employing correction factors for the leakage terms in the balance equation~\cite{Tomatis-2011}.
 The current correction factors were derived from the correction currents, which were estimated by the integral transport theory~\cite{Gross-2020}.
@@
 In a sense, the pCMFD is a more natural choice of the Ronen method scheme, since the implementation of pCMFD can be naturally formulated in terms of partial currents.
-The performances of both implementations, CMFD and pCMFD, are thoroughly evaluated against an analytic benchmarks for the criticality eigenvalue and the spatial distribution of the associated critical eigenflux~\cite{Sood2003}.
+The performances of both implementations, CMFD and pCMFD, are thoroughly evaluated against analytic benchmarks for the criticality eigenvalue and the spatial distribution of the associated critical eigenflux~\cite{Sood2003}.
 
@@
 (2003)~\cite{Sood2003} presents one-dimensional homogeneous and heterogeneous critical configurations, including the associated one-, two-, and three-group cross-sections.
-For some problems, the spatial distribution of the flux is given at certain points.
+For some problems, the spatial distribution of the flux is given at specific points.
 %
@@
 The Ronen method is implemented as an iterative scheme that employs an integral expression for the current to introduce new corrected currents.
-These corrections are used in diffusion solver to obtain more accurate solutions.
-The use of CMFD and pCMFD eliminates the possible division by zero when flux gradient tend to zero.
+These corrections are used in a diffusion solver to obtain more accurate solutions.
+The use of CMFD and pCMFD eliminates the possible division by zero when the flux gradient tends to zero.
 No significant differences are observed between CMFD and pCMFD in terms of relative error in the criticality of the flux.
@@
 %
-The full paper will include a comprehensive benchmark of the Ronen method that will provide better understanding on its performances, also in terms of numerical stability.
+The full paper will include a comprehensive benchmark of the Ronen method that will provide a better understanding of its performances, also in terms of numerical stability.
 

### 2020-09-04 FD1dMGdiff/data/SoodPNE2003.py
complete merge of JCTT-revision and get new test cases

@@ -22,6 +22,7 @@ Pu-239 (b) 2.84 0.081600 0.019584 0.225216 0.32640 1.40
 H2O (refl) 0.0  0.0      0.032640 0.293760 0.32640 0.90
 """
 
+
 Table9 = \
 """
 # Material nu       Sf       Sc       Ss       St      c
@@ -30,6 +31,7 @@ U-235  (b) 2.797101 0.065280 0.013056 0.248064 0.32640 1.3194202
 U-235  (c) 2.707308 0.065280 0.013056 0.248064 0.32640 1.3014616
 U-235  (d) 2.679198 0.065280 0.013056 0.248064 0.32640 1.2958396
 """
+
 
 # water from Table 13 has same c, but different st
 Table13 = \
@@ -205,14 +207,14 @@ def calc_kinf(nsf, st=None, ss0=None, chi=None, flx_inf=None):
 if __name__ == "__main__":
 
     lg.info("*** Check homogeneous cross sections data ***")
-    ref_kinf = {'PUa': 2.612903,  # problem 1
-                'PUb': 2.290323,  # problem 5
-                'Ua': 2.250000,   # problem 11
-                'Ub': 2.330917,   # problem 15
-                'Uc': 2.256090,   # problem 17 (communicated 2.256083)
-                'Ud': 2.232665,   # problem 19 (communicated 2.232667)
+    ref_kinf = {'PUa': 2.612903,   # problem 1
+                'PUb': 2.290323,   # problem 5
+                'Ua': 2.250000,    # problem 11
+                'Ub': 2.330917,    # problem 15
+                'Uc': 2.256090,    # problem 17 (communicated 2.256083)
+                'Ud': 2.232665,    # problem 19 (communicated 2.232667)
                 'UD2O': 1.133333,  # problem 21
-                'Ue': 2.1806667  # problem 29
+                'Ue': 2.1806667    # problem 29
                }
     
     for m, xs in materials.items():

### 2020-09-04 FD1dMGdiff/tests/Sood_PUx-H2Ox-1-0-x.py

@@ -19,7 +19,7 @@ from data.SoodPNE2003 import *
 from FDsDiff1D import input_data, solver_options, run_calc_with_RM_its
 from GeoMatTools import geomprogr_mesh, equivolume_mesh
 
-odir = "../output"
+odir = "output"  # output folder of test cases
 refdir = os.path.join("..", "..", "CPM1D", "tests", "output")
 
 
@@ -95,7 +95,7 @@ if __name__ == "__main__":
     #     r = np.append(r, equivolume_mesh(Ix, Lb, Le, geo)[1:])
     
     # data = input_data(xs_media, media, r, geo, LBC=LBC, RBC=RBC)
-    # slvr_opts = solver_options(iitmax=5, oitmax=5, ritmax=300, CMFD=True,
+    # slvr_opts = solver_options(iitmax=5, oitmax=5, ritmax=200, CMFD=True,
     #                            pCMFD=False, Anderson_depth='auto')
     # filename = os.path.join(odir, case + "_LBC%dRBC%d_I%d" %
     #                         (LBC, RBC, I))

### 2020-09-04 docs/MC2021/Abstract/Gross_mc2021-V2.tex
first iteration on the MC2021 ext abstract

@@
 
+\vspace{-4.5mm}
+
 \begin{abstract}
@@
 The Ronen method (RM) is designed to overcome the inaccuracies of the diffusion approximation by correcting the diffusion currents, using the integral transport theory~\cite{Tomatis-2011,Gross-2020,Tomatis-2020}.
-The underlying hypothesis of the Ronen method is the modification of the current such that the neutron current approximated by Fick's law, $\bm{J}^D\rE$, will approach the accurate one, calculated by transport theory $\bm{J}\rE$, with the addition of a correction current $\delta\bm{J}\rE$,
-\begin{align}
-\label{eq:Fick}
-& \bm{J}\rE \cong \bm{J}^D\rE + \delta\bm{J}\rE \\ 
-& \bm{J}^D\rE = -D\rE\bnabla\phi\rE  \,\,.
-\end{align}
-Ronen also suggested an iterative update of the diffusion coefficients ($k$ is the iteration index) ~\cite{Ronen-2004},
+The underlying hypothesis of the RM is the modification of the current calculated by the diffusion solver in order to reproduce the one obtained by an integral transport operator, which is assumed to be more accurate.
+This implies an iterative scheme since the more accurate current is determined with the solution of the diffusion calculation.
+
+\vspace{-1.5mm}
+
+Originally, Ronen suggested to update the diffusion coefficient as ($k$ is the iteration index)~\cite{Ronen-2004}
 \begin{equation}
@@
 
-The Ronen method was implemented numerically using the Coarse Mesh Finite Difference (CMFD) scheme in the diffusion solver and is employing correction factors for the leakage terms in the balance equation~\cite{Tomatis-2011}.
-The current correction factors were derived from the correction currents, which were estimated by the integral transport theory~\cite{Gross-2020}.
-This implementation eliminated the divergence problem in Eq.~\eqref{eq:RM-it} for small flux gradients and accurately reproduced the criticality eigenvalue and the associated eigenflux calculated by a reference discrete ordinates code.
+Later, the RM was implemented in the diffusion solver using the Coarse Mesh Finite Difference (CMFD) scheme, thus employing correction factors for the leakage terms in the discretized form of the balance equation~\cite{Tomatis-2011,Gross-2020}.
+Basically, a correction to the current approximated by Fick's law, $\bm{J}^D$, was introduced,
+\begin{align}
+\label{eq:Fick}
+& \bm{J}\rE = \bm{J}^D\rE + \delta\bm{J}\rE \\ 
+& \bm{J}^D\rE = -D\rE\bnabla\phi\rE,
+\end{align}
+with $\delta\bm{J}$ determined through the integral transport operator.
+This implementation eliminated the divergence problem in Eq.~\eqref{eq:RM-it} for small flux gradients and accurately reproduced the criticality eigenvalue and the associated eigenflux calculated by a reference discrete-ordinates code.
 
@@
 
-In this study, the Ronen method is implemented using a variant of the CMFD method, i.e., the partial-currents CMFD (pCMFD)~\cite{Cho-2003}.
-In a sense, the pCMFD is a more natural choice of the Ronen method scheme, since the implementation of pCMFD can be naturally formulated in terms of partial currents.
+In this study, the RM is implemented using a variant of the CMFD method, i.e., the partial-currents CMFD (pCMFD)~\cite{Cho-2003}.
+In a sense, the pCMFD is a more natural choice for the RM, since the implementation of pCMFD can be naturally formulated in terms of partial currents.
 The performances of both implementations, CMFD and pCMFD, are thoroughly evaluated against analytic benchmarks for the criticality eigenvalue and the spatial distribution of the associated critical eigenflux~\cite{Sood2003}.
@@
 \label{eq:balance}
-J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g},
+J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g} \quad \forall i,
 \end{equation}
@@
 
-\vspace{-1.5mm}
+\vspace{-2.5mm}
 
-The integral expressions for the net current is used with the scalar flux in the emission source to obtain a more accurate estimation of the net current.
-In the Ronen method implementation, the correction terms $\delta J$ are obtained  iteratively as the difference between the net current $J$ and the diffusion-approximated current $\jD$,
+The integral expression for the net current is evaluated by using the scalar flux in the emission source to obtain a more accurate estimation of the net current.
+In the RM implementation, the correction terms $\delta J$ are obtained  iteratively as the difference between the net current $J$ and the diffusion-approximated current $\jD$,
 \begin{equation}
@@
 
-\vspace{-1.5mm}
+\vspace{-2.5mm}
 
@@
 In the pCMFD implementation~\cite{Cho-2003}, two correction terms are introduced per interface, consistent with the partition of the net current into two partial ones, i.e., $J = \jp - \jm = \jD + \delta J^+ + \delta J^-$, defined by $\delta \jp _{i+\hzi} = -\delta D^+ _{i+\hzi} \phi_i$ and $\delta \jm _{i+\hzi} = -\delta D^- _{i+\hzi} \phi_{i+1}$~\cite{Jarrett-2016,Zhu-2016}.
-By equally distributing the diffusion-approximated current on the partial currents, the relations between the net current, the diffusion-approximated currents and the correction terms are given by
+These correction terms are then obtained by equally distributing the diffusion-approximated current on the partial currents,
 \begin{equation}
@@
 
-\vspace{-5.5mm}
-
+\vspace{-6.5mm}
+%
 %\begin{figure}[!htb]
@@
 %
-The deviations between the criticality eigenvalues, calculated using the CMFD and pCMFD implementations of the Ronen method ($\krm$, and $\kd$ for pure diffusion), and the reference eigenvalue ($\kref=1$) are shown in Table~\ref{table:res1} for a selected set of problems.
-The deviations are shown in both units of reactivity ($\Delta\rho = \left(\sfrac{1}{\kref}- \sfrac{1}{\kd,\krm}\right)\times 10^5$ [pcm]), and in relative error in the critical width ($\Delta w = \text{abs}\left[ \sfrac{ \left( \rc-\rcref\right)}{\rcref}\times 100\right]$ [\%]), where $r$ is the critical dimension, i.e., the distance from the fuel's center to one of the boundaries.
+The deviations between the criticality eigenvalues, calculated using the CMFD and pCMFD implementations of the RM ($\krm$, and $\kd$ for pure diffusion), and the reference eigenvalue ($\kref=1$) are shown in Table~\ref{table:res1} for a selected set of problems.
+The deviations are shown in both units of reactivity ($\Delta\rho = \left(\sfrac{1}{\kref}- \sfrac{1}{\kd,\krm}\right)\times 10^5$ [pcm]), and in relative error in the critical width ($\Delta w = \text{abs}\left[ \sfrac{ \left( \rc-\rcref\right)}{\rcref}\times 100\right]$ [\%]), where $r_c$ is the critical dimension, i.e., the distance from the fuel's center to one of the boundaries.
 The number of cells within the water region is $I_w$.
@@
 %
-\begin{table}[!htb]
+\begin{table}[hbt]
 	\vspace{-7.5mm}	
@@
 %
-\begin{table}[!htb]
+\begin{table}[htb]
 	\vspace{-5.5mm}
@@
 
+\vspace{-6.5mm}
+
 \section{CONCLUSIONS}
@@
 No significant differences are observed between CMFD and pCMFD in terms of relative error in the criticality of the flux.
+
+\vspace{-1.5mm}
 
@@
 
+\vspace{-2.5mm}
+
 \section*{ACKNOWLEDGEMENTS}
@@
 % thebibliography environment.
+
+\vspace{-2.5mm}
 

### 2020-09-06 docs/MC2021/Abstract/Gross_mc2021-V2.tex
Update Gross_mc2021-V2.tex

@@
 Originally, Ronen suggested to update the diffusion coefficient as ($k$ is the iteration index)~\cite{Ronen-2004}
-\begin{equation}
-\label{eq:RM-it}
-D^{(k+1)}\rE = \left. - \lvert \bm{J}^{(k)}\rE \rvert \middle/ \lvert \bnabla \phi^{(k)}\rE \rvert. \right.
+\begin{equation}\label{eq:RM-it}
+	D^{(k+1)}(x,E) = -\frac{\displaystyle \frac{1}{2}\int_0^a dx' E_2[\sigma(E)\lvert
+		x-x'\rvert]\operatorname{Sgn}(x-x')q^{(k)}(x',E)}
+	{\partial \phi^{(k)}(x,E)/\partial x}.
+%\label{eq:RM-it}
+%D^{(k+1)}\rE = \left. - \lvert \bm{J}^{(k)}\rE \rvert \middle/ \lvert \bnabla \phi^{(k)}\rE \rvert. \right.
 \end{equation}
@@
 \label{eq:balance}
-J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g} \quad \forall i,
+J_{i+\hzi,g} - J_{i-\hzi,g} + \sigma_{i,g} \phi_{i,g} = q_{i,g} \quad \forall i,g,
 \end{equation}
@@
 \frac{\phi_{i+1,g} - \phi_{i,g}}{(\Delta_{i+1} + \Delta_i)/2},
-\quad \text{where }
+\,\, \text{where }
+%D_{i+\hzi,g} = \left\{\begin{array}{ll}
+%	-J_{i+\hzi,g} \frac{(\Delta_{i+1} + \Delta_i)/2}{\phi_{i+1,g} - \phi_{i,g}}, & \text{for } J_{i+\hzi,g} \ne 0\\
+%	0, & \text{otherwise}
+%\end{array}\right.
 D_{i+\hzi,g} = \frac{\Delta_i D_{i,g} + \Delta_{i+1} D_{i+1,g}}
@@
 The deviations between the criticality eigenvalues, calculated using the CMFD and pCMFD implementations of the RM ($\krm$, and $\kd$ for pure diffusion), and the reference eigenvalue ($\kref=1$) are shown in Table~\ref{table:res1} for a selected set of problems.
-The deviations are shown in both units of reactivity ($\Delta\rho = \left(\sfrac{1}{\kref}- \sfrac{1}{\kd,\krm}\right)\times 10^5$ [pcm]), and in relative error in the critical width ($\Delta w = \text{abs}\left[ \sfrac{ \left( \rc-\rcref\right)}{\rcref}\times 100\right]$ [\%]), where $r_c$ is the critical dimension, i.e., the distance from the fuel's center to one of the boundaries.
-The number of cells within the water region is $I_w$.
+The deviations are shown in both units of reactivity ($\Delta\rho =  (\kref^{-1}-k^{-1})\times 10^5$ [pcm]), and in relative error in the critical width ($\Delta L =  (L_c-L_{c,\text{ref}}) / L_{c,\text{ref}}$ [\%]), where $L_c$ is the critical dimension, i.e., the distance from the fuel's center to one of the boundaries.
+The number of cells in the water region is half of that in the fuel region (where applied).
 %
-The deviations between the CMFD normalized flux and the reference analytic solutions,  $\Delta\phi = \left[\sfrac{\left(\phirm - \phiref\right)}{\phiref}\right]\times 100$ [\%], are shown in Table~\ref{table:res2} for a selected set of problems.
+The deviations between the CMFD normalized flux and the reference analytic solutions,  $\Delta\phi = (\phirm - \phiref)/\phiref$ [\%], are shown in Table~\ref{table:res2} for a selected set of problems at positions $L_i$.
 %
@@
 	\centering
-	\small
 	\caption{\bf Deviations of the eigenvalues \keff \ calculated by the RM from criticality.}
 	\label{table:res1} 
-  \begin{tabular}{|l|l|c|c|c|c|c|} \hline 
-	\multirow{2}{*}{Problem ID} & \multirow{2}{*}{Method} & \multicolumn{4}{c|}{$\Delta\rho$ [pcm], ($\Delta w$ [\%])} & \multirow{2}{*}{Comments} \\ 
-	\cline{3-6}
-	&  	 & $I_1 = 50$   & $I_2 = 100$ & $I_3 = 150$ & $I_4 = 200$    & \\ 
+	\small
+\begin{tabular}{|l|l|c|c|c|c|c|c|} \hline 
+	\multirow{2}{*}{Problem ID} & \multirow{2}{*}{Method} & \multicolumn{6}{c|}{$\Delta\rho$ [pcm], ($\Delta L$ [\%])} \\ 
+	\cline{3-9}
+	&  	 & $I = 5$ & $I = 10$ & $I = 25$ & $I = 50$ & $I = 100$ & $I = 200$ \\ 
 	\hline
-	\multirow{3}{*}{PUa-1-0-SL} 		 & Diffusion  & -12,099,(-)  & -12,108,(-) & -12,109,(-) &-12,110,(-)   & \multirow{2}{*}{}\\ 
-	\cline{2-6}
-	& RM-CMFD  & -10, (0.016) & -3, (0.005) & -1, (0.002) & 0, (0.002)      & \multirow{2}{*}{}\\ 
-	\cline{2-6}
-	& RM-pCMFD & -10, (0.016) & -3, (0.005) & -1, (0.002) & -1, (0.0) & \\ 
+	\multirow{3}{*}{} & Diffusion & -10,983,(-) & -11,826,(-) & -12,065,(-) & -12,099,(-) & -12,108,(-) & -12,110,(-) \\ 
+	\cline{2-9}
+	PUa-1-0-SL & CMFD  & -851,(1.257) & -241,(0.353) & -41,(0.062) & -10,(0.016) & -3,(0.005) & 0,(0.002) \\ 
+	\cline{2-9}
+	& pCMFD & -847,(1.257) & -241,(0.353) & -41,(0.062) & -10,(0.016) & -3,(0.005) & -1,(0.0) \\ 
 	\hline
-	\multirow{3}{*}{Ua-1-0-SL} 		     & Diffusion  & -7,541, (-)  & -7,550, (-) & -7,552, (-)  & -7553, (-)  & \multirow{2}{*}{}\\ 
-	\cline{2-6}
-	& RM-CMFD  & -19, (0.027)  & -5, (0.006) & -2, (0.002)  & -1, (0.0)  & \multirow{2}{*}{}\\ 
-	\cline{2-6}
-	& RM-pCMFD & -19, (0.027)  & -5, (0.006) & -2, (0.002)  & -1, (0.0)	  & \\ 
+	\multirow{3}{*}{} & Diffusion & -6,309,(-) & -7,239,(-) & -7,503,(-) & -7,541,(-) & -7,550,(-) & -7553,(-) \\ 
+	\cline{2-9}
+	Ua-1-0-SL & CMFD  & -1,507,(2.286) & -435,(0.644) & -75,(0.109) & -19,(0.027) & -5,(0.006) & -1,(0.0) \\ 
+	\cline{2-9}
+	& pCMFD & -1,507,(2.286) & -435,(0.644) & -75,(0.109) & -19,(0.027) & -5,(0.006) & -1,(0.0) \\ 
 	\hline
-	\multirow{2}{*}{PUa-H2O(0.5)-1-0-SL} & Diffusion  & -15,921, (-) & -15,927, (-) & -15,928, (-) & -15,928, (-) & \multirow{2}{*}{$I_w = 0.5\times I_f$} \\ 
-	\cline{2-6}
-	& RM-CMFD  & -8, (0.011)  & -3, (0.005) & -3, (0.001)	& -1, (0.001) &  \\ 
-	\cline{2-6}
-	& RM-pCMFD &-8, (0.011)	& -3, (0.005) & -1, (0.001)	& -1, (0.001) & \\ 
+	\multirow{2}{*}{} & Diffusion & -15,244,(-) & -15,756,(-) & -15,901,(-) & -15,921,(-) & -15,927,(-) & -15,928,(-)  \\ 
+	\cline{2-9}
+	PUa-H2O & CMFD  & -319,(0.531) & -86,(0.144) & -15,(0.022) & -8,(0.011) & -3,(0.005) & -1,(0.001) \\ 
+	\cline{2-9}
+	(0.5)-1-0-SL & pCMFD & -320,(0.531) & -86,(0.142) & -14,(0.022) & -8,(0.011) & -3,(0.005) & -1,(0.001) \\ 
 	\hline
@@
 \end{table}
-%
+\vspace{-5.0mm}
 \begin{table}[htb]
@@
 	\centering	
-	\small
 	\caption{\bf Deviations of the normalized flux calculated by the RM from the analytic solution.}
 	\label{table:res2} 
-	\begin{tabular}{|c|c|c|c|c|c|c|} \hline 
-	\multirow{2}{*}{Problem ID} & \multirow{2}{*}{Method} & \multicolumn{4}{c|}{$\Delta\phi$ [\%]} & \multirow{2}{*}{Comments} \\
+	\small
+	\begin{tabular}{|c|c|c|c|c|c|} \hline 
+	\multirow{2}{*}{Problem ID} & \multirow{2}{*}{Method} & \multicolumn{4}{c|}{$\Delta\phi$ [\%]}  \\
 	\cline{3-6}
-	& & $r_1 = 0.25$ & $r_2 = 0.5$ & $r_3 = 0.75$ & $r_4 = 1.0$ & \\
+	& & $L_1 = 0.25$ & $L_2 = 0.5$ & $L_3 = 0.75$ & $L_4 = 1.0$  \\
 	\hline
-	\multirow{2}{*}{Pub-1-0-SL} & Diffusion  & 0.63 & 2.88 & 8.46 & 31.25 & \multirow{2}{*}{$I=100$} \\
+	\multirow{2}{*}{Pub-1-0-SL} & Diffusion  & 0.6392 & 2.8850 & 8.4621 & 31.2535  \\
 	\cline{2-6}
-	& RM-CMFD 	     & 0.0 & 0.0 & 0.0 & 0.8 & \\ \hline
-	\multirow{2}{*}{Ua-1-0-SL}  & Diffusion  & 0.53 & 2.42 & 7.39 & 30.72 & \multirow{2}{*}{$I=100$}\\
+	$(I=100)$ & CMFD 	     & 0.0048 & 0.0002 & 0.0039 & 0.8033  \\ \hline
+	\multirow{2}{*}{Ua-1-0-SL}  & Diffusion  & 0.5307 & 2.4284 & 7.3924 & 30.7287 \\
 	\cline{2-6} 
-	& RM-CMFD       & 0.0 & 0.0 & 0.01 & 1.44 & \\ \hline 
-	\multirow{2}{*}{UD20-1-0-SL} & Diffusion & 1.14 & 4.1 & 7.85 & 35.58 & \multirow{2}{*}{$I=200$} \\ 
+	$(I=100)$ & CMFD       & 0.0053 & 0.0002 & 0.0096 & 1.4473  \\ \hline 
+	\multirow{2}{*}{UD20-1-0-SL} & Diffusion & 1.1404 & 4.1067 & 7.8579 & 35.5854  \\ 
 	\cline{2-6} 		
-	& RM-CMFD      & 0.0 & 0.0 & 0.0 & 1.89 & \\ \hline 		
+	$(I=200)$& CMFD      & 0.0006 & 0.0030 & 0.0091 & 1.8900  \\ \hline 		
 \end{tabular}
@@
 
-This research was supported by the Ministry of Energy as part of the scholarship program for undergraduate and graduate students in energy-related fields, contract no. 219-01-045.
+This research was supported by the Ministry of Energy as part of the scholarship program for undergraduate and graduate students in energy-related fields, contract no. 219-11-045.
 % You can enter a bibliography into the document using either BibTex with the bibliography
